### 2021-05-16 R/ARR.Rmd

---
title: "New Effect Sizes: Acclimation Response Ratio (ARR)"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## ARR (Acclimation Response Ratio)

### Point estimate and definition

$$
\text{ARR} = \frac{ \text{CT}_{\text{max}[T_2]} - \text{CT}_{\text{max}[T_1]}}{T_2 - T_1},
$$ where *T* stands for temperature in Celsius and $T_2 > T_1$.

### Sampling variance for AAR

#### Independent case

$$
s^2(\text{AAR}) = \left( \frac{1} {T_2 - T_1} \right)^2 
\left( \frac{sd^2_{[T_1]}} {n_{[T_1]}} + \frac{sd^2_{[T_2]}} {n_{[T_2]}} \right).
$$

#### Dependent case

$$
s^2(\text{AAR}) = \left( \frac{1} {T_2 - T_1} \right)^2 
\left( \frac{sd^2_{[T_1]} + sd^2_{[T_2]} - r_{[T_1T_2]}sd_{[T_1]}sd_{[T_2]}} {n} 
\right).
$$

### Basics about variance

See <https://en.wikipedia.org/wiki/Variance>

Adding a constant ($a$) does not change the variance of a random variable $X$. $$
\operatorname{Var}(X+a)=\operatorname{Var}(X)
$$

Multiplying a constant ($a$) does increase the variance of $X$ by $a^2$.

$$
\operatorname{Var}(aX)=a^2\operatorname{Var}(X)
$$

When we consider two random variables $X$ and $Y$, we need to know their covariance.

$$
\operatorname{Var}(aX\pm bY)=a^2\operatorname{Var}(X)+b^2\operatorname{Var}(Y) \pm 2ab\operatorname{Cov}(X,Y)
$$

### 2021-05-17 MS/ms.Rmd
Adding the MS

---
title: "Meta-analytic approaches and new effect sizes to account for treatment differences across studies in comparative physiology"
author: Daniel W.A. Noble, Patrice Potter, Sammy Burke, Szymek Drobniak, Malgorzata Lagisz, Rose O’Dea, Shinichi Nakagawa
date: "`r Sys.Date()`"
bibliography: ../bib/refs.bib
csl: ../bib/the-journal-of-experimental-biology.csl
output: 
  bookdown::word_document2:
    toc: no
    toc_depth: 6
    number_sections: false
    reference_docx: template.docx
  bookdown::html_document2:
    code_folding: hide
    number_sections: no
    toc: yes
    toc_depth: 6
    toc_float: yes
    bibliography: refs.bib
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
  knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
  ## numbers >= 10^5 will be denoted in scientific notation,		  ## numbers >= 10^5 will be denoted in scientific notation,
    ## and rounded to 2 digits		  ## and rounded to 2 digits
    options(digits = 2)
```

# **Abstract**

Meta-analysis is a tool that provides comparative physiologists with powerful, unbiased and quantitatively informed answers to topical research questions by synthesising effect sizes across disparate studies. Distilling published research results into standardised effect sizes that can be weighted by their sample size (i.e., inverse sampling variance) and compared across broad sets of research designs, study systems and species is its core objective and strength. Estimating overall effect sizes, and understanding what drives effect variability, provides opportunities to model how organisms will respond to pressing global challenges. Despite this ambition, research designs in comparative physiology can appear, at the outset, as being vastly different to each other (e.g., using different temperatures or treatment dosages). Differences in treatments across studies has led many to believe that meta-analysis is an exercise in comparing “apples with oranges”. Here, we dispel this myth by showing how standardised effects sizes can be used in conjunction with powerful multi-level meta-analytic models to both account for factors driving differences across studies and make them more comparable. In addition, we derive new effect size measures that provide comparative physiologists with a means to directly make effect sizes comparable without the need to resort to more complex statistical models that may be harder to interpret. Our ‘new’ effect sizes and corresponding sampling variances help physiologists deal with temperature and dosage differences across studies; allowing researchers to compare both mean differences (e.g., Q10 to compare mean differences in physiological rates over 10 degrees) and associated differences in variance (e.g, SQ10 for comparing variability in in physiological rates over 10 degrees) for physiological traits. The new effect sizes we propose, in combination with existing meta-analytic models, will pave the way for comparative physiologists to explore exciting new questions by making results from large-scale data sets from the literature more accessible and widely interpretable.

### 2021-05-17 MS/ms.Rmd
Adding some refs, just getting ideas on paper

@@
 ---
-title: "Meta-analytic approaches and new effect sizes to account for treatment differences across studies in comparative physiology"
+title: "Meta-analytic approaches and new effect sizes for treatment effects in comparative physiology"
 author: Daniel W.A. Noble, Patrice Potter, Sammy Burke, Szymek Drobniak, Malgorzata Lagisz, Rose O’Dea, Shinichi Nakagawa
@@
 
-# **Abstract**
+## **Abstract**
 
@@
 The new effect sizes we propose, in combination with existing meta-analytic models, will pave the way for comparative physiologists to explore exciting new questions by making results from large-scale data sets from the literature more accessible and widely interpretable.
+
+## **Introduction**
+Meta-analysis provides unbiased and quantitatively informed answers to research questions in comparative physiology by using a transparent and reproducible search strategy to synthesise research results across studies and identify sources of variation [@Nakagawa2017; @Gurevitch2018; @Cooper2009; @Arnqvist1995; @Koricheva2013].
+Meta-analysing independent studies provides greater statistical power and precision than what any individual study on its own would be able to provide on a given question - particularly given that most studies are already under-powered in ecological and evolutionary research [@Forstmeier2017; @Jennions2003].
+By expressing study effects on a common scale (i.e., effect size) a meta-analyst can gain broader insight into the direction and efficacy of a particular treatment effect or strength of a relationship between two variables of interest [@Gurevitch2018; @Koricheva2013].
+A critically important feature of meta-analaysis that provides improved precision when estimating overall effects is the ability to account for sampling error - this can be derived assuming the sampling distribution of a given effect size is known [].
+
+Despite the widespread adoption and well established methodological procedures of meta-analysis it has been criticised for mixing 'apples and oranges'; in otherwords, mixing effects from studies that lack comparability [@Arnqvist1995; @Gallo1979; @Carpenter2020; @Stewart2010].
+Lack of comparability could result from studies differing in experimental design, species, measurement variables and sampling units, which can impact the generalisability of meta-analytic results [@Arnqvist1995; @Stewart2010].
+Indeed, study specific differences in comparative physiology are widspread.
+For example, experimental designs can vary in the temperatures that they apply or in the dosages of chemical modifiers used in experimental treatments [e.g., ].
+They often inlcude a diversity of study species.
+
+The goal of our review is to reassure comparative physiologists that heterogeneity among effect sizes can be comfortably dealt with through modifications of existing effect sizes measures and using multilevel meta-regression models.
+We first conduct a survey of published meta-analyses in the field of comparative physiology to gauge methodological and meta-analytic practices - assessing what types of effect sizes are commonly used, how often effect size estimates are impacted by continuous treatment differences and whether meta-analytic models (i.e., models that account for sampling variance) are commonly applied.
+We then introduce new effect sizes and their assocaited sampling variance to provide comparative physiologists opportunities to explictly incorperate treatment differences into the effect size estimates.
+We then describe how more complex treatment differences, such as dosage differences which may have more complex non-linear effects, can be accomodated using multilevel meta-regression models.
+Expanding the meta-analtic toolkit for comparative physiologists will provide new opportunities to address global scale problems that attempt to undersatnd how organisms will cope with rapidly changing environments in the future.
+
+## **Meta-Analytic Models that Control for Treatment Differences Within and Across Studies**
+
+Quantifying effect size heterogenity (i.e., effect size variance) provides a pathway to explore hypotheses thought to explain why effect might vary across studies.
+
+## **References**

### 2021-05-17 MS/ms.Rmd
just updating the outline a bit, few wording change sto make things a little more clear / accurate

@@
 Meta-analysis is a tool that provides comparative physiologists with powerful, unbiased and quantitatively informed answers to topical research questions by synthesising effect sizes across disparate studies.
-Distilling published research results into standardised effect sizes that can be weighted by their sample size (i.e., inverse sampling variance) and compared across broad sets of research designs, study systems and species is its core objective and strength.
+Distilling published research results into standardised effect sizes that can be weighted (i.e., by their inverse sampling variance) in a meta-analysis, and compared across broad sets of research designs, study systems and species is its core objective and strength.
 Estimating overall effect sizes, and understanding what drives effect variability, provides opportunities to model how organisms will respond to pressing global challenges.
@@
 In addition, we derive new effect size measures that provide comparative physiologists with a means to directly make effect sizes comparable without the need to resort to more complex statistical models that may be harder to interpret.
-Our ‘new’ effect sizes and corresponding sampling variances help physiologists deal with temperature and dosage differences across studies; allowing researchers to compare both mean differences (e.g., Q10 to compare mean differences in physiological rates over 10 degrees) and associated differences in variance (e.g, SQ10 for comparing variability in in physiological rates over 10 degrees) for physiological traits.
-The new effect sizes we propose, in combination with existing meta-analytic models, will pave the way for comparative physiologists to explore exciting new questions by making results from large-scale data sets from the literature more accessible and widely interpretable.
+Our ‘new’ effect sizes and corresponding sampling variances help physiologists deal with common treatment differeces across studies; allowing researchers to compare both mean differences (e.g., Q10 to compare mean differences in physiological rates over 10 degrees) and associated differences in variance (e.g, SQ10 for comparing variability in in physiological rates over 10 degrees) for physiological traits.
+The new effect sizes we propose, in combination with existing meta-analytic models, will pave the way for comparative physiologists to explore exciting new questions by making results from large-scale data sets collected from the literature more accessible and widely interpretable.
 
@@
 
+## **Survey of Meta-Analytic Practices in Comparative Physiology**
+
+#### *Literature Search and Data Collection*
+To understand meta-analytic practices in comparative physiology, we searched for meta-analyses tackling comparative physiological questions that relied on data compiled from studies using animal model systems with more than a single species.
+All searches were conducted......**write details here**.
+
+We excluded plant meta-analyses because they were often focused on ecological (e.g., quantified changes in abundance and distribution of species) or agricultural questions (e.g., studies on soil microbial function, nitrogen and phosphorus capture, methane output and greenhouse gas emissions) that did not focus on organism physiological function across species.
+Meta-analyses needed to have collected physiological trait data from the literature including traits, such as hormones, thermal physiology (CTmax, CTmin, thermal preferences, thermal breadth, LT50, lethal thresholds), metabolic rates (routine, maximum, and minimum metabolic rate, aerobic scope), enzyme reaction rates and concentrations, oxidative stress and consequences (e.g., DNA damage, teleomere attrition), performance measurements (heart rates, sprint speed, swim speed, growth rates) and immune traits (cell function, antibodies, ect).
+Studies were also included if they measured reproductive allocation, survival / mortality or quantified scaling relationships with body size (e.g., metabolic scaling) across taxa.
+Studies on behavior were only included if they were explicitly interested in proximate physiological drivers of behavioral variation.
+Meta-analyses quantifying phenology, differences in body sizes between the sexes (i.e., SSD) and those focused on validating physiological methodology were excluded because the underlying question was not physiological in nature.
+#### *Current Meta-analytic Practices in Comparative Physiology*
+
+## **Opening up New Opportunities in Comparative Physiology: Expanding the Breadth of Effect Sizes and Sampling Variances**
+
+#### *Brief Introduction to Common Effect Sizes and Sampling Errors that are Useful in Comparative Physiology*
+#### *Expanding the Scope of Effect Size Metrics in Comparative Physiology*
+#### *New Effect Size Metrics that Account for Variability in Treatments*
+
 ## **Meta-Analytic Models that Control for Treatment Differences Within and Across Studies**
+
+#### *Multi-level Meta-Analysis when the Overall Effect is of Interest*
+#### *Quantifying Heterogenity in Effects: Is it as variable as you think?*
+#### *Multi-level Metaregression to Understand Variation and Imrpove Interpretation*
+
+## **Conclusions and Future Directions**
 

### 2021-05-17 MS/ms.Rmd
small udpate.

@@
 
-Despite the widespread adoption and well established methodological procedures of meta-analysis it has been criticised for mixing 'apples and oranges'; in otherwords, mixing effects from studies that lack comparability [@Arnqvist1995; @Gallo1979; @Carpenter2020; @Stewart2010].
+Despite the widespread adoption and well established methodological procedures of meta-analysis it has been criticised for mixing 'apples and oranges'; in otherwords, mixing effects from studies that lack comparability [@Gurevitch2018; @Arnqvist1995; @Gallo1979; @Carpenter2020; @Stewart2010].
 Lack of comparability could result from studies differing in experimental design, species, measurement variables and sampling units, which can impact the generalisability of meta-analytic results [@Arnqvist1995; @Stewart2010].
@@
 Meta-analyses quantifying phenology, differences in body sizes between the sexes (i.e., SSD) and those focused on validating physiological methodology were excluded because the underlying question was not physiological in nature.
+
 #### *Current Meta-analytic Practices in Comparative Physiology*
@@
 #### *Multi-level Meta-Analysis when the Overall Effect is of Interest*
-#### *Quantifying Heterogenity in Effects: Is it as variable as you think?*
+#### *Heterogenity Analysis: How Much Effect Size Variation Actually Exists?*
 #### *Multi-level Metaregression to Understand Variation and Imrpove Interpretation*

### 2021-05-17 MS/ms.Rmd
Small changes

@@
 
-#### *Literature Search and Data Collection*
+#### *Literature Search and Survey Data Collection*
 To understand meta-analytic practices in comparative physiology, we searched for meta-analyses tackling comparative physiological questions that relied on data compiled from studies using animal model systems with more than a single species.
@@
 #### *Heterogenity Analysis: How Much Effect Size Variation Actually Exists?*
+Quantifying effect size heterogenity (i.e., effect size variance) provides a pathway to explore hypotheses thought to explain why effect might vary across studies.
+
 #### *Multi-level Metaregression to Understand Variation and Imrpove Interpretation*
@@
 
-Quantifying effect size heterogenity (i.e., effect size variance) provides a pathway to explore hypotheses thought to explain why effect might vary across studies.
-
 ## **References**

### 2021-05-18 MS/ms.Rmd
Sub-title change
Words, just words
Playing with title and doing some more writing and planning

@@
 ---
-title: "Meta-analytic approaches and new effect sizes for treatment effects in comparative physiology"
+title: "Meta-analytic approaches and 'new' effect sizes to account for heterogeneous effects in comparative physiology"
 author: Daniel W.A. Noble, Patrice Potter, Sammy Burke, Szymek Drobniak, Malgorzata Lagisz, Rose O’Dea, Shinichi Nakagawa
@@
 ## **Introduction**
-Meta-analysis provides unbiased and quantitatively informed answers to research questions in comparative physiology by using a transparent and reproducible search strategy to synthesise research results across studies and identify sources of variation [@Nakagawa2017; @Gurevitch2018; @Cooper2009; @Arnqvist1995; @Koricheva2013].
-Meta-analysing independent studies provides greater statistical power and precision than what any individual study on its own would be able to provide on a given question - particularly given that most studies are already under-powered in ecological and evolutionary research [@Forstmeier2017; @Jennions2003].
-By expressing study effects on a common scale (i.e., effect size) a meta-analyst can gain broader insight into the direction and efficacy of a particular treatment effect or strength of a relationship between two variables of interest [@Gurevitch2018; @Koricheva2013].
+Meta-analysis provides quantitatively informed answers to research questions by using a transparent and reproducible search strategy to synthesise research results across studies and identify sources of variation [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Arnqvist1995; @Koricheva2013].
+Meta-analysing independent studies provides greater statistical power and precision than what any individual study on its own would be able to provide on a given question - particularly given that most empirical studies are already under-powered in many areas of biology [@Forstmeier2017; @Jennions2003; @Button2013].
+By expressing study effects on a common scale (i.e., standardised effect size) a meta-analyst can gain broader insight into the direction and efficacy of a particular treatment effect or the strength of a relationship between two variables of interest [@Gurevitch2018; @Koricheva2013].
+Quntitative syntheses, including meta-analyses, have provided comparative physiologists with powerful insights on pressing global challenges - from testing whether physiological plasticity can buffer orgamisms against climate change [e.g, @Seebacher2015] to the degree to which endocrine disrupting chemicals, such as bisphenol A (BPA), impact aquatic organisms [e.g., @WuSeebacher2020].
+
 A critically important feature of meta-analaysis that provides improved precision when estimating overall effects is the ability to account for sampling error - this can be derived assuming the sampling distribution of a given effect size is known [].
 
-Despite the widespread adoption and well established methodological procedures of meta-analysis it has been criticised for mixing 'apples and oranges'; in otherwords, mixing effects from studies that lack comparability [@Gurevitch2018; @Arnqvist1995; @Gallo1979; @Carpenter2020; @Stewart2010].
+Despite the widespread adoption and well established methodological procedures of meta-analysis it is often criticised for mixing 'apples and oranges' - in otherwords, mixing effects from studies that lack comparability [@Gurevitch2018; @Arnqvist1995; @Gallo1979; @Carpenter2020; @Stewart2010].
 Lack of comparability could result from studies differing in experimental design, species, measurement variables and sampling units, which can impact the generalisability of meta-analytic results [@Arnqvist1995; @Stewart2010].
@@
 For example, experimental designs can vary in the temperatures that they apply or in the dosages of chemical modifiers used in experimental treatments [e.g., ].
-They often inlcude a diversity of study species.
+In adidtion, they often inlcude a diversity of study species which can vary in responses.
 
-The goal of our review is to reassure comparative physiologists that heterogeneity among effect sizes can be comfortably dealt with through modifications of existing effect sizes measures and using multilevel meta-regression models.
-We first conduct a survey of published meta-analyses in the field of comparative physiology to gauge methodological and meta-analytic practices - assessing what types of effect sizes are commonly used, how often effect size estimates are impacted by continuous treatment differences and whether meta-analytic models (i.e., models that account for sampling variance) are commonly applied.
-We then introduce new effect sizes and their assocaited sampling variance to provide comparative physiologists opportunities to explictly incorperate treatment differences into the effect size estimates.
-We then describe how more complex treatment differences, such as dosage differences which may have more complex non-linear effects, can be accomodated using multilevel meta-regression models.
+The goal of our review is to briefly overview meta-analytic practices and reassure comparative physiologists that heterogeneity among effect sizes can be comfortably dealt with by modifying existing effect sizes measures and using multilevel meta-regression models.
+We first conduct a survey of published meta-analyses in the field of comparative physiology to gauge methodological and meta-analytic approaches - assessing what types of effect sizes are commonly used, how often effect size estimates are impacted by continuous treatment differences and whether meta-analytic models (i.e., models that account for sampling variance) are commonly applied.
+We then introduce new effect sizes and their assocaited sampling variance to provide comparative physiologists opportunities to explictly incorperate treatment differences into the effect size estimates to easy their interpretation.
+We then describe how more complex treatment differences, such as dosage differences, which may have more complex non-linear effects, can be accomodated using multilevel meta-regression models.
 Expanding the meta-analtic toolkit for comparative physiologists will provide new opportunities to address global scale problems that attempt to undersatnd how organisms will cope with rapidly changing environments in the future.
@@
 
-## **Opening up New Opportunities in Comparative Physiology: Expanding the Breadth of Effect Sizes and Sampling Variances**
+## **Opening Up New Opportunities in Comparative Physiology: Expanding the Breadth of Effect Sizes to Deal with Treatment Differences Across Studies**
 
@@
 #### *Expanding the Scope of Effect Size Metrics in Comparative Physiology*
+
 #### *New Effect Size Metrics that Account for Variability in Treatments*

### 2021-05-18 MS/ms.Rmd
Added one more important point to existing exclusion criteria. That is, we should only focus on studies that collate data from literature

@@
 
-A critically important feature of meta-analaysis that provides improved precision when estimating overall effects is the ability to account for sampling error - this can be derived assuming the sampling distribution of a given effect size is known [].
+Meta-analysis is a well-developed research field with a long history in the fields of statistics, medicine, psychology and ecology [@Gurevitch2018; @Nakagawa2017].
+It has emerged as the 'gold-standard' across various disciplines for quantitative synthesis, and is becoming increasingly more prominant the field of comparative physiology.
+Meta-analysis involves strict literature-based search protocols and data extraction (i.e., following the PRISMA protocol, e.g., [@ODea2021]) to achieve two major goals, 1) to provide an overall mean estimate of a treatment effect or relationship and 2) to quantify effect size variance and understand key drivers explaining differences in effects across studies [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Koricheva2013].
+A critically important feature of meta-analaysis is its ability to account for sampling error [].
+The inverse sampling error is used to weight higher powered studies in the analysis and make overall esatimtes more precise.
+While many meta-analyses might employ unweighted analyses, these studies will not gain greater precision on esatimytes, even if the overall mean itself is unbiased.
 
@@
 Indeed, study specific differences in comparative physiology are widspread.
-For example, experimental designs can vary in the temperatures that they apply or in the dosages of chemical modifiers used in experimental treatments [e.g., ].
-In adidtion, they often inlcude a diversity of study species which can vary in responses.
+For example, experimental designs can vary in the temperatures that they apply or in the dosages of chemical modifiers used in experimental treatments [e.g., @WuSeebacher2020].
+In addition, they often include a diversity of study species which can vary in responses.
 
@@
 Meta-analyses quantifying phenology, differences in body sizes between the sexes (i.e., SSD) and those focused on validating physiological methodology were excluded because the underlying question was not physiological in nature.
+While many studies in comparative physiology collect data as part of a comparative analysis, we focus here only on studies collating data from existing literature.
 
@@
 
-#### *New Effect Size Metrics that Account for Variability in Treatments*
+A very common occurance in comparative physiology is to manipulate the tempearture organisms experience and measure some physiologcal rate (e.g., metabolic rate).
+Physiological rates are often compared using $Q_{10}$ values (e.g., [@Rodger2021]), which describe the multiplicative change in physiological rates across a 10&deg;C temperature change.
+Higher $Q_{10}$ values indicate larger changes in physiological rates.
+Currently, however, we do not have associated sampling variances derived for $Q_{10}$ making it challenging to weight effect size estimates by sampling variance as is typical in meta-analysis.
+Recognition of the similarity between *lnRR* and $Q_{10}$ means that we can derive $Q_{10}$ based effect sizes using the well known mathematical properties of *lnRR*, and improve upon our ability to account for sources of non-independence that are typical in meta-analysis [@Lajeunesse2011; @Noble2017].
+As such, here we derive a series of $Q_{10}$ based effect sizes along with their associated sampling variances that allow one to compare both changes in mean and variance of physiological rates.
+
+#### *Comparing changes in mean physiological rates*
+
+Prior to showing how the relevant $Q_{10}$ effect size can be calculated it can be helpful to understand its similarities to *lnRR*.
+The *lnRR* described by @Hedges1999 and extended by  @Lajeunesse2011 and can be calculated as follows:
+
+$$
+\begin{equation} 
+  \begin{aligned}
+  lnRR = ln\left ( \frac{X_{1}}{X_{2}}\right )
+  \end{aligned}
+  (\#eq:lnRR)
+\end{equation} 
+$$
+
+$$
+\begin{equation} 
+  s_{lnRR} = \left ( \frac{SD_{1}^2}{N_{1}X_{1}^2}\right ) + \left ( \frac{SD_{2}^2}{N_{2}X_{2}^2}\right )
+  (\#eq:slnRR)
+\end{equation} 
+$$
+In equation \@ref(eq:lnRR), $X_{1}$ is the mean of group 1, often a control group, where as $X_{2}$ is the mean of group 2 (e.g., a treatment group).
+The mean of $X_{i}$ for group *i* can be any measurement type (e.g.
+a physiological rate, mass etc) so long as the measurement variable is ratio scale.
+Log transformation of this ratio makes the effect size normally distributed.
+Equation \@ref(eq:slnRR) is the analytical solution for *lnRR*'s sampling variance where, $SD_{1}^2$ and $SD_{2}^2$ is the variance in group 1 and 2, respectively and $N_{1}$ and $N_{2}$ is the sample size in group 1 and 2.
+
+The equations for *lnRR* and its sampling variance allow us to easily extend this to $Q_{10}$ based effect sizes. Recall that $Q_{10}$ is described as follows:
+
+$$
+\begin{equation} 
+  Q_{10} = \left( \frac{R_{2}}{R_{1}} \right)^{ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
+  (\#eq:q10)
+\end{equation} 
+$$
+Here, $R_{1}$ and  $R_{2}$ are mean physiological rates and  $T_{1}$ and  $T_{2}$ are the temperatures that these rates are measured.
+Log transformation of equation \@ref(eq:q10) leads to the following log transformed $Q_{10}$:
+
+$$
+\begin{equation} 
+  lnRR_{Q_{10}} = ln\left( \frac{R_{2}}{R_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
+(\#eq:lnq10)
+\end{equation} 
+$$
+Equation \@ref(eq:lnq10) is essentially a temperature corrected equivalent to lnRR when the numerator and denomenator are measured at different temperatures.
+This allows one to compare the mean of two temperature treatments directly regardless of the temperatures that these groups have been measured.
+Here, we will refer to this as the log $Q_{10}$ response ratio, $lnRR_{Q_{10}}$.
+Recognition of this equivalence means that we can easily calculate the sampling variance for equation \@ref(eq:lnq10) as follows:
+
+$$
+\begin{equation} 
+  s_{lnRR_{Q_{10}}} = \left( \frac{SD_{2}^2}{R^2_{2}N_{2}} + \frac{SD_{1}^2}{R^2_{1}N_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
+  (\#eq:Vlnq10)
+\end{equation} 
+$$
+
+#### *New Effect Size Metrics that Compare Changes in Variability Across Treatments*
+
+@Nakagawa2015 recently proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
+Like *lnRR*, *lnVR* and *lnCVR* are ratios that describe the relative difference in trait variablity between two groups.
+We refer readers to @Nakagawa2015 for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling varaince) as follows:
+
+$$
+\begin{equation} 
+lnVR_{Q_{10}} = ln\left( \frac{SD_{2}}{SD_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
+(\#eq:lnq10VR)
+\end{equation} 
+$$
+$$
+\begin{equation} 
+s_{lnVR_{Q_{10}}} = \left( \frac{1}{2\left( N_{2}-1 \right)} + \frac{1}{2\left(N_{1} - 1\right)} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
+(\#eq:slnq10VR)
+\end{equation} 
+$$
+
+Equations \@ref(eq:lnq10VR) and \@ref(eq:slnq10VR) describe the change in physiological rate variance (eqn \@ref(eq:lnq10VR)) across a 10&deg;C temperature change along with its sampling variance (eqn \@ref(eq:slnq10VR)).
+While this is a useful metric, as discussed by Nakagawa *et al* @nakagawa2015meta there is often a strong mean-variance relationship that needs to be accounted for in analysing changes in variance.
+As such, we can calculate the coefficient of variation, which standardises changes in variance for changes in means as follows:
+
+$$
+\begin{equation} 
+lnCVR_{Q_{10}} = ln\left( \frac{\text{CV}_{2}}{\text{CV}_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
+(\#eq:lnq10CVR)
+\end{equation} 
+$$
+$$
+\begin{equation} 
+s_{lnCVR_{Q_{10}}} = \left[ \frac{(\text{SD}_{1})^2}{N_{1}({R}_{1})^2} + \frac{(\text{SD}_{2})^2}{N_{2} ({R}_{2})^2} + \frac{1}{2\left( N_{1}-1 \right)} + \frac{1}{2\left(N_{2} - 1\right)} \right]{ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
+(\#eq:slnq10CVR)
+\end{equation} 
+$$
+
+where $CV$ is the coefficient of variation defined as $SD / R$.
 

### 2021-05-18 MS/ms.Rmd
More writing to hash out ideas and structure a little more...fun, fun!

@@
 In addition, we derive new effect size measures that provide comparative physiologists with a means to directly make effect sizes comparable without the need to resort to more complex statistical models that may be harder to interpret.
-Our ‘new’ effect sizes and corresponding sampling variances help physiologists deal with common treatment differeces across studies; allowing researchers to compare both mean differences (e.g., Q10 to compare mean differences in physiological rates over 10 degrees) and associated differences in variance (e.g, SQ10 for comparing variability in in physiological rates over 10 degrees) for physiological traits.
+Our ‘new’ effect sizes and corresponding sampling variances help physiologists deal with common treatment differeces across studies; allowing researchers to compare both mean differences (e.g., $Q_{10}$ to compare mean differences in physiological rates over 10 degrees) and associated differences in variance (e.g, $S_{Q10}$ for comparing variability in in physiological rates over 10 degrees) for physiological traits.
 The new effect sizes we propose, in combination with existing meta-analytic models, will pave the way for comparative physiologists to explore exciting new questions by making results from large-scale data sets collected from the literature more accessible and widely interpretable.
@@
 It has emerged as the 'gold-standard' across various disciplines for quantitative synthesis, and is becoming increasingly more prominant the field of comparative physiology.
-Meta-analysis involves strict literature-based search protocols and data extraction (i.e., following the PRISMA protocol, e.g., [@ODea2021]) to achieve two major goals, 1) to provide an overall mean estimate of a treatment effect or relationship and 2) to quantify effect size variance and understand key drivers explaining differences in effects across studies [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Koricheva2013].
+Meta-analysis involves strict literature-based search protocols and data extraction [i.e., following the PRISMA protocol, see @ODea2021] to achieve two major goals, 1) to provide an overall mean estimate of a treatment effect or relationship and 2) to quantify effect size variance and understand key drivers explaining differences in effects across studies [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Koricheva2013].
 A critically important feature of meta-analaysis is its ability to account for sampling error [].
@@
 A very common occurance in comparative physiology is to manipulate the tempearture organisms experience and measure some physiologcal rate (e.g., metabolic rate).
-Physiological rates are often compared using $Q_{10}$ values (e.g., [@Rodger2021]), which describe the multiplicative change in physiological rates across a 10&deg;C temperature change.
+Using normal effect size measures (see above) would result in the effect sizes varying in the types of temperatures applied within and across across studies contributing to 'comparablity' issues.
+As such, it is often of interest to standardsise effects by temperature.
+One common effect size measure already used in comparative physiology to compare physiological rates is $Q_{10}$ [e.g., @Rodgers2021; @Seebacher2015; @Havird2020], which describes the multiplicative change in physiological rates across a 10&deg;C temperature change.
 Higher $Q_{10}$ values indicate larger changes in physiological rates.
-Currently, however, we do not have associated sampling variances derived for $Q_{10}$ making it challenging to weight effect size estimates by sampling variance as is typical in meta-analysis.
-Recognition of the similarity between *lnRR* and $Q_{10}$ means that we can derive $Q_{10}$ based effect sizes using the well known mathematical properties of *lnRR*, and improve upon our ability to account for sources of non-independence that are typical in meta-analysis [@Lajeunesse2011; @Noble2017].
-As such, here we derive a series of $Q_{10}$ based effect sizes along with their associated sampling variances that allow one to compare both changes in mean and variance of physiological rates.
+Currently, however, we do not have associated sampling variances derived for $Q_{10}$ making it challenging to make use of the full power of weighted meta-analytic models.
+Interstingly, $Q_{10}$ is quite similar to *lnRR*, meaning that we can derive a $Q_{10}$ based effect size and sampling error using the well known mathematical properties of *lnRR*.
+This opens up the meta-analtic toolbox and improves upon our ability to account for well known sources of non-independence that are typical in meta-analysis [@Lajeunesse2011; @Noble2017].
 
@@
 
-## **Meta-Analytic Models that Control for Treatment Differences Within and Across Studies**
+## **Meta-Analytic Models to Control for Heterogeous Effects Within and Across Studies**
+
+It will not possible to derive an effect size that completely controls for known heterogenity at the effect size level all the time.
+This may because because treatment effects may not be simple linear or exponential functions of the mean response making the relationship with effect size complex [e.g., thermal performance curves; @Noble2018].
+For example, dosages applied to treatments can follow quite complex non-linear relationships, with expoential or quadratic relationships in relation to some mean response.
+When this occurs we recommend comparative physiologists apply meta-regerssion approaches, controlling for these known treatment differences as a moderator.
+There are simple statisical approaches a meta-analyst can use to then make the overall effects interpretable [@Schielzeth2010].
+Before diving into meta-regression models, we will first overview the meta-analytical approaches or steps commonly used.
 
 #### *Multi-level Meta-Analysis when the Overall Effect is of Interest*
+One of the main goals of meta-analysis is to obtain an overall meta-analytic mean estimate (and some form of uncertainty around that mean, like a 95% confidence interval, may be even with a prediction interval - @Nakagawa2021c) which describes the magnitude of effect across all the studies / effects included in the meta-analysis.
+This is generally done with a simple random effects or multilevel meta-analytic model that accounts for effect size sampling error [@Nakagawa2017; @NakagawaSantos2012].
+More often than not, meta-analyses in comparative physiology will have complex hierachical structure.
+For example, multiple effect sizes may be taken from a single study on different traits measured on the same individuals, or come from many different species that share an evolutionary history [@Noble2017].
+As such, it is far more likely that comparative physiologists will need to apply a multi-level meta-analytic model to control for the various sources of non-independence [@NakagawaSantos2012; @Song2021; @Nakagawa2021; @Noble2017].
+Multilevel models are also extremely useful in describing the various sources contributing to effect size variance.
+For the purpose of our discussion, we will assume the meta-analyst plans to use more advanced multilevel models.
+Having said that, it maybe sufficient for many meta-analyses to make use of traditional random effects models.
+We refer readers to excellent reviews and books that overview the distinctions between common (fixed) effect, random effect and multilevel models and when one might want (or not want) to apply these models [@Nakagawa2017; @NakagawaSantos2012; @Koricheva2013; @Borenstein2009].
+
 #### *Heterogenity Analysis: How Much Effect Size Variation Actually Exists?*
@@
 
-#### *Multi-level Metaregression to Understand Variation and Imrpove Interpretation*
+#### *Multi-level Metaregression to Understand Variation and Improve Interpretation*
 

### 2021-05-18 MS/ms.Rmd
small changes

@@
 
-Meta-analysis is a well-developed research field with a long history in the fields of statistics, medicine, psychology and ecology [@Gurevitch2018; @Nakagawa2017].
+Meta-analysis is a well-developed research field with a long history in statistics, medicine, psychology and ecology [@Gurevitch2018; @Nakagawa2017].
 It has emerged as the 'gold-standard' across various disciplines for quantitative synthesis, and is becoming increasingly more prominant the field of comparative physiology.
-Meta-analysis involves strict literature-based search protocols and data extraction [i.e., following the PRISMA protocol, see @ODea2021] to achieve two major goals, 1) to provide an overall mean estimate of a treatment effect or relationship and 2) to quantify effect size variance and understand key drivers explaining differences in effects across studies [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Koricheva2013].
+Formal meta-analyses involve a systematic literature-based search, extraction of data from studies meeting specific inclusion criteria, and the subsequent calculation of effects sizes from summary statistics provided by papers.
+The entire process should follow and report upon this entire process carefully to ensure the meta-analysis is as transparent and reproducible as possible [i.e., see the Preferred Reporting Items for Systematic Reviews and Meta-Analyses in Ecology and Evolution (PRISMAEcoEvo) protocol, @ODea2021].
+Aside from providing an up-to-date overview of the research question, along with identifying any gaps and biases, there are two major goals of meta-analysis: 1) to provide an overall mean estimate of a treatment effect or relationship and 2) to quantify effect size variance and understand key drivers explaining differences in effects across studies [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Koricheva2013].
 A critically important feature of meta-analaysis is its ability to account for sampling error [].
@@
 Equations \@ref(eq:lnq10VR) and \@ref(eq:slnq10VR) describe the change in physiological rate variance (eqn \@ref(eq:lnq10VR)) across a 10&deg;C temperature change along with its sampling variance (eqn \@ref(eq:slnq10VR)).
-While this is a useful metric, as discussed by Nakagawa *et al* @nakagawa2015meta there is often a strong mean-variance relationship that needs to be accounted for in analysing changes in variance.
+While this is a useful metric, as discussed by @Nakagawa2015 there is often a strong mean-variance relationship that needs to be accounted for in analysing changes in variance.
 As such, we can calculate the coefficient of variation, which standardises changes in variance for changes in means as follows:
@@
 
-It will not possible to derive an effect size that completely controls for known heterogenity at the effect size level all the time.
+It will not be possible to derive an effect size that completely controls for known heterogenity at the effect size level all the time.
 This may because because treatment effects may not be simple linear or exponential functions of the mean response making the relationship with effect size complex [e.g., thermal performance curves; @Noble2018].
@@
 Having said that, it maybe sufficient for many meta-analyses to make use of traditional random effects models.
-We refer readers to excellent reviews and books that overview the distinctions between common (fixed) effect, random effect and multilevel models and when one might want (or not want) to apply these models [@Nakagawa2017; @NakagawaSantos2012; @Koricheva2013; @Borenstein2009].
+We refer readers to excellent reviews and books that overview the distinctions between common (fixed) effect, random effect and multilevel models and when one might want (or not want) to apply these models [@Nakagawa2017; @NakagawaSantos2012; @Koricheva2013; @Borenstein2009; @Schmid2021].
 

### 2021-05-19 MS/ms.Rmd
Updated inclusion/exclusion

@@
 We excluded plant meta-analyses because they were often focused on ecological (e.g., quantified changes in abundance and distribution of species) or agricultural questions (e.g., studies on soil microbial function, nitrogen and phosphorus capture, methane output and greenhouse gas emissions) that did not focus on organism physiological function across species.
-Meta-analyses needed to have collected physiological trait data from the literature including traits, such as hormones, thermal physiology (CTmax, CTmin, thermal preferences, thermal breadth, LT50, lethal thresholds), metabolic rates (routine, maximum, and minimum metabolic rate, aerobic scope), enzyme reaction rates and concentrations, oxidative stress and consequences (e.g., DNA damage, teleomere attrition), performance measurements (heart rates, sprint speed, swim speed, growth rates) and immune traits (cell function, antibodies, ect).
-Studies were also included if they measured reproductive allocation, survival / mortality or quantified scaling relationships with body size (e.g., metabolic scaling) across taxa.
+Meta-analyses needed to have collected physiological trait data from the literature including traits, such as hormones, thermal physiology (CTmax, CTmin, thermal preferences, thermal breadth, LT50, lethal thresholds), metabolic rates (routine, maximum, and minimum metabolic rate, aerobic scope), enzyme reaction rates and concentrations, oxidative stress and consequences (e.g., DNA damage, teleomere attrition), performance measurements (e.g., heart rates, sprint speed, swim speed, growth rates) and immune traits (e.g., cell function, antibodies, ect.).
+Studies were also included if they measured the relationship between physiological traits and body size, reproductive allocation, or survival / mortality (e.g., metabolic scaling) across taxa.
 Studies on behavior were only included if they were explicitly interested in proximate physiological drivers of behavioral variation.
-Meta-analyses quantifying phenology, differences in body sizes between the sexes (i.e., SSD) and those focused on validating physiological methodology were excluded because the underlying question was not physiological in nature.
-While many studies in comparative physiology collect data as part of a comparative analysis, we focus here only on studies collating data from existing literature.
+We also included meta-analyses that quantify plasticity in physiological traits across taxa for the purpose of understanding adaptive plasticity in response to environmental variation.
+Meta-analyses quantifying phenology, differences in body sizes between the sexes (i.e., SSD, except if the study was interested in sexual differences in physiological traits), those focused on validating physiological methodology or meta-analyses focusing on population genetic structure, gene transcription and quantitative genetics were excluded.
+There were also meta-analyses that focused on colour evolution and contrast which varied in their goals but were most often not focused on physiological  questions.
+As such, these studies were also excluded.
+While many studies in comparative physiology collect data as part of a comparative analysis, we focus here only on studies collating data from existing literature because this is the major data source for quantitative syntheses.
+Narrative reviews and comments were also not considered because they did not collate quantitative data from the literature.
 

### 2021-05-25 MS/ms.Rmd
Udpated the inclusion paragraph

--- 2021-05-18 MS/ms.Rmd
@@
 
-We excluded plant meta-analyses because they were often focused on ecological (e.g., quantified changes in abundance and distribution of species) or agricultural questions (e.g., studies on soil microbial function, nitrogen and phosphorus capture, methane output and greenhouse gas emissions) that did not focus on organism physiological function across species.
-Meta-analyses needed to have collected physiological trait data from the literature including traits, such as hormones, thermal physiology (CTmax, CTmin, thermal preferences, thermal breadth, LT50, lethal thresholds), metabolic rates (routine, maximum, and minimum metabolic rate, aerobic scope), enzyme reaction rates and concentrations, oxidative stress and consequences (e.g., DNA damage, teleomere attrition), performance measurements (heart rates, sprint speed, swim speed, growth rates) and immune traits (cell function, antibodies, ect).
-Studies were also included if they measured reproductive allocation, survival / mortality or quantified scaling relationships with body size (e.g., metabolic scaling) across taxa.
-Studies on behavior were only included if they were explicitly interested in proximate physiological drivers of behavioral variation.
-Meta-analyses quantifying phenology, differences in body sizes between the sexes (i.e., SSD) and those focused on validating physiological methodology were excluded because the underlying question was not physiological in nature.
-While many studies in comparative physiology collect data as part of a comparative analysis, we focus here only on studies collating data from existing literature.
+We included quantitative syntheses, including meta-analyses (*sensu stricto*), that were focused on comparative physiologcial questions.
+Narrative reviews and comments were not considered because they did not collate quantitative data from the literature.
+Studies needed to have collected physiological trait data from the literature including traits, such as hormones, thermal physiology (CTmax, CTmin, thermal preferences, thermal breadth, LT50, lethal thresholds), metabolic rates (routine, maximum, and minimum metabolic rate, aerobic scope), enzyme reaction rates and concentrations, oxidative stress and consequences (e.g., DNA damage, teleomere attrition), performance measurements (e.g., heart rates, sprint speed, swim speed, growth rates), body composition (e.g., fatty acid profiles) and immune traits (e.g., cell function, antibodies, ect.).
+Studies were also included if they measured the relationship between physiological traits and body size (e.g., metabolic scaling), reproductive allocation, or survival / mortality across taxa.
+Studies on behavior were only included if the synthesis was explicitly interested in the proximate physiological drivers of behavioral variation.
+We also included meta-analyses that quantify plasticity in physiological traits across taxa for the purpose of understanding adaptive plasticity in response to environmental variation.
+While many studies in comparative physiology collect data as part of a comparative analysis, we focus here only on studies collating data from existing literature because this is the major data source for quantitative synthesis.
+Quantitative syntheses interested in phenology, biomechanics, sexual size dimorphism (i.e., SSD, except if the study was interested in sexual differences in physiological traits), those focused on validating physiological methodology, or characterising population genetic structure, gene transcription and quantitative genetics were excluded.
+There were also meta-analyses that focused on colour evolution and contrast which varied in their goals but were most often not focused on physiological questions.
+As such, these studies were also exclude.
+We also excluded plant synthesis papers because they were often focused on ecological (e.g., quantified changes in abundance and distribution of species) or agricultural questions (e.g., studies on soil microbial function, nitrogen and phosphorus capture, methane output and greenhouse gas emissions) that did not focus on organism physiological function across species.
 

### 2021-05-26 MS/supp.Rmd
Startng supplement

---
title: "Supplemental Materials for "Meta-analytic approaches and 'new' effect sizes to account for heterogeneous effects in comparative physiology""
author: Daniel W.A. Noble, Patrice Potter, Sammy Burke, Szymek Drobniak, Malgorzata Lagisz, Rose O’Dea, Shinichi Nakagawa
date: "`r Sys.Date()`"
bibliography: ../bib/refs.bib
csl: ../bib/the-journal-of-experimental-biology.csl
output: 
  bookdown::word_document2:
    toc: no
    toc_depth: 6
    number_sections: false
    reference_docx: template.docx
  bookdown::html_document2:
    code_folding: hide
    number_sections: no
    toc: yes
    toc_depth: 6
    toc_float: yes
    bibliography: refs.bib
editor_options: 
  chunk_output_type: console
---
```{r loadpackages, echo = FALSE, results = 'hide'}
pacman::p_load(png, jpeg, cowplot)
```

```{r figS1, fig.cap="PRISMA flowchart for study selection and inclusion"}

img1 <- readPNG("../figs/PRISMA_diagram_v0.png")

p1 <- cowplot::ggdraw()+
        cowplot::draw_image(img1)

```

### 2021-06-03 MS/supp.Rmd
Updated supp to include details on searches

@@
 ---
-title: "Supplemental Materials for "Meta-analytic approaches and 'new' effect sizes to account for heterogeneous effects in comparative physiology""
+title: "Supplemental Materials for: Meta-analytic approaches and new effect sizes to account for heterogeneous effects in comparative physiology"
 author: Daniel W.A. Noble, Patrice Potter, Sammy Burke, Szymek Drobniak, Malgorzata Lagisz, Rose O’Dea, Shinichi Nakagawa
@@
 output: 
-  bookdown::word_document2:
-    toc: no
-    toc_depth: 6
-    number_sections: false
-    reference_docx: template.docx
   bookdown::html_document2:
@@
     toc_float: yes
-    bibliography: refs.bib
+  bookdown::word_document2:
+    toc: no
+    toc_depth: 6
+    number_sections: false
+    reference_docx: template.docx
 editor_options: 
@@
 ---
+
 ```{r loadpackages, echo = FALSE, results = 'hide'}
-pacman::p_load(png, jpeg, cowplot)
+pacman::p_load(png, jpeg, cowplot, flextable, tidyverse)
 ```
 
-```{r figS1, fig.cap="PRISMA flowchart for study selection and inclusion"}
+# Supplementary Materials for Survey Study Selection
+
+Here we provide greater detail on the search strategy, keyword selection and the numbers of final studies included at each step pf the screening process for our survey.
+Figure \@ref(fig:figS1) outlines our PRSIMA flowchart detailing the number of papers hit, their sources and how many records were excluded and included at each screening phase.
+The full search strings used to refine our search query can be found in Table \@ref(tab:tabS1).
+Note that results from our final searches (25 & 28) are the ones we used.
+Our query was restricted to a pre-specified set of comparative physiology journals within the last 6 years of publication.
+The journals used and their ISSN numbers are provided in Table \@ref(tab:tabS2).
+In total, out of the 79 papers screened at the full-text stage we ended up including 62 full texts.
+We excluded N = 17 meta-/comparative analyses because they: 1) did not include physiological traits (N = 4); 2) were empirical studies that collected their own data and did not collate data from the literature (N = 10); 3) Were not actual quantitative syntheses, but rather systematic reviews (N = 1) and 4) were studies with a focus on biomechanics (N = 2).
+
+```{r figS1, fig.align='center', echo = FALSE, fig.cap="PRISMA flowchart for study selection and inclusion"}
 
@@
         cowplot::draw_image(img1)
+p1
+```
 
+```{r tabS1,  echo = FALSE, tab.cap="Log of search string development"}
+
+table <- read.csv("../tables/Table_S1.csv")
+
+table_s1 <- flextable(table)                                                                            %>% 
+            flextable::compose(j = 1, part = "header", value = as_paragraph(as_b("Date")))              %>% 
+            flextable::compose(j = 2, part = "header", value = as_paragraph(as_b("Search Number")))     %>% 
+            flextable::compose(j = 3, part = "header", value = as_paragraph(as_b("Search String")))     %>% 
+            flextable::compose(j = 4, part = "header", value = as_paragraph(as_b("Number of Records"))) %>% 
+            flextable::compose(j = 5, part = "header", value = as_paragraph(as_b("Comments")))          %>% 
+            flextable::compose(j = 6, part = "header", value = as_paragraph(as_b("Notes"))) 
+ table_s1
 ```
+
+```{r tabS2, echo = FALSE, tab.cap="Log of search string development"}
+
+table <- read.csv("../tables/Table_S2.csv")
+
+table_s2 <- flextable(table)                                                                            %>% 
+            flextable::compose(j = 1, part = "header", value = as_paragraph(as_b("Journal Name")))      %>% 
+            flextable::compose(j = 2, part = "header", value = as_paragraph(as_b("ISSN Number")))       %>% 
+            flextable::width(j = 1, 5)
+table_s2
+```

### 2021-06-03 MS/ms.Rmd
Bunch more writing. Sorted out the survey methods description, added to the modelling section

@@
 title: "Meta-analytic approaches and 'new' effect sizes to account for heterogeneous effects in comparative physiology"
-author: Daniel W.A. Noble, Patrice Potter, Sammy Burke, Szymek Drobniak, Malgorzata Lagisz, Rose O’Dea, Shinichi Nakagawa
-date: "`r Sys.Date()`"
 bibliography: ../bib/refs.bib
@@
 
+Daniel W.A. Noble$^{1,*}$, Patrice Potter$^{2}$, Sammy Burke$^{2}$, Szymek Drobniak$^{2}$, Malgorzata Lagisz$^{2}$, Rose O’Dea$^{2}$, Shinichi Nakagawa$^{2}$
+
+$^{1}$ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2600
+
+$^{2}$ School of Biological, Earth and Environmental Sciences, University of New South Wales, Sydney, NSW
+
+* Corespondance:
+
 ## **Abstract**
@@
 Meta-analysis is a well-developed research field with a long history in statistics, medicine, psychology and ecology [@Gurevitch2018; @Nakagawa2017].
-It has emerged as the 'gold-standard' across various disciplines for quantitative synthesis, and is becoming increasingly more prominant the field of comparative physiology.
+It has emerged as the 'gold-standard' across various disciplines for quantitative synthesis and is becoming increasingly more prominant the field of comparative physiology.
 Formal meta-analyses involve a systematic literature-based search, extraction of data from studies meeting specific inclusion criteria, and the subsequent calculation of effects sizes from summary statistics provided by papers.
@@
 Aside from providing an up-to-date overview of the research question, along with identifying any gaps and biases, there are two major goals of meta-analysis: 1) to provide an overall mean estimate of a treatment effect or relationship and 2) to quantify effect size variance and understand key drivers explaining differences in effects across studies [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Koricheva2013].
-A critically important feature of meta-analaysis is its ability to account for sampling error [].
+A critically important feature of meta-analaysis is its ability to account for sampling error [@Koricheva2013].
 The inverse sampling error is used to weight higher powered studies in the analysis and make overall esatimtes more precise.
-While many meta-analyses might employ unweighted analyses, these studies will not gain greater precision on esatimytes, even if the overall mean itself is unbiased.
+While many meta-analyses might employ unweighted analyses, these studies will not gain greater precision on estimates because sampling variance cannot be formally accounted for in the analysis, even if the overall mean itself is unbiased.
 
@@
 ## **Survey of Meta-Analytic Practices in Comparative Physiology**
+#### *Literature Search and Survey Data Collection*
+To understand meta-analytic practices in comparative physiology, we searched for meta-analyses and comparative analyses that tackled questions that relied on using physiological data compiled from animal studies across multiple species.
+We were specifically interested in asking: 1) what type of effect size was used within the quantitative synthesis?
+2) based on the methods provided, was the effect size likely susceptable to variation in how treatments are applied across studies?
+3) If so, was the variation resulting from treatment differences accounted for in the effect size or during analysis?, and finally, 4) how were effect sizes analysed in the quantitative synthesis, were these weighted analyses, and what program was used for analysis?
+We also recorded whether publication bias and sensitivity analyses were conducted, if data were publicly available, where it was stored and if so it was usable (i.e., in a format like .txt).
+All searches were conducted in Scopus between May 16 - 18, 2021.
+Briefly, we first did a series of pilot searches (detailed in Supplementary Materials) to refine our search query.
+We searched for studies that included: 'meta-analysis', 'meta regression' , 'comparative analysis', 'comprehensive analysis' 'global analysis' or 'macrophysiology' in their title and abstract, restricting our search to key comparative physiology journals (deatiled in Table X - Supplementary Materials) within the last 6 years.
+We expected this to provide a contemporay overview of quantitative syntheses in comparative physiology while making the survey and screening feasible.
+We awknowledge that this may have missed some important, and influential, quantitative synthese in the field of comparative physiology, but likely provided a random sample to inform on the questions we sought to address (see below).
 
-#### *Literature Search and Survey Data Collection*
-To understand meta-analytic practices in comparative physiology, we searched for meta-analyses tackling comparative physiological questions that relied on data compiled from studies using animal model systems with more than a single species.
-All searches were conducted......**write details here**.
-
-We included quantitative syntheses, including meta-analyses (*sensu stricto*), that were focused on comparative physiologcial questions.
+We included quantitative syntheses, including meta-analyses (*sensu stricto*), that were focused on comparative physiologcial questions only.
 Narrative reviews and comments were not considered because they did not collate quantitative data from the literature.
@@
 Studies on behavior were only included if the synthesis was explicitly interested in the proximate physiological drivers of behavioral variation.
-We also included meta-analyses that quantify plasticity in physiological traits across taxa for the purpose of understanding adaptive plasticity in response to environmental variation.
+We also included meta-analyses that quantifed plasticity in physiological traits across taxa for the purpose of understanding adaptive plasticity in response to environmental variation.
 While many studies in comparative physiology collect data as part of a comparative analysis, we focus here only on studies collating data from existing literature because this is the major data source for quantitative synthesis.
@@
 As such, these studies were also exclude.
-We also excluded plant synthesis papers because they were often focused on ecological (e.g., quantified changes in abundance and distribution of species) or agricultural questions (e.g., studies on soil microbial function, nitrogen and phosphorus capture, methane output and greenhouse gas emissions) that did not focus on organism physiological function across species.
+We restricted our focus to animal studies because plant synthesis papers were often only focused on ecological (e.g., quantified changes in abundance and distribution of species) or agricultural questions (e.g., studies on soil microbial function, nitrogen and phosphorus capture, methane output and greenhouse gas emissions).
+
+All titles and abstracts and full text screening was done by two people (DWAN and ML).
+Any conflicts or disagreements were resolved by discussion and a concensus on a paper was reached.
+Out of the 417 papers, 79 full texts were screened and we included a total of 62 for final data extraction.
+For full details on the search strings used, dates searched, the number of papers found, and our PRISMA flowchart (along with reasons for exclusion at the full text stage) we refer readers to the *Supplementary Materials*.
 
@@
 ## **Opening Up New Opportunities in Comparative Physiology: Expanding the Breadth of Effect Sizes to Deal with Treatment Differences Across Studies**
+#### *Brief Introduction to Common Effect Sizes and Sampling Errors that are Useful in Comparative Physiology*
 
-#### *Brief Introduction to Common Effect Sizes and Sampling Errors that are Useful in Comparative Physiology*
 #### *Expanding the Scope of Effect Size Metrics in Comparative Physiology*
@@
 Like *lnRR*, *lnVR* and *lnCVR* are ratios that describe the relative difference in trait variablity between two groups.
-We refer readers to @Nakagawa2015 for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling varaince) as follows:
+We refer readers to @Nakagawa2015 for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling variances) as follows:
 
@@
 
+If we assume that we are interested in understanding the overall effect of, say, stress (i.e., corticosterone) on XX we might extract data from studies manipulating corticosterone on eggs.
+Of course, these studies are diverse, apply different dosages of corticosterone and are working across many species.
+If the studies are experimental in nature, than a standardised effect size, such as $ln_{RR}$ might be applicable.
+We then might fit an overall, multilevel meta-analytic model as follows:
+
+$$ z_{i} = u + a_{k[i]} + sp_{k[i]} + s_{j[i]} + e_{i} + m_{i} $$
+
+where $z_{i}$ is the *i*th effect size (*i* = 1 ...
+$N_{ES}$, the number of effect sizes), *u* the overall meta-analytic mean, $a_{k[i]}$ is the phylogenetic effect for species *k* applied to effect size *i*.
+Phylogenetic effects are assumed to be normally distributed deviates sampled from a distribution with a mean of 0 and variance $\sigma^{2}_aA$ [hereafter denoted ~ *N*$(0, \sigma^{2}_aA)$], where A is a phylogenetic correlation matrix derived from a phylogenetic tree, $sp_{k[i]}$ is the species-specific effect for the *k*th species applied to effect size *i* [assumed to be ~ *N*$(0, \sigma^{2}_{sp}I)$], $s_{j[i]}$ is the study-specific effect for the *j*th study applied to effect size *i* [assumed to be ~ *N*$(0, \sigma^{2}_{s}I)$, where I is an identity matrix], $e_{i}$ is the effect size-specific effect (or within study effect, or residuals) for the *i*th effect size [assumed to be ~ *N*$(0, \sigma^{2}_eE)$], and $m_{i}$ is the sampling variance effect around the *i*th effect as a result of variation in precision among each effect size [assumed to be  ~ *N*$(0, M)$], where M is a variance-covariance matrix with the diagonal elements being the effect size sampling variance.
+This model is a 'weighted' multilevel meta-analysis model because we can estimate the overall sampling variance.
+This is very important because it provides a way for us to understand just how much variation in effects are simplly the result of sampling differences across studies versus other, potentially improtant sources of variation such as differences in the methods applied, species differences or even real biological effects that impact the effect size a study is likely to observe.
+This is formalised in what we call 'heterogenetiy analysis' which we describe below.
+Importantly, this model provides us with the answer to our overall question: Across all the species and studies manipulating corticosterone, how much of an overall effect does corticostrone have on XX relative to control conditions?
+
 #### *Heterogenity Analysis: How Much Effect Size Variation Actually Exists?*

### 2021-06-04 MS/ms.Rmd
Started table 1, and started writing general effect size paragraph

@@
 
-All titles and abstracts and full text screening was done by two people (DWAN and ML).
+All title, abstract and full text screening was done by two people (DWAN and ML).
 Any conflicts or disagreements were resolved by discussion and a concensus on a paper was reached.
@@
 #### *Brief Introduction to Common Effect Sizes and Sampling Errors that are Useful in Comparative Physiology*
+
+Meta-analysis requires comparative physiologists to make use of effect sizes that are suitable for answering their specific question.
+The key features of all effect sizes used in meta-analyses are that they are: 1) statistical parameters that have been placed on a common scale so that they can be compared across studies and 2) that they have some associated measure of precision (i.e., sampling variance)[@Koricheva2013; @Borenstein2009; @Schmid2021].
+Effect sizes in comparative physiology are quite variable; they can be the mean difference between two groups (e.g., difference in mean between a control and treatment group - see @WuSeebacher2020), the slope of a regression (e.g., between body size and metabolic rate), a correlation between two variables, or even the raw mean (or variance) itself (e.g., comparing CTmax across species - see @Sunday2014).
+In many cases, multiple types of effect sizes might be used depending on the question.
+For example, studies interested in the effect of temperature on some physiological trait that have measured the trait across studies experimentally manipulating temperature could analyse the mean 'effect' by creating contrast-based effect sizes or by analysing the mean in each temperature treatment.
+The choice as to which one to use will boil down to the types of data available from primary studies, the specific question of interest and whether studies are observational or experimental in nature.
+Considering our temperature example above, if we are interested in the magnitude of change between temperature treatments, we may want to use a contrast-based effect size, such as the log response ratio $ln_{RR}$.
+If we are instead interested in how the mean of some physiological trait changes with tempearture we may instead model the mean itself.
+In the latter scenerio, so long as all the means are measured in the same units (e.g., ; or can be converted to the same units) then the mean may provide the desired answer to a given question.
+We provide details on different effect measures and associated sample sizes in Table \@ref(tab:tablea).
+
+```{r tablea, echo = FALSE, tab.cap = "Common effect sizes, associated sampling variances and notes on when they might be used.
+Note that for log odds ratio a continuity correction is applied (i.e., 0.5) to each proportion.
+In addition, a correction factor, J (1-3 / ..), is applied to the standardised to correct for small sample effects"}
+
+# I'm just listing a bunch here, but we should think about what we want to include. Here's an example of how we can make a table with all equations. Fun!
+names <- c("Mean",
+           "Variance",
+           "Log Response Ratio",
+           "Standardised Mean Difference",
+           "Zr (Correlation Coefficient)",
+           "Log Odds Ratio")
+eqns_yi <- c("X_{i}",
+             "\\sigma^2",
+             "log \\left( \\frac{X_{1}}{X_{2}} \\right)",
+             "\\frac{\\left( X_{1} - X_{2}  \\right)}{sd_{p}}J",
+             "\\frac{1}{2} log \\left( \\frac{1+r_{i}}{1-r_{i}} \\right)",
+             "log \\left( \\frac{y_{i2}+0.5}{n_{i2} - y_{i2}+0.5} \\right) - log \\left( \\frac{y_{i1}+0.5}{n_{i1} - y_{i1}+0.5} \\right)")
+#eqns_vi <- c()
+
+table_fin <- data.frame(names, eqns_yi)
+
+# Note: It is esssential that you be clear that the function 'compose' is exported from the flextable package. That's because purr also has the same function, so it gets messy.
+tablea <- flextable(table_fin) %>% 
+          flextable::compose(j = "names", part = "header", value = as_paragraph(as_b("Effect Measure"))) %>% 
+          flextable::compose(j = "eqns_yi", part = "header", value = as_paragraph(as_b("Definition"))) %>% 
+          flextable::compose(j = "eqns_yi", value = as_paragraph(as_equation(eqns_yi))) %>% 
+          flextable::width(j = 1, 3) %>% 
+          flextable::width(j = 2, 2)
+
+tablea
+
+```
 

### 2021-06-04 MS/ms.Rmd
Started writing heterogenity section some more

@@
     number_sections: no
-    toc: yes
+    toc: no
     toc_depth: 6
@@
     options(digits = 2)
+
+  pacman::p_load(flextable, tidyverse, equatags)  
 ```
@@
 Note that for log odds ratio a continuity correction is applied (i.e., 0.5) to each proportion.
-In addition, a correction factor, J (1-3 / ..), is applied to the standardised to correct for small sample effects"}
+In addition, a correction factor, J (1-3 ), is applied to the standardised to correct for small sample effects"}
 
-# I'm just listing a bunch here, but we should think about what we want to include. Here's an example of how we can make a table with all equations. Fun!
+# I'm just listing a bunch here, but we should think about what we want to include.
+Here's an example of how we can make a table with all equations.
+Fun!
+Really useful website here: https://math.meta.stackexchange.com/questions/5020/mathjax-basic-tutorial-and-quick-reference.
+Something wrong with character coding when rendering word document.
+Has to do with the log odds ratio equation.
+Renders fine in html, but just stops when word
 names <- c("Mean",
@@
            "Standardised Mean Difference",
-           "Zr (Correlation Coefficient)",
-           "Log Odds Ratio")
+           "Zr (Correlation Coefficient)")
+           #"Log Odds Ratio",
+           #"")
+
 eqns_yi <- c("X_{i}",
              "\\sigma^2",
-             "log \\left( \\frac{X_{1}}{X_{2}} \\right)",
-             "\\frac{\\left( X_{1} - X_{2}  \\right)}{sd_{p}}J",
-             "\\frac{1}{2} log \\left( \\frac{1+r_{i}}{1-r_{i}} \\right)",
-             "log \\left( \\frac{y_{i2}+0.5}{n_{i2} - y_{i2}+0.5} \\right) - log \\left( \\frac{y_{i1}+0.5}{n_{i1} - y_{i1}+0.5} \\right)")
-#eqns_vi <- c()
+             "log \\left( \\frac{X_{1}}{X_{2}}\\right)",
+             "\\frac{\\left( X_{2} - X_{1}\\right)}{sd_{p}}J",
+             "\\frac{1}{2}log\\left(\\frac{1+r_{i}}{1-r_{i}}\\right)")
+             #"log\\left(\\frac{y_{i2}+0.5}{n_{i2}-y_{i2}+0.5}\\right) ",
+             #"- log\\left(\\frac{y_{i1}+0.5}{n_{i1}-y_{i1}+0.5}\\right)")
 
-table_fin <- data.frame(names, eqns_yi)
+# Just placeholders for now
+eqns_vi <- c("\\frac{s_{i}^2}{n_{i}}",
+             "\\frac{s_{i}^2}{n_{i}}",
+             "\\frac{s_{i}^2}{n_{i}}",
+             "\\frac{s_{i}^2}{n_{i}}",
+             "\\frac{s_{i}^2}{n_{i}}")
+             #"\\frac{s_{i}^2}{n_{i}}",
+             #"")
+
+table_fin <- data.frame(names, eqns_yi, eqns_vi)
 
@@
           flextable::compose(j = "eqns_yi", part = "header", value = as_paragraph(as_b("Definition")))        %>% 
+          flextable::compose(j = "eqns_vi", part = "header", value = as_paragraph(as_b("Sampling Variance"))) %>%
           flextable::compose(j = "eqns_yi", value = as_paragraph(as_equation(eqns_yi)))                       %>%
+          flextable::compose(j = "eqns_vi", value = as_paragraph(as_equation(eqns_vi)))                       %>% 
           flextable::width(j = 1, 3)                                                                          %>% 
@@
 #### *Heterogenity Analysis: How Much Effect Size Variation Actually Exists?*
-Quantifying effect size heterogenity (i.e., effect size variance) provides a pathway to explore hypotheses thought to explain why effect might vary across studies.
+Quantifying effect size heterogenity (i.e., effect size variance) provides a pathway to explore hypotheses thought to explain why effects might vary within and across studies.
+Effect size heterogeneity can be thought of as the percentage of variance between effect sizes that cannot be attributable to sampling error (often as called 'total' heterogenity) @Higgins2002.
+It provides a formal way to assess how much variation is the result of 'true' biological or methodological differences as opposed to simply chance (i.e., sampling variance).
+We can only conduct such analyses if we have an estimate of the sampling variance for a given effect measure becasue only then can we quantify how much variation is the result of sampling variability.
+@Senior2016 has shown that total heterogenity is often extremely high in ecological and evolutionary meta-analysis (~91%), suggesting that effect measures vary widely across within and studies.
+Some of the variation is clearly the result of working with different species or strains, different traits and different outcome measures, however, some of this variation also arises because of methodological differences across studies
 

### 2021-06-04 MS/ms.Rmd
Just some notes

@@
 Effect size heterogeneity can be thought of as the percentage of variance between effect sizes that cannot be attributable to sampling error (often as called 'total' heterogenity) @Higgins2002.
-It provides a formal way to assess how much variation is the result of 'true' biological or methodological differences as opposed to simply chance (i.e., sampling variance).
+We can qauntify this using our multilevel meta-analytic models we describe above.
+Quantifying heterogenity provides a formal way to assess how much variation is the result of 'true' biological or methodological differences as opposed to simply chance (i.e., sampling variance).
 We can only conduct such analyses if we have an estimate of the sampling variance for a given effect measure becasue only then can we quantify how much variation is the result of sampling variability.
@@
 Some of the variation is clearly the result of working with different species or strains, different traits and different outcome measures, however, some of this variation also arises because of methodological differences across studies
+** NOTE THAT WE MAY WNAT TO SWITCH POSITION, INTRODUCE METEREGRESSION FIRSTs
 

### 2021-06-07 MS/ms.Rmd
Writing heterogeneity section. Trying to link back to initial point of paper a bit better

--- 2021-06-04 MS/ms.Rmd
@@
 Meta-analysis provides quantitatively informed answers to research questions by using a transparent and reproducible search strategy to synthesise research results across studies and identify sources of variation [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Arnqvist1995; @Koricheva2013].
-Meta-analysing independent studies provides greater statistical power and precision than what any individual study on its own would be able to provide on a given question - particularly given that most empirical studies are already under-powered in many areas of biology [@Forstmeier2017; @Jennions2003; @Button2013].
+Meta-analysing independent studies provides greater statistical power and precision than what any individual study on its own would be able to provide on a question - particularly given that most empirical studies are already under-powered in many areas of biology [@Forstmeier2017; @Jennions2003; @Button2013].
 By expressing study effects on a common scale (i.e., standardised effect size) a meta-analyst can gain broader insight into the direction and efficacy of a particular treatment effect or the strength of a relationship between two variables of interest [@Gurevitch2018; @Koricheva2013].
@@
 A critically important feature of meta-analaysis is its ability to account for sampling error [@Koricheva2013].
-The inverse sampling error is used to weight higher powered studies in the analysis and make overall esatimtes more precise.
+The inverse sampling error is used to weight higher powered studies in the analysis and make overall estimates more precise.
 While many meta-analyses might employ unweighted analyses, these studies will not gain greater precision on estimates because sampling variance cannot be formally accounted for in the analysis, even if the overall mean itself is unbiased.
@@
 In addition, they often include a diversity of study species which can vary in responses.
+To the uninitiated the concern might not be unfounded given that meta-analyses in ecology and evolution often mix highly heterogenous effect size estimates often resulting in high variability [@Senior2016].
 
@@
 #### *Multi-level Meta-Analysis when the Overall Effect is of Interest*
-One of the main goals of meta-analysis is to obtain an overall meta-analytic mean estimate (and some form of uncertainty around that mean, like a 95% confidence interval, may be even with a prediction interval - @Nakagawa2021c) which describes the magnitude of effect across all the studies / effects included in the meta-analysis.
-This is generally done with a simple random effects or multilevel meta-analytic model that accounts for effect size sampling error [@Nakagawa2017; @NakagawaSantos2012].
+One of the main goals of meta-analysis is to obtain an overall meta-analytic mean effect size estimate and some form of uncertainty around that mean, like a 95% confidence interval (CI).
+Including a prediction interval (PI) can also be quite useful because, in the context of a meta-analysis, it provides the range of effect size values we might expect to observe if a new study were to be conducted [@Nakagawa2021c].
+Estimating an overall mean along with 95% CI (or PI) is generally done with a simple random effects or multilevel meta-analytic model that accounts for effect size sampling error [@Nakagawa2017; @NakagawaSantos2012].
 More often than not, meta-analyses in comparative physiology will have complex hierachical structure.
@@
 Quantifying effect size heterogenity (i.e., effect size variance) provides a pathway to explore hypotheses thought to explain why effects might vary within and across studies.
-Effect size heterogeneity can be thought of as the percentage of variance between effect sizes that cannot be attributable to sampling error (often as called 'total' heterogenity) @Higgins2002.
-It provides a formal way to assess how much variation is the result of 'true' biological or methodological differences as opposed to simply chance (i.e., sampling variance).
-We can only conduct such analyses if we have an estimate of the sampling variance for a given effect measure becasue only then can we quantify how much variation is the result of sampling variability.
-@Senior2016 has shown that total heterogenity is often extremely high in ecological and evolutionary meta-analysis (~91%), suggesting that effect measures vary widely across within and studies.
-Some of the variation is clearly the result of working with different species or strains, different traits and different outcome measures, however, some of this variation also arises because of methodological differences across studies
+Effect size heterogeneity can be thought of as the percentage of variance between effect sizes that cannot be attributable to sampling error (often as called 'total' heterogenity) [@Higgins2002].
+More formally, we can quantify heterogenity using the multilevel meta-analytic model we describe above as:
+
+$$ I^2_{total} = \frac{\sigma^2_{total} - \sigma^2_{m}}{\sigma^2_{total}} $$
+where $\sigma^2_{total}$ is the  total effect size variance (using the above multilevel model than $\sigma^2_{total} = \sigma^2_{study} + \sigma^2_{phylogeny} + \sigma^2_{species} + \sigma^2_{residual} +\sigma^2_{m}$) and $\sigma^2_{m}$ is the total sampling error variance.
+Quantifying heterogenity provides a formal way to assess how much variation is the result of 'true' biological or methodological differences as opposed to simply chance (i.e., sampling variance) [@NakagawaSantos2012; @Higgins2002].
+We can only conduct such analyses if we have an estimate of the sampling variance for a given effect measure because only then can we quantify how much variation is the result of sampling variability.
+@Senior2016 have shown that total heterogenity is often extremely high in ecological and evolutionary meta-analysis (~91%), suggesting that effect measures vary widely across and within studies.
+Some of the variation is clearly the result of working with different species or strains, different traits and different outcome measures, however, some of this variation also arises because of methodological differences across studies that might be related to the dosages or temperatures used for treatments.
+Formally quantifying and presenting heterogenity estimates from meta-analytic models can provide a way to undersand the major drivers of effect size variation by allowing researchers to produce various $I^2$ estimates which can be formally compared within and across studies.
+For example, we could fit the multilevel model described above to understand what proportion of variation is the result of, say, 'study' effects following @NakagawaSantos2012:
+
+$$ I^2_{study} = \frac{\sigma^2_{study}}{\sigma^2_{study} + \sigma^2_{phylogeny} + \sigma^2_{species} + \sigma^2_{residual} +\sigma^2_{m}} $$
+where $\sigma^2_{study}$ is the study specific variance, and all other variance components are for phylogeny, species, residual (effect size level) and m (total measurement/sampling error).
+Many readers will notice the similarities between $I^2$ and $R^2$ [@Nakgawa2013; @Nakagawa2010].
+If we want to formally assess how much effect size variation is the result of methodological factors, such as temperature and dosage differences applied across studies, then we could fit our multilevel meta-regression model, including dosage or temperature (linear, quadratic or even more complex fits), and estimate how much variation is explained by these fixed effects.
+
+** NOTE THAT WE MAY WNAT TO SWITCH POSITION, INTRODUCE METEREGRESSION FIRSTs
 

### 2021-06-07 MS/ms.Rmd
Wrote het section and also meta-regerssion section, but first draft

@@
 It will not be possible to derive an effect size that completely controls for known heterogenity at the effect size level all the time.
-This may because because treatment effects may not be simple linear or exponential functions of the mean response making the relationship with effect size complex [e.g., thermal performance curves; @Noble2018].
+This may be because treatment effects are not be simple linear or exponential functions of the mean response making the effect sizes we discuss above unsuitable [e.g., thermal performance curves; @Noble2018].
 For example, dosages applied to treatments can follow quite complex non-linear relationships, with expoential or quadratic relationships in relation to some mean response.
@@
 
-If we assume that we are interested in understanding the overall effect of, say, stress (i.e., corticosterone) on XX we might extract data from studies manipulating corticosterone on eggs.
+Assume that we are interested in understanding the overall effect of, say, stress (i.e., corticosterone - CORT) on reproduction [e.g., see @Podmola2018] we might extract data from studies manipulating corticosterone in bird eggs.
 Of course, these studies are diverse, apply different dosages of corticosterone and are working across many species.
-If the studies are experimental in nature, than a standardised effect size, such as $ln_{RR}$ might be applicable.
+If the studies are experimental in nature, than a standardised effect size, such as $ln_{RR}$ or Hedges' *d* might be applicable.
 We then might fit an overall, multilevel meta-analytic model as follows:
+$$
+\begin{equation} 
+Y_{i} = \beta_{0} + a_{k[i]} + sp_{k[i]} + s_{j[i]} + e_{i} + m_{i}\\
+a_{k[i]}\sim N(0, \sigma^{2}_aA),\\
+sp_{k[i]}\sim N(0, \sigma^{2}_{sp}I),\\
+s_{j[i]}\sim N(0, \sigma^{2}_{sp}I),\\
+e_{i}\sim N(0, \sigma^{2}_eI),\\
+m_{i} \sim N(0, v_{i})\\
+(\#eq:MLMM)
+\end{equation} 
+$$
+where $Y_{i}$ is the *i*th effect size (*i* = 1 ...
+$N_{ES}$, the number of effect sizes), $\beta_{0}$ is the overall meta-analytic mean, $a_{k[i]}$ is the phylogenetic effect for species *k* applied to effect size *i*.
+Phylogenetic effects are assumed to be normally distributed deviates sampled from a distribution with a mean of 0 and variance $\sigma^{2}_aA$ [i.e., *N*$(0, \sigma^{2}_aA)$], where A is a phylogenetic correlation matrix derived from a phylogenetic tree, $sp_{k[i]}$ is the species-specific effect for the *k*th species applied to effect size *i*, $s_{j[i]}$ is the study-specific effect for the *j*th study applied to effect size *i*, $e_{i}$ is the effect size-specific effect (or within study effect, or residuals) for the *i*th effect size, and $m_{i}$ is the sampling variance effect around the *i*th effect as a result of variation in precision among each effect sizes, $v_{i}$, which is known.
+This model is a 'weighted' multilevel meta-analysis model because the estimation of *u* is weighted by the inverse sampling variance of each effect size.
+The fact that we can obtain an overall estimate of sampling variance (i.e., $\sigma^2_{m}$) is very important because it provides a way for us to understand just how much variation in effects are the result of sampling differences across studies versus other, potentially improtant sources of variation such as differences in the methods applied, species differences or even real biological effects that impact the effect size a study is likely to observe [@Nakagawa2017; @NakagawaSantos2012].
+This is formalised in what we call 'heterogenetiy analysis' which we describe below.
+Importantly, this model provides us with the answer to our overall question: Across all the species and studies manipulating egg corticosterone, how much of an overall effect does corticostrone have on reproduction relative to control conditions?
 
-$$ z_{i} = u + a_{k[i]} + sp_{k[i]} + s_{j[i]} + e_{i} + m_{i} $$
+Of course, the overall effect does not provide us a way to interpret its magnitude in the context of how much CORT has been applied in the treatment.
+The most we can say about it, is that the effect is small, moderator of large out of the sample of effect sizes extracted from this set of studies.
+In the next section, we show how to 'correct' the overall effect size so that its interpretation is more meaningful.
 
-where $z_{i}$ is the *i*th effect size (*i* = 1 ...
-$N_{ES}$, the number of effect sizes), *u* the overall meta-analytic mean, $a_{k[i]}$ is the phylogenetic effect for species *k* applied to effect size *i*.
-Phylogenetic effects are assumed to be normally distributed deviates sampled from a distribution with a mean of 0 and variance $\sigma^{2}_aA$ [hereafter denoted ~ *N*$(0, \sigma^{2}_aA)$], where A is a phylogenetic correlation matrix derived from a phylogenetic tree, $sp_{k[i]}$ is the species-specific effect for the *k*th species applied to effect size *i* [assumed to be ~ *N*$(0, \sigma^{2}_{sp}I)$], $s_{j[i]}$ is the study-specific effect for the *j*th study applied to effect size *i* [assumed to be ~ *N*$(0, \sigma^{2}_{s}I)$, where I is an identity matrix], $e_{i}$ is the effect size-specific effect (or within study effect, or residuals) for the *i*th effect size [assumed to be ~ *N*$(0, \sigma^{2}_eE)$], and $m_{i}$ is the sampling variance effect around the *i*th effect as a result of variation in precision among each effect size [assumed to be  ~ *N*$(0, M)$], where M is a variance-covariance matrix with the diagonal elements being the effect size sampling variance.
-This model is a 'weighted' multilevel meta-analysis model because we can estimate the overall sampling variance.
-This is very important because it provides a way for us to understand just how much variation in effects are simplly the result of sampling differences across studies versus other, potentially improtant sources of variation such as differences in the methods applied, species differences or even real biological effects that impact the effect size a study is likely to observe.
-This is formalised in what we call 'heterogenetiy analysis' which we describe below.
-Importantly, this model provides us with the answer to our overall question: Across all the species and studies manipulating corticosterone, how much of an overall effect does corticostrone have on XX relative to control conditions?
+#### *Multilevel Metaregression to Understand Variation and Improve Interpretation*
+
+Heterogenity among effects that result from known differences in how treatments are applied can also be dealt with using multilevel meta-regression models.
+Multilevel meta-regression models include all the same random effects that we have already discussed, but they also include fixed effects (i.e., predictors or moderators) that attempt to explain changes in the mean effect size.
+In otherwords, we can modify our multilevel meta-analytic model to turn it into a multilevel meta-regression model as follows:
+
+$$ Y_{i} = \beta_{0} + \sum \beta_{j}x_{j} + a_{k[i]} + sp_{k[i]} + s_{j[i]} + e_{i} + m_{i} $$
+where $\sum \beta_{j}x_{j}$ is simply the sum of all slope effects for all moderators, $x_{j}$.
+All other notation is the same as described above.
+Importantly, the variable $x_{j}$ could be any moderator collected from studies, including dosage, temperature, salinity, or pH.
+Some moderators will be at the level of the study (e.g., was the study experimental or observational in nature) but others could be taken at the effect size level (i.e., was the effect derived using a tempearture of 23&deg;C or 35&deg;C).
+By including these moderators in a meta-regression model, the interpretation of the overall meta-analytic mean, $\beta_{0}$, changes.
+For example, assume we collected the change in CORT dosage relative to a control group (i.e., in uL / g) for our meta-analysis on egg CORT effects on bird reproduction.
+If the untransformed dosage, $x_{j}$, is included in the model then the overall meta-analystic mean estimate, $\beta_{0}$, would be the mean effect of CORT relative to a control treatment, on reproduction  when the dosage difference between the treatment and control group is 0 uL /g.
+Of course, this interpretation does not make much sense.
+We can, however, apply some simple transformations to make the overall mean estimate more intuitive to understand with the added benefit that it can help improve the interpretation of non-linear parameters estimated by the model [@Schielzeth2010; @GelmanHill2007].
+One simple transformation would be to centre the variable $x_{j}$, by subtracting each value from the mean to create a new input variable (i.e., $c_{i}=x_{i}-\bar{x}$, where the subscript *i* denotes each individual effect size dosage).
+The new variable, $c_{j}$, is now centered on the mean and can replace $x_{j}$.
+When the model is refit with $c_{j}$ the estimated $\beta_{0}$ can now be more intuitivly interpreted as the overall mean effect of CORT on reproduction at an average dosage difference between treatment and control groups.
+Importantly, by centering, we retain the original units (uL / g) of the variable, which can be very useful to allow for a more general interpretation of the effect magnitude.
+Of course, if one is not interested in the magnitude of effect, we could also change our question and simply model mean reproductive output as a function of dosage (often what are referred to as 'arm-based' meta-analytic models).
+Here, one can model the mean for each group (i.e., control and treatment group), and acount for the known sampling variance associated with each group mean.
+Dosage, or other continuous variables like temperature, can then be modelled (accounting for sampling variance) to understand how mean reproductive output changes.
+It is important to recognise that all means need to be comparable and that these models are more complex to fit.
+While they can be equivalent to 'contrast-based' models, they require complex interactions to be estimated [@Nakagawa2015].
+
+Centering moderator variables, like temperature and dosage, not only provides a way to make the overall mean effect more interpretable in the face of treatment heterogenity, but it also allows more complex relationships to be fit without compromising interpretations, including non-linear parameters and interactions (e.g., polynomials).
+In other words, linear / main effects can still be interpreted normally in the presence of non-linear / interactions fit in the model [@Schielzeth2010; @GelmanHill2007].
+This can be particularly powerful when more complex, nonlinear, dosage relationships exist.
+We provide examples in the online supplementary material (with R code) to show readers how teh models we describe above can be fit, and how, meta-analytic means can be adjusted for treatment heterogenity.
 
@@
 
-$$ I^2_{total} = \frac{\sigma^2_{total} - \sigma^2_{m}}{\sigma^2_{total}} $$
-where $\sigma^2_{total}$ is the  total effect size variance (using the above multilevel model than $\sigma^2_{total} = \sigma^2_{study} + \sigma^2_{phylogeny} + \sigma^2_{species} + \sigma^2_{residual} +\sigma^2_{m}$) and $\sigma^2_{m}$ is the total sampling error variance.
+$$ I^2_{total} = \frac{\sigma^2_{total} - \sigma^2_{m}}{\sigma^2_{total}}, \
+\sigma^2_{total} = \sigma^2_{study} + \sigma^2_{phylogeny} + \sigma^2_{species} + \sigma^2_{residual} +\sigma^2_{m}
+$$
+where $\sigma^2_{total}$ is the  total effect size variance (using the above multilevel model) and $\sigma^2_{m}$ is the total sampling error variance.
 Quantifying heterogenity provides a formal way to assess how much variation is the result of 'true' biological or methodological differences as opposed to simply chance (i.e., sampling variance) [@NakagawaSantos2012; @Higgins2002].
@@
 
-$$ I^2_{study} = \frac{\sigma^2_{study}}{\sigma^2_{study} + \sigma^2_{phylogeny} + \sigma^2_{species} + \sigma^2_{residual} +\sigma^2_{m}} $$
+$$ I^2_{study} = \frac{\sigma^2_{study}}{\sigma^2_{total}} $$
 where $\sigma^2_{study}$ is the study specific variance, and all other variance components are for phylogeny, species, residual (effect size level) and m (total measurement/sampling error).
 Many readers will notice the similarities between $I^2$ and $R^2$ [@Nakgawa2013; @Nakagawa2010].
-If we want to formally assess how much effect size variation is the result of methodological factors, such as temperature and dosage differences applied across studies, then we could fit our multilevel meta-regression model, including dosage or temperature (linear, quadratic or even more complex fits), and estimate how much variation is explained by these fixed effects.
+If we want to formally assess how much effect size variation is the result of methodological factors, such as temperature and dosage differences applied across studies, then we could fit our multilevel meta-regression model, including dosage or temperature (linear, quadratic or even more complex fits), and estimate how much variation is explained by these fixed effects following @Nakgawa2013.
 
-** NOTE THAT WE MAY WNAT TO SWITCH POSITION, INTRODUCE METEREGRESSION FIRSTs
+$$ I^2_{hetero} = \frac{\sigma^2_{fixed}}{\sigma^2_{fixed} + \sigma^2_{total}} $$
 
-#### *Multi-level Metaregression to Understand Variation and Improve Interpretation*
+The $I^2_{hetero}$ provides a formal means to assess just how much variation in effects is teh result of known heterogeneity at the effect size level, driven by continuous moderators such as dosage, temperature, salinity, and even pH.
+$I^2_{hetero}$ maybe a useful measure to provide to help readers understand just how much effec variation can result from the specific treatment application.
 

### 2021-06-14 MS/ms.Rmd
I think we need to 1) add another section on the apples and oranges problem to make it super clear to the reader what exactly it is. The introduction may not currently achieve this well enough, and it seems like an abrupt transition to survey from the introduction. 2) Seperate out goasl of survey before jumping into the methods.

@@
 
-* Corespondance:
-
 ## **Abstract**
@@
 Here, we dispel this myth by showing how standardised effects sizes can be used in conjunction with powerful multi-level meta-analytic models to both account for factors driving differences across studies and make them more comparable.
-In addition, we derive new effect size measures that provide comparative physiologists with a means to directly make effect sizes comparable without the need to resort to more complex statistical models that may be harder to interpret.
-Our ‘new’ effect sizes and corresponding sampling variances help physiologists deal with common treatment differeces across studies; allowing researchers to compare both mean differences (e.g., $Q_{10}$ to compare mean differences in physiological rates over 10 degrees) and associated differences in variance (e.g, $S_{Q10}$ for comparing variability in in physiological rates over 10 degrees) for physiological traits.
+In addition, we derive new effect size measures that provide comparative physiologists with a means to directly make effect measures comparable without the need to resort to more complex statistical models that may be harder to interpret.
+Our ‘new’ effect sizes and corresponding sampling variances help physiologists deal with common treatment differeces across studies; allowing researchers to compare both mean differences and associated differences in variance for physiological traits.
 The new effect sizes we propose, in combination with existing meta-analytic models, will pave the way for comparative physiologists to explore exciting new questions by making results from large-scale data sets collected from the literature more accessible and widely interpretable.
@@
 We first conduct a survey of published meta-analyses in the field of comparative physiology to gauge methodological and meta-analytic approaches - assessing what types of effect sizes are commonly used, how often effect size estimates are impacted by continuous treatment differences and whether meta-analytic models (i.e., models that account for sampling variance) are commonly applied.
-We then introduce new effect sizes and their assocaited sampling variance to provide comparative physiologists opportunities to explictly incorperate treatment differences into the effect size estimates to easy their interpretation.
-We then describe how more complex treatment differences, such as dosage differences, which may have more complex non-linear effects, can be accomodated using multilevel meta-regression models.
-Expanding the meta-analtic toolkit for comparative physiologists will provide new opportunities to address global scale problems that attempt to undersatnd how organisms will cope with rapidly changing environments in the future.
+We then introduce new effect sizes and their assocaited sampling variance to provide comparative physiologists opportunities to explictly incorperate treatment differences into the effect size estimates to ease their interpretation.
+We then describe how more complex treatment differences, such as dosage differences, which may have non-linear effects, can be accomodated using multilevel meta-regression models.
+We hope to show how expanding the meta-analtic toolkit for comparative physiologists will provide new opportunities to address global scale problems that attempt to understand how organisms will cope with rapidly changing environments in the future.
+
+## **The Apples and Oranges 'Problem': How lack of comparability can make effects vary widely across studies**
+ I'm thinking now, in re-reading this, that we could use a slightly expanded version of paragraph 4 taht describes this problem in a little more detail.
+This is likely the place for a figure, which I am having some trouble envisaging where one is best placed.
+It just otherwise seems like a bit of a jump to otherwise head straight into the survey
 
 ## **Survey of Meta-Analytic Practices in Comparative Physiology**
-#### *Literature Search and Survey Data Collection*
-To understand meta-analytic practices in comparative physiology, we searched for meta-analyses and comparative analyses that tackled questions that relied on using physiological data compiled from animal studies across multiple species.
+As discussed above, it is clear that different types of questions and experimental approaches will be more or less susceptable to the 'apples and oranges' problem.
+As such, before embarking on our path to 'meta-analytic enlightenment', we conducted a literatrure survey to understand how widespread the problem may be in comparative physiology and gauge the ways in which it is currently being addressed, if at all.
+To accomplish this goal, we searched for meta-analyses and comparative analyses that tackled questions using physiological data compiled from animal studies across multiple species.
 We were specifically interested in asking: 1) what type of effect size was used within the quantitative synthesis?
@@
 3) If so, was the variation resulting from treatment differences accounted for in the effect size or during analysis?, and finally, 4) how were effect sizes analysed in the quantitative synthesis, were these weighted analyses, and what program was used for analysis?
-We also recorded whether publication bias and sensitivity analyses were conducted, if data were publicly available, where it was stored and if so it was usable (i.e., in a format like .txt).
+We also recorded whether publication bias and sensitivity analyses were conducted, if data were publicly available, where it was stored, and if so, if it was usable (i.e., in a machine readable format).
+
+#### *Literature Search and Survey Data Collection*
 All searches were conducted in Scopus between May 16 - 18, 2021.

### 2021-06-14 MS/ms.Rmd
Adding some written stuff. Update dto ref

@@
 
-Despite the widespread adoption and well established methodological procedures of meta-analysis it is often criticised for mixing 'apples and oranges' - in otherwords, mixing effects from studies that lack comparability [@Gurevitch2018; @Arnqvist1995; @Gallo1979; @Carpenter2020; @Stewart2010].
+Despite the widespread adoption and well established methodological procedures of meta-analysis it is often criticised for mixing 'apples and oranges' - in otherwords, mixing effects from studies that lack comparability [@Gurevitch2018; @Arnqvist1995; @Gallo1979; @Carpenter2020; @Stewart2010; @Glass2015].
 Lack of comparability could result from studies differing in experimental design, species, measurement variables and sampling units, which can impact the generalisability of meta-analytic results [@Arnqvist1995; @Stewart2010].
@@
 This is likely the place for a figure, which I am having some trouble envisaging where one is best placed.
-It just otherwise seems like a bit of a jump to otherwise head straight into the survey
+It just otherwise seems like a bit of a jump to otherwise head straight into the survey.
+Here we should also talk about quality control, the need to be transparent and have careful reporting.
+This is a big issue in medicine.
+Talked about a lot.
+Integrate blurb below...try to take a balanced approach.
+
+In the words of Gene Glass, arguably the father of meta-analysis: "Of course it mixes apples and oranges; in the study of fruit nothing else is sensible; comparing apples and oranges is the only endeavor worthy of true scientists; comparing apples to apples is trivial" [p.g., 224, @Glass2015].
+We tend to agree, particularly in comparative physiology.
+By synthesizing diverse study outcomes, it allows us to not just report on overall effects, but understand critical features of the literature, study systems and approaches that can explain the diversity of effect outcomes observed.
+In doing so, it provides a richer set of conclusions that can draw attention to important sources of variability that might otherwise be overlooked.
+Having said that, it is still very improtant to understand the limitations and diversity of studies included within a meta-analysis.
+Answers to certain questions will inevitably depend on the homogeneity of effects being synthesized.
 

### 2021-06-14 MS/ms.Rmd
Fixing equation for MLMM

@@
 \begin{equation} 
-Y_{i} = \beta_{0} + a_{k[i]} + sp_{k[i]} + s_{j[i]} + e_{i} + m_{i}\\
-a_{k[i]}\sim N(0, \sigma^{2}_aA),\\
-sp_{k[i]}\sim N(0, \sigma^{2}_{sp}I),\\
-s_{j[i]}\sim N(0, \sigma^{2}_{sp}I),\\
-e_{i}\sim N(0, \sigma^{2}_eI),\\
-m_{i} \sim N(0, v_{i})\\
+Y_{i} = \beta_{0} + a_{k[i]} + sp_{k[i]} + s_{j[i]} + e_{i} + m_{i}\
 (\#eq:MLMM)
@@
 $$
+$$
+\begin{equation} 
+a_{k[i]}\sim N(0, \sigma^{2}_aA),\
+sp_{k[i]}\sim N(0, \sigma^{2}_{sp}I),\
+s_{j[i]}\sim N(0, \sigma^{2}_{sp}I),\
+e_{i}\sim N(0, \sigma^{2}_eI),\
+m_{i} \sim N(0, v_{i})\
+(\#eq:dist)
+\end{equation} 
+$$
+
 where $Y_{i}$ is the *i*th effect size (*i* = 1 ...

### 2021-06-14 MS/ms.Rmd
Adding some clarification

@@
 In the words of Gene Glass, arguably the father of meta-analysis: "Of course it mixes apples and oranges; in the study of fruit nothing else is sensible; comparing apples and oranges is the only endeavor worthy of true scientists; comparing apples to apples is trivial" [p.g., 224, @Glass2015].
-We tend to agree, particularly in comparative physiology.
+@Glass2015's intention was to simply highlight that whether comparing apples and oranges is a good idea simply boils down to the specific question of interest.
+If we are interested in gaining insight into 'fruit' then synthesising apples and oranges is a good idea.
+Instead, if we are intersted in generalising to apples only, then mixing fruit will not be ideal.
+We tend to agree with @Glass2015 and his sentiment is of particular relevance to comparative physiology.
 By synthesizing diverse study outcomes, it allows us to not just report on overall effects, but understand critical features of the literature, study systems and approaches that can explain the diversity of effect outcomes observed.
-In doing so, it provides a richer set of conclusions that can draw attention to important sources of variability that might otherwise be overlooked.
-Having said that, it is still very improtant to understand the limitations and diversity of studies included within a meta-analysis.
+In doing so, it provides a richer set of conclusions that can draw attention to important sources of variability that might have otherwise been overlooked.
+Having said that, it is still very important to understand the limitations and diversity of studies included within a meta-analysis.
 Answers to certain questions will inevitably depend on the homogeneity of effects being synthesized.

### 2021-06-14 MS/ms.Rmd
More writing of applesa nd oranges problem

@@
 
-Meta-analysis is a well-developed research field with a long history in statistics, medicine, psychology and ecology [@Gurevitch2018; @Nakagawa2017].
+Meta-analysis is a well-developed research field with a long history in statistics, medicine, psychology and ecology [@Gurevitch2018; @Nakagawa2017; @Glass2015].
 It has emerged as the 'gold-standard' across various disciplines for quantitative synthesis and is becoming increasingly more prominant the field of comparative physiology.
@@
 Integrate blurb below...try to take a balanced approach.
+*I will add an introduction bit to this paragraph below to put into context....*
 
-In the words of Gene Glass, arguably the father of meta-analysis: "Of course it mixes apples and oranges; in the study of fruit nothing else is sensible; comparing apples and oranges is the only endeavor worthy of true scientists; comparing apples to apples is trivial" [p.g., 224, @Glass2015].
+In the words of Gene Glass, the father of meta-analysis: "Of course it mixes apples and oranges; in the study of fruit nothing else is sensible; comparing apples and oranges is the only endeavor worthy of true scientists; comparing apples to apples is trivial" [p.g., 224, @Glass2015].
 @Glass2015's intention was to simply highlight that whether comparing apples and oranges is a good idea simply boils down to the specific question of interest.
-If we are interested in gaining insight into 'fruit' then synthesising apples and oranges is a good idea.
-Instead, if we are intersted in generalising to apples only, then mixing fruit will not be ideal.
-We tend to agree with @Glass2015 and his sentiment is of particular relevance to comparative physiology.
-By synthesizing diverse study outcomes, it allows us to not just report on overall effects, but understand critical features of the literature, study systems and approaches that can explain the diversity of effect outcomes observed.
+If we are interested in gaining insight into 'fruit' then synthesising apples and oranges is the only thing that makes sense.
+Instead, if we are interested in generalising only to apples then mixing fruit will not be ideal.
+We tend to agree with @Glass2015, and his sentiment is of particular relevance to comparative physiology.
+For example, if we want to understand the impact of a pollutant on reproduction in aquatic organisms then including aquatic mammals and fish would provide answers to this general question, even if their reproductive biology and physiology are known to differ.
+By synthesizing diverse study outcomes, it allows us to not just report on overall effects (if the question is relevant to ask), but understand critical features of the literature, study systems (e.g., different effects of pollutants on fish and mammal reproduction) and approaches that can explain the diversity of effect outcomes observed.
 In doing so, it provides a richer set of conclusions that can draw attention to important sources of variability that might have otherwise been overlooked.
-Having said that, it is still very important to understand the limitations and diversity of studies included within a meta-analysis.
-Answers to certain questions will inevitably depend on the homogeneity of effects being synthesized.
+Having said that, it is still very important to understand the limitations and diversity of studies included within a meta-analysis - an important reason why transparency and reproducibility are such a prominant feature of meta-analysis (or ideally should be) [@ODea2021].
+The validity of general conclusions to certain questions (e.g., what is the overall effect of a polluntant on reproduction?) will inevitably depend on the homogeneity of effects being synthesized.
+For example, given the very different physiology of aquatic mammals and fish, understanding an overall combined effect on reproduction may not be particularly relevant, and indeed may be misleading.
+It is important to consider these questions when conducting meta-analyses.
+
+Of course, there are certain types of heterogenity that transcend different questions.
+In other words, if we compare different types of 'apples' is it still fair to synthesize these studies to understand overall effects?
+This situation might be analogous to a meta-analysis in comparative physiology that attemps to understand the effects of temperature on fish growth.
+Studies might rear populations of fish under different temperatures, but in the end, they are still all fish, governed by the same thermodynamic effects on growth.
+In this situation, we might still be interested in understanding overall effects, but we may question whether such a conclusion is sensible given the diversity of temperatures applied.
+However, such a study does not preclude us from also exploring important moderators or predictors of variability in effects across studies.
 

### 2021-06-14 MS/ms.Rmd
Fixes to paragraph

@@
 
-## **The Apples and Oranges 'Problem': How lack of comparability can make effects vary widely across studies**
+## **The Apples and Oranges 'Problem' in Comparative Physiology**
  I'm thinking now, in re-reading this, that we could use a slightly expanded version of paragraph 4 taht describes this problem in a little more detail.
@@
 In the words of Gene Glass, the father of meta-analysis: "Of course it mixes apples and oranges; in the study of fruit nothing else is sensible; comparing apples and oranges is the only endeavor worthy of true scientists; comparing apples to apples is trivial" [p.g., 224, @Glass2015].
-@Glass2015's intention was to simply highlight that whether comparing apples and oranges is a good idea simply boils down to the specific question of interest.
+@Glass2015's intention was to simply highlight that whether comparing apples and oranges is a good idea simply boils down to the specific question of interest and the population one wishes to make conclusions about.
 If we are interested in gaining insight into 'fruit' then synthesising apples and oranges is the only thing that makes sense.

### 2021-06-27 R/survey_explore.R
Some code

@@ -8,3 +8,15 @@
 	data <- read.csv("./data/MA_CompPysio_Survey.csv")
 # Have a look
 	data %>% glimpse()
+
+# Lets just subset to the main questions for simplicity
+
+	data2 <- data %>% select(!grep("Comment", colnames(data)))
+
+# Just some simple plots. Ok, needs some cleaning looking at this. Studies often used multiple effects
+
+	ggplot(data2, aes(x = Q2.1_EffectUsed)) + 
+		geom_histogram(stat = "count") +
+		theme(axis.text = element_text(size =6))
+
+

### 2021-06-29 MS/ms.Rmd
Last updates for day on new section
some comments and minor edits

@@
 
-Daniel W.A. Noble$^{1,*}$, Patrice Potter$^{2}$, Sammy Burke$^{2}$, Szymek Drobniak$^{2}$, Malgorzata Lagisz$^{2}$, Rose O’Dea$^{2}$, Shinichi Nakagawa$^{2}$
+Daniel W.A. Noble$^{1,*}$, Patrice Potter$^{2}$, Sammy Burke$^{2}$, Szymek Drobniak$^{2}$, Malgorzata Lagisz$^{2}$, Rose O'Dea$^{2}$, Shinichi Nakagawa$^{2}$
 
@@
 Meta-analysis is a tool that provides comparative physiologists with powerful, unbiased and quantitatively informed answers to topical research questions by synthesising effect sizes across disparate studies.
-Distilling published research results into standardised effect sizes that can be weighted (i.e., by their inverse sampling variance) in a meta-analysis, and compared across broad sets of research designs, study systems and species is its core objective and strength.
+Meta-analysis's core objective and strength is to distill published research results into standardised effect sizes that can be weighted (i.e., by their inverse sampling variance), and which can be compared across broad sets of research designs, study systems and species.
 Estimating overall effect sizes, and understanding what drives effect variability, provides opportunities to model how organisms will respond to pressing global challenges.
 Despite this ambition, research designs in comparative physiology can appear, at the outset, as being vastly different to each other (e.g., using different temperatures or treatment dosages).
-Differences in treatments across studies has led many to believe that meta-analysis is an exercise in comparing “apples with oranges”.
-Here, we dispel this myth by showing how standardised effects sizes can be used in conjunction with powerful multi-level meta-analytic models to both account for factors driving differences across studies and make them more comparable.
+Differences in treatments across studies has led many to believe that meta-analysis is an exercise in comparing "apples with oranges".
+Here, we dispel this myth by showing how standardised effects sizes can be used in conjunction with powerful multi-level meta-regression models to both account for factors driving differences across studies and make them more comparable.
 In addition, we derive new effect size measures that provide comparative physiologists with a means to directly make effect measures comparable without the need to resort to more complex statistical models that may be harder to interpret.
-Our ‘new’ effect sizes and corresponding sampling variances help physiologists deal with common treatment differeces across studies; allowing researchers to compare both mean differences and associated differences in variance for physiological traits.
+Our 'new' effect sizes and corresponding sampling variances help physiologists deal with common treatment differeces across studies; allowing researchers to compare both mean differences and associated differences in variance for physiological traits.
 The new effect sizes we propose, in combination with existing meta-analytic models, will pave the way for comparative physiologists to explore exciting new questions by making results from large-scale data sets collected from the literature more accessible and widely interpretable.
 
+<!--- Dan - new effect sizes here is a big vague.
+Don't we just say - we formalize Q10 for by deriving the sampling error variance (the inverse of weight) of its natural logarithm Further, we propose two additional related effect sizes, which use Q10's standard deviation and coefficence of variation (CV).
+Also, this is an examplar of what eco-phsiologists are familiar with can be used as a standaridsed effect size and they can draw on the tools developed for meta-analysis --->
+
+<!--- xxxx --->
+
 ## **Introduction**
-Meta-analysis provides quantitatively informed answers to research questions by using a transparent and reproducible search strategy to synthesise research results across studies and identify sources of variation [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Arnqvist1995; @Koricheva2013].
-Meta-analysing independent studies provides greater statistical power and precision than what any individual study on its own would be able to provide on a question - particularly given that most empirical studies are already under-powered in many areas of biology [@Forstmeier2017; @Jennions2003; @Button2013].
+
+A meta-analysis, being part of systematic review, provides quantitatively informed answers to research questions by using a transparent and reproducible search strategy to synthesise research results across studies and identify sources of variation [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Arnqvist1995; @Koricheva2013].
+<!--- note meta-analysis itself is not really about transparency etc - it is a stasitical tool - these other bits come in as a part of systeamtic review ---> Meta-analysing independent studies provides greater statistical power and precision than what any individual study on its own would be able to provide on a question - particularly given that most empirical studies are already under-powered in many areas of biology [@Forstmeier2017; @Jennions2003; @Button2013].
 By expressing study effects on a common scale (i.e., standardised effect size) a meta-analyst can gain broader insight into the direction and efficacy of a particular treatment effect or the strength of a relationship between two variables of interest [@Gurevitch2018; @Koricheva2013].
-Quntitative syntheses, including meta-analyses, have provided comparative physiologists with powerful insights on pressing global challenges - from testing whether physiological plasticity can buffer orgamisms against climate change [e.g, @Seebacher2015] to the degree to which endocrine disrupting chemicals, such as bisphenol A (BPA), impact aquatic organisms [e.g., @WuSeebacher2020].
+Quantitative syntheses, including meta-analyses, have provided comparative physiologists with powerful insights on pressing global challenges - from testing whether physiological plasticity can buffer organisms against climate change [e.g, @Seebacher2015] to the degree to which endocrine disrupting chemicals, such as bisphenol A (BPA), impact aquatic organisms [e.g., @WuSeebacher2020].
 
-Meta-analysis is a well-developed research field with a long history in statistics, medicine, psychology and ecology [@Gurevitch2018; @Nakagawa2017; @Glass2015].
-It has emerged as the 'gold-standard' across various disciplines for quantitative synthesis and is becoming increasingly more prominant the field of comparative physiology.
-Formal meta-analyses involve a systematic literature-based search, extraction of data from studies meeting specific inclusion criteria, and the subsequent calculation of effects sizes from summary statistics provided by papers.
-The entire process should follow and report upon this entire process carefully to ensure the meta-analysis is as transparent and reproducible as possible [i.e., see the Preferred Reporting Items for Systematic Reviews and Meta-Analyses in Ecology and Evolution (PRISMAEcoEvo) protocol, @ODea2021].
+Meta-analysis is a well-developed research topic with a long history in statistics, medicine, psychology and ecology [@Gurevitch2018; @Nakagawa2017; @Glass2015].
+It has emerged as the 'gold-standard' across various disciplines for quantitative synthesis and is becoming increasingly more prominent in the field of comparative physiology.
+Formal meta-analyses, as a part of a systematic review, involve a systematic literature-based search, extraction of data from studies meeting specific inclusion criteria, and the subsequent calculation of effects sizes from summary statistics provided by papers.
+The entire process should follow and report upon this entire process carefully to ensure the meta-analysis within a systematic review, is as transparent and reproducible as possible [i.e., see the Preferred Reporting Items for Systematic Reviews and Meta-Analyses in Ecology and Evolution (PRISMA-EcoEvo) protocol, @ODea2021].
 Aside from providing an up-to-date overview of the research question, along with identifying any gaps and biases, there are two major goals of meta-analysis: 1) to provide an overall mean estimate of a treatment effect or relationship and 2) to quantify effect size variance and understand key drivers explaining differences in effects across studies [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Koricheva2013].
 A critically important feature of meta-analaysis is its ability to account for sampling error [@Koricheva2013].
-The inverse sampling error is used to weight higher powered studies in the analysis and make overall estimates more precise.
-While many meta-analyses might employ unweighted analyses, these studies will not gain greater precision on estimates because sampling variance cannot be formally accounted for in the analysis, even if the overall mean itself is unbiased.
+The inverse of sampling error variance is used to weight studies, accordingly, in the analysis and make overall estimates more precise.
+While many meta-analyses might employ unweighted analyses, these studies will not gain greater precision on estimates because sampling variance cannot be formally accounted for in the analysis, even if the overall mean itself may be unbiased.
+<!--- cite Morrissey here - also, the overall mean is unbiased given there is no publication bias or small study effects - this is important as many meta-analyses are likley to suffer from small study effects; my pick sann does not seem like you have talked about publcaiton bias too much - an ablity of meta-analysis to detect publicaiton bias is one of its strength - or probalby the major strength...
+--->
 
-Despite the widespread adoption and well established methodological procedures of meta-analysis it is often criticised for mixing 'apples and oranges' - in otherwords, mixing effects from studies that lack comparability [@Gurevitch2018; @Arnqvist1995; @Gallo1979; @Carpenter2020; @Stewart2010; @Glass2015].
+Despite the widespread adoption and well established methodological procedures of meta-analysis, it is often criticised for mixing 'apples and oranges' -- in other words, mixing effects from studies that lack comparability [@Gurevitch2018; @Arnqvist1995; @Gallo1979; @Carpenter2020; @Stewart2010; @Glass2015].
 Lack of comparability could result from studies differing in experimental design, species, measurement variables and sampling units, which can impact the generalisability of meta-analytic results [@Arnqvist1995; @Stewart2010].
-Indeed, study specific differences in comparative physiology are widspread.
+Indeed, study specific differences in comparative physiology are widespread.
 For example, experimental designs can vary in the temperatures that they apply or in the dosages of chemical modifiers used in experimental treatments [e.g., @WuSeebacher2020].
 In addition, they often include a diversity of study species which can vary in responses.
-To the uninitiated the concern might not be unfounded given that meta-analyses in ecology and evolution often mix highly heterogenous effect size estimates often resulting in high variability [@Senior2016].
+To the uninitiated, the concern might not be unfounded given that meta-analyses in ecology and evolution often mix highly heterogeneous effect size estimates, resulting in high variability [@Senior2016].
+<!--- this last sentence does not seem to fit well or not completely logical - did you want to say -heterogeniety is normal.
+Actually Jessica always say in ecology meta-analysis is probalby not that useful; meta-regression is what we are most interested - I think yo cna make a similar point or you are already making one but make it clearer  - the first sentence is a good one but rather than focusing on "contolling" for hetero but finding out what causes hetero should our (comparative phsiologists') main aim for meta-analysis.
+I know you are probably intending to say something like this but not coming through at the moment.
+Also, I note that "review generated evidence" only comes from meta-regression not meta-analysis = intercept models - as study general evidnece can be equivalent to meta-analytic results --->
 
@@
 We first conduct a survey of published meta-analyses in the field of comparative physiology to gauge methodological and meta-analytic approaches - assessing what types of effect sizes are commonly used, how often effect size estimates are impacted by continuous treatment differences and whether meta-analytic models (i.e., models that account for sampling variance) are commonly applied.
-We then introduce new effect sizes and their assocaited sampling variance to provide comparative physiologists opportunities to explictly incorperate treatment differences into the effect size estimates to ease their interpretation.
-We then describe how more complex treatment differences, such as dosage differences, which may have non-linear effects, can be accomodated using multilevel meta-regression models.
-We hope to show how expanding the meta-analtic toolkit for comparative physiologists will provide new opportunities to address global scale problems that attempt to understand how organisms will cope with rapidly changing environments in the future.
+We then introduce new effect sizes and their associated sampling variance to provide comparative physiologists opportunities to explicitly incorporate treatment differences into the effect size estimates to ease their interpretation.
+<!--- see my comments above - they are not really new effec sizes - just formalising we can chat about this lnRR, lnVR and lnCVR and Q10 all exisit already ---> We then describe how more complex treatment differences, such as dosage differences, which may have non-linear effects, can be accommodated using multilevel meta-regression models.
+We hope to show how expanding the meta-analytic toolkit for comparative physiologists will provide new opportunities to address global scale problems that attempt to understand how organisms will cope with rapidly changing environments in the future.
 
 ## **The Apples and Oranges 'Problem' in Comparative Physiology**
- I'm thinking now, in re-reading this, that we could use a slightly expanded version of paragraph 4 taht describes this problem in a little more detail.
+
+<!---  Dan syas: I'm thinking now, in re-reading this, that we could use a slightly expanded version of paragraph 4 taht describes this problem in a little more detail.
 This is likely the place for a figure, which I am having some trouble envisaging where one is best placed.
@@
 Talked about a lot.
-Integrate blurb below...try to take a balanced approach.
-*I will add an introduction bit to this paragraph below to put into context....*
+Integrate blurb below…try to take a balanced approach.
+I will add an introduction bit to this paragraph below to put into context….
+xxxx --->
 
@@
 If we are interested in gaining insight into 'fruit' then synthesising apples and oranges is the only thing that makes sense.
-Instead, if we are interested in generalising only to apples then mixing fruit will not be ideal.
+<!---  as said, comparative analysis by definition, compares applies and oranges - = different species - I guess you are mainly talking about mixing different methods ones - this is where I said earlier - focusing on explaining hetero comes in.
+Also, mixing different quality of studies are often referred to as "Garbage in and garbage out" ---> Instead, if we are interested in generalising only to apples then mixing fruit will not be ideal.
 We tend to agree with @Glass2015, and his sentiment is of particular relevance to comparative physiology.
@@
 In doing so, it provides a richer set of conclusions that can draw attention to important sources of variability that might have otherwise been overlooked.
-Having said that, it is still very important to understand the limitations and diversity of studies included within a meta-analysis - an important reason why transparency and reproducibility are such a prominant feature of meta-analysis (or ideally should be) [@ODea2021].
+Having said that, it is still very important to understand the limitations and diversity of studies included within a meta-analysis - an important reason why transparency and reproducibility are such a prominent feature of meta-analysis (or ideally should be) [@ODea2021].
 The validity of general conclusions to certain questions (e.g., what is the overall effect of a polluntant on reproduction?) will inevitably depend on the homogeneity of effects being synthesized.
-For example, given the very different physiology of aquatic mammals and fish, understanding an overall combined effect on reproduction may not be particularly relevant, and indeed may be misleading.
+<!--- this is know as putting one number on so many different kinds of studies - but of course, this may not be that interesting apart from a starting point for subsequent meta-regressoin analyses ---> For example, given the very different physiology of aquatic mammals and fish, understanding an overall combined effect on reproduction may not be particularly relevant, and indeed may be misleading.
 It is important to consider these questions when conducting meta-analyses.
 
-Of course, there are certain types of heterogenity that transcend different questions.
+Of course, there are certain types of heterogeneity that transcend different questions.
 In other words, if we compare different types of 'apples' is it still fair to synthesize these studies to understand overall effects?
-This situation might be analogous to a meta-analysis in comparative physiology that attemps to understand the effects of temperature on fish growth.
-Studies might rear populations of fish under different temperatures, but in the end, they are still all fish, governed by the same thermodynamic effects on growth.
+This situation might be analogous to a meta-analysis in comparative physiology that attempts to understand the effects of temperature on fish growth.
+<!--- taxnomically speaking - comparing different applies are comparing different populations of the same spieces of fish so not quite sure whether this is quite correct - I am being of course a bit pedentic---> Studies might rear populations of fish under different temperatures, but in the end, they are still all fish, governed by the same thermodynamic effects on growth.
 In this situation, we might still be interested in understanding overall effects, but we may question whether such a conclusion is sensible given the diversity of temperatures applied.
-However, such a study does not preclude us from also exploring important moderators or predictors of variability in effects across studies.
+Such a study does not preclude us from also exploring important moderators or predictors of variability in effects across studies.....
 
 ## **Survey of Meta-Analytic Practices in Comparative Physiology**
+
 As discussed above, it is clear that different types of questions and experimental approaches will be more or less susceptable to the 'apples and oranges' problem.
-As such, before embarking on our path to 'meta-analytic enlightenment', we conducted a literatrure survey to understand how widespread the problem may be in comparative physiology and gauge the ways in which it is currently being addressed, if at all.
+<!--- not sure whehter it is a good idea to hightlight it as a problem as said earlier - explaining hetero is what's interesting and even the main porupose of meta-analysis for comparative physiologiests - they are not the problem but they are what we are going to invesitgate.
+I do not think 'suspetible' is a good word here given the average hetero = > 90% - you are nearly 100% guranteed to have hetero and this is what's interesting ---> As such, before embarking on our path to 'meta-analytic enlightenment', we conducted a literatrure survey to understand how widespread the problem may be in comparative physiology and gauge the ways in which it is currently being addressed, if at all.
 To accomplish this goal, we searched for meta-analyses and comparative analyses that tackled questions using physiological data compiled from animal studies across multiple species.
@@
 #### *Literature Search and Survey Data Collection*
+
 All searches were conducted in Scopus between May 16 - 18, 2021.
@@
 Studies on behavior were only included if the synthesis was explicitly interested in the proximate physiological drivers of behavioral variation.
-We also included meta-analyses that quantifed plasticity in physiological traits across taxa for the purpose of understanding adaptive plasticity in response to environmental variation.
+We also included meta-analyses that quantified plasticity in physiological traits across taxa for the purpose of understanding adaptive plasticity in response to environmental variation.
 While many studies in comparative physiology collect data as part of a comparative analysis, we focus here only on studies collating data from existing literature because this is the major data source for quantitative synthesis.
@@
 All title, abstract and full text screening was done by two people (DWAN and ML).
-Any conflicts or disagreements were resolved by discussion and a concensus on a paper was reached.
+Any conflicts or disagreements were resolved by discussion and a consensus on a paper was reached.
 Out of the 417 papers, 79 full texts were screened and we included a total of 62 for final data extraction.
@@
 ## **Opening Up New Opportunities in Comparative Physiology: Expanding the Breadth of Effect Sizes to Deal with Treatment Differences Across Studies**
+
 #### *Brief Introduction to Common Effect Sizes and Sampling Errors that are Useful in Comparative Physiology*
@@
 The key features of all effect sizes used in meta-analyses are that they are: 1) statistical parameters that have been placed on a common scale so that they can be compared across studies and 2) that they have some associated measure of precision (i.e., sampling variance)[@Koricheva2013; @Borenstein2009; @Schmid2021].
-Effect sizes in comparative physiology are quite variable; they can be the mean difference between two groups (e.g., difference in mean between a control and treatment group - see @WuSeebacher2020), the slope of a regression (e.g., between body size and metabolic rate), a correlation between two variables, or even the raw mean (or variance) itself (e.g., comparing CTmax across species - see @Sunday2014).
+Effect sizes in comparative physiology are quite variable; they can be the mean difference between two groups (e.g., difference in mean between a control and treatment group - see @WuSeebacher2020), the slope of a regression (e.g., between body size and metabolic rate), a correlation between two variables, or even the raw mean (or variance) itself (e.g., comparing CTmax or CTmin across species - see @Sunday2014).
 In many cases, multiple types of effect sizes might be used depending on the question.
@@
 The choice as to which one to use will boil down to the types of data available from primary studies, the specific question of interest and whether studies are observational or experimental in nature.
-Considering our temperature example above, if we are interested in the magnitude of change between temperature treatments, we may want to use a contrast-based effect size, such as the log response ratio $ln_{RR}$.
+Considering our temperature example above, if we are interested in the magnitude of change between temperature treatments, we may want to use a contrast-based effect size, such as the log response ratio $\ln{RR}$.
 If we are instead interested in how the mean of some physiological trait changes with tempearture we may instead model the mean itself.
@@
 names <- c("Mean",
-           "Variance",
-           "Log Response Ratio",
-           "Standardised Mean Difference",
-           "Zr (Correlation Coefficient)")
+           "Log Standard deviation. lnSD",
+           "Log Response Ratio, lnRR",
+           # leave this for now??? - we introduce this later
+           "Standardised Mean Difference, SMD",
+           "Zr (Fisher Trasnformaiton of \n correlation Coefficient, r)")
            #"Log Odds Ratio",
@@
 
-eqns_yi <- c("X_{i}",
-             "\\sigma^2",
-             "log \\left( \\frac{X_{1}}{X_{2}}\\right)",
-             "\\frac{\\left( X_{2} - X_{1}\\right)}{sd_{p}}J",
+# the index i is not really applied consistently so I am adding it more (to do)
+# we shoudl discuss what kinds of notations we want to use consistely
+
+eqns_yi <- c("M_i",
+             "\\ln{SD_i} + \\frac{1}{2(N_i - 1)}",
+             # Senior will have a better version but this is good for now
+             "\\ln \\left( \\frac{M_{i1}}{M_{i2}}\\right)",
+             "\\frac{\\left( X_{i2} - X_{i1}\\right)}{SD_{p}}J",
+             # we need to spell out SD_p somewhere
              "\\frac{1}{2}log\\left(\\frac{1+r_{i}}{1-r_{i}}\\right)")
@@
 # Just placeholders for now
-eqns_vi <- c("\\frac{s_{i}^2}{n_{i}}",
-             "\\frac{s_{i}^2}{n_{i}}",
-             "\\frac{s_{i}^2}{n_{i}}",
-             "\\frac{s_{i}^2}{n_{i}}",
-             "\\frac{s_{i}^2}{n_{i}}")
+eqns_vi <- c("\\frac{SD_{i}^2}{N_{i}}",
+             "\\frac{1}{2(N_i - 1)}",
+             "\\frac{N_{1i} + N_{2i}}{N_{1i}N_{2i}} + \\frac{SMD^2}{2(N_{1i} + N_{2i})}",
+             "\\frac{SD_{1i}} {M^2_{1i}N_{1i}} + \\frac{SD_{2i}} {M^2_{2i}N_{2i}}",
+             # see my commenst
+             "\\frac{1}{N_i - 3}")
              #"\\frac{s_{i}^2}{n_{i}}",
@@
 As such, it is often of interest to standardsise effects by temperature.
-One common effect size measure already used in comparative physiology to compare physiological rates is $Q_{10}$ [e.g., @Rodgers2021; @Seebacher2015; @Havird2020], which describes the multiplicative change in physiological rates across a 10&deg;C temperature change.
+One common effect size measure already used in comparative physiology to compare physiological rates is $Q_{10}$ [e.g., @Rodgers2021; @Seebacher2015; @Havird2020], which describes the multiplicative change in physiological rates across a 10°C temperature change.
 Higher $Q_{10}$ values indicate larger changes in physiological rates.
 Currently, however, we do not have associated sampling variances derived for $Q_{10}$ making it challenging to make use of the full power of weighted meta-analytic models.
-Interstingly, $Q_{10}$ is quite similar to *lnRR*, meaning that we can derive a $Q_{10}$ based effect size and sampling error using the well known mathematical properties of *lnRR*.
-This opens up the meta-analtic toolbox and improves upon our ability to account for well known sources of non-independence that are typical in meta-analysis [@Lajeunesse2011; @Noble2017].
+Interestingly, $Q_{10}$ can be seen as a variant of *lnRR*, meaning that we can derive a $Q_{10}$ based effect size and sampling error using the well known mathematical properties of *lnRR*.
+This opens up the meta-analytic toolbox and improves upon our ability to account for well known sources of non-independence that are typical in meta-analysis [@Lajeunesse2011; @Noble2017].
 
@@
 Prior to showing how the relevant $Q_{10}$ effect size can be calculated it can be helpful to understand its similarities to *lnRR*.
-The *lnRR* described by @Hedges1999 and extended by  @Lajeunesse2011 and can be calculated as follows:
+The *lnRR* described by @Hedges1999 and extended by @Lajeunesse2011 and can be calculated as follows <!---put see also Senior et al.
+2020 RSM as well - there we expand the 2nd order delta method stuff - so unbiased formlas for all lnRR, lnVR etc is a bit different - we do not want to put it here but mention by the way - Lajeuness 2011 is not the one I would cite Lajeuness 2015 is more relevant ---> :
 
@@
 \end{equation} 
-$$
-In equation \@ref(eq:lnRR), $X_{1}$ is the mean of group 1, often a control group, where as $X_{2}$ is the mean of group 2 (e.g., a treatment group).
+$$ In equation \@ref(eq:lnRR), $X_{1}$ is the mean of group 1, often a control group, where as $X_{2}$ is the mean of group 2 (e.g., a treatment group).
 The mean of $X_{i}$ for group *i* can be any measurement type (e.g.
@@
 Log transformation of this ratio makes the effect size normally distributed.
-Equation \@ref(eq:slnRR) is the analytical solution for *lnRR*'s sampling variance where, $SD_{1}^2$ and $SD_{2}^2$ is the variance in group 1 and 2, respectively and $N_{1}$ and $N_{2}$ is the sample size in group 1 and 2.
+<!--- use consistent notations in relation to the table - do you want to put i or not - then you need to put i throughout ---> Equation \@ref(eq:slnRR) is the analytical solution for *lnRR*'s sampling variance where, $SD_{1}^2$ and $SD_{2}^2$ is the sample variance in group 1 and 2, respectively and $N_{1}$ and $N_{2}$ is the sample size in group 1 and 2.
 
@@
 \end{equation} 
-$$
-Here, $R_{1}$ and  $R_{2}$ are mean physiological rates and  $T_{1}$ and  $T_{2}$ are the temperatures that these rates are measured.
+$$ Here, $R_{1}$ and $R_{2}$ are mean physiological rates and $T_{1}$ and $T_{2}$ are the temperatures that these rates are measured.
 Log transformation of equation \@ref(eq:q10) leads to the following log transformed $Q_{10}$:
@@
 \end{equation} 
-$$
-Equation \@ref(eq:lnq10) is essentially a temperature corrected equivalent to lnRR when the numerator and denomenator are measured at different temperatures.
+$$ Equation \@ref(eq:lnq10) is essentially a temperature corrected equivalent to lnRR when the numerator and denomenator are measured at different temperatures.
 This allows one to compare the mean of two temperature treatments directly regardless of the temperatures that these groups have been measured.
 Here, we will refer to this as the log $Q_{10}$ response ratio, $lnRR_{Q_{10}}$.
-Recognition of this equivalence means that we can easily calculate the sampling variance for equation \@ref(eq:lnq10) as follows:
+Notably, by taking the natural logarithm, there are two statistical advantages: 1) 0 becomes biological meaningful as 0 means two rates are the exactly the same and 'statistically significantly different from 0' means that two rates are significantly different to each other and 2) $lnRR_{Q_{10}}$ is more likely to satisfy the assumption of residual normality than $Q_{10}$ (see @Hedges1999).
+Also, the recognition of this equivalence means that we can easily calculate the sampling variance for equation \@ref(eq:lnq10) as follows:
 
@@
 \end{equation} 
-$$
-$$
+$$ $$
 \begin{equation} 
@@
 
-Equations \@ref(eq:lnq10VR) and \@ref(eq:slnq10VR) describe the change in physiological rate variance (eqn \@ref(eq:lnq10VR)) across a 10&deg;C temperature change along with its sampling variance (eqn \@ref(eq:slnq10VR)).
+Equations \@ref(eq:lnq10VR) and \@ref(eq:slnq10VR) describe the change in physiological rate variance (eqn \@ref(eq:lnq10VR)) across a 10°C temperature change along with its sampling variance (eqn \@ref(eq:slnq10VR)).
 While this is a useful metric, as discussed by @Nakagawa2015 there is often a strong mean-variance relationship that needs to be accounted for in analysing changes in variance.
@@
 where $CV$ is the coefficient of variation defined as $SD / R$.
+Whether one choose to use SD or CV-based effect size depends on questions at hand (discussed in @Nakagawa2015 and Senior et al.
+2020 <!--- sorry I have not added it to bib file - I will do this later once I go through --->)
 
-## **Meta-Analytic Models to Control for Heterogeous Effects Within and Across Studies**
+## **Meta-Analytic Models to Control for and Investigate into Heterogeneous Effects Within and Across Studies**
 
-It will not be possible to derive an effect size that completely controls for known heterogenity at the effect size level all the time.
-This may be because treatment effects are not be simple linear or exponential functions of the mean response making the effect sizes we discuss above unsuitable [e.g., thermal performance curves; @Noble2018].
-For example, dosages applied to treatments can follow quite complex non-linear relationships, with expoential or quadratic relationships in relation to some mean response.
-When this occurs we recommend comparative physiologists apply meta-regerssion approaches, controlling for these known treatment differences as a moderator.
+<!--- As said before you want to play up the aspect of investigaing heterogeneity rather than controlling for it - controlling for it seems to mean you still want to know the overall effect after getting rid of every confunders.
+Whilst it is also waht we want, we really want to explain the hetero --->
+
+It will not be possible to derive an effect size that completely controls for known heterogeneity at the effect size level all the time.
+This limitation is partly because treatment effects are not be simple linear or exponential functions of the mean response making the effect sizes we discuss above unsuitable [e.g., thermal performance curves; @Noble2018].
+For example, dosages applied to treatments can follow quite complex non-linear relationships, with exponential or quadratic relationships in relation to some mean response.
+When this occurs we recommend comparative physiologists apply meta-regression approaches, controlling for these known treatment differences as a moderator.
 There are simple statisical approaches a meta-analyst can use to then make the overall effects interpretable [@Schielzeth2010].
-Before diving into meta-regression models, we will first overview the meta-analytical approaches or steps commonly used.
+Before diving into meta-regression models, we will first overview the meta-analytic approaches or steps commonly used.
 
 #### *Multi-level Meta-Analysis when the Overall Effect is of Interest*
+
 One of the main goals of meta-analysis is to obtain an overall meta-analytic mean effect size estimate and some form of uncertainty around that mean, like a 95% confidence interval (CI).
@@
 Estimating an overall mean along with 95% CI (or PI) is generally done with a simple random effects or multilevel meta-analytic model that accounts for effect size sampling error [@Nakagawa2017; @NakagawaSantos2012].
-More often than not, meta-analyses in comparative physiology will have complex hierachical structure.
+More often than not, meta-analyses in comparative physiology will have complex hierarchical structure.
 For example, multiple effect sizes may be taken from a single study on different traits measured on the same individuals, or come from many different species that share an evolutionary history [@Noble2017].
@@
 If the studies are experimental in nature, than a standardised effect size, such as $ln_{RR}$ or Hedges' *d* might be applicable.
-We then might fit an overall, multilevel meta-analytic model as follows:
-$$
+We then might fit an overall, multilevel meta-analytic model as follows: $$
 \begin{equation} 
@@
 
+<!--- you can use ni instead of spi???
+- also refer to this paper in this seciton which really justify or even nessates people using this rather complext model and having a and sp are rather crtical!
+- https://ecoevorxiv.org/su4zv/--->
+
 where $Y_{i}$ is the *i*th effect size (*i* = 1 ...
-$N_{ES}$, the number of effect sizes), $\beta_{0}$ is the overall meta-analytic mean, $a_{k[i]}$ is the phylogenetic effect for species *k* applied to effect size *i*.
+$N_{ES}$, the number of effect sizes), $\beta_{0}$ is the overall meta-analytic mean, $a_{k[i]}$ is the phylogenetic effect (a random effect) for species *k* applied to effect size *i*.
 Phylogenetic effects are assumed to be normally distributed deviates sampled from a distribution with a mean of 0 and variance $\sigma^{2}_aA$ [i.e., *N*$(0, \sigma^{2}_aA)$], where A is a phylogenetic correlation matrix derived from a phylogenetic tree, $sp_{k[i]}$ is the species-specific effect for the *k*th species applied to effect size *i*, $s_{j[i]}$ is the study-specific effect for the *j*th study applied to effect size *i*, $e_{i}$ is the effect size-specific effect (or within study effect, or residuals) for the *i*th effect size, and $m_{i}$ is the sampling variance effect around the *i*th effect as a result of variation in precision among each effect sizes, $v_{i}$, which is known.
 This model is a 'weighted' multilevel meta-analysis model because the estimation of *u* is weighted by the inverse sampling variance of each effect size.
-The fact that we can obtain an overall estimate of sampling variance (i.e., $\sigma^2_{m}$) is very important because it provides a way for us to understand just how much variation in effects are the result of sampling differences across studies versus other, potentially improtant sources of variation such as differences in the methods applied, species differences or even real biological effects that impact the effect size a study is likely to observe [@Nakagawa2017; @NakagawaSantos2012].
-This is formalised in what we call 'heterogenetiy analysis' which we describe below.
-Importantly, this model provides us with the answer to our overall question: Across all the species and studies manipulating egg corticosterone, how much of an overall effect does corticostrone have on reproduction relative to control conditions?
+The fact that we can obtain an overall estimate of sampling variance (i.e., $\sigma^2_{m}$) is very important because it provides a way for us to understand just how much variation in effects are the result of sampling differences across studies versus other, potentially important sources of variation such as differences in the methods applied, species differences or even real biological effects that impact the effect size a study is likely to observe [@Nakagawa2017; @NakagawaSantos2012].
+This is formalised in what we call 'heterogeneity analysis' which we describe below.
+Importantly, this model provides us with the answer to our overall question: Across all the species and studies manipulating egg corticosterone, how much of an overall effect does corticosterone have on reproduction relative to control conditions?
+<!--- don't we need to mention in the case of VCV for mi--->
 
@@
 
-#### *Multilevel Metaregression to Understand Variation and Improve Interpretation*
+#### *Multilevel Meta-regression to Understand Variation and Improve Interpretation*
 
-Heterogenity among effects that result from known differences in how treatments are applied can also be dealt with using multilevel meta-regression models.
+Heterogeneity among effects that result from known differences in how treatments are applied can also be dealt with using multilevel meta-regression models.
 Multilevel meta-regression models include all the same random effects that we have already discussed, but they also include fixed effects (i.e., predictors or moderators) that attempt to explain changes in the mean effect size.
@@
 
-$$ Y_{i} = \beta_{0} + \sum \beta_{j}x_{j} + a_{k[i]} + sp_{k[i]} + s_{j[i]} + e_{i} + m_{i} $$
-where $\sum \beta_{j}x_{j}$ is simply the sum of all slope effects for all moderators, $x_{j}$.
+$$ Y_{i} = \beta_{0} + \sum \beta_{j}x_{j} + a_{k[i]} + sp_{k[i]} + s_{j[i]} + e_{i} + m_{i} $$ where $\sum \beta_{j}x_{j}$ is simply the sum of all effects for all moderators (fixed effects), $x_{j}$.
 All other notation is the same as described above.
 Importantly, the variable $x_{j}$ could be any moderator collected from studies, including dosage, temperature, salinity, or pH.
-Some moderators will be at the level of the study (e.g., was the study experimental or observational in nature) but others could be taken at the effect size level (i.e., was the effect derived using a tempearture of 23&deg;C or 35&deg;C).
+Some moderators will be at the level of the study (e.g., was the study experimental or observational in nature) but others could be taken at the effect size level (i.e., was the effect derived using a tempearture of 23°C or 35°C).
 By including these moderators in a meta-regression model, the interpretation of the overall meta-analytic mean, $\beta_{0}$, changes.
@@
 #### *Heterogenity Analysis: How Much Effect Size Variation Actually Exists?*
-Quantifying effect size heterogenity (i.e., effect size variance) provides a pathway to explore hypotheses thought to explain why effects might vary within and across studies.
-Effect size heterogeneity can be thought of as the percentage of variance between effect sizes that cannot be attributable to sampling error (often as called 'total' heterogenity) [@Higgins2002].
-More formally, we can quantify heterogenity using the multilevel meta-analytic model we describe above as:
 
-$$ I^2_{total} = \frac{\sigma^2_{total} - \sigma^2_{m}}{\sigma^2_{total}}, \
-\sigma^2_{total} = \sigma^2_{study} + \sigma^2_{phylogeny} + \sigma^2_{species} + \sigma^2_{residual} +\sigma^2_{m}
+Quantifying effect size heterogeneity (i.e., effect size variance) provides a pathway to explore hypotheses thought to explain why effects might vary within and across studies.
+Effect size heterogeneity can be thought of as the percentage of variance between effect sizes that cannot be attributable to sampling error (often as called 'total' heterogeneity) [@Higgins2002].
+More formally, we can quantify heterogeneity using the multilevel meta-analytic model we describe above as:
+
 $$ 
-where $\sigma^2_{total}$ is the  total effect size variance (using the above multilevel model) and $\sigma^2_{m}$ is the total sampling error variance.
-Quantifying heterogenity provides a formal way to assess how much variation is the result of 'true' biological or methodological differences as opposed to simply chance (i.e., sampling variance) [@NakagawaSantos2012; @Higgins2002].
+I^2_{total} = \frac{\sigma^2_{study} + \sigma^2_{phylogeny} + \sigma^2_{species} + \sigma^2_{residual}}{\sigma^2_{study} + \sigma^2_{phylogeny} + \sigma^2_{species} + \sigma^2_{residual} +\sigma^2_{m}}
+$$
+
+<!--- be consistent with sigma notations above - actuall total - m may sometimes not work - so best adding up all like this, which was the core finding in Nakagawa & Schielzeth's R2 --->
+
+where $\sigma^2_{total} = \sigma^2_{study} + \sigma^2_{phylogeny} + \sigma^2_{species} + \sigma^2_{residual} +\sigma^2_{m}$ is the total effect size variance (using the above multilevel model) and $\sigma^2_{m}$ is 'typical' the sampling error variance.
+<!--- you need more than that sigma_m is a typical one - you may need to provide a formula here --->.
+Quantifying heterogeneity provides a formal way to assess how much variation is the result of 'true' biological or methodological differences as opposed to simply chance (i.e., sampling variance) [@NakagawaSantos2012; @Higgins2002].
 We can only conduct such analyses if we have an estimate of the sampling variance for a given effect measure because only then can we quantify how much variation is the result of sampling variability.
-@Senior2016 have shown that total heterogenity is often extremely high in ecological and evolutionary meta-analysis (~91%), suggesting that effect measures vary widely across and within studies.
+@Senior2016 have shown that total heterogeneity is often extremely high in ecological and evolutionary meta-analysis (\~91%), suggesting that effect measures vary widely across and within studies.
 Some of the variation is clearly the result of working with different species or strains, different traits and different outcome measures, however, some of this variation also arises because of methodological differences across studies that might be related to the dosages or temperatures used for treatments.
-Formally quantifying and presenting heterogenity estimates from meta-analytic models can provide a way to undersand the major drivers of effect size variation by allowing researchers to produce various $I^2$ estimates which can be formally compared within and across studies.
+Formally quantifying and presenting heterogeneity estimates from meta-analytic models can provide a way to understand the major drivers of effect size variation by allowing researchers to produce various $I^2$ estimates which can be formally compared within and across studies.
 For example, we could fit the multilevel model described above to understand what proportion of variation is the result of, say, 'study' effects following @NakagawaSantos2012:
 
-$$ I^2_{study} = \frac{\sigma^2_{study}}{\sigma^2_{total}} $$
-where $\sigma^2_{study}$ is the study specific variance, and all other variance components are for phylogeny, species, residual (effect size level) and m (total measurement/sampling error).
+$$ I^2_{study} = \frac{\sigma^2_{study}}{\sigma^2_{total}} $$ where $\sigma^2_{study}$ is the study specific variance, and all other variance components are for phylogeny, species, residual (effect size level) and m (total measurement/sampling error).
 Many readers will notice the similarities between $I^2$ and $R^2$ [@Nakgawa2013; @Nakagawa2010].
@@
 
-$$ I^2_{hetero} = \frac{\sigma^2_{fixed}}{\sigma^2_{fixed} + \sigma^2_{total}} $$
+$$ R^2_{marginal} = \frac{\sigma^2_{fixed}}{\sigma^2_{fixed} + \sigma^2_{study} + \sigma^2_{phylogeny} + \sigma^2_{species} + \sigma^2_{residual}} $$
 
-The $I^2_{hetero}$ provides a formal means to assess just how much variation in effects is teh result of known heterogeneity at the effect size level, driven by continuous moderators such as dosage, temperature, salinity, and even pH.
-$I^2_{hetero}$ maybe a useful measure to provide to help readers understand just how much effec variation can result from the specific treatment application.
+Note that this formula does not include $\sigma^2_{m}$ as sampling error variance is assumed to be known in meta-analysis as explained above <!--- if you have not done so, please do --->.
+The $R^2_{marginal}$ provides a formal means to assess just how much variation in effects is teh result of known heterogeneity at the effect size level <!--- note what level's variation it accounts for depends on the type of a fixed effect or moderator --->, driven by continuous moderators such as dosage, temperature, salinity, and even pH.
+$I^2_{hetero}$ maybe a useful measure to provide to help readers understand just how much effect variation can result from the specific treatment application.
+<!--- you can also say metaAider and orcharRd packages have functions to cacualte this already via metafor - implemention is important --->
 

### 2021-06-29 MS/ms.Rmd
Just correcting spelling errors as I have a look at Shin's comments

@@
 Having said that, it is still very important to understand the limitations and diversity of studies included within a meta-analysis - an important reason why transparency and reproducibility are such a prominent feature of meta-analysis (or ideally should be) [@ODea2021].
-The validity of general conclusions to certain questions (e.g., what is the overall effect of a polluntant on reproduction?) will inevitably depend on the homogeneity of effects being synthesized.
+The validity of general conclusions to certain questions (e.g., what is the overall effect of a pollutant on reproduction?) will inevitably depend on the homogeneity of effects being synthesized.
 <!--- this is know as putting one number on so many different kinds of studies - but of course, this may not be that interesting apart from a starting point for subsequent meta-regressoin analyses ---> For example, given the very different physiology of aquatic mammals and fish, understanding an overall combined effect on reproduction may not be particularly relevant, and indeed may be misleading.
@@
 <!--- not sure whehter it is a good idea to hightlight it as a problem as said earlier - explaining hetero is what's interesting and even the main porupose of meta-analysis for comparative physiologiests - they are not the problem but they are what we are going to invesitgate.
-I do not think 'suspetible' is a good word here given the average hetero = > 90% - you are nearly 100% guranteed to have hetero and this is what's interesting ---> As such, before embarking on our path to 'meta-analytic enlightenment', we conducted a literatrure survey to understand how widespread the problem may be in comparative physiology and gauge the ways in which it is currently being addressed, if at all.
+I do not think 'suspetible' is a good word here given the average hetero = > 90% - you are nearly 100% guranteed to have hetero and this is what's interesting ---> As such, before embarking on our path to 'meta-analytic enlightenment', we conducted a literature survey to understand how widespread the problem may be in comparative physiology and gauge the ways in which it is currently being addressed, if at all.
 To accomplish this goal, we searched for meta-analyses and comparative analyses that tackled questions using physiological data compiled from animal studies across multiple species.
 We were specifically interested in asking: 1) what type of effect size was used within the quantitative synthesis?
-2) based on the methods provided, was the effect size likely susceptable to variation in how treatments are applied across studies?
+2) based on the methods provided, was the effect size likely susceptible to variation in how treatments are applied across studies?
 3) If so, was the variation resulting from treatment differences accounted for in the effect size or during analysis?, and finally, 4) how were effect sizes analysed in the quantitative synthesis, were these weighted analyses, and what program was used for analysis?
@@
 
-A very common occurance in comparative physiology is to manipulate the tempearture organisms experience and measure some physiologcal rate (e.g., metabolic rate).
-Using normal effect size measures (see above) would result in the effect sizes varying in the types of temperatures applied within and across across studies contributing to 'comparablity' issues.
+A very common occurrence in comparative physiology is to manipulate the temperature organisms experience and measure some physiological rate (e.g., metabolic rate).
+Using normal effect size measures (see above) would result in the effect sizes varying in the types of temperatures applied within and across across studies contributing to 'comparability' issues.
 As such, it is often of interest to standardsise effects by temperature.
@@
 \end{equation} 
-$$ Equation \@ref(eq:lnq10) is essentially a temperature corrected equivalent to lnRR when the numerator and denomenator are measured at different temperatures.
+$$ Equation \@ref(eq:lnq10) is essentially a temperature corrected equivalent to lnRR when the numerator and denominator are measured at different temperatures.
 This allows one to compare the mean of two temperature treatments directly regardless of the temperatures that these groups have been measured.
@@
 @Nakagawa2015 recently proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
-Like *lnRR*, *lnVR* and *lnCVR* are ratios that describe the relative difference in trait variablity between two groups.
+Like *lnRR*, *lnVR* and *lnCVR* are ratios that describe the relative difference in trait variability between two groups.
 We refer readers to @Nakagawa2015 for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling variances) as follows:
@@
 When this occurs we recommend comparative physiologists apply meta-regression approaches, controlling for these known treatment differences as a moderator.
-There are simple statisical approaches a meta-analyst can use to then make the overall effects interpretable [@Schielzeth2010].
+There are simple statistical approaches a meta-analyst can use to then make the overall effects interpretable [@Schielzeth2010].
 Before diving into meta-regression models, we will first overview the meta-analytic approaches or steps commonly used.
@@
 For example, assume we collected the change in CORT dosage relative to a control group (i.e., in uL / g) for our meta-analysis on egg CORT effects on bird reproduction.
-If the untransformed dosage, $x_{j}$, is included in the model then the overall meta-analystic mean estimate, $\beta_{0}$, would be the mean effect of CORT relative to a control treatment, on reproduction when the dosage difference between the treatment and control group is 0 uL /g.
+If the untransformed dosage, $x_{j}$, is included in the model then the overall meta-analytic mean estimate, $\beta_{0}$, would be the mean effect of CORT relative to a control treatment, on reproduction when the dosage difference between the treatment and control group is 0 uL /g.
 Of course, this interpretation does not make much sense.
@@
 The new variable, $c_{j}$, is now centered on the mean and can replace $x_{j}$.
-When the model is refit with $c_{j}$ the estimated $\beta_{0}$ can now be more intuitivly interpreted as the overall mean effect of CORT on reproduction at an average dosage difference between treatment and control groups.
+When the model is refit with $c_{j}$ the estimated $\beta_{0}$ can now be more intuitively interpreted as the overall mean effect of CORT on reproduction at an average dosage difference between treatment and control groups.
 Importantly, by centering, we retain the original units (uL / g) of the variable, which can be very useful to allow for a more general interpretation of the effect magnitude.
 Of course, if one is not interested in the magnitude of effect, we could also change our question and simply model mean reproductive output as a function of dosage (often what are referred to as 'arm-based' meta-analytic models).
-Here, one can model the mean for each group (i.e., control and treatment group), and acount for the known sampling variance associated with each group mean.
-Dosage, or other continuous variables like temperature, can then be modelled (accounting for sampling variance) to understand how mean reproductive output changes.
+Here, one can model the mean for each group (i.e., control and treatment group), and account for the known sampling variance associated with each group mean.
+Dosage, or other continuous variables like temperature, can then be modeled (accounting for sampling variance) to understand how mean reproductive output changes.
 It is important to recognise that all means need to be comparable and that these models are more complex to fit.
@@
 
-Centering moderator variables, like temperature and dosage, not only provides a way to make the overall mean effect more interpretable in the face of treatment heterogenity, but it also allows more complex relationships to be fit without compromising interpretations, including non-linear parameters and interactions (e.g., polynomials).
+Centering moderator variables, like temperature and dosage, not only provides a way to make the overall mean effect more interpretable in the face of treatment heterogeneity, but it also allows more complex relationships to be fit without compromising interpretations, including non-linear parameters and interactions (e.g., polynomials).
 In other words, linear / main effects can still be interpreted normally in the presence of non-linear / interactions fit in the model [@Schielzeth2010; @GelmanHill2007].
 This can be particularly powerful when more complex, nonlinear, dosage relationships exist.
-We provide examples in the online supplementary material (with R code) to show readers how teh models we describe above can be fit, and how, meta-analytic means can be adjusted for treatment heterogenity.
+We provide examples in the online supplementary material (with R code) to show readers how the models we describe above can be fit, and how, meta-analytic means can be adjusted for treatment heterogeneity.
 
@@
 Formally quantifying and presenting heterogeneity estimates from meta-analytic models can provide a way to understand the major drivers of effect size variation by allowing researchers to produce various $I^2$ estimates which can be formally compared within and across studies.
-For example, we could fit the multilevel model described above to understand what proportion of variation is the result of, say, 'study' effects following @NakagawaSantos2012:
-
-$$ I^2_{study} = \frac{\sigma^2_{study}}{\sigma^2_{total}} $$ where $\sigma^2_{study}$ is the study specific variance, and all other variance components are for phylogeny, species, residual (effect size level) and m (total measurement/sampling error).
+For example, we could fit the multilevel model described above to understand what proportion of variation is the result of, say, 'study' effects following @NakagawaSantos2012: $I^2_{study} = \frac{\sigma^2_{study}}{\sigma^2_{total}}$ where $\sigma^2_{study}$ is the study specific variance, and all other variance components are for phylogeny, species, residual (effect size level) and m (total measurement/sampling error).
 Many readers will notice the similarities between $I^2$ and $R^2$ [@Nakgawa2013; @Nakagawa2010].
@@
 
-$$ R^2_{marginal} = \frac{\sigma^2_{fixed}}{\sigma^2_{fixed} + \sigma^2_{study} + \sigma^2_{phylogeny} + \sigma^2_{species} + \sigma^2_{residual}} $$
+$$ R^2_{marginal} = \frac{\sigma^2_{fixed}}{\sigma^2_{fixed} + \sigma^2_{study} + \sigma^2_{phylogeny} + \sigma^2_{species} + \sigma^2_{residual}}$$
 

### 2021-06-29 MS/ms.Rmd
Just goig through spelling errors

@@
 In addition, we derive new effect size measures that provide comparative physiologists with a means to directly make effect measures comparable without the need to resort to more complex statistical models that may be harder to interpret.
-Our 'new' effect sizes and corresponding sampling variances help physiologists deal with common treatment differeces across studies; allowing researchers to compare both mean differences and associated differences in variance for physiological traits.
+Our 'new' effect sizes and corresponding sampling variances help physiologists deal with common treatment differences across studies; allowing researchers to compare both mean differences and associated differences in variance for physiological traits.
 The new effect sizes we propose, in combination with existing meta-analytic models, will pave the way for comparative physiologists to explore exciting new questions by making results from large-scale data sets collected from the literature more accessible and widely interpretable.
@@
 A meta-analysis, being part of systematic review, provides quantitatively informed answers to research questions by using a transparent and reproducible search strategy to synthesise research results across studies and identify sources of variation [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Arnqvist1995; @Koricheva2013].
-<!--- note meta-analysis itself is not really about transparency etc - it is a stasitical tool - these other bits come in as a part of systeamtic review ---> Meta-analysing independent studies provides greater statistical power and precision than what any individual study on its own would be able to provide on a question - particularly given that most empirical studies are already under-powered in many areas of biology [@Forstmeier2017; @Jennions2003; @Button2013].
+<!--- note meta-analysis itself is not really about transparency etc - it is a stasitical tool - these other bits come in as a part of systematic review ---> Meta-analysing independent studies provides greater statistical power and precision than what any individual study on its own would be able to provide on a question - particularly given that most empirical studies are already under-powered in many areas of biology [@Forstmeier2017; @Jennions2003; @Button2013].
 By expressing study effects on a common scale (i.e., standardised effect size) a meta-analyst can gain broader insight into the direction and efficacy of a particular treatment effect or the strength of a relationship between two variables of interest [@Gurevitch2018; @Koricheva2013].
-Quantitative syntheses, including meta-analyses, have provided comparative physiologists with powerful insights on pressing global challenges - from testing whether physiological plasticity can buffer organisms against climate change [e.g, @Seebacher2015] to the degree to which endocrine disrupting chemicals, such as bisphenol A (BPA), impact aquatic organisms [e.g., @WuSeebacher2020].
+Quantitative syntheses, including meta-analyses, have provided comparative physiologists with powerful insights on pressing global challenges - from testing whether physiological plasticity can buffer organisms against climate change [e.g, @Seebacher2015] to the degree to which endocrine disrupting chemicals, such as bis phenol A (BPA), impact aquatic organisms [e.g., @WuSeebacher2020].
 
@@
 Aside from providing an up-to-date overview of the research question, along with identifying any gaps and biases, there are two major goals of meta-analysis: 1) to provide an overall mean estimate of a treatment effect or relationship and 2) to quantify effect size variance and understand key drivers explaining differences in effects across studies [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Koricheva2013].
-A critically important feature of meta-analaysis is its ability to account for sampling error [@Koricheva2013].
+A critically important feature of meta-analysis is its ability to account for sampling error [@Koricheva2013].
 The inverse of sampling error variance is used to weight studies, accordingly, in the analysis and make overall estimates more precise.
 While many meta-analyses might employ unweighted analyses, these studies will not gain greater precision on estimates because sampling variance cannot be formally accounted for in the analysis, even if the overall mean itself may be unbiased.
-<!--- cite Morrissey here - also, the overall mean is unbiased given there is no publication bias or small study effects - this is important as many meta-analyses are likley to suffer from small study effects; my pick sann does not seem like you have talked about publcaiton bias too much - an ablity of meta-analysis to detect publicaiton bias is one of its strength - or probalby the major strength...
+<!--- cite Morrissey here - also, the overall mean is unbiased given there is no publication bias or small study effects - this is important as many meta-analyses are likley to suffer from small study effects; my pick sann does not seem like you have talked about publcaiton bias too much - an ability of meta-analysis to detect publication bias is one of its strength - or probably the major strength...
 --->
@@
 To the uninitiated, the concern might not be unfounded given that meta-analyses in ecology and evolution often mix highly heterogeneous effect size estimates, resulting in high variability [@Senior2016].
-<!--- this last sentence does not seem to fit well or not completely logical - did you want to say -heterogeniety is normal.
-Actually Jessica always say in ecology meta-analysis is probalby not that useful; meta-regression is what we are most interested - I think yo cna make a similar point or you are already making one but make it clearer  - the first sentence is a good one but rather than focusing on "contolling" for hetero but finding out what causes hetero should our (comparative phsiologists') main aim for meta-analysis.
+<!--- this last sentence does not seem to fit well or not completely logical - did you want to say -heterogeneity is normal.
+Actually Jessica always say in ecology meta-analysis is probably not that useful; meta-regression is what we are most interested - I think yo can make a similar point or you are already making one but make it clearer  - the first sentence is a good one but rather than focusing on "controlling" for hetero but finding out what causes hetero should our (comparative physiologists') main aim for meta-analysis.
 I know you are probably intending to say something like this but not coming through at the moment.
-Also, I note that "review generated evidence" only comes from meta-regression not meta-analysis = intercept models - as study general evidnece can be equivalent to meta-analytic results --->
+Also, I note that "review generated evidence" only comes from meta-regression not meta-analysis = intercept models - as study general evidence can be equivalent to meta-analytic results --->
 
@@
 We then introduce new effect sizes and their associated sampling variance to provide comparative physiologists opportunities to explicitly incorporate treatment differences into the effect size estimates to ease their interpretation.
-<!--- see my comments above - they are not really new effec sizes - just formalising we can chat about this lnRR, lnVR and lnCVR and Q10 all exisit already ---> We then describe how more complex treatment differences, such as dosage differences, which may have non-linear effects, can be accommodated using multilevel meta-regression models.
+<!--- see my comments above - they are not really new effect sizes - just formalising we can chat about this lnRR, lnVR and lnCVR and Q10 all exisit already ---> We then describe how more complex treatment differences, such as dosage differences, which may have non-linear effects, can be accommodated using multilevel meta-regression models.
 We hope to show how expanding the meta-analytic toolkit for comparative physiologists will provide new opportunities to address global scale problems that attempt to understand how organisms will cope with rapidly changing environments in the future.
@@
 
-<!---  Dan syas: I'm thinking now, in re-reading this, that we could use a slightly expanded version of paragraph 4 taht describes this problem in a little more detail.
+<!---  Dan says: I'm thinking now, in re-reading this, that we could use a slightly expanded version of paragraph 4 that describes this problem in a little more detail.
 This is likely the place for a figure, which I am having some trouble envisaging where one is best placed.
@@
 The validity of general conclusions to certain questions (e.g., what is the overall effect of a pollutant on reproduction?) will inevitably depend on the homogeneity of effects being synthesized.
-<!--- this is know as putting one number on so many different kinds of studies - but of course, this may not be that interesting apart from a starting point for subsequent meta-regressoin analyses ---> For example, given the very different physiology of aquatic mammals and fish, understanding an overall combined effect on reproduction may not be particularly relevant, and indeed may be misleading.
+<!--- this is know as putting one number on so many different kinds of studies - but of course, this may not be that interesting apart from a starting point for subsequent meta-regression analyses ---> For example, given the very different physiology of aquatic mammals and fish, understanding an overall combined effect on reproduction may not be particularly relevant, and indeed may be misleading.
 It is important to consider these questions when conducting meta-analyses.
@@
 This situation might be analogous to a meta-analysis in comparative physiology that attempts to understand the effects of temperature on fish growth.
-<!--- taxnomically speaking - comparing different applies are comparing different populations of the same spieces of fish so not quite sure whether this is quite correct - I am being of course a bit pedentic---> Studies might rear populations of fish under different temperatures, but in the end, they are still all fish, governed by the same thermodynamic effects on growth.
+<!--- taxnomically speaking - comparing different applies are comparing different populations of the same species of fish so not quite sure whether this is quite correct - I am being of course a bit pedantic---> Studies might rear populations of fish under different temperatures, but in the end, they are still all fish, governed by the same thermodynamic effects on growth.
 In this situation, we might still be interested in understanding overall effects, but we may question whether such a conclusion is sensible given the diversity of temperatures applied.
@@
 
-As discussed above, it is clear that different types of questions and experimental approaches will be more or less susceptable to the 'apples and oranges' problem.
-<!--- not sure whehter it is a good idea to hightlight it as a problem as said earlier - explaining hetero is what's interesting and even the main porupose of meta-analysis for comparative physiologiests - they are not the problem but they are what we are going to invesitgate.
-I do not think 'suspetible' is a good word here given the average hetero = > 90% - you are nearly 100% guranteed to have hetero and this is what's interesting ---> As such, before embarking on our path to 'meta-analytic enlightenment', we conducted a literature survey to understand how widespread the problem may be in comparative physiology and gauge the ways in which it is currently being addressed, if at all.
+As discussed above, it is clear that different types of questions and experimental approaches will be more or less susceptible to the 'apples and oranges' problem.
+<!--- not sure whether it is a good idea to highlight it as a problem as said earlier - explaining hetero is what's interesting and even the main purpose of meta-analysis for comparative physiologists - they are not the problem but they are what we are going to investigate.
+I do not think 'susceptible' is a good word here given the average hetero = > 90% - you are nearly 100% guaranteed to have hetero and this is what's interesting ---> As such, before embarking on our path to 'meta-analytic enlightenment', we conducted a literature survey to understand how widespread the problem may be in comparative physiology and gauge the ways in which it is currently being addressed, if at all.
 To accomplish this goal, we searched for meta-analyses and comparative analyses that tackled questions using physiological data compiled from animal studies across multiple species.
@@
 Briefly, we first did a series of pilot searches (detailed in Supplementary Materials) to refine our search query.
-We searched for studies that included: 'meta-analysis', 'meta regression' , 'comparative analysis', 'comprehensive analysis' 'global analysis' or 'macrophysiology' in their title and abstract, restricting our search to key comparative physiology journals (deatiled in Table X - Supplementary Materials) within the last 6 years.
-We expected this to provide a contemporay overview of quantitative syntheses in comparative physiology while making the survey and screening feasible.
-We awknowledge that this may have missed some important, and influential, quantitative synthese in the field of comparative physiology, but likely provided a random sample to inform on the questions we sought to address (see below).
+We searched for studies that included: 'meta-analysis', 'meta regression' , 'comparative analysis', 'comprehensive analysis' 'global analysis' or 'macro physiology' in their title and abstract, restricting our search to key comparative physiology journals (detailed in Table X - Supplementary Materials) within the last 6 years.
+We expected this to provide a contemporary overview of quantitative syntheses in comparative physiology while making the survey and screening feasible.
+We acknowledge that this may have missed some important, and influential, quantitative synthesis in the field of comparative physiology, but likely provided a random sample to inform on the questions we sought to address (see below).
 
-We included quantitative syntheses, including meta-analyses (*sensu stricto*), that were focused on comparative physiologcial questions only.
+We included quantitative syntheses, including meta-analyses (*sensu stricto*), that were focused on comparative physiological questions only.
 Narrative reviews and comments were not considered because they did not collate quantitative data from the literature.
@@
 While many studies in comparative physiology collect data as part of a comparative analysis, we focus here only on studies collating data from existing literature because this is the major data source for quantitative synthesis.
-Quantitative syntheses interested in phenology, biomechanics, sexual size dimorphism (i.e., SSD, except if the study was interested in sexual differences in physiological traits), those focused on validating physiological methodology, or characterising population genetic structure, gene transcription and quantitative genetics were excluded.
+Quantitative syntheses interested in phenology, bio-mechanics, sexual size dimorphism (i.e., SSD, except if the study was interested in sexual differences in physiological traits), those focused on validating physiological methodology, or characterising population genetic structure, gene transcription and quantitative genetics were excluded.
 There were also meta-analyses that focused on colour evolution and contrast which varied in their goals but were most often not focused on physiological questions.
@@
 Considering our temperature example above, if we are interested in the magnitude of change between temperature treatments, we may want to use a contrast-based effect size, such as the log response ratio $\ln{RR}$.
-If we are instead interested in how the mean of some physiological trait changes with tempearture we may instead model the mean itself.
-In the latter scenerio, so long as all the means are measured in the same units (e.g., ; or can be converted to the same units) then the mean may provide the desired answer to a given question.
+If we are instead interested in how the mean of some physiological trait changes with temperature we may instead model the mean itself.
+In the latter scenario, so long as all the means are measured in the same units (e.g., ; or can be converted to the same units) then the mean may provide the desired answer to a given question.
 We provide details on different effect measures and associated sample sizes in Table \@ref(tab:tablea).
@@
 Using normal effect size measures (see above) would result in the effect sizes varying in the types of temperatures applied within and across across studies contributing to 'comparability' issues.
-As such, it is often of interest to standardsise effects by temperature.
+As such, it is often of interest to standardize effects by temperature.
 One common effect size measure already used in comparative physiology to compare physiological rates is $Q_{10}$ [e.g., @Rodgers2021; @Seebacher2015; @Havird2020], which describes the multiplicative change in physiological rates across a 10°C temperature change.
@@
 <!--- As said before you want to play up the aspect of investigaing heterogeneity rather than controlling for it - controlling for it seems to mean you still want to know the overall effect after getting rid of every confunders.
-Whilst it is also waht we want, we really want to explain the hetero --->
+Whilst it is also what we want, we really want to explain the hetero --->
 
@@
 Multilevel meta-regression models include all the same random effects that we have already discussed, but they also include fixed effects (i.e., predictors or moderators) that attempt to explain changes in the mean effect size.
-In otherwords, we can modify our multilevel meta-analytic model to turn it into a multilevel meta-regression model as follows:
+In other words, we can modify our multilevel meta-analytic model to turn it into a multilevel meta-regression model as follows:
 
@@
 Importantly, the variable $x_{j}$ could be any moderator collected from studies, including dosage, temperature, salinity, or pH.
-Some moderators will be at the level of the study (e.g., was the study experimental or observational in nature) but others could be taken at the effect size level (i.e., was the effect derived using a tempearture of 23°C or 35°C).
+Some moderators will be at the level of the study (e.g., was the study experimental or observational in nature) but others could be taken at the effect size level (i.e., was the effect derived using a temperature of 23°C or 35°C).
 By including these moderators in a meta-regression model, the interpretation of the overall meta-analytic mean, $\beta_{0}$, changes.
@@
 
-<!--- be consistent with sigma notations above - actuall total - m may sometimes not work - so best adding up all like this, which was the core finding in Nakagawa & Schielzeth's R2 --->
+<!--- be consistent with sigma notations above - actually total - m may sometimes not work - so best adding up all like this, which was the core finding in Nakagawa & Schielzeth's R2 --->
 
@@
 Note that this formula does not include $\sigma^2_{m}$ as sampling error variance is assumed to be known in meta-analysis as explained above <!--- if you have not done so, please do --->.
-The $R^2_{marginal}$ provides a formal means to assess just how much variation in effects is teh result of known heterogeneity at the effect size level <!--- note what level's variation it accounts for depends on the type of a fixed effect or moderator --->, driven by continuous moderators such as dosage, temperature, salinity, and even pH.
+The $R^2_{marginal}$ provides a formal means to assess just how much variation in effects is the result of known heterogeneity at the effect size level <!--- note what level's variation it accounts for depends on the type of a fixed effect or moderator --->, driven by continuous moderators such as dosage, temperature, salinity, and even pH.
 $I^2_{hetero}$ maybe a useful measure to provide to help readers understand just how much effect variation can result from the specific treatment application.

### 2021-06-30 MS/ms.Rmd
Adding some more detailed survey methods for categorisation / decisions. Its not easy, but hopfully this is more clear

@@
 We were specifically interested in asking: 1) what type of effect size was used within the quantitative synthesis?
-2) based on the methods provided, was the effect size likely susceptible to variation in how treatments are applied across studies?
+2) based on the methods provided, was the effect size likely susceptible to continuous variation in how treatments were applied (e.g., for contarst-based effects) or the conditions under which traits were measured (i.e., for correlatioons) across studies?
 3) If so, was the variation resulting from treatment differences accounted for in the effect size or during analysis?, and finally, 4) how were effect sizes analysed in the quantitative synthesis, were these weighted analyses, and what program was used for analysis?
@@
 For full details on the search strings used, dates searched, the number of papers found, and our PRISMA flowchart (along with reasons for exclusion at the full text stage) we refer readers to the *Supplementary Materials*.
+To address our questions, we categorised effect sizes as falling into the following categories: Response Ratio (lnRR), Standardised Mean Differences (SMD; e.g., Hedges d, g or Cohen's d), Correlation or Fisher's Z -transformed Correlation, Regression Slopes (Slopes), Risk Ratios, or whether the paper analysed the raw data or summary statistics directly (i.e., means/proportions) (which we label as raw/mean/proportion).
+For all other effects we labelled as 'other'.
+To determine whether effect sizes were likely to vary based on some underlying continuous variable or were dependent on the context in which traits were measured, we assessed whether authors: 1) acknowledged this explicitly in the paper or 2) accounted for it in their models.
+If it was not clear, two of us (DWAN & PP) discussed the paper, and made a decision.
+For example, trait means, such as ectothermic metabolic rate (i.e., raw/mean/proportion-based effect size), will vary depending on the temperature being measured, the magnitude of differences between two treatments (e.g, contrast-based effect sizes - SMD or lnRR) might depend on the temperature or dosage used in treatments, and the strength of relationship between two variables (e.g., correlation between behaviour and metabolism) might depend on the temperature context under which metabolic rate or behaviour were measured.
+Given the high heterogeneity in effects used in comparative physiology, we expected this to be common to most effect sizes, however, it has not been formally quantified.
 

### 2021-06-30 MS/ms.Rmd
Fixed spelling/wording in new section. Fixed a few easy correcions from Shin

@@
 
-Daniel W.A. Noble$^{1,*}$, Patrice Potter$^{2}$, Sammy Burke$^{2}$, Szymek Drobniak$^{2}$, Malgorzata Lagisz$^{2}$, Rose O'Dea$^{2}$, Shinichi Nakagawa$^{2}$
+Daniel W.A. Noble$^{1,*}$, Patrice Potter$^{2}$, Malgorzata Lagisz$^{2}$, Sammy Burke$^{2}$, Szymek Drobniak$^{2}$, Rose O'Dea$^{2}$, Shinichi Nakagawa$^{2}$
 
@@
 
-A meta-analysis, being part of systematic review, provides quantitatively informed answers to research questions by using a transparent and reproducible search strategy to synthesise research results across studies and identify sources of variation [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Arnqvist1995; @Koricheva2013].
-<!--- note meta-analysis itself is not really about transparency etc - it is a stasitical tool - these other bits come in as a part of systematic review ---> Meta-analysing independent studies provides greater statistical power and precision than what any individual study on its own would be able to provide on a question - particularly given that most empirical studies are already under-powered in many areas of biology [@Forstmeier2017; @Jennions2003; @Button2013].
+A meta-analysis, being part of systematic review, provides quantitatively informed answers to research questions by synthesising research results across studies and identify sources of variation [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Arnqvist1995; @Koricheva2013].
+Meta-analysing independent studies provides greater statistical power and precision than what any individual study on its own would be able to provide on a question - particularly given that most empirical studies are already under-powered in many areas of biology [@Forstmeier2017; @Jennions2003; @Button2013].
 By expressing study effects on a common scale (i.e., standardised effect size) a meta-analyst can gain broader insight into the direction and efficacy of a particular treatment effect or the strength of a relationship between two variables of interest [@Gurevitch2018; @Koricheva2013].
@@
 The inverse of sampling error variance is used to weight studies, accordingly, in the analysis and make overall estimates more precise.
-While many meta-analyses might employ unweighted analyses, these studies will not gain greater precision on estimates because sampling variance cannot be formally accounted for in the analysis, even if the overall mean itself may be unbiased.
+While many meta-analyses might employ unweighted analyses, these studies will not gain greater precision on estimates because sampling variance cannot be formally accounted for in the analysis, even if the overall mean itself will be unbiased [@Morrissey2016a].
 <!--- cite Morrissey here - also, the overall mean is unbiased given there is no publication bias or small study effects - this is important as many meta-analyses are likley to suffer from small study effects; my pick sann does not seem like you have talked about publcaiton bias too much - an ability of meta-analysis to detect publication bias is one of its strength - or probably the major strength...

### 2021-06-30 MS/ms.Rmd
MOre fixes and dealing with a few more comments from Shin

@@
 In other words, if we compare different types of 'apples' is it still fair to synthesize these studies to understand overall effects?
-This situation might be analogous to a meta-analysis in comparative physiology that attempts to understand the effects of temperature on fish growth.
-<!--- taxnomically speaking - comparing different applies are comparing different populations of the same species of fish so not quite sure whether this is quite correct - I am being of course a bit pedantic---> Studies might rear populations of fish under different temperatures, but in the end, they are still all fish, governed by the same thermodynamic effects on growth.
+This situation might be analogous to a meta-analysis in comparative physiology that attempts to understand the effects of temperature on fish growth across different populations of a widely distributed (cosmopoliton) species.
+Studies might rear populations of fish under different temperatures, but in the end, they are still all the same fish species, governed by the same thermodynamic effects on growth.
 In this situation, we might still be interested in understanding overall effects, but we may question whether such a conclusion is sensible given the diversity of temperatures applied.
@@
 
-As discussed above, it is clear that different types of questions and experimental approaches will be more or less susceptible to the 'apples and oranges' problem.
-<!--- not sure whether it is a good idea to highlight it as a problem as said earlier - explaining hetero is what's interesting and even the main purpose of meta-analysis for comparative physiologists - they are not the problem but they are what we are going to investigate.
-I do not think 'susceptible' is a good word here given the average hetero = > 90% - you are nearly 100% guaranteed to have hetero and this is what's interesting ---> As such, before embarking on our path to 'meta-analytic enlightenment', we conducted a literature survey to understand how widespread the problem may be in comparative physiology and gauge the ways in which it is currently being addressed, if at all.
+As discussed above, it is clear that different types of questions and experimental approaches will mix 'apples and oranges' to varying extents, and indeed, this heterogenity (or basket of fruit) is often the main interest to comparative biologists.
+To better understand the different types of effect sizes being used, thier susceptability to known sources of methodological / environmental variablity across studies, and how these sources are controlled we conducted a literature survey.
 To accomplish this goal, we searched for meta-analyses and comparative analyses that tackled questions using physiological data compiled from animal studies across multiple species.
@@
 Given the high heterogeneity in effects used in comparative physiology, we expected this to be common to most effect sizes, however, it has not been formally quantified.
+We categorised the types of staitsical models fit in each study as: 1) fixed-effect meta-analysis; 2) random effects meta-analysis (i.e., intercept only model, but has random study effects); 3) multi-level meta-analysis (i.e., intercept only model, but has multiple random effect levels such as study, species, observation-level random effects); 4) meta-regression models (i.e., a multilevel or random effect model with fixed effects - including random effects); 5) weighted regression models, inluding mixed effect models; and 6) linear regression models (including linear and generalised linear mixed effect models, and phylogenetic least squares models).
+Notably, only model types 1-5 are weighted models.
 
@@
 Prior to showing how the relevant $Q_{10}$ effect size can be calculated it can be helpful to understand its similarities to *lnRR*.
-The *lnRR* described by @Hedges1999 and extended by @Lajeunesse2011 and can be calculated as follows <!---put see also Senior et al.
-2020 RSM as well - there we expand the 2nd order delta method stuff - so unbiased formlas for all lnRR, lnVR etc is a bit different - we do not want to put it here but mention by the way - Lajeuness 2011 is not the one I would cite Lajeuness 2015 is more relevant ---> :
+The *lnRR* described by @Hedges1999 and extended by @Lajeunesse2015 and can be calculated as follows [but see also @Senior2020]:
 

### 2021-07-03 MS/ms.Rmd
Writing some conclusions to hopefully better capture the goals. Also, a box would be really good and then we can use the Q10 effect sizes to walk reader through. Box can be more general, and maybe use a different effect size like SMD.

@@
     bibliography: refs.bib
+  bookdown::word_document2:
+    toc: no
+    toc_depth: 6
+    number_sections: false
+    reference_docx: template.docx
 editor_options: 
@@
 If the studies are experimental in nature, than a standardised effect size, such as $ln_{RR}$ or Hedges' *d* might be applicable.
-We then might fit an overall, multilevel meta-analytic model as follows: $$
+We then might fit an overall, multilevel meta-analytic model as follows:
+$$
 \begin{equation} 
@@
 \end{equation} 
-$$ $$
+$$ 
+$$
 \begin{equation} 
@@
 Of course, the overall effect does not provide us a way to interpret its magnitude in the context of how much CORT has been applied in the treatment.
-The most we can say about it, is that the effect is small, moderator of large out of the sample of effect sizes extracted from this set of studies.
+The most we can say about it, is that the effect is small, moderate or large out of the sample of effect sizes extracted from this set of studies.
 In the next section, we show how to 'correct' the overall effect size so that its interpretation is more meaningful.
@@
 The $R^2_{marginal}$ provides a formal means to assess just how much variation in effects is the result of known heterogeneity at the effect size level <!--- note what level's variation it accounts for depends on the type of a fixed effect or moderator --->, driven by continuous moderators such as dosage, temperature, salinity, and even pH.
-$I^2_{hetero}$ maybe a useful measure to provide to help readers understand just how much effect variation can result from the specific treatment application.
+$R^2_{marginal}$, or how we like to think of it, $R^2_{heterogenity}$, maybe a useful measure to provide to help readers understand just how much effect variation can result from the specific treatment application.
+If the heterogeneity is high as a result, say, dosages differences, then it is clear that the choice of dosage within and across studies will have a critical impact on the effect of interest.
 <!--- you can also say metaAider and orcharRd packages have functions to cacualte this already via metafor - implemention is important --->
@@
 ## **Conclusions and Future Directions**
+Comparative physiologists are intersted in meta-analysing effects across a diversity of species, experimental approaches / designs and environments.
+While an overall meta-analytic mean may be of interest, more often than not, understanding the drivers of effect size heterogenity will be the primary interest.
+However, obvious drivers of effect size heterogenity, such as temperature and dosage differences across studies, may not really be of interest.
+Indeed, comparative physiolgists are likely to want an effect size or analytical approach that allows them to remove these 'nusances'.
+Here, we provide comparative physiologists with a set of tools to deal with 'nusance heterogenity' by creatively 'reinventing' standard effect sizes or using meta-regerssion models.
+Of course, nusance heterogenity might in of itself be the main interest, in which case standard meta-regression approaches will work sufficiently.
+However, in many cases, comparative physiolgists might simply want to focus on bigger, more interesting biological moderators of effect size direction and magnitude.
+However, estimating complex meta-regression models with a multitude of fixed effects might result in more challenging model interpretation.
+As such, a combined approach, where some of the known heterogenity is dealt with by deriving a variant effect size and associated sampling variance, and other biologically interesting moderators are fit in a meta-regerssin model, might be the desired.
+Indeed, this may even be a necessity to simplify the model.
 

### 2021-07-03 MS/ms.Rmd
Bunch more writing. Getting really great discission ideas with Shin down on paper. Trying to resolve clarity issues etc. Need to add refs and edit some more though

@@
 Meta-analysis is a tool that provides comparative physiologists with powerful, unbiased and quantitatively informed answers to topical research questions by synthesising effect sizes across disparate studies.
-Meta-analysis's core objective and strength is to distill published research results into standardised effect sizes that can be weighted (i.e., by their inverse sampling variance), and which can be compared across broad sets of research designs, study systems and species.
+Meta-analysis' core objective and strength is to distill published research results into standardised effect sizes that can be weighted (i.e., by their inverse sampling variance), and which can be compared across broad sets of research designs, study systems and species.
 Estimating overall effect sizes, and understanding what drives effect variability, provides opportunities to model how organisms will respond to pressing global challenges.
@@
 Here, we dispel this myth by showing how standardised effects sizes can be used in conjunction with powerful multi-level meta-regression models to both account for factors driving differences across studies and make them more comparable.
-In addition, we derive new effect size measures that provide comparative physiologists with a means to directly make effect measures comparable without the need to resort to more complex statistical models that may be harder to interpret.
-Our 'new' effect sizes and corresponding sampling variances help physiologists deal with common treatment differences across studies; allowing researchers to compare both mean differences and associated differences in variance for physiological traits.
-The new effect sizes we propose, in combination with existing meta-analytic models, will pave the way for comparative physiologists to explore exciting new questions by making results from large-scale data sets collected from the literature more accessible and widely interpretable.
-
-<!--- Dan - new effect sizes here is a big vague.
-Don't we just say - we formalize Q10 for by deriving the sampling error variance (the inverse of weight) of its natural logarithm Further, we propose two additional related effect sizes, which use Q10's standard deviation and coefficence of variation (CV).
-Also, this is an examplar of what eco-phsiologists are familiar with can be used as a standaridsed effect size and they can draw on the tools developed for meta-analysis --->
-
-<!--- xxxx --->
+In addition, we formalise effect size measures that provide comparative physiologists with a means to directly make effect measures comparable, removing 'nusance heterogenity' without the need to resort to more complex statistical models that may be harder to interpret.
+We also describe more general approaches that can be usefully applied to a variety of different contexts to derive 'new' effects sizes and sampling variances.
+The effect sizes and their corresponding sampling variances we describe should help physiologists deal with common treatment differences across studies.
+Using effect sizes that account for components of effect heterogenity, in combination with existing meta-analytic models, will pave the way for comparative physiologists to explore exciting new questions by making results from large-scale data sets collected from the literature more accessible and widely interpretable.
 
@@
 The goal of our review is to briefly overview meta-analytic practices and reassure comparative physiologists that heterogeneity among effect sizes can be comfortably dealt with by modifying existing effect sizes measures and using multilevel meta-regression models.
+Indeed, a combination of these approaches might often be ideal.
 We first conduct a survey of published meta-analyses in the field of comparative physiology to gauge methodological and meta-analytic approaches - assessing what types of effect sizes are commonly used, how often effect size estimates are impacted by continuous treatment differences and whether meta-analytic models (i.e., models that account for sampling variance) are commonly applied.
@@
 
-<!---  Dan says: I'm thinking now, in re-reading this, that we could use a slightly expanded version of paragraph 4 that describes this problem in a little more detail.
-This is likely the place for a figure, which I am having some trouble envisaging where one is best placed.
-It just otherwise seems like a bit of a jump to otherwise head straight into the survey.
-Here we should also talk about quality control, the need to be transparent and have careful reporting.
-This is a big issue in medicine.
-Talked about a lot.
-Integrate blurb below…try to take a balanced approach.
-I will add an introduction bit to this paragraph below to put into context….
-xxxx --->
+Meta-analysis is always concerned with effect heterogenity.
+In other words, the factors that drive differences in the direction and magnitude an of effect within and across studies [@Nakagawa2017; @Gurevitch2018].
+The concept of heterogenity is vitally important because it tells us how general a specific conclusion is likely to be, how much of the variance we see is the result of real biology (and not just sampling variance), and provides a way to understand what the key biological factors are leading to an effect.
+There are a plethera of phenomena driving effect heterogenity, some of which are intersting and others that are less so.
+Generally, contributors to effect size heterogenity fall within a number of broad categories.
+First, sampling variance contributes to heterogenity; the variability in an effect because of the inherent variability in sampling a given population.
+We cannot sample the entire population and nor do we necessarily want to.
+As a consequence, we need to rely on a sub-sample to estimate a population parameter (e.g., correlation between two traits).
+How many independent samples we collect impacts our precision in estimating this 'true' effect.
+In meta-analysis we formally include sampling variance to remove this sourec of heterogenity directly - hence why having sampling variances for an effect is so important.
+Second, there are socialogical factors impacting heterogenity.
+These include attitudes towards publishing non-significant results.
+Low powered studies that do not find an 'effect' or that find an effect in the opposite direction often lead to what is called publication bias.
+Third, there is real biology driving differences in effects.
+This is particularly true in comparative physiology where different species with varying habitats, life-histories, mating systems and reproductive modes are synthesised.
+As comparative physiologists, this is the stuff that gets us up every morning!
+Much variation could result from shared evolutionary history (i.e., phylogeny) or because of the different thermal environments species (or populations) occupy.
+We can model these biological factors to test predcitions on what we hypothsise are key players impacting an effect improving our understanding of the biologcial world around us.
+Finally, methodological factors are also big contributers to effect variability.
+In some cases, these methodological factors are of direct interest.
+For example, the methods for measuring an outcome variable can result in different effects, and it's improtant we know and understand this as it can determine how expetriments are designed in the future.
+In other cases, methodological factors might be considered 'nusance heterogenity' - factors we know vary, but are rather unsurprising to us.
+These can include differences in tempertature, pH, dosages, water potential etc.
+that are obviously going to vary and have an impact on the magnitude of an effect.
+In some cases, these factors might actually not be 'nusance' variables but rather the main interest.
+However, in many cases the can result in a more complicated interpretation of an effect measure then what is desired.
 
+All the various sources of heterogenity (except sampling variance) all contribute (to varying extents) to the 'apples and oranges' problem often touted as being a problem in meta-analyses (or quantitaive syntheses more generally).
+Combinding standardised effects, while ignoring these sources of heterogenity can result in the meaning of a meta-analysis not being particularly useful to many.
+Many others, however, argue that this is just what we are interested in synthesizing.
 In the words of Gene Glass, the father of meta-analysis: "Of course it mixes apples and oranges; in the study of fruit nothing else is sensible; comparing apples and oranges is the only endeavor worthy of true scientists; comparing apples to apples is trivial" [p.g., 224, @Glass2015].
@@
 In this situation, we might still be interested in understanding overall effects, but we may question whether such a conclusion is sensible given the diversity of temperatures applied.
-Such a study does not preclude us from also exploring important moderators or predictors of variability in effects across studies.....
+It is not always clear how we should tackle these sources of heterogenity.
+If temperature differences are of direct interest, then we should definitely model them.
+If, however, it is less interesting, than say the habitat occupied then it may introduce an unnecessary complication to the interpretation of the effect(s) of interest.
+Regardless, a diversity of factors *a priori* that are hypothesised or known to impact heterogenity does not preclude us from also exploring all these important moderators or predictors of variability in effects across studies; however, depending on the effect size used it may just complicate their interpretation or make modelling of all these effects challenging.
 

### 2021-07-03 MS/ms.Rmd
More writing. Fixing Table...not clear why i was added...my mistake

@@
 names <- c("Mean",
-           "Log Standard deviation. lnSD",
+           "Log Standard deviation, lnSD",
            "Log Response Ratio, lnRR",
@@
 
-eqns_yi <- c("M_i",
-             "\\ln{SD_i} + \\frac{1}{2(N_i - 1)}",
+eqns_yi <- c("M",
+             "\\ln{SD} + \\frac{1}{2(N - 1)}",
              # Senior will have a better version but this is good for now
-             "\\ln \\left( \\frac{M_{i1}}{M_{i2}}\\right)",
-             "\\frac{\\left( X_{i2} - X_{i1}\\right)}{SD_{p}}J",
+             "\\ln \\left( \\frac{M_{1}}{M_{2}}\\right)",
+             "\\frac{\\left( X_{2} - X_{1}\\right)}{SD_{p}}J",
              # we need to spell out SD_p somewhere
-             "\\frac{1}{2}log\\left(\\frac{1+r_{i}}{1-r_{i}}\\right)")
+             "\\frac{1}{2}log\\left(\\frac{1+r}{1-r}\\right)")
              #"log\\left(\\frac{y_{i2}+0.5}{n_{i2}-y_{i2}+0.5}\\right) ",
@@
 # Just placeholders for now
-eqns_vi <- c("\\frac{SD_{i}^2}{N_{i}}",
-             "\\frac{1}{2(N_i - 1)}",
-             "\\frac{N_{1i} + N_{2i}}{N_{1i}N_{2i}} + \\frac{SMD^2}{2(N_{1i} + N_{2i})}",
-             "\\frac{SD_{1i}} {M^2_{1i}N_{1i}} + \\frac{SD_{2i}} {M^2_{2i}N_{2i}}",
+eqns_vi <- c("\\frac{SD^2}{N}",
+             "\\frac{1}{2(N - 1)}",
+             "\\frac{N_{1} + N_{2}}{N_{1}N_{2}} + \\frac{SMD^2}{2(N_{1} + N_{2})}",
+             "\\frac{SD_{1}} {M^2_{1}N_{1}} + \\frac{SD_{2}} {M^2_{2}N_{2}}",
              # see my commenst
-             "\\frac{1}{N_i - 3}")
+             "\\frac{1}{N - 3}")
              #"\\frac{s_{i}^2}{n_{i}}",
              #"")
+
+# Maybe add some examples for each effect size in a new column. SHould help
+eg <- c("CT_{min}, CT_{max}, MR",
+        "")
 
@@
 #### *Expanding the Scope of Effect Size Metrics in Comparative Physiology*
+
+As is clear from Table \@ref(tab:tablea) none of the effect measures control for 'nusance heterogenity'.
+For example, the magnitude of response between two treatment groups for lnRR or SMD might depend on just how different the tempeartures, dosages, pH or water potential applied in each treatment.
+Even modelling just the mean often needs to account for 'nusance heterogenity'.
+For example, standard metabolic rate (SMR) is tempearture dependent.
+As such, one needs to standardise the temperature measurement to compare across studies [@White2006; @Uyeda2017; if, of course, temperature is not of interest in of itself].
+While we could of course model this explictly, this may not always be desireable.
+It can often be useful to standardise the effect to both ease its interpretation and simplify modelling.
+In Box 1 we provide readers with guidance on how comparative physiologists can apply corrections to the effect measure itself.
+We highlight two examples in the box focusing mainly on generality.
+Below, we show using a common well understood effect measure of interest to comparative physiologys, $Q_{10}$ how we can formalise a common effect size measure $lnRR$ to capture this 'nusance variation'.
 

### 2021-07-03 MS/ms.Rmd
small fixes.

@@
 For example, standard metabolic rate (SMR) is tempearture dependent.
-As such, one needs to standardise the temperature measurement to compare across studies [@White2006; @Uyeda2017; if, of course, temperature is not of interest in of itself].
+As such, one needs to standardise the temperature measurement to compare across studies [@White2006; @Uyeda2017, if, of course, temperature is not of interest in of itself].
 While we could of course model this explictly, this may not always be desireable.

### 2021-07-04 R/survey_explore.R
Some survey viz experiments

@@ -1,33 +1,52 @@
-
 ## Survey Analysis
 
 # Load libs
-	pacman::p_load(tidyverse, flextable, ggplot2, janitor)
+pacman::p_load(tidyverse, flextable, ggplot2, janitor, ggalluvial)
 
 # Load data
-	data <- read.csv("./data/MA_CompPysio_Survey.csv")
+data <- read.csv("./data/MA_CompPysio_Survey.csv")
 # Have a look
-	data %>% glimpse()
+data %>% glimpse()
 
 # Lets just subset to the main questions for simplicity
 
-	data2 <- data %>% select(!grep("Comment", colnames(data)))
+data2 <- data %>% select(!grep("Comment", colnames(data)))
 
 # Have a look at frequency and stuff
-		data2 %>% tabyl(Q2.2_ContVariable)
+data2 %>% tabyl(Q2.2_ContVariable)
 
 # Just some simple plots. Ok, needs some cleaning looking at this. Studies often used multiple effects
 
-	data2 %>% tabyl(Q2.1_EffectUsed) %>%
-		summarise(SMD = if_else(grepl("SMD", Q2.1_EffectUsed), n, 0),
-				 lnRR = if_else(grepl("Response Ratio", Q2.1_EffectUsed), n, 0),
-				    r = if_else(grepl("correlation", Q2.1_EffectUsed), n, 0),
-				other = if_else(grepl("unclear/other", Q2.1_EffectUsed), n, 0)) %>% colSums(.)
+data2 %>% tabyl(Q2.1_EffectUsed) %>%
+  summarise(SMD = if_else(grepl("SMD", Q2.1_EffectUsed), n, 0),
+            lnRR = if_else(grepl("Response Ratio", Q2.1_EffectUsed), n, 0),
+            r = if_else(grepl("correlation", Q2.1_EffectUsed), n, 0),
+            other = if_else(grepl("unclear/other", Q2.1_EffectUsed), n, 0)) %>% colSums(.)
 
 
-	ggplot(data2, aes(x = Q2.1_EffectUsed)) + 
-		geom_histogram(stat = "count") +
-		theme(axis.text = element_text(size =6))
+ggplot(data2, aes(x = Q2.1_EffectUsed)) + 
+  geom_histogram(stat = "count") +
+  theme(axis.text = element_text(size =6))
 
 
- 
+data2 %>% ggplot(aes(x = Q1.4, fill = Q2.4_WeightedModel)) +
+  geom_bar() +
[…]

### 2021-07-05 MS/ms.Rmd
Fixing spelling

@@
 Here, we dispel this myth by showing how standardised effects sizes can be used in conjunction with powerful multi-level meta-regression models to both account for factors driving differences across studies and make them more comparable.
-In addition, we formalise effect size measures that provide comparative physiologists with a means to directly make effect measures comparable, removing 'nusance heterogenity' without the need to resort to more complex statistical models that may be harder to interpret.
+In addition, we formalise effect size measures that provide comparative physiologists with a means to directly make effect measures comparable, removing 'nuisance heterogeneity' without the need to resort to more complex statistical models that may be harder to interpret.
 We also describe more general approaches that can be usefully applied to a variety of different contexts to derive 'new' effects sizes and sampling variances.
 The effect sizes and their corresponding sampling variances we describe should help physiologists deal with common treatment differences across studies.
-Using effect sizes that account for components of effect heterogenity, in combination with existing meta-analytic models, will pave the way for comparative physiologists to explore exciting new questions by making results from large-scale data sets collected from the literature more accessible and widely interpretable.
+Using effect sizes that account for components of effect heterogeneity, in combination with existing meta-analytic models, will pave the way for comparative physiologists to explore exciting new questions by making results from large-scale data sets collected from the literature more accessible and widely interpretable.
 
@@
 
-Meta-analysis is always concerned with effect heterogenity.
+Meta-analysis is always concerned with effect heterogeneity.
 In other words, the factors that drive differences in the direction and magnitude an of effect within and across studies [@Nakagawa2017; @Gurevitch2018].
-The concept of heterogenity is vitally important because it tells us how general a specific conclusion is likely to be, how much of the variance we see is the result of real biology (and not just sampling variance), and provides a way to understand what the key biological factors are leading to an effect.
-There are a plethera of phenomena driving effect heterogenity, some of which are intersting and others that are less so.
-Generally, contributors to effect size heterogenity fall within a number of broad categories.
-First, sampling variance contributes to heterogenity; the variability in an effect because of the inherent variability in sampling a given population.
+The concept of heterogeneity is vitally important because it tells us how general a specific conclusion is likely to be, how much of the variance we see is the result of real biology (and not just sampling variance), and provides a way to understand what the key biological factors are leading to an effect.
+There are a plethora of phenomena driving effect heterogeneity, some of which are interesting and others that are less so.
+Generally, contributors to effect size heterogeneity fall within a number of broad categories.
+First, sampling variance contributes to heterogeneity; the variability in an effect because of the inherent variability in sampling a given population.
 We cannot sample the entire population and nor do we necessarily want to.
@@
 How many independent samples we collect impacts our precision in estimating this 'true' effect.
-In meta-analysis we formally include sampling variance to remove this sourec of heterogenity directly - hence why having sampling variances for an effect is so important.
-Second, there are socialogical factors impacting heterogenity.
+In meta-analysis we formally include sampling variance to remove this source of heterogeneity directly - hence why having sampling variances for an effect is so important.
+Second, there are sociological factors impacting heterogeneity.
 These include attitudes towards publishing non-significant results.
@@
 Much variation could result from shared evolutionary history (i.e., phylogeny) or because of the different thermal environments species (or populations) occupy.
-We can model these biological factors to test predcitions on what we hypothsise are key players impacting an effect improving our understanding of the biologcial world around us.
-Finally, methodological factors are also big contributers to effect variability.
+We can model these biological factors to test predictions on what we hypothesize are key players impacting an effect improving our understanding of the biological world around us.
+Finally, methodological factors are also big contributors to effect variability.
 In some cases, these methodological factors are of direct interest.
-For example, the methods for measuring an outcome variable can result in different effects, and it's improtant we know and understand this as it can determine how expetriments are designed in the future.
-In other cases, methodological factors might be considered 'nusance heterogenity' - factors we know vary, but are rather unsurprising to us.
-These can include differences in tempertature, pH, dosages, water potential etc.
+For example, the methods for measuring an outcome variable can result in different effects, and it's important we know and understand this as it can determine how experiments are designed in the future.
+In other cases, methodological factors might be considered 'nuisance heterogeneity' - factors we know vary, but are rather unsurprising to us.
+These can include differences in temperature, pH, dosages, water potential etc.
 that are obviously going to vary and have an impact on the magnitude of an effect.
-In some cases, these factors might actually not be 'nusance' variables but rather the main interest.
+In some cases, these factors might actually not be 'nuisance' variables but rather the main interest.
 However, in many cases the can result in a more complicated interpretation of an effect measure then what is desired.
 
-All the various sources of heterogenity (except sampling variance) all contribute (to varying extents) to the 'apples and oranges' problem often touted as being a problem in meta-analyses (or quantitaive syntheses more generally).
-Combinding standardised effects, while ignoring these sources of heterogenity can result in the meaning of a meta-analysis not being particularly useful to many.
+All the various sources of heterogeneity (except sampling variance) all contribute (to varying extents) to the 'apples and oranges' problem often touted as being a problem in meta-analyses (or quantitative syntheses more generally).
+Combining standardised effects, while ignoring these sources of heterogeneity can result in the meaning of a meta-analysis not being particularly useful to many.
 Many others, however, argue that this is just what we are interested in synthesizing.
@@
 In other words, if we compare different types of 'apples' is it still fair to synthesize these studies to understand overall effects?
-This situation might be analogous to a meta-analysis in comparative physiology that attempts to understand the effects of temperature on fish growth across different populations of a widely distributed (cosmopoliton) species.
+This situation might be analogous to a meta-analysis in comparative physiology that attempts to understand the effects of temperature on fish growth across different populations of a widely distributed (cosmopolitan) species.
 Studies might rear populations of fish under different temperatures, but in the end, they are still all the same fish species, governed by the same thermodynamic effects on growth.
 In this situation, we might still be interested in understanding overall effects, but we may question whether such a conclusion is sensible given the diversity of temperatures applied.
-It is not always clear how we should tackle these sources of heterogenity.
+It is not always clear how we should tackle these sources of heterogeneity.
 If temperature differences are of direct interest, then we should definitely model them.
 If, however, it is less interesting, than say the habitat occupied then it may introduce an unnecessary complication to the interpretation of the effect(s) of interest.
-Regardless, a diversity of factors *a priori* that are hypothesised or known to impact heterogenity does not preclude us from also exploring all these important moderators or predictors of variability in effects across studies; however, depending on the effect size used it may just complicate their interpretation or make modelling of all these effects challenging.
+Regardless, a diversity of factors *a priori* that are hypothesised or known to impact heterogeneity does not preclude us from also exploring all these important moderators or predictors of variability in effects across studies; however, depending on the effect size used it may just complicate their interpretation or make modelling of all these effects challenging.
 
@@
 
-As discussed above, it is clear that different types of questions and experimental approaches will mix 'apples and oranges' to varying extents, and indeed, this heterogenity (or basket of fruit) is often the main interest to comparative biologists.
-To better understand the different types of effect sizes being used, thier susceptability to known sources of methodological / environmental variablity across studies, and how these sources are controlled we conducted a literature survey.
+As discussed above, it is clear that different types of questions and experimental approaches will mix 'apples and oranges' to varying extents, and indeed, this heterogeneity (or basket of fruit) is often the main interest to comparative biologists.
+To better understand the different types of effect sizes being used, their susceptibility to known sources of methodological / environmental variability across studies, and how these sources are controlled we conducted a literature survey.
 To accomplish this goal, we searched for meta-analyses and comparative analyses that tackled questions using physiological data compiled from animal studies across multiple species.
 We were specifically interested in asking: 1) what type of effect size was used within the quantitative synthesis?
-2) based on the methods provided, was the effect size likely susceptible to continuous variation in how treatments were applied (e.g., for contarst-based effects) or the conditions under which traits were measured (i.e., for correlatioons) across studies?
+2) based on the methods provided, was the effect size likely susceptible to continuous variation in how treatments were applied (e.g., for contrast-based effects) or the conditions under which traits were measured (i.e., for correlations) across studies?
 3) If so, was the variation resulting from treatment differences accounted for in the effect size or during analysis?, and finally, 4) how were effect sizes analysed in the quantitative synthesis, were these weighted analyses, and what program was used for analysis?
@@
 ## **Conclusions and Future Directions**
-Comparative physiologists are intersted in meta-analysing effects across a diversity of species, experimental approaches / designs and environments.
-While an overall meta-analytic mean may be of interest, more often than not, understanding the drivers of effect size heterogenity will be the primary interest.
-However, obvious drivers of effect size heterogenity, such as temperature and dosage differences across studies, may not really be of interest.
-Indeed, comparative physiolgists are likely to want an effect size or analytical approach that allows them to remove these 'nusances'.
-Here, we provide comparative physiologists with a set of tools to deal with 'nusance heterogenity' by creatively 'reinventing' standard effect sizes or using meta-regerssion models.
-Of course, nusance heterogenity might in of itself be the main interest, in which case standard meta-regression approaches will work sufficiently.
-However, in many cases, comparative physiolgists might simply want to focus on bigger, more interesting biological moderators of effect size direction and magnitude.
+Comparative physiologists are interested in meta-analysing effects across a diversity of species, experimental approaches / designs and environments.
+While an overall meta-analytic mean may be of interest, more often than not, understanding the drivers of effect size heterogeneity will be the primary interest.
+However, obvious drivers of effect size heterogeneity, such as temperature and dosage differences across studies, may not really be of interest.
+Indeed, comparative physiologists are likely to want an effect size or analytical approach that allows them to remove these 'nuisances'.
+Here, we provide comparative physiologists with a set of tools to deal with 'nuisance heterogeneity' by creatively 'reinventing' standard effect sizes or using meta-regression models.
+Of course, nuisance heterogeneity might in of itself be the main interest, in which case standard meta-regression approaches will work sufficiently.
+However, in many cases, comparative physiologists might simply want to focus on bigger, more interesting biological moderators of effect size direction and magnitude.
 However, estimating complex meta-regression models with a multitude of fixed effects might result in more challenging model interpretation.
-As such, a combined approach, where some of the known heterogenity is dealt with by deriving a variant effect size and associated sampling variance, and other biologically interesting moderators are fit in a meta-regerssin model, might be the desired.
+As such, a combined approach, where some of the known heterogeneity is dealt with by deriving a variant effect size and associated sampling variance, and other biologically interesting moderators are fit in a meta-regression model, might be the desired.
 Indeed, this may even be a necessity to simplify the model.

### 2021-07-06 R/survey_explore.R
adding namespace to survey data exploration

@@ -6,22 +6,22 @@ pacman::p_load(tidyverse, flextable, ggplot2, janitor, ggalluvial)
 # Load data
 data <- read.csv("./data/MA_CompPysio_Survey.csv")
 # Have a look
-data %>% glimpse()
+data %>% dplyr::glimpse()
 
 # Lets just subset to the main questions for simplicity
 
-data2 <- data %>% select(!grep("Comment", colnames(data)))
+data2 <- data %>% dplyr::select(!grep("Comment", colnames(data)))
 
 # Have a look at frequency and stuff
-data2 %>% tabyl(Q2.2_ContVariable)
+data2 %>% janitor::tabyl(Q2.2_ContVariable)
 
 # Just some simple plots. Ok, needs some cleaning looking at this. Studies often used multiple effects
 
-data2 %>% tabyl(Q2.1_EffectUsed) %>%
-  summarise(SMD = if_else(grepl("SMD", Q2.1_EffectUsed), n, 0),
-            lnRR = if_else(grepl("Response Ratio", Q2.1_EffectUsed), n, 0),
-            r = if_else(grepl("correlation", Q2.1_EffectUsed), n, 0),
-            other = if_else(grepl("unclear/other", Q2.1_EffectUsed), n, 0)) %>% colSums(.)
+data2 %>% janitor::tabyl(Q2.1_EffectUsed) %>%
+  dplyr::summarise(SMD = dplyr::if_else(grepl("SMD", Q2.1_EffectUsed), n, 0),
+            lnRR = dplyr::if_else(grepl("Response Ratio", Q2.1_EffectUsed), n, 0),
+            r = dplyr::if_else(grepl("correlation", Q2.1_EffectUsed), n, 0),
+            other = dplyr::if_else(grepl("unclear/other", Q2.1_EffectUsed), n, 0)) %>% colSums(.)
 
 
 ggplot(data2, aes(x = Q2.1_EffectUsed)) + 
@@ -38,13 +38,13 @@ data2 %>% ggplot(aes(x = Q1.4, fill = Q2.4_WeightedModel)) +
 
 
 data2 %>%
-  mutate(Q2.4_short = factor(Q2.4_WeightedModel, labels = c('unclear/other', 'unweighted', 'weighted'))) %>%
+  dplyr::mutate(Q2.4_short = factor(Q2.4_WeightedModel, labels = c('unclear/other', 'unweighted', 'weighted'))) %>%
[…]

### 2021-07-06 R/survey_data_results.Rmd
starting to look at results from survey

---
title: "Survey Results from: Meta-analytic approaches and new effect sizes to account for heterogeneous effects in comparative physiology"
author: Daniel W.A. Noble, Patrice Potter, Sammy Burke, Szymek Drobniak, Malgorzata Lagisz, Rose O’Dea, Shinichi Nakagawa
date: "`r Sys.Date()`"
output:
  html_document:
    theme: paper  
    highlight: tango  
    toc: true
    toc_depth: 5
    number_sections: false  
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

pacman::p_load(dplyr,ggplot2)

# loading data
raw <- read.csv("./data/MA_CompPysio_Survey.csv")
metadata <- read.csv("./data/MA_CompPysio_Survey_metadata.csv")

# tidying data
dat <- raw
names(dat) <- metadata$Procesed.Column.Name[match(names(dat), metadata$Raw.Column.Name)]

# tidying categorical options
dat$meta_analysis_self_described <- factor(gsub(" \\(.*", "", dat$meta_analysis_self_described), levels = c("yes","no","unclear/other"))
dat$comparative_physiology_main_focus <- factor(gsub(" \\(.*", "", dat$comparative_physiology_main_focus), levels = c("yes","no","unclear/other"))

# fixing format of journals

#dat$DOI[dat$journal=="2017"] # Typo
dat$journal[dat$journal=="2017"] <- "Biology Letters"

#dat$DOI[grep("Proceedings", dat$journal)] # all the same journal
dat$journal[grep("Proceedings", dat$journal)] <- "Proceedings of the Royal Society B: Biological Sciences"

# standardising DOI format
dat$DOI <- gsub(".*org/", "", dat$DOI)
dat$DOI <-gsub(".* ", "", dat$DOI)

# ggplot2 theme for plots
background.colour <- "white"
text.colour <- "black"
# Font Choice
#loadfonts()
text.font <- "Arial"

tm <- theme(panel.background = element_rect(fill = background.colour),
            plot.background = element_rect(fill = background.colour),
            panel.grid = element_blank(),
            text =  element_text(family = text.font, colour = text.colour),
            axis.text = element_text(colour = text.colour),
            axis.title.x = element_text(margin = margin(10,0,0,0)),
            axis.title.y = element_text(margin = margin(0,10,0,0)),
            axis.line = element_line(colour = text.colour, size = 0.5),
            axis.ticks = element_line(colour = text.colour, size = 0.5),
            plot.title = element_text(hjust = 0.5),
            legend.background = element_rect(fill = background.colour),
            legend.key = element_rect(fill = background.colour),
            plot.margin = margin(6,6,6,6)) 
```

## Sample of `r nrow(dat)` papers {.tabset}

### Meta-analysis {.tabset .tabset-fade .tabset-pills}

Answer to the question "Is paper self-describing as containing a meta-analysis (or meta-regression) or actually using meta-analysis/regression approach?".

```{r}
dat %>% dplyr::group_by(meta_analysis_self_described) %>% dplyr::tally() %>% 
  ggplot() + tm +
  geom_col(aes(x = meta_analysis_self_described, y = n), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
  scale_y_continuous(expand=c(0,0)) +
  labs(x = "meta-analysis or meta-regression",
       y = "number of papers") 
```

### Comparative physiology {.tabset .tabset-fade .tabset-pills}

Answer to the question ""Is the study's main focus on comparative physiology?"

- yes = focused only on physiological traits very clearly)  
- no =  does have physiological traits, but is interested in broader questions involving many different traits

```{r}
dat %>% dplyr::group_by(comparative_physiology_main_focus) %>% dplyr::tally() %>% 
  ggplot() + tm +
  geom_col(aes(x = comparative_physiology_main_focus, y = n), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
  scale_y_continuous(expand=c(0,0)) +
  labs(x = "main focus on comparative physiology",
       y = "number of papers") 
```

### Journals {.tabset .tabset-fade .tabset-pills}

```{r}
dat %>% dplyr::group_by(journal) %>% dplyr::tally() %>% dplyr::arrange(n) %>% dplyr::mutate(journal = factor(journal, levels = unique(journal))) %>% 
  ggplot() + tm + theme(axis.title.y = element_blank(),
                        axis.text.y = element_text(size=8)) +
  geom_col(aes(x = journal, y = n), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
  scale_y_continuous(expand=c(0,0),breaks=seq(1,13,2)) +
  labs(x = "journal",
       y = "number of papers") +
  coord_flip()
```

### Publication years {.tabset .tabset-fade .tabset-pills}

```{r}
dat %>% dplyr::group_by(pub_year) %>% dplyr::tally() %>% 
  ggplot() + tm +
  geom_col(aes(x = pub_year, y = n), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
  scale_y_continuous(expand=c(0,0),breaks=seq(1,13,2)) +
  scale_x_continuous(breaks = min(dat$pub_year):max(dat$pub_year)) +
  labs(x = "publication year",
       y = "number of papers")
```

## R Session Information   
```{r}
print(sessionInfo(), locale = F)
```

### 2021-07-07 MS/ms.Rmd
Making some revisions

@@
 
-A meta-analysis, being part of systematic review, provides quantitatively informed answers to research questions by synthesising research results across studies and identify sources of variation [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Arnqvist1995; @Koricheva2013].
+A meta-analysis, being part of systematic review, provides quantitatively informed answers to research questions by synthesising research results across studies and identify sources of variation [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Arnqvist1995; @Koricheva2013; @Borenstein2019].
 Meta-analysing independent studies provides greater statistical power and precision than what any individual study on its own would be able to provide on a question - particularly given that most empirical studies are already under-powered in many areas of biology [@Forstmeier2017; @Jennions2003; @Button2013].
@@
 Formal meta-analyses, as a part of a systematic review, involve a systematic literature-based search, extraction of data from studies meeting specific inclusion criteria, and the subsequent calculation of effects sizes from summary statistics provided by papers.
-The entire process should follow and report upon this entire process carefully to ensure the meta-analysis within a systematic review, is as transparent and reproducible as possible [i.e., see the Preferred Reporting Items for Systematic Reviews and Meta-Analyses in Ecology and Evolution (PRISMA-EcoEvo) protocol, @ODea2021].
-Aside from providing an up-to-date overview of the research question, along with identifying any gaps and biases, there are two major goals of meta-analysis: 1) to provide an overall mean estimate of a treatment effect or relationship and 2) to quantify effect size variance and understand key drivers explaining differences in effects across studies [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Koricheva2013].
-A critically important feature of meta-analysis is its ability to account for sampling error [@Koricheva2013].
+The entire process should follow and report upon this entire process carefully to ensure the review process and data collation, are as transparent and reproducible as possible [i.e., see the Preferred Reporting Items for Systematic Reviews and Meta-Analyses in Ecology and Evolution (PRISMA-EcoEvo) protocol, @ODea2021].
+Aside from providing an up-to-date overview of the research question there are three major goals of meta-analysis: 1) to provide an overall mean estimate of a treatment effect or relationship, 2) to quantify effect size variance and understand key drivers explaining differences in effects across studies and 3) attempt to identify gaps and publication biases [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Koricheva2013; @Borenstein2019].
+A critically important feature of a meta-analysis is its ability to account for sampling error [@Koricheva2013].
 The inverse of sampling error variance is used to weight studies, accordingly, in the analysis and make overall estimates more precise.
 While many meta-analyses might employ unweighted analyses, these studies will not gain greater precision on estimates because sampling variance cannot be formally accounted for in the analysis, even if the overall mean itself will be unbiased [@Morrissey2016a].
-<!--- cite Morrissey here - also, the overall mean is unbiased given there is no publication bias or small study effects - this is important as many meta-analyses are likley to suffer from small study effects; my pick sann does not seem like you have talked about publcaiton bias too much - an ability of meta-analysis to detect publication bias is one of its strength - or probably the major strength...
---->
 
-Despite the widespread adoption and well established methodological procedures of meta-analysis, it is often criticised for mixing 'apples and oranges' -- in other words, mixing effects from studies that lack comparability [@Gurevitch2018; @Arnqvist1995; @Gallo1979; @Carpenter2020; @Stewart2010; @Glass2015].
+Despite its widespread adoption and well established methodological procedures, meta-analysis is often criticised for mixing 'apples and oranges' -- in other words, mixing effects from studies that lack comparability [@Gurevitch2018; @Arnqvist1995; @Gallo1979; @Carpenter2020; @Stewart2010; @Glass2015].
 Lack of comparability could result from studies differing in experimental design, species, measurement variables and sampling units, which can impact the generalisability of meta-analytic results [@Arnqvist1995; @Stewart2010].
@@
 For example, experimental designs can vary in the temperatures that they apply or in the dosages of chemical modifiers used in experimental treatments [e.g., @WuSeebacher2020].
-In addition, they often include a diversity of study species which can vary in responses.
-To the uninitiated, the concern might not be unfounded given that meta-analyses in ecology and evolution often mix highly heterogeneous effect size estimates, resulting in high variability [@Senior2016].
-<!--- this last sentence does not seem to fit well or not completely logical - did you want to say -heterogeneity is normal.
-Actually Jessica always say in ecology meta-analysis is probably not that useful; meta-regression is what we are most interested - I think yo can make a similar point or you are already making one but make it clearer  - the first sentence is a good one but rather than focusing on "controlling" for hetero but finding out what causes hetero should our (comparative physiologists') main aim for meta-analysis.
-I know you are probably intending to say something like this but not coming through at the moment.
-Also, I note that "review generated evidence" only comes from meta-regression not meta-analysis = intercept models - as study general evidence can be equivalent to meta-analytic results --->
+To the uninitiated, this concern might not be unfounded given that heterogenity in effects is often high in ecological and evolutionary meta-analyses [@Senior2016], telling us that the effect size varies a great deal from one population to another.
+However, to many, the very fact that highly heterogeneous effects exist is the core strength of meta-analysis when considered carefully [@Cooperetal2019; @Borenstein2019; @Gurevitch2018; @Glass2015].
+Indeed, exploring the reasons for why effects are likely to vary across studies "...is the spice of life" [p.g., 519; @Cooperetal2019].
 
@@
 Meta-analysis is always concerned with effect heterogeneity.
-In other words, the factors that drive differences in the direction and magnitude an of effect within and across studies [@Nakagawa2017; @Gurevitch2018].
+In other words, the factors that drive differences in the direction and magnitude an of effect within and across studies [@Nakagawa2017; @Gurevitch2018; @Cooperetal2019; @Borenstein2019].
 The concept of heterogeneity is vitally important because it tells us how general a specific conclusion is likely to be, how much of the variance we see is the result of real biology (and not just sampling variance), and provides a way to understand what the key biological factors are leading to an effect.

### 2021-07-07 MS/ms.Rmd
Few more fixes to writing, and dealing with some more of Shin' comments before running off to meeting

@@
 To the uninitiated, this concern might not be unfounded given that heterogenity in effects is often high in ecological and evolutionary meta-analyses [@Senior2016], telling us that the effect size varies a great deal from one population to another.
-However, to many, the very fact that highly heterogeneous effects exist is the core strength of meta-analysis when considered carefully [@Cooperetal2019; @Borenstein2019; @Gurevitch2018; @Glass2015].
+However, to many, the very fact that highly heterogeneous effects exist is a core strength of meta-analysis [@Cooperetal2019; @Borenstein2019; @Gurevitch2018; @Glass2015].
 Indeed, exploring the reasons for why effects are likely to vary across studies "...is the spice of life" [p.g., 519; @Cooperetal2019].
@@
 
-Meta-analysis is always concerned with effect heterogeneity.
-In other words, the factors that drive differences in the direction and magnitude an of effect within and across studies [@Nakagawa2017; @Gurevitch2018; @Cooperetal2019; @Borenstein2019].
-The concept of heterogeneity is vitally important because it tells us how general a specific conclusion is likely to be, how much of the variance we see is the result of real biology (and not just sampling variance), and provides a way to understand what the key biological factors are leading to an effect.
+Meta-analysis is always concerned with effect heterogeneity; in other words, the factors that drive differences in the direction and magnitude an of effect within and across studies [@Nakagawa2017; @Gurevitch2018; @Cooperetal2019; @Borenstein2019].
+The concept of heterogeneity is vitally important because it tells us how general a specific conclusion is likely to be, how much of the variance we see is the result of real biology (and not just sampling variance), and provides a way to understand what the key biological factors are leading to an effect [@Nakagawa2017; @Borenstein2019].
 There are a plethora of phenomena driving effect heterogeneity, some of which are interesting and others that are less so.
+
 Generally, contributors to effect size heterogeneity fall within a number of broad categories.
-First, sampling variance contributes to heterogeneity; the variability in an effect because of the inherent variability in sampling a given population.
+First, sampling variance contributes to heterogeneity; the variability driven by the inherent uncertainty in sampling of a given population.
 We cannot sample the entire population and nor do we necessarily want to.
@@
 How many independent samples we collect impacts our precision in estimating this 'true' effect.
-In meta-analysis we formally include sampling variance to remove this source of heterogeneity directly - hence why having sampling variances for an effect is so important.
+In meta-analysis we formally include sampling variance to remove this source of heterogeneity directly - hence why having sampling variances for an effect is so important [@Gurevitch2018; @Koricheva2013].
 Second, there are sociological factors impacting heterogeneity.
@@
 Much variation could result from shared evolutionary history (i.e., phylogeny) or because of the different thermal environments species (or populations) occupy.
-We can model these biological factors to test predictions on what we hypothesize are key players impacting an effect improving our understanding of the biological world around us.
+We can model these biological factors to test predictions from hypotheses we believe are key players impacting an effect.
+This improves our understanding of the biological world around us and helps inform on future research directions.
 Finally, methodological factors are also big contributors to effect variability.
 In some cases, these methodological factors are of direct interest.
-For example, the methods for measuring an outcome variable can result in different effects, and it's important we know and understand this as it can determine how experiments are designed in the future.
-In other cases, methodological factors might be considered 'nuisance heterogeneity' - factors we know vary, but are rather unsurprising to us.
+For example, the methods for measuring an outcome variable can result in different effects, and it is important we know and understand this as it can determine how experiments are designed in the future.
+In other cases, methodological factors might be considered 'nuisance heterogeneity' [@Cooperetal2019] - factors we know vary, but are rather unsurprising to us.
 These can include differences in temperature, pH, dosages, water potential etc.
 that are obviously going to vary and have an impact on the magnitude of an effect.
-In some cases, these factors might actually not be 'nuisance' variables but rather the main interest.
-However, in many cases the can result in a more complicated interpretation of an effect measure then what is desired.
+In some cases, these factors might actually not be 'nuisance' variables but rather the main interest of a synthesis.
+However, in many cases they can result in a more complicated interpretation of an effect measure then what is desired.
 
-All the various sources of heterogeneity (except sampling variance) all contribute (to varying extents) to the 'apples and oranges' problem often touted as being a problem in meta-analyses (or quantitative syntheses more generally).
+All the various sources of heterogeneity (except sampling variance) all contribute (to varying extents) to the 'apples and oranges' problem often touted as being an issues with some meta-analyses (or quantitative syntheses more generally).
+Indeed, some of this criticism revolves around combining studies that vary in their quality (e.g., observational vs experimental).
 Combining standardised effects, while ignoring these sources of heterogeneity can result in the meaning of a meta-analysis not being particularly useful to many.
-Many others, however, argue that this is just what we are interested in synthesizing.
+However, many argue that this is just what we are interested in synthesizing [@Cooperetal2019; @Borenstein2019; @Gurevitch2018; @Glass2015].
 In the words of Gene Glass, the father of meta-analysis: "Of course it mixes apples and oranges; in the study of fruit nothing else is sensible; comparing apples and oranges is the only endeavor worthy of true scientists; comparing apples to apples is trivial" [p.g., 224, @Glass2015].
-@Glass2015's intention was to simply highlight that whether comparing apples and oranges is a good idea simply boils down to the specific question of interest and the population one wishes to make conclusions about.
+@Glass2015's intention was to simply highlight that whether comparing apples and oranges is a good idea simply boils down to the specific question of interest, the population one wishes to make conclusions about and how hetergenous effects actually are.
 If we are interested in gaining insight into 'fruit' then synthesising apples and oranges is the only thing that makes sense.
-<!---  as said, comparative analysis by definition, compares applies and oranges - = different species - I guess you are mainly talking about mixing different methods ones - this is where I said earlier - focusing on explaining hetero comes in.
-Also, mixing different quality of studies are often referred to as "Garbage in and garbage out" ---> Instead, if we are interested in generalising only to apples then mixing fruit will not be ideal.
+Instead, if we are interested in generalising only to apples then mixing fruit will not be ideal.
+In addition, if we want to understand why different 'fruit' vary in their effects, then we can only ask this question by including all fruit [@Borenstein2019].
+
 We tend to agree with @Glass2015, and his sentiment is of particular relevance to comparative physiology.
@@
 In doing so, it provides a richer set of conclusions that can draw attention to important sources of variability that might have otherwise been overlooked.
-Having said that, it is still very important to understand the limitations and diversity of studies included within a meta-analysis - an important reason why transparency and reproducibility are such a prominent feature of meta-analysis (or ideally should be) [@ODea2021].
+Having said that, it is still very important to understand the limitations and diversity of studies included within a meta-analysis, and how this can affect interpretations made - an important reason why transparency and reproducibility are such a prominent feature of meta-analysis (or ideally should be) [@ODea2021].
 The validity of general conclusions to certain questions (e.g., what is the overall effect of a pollutant on reproduction?) will inevitably depend on the homogeneity of effects being synthesized.
-<!--- this is know as putting one number on so many different kinds of studies - but of course, this may not be that interesting apart from a starting point for subsequent meta-regression analyses ---> For example, given the very different physiology of aquatic mammals and fish, understanding an overall combined effect on reproduction may not be particularly relevant, and indeed may be misleading.
+If the estimate of an overall effect coincies with low heterogenity esatimtes, then the effects are reasonably consistent [@Borenstein2019].
+If, however, an overall effect is accompanied by large heterogenity, then we would shift focus and explore drivers of that heterogeneity.
+For example, given the very different physiology of aquatic mammals and fish, understanding an overall combined effect on reproduction may not be particularly relevant, and indeed may be misleading.
 It is important to consider these questions when conducting meta-analyses.
 
-Of course, there are certain types of heterogeneity that transcend different questions.
+Of course, there are certain types of heterogeneity that transcend different questions or that are simply a 'nuisance' to interpreting effects.
 In other words, if we compare different types of 'apples' is it still fair to synthesize these studies to understand overall effects?
@@
 If temperature differences are of direct interest, then we should definitely model them.
-If, however, it is less interesting, than say the habitat occupied then it may introduce an unnecessary complication to the interpretation of the effect(s) of interest.
+If, however, it is less interesting, than say the habitat occupied, then it may introduce an unnecessary complication to the interpretation of the effect(s) of interest.
 Regardless, a diversity of factors *a priori* that are hypothesised or known to impact heterogeneity does not preclude us from also exploring all these important moderators or predictors of variability in effects across studies; however, depending on the effect size used it may just complicate their interpretation or make modelling of all these effects challenging.

### 2021-07-08 MS/ms.Rmd
More writing. Fixing heterogenity section, introducing some important ideas on PIs

@@
 
-<!--- As said before you want to play up the aspect of investigaing heterogeneity rather than controlling for it - controlling for it seems to mean you still want to know the overall effect after getting rid of every confunders.
-Whilst it is also what we want, we really want to explain the hetero --->
-
-It will not be possible to derive an effect size that completely controls for known heterogeneity at the effect size level all the time.
-This limitation is partly because treatment effects are not be simple linear or exponential functions of the mean response making the effect sizes we discuss above unsuitable [e.g., thermal performance curves; @Noble2018].
-For example, dosages applied to treatments can follow quite complex non-linear relationships, with exponential or quadratic relationships in relation to some mean response.
-When this occurs we recommend comparative physiologists apply meta-regression approaches, controlling for these known treatment differences as a moderator.
-There are simple statistical approaches a meta-analyst can use to then make the overall effects interpretable [@Schielzeth2010].
+It will not be possible to derive an effect size that completely controls for 'nuisance' heterogeneity at the effect size level all the time.
+This limitation is partly because treatment effects may not be simple linear or exponential functions of the mean response making the effect sizes we discuss above unsuitable [e.g., thermal performance curves; @Noble2018].
+For example, dosages applied to treatments can follow quite complex non-linear relationships (e.g., quadratic relationships) in relation to some mean response.
+When this occurs we recommend comparative physiologists apply meta-regression approaches, controlling for 'these known treatment differences 'nusiance heterogenity' as a moderator.
+In many cases, this will be the easiest, or even preferred approach because exploring drivers of heterogenity will be the main interest in most meta-analyses.
+Nonetheless, there are some simple statistical approaches a meta-analyst can use to then make the overall effects interpretable, allowing one to control for 'nuisance heterogenity', while also allowing other biological moderators of interest to be tested [@Schielzeth2010].
 Before diving into meta-regression models, we will first overview the meta-analytic approaches or steps commonly used.
@@
 \begin{equation} 
-a_{k[i]}\sim N(0, \sigma^{2}_aA),\
-sp_{k[i]}\sim N(0, \sigma^{2}_{sp}I),\
-s_{j[i]}\sim N(0, \sigma^{2}_{sp}I),\
-e_{i}\sim N(0, \sigma^{2}_eI),\
+a_{k[i]}\sim N(0, \sigma^{2}_{phylogeny}A),\
+sp_{k[i]}\sim N(0, \sigma^{2}_{species}I),\
+s_{j[i]}\sim N(0, \sigma^{2}_{study}I),\
+e_{i}\sim N(0, \sigma^{2}_{residual}I),\
 m_{i} \sim N(0, v_{i})\
@@
 $N_{ES}$, the number of effect sizes), $\beta_{0}$ is the overall meta-analytic mean, $a_{k[i]}$ is the phylogenetic effect (a random effect) for species *k* applied to effect size *i*.
-Phylogenetic effects are assumed to be normally distributed deviates sampled from a distribution with a mean of 0 and variance $\sigma^{2}_aA$ [i.e., *N*$(0, \sigma^{2}_aA)$], where A is a phylogenetic correlation matrix derived from a phylogenetic tree, $sp_{k[i]}$ is the species-specific effect for the *k*th species applied to effect size *i*, $s_{j[i]}$ is the study-specific effect for the *j*th study applied to effect size *i*, $e_{i}$ is the effect size-specific effect (or within study effect, or residuals) for the *i*th effect size, and $m_{i}$ is the sampling variance effect around the *i*th effect as a result of variation in precision among each effect sizes, $v_{i}$, which is known.
-This model is a 'weighted' multilevel meta-analysis model because the estimation of *u* is weighted by the inverse sampling variance of each effect size.
+Phylogenetic effects are assumed to be normally distributed deviates sampled from a distribution with a mean of 0 and variance $\sigma^{2}_{phylogeny}$ [i.e., *N*$(0, \sigma^{2}_{phylogeny}A)$], where A is a phylogenetic correlation matrix derived from a phylogenetic tree, $sp_{k[i]}$ is the species-specific effect for the *k*th species applied to effect size *i*, $s_{j[i]}$ is the study-specific effect for the *j*th study applied to effect size *i*, $e_{i}$ is the effect size-specific effect (or within study effect, or residuals) for the *i*th effect size, and $m_{i}$ is the sampling variance effect around the *i*th effect as a result of variation in precision among each effect sizes, $v_{i}$, which is known as the sampling variance for effect.
+This model is a 'weighted' multilevel meta-analysis model because the estimation of the overall meta-analytic mean, $\beta_{0}$, is weighted by the inverse sampling variance of each effect size.
 The fact that we can obtain an overall estimate of sampling variance (i.e., $\sigma^2_{m}$) is very important because it provides a way for us to understand just how much variation in effects are the result of sampling differences across studies versus other, potentially important sources of variation such as differences in the methods applied, species differences or even real biological effects that impact the effect size a study is likely to observe [@Nakagawa2017; @NakagawaSantos2012].
@@
 
-Quantifying effect size heterogeneity (i.e., effect size variance) provides a pathway to explore hypotheses thought to explain why effects might vary within and across studies.
-Effect size heterogeneity can be thought of as the percentage of variance between effect sizes that cannot be attributable to sampling error (often as called 'total' heterogeneity) [@Higgins2002].
-More formally, we can quantify heterogeneity using the multilevel meta-analytic model we describe above as:
+Quantifying effect size heterogeneity (i.e., effect size variance) provides the impetus for exploring hypotheses that are thought to explain why effects might vary within and across studies, while also providing context for interpreting the generality of effects.
+There are a number of measures commonly used to quantify effect size heterogenity [@Borenstein2019], however, in ecological and evolutionary meta-analysis, heterogeneity is often calculated and reported as $I_{total}^2$ as follows (if using a multilevel meta-analytic model as we describe above):
 
@@
 
-where $\sigma^2_{total} = \sigma^2_{study} + \sigma^2_{phylogeny} + \sigma^2_{species} + \sigma^2_{residual} +\sigma^2_{m}$ is the total effect size variance (using the above multilevel model) and $\sigma^2_{m}$ is 'typical' the sampling error variance.
-<!--- you need more than that sigma_m is a typical one - you may need to provide a formula here --->.
-Quantifying heterogeneity provides a formal way to assess how much variation is the result of 'true' biological or methodological differences as opposed to simply chance (i.e., sampling variance) [@NakagawaSantos2012; @Higgins2002].
-We can only conduct such analyses if we have an estimate of the sampling variance for a given effect measure because only then can we quantify how much variation is the result of sampling variability.
+where $\sigma^2_{total} = \sigma^2_{study} + \sigma^2_{phylogeny} + \sigma^2_{species} + \sigma^2_{residual} +\sigma^2_{m}$ is the total effect size variance  and $\sigma^2_{m}$ is the sampling error variance calculated as:
+$$
+
+$$
+Quantifying heterogeneity using $I_{total}^2$ provides a formal way to assess the relative amount of variation that is the result of 'true' biological or methodological differences as opposed to simply chance (i.e., sampling variance) [@NakagawaSantos2012; @Higgins2002].
+In other words, $I_{total}^2$ can be thought of as the percentage of variance between effect sizes that cannot be attributable to sampling error [@Higgins2002].
+We can only calculate this metric if we have an estimate of the sampling variance for a given effect measure because only then can we quantify the proportion of variation that is the result of sampling variability.
 @Senior2016 have shown that total heterogeneity is often extremely high in ecological and evolutionary meta-analysis (\~91%), suggesting that effect measures vary widely across and within studies.
@@
 
-Note that this formula does not include $\sigma^2_{m}$ as sampling error variance is assumed to be known in meta-analysis as explained above <!--- if you have not done so, please do --->.
-The $R^2_{marginal}$ provides a formal means to assess just how much variation in effects is the result of known heterogeneity at the effect size level <!--- note what level's variation it accounts for depends on the type of a fixed effect or moderator --->, driven by continuous moderators such as dosage, temperature, salinity, and even pH.
-$R^2_{marginal}$, or how we like to think of it, $R^2_{heterogenity}$, maybe a useful measure to provide to help readers understand just how much effect variation can result from the specific treatment application.
-If the heterogeneity is high as a result, say, dosages differences, then it is clear that the choice of dosage within and across studies will have a critical impact on the effect of interest.
-<!--- you can also say metaAider and orcharRd packages have functions to cacualte this already via metafor - implemention is important --->
+Note that this formula does not include $\sigma^2_{m}$ as sampling error variance is assumed to be known in meta-analysis as explained above.
+When including continuous moderators, such as dosage, temperature, salinity, and even pH, $R^2_{marginal}$ provides a formal means to assess just how much variation in effects is the result of 'nuisance' heterogeneity at the effect size level.
+Other biological moderators of interest could also be included as fixed effects and $R^2_{marginal}$ calculated for each independently or all together.
+Importantly, moderators could be those that explain variation at the effect size level (i.e., dosage, temperature) or they could explain variation at the study or species level (e.g., reproductive mode, endothermy etc).
+$R^2_{marginal}$, or how we like to think of it, $R^2_{'nuisance'}$, maybe a useful measure to help readers understand just how much effect variation can result from the specific treatment application.
+If the heterogeneity is high as a result of, say, dosages differences, then it is clear that the choice of dosage within and across studies will have a critical impact on the effect of interest.
+Comparative physiologists intersted in implementing thse calculations can do so using our packages `orchaRd` [@Nakagawa2021c] or `metaAidR` (https://github.com/daniel1noble/metaAidR).
+
+While heterogenity estimates using $I^2$ measures can be useful for understanding the relative contributions of different factors to effect size variation, prediction intervals might be more appropriate in many cases [@Nakagawa2021c; @Borenstein2019].
+Unlike $I^2$, prediction intervals are more holistic and probably more meaningful in the context of meta-analysis.
+Prediction intervals make use of the standard deviation of the mean instead of the standard error (which creates confidence intervals) [@Borenstein2019].
 

### 2021-07-08 MS/ms.Rmd
Editing paper to point of survey

@@
 
-A meta-analysis, being part of systematic review, provides quantitatively informed answers to research questions by synthesising research results across studies and identify sources of variation [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Arnqvist1995; @Koricheva2013; @Borenstein2019].
+A meta-analysis provides quantitatively informed answers to research questions by synthesising research results across studies and identifying sources of variation [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Arnqvist1995; @Koricheva2013; @Borenstein2019].
 Meta-analysing independent studies provides greater statistical power and precision than what any individual study on its own would be able to provide on a question - particularly given that most empirical studies are already under-powered in many areas of biology [@Forstmeier2017; @Jennions2003; @Button2013].
@@
 It has emerged as the 'gold-standard' across various disciplines for quantitative synthesis and is becoming increasingly more prominent in the field of comparative physiology.
-Formal meta-analyses, as a part of a systematic review, involve a systematic literature-based search, extraction of data from studies meeting specific inclusion criteria, and the subsequent calculation of effects sizes from summary statistics provided by papers.
+Formal meta-analyses are part of a systematic review and involve a systematic literature-based search, extraction of data from studies meeting specific inclusion criteria, and the subsequent calculation of effects sizes from summary statistics provided by papers.
 The entire process should follow and report upon this entire process carefully to ensure the review process and data collation, are as transparent and reproducible as possible [i.e., see the Preferred Reporting Items for Systematic Reviews and Meta-Analyses in Ecology and Evolution (PRISMA-EcoEvo) protocol, @ODea2021].
@@
 The inverse of sampling error variance is used to weight studies, accordingly, in the analysis and make overall estimates more precise.
-While many meta-analyses might employ unweighted analyses, these studies will not gain greater precision on estimates because sampling variance cannot be formally accounted for in the analysis, even if the overall mean itself will be unbiased [@Morrissey2016a].
+While many meta-analyses might employ unweighted analyses, these studies will not gain greater precision on estimates because sampling variance cannot be formally accounted for in the analysis, even if the overall mean itself is unbiased [@Morrissey2016a].
 
@@
 
-The goal of our review is to briefly overview meta-analytic practices and reassure comparative physiologists that heterogeneity among effect sizes can be comfortably dealt with by modifying existing effect sizes measures and using multilevel meta-regression models.
-Indeed, a combination of these approaches might often be ideal.
-We first conduct a survey of published meta-analyses in the field of comparative physiology to gauge methodological and meta-analytic approaches - assessing what types of effect sizes are commonly used, how often effect size estimates are impacted by continuous treatment differences and whether meta-analytic models (i.e., models that account for sampling variance) are commonly applied.
-We then introduce new effect sizes and their associated sampling variance to provide comparative physiologists opportunities to explicitly incorporate treatment differences into the effect size estimates to ease their interpretation.
-<!--- see my comments above - they are not really new effect sizes - just formalising we can chat about this lnRR, lnVR and lnCVR and Q10 all exisit already ---> We then describe how more complex treatment differences, such as dosage differences, which may have non-linear effects, can be accommodated using multilevel meta-regression models.
+The goal of our review is to briefly overview meta-analytic practices and reassure comparative physiologists that heterogeneity among effect sizes can be comfortably dealt through modification of existing effect sizes measures and using multilevel meta-regression models.
+Indeed, a combination of these approaches might often be ideal given that explaining heterogeneity will most often be the core goal of any meta-analysis in comparative physiology.
+We first conduct a survey of published meta-analyses in the field of comparative physiology to gauge methodological and meta-analytic approaches -- assessing what types of effect sizes are commonly used, how often effect size estimates are impacted by continuous treatment differences and whether meta-analytic models (i.e., models that account for sampling variance) are commonly applied.
+We then formalise alternative effect sizes and their associated sampling variance to provide comparative physiologists opportunities to explicitly incorporate treatment differences into the effect size estimates to ease their interpretation.
+We then describe how more complex treatment differences, such as dosage differences (which may have non-linear effects) can be accommodated using multilevel meta-regression models.
 We hope to show how expanding the meta-analytic toolkit for comparative physiologists will provide new opportunities to address global scale problems that attempt to understand how organisms will cope with rapidly changing environments in the future.
@@
 Generally, contributors to effect size heterogeneity fall within a number of broad categories.
-First, sampling variance contributes to heterogeneity; the variability driven by the inherent uncertainty in sampling of a given population.
+First, sampling variance contributes to heterogeneity; the variability driven by the inherent uncertainty in sampling a given population.
 We cannot sample the entire population and nor do we necessarily want to.
 As a consequence, we need to rely on a sub-sample to estimate a population parameter (e.g., correlation between two traits).
-How many independent samples we collect impacts our precision in estimating this 'true' effect.
-In meta-analysis we formally include sampling variance to remove this source of heterogeneity directly - hence why having sampling variances for an effect is so important [@Gurevitch2018; @Koricheva2013].
+How many independent samples we collect impacts our precision in estimating this 'true' effect [@Borenstein2019].
+In meta-analysis we formally include sampling variance to remove this source of heterogeneity directly -- hence why having sampling variances for an effect is so important [@Gurevitch2018; @Koricheva2013].
 Second, there are sociological factors impacting heterogeneity.
 These include attitudes towards publishing non-significant results.
-Low powered studies that do not find an 'effect' or that find an effect in the opposite direction often lead to what is called publication bias.
+Low powered studies that do not find an 'effect' or that find an effect in the opposite direction often lead to what is called publication bias [@Jennions2013; @Nakagawa2021b; @Rothstein2005].
 Third, there is real biology driving differences in effects.
@@
 Much variation could result from shared evolutionary history (i.e., phylogeny) or because of the different thermal environments species (or populations) occupy.
-We can model these biological factors to test predictions from hypotheses we believe are key players impacting an effect.
-This improves our understanding of the biological world around us and helps inform on future research directions.
+We can model these biological factors to test predictions from hypotheses that we believe are key players impacting mean effect size and direction.
+This improves our understanding of the biological world around us, and helps inform on future research directions.
 Finally, methodological factors are also big contributors to effect variability.
@@
 For example, the methods for measuring an outcome variable can result in different effects, and it is important we know and understand this as it can determine how experiments are designed in the future.
-In other cases, methodological factors might be considered 'nuisance heterogeneity' [@Cooperetal2019] - factors we know vary, but are rather unsurprising to us.
+In other cases, methodological factors might be considered 'nuisance heterogeneity' [following from @Cooperetal2019] -- factors we know vary, but are rather unsurprising to us.
 These can include differences in temperature, pH, dosages, water potential etc.
-that are obviously going to vary and have an impact on the magnitude of an effect.
-In some cases, these factors might actually not be 'nuisance' variables but rather the main interest of a synthesis.
+The factors are obviously going to vary and have an impact on the magnitude of an effect, but they might distract from the core interest.
+In some cases, however, these factors might actually not be 'nuisance' variables but rather the main interest of a synthesis.
 However, in many cases they can result in a more complicated interpretation of an effect measure then what is desired.
@@
 For example, if we want to understand the impact of a pollutant on reproduction in aquatic organisms then including aquatic mammals and fish would provide answers to this general question, even if their reproductive biology and physiology are known to differ.
-By synthesizing diverse study outcomes, it allows us to not just report on overall effects (if the question is relevant to ask), but understand critical features of the literature, study systems (e.g., different effects of pollutants on fish and mammal reproduction) and approaches that can explain the diversity of effect outcomes observed.
+By synthesizing diverse study outcomes, it allows us to not just report on overall effects (if the question is relevant to ask), but to understand critical features of the literature, study systems (e.g., different effects of pollutants on fish and mammal reproduction) and approaches that can explain the diversity of effect outcomes observed.
 In doing so, it provides a richer set of conclusions that can draw attention to important sources of variability that might have otherwise been overlooked.
-Having said that, it is still very important to understand the limitations and diversity of studies included within a meta-analysis, and how this can affect interpretations made - an important reason why transparency and reproducibility are such a prominent feature of meta-analysis (or ideally should be) [@ODea2021].
+Having said that, it is still very important to understand the limitations and diversity of studies included within a meta-analysis, and how this can affect interpretations made -- an important reason why transparency and reproducibility are such a prominent feature of meta-analysis (or ideally should be) [@ODea2021].
 The validity of general conclusions to certain questions (e.g., what is the overall effect of a pollutant on reproduction?) will inevitably depend on the homogeneity of effects being synthesized.
-If the estimate of an overall effect coincies with low heterogenity esatimtes, then the effects are reasonably consistent [@Borenstein2019].
-If, however, an overall effect is accompanied by large heterogenity, then we would shift focus and explore drivers of that heterogeneity.
+If the estimate of an overall effect coincides with low heterogenity estimates then the effects are reasonably consistent [@Borenstein2019].
+If, however, an overall effect is accompanied by large heterogenity estimates, then we would shift focus and explore drivers of that heterogeneity.
 For example, given the very different physiology of aquatic mammals and fish, understanding an overall combined effect on reproduction may not be particularly relevant, and indeed may be misleading.
+Therefore, understanding overall effects in each of these groups seperately (and whether they differ) will be more useful.
 It is important to consider these questions when conducting meta-analyses.
@@
 In other words, if we compare different types of 'apples' is it still fair to synthesize these studies to understand overall effects?
-This situation might be analogous to a meta-analysis in comparative physiology that attempts to understand the effects of temperature on fish growth across different populations of a widely distributed (cosmopolitan) species.
+This situation might be analogous to a meta-analysis in comparative physiology that attempts to understand the effects of dietary on fish growth across different populations of a widely distributed (cosmopolitan) species.
 Studies might rear populations of fish under different temperatures, but in the end, they are still all the same fish species, governed by the same thermodynamic effects on growth.
@@
 If temperature differences are of direct interest, then we should definitely model them.
-If, however, it is less interesting, than say the habitat occupied, then it may introduce an unnecessary complication to the interpretation of the effect(s) of interest.
+If, however, it is less interesting, than say the diet administered, then it may introduce an unnecessary complication to the interpretation of the effect(s) of interest.
 Regardless, a diversity of factors *a priori* that are hypothesised or known to impact heterogeneity does not preclude us from also exploring all these important moderators or predictors of variability in effects across studies; however, depending on the effect size used it may just complicate their interpretation or make modelling of all these effects challenging.

### 2021-07-08 MS/ms.Rmd
Fixed some bib problems. Did some fixing of text.

@@
 If, however, it is less interesting, than say the diet administered, then it may introduce an unnecessary complication to the interpretation of the effect(s) of interest.
-Regardless, a diversity of factors *a priori* that are hypothesised or known to impact heterogeneity does not preclude us from also exploring all these important moderators or predictors of variability in effects across studies; however, depending on the effect size used it may just complicate their interpretation or make modelling of all these effects challenging.
 
@@
 
-As discussed above, it is clear that different types of questions and experimental approaches will mix 'apples and oranges' to varying extents, and indeed, this heterogeneity (or basket of fruit) is often the main interest to comparative biologists.
+As discussed above, different types of questions and experimental approaches will mix 'apples and oranges' to varying extents, and indeed, this heterogeneity (or basket of fruit) is often the main interest to comparative biologists.
 To better understand the different types of effect sizes being used, their susceptibility to known sources of methodological / environmental variability across studies, and how these sources are controlled we conducted a literature survey.
@@
 All searches were conducted in Scopus between May 16 - 18, 2021.
-Briefly, we first did a series of pilot searches (detailed in Supplementary Materials) to refine our search query.
+Briefly, we first did a series of pilot searches (detailed in Supplementary Materials) to refine our search query [See @Foo2021 for an overview of this process].
 We searched for studies that included: 'meta-analysis', 'meta regression' , 'comparative analysis', 'comprehensive analysis' 'global analysis' or 'macro physiology' in their title and abstract, restricting our search to key comparative physiology journals (detailed in Table X - Supplementary Materials) within the last 6 years.
@@
 
-## **Opening Up New Opportunities in Comparative Physiology: Expanding the Breadth of Effect Sizes to Deal with Treatment Differences Across Studies**
+## **Opening Up New Opportunities in Comparative Physiology: Expanding the Breadth of Effect Sizes to Deal with "Nuisiance Heterogenity"**
 
-#### *Brief Introduction to Common Effect Sizes and Sampling Errors that are Useful in Comparative Physiology*
+#### *Common Effect Sizes and Sampling Errors that are Useful in Comparative Physiology*
 
@@
 
+#### *Comparing Changes in Mean Physiological Rates, $Q_{10}$*
 A very common occurrence in comparative physiology is to manipulate the temperature organisms experience and measure some physiological rate (e.g., metabolic rate).
@@
 This opens up the meta-analytic toolbox and improves upon our ability to account for well known sources of non-independence that are typical in meta-analysis [@Lajeunesse2011; @Noble2017].
-
-#### *Comparing changes in mean physiological rates*
 
@@
 
-#### *New Effect Size Metrics that Compare Changes in Variability Across Treatments*
+#### *Formalising Effect Size Metrics that Compare Changes in Variability Across Treatments in the Presence of "Nuisance Heterogenity"*
 
@@
 
-where $CV$ is the coefficient of variation defined as $SD / R$.
-Whether one choose to use SD or CV-based effect size depends on questions at hand (discussed in @Nakagawa2015 and Senior et al.
-2020 <!--- sorry I have not added it to bib file - I will do this later once I go through --->)
+where $CV$ is the coefficient of variation defined as $SD / R$. Whether one choose to use SD or CV-based effect size depends on questions at hand [discussed in @Nakagawa2015 and @Senior2020].
 
-## **Meta-Analytic Models to Control for and Investigate into Heterogeneous Effects Within and Across Studies**
+Our example using $Q_{10}$, a well known effect measure in comparative physiology, shows how common effect size measures can be re-formalised to account for 'nuisance hetreogenity', in this case temperature.
+We can apply similar approaches to other commonly used effect size metrics.
+We describe more generally how this can be done in Box 1, applying similar principles to standardise temperature differences for slopes and for standardised mean differences.
+
+## **Meta-Analytic Models to Control for and Investigate Heterogeneous Effects Within and Across Studies**
 
@@
 Unlike $I^2$, prediction intervals are more holistic and probably more meaningful in the context of meta-analysis.
-Prediction intervals make use of the standard deviation of the mean instead of the standard error (which creates confidence intervals) [@Borenstein2019].
+Prediction intervals make use of the standard deviation of the mean instead of the standard error (which is used to calculate confidence intervals) [@Borenstein2019].
 
@@
 Of course, nuisance heterogeneity might in of itself be the main interest, in which case standard meta-regression approaches will work sufficiently.
-However, in many cases, comparative physiologists might simply want to focus on bigger, more interesting biological moderators of effect size direction and magnitude.
+However, in many cases, comparative physiologists might simply want to focus on bigger, more interesting biological drivers of effect size direction and magnitude.
 However, estimating complex meta-regression models with a multitude of fixed effects might result in more challenging model interpretation.

### 2021-07-08 R/survey_data_results.Rmd
file pathing update
Quick look at effect sizes used

@@
 
-pacman::p_load(dplyr,ggplot2)
+pacman::p_load(dplyr,ggplot2,here, pander, janitor)
 
 # loading data
-raw <- read.csv("./data/MA_CompPysio_Survey.csv")
-metadata <- read.csv("./data/MA_CompPysio_Survey_metadata.csv")
+raw <- read.csv(here("data","MA_CompPysio_Survey.csv"))
+metadata <- read.csv(here("data","MA_CompPysio_Survey_metadata.csv"))
 
@@
 
-### Journals {.tabset .tabset-fade .tabset-pills}
+### Effect Sizes Used {.tabset .tabset-fade .tabset-pills}
 
 ```{r}
-dat %>% dplyr::group_by(journal) %>% dplyr::tally() %>% dplyr::arrange(n) %>% dplyr::mutate(journal = factor(journal, levels = unique(journal))) %>% 
+dat %>% dplyr::group_by(effect_size_type) %>% janitor::tabyl(effect_size_type) %>%
+  dplyr::summarise(SMD = dplyr::if_else(grepl("SMD", effect_size_type), n, 0),
+                  lnRR = dplyr::if_else(grepl("Response Ratio", effect_size_type), n, 0),
+                    Zr = dplyr::if_else(grepl("correlation", effect_size_type), n, 0),
+                 Other = dplyr::if_else(grepl("other|Q10", effect_size_type), n, 0),
+                 Means = dplyr::if_else(grepl("mean/proportion/raw", effect_size_type), n, 0),
+                 lnCVR = dplyr::if_else(grepl("lnCVR", effect_size_type), n, 0),
+                 Slope = dplyr::if_else(grepl("slope", effect_size_type), n, 0)) %>% 
+  colSums(.) %>% data.frame(effect = names(.), n = .) %>% mutate(prop = n / sum(n)) %>% arrange(effect) %>% 
   ggplot() + tm + theme(axis.title.y = element_blank(),
                         axis.text.y = element_text(size=8)) +
-  geom_col(aes(x = journal, y = n), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
-  scale_y_continuous(expand=c(0,0),breaks=seq(1,13,2)) +
-  labs(x = "journal",
-       y = "number of papers") +
+  geom_col(aes(x = effect, y = n), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
+  scale_y_continuous(expand=c(0,0),breaks=seq(1,20,2)) +
+  labs(x = "Effect Size",
+       y = "Number of Papers") +
   coord_flip()
@@
 ```{r}
-print(sessionInfo(), locale = F)
+pander(sessionInfo(), locale = FALSE)
 ```

### 2021-07-08 MS/ms.Rmd
Fixed error in table and updated with some examples relavant to comp phys

@@
              "\\frac{1}{2(N - 1)}",
+             "\\frac{SD_{1}^2} {M^2_{1}N_{1}} + \\frac{SD_{2}^2} {M^2_{2}N_{2}}",
              "\\frac{N_{1} + N_{2}}{N_{1}N_{2}} + \\frac{SMD^2}{2(N_{1} + N_{2})}",
-             "\\frac{SD_{1}} {M^2_{1}N_{1}} + \\frac{SD_{2}} {M^2_{2}N_{2}}",
              # see my commenst
@@
 # Maybe add some examples for each effect size in a new column. SHould help
-eg <- c("CT_{min}, CT_{max}, MR",
-        "")
+eg <- c("CTmin, CTmax, Metabolic Rate (MR)",
+        "Variability in CTmin, CTmax, MR",
+        "Ratio between BPA treatment (BPA-exposed group) and control (no BPA)",
+        "Difference in immune response between males and females or performance difference in the presence of stressor compared to absence of stressor",
+        "Relationship between sex hormones and immune responses or metabolic rate and behaviour")
 
-table_fin <- data.frame(names, eqns_yi, eqns_vi)
+table_fin <- data.frame(names, eqns_yi, eqns_vi, eg)
 
@@
 tablea <- flextable(table_fin)                                                                                %>% 
-          flextable::compose(j = "names", part = "header", value = as_paragraph(as_b("Effect Measure")))      %>% 
-          flextable::compose(j = "eqns_yi", part = "header", value = as_paragraph(as_b("Definition")))        %>% 
-          flextable::compose(j = "eqns_vi", part = "header", value = as_paragraph(as_b("Sampling Variance"))) %>%
-          flextable::compose(j = "eqns_yi", value = as_paragraph(as_equation(eqns_yi)))                       %>%
-          flextable::compose(j = "eqns_vi", value = as_paragraph(as_equation(eqns_vi)))                       %>% 
+          flextable::compose(j = 1:4, part = "header", value = as_paragraph(as_b(c("Effect Measure", "Definition", "Sampling Variance", "Examples")))) %>% 
+          flextable::compose(j = 2:3, value = as_paragraph(as_equation(c(eqns_yi, eqns_vi))))             %>%
+          flextable::compose(j = 4, value = as_paragraph(eg))             %>%
           flextable::width(j = 1, 3)                                                                          %>% 
-          flextable::width(j = 2, 2)
+          flextable::width(j = 2, 2) %>% 
+          flextable::width(j = 4, 5)
 
@@
 Indeed, this may even be a necessity to simplify the model.
+We hope the set of tools we describe here provide clarification around sourfes of heterogenity and provides ways to help comparative physiologists to communicate effect measures more richly to help guide our understanding and decisions around pressing global challenges.
 

### 2021-07-08 MS/ms.Rmd
Fixing intro a bit as not happy with last paragraph

@@
 The effect sizes and their corresponding sampling variances we describe should help physiologists deal with common treatment differences across studies.
-Using effect sizes that account for components of effect heterogeneity, in combination with existing meta-analytic models, will pave the way for comparative physiologists to explore exciting new questions by making results from large-scale data sets collected from the literature more accessible and widely interpretable.
+By using effect sizes that account for components of effect heterogeneity, in combination with existing meta-analytic models, comparative physiologists can explore exciting new questions by making results from large-scale data sets collected from the literature more accessible and widely interpretable.
 
@@
 By expressing study effects on a common scale (i.e., standardised effect size) a meta-analyst can gain broader insight into the direction and efficacy of a particular treatment effect or the strength of a relationship between two variables of interest [@Gurevitch2018; @Koricheva2013].
-Quantitative syntheses, including meta-analyses, have provided comparative physiologists with powerful insights on pressing global challenges - from testing whether physiological plasticity can buffer organisms against climate change [e.g, @Seebacher2015] to the degree to which endocrine disrupting chemicals, such as bis phenol A (BPA), impact aquatic organisms [e.g., @WuSeebacher2020].
+Quantitative syntheses, including meta-analyses, have provided comparative physiologists with powerful insights on pressing global challenges - from testing whether physiological plasticity can buffer organisms against climate change [e.g, @Seebacher2015] to the degree to which endocrine disrupting chemicals, such as bisphenol A (BPA), impact aquatic organisms [e.g., @WuSeebacher2020].
 
-Meta-analysis is a well-developed research topic with a long history in statistics, medicine, psychology and ecology [@Gurevitch2018; @Nakagawa2017; @Glass2015].
+Meta-analysis is a well-developed research field with a long history in statistics, medicine, psychology and ecology [@Gurevitch2018; @Nakagawa2017; @Glass2015].
 It has emerged as the 'gold-standard' across various disciplines for quantitative synthesis and is becoming increasingly more prominent in the field of comparative physiology.
 Formal meta-analyses are part of a systematic review and involve a systematic literature-based search, extraction of data from studies meeting specific inclusion criteria, and the subsequent calculation of effects sizes from summary statistics provided by papers.
-The entire process should follow and report upon this entire process carefully to ensure the review process and data collation, are as transparent and reproducible as possible [i.e., see the Preferred Reporting Items for Systematic Reviews and Meta-Analyses in Ecology and Evolution (PRISMA-EcoEvo) protocol, @ODea2021].
-Aside from providing an up-to-date overview of the research question there are three major goals of meta-analysis: 1) to provide an overall mean estimate of a treatment effect or relationship, 2) to quantify effect size variance and understand key drivers explaining differences in effects across studies and 3) attempt to identify gaps and publication biases [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Koricheva2013; @Borenstein2019].
+A meta-analysis should follow and report upon this entire process carefully to ensure the review process and data collation, are as transparent and reproducible as possible [i.e., see the Preferred Reporting Items for Systematic Reviews and Meta-Analyses in Ecology and Evolution (PRISMA-EcoEvo) protocol, @ODea2021].
+Aside from providing an up-to-date overview of a research field there are three major goals of meta-analysis: 1) to provide an overall mean estimate of a treatment effect or relationship, 2) to quantify effect size variance and understand key drivers explaining differences in effects across studies and 3) attempt to identify gaps and publication biases [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Koricheva2013; @Borenstein2019].
 A critically important feature of a meta-analysis is its ability to account for sampling error [@Koricheva2013].
@@
 
-The goal of our review is to briefly overview meta-analytic practices and reassure comparative physiologists that heterogeneity among effect sizes can be comfortably dealt through modification of existing effect sizes measures and using multilevel meta-regression models.
-Indeed, a combination of these approaches might often be ideal given that explaining heterogeneity will most often be the core goal of any meta-analysis in comparative physiology.
-We first conduct a survey of published meta-analyses in the field of comparative physiology to gauge methodological and meta-analytic approaches -- assessing what types of effect sizes are commonly used, how often effect size estimates are impacted by continuous treatment differences and whether meta-analytic models (i.e., models that account for sampling variance) are commonly applied.
+The goal of our review is to briefly overview the process of meta-analysis, making a case for why heterogenity in a meta-analysis is a good thing for answering fundamental reserch problems and guiding research directions.
+We introduce the idea of 'nuisance heterogenity', showing comparative physiologists that it can be comfortably dealt with be re-formalising many existing effect sizes measures and/or by using multilevel meta-regression models.
+Indeed, a combination of these approaches might often be ideal.
+We first conduct a survey of published meta-analyses in the field of comparative physiology to gauge methodological and meta-analytic practices -- assessing what types of effect sizes are commonly used, how often effect size estimates are impacted by continuous treatment differences and whether meta-analytic models (i.e., models that account for sampling variance) are commonly applied.
 We then formalise alternative effect sizes and their associated sampling variance to provide comparative physiologists opportunities to explicitly incorporate treatment differences into the effect size estimates to ease their interpretation.

### 2021-07-08 MS/ms.Rmd
Fix table legend

@@
 
-```{r tablea, echo = FALSE, tab.cap = "Common effect sizes, associated sampling variances and notes on when they might be used.
-Note that for log odds ratio a continuity correction is applied (i.e., 0.5) to each proportion.
-In addition, a correction factor, J (1-3 ), is applied to the standardised to correct for small sample effects"}
+```{r tablea, echo = FALSE, tab.cap = "Common effect sizes used throughout meta-analyses in comparative physiology, their associated sampling variances and examples on when they might be used.
+Note that that a correction factor, J = 1 - (3 /  (4(N1 + N2 - 2) - 1)), is applied to the SMD to correct for small sample effects"}
 

### 2021-07-08 MS/ms.Rmd
Finished re-writing heterogenity section

@@
 
-```{r tablea, echo = FALSE, tab.cap = "Common effect sizes used throughout meta-analyses in comparative physiology, their associated sampling variances and examples on when they might be used.
-Note that that a correction factor, J = 1 - (3 /  (4(N1 + N2 - 2) - 1)), is applied to the SMD to correct for small sample effects"}
+```{r tablea, echo = FALSE, tab.cap = "Common effect sizes used throughout meta-analyses in comparative physiology, their associated sampling variances and examples on when they might be used."}
 
@@
 
+footnotes <- c("Notes: J = 1 - \\frac{3}{4\\left(N_{1} + N_{2} - 2\\right) - 1}",
+               "SD_{p} = \\sqrt \\frac{\\left( N_{1}-1 \\right)SD_{1}^2 + \\left( N_{2}-1 \\right)SD_{2}^2}{N_{1} + N_{2} - 2}")
+
 # Note: It is esssential that you be clear that the function 'compose' is exported from the flextable package. That's because purr also has the same function, so it gets messy.
@@
           flextable::width(j = 2, 2) %>% 
-          flextable::width(j = 4, 5)
+          flextable::width(j = 4, 5) %>% 
+          flextable::footnote(i = 4, j = 1, value = as_paragraph(as_equation(footnotes)),
+               ref_symbols = c("a"),
+               part = "body", inline = TRUE)
 
@@
 
-While heterogenity estimates using $I^2$ measures can be useful for understanding the relative contributions of different factors to effect size variation, prediction intervals might be more appropriate in many cases [@Nakagawa2021c; @Borenstein2019].
-Unlike $I^2$, prediction intervals are more holistic and probably more meaningful in the context of meta-analysis.
-Prediction intervals make use of the standard deviation of the mean instead of the standard error (which is used to calculate confidence intervals) [@Borenstein2019].
+Heterogenity described using $I^2$ measures can be useful for understanding the relative contributions of different factors to effect size variation, however, prediction intervals might be more appropriate in many cases [@Nakagawa2021c; @Borenstein2019].
+Unlike $I^2$, prediction intervals (PI's) are probably more meaningful in the context of meta-analysis because they explicitly incorperate measures of dispersion around a mean effect size providing information about the likely effect size one can expect if we were to randomly sample a new population.
+For example, assume that we were interested in the overall impact of salinity stress in freshwater fish.
+To tackle this question, we collected experimental studies measuring freshwater fish swim performance under high salinity treatments (~15-20ppm NaCl) compared to freshwater (~0ppm NaCl) controls and used SMD to quantify the magnitude of effect salinity had on swim performance.
+We conduct a meta-analysis and estimate an overall SMD of 0.50 with a prediction interval of 0.05 to 0.85.
+The PI indicates that effects can vary widely from as low as an SMD of 0.05 to as high as an SMD 0.95, depending on the population.
+In otherwords, if we were to repeat a study we would expect a new effect to fall within the range of 0.05 and 0.85, 95\% of the time [@Borenstein2019; @Nakagawa2021c].
+This is a very intutive interprettaion of how variable effects are, yet PIs are often not reported in meta-analyses [@Nakagawa2021c].
 

### 2021-07-08 MS/ms.Rmd
Added sampling variance eqn from Nakagawa and Santos.

@@
 where $\sigma^2_{total} = \sigma^2_{study} + \sigma^2_{phylogeny} + \sigma^2_{species} + \sigma^2_{residual} +\sigma^2_{m}$ is the total effect size variance  and $\sigma^2_{m}$ is the sampling error variance calculated as:
+
+$$
+\sigma_{m}^2 = \sum w_{j}\left( k-1\right) / \left[ \left( \sum w_{j}\right)^2  + \sum w_{j}^2\right]
 $$
 
-$$
+where *k* is the number of studies and the weights, $w_{j} = \frac{1}{v_{j}}$, can be calcualted as the inverse of the sampling variance ($v_{j}$) for each effect size, *j*.
+
 Quantifying heterogeneity using $I_{total}^2$ provides a formal way to assess the relative amount of variation that is the result of 'true' biological or methodological differences as opposed to simply chance (i.e., sampling variance) [@NakagawaSantos2012; @Higgins2002].
@@
 Formally quantifying and presenting heterogeneity estimates from meta-analytic models can provide a way to understand the major drivers of effect size variation by allowing researchers to produce various $I^2$ estimates which can be formally compared within and across studies.
-For example, we could fit the multilevel model described above to understand what proportion of variation is the result of, say, 'study' effects following @NakagawaSantos2012: $I^2_{study} = \frac{\sigma^2_{study}}{\sigma^2_{total}}$ where $\sigma^2_{study}$ is the study specific variance, and all other variance components are for phylogeny, species, residual (effect size level) and m (total measurement/sampling error).
+For example, we could fit the multilevel model described above to understand what proportion of variation is the result of, say, 'study' effects following @NakagawaSantos2012: $I^2_{study} = \frac{\sigma^2_{study}}{\sigma^2_{total}}$ where $\sigma^2_{study}$ is the study specific variance.
+
 Many readers will notice the similarities between $I^2$ and $R^2$ [@Nakgawa2013; @Nakagawa2010].

### 2021-07-08 MS/ms.Rmd
Small changes to opening sentences

@@
 The goal of our review is to briefly overview the process of meta-analysis, making a case for why heterogenity in a meta-analysis is a good thing for answering fundamental reserch problems and guiding research directions.
-We introduce the idea of 'nuisance heterogenity', showing comparative physiologists that it can be comfortably dealt with be re-formalising many existing effect sizes measures and/or by using multilevel meta-regression models.
+We introduce the idea of 'nuisance heterogenity', showing comparative physiologists that it can be comfortably dealt with by re-formalising many existing effect sizes measures and/or by using multilevel meta-regression models.
 Indeed, a combination of these approaches might often be ideal.
-We first conduct a survey of published meta-analyses in the field of comparative physiology to gauge methodological and meta-analytic practices -- assessing what types of effect sizes are commonly used, how often effect size estimates are impacted by continuous treatment differences and whether meta-analytic models (i.e., models that account for sampling variance) are commonly applied.
+We first conduct a survey of published meta-analyses in the field of comparative physiology to gauge methodological and meta-analytic practices -- determining what types of effect sizes are commonly used, how often effect size estimates are impacted by 'nuisance heterogeneity' and whether meta-analytic models (i.e., models that account for sampling variance) are commonly applied.
 We then formalise alternative effect sizes and their associated sampling variance to provide comparative physiologists opportunities to explicitly incorporate treatment differences into the effect size estimates to ease their interpretation.
@@
 
-where $CV$ is the coefficient of variation defined as $SD / R$. Whether one choose to use SD or CV-based effect size depends on questions at hand [discussed in @Nakagawa2015 and @Senior2020].
+where $CV$ is the coefficient of variation defined as $SD / R$. Whether one choose to use SD or CV-based effect size depends on questions at hand [See @Nakagawa2015; @Senior2020].
 
@@
 $$
-\sigma_{m}^2 = \sum w_{j}\left( k-1\right) / \left[ \left( \sum w_{j}\right)^2  + \sum w_{j}^2\right]
+\sigma_{m}^2 = \sum w_{i}\left( k-1\right) / \left[ \left( \sum w_{i}\right)^2  + \sum w_{i}^2\right]
 $$
 
-where *k* is the number of studies and the weights, $w_{j} = \frac{1}{v_{j}}$, can be calcualted as the inverse of the sampling variance ($v_{j}$) for each effect size, *j*.
+where *k* is the number of studies and the weights, $w_{i} = \frac{1}{v_{i}}$, can be calcualted as the inverse of the sampling variance ($v_{i}$) for each effect size, *i*.
 

### 2021-07-08 MS/ms.Rmd
Rendered word. Table messed up as expected, but should be easy to fix.

@@
 output: 
+  bookdown::word_document2:
+    toc: no
+    toc_depth: 6
+    number_sections: false
+    reference_docx: template.docx
   bookdown::html_document2:
@@
     bibliography: refs.bib
-  bookdown::word_document2:
-    toc: no
-    toc_depth: 6
-    number_sections: false
-    reference_docx: template.docx
 editor_options: 

### 2021-07-09 MS/ms.Rmd
adding a box (not done yet)

@@
 The validity of general conclusions to certain questions (e.g., what is the overall effect of a pollutant on reproduction?) will inevitably depend on the homogeneity of effects being synthesized.
-If the estimate of an overall effect coincides with low heterogenity estimates then the effects are reasonably consistent [@Borenstein2019].
-If, however, an overall effect is accompanied by large heterogenity estimates, then we would shift focus and explore drivers of that heterogeneity.
+If the estimate of an overall effect coincides with low heterogeneity estimates then the effects are reasonably consistent [@Borenstein2019].
+If, however, an overall effect is accompanied by large heterogeneity estimates, then we would shift focus and explore drivers of that heterogeneity.
 For example, given the very different physiology of aquatic mammals and fish, understanding an overall combined effect on reproduction may not be particularly relevant, and indeed may be misleading.
-Therefore, understanding overall effects in each of these groups seperately (and whether they differ) will be more useful.
+Therefore, understanding overall effects in each of these groups separately (and whether they differ) will be more useful.
 It is important to consider these questions when conducting meta-analyses.
@@
 
-#### *Comparing Changes in Mean Physiological Rates, $Q_{10}$*
+#### *Comparing Changes in Mean Physiological Rates,* $Q_{10}$
+
 A very common occurrence in comparative physiology is to manipulate the temperature organisms experience and measure some physiological rate (e.g., metabolic rate).
@@
 \end{equation} 
-$$ 
-$$
+$$ $$
 \begin{equation} 
@@
 If the heterogeneity is high as a result of, say, dosages differences, then it is clear that the choice of dosage within and across studies will have a critical impact on the effect of interest.
-Comparative physiologists intersted in implementing thse calculations can do so using our packages `orchaRd` [@Nakagawa2021c] or `metaAidR` (https://github.com/daniel1noble/metaAidR).
+Comparative physiologists intersted in implementing thse calculations can do so using our packages `orchaRd` [@Nakagawa2021c] or `metaAidR` (<https://github.com/daniel1noble/metaAidR>).
 
@@
 For example, assume that we were interested in the overall impact of salinity stress in freshwater fish.
-To tackle this question, we collected experimental studies measuring freshwater fish swim performance under high salinity treatments (~15-20ppm NaCl) compared to freshwater (~0ppm NaCl) controls and used SMD to quantify the magnitude of effect salinity had on swim performance.
+To tackle this question, we collected experimental studies measuring freshwater fish swim performance under high salinity treatments (\~15-20ppm NaCl) compared to freshwater (\~0ppm NaCl) controls and used SMD to quantify the magnitude of effect salinity had on swim performance.
 We conduct a meta-analysis and estimate an overall SMD of 0.50 with a prediction interval of 0.05 to 0.85.
 The PI indicates that effects can vary widely from as low as an SMD of 0.05 to as high as an SMD 0.95, depending on the population.
-In otherwords, if we were to repeat a study we would expect a new effect to fall within the range of 0.05 and 0.85, 95\% of the time [@Borenstein2019; @Nakagawa2021c].
+In otherwords, if we were to repeat a study we would expect a new effect to fall within the range of 0.05 and 0.85, 95% of the time [@Borenstein2019; @Nakagawa2021c].
 This is a very intutive interprettaion of how variable effects are, yet PIs are often not reported in meta-analyses [@Nakagawa2021c].
@@
 ## **Conclusions and Future Directions**
+
 Comparative physiologists are interested in meta-analysing effects across a diversity of species, experimental approaches / designs and environments.

### 2021-07-09 MS/ms.Rmd
Finished off text. Corrected spelling. Need to add survey and do supplement and first draft should be ready

--- 2021-07-08 MS/ms.Rmd
@@
 By expressing study effects on a common scale (i.e., standardised effect size) a meta-analyst can gain broader insight into the direction and efficacy of a particular treatment effect or the strength of a relationship between two variables of interest [@Gurevitch2018; @Koricheva2013].
-Quantitative syntheses, including meta-analyses, have provided comparative physiologists with powerful insights on pressing global challenges - from testing whether physiological plasticity can buffer organisms against climate change [e.g, @Seebacher2015] to the degree to which endocrine disrupting chemicals, such as bisphenol A (BPA), impact aquatic organisms [e.g., @WuSeebacher2020].
+Quantitative syntheses, including meta-analyses, have provided comparative physiologists with powerful insights on pressing global challenges - from testing whether physiological plasticity can buffer organisms against climate change [e.g, @Seebacher2015] to the degree to which endocrine disrupting chemicals, such as bis-phenol A (BPA), impact aquatic organisms [e.g., @WuSeebacher2020].
 
@@
 For example, experimental designs can vary in the temperatures that they apply or in the dosages of chemical modifiers used in experimental treatments [e.g., @WuSeebacher2020].
-To the uninitiated, this concern might not be unfounded given that heterogenity in effects is often high in ecological and evolutionary meta-analyses [@Senior2016], telling us that the effect size varies a great deal from one population to another.
+To the uninitiated, this concern might not be unfounded given that heterogeneity in effects is often high in ecological and evolutionary meta-analyses [@Senior2016], telling us that the effect size varies a great deal from one population to another.
 However, to many, the very fact that highly heterogeneous effects exist is a core strength of meta-analysis [@Cooperetal2019; @Borenstein2019; @Gurevitch2018; @Glass2015].
@@
 
-The goal of our review is to briefly overview the process of meta-analysis, making a case for why heterogenity in a meta-analysis is a good thing for answering fundamental reserch problems and guiding research directions.
-We introduce the idea of 'nuisance heterogenity', showing comparative physiologists that it can be comfortably dealt with by re-formalising many existing effect sizes measures and/or by using multilevel meta-regression models.
+The goal of our review is to briefly overview the process of meta-analysis, making a case for why heterogeneity in a meta-analysis is a good thing for answering fundamental research problems and guiding research directions.
+We introduce the idea of 'nuisance heterogeneity', showing comparative physiologists that it can be comfortably dealt with by re-formalising many existing effect sizes measures and/or by using multilevel meta-regression models.
 Indeed, a combination of these approaches might often be ideal.
@@
 How many independent samples we collect impacts our precision in estimating this 'true' effect [@Borenstein2019].
-In meta-analysis we formally include sampling variance to remove this source of heterogeneity directly -- hence why having sampling variances for an effect is so important [@Gurevitch2018; @Koricheva2013].
+In meta-analysis we formally include sampling variance to remove this source of heterogeneity directly because it is known -- hence why having sampling variances for an effect is so important [@Gurevitch2018; @Koricheva2013].
 Second, there are sociological factors impacting heterogeneity.
@@
 We can model these biological factors to test predictions from hypotheses that we believe are key players impacting mean effect size and direction.
-This improves our understanding of the biological world around us, and helps inform on future research directions.
+This improves our understanding of the biological world around us and helps inform on future research directions.
 Finally, methodological factors are also big contributors to effect variability.
@@
 In other cases, methodological factors might be considered 'nuisance heterogeneity' [following from @Cooperetal2019] -- factors we know vary, but are rather unsurprising to us.
-These can include differences in temperature, pH, dosages, water potential etc.
-The factors are obviously going to vary and have an impact on the magnitude of an effect, but they might distract from the core interest.
-In some cases, however, these factors might actually not be 'nuisance' variables but rather the main interest of a synthesis.
+These might include differences in temperature, pH, dosages, water potential etc.
+It might already be clear that these factors will have an impact on the magnitude of an effect, but they might distract from the core interest of a meta-analysis.
+In some cases, however, the latter factors might actually not be 'nuisance' variables but the main interest of a synthesis.
 However, in many cases they can result in a more complicated interpretation of an effect measure then what is desired.
@@
 However, many argue that this is just what we are interested in synthesizing [@Cooperetal2019; @Borenstein2019; @Gurevitch2018; @Glass2015].
-In the words of Gene Glass, the father of meta-analysis: "Of course it mixes apples and oranges; in the study of fruit nothing else is sensible; comparing apples and oranges is the only endeavor worthy of true scientists; comparing apples to apples is trivial" [p.g., 224, @Glass2015].
-@Glass2015's intention was to simply highlight that whether comparing apples and oranges is a good idea simply boils down to the specific question of interest, the population one wishes to make conclusions about and how hetergenous effects actually are.
+In the words of Gene Glass, the father of meta-analysis: "Of course it [meta-analysis] mixes apples and oranges; in the study of fruit nothing else is sensible; comparing apples and oranges is the only endeavor worthy of true scientists; comparing apples to apples is trivial" [p.g., 224, @Glass2015].
+@Glass2015's intention was to simply highlight that whether comparing apples and oranges is a good idea simply boils down to the specific question of interest, the population one wishes to make conclusions about and how heterogeneous effects actually are.
 If we are interested in gaining insight into 'fruit' then synthesising apples and oranges is the only thing that makes sense.
@@
 In other words, if we compare different types of 'apples' is it still fair to synthesize these studies to understand overall effects?
-This situation might be analogous to a meta-analysis in comparative physiology that attempts to understand the effects of dietary on fish growth across different populations of a widely distributed (cosmopolitan) species.
+This situation might be analogous to a meta-analysis in comparative physiology that attempts to understand the effects of diet on fish growth across different populations of a widely distributed (cosmopolitan) species.
 Studies might rear populations of fish under different temperatures, but in the end, they are still all the same fish species, governed by the same thermodynamic effects on growth.
@@
 If, however, it is less interesting, than say the diet administered, then it may introduce an unnecessary complication to the interpretation of the effect(s) of interest.
+Here, we focus on meta-analytic tools to circumvent these issues and demonstrate that the 'apples and oranges' problem is not really a problem at all.
 
@@
 
+Before embarking on "meta-analytic enlightenment" it is worth first understanding how comparative physiologists are currently conducting meta-analyses / comparative analysis.
 As discussed above, different types of questions and experimental approaches will mix 'apples and oranges' to varying extents, and indeed, this heterogeneity (or basket of fruit) is often the main interest to comparative biologists.
@@
 We were specifically interested in asking: 1) what type of effect size was used within the quantitative synthesis?
-2) based on the methods provided, was the effect size likely susceptible to continuous variation in how treatments were applied (e.g., for contrast-based effects) or the conditions under which traits were measured (i.e., for correlations) across studies?
-3) If so, was the variation resulting from treatment differences accounted for in the effect size or during analysis?, and finally, 4) how were effect sizes analysed in the quantitative synthesis, were these weighted analyses, and what program was used for analysis?
-We also recorded whether publication bias and sensitivity analyses were conducted, if data were publicly available, where it was stored, and if so, if it was usable (i.e., in a machine readable format).
+2) based on the methods provided, was the effect size likely susceptible to continuous variation in how treatments were applied (e.g., for contrast-based effects) or the conditions under which traits were measured (i.e., for correlations) across studies (i.e., 'nuisance heterogeneity')?
+3) If so, was the variation accounted for in the effect size or during analysis?, and finally, 4) how were effect sizes analysed in the quantitative synthesis, were these weighted analyses, and what program was used for analysis?
+We collected additional
 
@@
 Briefly, we first did a series of pilot searches (detailed in Supplementary Materials) to refine our search query [See @Foo2021 for an overview of this process].
-We searched for studies that included: 'meta-analysis', 'meta regression' , 'comparative analysis', 'comprehensive analysis' 'global analysis' or 'macro physiology' in their title and abstract, restricting our search to key comparative physiology journals (detailed in Table X - Supplementary Materials) within the last 6 years.
+We searched for studies that included: 'meta-analysis', 'meta regression' , 'comparative analysis', 'comprehensive analysis' 'global analysis' or 'macro physiology' in their title and abstract, restricting our search to key comparative physiology journals (detailed in Table S1 and S2 - Supplementary Materials) within the last 6 years.
 We expected this to provide a contemporary overview of quantitative syntheses in comparative physiology while making the survey and screening feasible.
@@
 There were also meta-analyses that focused on colour evolution and contrast which varied in their goals but were most often not focused on physiological questions.
-As such, these studies were also exclude.
+As such, these studies were also excluded.
 We restricted our focus to animal studies because plant synthesis papers were often only focused on ecological (e.g., quantified changes in abundance and distribution of species) or agricultural questions (e.g., studies on soil microbial function, nitrogen and phosphorus capture, methane output and greenhouse gas emissions).
@@
 Given the high heterogeneity in effects used in comparative physiology, we expected this to be common to most effect sizes, however, it has not been formally quantified.
-We categorised the types of staitsical models fit in each study as: 1) fixed-effect meta-analysis; 2) random effects meta-analysis (i.e., intercept only model, but has random study effects); 3) multi-level meta-analysis (i.e., intercept only model, but has multiple random effect levels such as study, species, observation-level random effects); 4) meta-regression models (i.e., a multilevel or random effect model with fixed effects - including random effects); 5) weighted regression models, inluding mixed effect models; and 6) linear regression models (including linear and generalised linear mixed effect models, and phylogenetic least squares models).
+We categorised the types of statistical models fit in each study as: 1) fixed-effect meta-analysis; 2) random effects meta-analysis (i.e., intercept only model, but has random study effects); 3) multi-level meta-analysis (i.e., intercept only model, but has multiple random effect levels such as study, species, observation-level random effects); 4) meta-regression models (i.e., a multilevel or random effect model with fixed effects - including random effects); 5) weighted regression models, including mixed effect models; and 6) linear regression models (including linear and generalised linear mixed effect models, and phylogenetic least squares models).
 Notably, only model types 1-5 are weighted models.
@@
 
-## **Opening Up New Opportunities in Comparative Physiology: Expanding the Breadth of Effect Sizes to Deal with "Nuisiance Heterogenity"**
+## **Opening Up New Opportunities in Comparative Physiology: Expanding the Breadth of Effect Sizes to Deal with "Nuisance Heterogeneity"**
 
@@
 
-As is clear from Table \@ref(tab:tablea) none of the effect measures control for 'nusance heterogenity'.
-For example, the magnitude of response between two treatment groups for lnRR or SMD might depend on just how different the tempeartures, dosages, pH or water potential applied in each treatment.
-Even modelling just the mean often needs to account for 'nusance heterogenity'.
-For example, standard metabolic rate (SMR) is tempearture dependent.
-As such, one needs to standardise the temperature measurement to compare across studies [@White2006; @Uyeda2017, if, of course, temperature is not of interest in of itself].
-While we could of course model this explictly, this may not always be desireable.
+As is clear from Table \@ref(tab:tablea) none of the effect measures control for 'nuisance heterogeneity'.
+For example, the magnitude of response between two treatment groups for lnRR or SMD might depend on just how different the temperatures, dosages, pH or water potential applied in each treatment.
+Even modelling just the mean often needs to control for various sources of 'nuisance heterogeneity'.
+For example, standard metabolic rate (SMR) is temperature dependent.
+As such, one needs to standardise the temperature measurement to compare across studies [@White2006; @Uyeda2017] (if, of course, temperature is not of interest in of itself).
+While we could of course model this explicitly, this may not always be desirable.
 It can often be useful to standardise the effect to both ease its interpretation and simplify modelling.
@@
 We highlight two examples in the box focusing mainly on generality.
-Below, we show using a common well understood effect measure of interest to comparative physiologys, $Q_{10}$ how we can formalise a common effect size measure $lnRR$ to capture this 'nusance variation'.
+Below, we show using a common, well understood effect measure of interest to comparative physiology, $Q_{10}$ how we can formalise a traditional effect sizes', such as $lnRR$, to capture this 'nuisance variation'.
 
@@
 A very common occurrence in comparative physiology is to manipulate the temperature organisms experience and measure some physiological rate (e.g., metabolic rate).
-Using normal effect size measures (see above) would result in the effect sizes varying in the types of temperatures applied within and across across studies contributing to 'comparability' issues.
+Using normal effect size measures (see Table \@ref(tab:tablea)) would result in the effect sizes varying in the types of temperatures applied within and across across studies contributing to 'comparability' issues.
 As such, it is often of interest to standardize effects by temperature.
@@
 a physiological rate, mass etc) so long as the measurement variable is ratio scale.
-Log transformation of this ratio makes the effect size normally distributed.
-<!--- use consistent notations in relation to the table - do you want to put i or not - then you need to put i throughout ---> Equation \@ref(eq:slnRR) is the analytical solution for *lnRR*'s sampling variance where, $SD_{1}^2$ and $SD_{2}^2$ is the sample variance in group 1 and 2, respectively and $N_{1}$ and $N_{2}$ is the sample size in group 1 and 2.
+Log transformation of this ratio makes the effect size normally distributed (most commonly assumed by meta-analytic models).
+Equation \@ref(eq:slnRR) is the analytical solution for *lnRR*'s sampling variance where, $SD_{1}^2$ and $SD_{2}^2$ is the sample variance in group 1 and 2, respectively and $N_{1}$ and $N_{2}$ is the sample size in group 1 and 2.
 
@@
 \end{equation} 
-$$ Equation \@ref(eq:lnq10) is essentially a temperature corrected equivalent to lnRR when the numerator and denominator are measured at different temperatures.
+$$ Equation \@ref(eq:lnq10) is essentially a temperature corrected equivalent of lnRR when the numerator and denominator are measured at different temperatures.
 This allows one to compare the mean of two temperature treatments directly regardless of the temperatures that these groups have been measured.
 Here, we will refer to this as the log $Q_{10}$ response ratio, $lnRR_{Q_{10}}$.
-Notably, by taking the natural logarithm, there are two statistical advantages: 1) 0 becomes biological meaningful as 0 means two rates are the exactly the same and 'statistically significantly different from 0' means that two rates are significantly different to each other and 2) $lnRR_{Q_{10}}$ is more likely to satisfy the assumption of residual normality than $Q_{10}$ (see @Hedges1999).
-Also, the recognition of this equivalence means that we can easily calculate the sampling variance for equation \@ref(eq:lnq10) as follows:
+Notably, by taking the natural logarithm, there are two statistical advantages: 1) 0 becomes biological meaningful as 0 means two rates are the exactly the same and 'significantly different from 0' means that two rates are significantly different to each other and 2) $lnRR_{Q_{10}}$ is more likely to satisfy the assumption of residual normality than $Q_{10}$ (see @Hedges1999).
+The recognition of this equivalence means that we can easily calculate the sampling variance for equation \@ref(eq:lnq10) as follows:
 
@@
 
-#### *Formalising Effect Size Metrics that Compare Changes in Variability Across Treatments in the Presence of "Nuisance Heterogenity"*
+#### *Formalising Effect Size Metrics that Compare Changes in Variability Across Treatments in the Presence of "Nuisance Heterogeneity"*
 
@@
 
-Our example using $Q_{10}$, a well known effect measure in comparative physiology, shows how common effect size measures can be re-formalised to account for 'nuisance hetreogenity', in this case temperature.
-We can apply similar approaches to other commonly used effect size metrics.
+Our example using $Q_{10}$, a well known effect measure in comparative physiology, shows how common effect size's can be re-formalised to account for 'nuisance heterogeneity', in this case temperature.
+Of course, in doing this we are making assumptions about the nature of temperature effects on an effect size.
+Nonetheless, we can apply similar approaches to other commonly used effect size metrics.
 We describe more generally how this can be done in Box 1, applying similar principles to standardise temperature differences for slopes and for standardised mean differences.
@@
 For example, dosages applied to treatments can follow quite complex non-linear relationships (e.g., quadratic relationships) in relation to some mean response.
-When this occurs we recommend comparative physiologists apply meta-regression approaches, controlling for 'these known treatment differences 'nusiance heterogenity' as a moderator.
-In many cases, this will be the easiest, or even preferred approach because exploring drivers of heterogenity will be the main interest in most meta-analyses.
-Nonetheless, there are some simple statistical approaches a meta-analyst can use to then make the overall effects interpretable, allowing one to control for 'nuisance heterogenity', while also allowing other biological moderators of interest to be tested [@Schielzeth2010].
-Before diving into meta-regression models, we will first overview the meta-analytic approaches or steps commonly used.
+When this occurs we recommend comparative physiologists apply meta-regression approaches, controlling for 'nuisance heterogeneity' as a moderator.
+In many cases, this will be the easiest, or even preferred approach because exploring drivers of heterogeneity will be the main interest in most meta-analyses anyway.
+Nonetheless, there are some simple statistical approaches a meta-analyst can use to then make the overall effects more easily interpretable, allowing one to control for 'nuisance heterogeneity', while also testing other biological moderators of interest [@Schielzeth2010].
+Before diving into meta-regression models, we will first overview the meta-analytic models commonly used.
 
@@
 
-One of the main goals of meta-analysis is to obtain an overall meta-analytic mean effect size estimate and some form of uncertainty around that mean, like a 95% confidence interval (CI).
-Including a prediction interval (PI) can also be quite useful because, in the context of a meta-analysis, it provides the range of effect size values we might expect to observe if a new study were to be conducted [@Nakagawa2021c].
-Estimating an overall mean along with 95% CI (or PI) is generally done with a simple random effects or multilevel meta-analytic model that accounts for effect size sampling error [@Nakagawa2017; @NakagawaSantos2012].
+A common goal of meta-analysis is to obtain an overall meta-analytic mean effect size estimate and some form of uncertainty around that mean, like a 95% confidence interval (CI).
+Including a prediction interval (PI) can also be quite useful (see below for why) [@Nakagawa2021c].
+Estimating an overall mean and 95% CI is generally done with a simple random effects or multilevel meta-analytic model that accounts for effect size sampling error [@Nakagawa2017; @NakagawaSantos2012].
 More often than not, meta-analyses in comparative physiology will have complex hierarchical structure.
-For example, multiple effect sizes may be taken from a single study on different traits measured on the same individuals, or come from many different species that share an evolutionary history [@Noble2017].
-As such, it is far more likely that comparative physiologists will need to apply a multi-level meta-analytic model to control for the various sources of non-independence [@NakagawaSantos2012; @Song2021; @Nakagawa2021; @Noble2017].
-Multilevel models are also extremely useful in describing the various sources contributing to effect size variance.
-For the purpose of our discussion, we will assume the meta-analyst plans to use more advanced multilevel models.
-Having said that, it maybe sufficient for many meta-analyses to make use of traditional random effects models.
+For example, multiple effect sizes may be taken from a single study on different traits measured on the same individuals, or come from many different species that share an evolutionary history [@Cinar2021; @Noble2017].
+As such, it is far more likely that comparative physiologists will need to apply a multi-level meta-analytic model to control for the various sources of non-independence, and whenever possible they should [@Cinar2021; @NakagawaSantos2012; @Song2021; @Nakagawa2021; @Noble2017].
+Multilevel models are also extremely useful in describing the various sources contributing to effect size variance (a feature we describe below).
+For the purpose of our discussion, we will assume the meta-analyst needs to use more advanced multilevel models.
+Having said that, it maybe sufficient for a meta-analysis to make use of traditional random effects models.
 We refer readers to excellent reviews and books that overview the distinctions between common (fixed) effect, random effect and multilevel models and when one might want (or not want) to apply these models [@Nakagawa2017; @NakagawaSantos2012; @Koricheva2013; @Borenstein2009; @Schmid2021].
@@
 Of course, these studies are diverse, apply different dosages of corticosterone and are working across many species.
-If the studies are experimental in nature, than a standardised effect size, such as $ln_{RR}$ or Hedges' *d* might be applicable.
-We then might fit an overall, multilevel meta-analytic model as follows:
+If the studies are experimental in nature than a standardised effect size, such as $ln_{RR}$ or Hedges' *d*, might be applicable.
+We then might fit an overall multilevel meta-analytic model as follows:
 $$
@@
 \begin{equation} 
-a_{k[i]}\sim N(0, \sigma^{2}_{phylogeny}A),\
-sp_{k[i]}\sim N(0, \sigma^{2}_{species}I),\
-s_{j[i]}\sim N(0, \sigma^{2}_{study}I),\
-e_{i}\sim N(0, \sigma^{2}_{residual}I),\
+a_{k[i]}\sim N(0, \sigma^{2}_{phylogeny}\textbf{A}),\
+sp_{k[i]}\sim N(0, \sigma^{2}_{species}\textbf{I}),\
+s_{j[i]}\sim N(0, \sigma^{2}_{study}\textbf{I}),\
+e_{i}\sim N(0, \sigma^{2}_{residual}\textbf{I}),\
 m_{i} \sim N(0, v_{i})\
@@
 
-<!--- you can use ni instead of spi???
-- also refer to this paper in this seciton which really justify or even nessates people using this rather complext model and having a and sp are rather crtical!
-- https://ecoevorxiv.org/su4zv/--->
-
 where $Y_{i}$ is the *i*th effect size (*i* = 1 ...
 $N_{ES}$, the number of effect sizes), $\beta_{0}$ is the overall meta-analytic mean, $a_{k[i]}$ is the phylogenetic effect (a random effect) for species *k* applied to effect size *i*.
-Phylogenetic effects are assumed to be normally distributed deviates sampled from a distribution with a mean of 0 and variance $\sigma^{2}_{phylogeny}$ [i.e., *N*$(0, \sigma^{2}_{phylogeny}A)$], where A is a phylogenetic correlation matrix derived from a phylogenetic tree, $sp_{k[i]}$ is the species-specific effect for the *k*th species applied to effect size *i*, $s_{j[i]}$ is the study-specific effect for the *j*th study applied to effect size *i*, $e_{i}$ is the effect size-specific effect (or within study effect, or residuals) for the *i*th effect size, and $m_{i}$ is the sampling variance effect around the *i*th effect as a result of variation in precision among each effect sizes, $v_{i}$, which is known as the sampling variance for effect.
+Phylogenetic effects are assumed to be normally distributed deviates sampled from a distribution with a mean of 0 and variance $\sigma^{2}_{phylogeny}$ [i.e., *N*$(0, \sigma^{2}_{phylogeny}\textbf{A})$], where $\textbf{A}$ is a phylogenetic correlation matrix derived from a phylogenetic tree, $sp_{k[i]}$ is the species-specific effect for the *k*th species applied to effect size *i*, $s_{j[i]}$ is the study-specific effect for the *j*th study applied to effect size *i*, $e_{i}$ is the effect size-specific effect (or within study effect, or residuals) for the *i*th effect size, and $m_{i}$ is the sampling variance effect around the *i*th effect as a result of variation in precision among each effect sizes, $v_{i}$, which is known as the sampling variance for effect.
 This model is a 'weighted' multilevel meta-analysis model because the estimation of the overall meta-analytic mean, $\beta_{0}$, is weighted by the inverse sampling variance of each effect size.
@@
 
-Heterogeneity among effects that result from known differences in how treatments are applied can also be dealt with using multilevel meta-regression models.
+Heterogeneity among effects that result from 'nuisance heterogeneity' can be dealt with using multilevel meta-regression models.
 Multilevel meta-regression models include all the same random effects that we have already discussed, but they also include fixed effects (i.e., predictors or moderators) that attempt to explain changes in the mean effect size.
-In other words, we can modify our multilevel meta-analytic model to turn it into a multilevel meta-regression model as follows:
+In other words, we can modify our multilevel meta-analytic model and turn it into a multilevel meta-regression model as follows:
 
-$$ Y_{i} = \beta_{0} + \sum \beta_{j}x_{j} + a_{k[i]} + sp_{k[i]} + s_{j[i]} + e_{i} + m_{i} $$ where $\sum \beta_{j}x_{j}$ is simply the sum of all effects for all moderators (fixed effects), $x_{j}$.
+$$ Y_{i} = \beta_{0} + \sum \beta_{j}x_{j} + a_{k[i]} + sp_{k[i]} + s_{j[i]} + e_{i} + m_{i} $$
+
+where $\sum \beta_{j}x_{j}$ is simply the sum of all effects for all moderators (fixed effects), $x_{j}$.
 All other notation is the same as described above.
@@
 Of course, this interpretation does not make much sense.
+
 We can, however, apply some simple transformations to make the overall mean estimate more intuitive to understand with the added benefit that it can help improve the interpretation of non-linear parameters estimated by the model [@Schielzeth2010; @GelmanHill2007].
 One simple transformation would be to centre the variable $x_{j}$, by subtracting each value from the mean to create a new input variable (i.e., $c_{i}=x_{i}-\bar{x}$, where the subscript *i* denotes each individual effect size dosage).
-The new variable, $c_{j}$, is now centered on the mean and can replace $x_{j}$.
+The new variable, $c_{j}$, is now centered on the mean and can replace $x_{j}$ in the meta-regression model.
 When the model is refit with $c_{j}$ the estimated $\beta_{0}$ can now be more intuitively interpreted as the overall mean effect of CORT on reproduction at an average dosage difference between treatment and control groups.
-Importantly, by centering, we retain the original units (uL / g) of the variable, which can be very useful to allow for a more general interpretation of the effect magnitude.
+Importantly, by centering, we retain the original units (uL / g) of the variable, which can be very useful to allow for a more general interpretation of the effect magnitude (e.g., when the dosage different in 10 uL /g).
+This approach can even be extended to include other 'nuisance' variables that might creep into the dataset; the same centering can be done and the overall mean adjusted to include the new variable, in additional to dosage.
 Of course, if one is not interested in the magnitude of effect, we could also change our question and simply model mean reproductive output as a function of dosage (often what are referred to as 'arm-based' meta-analytic models).
@@
 
-Centering moderator variables, like temperature and dosage, not only provides a way to make the overall mean effect more interpretable in the face of treatment heterogeneity, but it also allows more complex relationships to be fit without compromising interpretations, including non-linear parameters and interactions (e.g., polynomials).
+Centering moderator variables, like temperature and dosage, not only provides a way to make the overall mean effect more interpretable in the face of treatment heterogeneity, but it also allows more complex relationships to be fit without compromising interpretations, such as when one includes non-linear parameters (e.g., polynomials) and interactions with other variables.
 In other words, linear / main effects can still be interpreted normally in the presence of non-linear / interactions fit in the model [@Schielzeth2010; @GelmanHill2007].
-This can be particularly powerful when more complex, nonlinear, dosage relationships exist.
 We provide examples in the online supplementary material (with R code) to show readers how the models we describe above can be fit, and how, meta-analytic means can be adjusted for treatment heterogeneity.
 
-#### *Heterogenity Analysis: How Much Effect Size Variation Actually Exists?*
+#### *Heterogeneity Analysis: How Much Effect Size Variation Actually Exists?*
 
-Quantifying effect size heterogeneity (i.e., effect size variance) provides the impetus for exploring hypotheses that are thought to explain why effects might vary within and across studies, while also providing context for interpreting the generality of effects.
-There are a number of measures commonly used to quantify effect size heterogenity [@Borenstein2019], however, in ecological and evolutionary meta-analysis, heterogeneity is often calculated and reported as $I_{total}^2$ as follows (if using a multilevel meta-analytic model as we describe above):
+As we have already emphasised, quantifying effect size heterogeneity (i.e., effect size variance) provides the impetus for exploring hypotheses that are thought to explain why effects might vary within and across studies, while also providing context for interpreting the generality of effects.
+There are a number of measures commonly used to quantify effect size heterogeneity [@Borenstein2019], however, in ecological and evolutionary meta-analysis, heterogeneity is often calculated and reported as $I_{total}^2$ as follows (if using a multilevel meta-analytic model as we describe above):
 
@@
 
-<!--- be consistent with sigma notations above - actually total - m may sometimes not work - so best adding up all like this, which was the core finding in Nakagawa & Schielzeth's R2 --->
-
-where $\sigma^2_{total} = \sigma^2_{study} + \sigma^2_{phylogeny} + \sigma^2_{species} + \sigma^2_{residual} +\sigma^2_{m}$ is the total effect size variance  and $\sigma^2_{m}$ is the sampling error variance calculated as:
+where $\sigma^2_{total} = \sigma^2_{study} + \sigma^2_{phylogeny} + \sigma^2_{species} + \sigma^2_{residual} +\sigma^2_{m}$ is the total effect size variance and $\sigma^2_{m}$ is the total sampling error variance calculated as:
 
@@
 
-where *k* is the number of studies and the weights, $w_{i} = \frac{1}{v_{i}}$, can be calcualted as the inverse of the sampling variance ($v_{i}$) for each effect size, *i*.
+where *k* is the number of studies and the weights, $w_{i} = \frac{1}{v_{i}}$, can be calculated as the inverse of the sampling variance ($v_{i}$) for each effect size, *i*.
 
 Quantifying heterogeneity using $I_{total}^2$ provides a formal way to assess the relative amount of variation that is the result of 'true' biological or methodological differences as opposed to simply chance (i.e., sampling variance) [@NakagawaSantos2012; @Higgins2002].
-In other words, $I_{total}^2$ can be thought of as the percentage of variance between effect sizes that cannot be attributable to sampling error [@Higgins2002].
+In other words, $I_{total}^2$ can be thought of as the percentage of variance between effect sizes after removing the effects of sampling error [@Higgins2002].
 We can only calculate this metric if we have an estimate of the sampling variance for a given effect measure because only then can we quantify the proportion of variation that is the result of sampling variability.
@@
 Some of the variation is clearly the result of working with different species or strains, different traits and different outcome measures, however, some of this variation also arises because of methodological differences across studies that might be related to the dosages or temperatures used for treatments.
-Formally quantifying and presenting heterogeneity estimates from meta-analytic models can provide a way to understand the major drivers of effect size variation by allowing researchers to produce various $I^2$ estimates which can be formally compared within and across studies.
+
+Formally quantifying and presenting heterogeneity estimates from meta-analytic models can provide a way to understand the major drivers of effect size variation by allowing researchers to produce various $I^2$ estimates which can be  compared within and across studies.
 For example, we could fit the multilevel model described above to understand what proportion of variation is the result of, say, 'study' effects following @NakagawaSantos2012: $I^2_{study} = \frac{\sigma^2_{study}}{\sigma^2_{total}}$ where $\sigma^2_{study}$ is the study specific variance.
@@
 Many readers will notice the similarities between $I^2$ and $R^2$ [@Nakgawa2013; @Nakagawa2010].
-If we want to formally assess how much effect size variation is the result of methodological factors, such as temperature and dosage differences applied across studies, then we could fit our multilevel meta-regression model, including dosage or temperature (linear, quadratic or even more complex fits), and estimate how much variation is explained by these fixed effects following @Nakgawa2013.
+If we want to formally assess how much effect size variation is the result of 'methodological factors 'nuisance' variation, such as temperature and dosage differences applied across studies, then we could fit our multilevel meta-regression model, including dosage or temperature (linear, quadratic or even more complex fits), and estimate how much variation is explained by these fixed effects following @Nakgawa2013.
 
@@
 Importantly, moderators could be those that explain variation at the effect size level (i.e., dosage, temperature) or they could explain variation at the study or species level (e.g., reproductive mode, endothermy etc).
-$R^2_{marginal}$, or how we like to think of it, $R^2_{'nuisance'}$, maybe a useful measure to help readers understand just how much effect variation can result from the specific treatment application.
-If the heterogeneity is high as a result of, say, dosages differences, then it is clear that the choice of dosage within and across studies will have a critical impact on the effect of interest.
-Comparative physiologists intersted in implementing thse calculations can do so using our packages `orchaRd` [@Nakagawa2021c] or `metaAidR` (https://github.com/daniel1noble/metaAidR).
+$R^2_{marginal}$, or how we like to think of it in this context as $R^2_{'nuisance'}$, maybe a useful measure to help readers understand just how much effect variation can result from the specific treatment application.
+If the heterogeneity is high as a result of, say, dosages differences, then it is clear that the choice of dosage will have a critical impact on the effect of interest.
+Comparative physiologists interested in implementing these calculations can do so using our packages `orchaRd` [@Nakagawa2021c] or `metaAidR` (https://github.com/daniel1noble/metaAidR).
 
-Heterogenity described using $I^2$ measures can be useful for understanding the relative contributions of different factors to effect size variation, however, prediction intervals might be more appropriate in many cases [@Nakagawa2021c; @Borenstein2019].
-Unlike $I^2$, prediction intervals (PI's) are probably more meaningful in the context of meta-analysis because they explicitly incorperate measures of dispersion around a mean effect size providing information about the likely effect size one can expect if we were to randomly sample a new population.
+Heterogeneity described using $I^2$ measures can be useful for understanding the relative contributions of different factors to effect size variation, however, prediction intervals might be more appropriate in many cases [@Nakagawa2021c; @Borenstein2019].
+Unlike $I^2$, prediction intervals (PI's) are probably more meaningful in the context of meta-analysis because they explicitly incorporate measures of dispersion around a mean effect size providing information about the likely effect size one can expect if we were to randomly sample a new population.
 For example, assume that we were interested in the overall impact of salinity stress in freshwater fish.
-To tackle this question, we collected experimental studies measuring freshwater fish swim performance under high salinity treatments (~15-20ppm NaCl) compared to freshwater (~0ppm NaCl) controls and used SMD to quantify the magnitude of effect salinity had on swim performance.
+To tackle this question, we collected experimental studies measuring fish swim performance under high salinity treatments (~15-20ppm Na Cl) compared to freshwater (~0ppm Na Cl) controls; using SMD to quantify the magnitude of effect salinity had on swim performance.
 We conduct a meta-analysis and estimate an overall SMD of 0.50 with a prediction interval of 0.05 to 0.85.
 The PI indicates that effects can vary widely from as low as an SMD of 0.05 to as high as an SMD 0.95, depending on the population.
-In otherwords, if we were to repeat a study we would expect a new effect to fall within the range of 0.05 and 0.85, 95\% of the time [@Borenstein2019; @Nakagawa2021c].
-This is a very intutive interprettaion of how variable effects are, yet PIs are often not reported in meta-analyses [@Nakagawa2021c].
+In addition, if we were to repeat a study we would expect a new effect to fall within the range of 0.05 and 0.85, 95\% of the time [@Borenstein2019; @Nakagawa2021c].
+This is a very intuitive interpretation of how variable effects are, yet PIs are often not reported in meta-analyses [@Nakagawa2021c].
+As such, we encourage more meta-analysts to report these.
 
-## **Conclusions and Future Directions**
+## **Conclusions**
 Comparative physiologists are interested in meta-analysing effects across a diversity of species, experimental approaches / designs and environments.
@@
 However, obvious drivers of effect size heterogeneity, such as temperature and dosage differences across studies, may not really be of interest.
-Indeed, comparative physiologists are likely to want an effect size or analytical approach that allows them to remove these 'nuisances'.
-Here, we provide comparative physiologists with a set of tools to deal with 'nuisance heterogeneity' by creatively 'reinventing' standard effect sizes or using meta-regression models.
-Of course, nuisance heterogeneity might in of itself be the main interest, in which case standard meta-regression approaches will work sufficiently.
+Indeed, comparative physiologists are likely to want an effect size or analytic approach that allows them to remove these 'nuisances'.
+Here, we provide a set of tools to deal with 'nuisance heterogeneity' by creatively 'reinventing' standard effect sizes or using meta-regression models.
+Of course, 'nuisance heterogeneity' might in of itself be the main interest, in which case standard meta-regression approaches will work sufficiently.
 However, in many cases, comparative physiologists might simply want to focus on bigger, more interesting biological drivers of effect size direction and magnitude.
 However, estimating complex meta-regression models with a multitude of fixed effects might result in more challenging model interpretation.
-As such, a combined approach, where some of the known heterogeneity is dealt with by deriving a variant effect size and associated sampling variance, and other biologically interesting moderators are fit in a meta-regression model, might be the desired.
+As such, a combined approach, where some of the known heterogeneity is dealt with by deriving a variant effect size and associated sampling variance, and other biologically interesting moderators are fit in a meta-regression model, might be desired.
 Indeed, this may even be a necessity to simplify the model.
-We hope the set of tools we describe here provide clarification around sourfes of heterogenity and provides ways to help comparative physiologists to communicate effect measures more richly to help guide our understanding and decisions around pressing global challenges.
+We hope the set of tools we describe provide clarification around different sources of heterogeneity; providing new ways to help comparative physiologists communicate effect measures more richly to guide our understanding and decisions around pressing global challenges.
 

### 2021-07-09 MS/supp.Rmd
Introduction blurb to supp

@@
 ---
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE, cache = TRUE, tidy = TRUE)
+```
+```{r klippy, echo=FALSE, include=TRUE, message=FALSE, warning=FALSE}
+#install.packages("devtools")
+remotes::install_github("rlesur/klippy")
+klippy::klippy(tooltip_message = 'Click to Copy Code', tooltip_success = 'Done', position = 'right', color = "red")
+```
 
-```{r loadpackages, echo = FALSE, results = 'hide'}
-pacman::p_load(png, jpeg, cowplot, flextable, tidyverse)
+# Citation
+This supplement is asscoaited with a special issue review paper and can be cited as follows:
+
+Daniel W.A.
+Noble, Patrice Potter, Sammy Burke, Szymek Drobniak, Malgorzata Lagisz, Rose O’Dea, Shinichi Nakagawa (2022) *Meta-analytic approaches and "new" effect sizes to account for heterogeneous effects in comparative physiology*.
+**Journal of Experimental Biology**
+
+# Introduction
+
+In this supplement we will demonstrate some of the principles we describe in our review paper.
+We'll show readers ways they can apply some of the 'new' effect sizes we describe to account for 'nuisance heterogeneity' in combination with multilevel meta-analytic models (MLMA) and/or multilevel meta-regression models.
+We realise that 'nuisance heterogeneity' may be a misnomer in some senses because such forms of heterogeneity may actually be the main interest of a given meta-analysis; in which case, multilevel meta-regressions are the way to go!
+
+We will overview two different case studies.
+The first case study will show readers how to account for known drivers of effect heterogeneity in the effect size, followed by how we can fit a MLMA (intercept only) model to estimate an overall meta-analytic mean.
+We then show readers how to interpret this mean and associated heterogeneity.
+In the second case study, we use a common effect size metric and instead model the 'nuisance' heterogeneity using a multi-level meta-regression approach.
+We also focus on showing readers how to interpret effects from this model along with heterogeneity.
+
+Throughout the supplement R code is contained within code blocks.
+We provide example data associated with this tutorial which readers can find on the [Open Science Framework](https://osf.io/wscz5/).
+Importantly, all relevant code chunks have a 'copy and paste' button in the top right corner so that the code can be easily transferred to your own R console.
+
+# Loading Data and R Packages
+
+Before embarking on the case studies readers will need to load the data along with the necessary R packages.
+Be sure to set your working directory to the folder or locations where you have put the data.
+
+```{r loadpackages, echo = TRUE, class.source='klippy'}
+pacman::p_load(png, jpeg, pander, cowplot, flextable, tidyverse, metafor, orchaRd)
+
+```
+
+# Case Study 1: 
+```{r class.source='klippy'}
+
+```
+
+# Case Study 2:
+```{r class.source='klippy'}
+
 ```
@@
 ```
+
+# Session Information
+
+```{r}
+pander(sessionInfo(), locale = FALSE)
+```

### 2021-07-09 MS/supp.Rmd
Adding supp download data code

@@
 Throughout the supplement R code is contained within code blocks.
-We provide example data associated with this tutorial which readers can find on the [Open Science Framework](https://osf.io/wscz5/).
+We provide example data associated with this tutorial which readers can find on the [Open Science Framework](https://osf.io/wscz5/), but the code chunks should automatically download and load these for you.
 Importantly, all relevant code chunks have a 'copy and paste' button in the top right corner so that the code can be easily transferred to your own R console.
@@
 
-Before embarking on the case studies readers will need to load the data along with the necessary R packages.
-Be sure to set your working directory to the folder or locations where you have put the data.
+Before embarking on the case studies readers will need to load the necessary R packages.
 
 ```{r loadpackages, echo = TRUE, class.source='klippy'}
-pacman::p_load(png, jpeg, pander, cowplot, flextable, tidyverse, metafor, orchaRd)
+pacman::p_load(png, jpeg, pander, cowplot, flextable, tidyverse, metafor, orchaRd, here)
 
@@
 
+# Example on how to download and load for reader. Should work anyway. Needs some testing
+download.file(url="https://ndownloader.figshare.com/files/7714777", destfile = "CaseStudy1.csv")
+
+data_CS1 <- read.csv(here("CaseStudy1.csv"))
+
 ```
@@
 ```{r class.source='klippy'}
+download.file(url="REPLACE URL FROM OSF HERE", destfile = "CaseStudy2.csv")
+
+data_CS1 <- read.csv(here("CaseStudy2.csv"))
 

### 2021-07-09 MS/box.Rmd

---
title: "Box"
author: "Shinichi Nakagawa"
date: "09/07/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## *BOX: An example of how to obtain sampling variance for effect sizes - let's create one yourself*

$$
\text{ARR} = \frac{ \text{CT}_{\text{max}[T_2]} - \text{CT}_{\text{max}[T_1]}}{T_2 - T_1},
$$
where *T* stands for temperature in Celsius and $T_2 > T_1$.

Let female ARR and male ARR, $\text{ARR}_{\text{f}}$ and $\text{ARR}_{\text{m}}$, respectively and then;

$$
\text{ARRD} = \text{ARR}_{\text{f}} - \text{ARR}_{\text{m}}.
$$
Importantly, ARRD behaves like traditional effect sizes such as standardized mean difference (aka, Cohen's $d$ or Hedges' $g$) and lnRR (log response ratio).

### Sampling variance for ARRD

#### Independent case

We assume all animals measured at at *T~1~* and *T~2~* are different (independent)

$$
s^2(\text{ARRD}) = \left( \frac{1} {T_2 - T_1} \right)^2 
\left( \frac{sd^2_{f[T_1]}} {n_{f[T_1]}} + \frac{sd^2_{f[T_2]}} {n_{f[T_2]}} +
\frac{sd^2_{m[T_1]}} {n_{m[T_1]}} + \frac{s^2_{m[T_2]}} {n_{m[T_2]}}\right),
$$
where $s^2$ is the sampling variance, $sd$ is the sample standard deviation, $n$ is the sample size.

#### Dependent case

We may have cases where the same animals are measured  both at *T~1~* and *T~2~*. So we have $n_f$ and $n_m$, which need to be the same at both temperatures. Then, we need to have an estimate of correlation between measurements of the same individuals ($r_{f[T_1T_2]}$ for females and $r_{m[T_1T_2]}$ for males).

$$
s^2(\text{ARRD}) = \left( \frac{1} {T_2 - T_1} \right)^2 
\left( \frac{sd^2_{f[T_1]} + sd^2_{f[T_2]} - r_{f[T_1T_2]}sd_{f[T_1]}sd_{f[T_2]}} {n_{f}}   +
\frac{sd^2_{m[T_1]} + sd^2_{m[T_2]} - r_{m[T_1T_2]}sd_{m[T_1]}sd_{m[T_2]}} {n_{m}}
\right).
$$

In reality, we often do not know the correlation $r_{[T_1T_2]}$ so we will probably use 0.5.

## AARR (ARR -1)

### Point estimate

$ARRD = 1$ represents perfect acclimation. We want to make 0 this value by substracting 1 and call this AARR (adjusted acclimation response ratio)

$$
\text{AARR} = \text{ARR} -1.
$$

Note AARD like ARRD behaves like tranditional effect statistics.

### Sampling variance for AARR

#### Independent case

$$
s^2(\text{AARR}) = \left( \frac{1} {T_2 - T_1} \right)^2 
\left( \frac{sd^2_{[T_1]}} {n_{[T_1]}} + \frac{sd^2_{[T_2]}} {n_{[T_2]}} \right).
$$

#### Dependent case

$$
s^2(\text{AARR}) = \left( \frac{1} {T_2 - T_1} \right)^2 
\left( \frac{sd^2_{[T_1]} + sd^2_{[T_2]} - r_{[T_1T_2]}sd_{[T_1]}sd_{[T_2]}} {n} 
\right).
$$

##### Basics about variance

See https://en.wikipedia.org/wiki/Variance

Adding a constant ($a$) does not change the variance of a random varaible $X$.
$$
\operatorname{Var}(X+a)=\operatorname{Var}(X)
$$

Multipling a constant ($a$) does increase the variance of $X$ by $a^2$.

$$
\operatorname{Var}(aX)=a^2\operatorname{Var}(X)
$$

When we consider two random variables $X$ and $Y$, we need to know their covariance.

$$
\operatorname{Var}(aX\pm bY)=a^2\operatorname{Var}(X)+b^2\operatorname{Var}(Y) \pm 2ab\operatorname{Cov}(X,Y)
$$

### 2021-07-09 MS/box.Rmd
Box to be done (lockdown at UNSW - hope to get back soon!)

@@
 title: "Box"
-author: "Shinichi Nakagawa"
 date: "09/07/2021"
@@
 
-## *BOX: An example of how to obtain sampling variance for effect sizes - let's create one yourself*
+## *BOX: An example of how to obtain sampling variance for an effect size - let's create one yourself*
 
@@
 $$
+## Note
+
+1. General Slope - some basics
+2. ARR
+3. Differences between slopes
+4. ARRD
+5. Delta method

### 2021-07-09 R/survey_data_results.Rmd

@@
 
+### Types of models used {.tabset .tabset-fade .tabset-pills}
+
+What models are used. Note that you need to take this approach because some papers use many different models.
+
+```{r}
+dat %>% dplyr::group_by(stat_model_type) %>% janitor::tabyl(stat_model_type) %>%
+  dplyr::summarise(MLMA = dplyr::if_else(grepl("multilevel meta-analysis", stat_model_type), n, 0),
+                  MLMR = dplyr::if_else(grepl("meta-regression models", stat_model_type), n, 0),
+                    LinearRegrs = dplyr::if_else(grepl("linear regression", stat_model_type), n, 0),
+                 Other = dplyr::if_else(grepl("unclear/other", stat_model_type), n, 0),
+                 Vote = dplyr::if_else(grepl("vote counting", stat_model_type), n, 0),
+                 WeightedReg = dplyr::if_else(grepl("weighted regression including mixed effects models", stat_model_type), n, 0),
+                 RE = dplyr::if_else(grepl("random-effects meta-analysis", stat_model_type), n, 0)) %>% 
+  colSums(.) %>% data.frame(effect = names(.), n = .) %>% mutate(prop = (n / sum(n)*100)) %>% arrange(effect) %>% 
+  ggplot() + tm + theme(axis.title.y = element_blank(),
+                        axis.text.y = element_text(size=8)) +
+  geom_col(aes(x = effect, y = n), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
+  scale_y_continuous(expand=c(0,0),breaks=seq(1,20,2)) +
+  labs(x = "Effect Size",
+       y = "Number of Papers") +
+  coord_flip()
+```
+
+### Weighted models? {.tabset .tabset-fade .tabset-pills}
+
+```{r}
+dat %>%  janitor::tabyl(meta_analysis_weighted) %>% 
+  ggplot() + tm +
+  geom_col(aes(x = meta_analysis_weighted, y = percent), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
+  scale_y_continuous(expand=c(0,0), limits = c(0,1)) +
+  labs(x = "Weighted Model?",
+       y = "Frequency") 
+```
+
+### Effect size impacted by 'nuisance heterogeneity'? {.tabset .tabset-fade .tabset-pills}
+
+```{r}
+dat %>%  janitor::tabyl(cont_moderator_variable) %>% 
+  ggplot() + tm +
+  geom_col(aes(x = cont_moderator_variable, y = percent), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
+  scale_y_continuous(expand=c(0,0), limits = c(0,1)) +
+  labs(x = "Nuisance Heterogenity?",
+       y = "Frequency") 
+```
+
+### Dealt with nuisance in model? {.tabset .tabset-fade .tabset-pills}
+
+Of the studis that said 'yes' how many actually modelled it or accounted for it?
+```{r}
+dat %>%  filter(!cont_moderator_variable_modelled=="") %>% janitor::tabyl(cont_moderator_variable_modelled) %>% 
+  ggplot() + tm +
+  geom_col(aes(x = cont_moderator_variable_modelled, y = percent), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
+  scale_y_continuous(expand=c(0,0), limits = c(0,1)) +
+  labs(x = "Nuisance Heterogenity Modelled?",
+       y = "Frequency") 
+```
+
+### Reported Heterogeneity? {.tabset .tabset-fade .tabset-pills}
+Of the studis that are weighted how many actually resported measures of heterogenity?
+```{r}
+dat %>%  filter(!heterogeneity_reported=="N/A (e.g.
+they conducted unweighted meta-analysis)") %>% mutate(heterogeneity_reported = if_else(heterogeneity_reported == "unclear/other (add comment)", "other", heterogeneity_reported)) %>% janitor::tabyl(heterogeneity_reported) %>%
+  ggplot() + tm +
+  geom_col(aes(x = heterogeneity_reported, y = percent), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
+  scale_y_continuous(expand=c(0,0), limits = c(0,1)) +
+  labs(x = "Heterogeneity reported?",
+       y = "Frequency") 
+```
+
 ### Publication years {.tabset .tabset-fade .tabset-pills}

### 2021-07-11 MS/box.Rmd
boxes done - a bit of corrections for ms.Rmd too

@@
 
-## *BOX: An example of how to obtain sampling variance for an effect size - let's create one yourself*
+## *BOX: Example of how to derive sampling variance*
+
+Here we show how to obtain sampling variance for a slope (or a 'rate of change') when you are given measurements of a physiological trait at two points in an environmental gradient (e.g.
+temperature, salinity, acidity).
+Then, we also go on to derive sampling variance for the difference between two slopes.
+
+### Sampling variance for a slope between two points
+
+It may be the best to start with a real example which comparative physiologists can easily associate, namely the (temperature) acclimation response ratio (ARR).
+ARR can be defined as a slope for physiological responses at two different temperature points, which is:
 
 $$
-\text{ARR} = \frac{ \text{CT}_{\text{max}[T_2]} - \text{CT}_{\text{max}[T_1]}}{T_2 - T_1},
+\text{ARR} = \frac{\overline{X}_{1} - \overline{X}_{2}}{T_2 - T_1},
 $$
-where *T* stands for temperature in Celsius and $T_2 > T_1$.
 
-Let female ARR and male ARR, $\text{ARR}_{\text{f}}$ and $\text{ARR}_{\text{m}}$, respectively and then;
+where *T* stands for temperature in Celsius and $T_2 > T_1$, and $\overline{X}_1$ and $\overline{X}_2$ are the average physiological responses at two temperature points $T_1$ and $T_2$.
+
+<!--- Dan we may need to use bar_X rather than just X or M for consistence in the main text --->
+
+To obtain the sampling variance for this equation (slope), we will need to know several basic properties of variance.
+Let's assume $X_1$ is a random variable which means that this variable has a mean and standard deviation (variance).
+Multiplying a constant ($a$) will change the variance by the square of that constant ($a^2$) while adding or subtracting the constant ($b$) does not change the variance of $X$.
+This can be summarized as:
 
 $$
-\text{ARRD} = \text{ARR}_{\text{f}} - \text{ARR}_{\text{m}}.
+\text{Var}(aX_1 \pm b)=a^2\text{Var}(X_1)
 $$
-Importantly, ARRD behaves like traditional effect sizes such as standardized mean difference (aka, Cohen's $d$ or Hedges' $g$) and lnRR (log response ratio).
 
-### Sampling variance for ARRD
-
-#### Independent case
-
-We assume all animals measured at at *T~1~* and *T~2~* are different (independent)
+Also, when adding two random variables ($X_1$ and $X_2$), the combined variance is the sum of the variance of$X1$ and and variance of $X2$ and 2 times the covariance between $X_1$ and $X_2$.
+This relationship can be written as:
 
 $$
-s^2(\text{ARRD}) = \left( \frac{1} {T_2 - T_1} \right)^2 
-\left( \frac{sd^2_{f[T_1]}} {n_{f[T_1]}} + \frac{sd^2_{f[T_2]}} {n_{f[T_2]}} +
-\frac{sd^2_{m[T_1]}} {n_{m[T_1]}} + \frac{s^2_{m[T_2]}} {n_{m[T_2]}}\right),
-$$
-where $s^2$ is the sampling variance, $sd$ is the sample standard deviation, $n$ is the sample size.
+\text{Var}(X_1 \pm X_2)= \text{Var}(X_1)+ \text{Var}(X_2) \pm 2\text{Cov}(X_1,X_2) \\
+= \text{Var}(X_1)+ \text{Var}(X_2) \pm 2\text{Cor}(X_1,X_2)\sqrt{ \text{Var}(X_1))\text{Var}(X_2) },
+$$ where the co-variance $\text{Cov}(X_1,X_2)$ equals to the correlation multiplied by the square-root of the two variances $2\text{Cor}(X_1,X_2)\sqrt{ \text{Var}(X_1))\text{Var}(X_2) }$.
 
-#### Dependent case
+Importantly, when $X_1$ and $X_2$ are independent of each other, the covariance is 0.
+More concretely, if measurements are done on two different groups of animals at two different temperature points ($T_1$ and $T_2$), then the co-variances between these two sets of measurements are 0.
 
-We may have cases where the same animals are measured  both at *T~1~* and *T~2~*.
-So we have $n_f$ and $n_m$, which need to be the same at both temperatures.
-Then, we need to have an estimate of correlation between measurements of the same individuals ($r_{f[T_1T_2]}$ for females and $r_{m[T_1T_2]}$ for males).
+Therefore, when $X_1$ and $X_2$ are indepedent, we can obtain the sampling variance for ARR as:
 
 $$
-s^2(\text{ARRD}) = \left( \frac{1} {T_2 - T_1} \right)^2 
-\left( \frac{sd^2_{f[T_1]} + sd^2_{f[T_2]} - r_{f[T_1T_2]}sd_{f[T_1]}sd_{f[T_2]}} {n_{f}}   +
-\frac{sd^2_{m[T_1]} + sd^2_{m[T_2]} - r_{m[T_1T_2]}sd_{m[T_1]}sd_{m[T_2]}} {n_{m}}
+\text{Var}(\text{AAR}) = \left( \frac{1} {T_2 - T_1} \right)^2 
+\left( \frac{SD^2_{1}} {N_{1}} + \frac{SD^2_{2}} {N_{2}} \right),
+$$
+
+where $SD_{1}$ and $SD_{2}$ and $N_1$ and $N_2$ are standard deviations and sampling sizes at temperature $T_1$ and $T_2$.
+Some may still find it difficult to see how we got this equation.
+Let us explain further.
+The (sampling) standard error for $X_1$ is $SE_1 = SD_{1} / \sqrt{N_{1}}$ -- we think many of you know this as the formula to obtain *SE* from *SD*.
+Given this, the sampling variance for $X_1$ is $SD^2_{1} / N_{1}$, which you see as an element of the sampling variance of ARR along with the sampling variance for $X_2$, which is $X_1$ is $SD^2_{1} / N_{1}$.
+the term $(1/(T_2 - T_1))^2$ comes from recognizing $1/(T_2 - T_1)$ as a constant.
+
+Now, it is not uncommon that we use the same group of animals (or plants) at two temperature points.
+Then, we need to add the co-variance between $X_1$ and $X_2$ ($\text{Cov}(X_1,X_2)$); note that as above, the covariance equals the corresponding correlation multiplied by square-root of two (sampling) variances.
+Therefore, the sampling variance can be now written as:
+
+$$
+\text{Var}(\text{AAR}) = \left( \frac{1} {T_2 - T_1} \right)^2 
+\left( 
+\frac{SD^2_{1}} {N_1} + \frac{SD^2_{2}} {N_2} - 2r \sqrt{\frac{SD^2_{1}} {N_1}  \frac{SD^2_{2}} {N_2}} 
+\right).
+$$ By assuming the number of animals (*N*) were the same at the two temperature points, we can slightly simplify this formula:
+
+$$ 
+\text{Var}(\text{AAR}) = \left( 
+\frac{1} {T_2 - T_1} 
+\right)
+\left( 
+\frac{SD^2_{1} + SD^2_{2}  - 2rSD_{1}SD_{2}} {N} 
 \right).
@@
 
-In reality, we often do not know the correlation $r_{[T_1T_2]}$ so we will probably use 0.5.
+where *r* is the correlation between a set of measurement $X_1$ and $X_2$ form the same individuals at two point $T_1$ and $T_2$.
+As you may notice, we need raw data to calculate *r*.
+So in reality, we often needs to assume a certain value of *r*.
+Noble et al (Mol Eco; REF) discuss why we can assume $r = 0.5$ and this may be the most reasonable thing to do when we do not have any estimate of *r*.
 
-## AARR (ARR -1)
+### Sampling variance for the difference between two slopes
 
-### Point estimate
-
-$ARRD = 1$ represents perfect acclimation. We want to make 0 this value by substracting 1 and call this AARR (adjusted acclimation response ratio)
+Now let us assume that we now want to know the difference between two different ARR values: female ARR, $\text{ARR}_{f}$ and Male ARR, $\text{ARR}_{m}$. Such a difference (ARRD) can be written as:
 
 $$
-\text{AARR} = \text{ARR} -1.
+\text{ARRD} = \text{ARR}_{f} - \text{ARR}_{m}.
 $$
 
-Note AARD like ARRD behaves like tranditional effect statistics.
-
-### Sampling variance for AARR
-
-#### Independent case
+Using the basic properties of variance and the results from the above, the sample variance for ARRD can be derived, when measurements at two temperature points are independent, as:
 
 $$
-s^2(\text{AARR}) = \left( \frac{1} {T_2 - T_1} \right)^2 
-\left( \frac{sd^2_{[T_1]}} {n_{[T_1]}} + \frac{sd^2_{[T_2]}} {n_{[T_2]}} \right).
-$$
+\text{Var}(\text{ARRD}) = \left( \frac{1} {T_2 - T_1} \right)^2 
+\left( \frac{SD^2_{f1}} {N_{f1}} + \frac{SD^2_{f2}} {N_{f2}} +
+ \frac{SD^2_{m1}} {N_{m1}} + \frac{SD^2_{m2}} {N_{m2}}
+\right),
+$$ where subscripts *f* and *m* stands for 'females' and 'males'.
 
-#### Dependent case
+Similarly, the dependent version of the sampling variance can be written as:
 
 $$
-s^2(\text{AARR}) = \left( \frac{1} {T_2 - T_1} \right)^2 
-\left( \frac{sd^2_{[T_1]} + sd^2_{[T_2]} - r_{[T_1T_2]}sd_{[T_1]}sd_{[T_2]}} {n} 
+\text{Var}(\text{ARRD}) = \left( \frac{1} {T_2 - T_1} \right)^2 
+\left( 
+\frac{SD^2_{f1} + SD^2_{f2}  - 2rSD_{f1}SD_{f2}} {N_f}   +
+\frac{SD^2_{m1} + SD^2_{m2}  - 2rSD_{m1}SD_{m2}} {N_m}
 \right).
@@
 
-##### Basics about variance
+Now we have derive sampling variances for 'temperature' ARR and ARRD for both independent and dependent cases.
+But these formulas can be applied to changes in salinity, PH, oxygen and other abotic factors.
+Also, the constant components of these formulas can be flexibly adjusted.
+For example, it may be possible that males and females were measured in slightly different temperatures; say females at $T_3$ and $T_4$ ($T_4 > T_3$) and male at $T_5$ and $T_6$ ($T_6 > T_5$) like below:
 
-See https://en.wikipedia.org/wiki/Variance
-
-Adding a constant ($a$) does not change the variance of a random varaible $X$.
 $$
-\operatorname{Var}(X+a)=\operatorname{Var}(X)
+\text{Var}(\text{ARRD}) = \left( \frac{1} {T_4 - T_3} \right)^2 
+\left( 
+\frac{SD^2_{f3} + SD^2_{f4}  - 2rSD_{f3}SD_{f4}} {N_f}   +
+\right) +
+\left( \frac{1} {T_6 - T_5} \right)^2 
+\left( 
+\frac{SD^2_{m5} + SD^2_{m6}  - 2rSD_{m5}SD_{m6}} {N_m}
+\right).
 $$
 
-Multipling a constant ($a$) does increase the variance of $X$ by $a^2$.
+Also, note that the difference between slopes does not need to be that of males and females. It can be between experimental and control groups or comparing any two groups or situations.
+
+### The delta method
+
+It is often limited when we can use the basic properties of variance to derive sampling variance.
+Therefore, we introduce a practical and widely applicable method to obtain approximate variance when the basic properties of variance cannot be applied.
+The method is widely known as the delta method, which can be written as:
+
+Here, we use the delta method to derive the sampling variance for the log repose ratio, which is:
 
 $$
-\operatorname{Var}(aX)=a^2\operatorname{Var}(X)
+\text{Var}(f(X_1)) \approx \text{Var}(X_1)* \left( 
+f'(X_1)
+\right)^2,
+$$ where $f(X_1)$ represents the function of the random variable $X_1$, and importantly, $f'(X_1)$ is the first derivative of $f(X_1)$.
+Probably it is hard to understand what does this really means without a concrete example.
+So let's derive the sampling variance for $\ln{RR}$, which is:
+
+$$
+\ln{RR} = \ln \left ( \frac{X_{1}}{X_{2}}\right ) = \ln{X_1} -\ln{X_2}.
+$$ Here, $f(X_1) = \ln{X_1}$. By applying $f'(X_1) = 1/{X_1}$ to the delta method and using the variance's basic properties, we have:
+
+$$
+\text{Var}(\ln{RR}) \approx  \left ( \frac{SD_{1}^2}{N_{1}X_{1}^2}\right ) + \left ( \frac{SD_{2}^2}{N_{2}X_{2}^2}\right ) 
+- 2r\sqrt{\frac{SD_{1}^2}{N_{1}X_{1}^2}}\sqrt{\frac{SD_{2}^2}{N_{2}X_{2}^2}},
 $$
 
-When we consider two random variables $X$ and $Y$, we need to know their covariance.
+where $r$ is 0 when two sets of measurements are independent (therefore, the term including $r$ disappears), while $r$ is the correlation between $\ln{X_1}$ and $\ln{X_2}$.
+As discussed, we usually do not have an estimate for this correlation coefficient.
 
-$$
-\operatorname{Var}(aX\pm bY)=a^2\operatorname{Var}(X)+b^2\operatorname{Var}(Y) \pm 2ab\operatorname{Cov}(X,Y)
-$$
-## Note
-
-1. General Slope - some basics
-2. ARR
-3. Differences between slopes
-4. ARRD
-5. Delta method
+Finally, we note that by using the basic properties of variance and the delta method, one can derive sampling variance for most of cases.
+Indeed, these were enough for us to derive samping variance for 'new' effect sizes (e.g.
+$lnQ_{10}$; see the main text) and as in Nakagawa et al.
+(2015, MEE) and Senior et al.
+(2020, RSM).

### 2021-07-11 MS/ms.Rmd
boxes done - a bit of corrections for ms.Rmd too

@@
   \begin{aligned}
-  lnRR = ln\left ( \frac{X_{1}}{X_{2}}\right )
+  \ln{RR} = \ln\left ( \frac{X_{1}}{X_{2}}\right )
   \end{aligned}
@@
 \begin{equation} 
-  s_{lnRR} = \left ( \frac{SD_{1}^2}{N_{1}X_{1}^2}\right ) + \left ( \frac{SD_{2}^2}{N_{2}X_{2}^2}\right )
+  s^2_{lnRR} = \left ( \frac{SD_{1}^2}{N_{1}X_{1}^2}\right ) + \left ( \frac{SD_{2}^2}{N_{2}X_{2}^2}\right )
   (\#eq:slnRR)
@@
 \begin{equation} 
-  s_{lnRR_{Q_{10}}} = \left( \frac{SD_{2}^2}{R^2_{2}N_{2}} + \frac{SD_{1}^2}{R^2_{1}N_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
+  s^2_{lnRR_{Q_{10}}} = \left( \frac{SD_{2}^2}{R^2_{2}N_{2}} + \frac{SD_{1}^2}{R^2_{1}N_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
   (\#eq:Vlnq10)
@@
 \begin{equation} 
-s_{lnVR_{Q_{10}}} = \left( \frac{1}{2\left( N_{2}-1 \right)} + \frac{1}{2\left(N_{1} - 1\right)} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
+s^2_{lnVR_{Q_{10}}} = \left( \frac{1}{2\left( N_{2}-1 \right)} + \frac{1}{2\left(N_{1} - 1\right)} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
 (\#eq:slnq10VR)
@@
 \begin{equation} 
-s_{lnCVR_{Q_{10}}} = \left[ \frac{(\text{SD}_{1})^2}{N_{1}({R}_{1})^2} + \frac{(\text{SD}_{2})^2}{N_{2} ({R}_{2})^2} + \frac{1}{2\left( N_{1}-1 \right)} + \frac{1}{2\left(N_{2} - 1\right)} \right]{ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
+s^2_{lnCVR_{Q_{10}}} = \left[ \frac{(\text{SD}_{1})^2}{N_{1}({R}_{1})^2} + \frac{(\text{SD}_{2})^2}{N_{2} ({R}_{2})^2} + \frac{1}{2\left( N_{1}-1 \right)} + \frac{1}{2\left(N_{2} - 1\right)} \right]{ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
 (\#eq:slnq10CVR)

### 2021-07-11 MS/box.Rmd
inconsistency fixed

@@
 $$
-\text{ARR} = \frac{\overline{X}_{1} - \overline{X}_{2}}{T_2 - T_1},
+\text{ARR} = \frac{X_{1} - X_{2}}{T_2 - T_1},
 $$
 
-where *T* stands for temperature in Celsius and $T_2 > T_1$, and $\overline{X}_1$ and $\overline{X}_2$ are the average physiological responses at two temperature points $T_1$ and $T_2$.
-
-<!--- Dan we may need to use bar_X rather than just X or M for consistence in the main text --->
+where *T* stands for temperature in Celsius and $T_2 > T_1$, and $X_1$ and $X_2$ are the average physiological responses (estimated means) at two temperature points $T_1$ and $T_2$.
 
 To obtain the sampling variance for this equation (slope), we will need to know several basic properties of variance.
-Let's assume $X_1$ is a random variable which means that this variable has a mean and standard deviation (variance).
+Let's assume $X_1$ is a random variable, which means that this variable has a mean and standard deviation (variance).
 Multiplying a constant ($a$) will change the variance by the square of that constant ($a^2$) while adding or subtracting the constant ($b$) does not change the variance of $X$.
@@
 
-Therefore, when $X_1$ and $X_2$ are indepedent, we can obtain the sampling variance for ARR as:
+Therefore, when $X_1$ and $X_2$ are independent, we can obtain the sampling variance for ARR as:
 
@@
 Finally, we note that by using the basic properties of variance and the delta method, one can derive sampling variance for most of cases.
-Indeed, these were enough for us to derive samping variance for 'new' effect sizes (e.g.
+Indeed, these were enough for us to derive sampling variance for 'new' effect sizes (e.g.
 $lnQ_{10}$; see the main text) and as in Nakagawa et al.

### 2021-07-12 MS/box.Rmd
a typo fixed
Edit MS a bit. INcluded VCV because of dpeendency stuff in box

@@
 ---
-title: "Box"
-date: "09/07/2021"
+bibliography: ../bib/refs.bib
+csl: ../bib/the-journal-of-experimental-biology.csl
 output: html_document
@@
 
-## *BOX: Example of how to derive sampling variance*
+## *BOX 1: Example of how to derive sampling variance*
 
@@
 temperature, salinity, acidity).
-Then, we also go on to derive sampling variance for the difference between two slopes.
+We also go on to derive sampling variance for the difference between two slopes so that we can use powerful meta-analytic models using this effect size.
 
@@
 
-It may be the best to start with a real example which comparative physiologists can easily associate, namely the (temperature) acclimation response ratio (ARR).
-ARR can be defined as a slope for physiological responses at two different temperature points, which is:
+It may be the best to start with a real example that comparative physiologists can easily associate, namely the temperature acclimation slope or as we call it the (temperature) acclimation response ratio (ARR).
+ARR can be defined as a slope for acclimated physiological responses at two different temperature points, defined as:
 
@@
 
-where *T* stands for temperature in Celsius and $T_2 > T_1$, and $X_1$ and $X_2$ are the average physiological responses (estimated means) at two temperature points $T_1$ and $T_2$.
+where *T* stands for temperature in degrees Celsius and $T_{2} > T_{1}$, and $X_{1}$ and $X_{2}$ are the average physiological responses (estimated means) at two temperature points $T_{1}$ and $T_{2}$.
 
-To obtain the sampling variance for this equation (slope), we will need to know several basic properties of variance.
-Let's assume $X_1$ is a random variable, which means that this variable has a mean and standard deviation (variance).
-Multiplying a constant ($a$) will change the variance by the square of that constant ($a^2$) while adding or subtracting the constant ($b$) does not change the variance of $X$.
+To obtain the sampling variance for this equation (slope), we need to know several basic properties of variance.
+Let's assume $X_{1}$ is a random variable, which means that this variable has a mean and standard deviation (variance).
+Multiplying a constant ($a$) will change the variance by the square of that constant ($a^2$) while adding or subtracting the constant ($b$) does not change the variance of $X_{1}$.
 This can be summarized as:
@@
 $$
-\text{Var}(aX_1 \pm b)=a^2\text{Var}(X_1)
+\sigma^2(aX_1 \pm b)=a^2 * \sigma^2_{X_{1}}
 $$
 
-Also, when adding two random variables ($X_1$ and $X_2$), the combined variance is the sum of the variance of$X1$ and and variance of $X2$ and 2 times the covariance between $X_1$ and $X_2$.
+Also, when adding two random variables ($X_{1}$ and $X_{2}$), the combined variance is the sum of the variance of $X_{1}$  and the variance of $X_{2}$ plus 2 times the covariance between $X_{1}$ and $X_{2}$.
 This relationship can be written as:
@@
 $$
-\text{Var}(X_1 \pm X_2)= \text{Var}(X_1)+ \text{Var}(X_2) \pm 2\text{Cov}(X_1,X_2) \\
-= \text{Var}(X_1)+ \text{Var}(X_2) \pm 2\text{Cor}(X_1,X_2)\sqrt{ \text{Var}(X_1))\text{Var}(X_2) },
-$$ where the co-variance $\text{Cov}(X_1,X_2)$ equals to the correlation multiplied by the square-root of the two variances $2\text{Cor}(X_1,X_2)\sqrt{ \text{Var}(X_1))\text{Var}(X_2) }$.
+\sigma^2_{X_1 \pm X_2} = \sigma^2_{X_1} + \sigma^2_{X_2} \pm 2\text{Cov}(X_1,X_2) \\
+= \sigma^2_{X_1} + \sigma^2_{X_2} \pm 2\text{Cor}(X_1,X_2)\sqrt{ \sigma^2_{X_1} \sigma^2_{X_2} }
+$$ 
+where the co-variance $\text{Cov}(X_1,X_2)$ equals to the correlation multiplied by the square-root of the two variances $2\text{Cor}(X_1,X_2)\sqrt{ \sigma^2_{X_1} \sigma^2_{X_2} }$.
 
-Importantly, when $X_1$ and $X_2$ are independent of each other, the covariance is 0.
+Importantly, when $X_{1}$ and $X_{2}$ are independent of each other the covariance is 0.
 More concretely, if measurements are done on two different groups of animals at two different temperature points ($T_1$ and $T_2$), then the co-variances between these two sets of measurements are 0.
 
-Therefore, when $X_1$ and $X_2$ are independent, we can obtain the sampling variance for ARR as:
+Therefore, when $X_{1}$ and $X_{2}$ are independent, we can obtain the sampling variance for ARR as:
 
 $$
-\text{Var}(\text{AAR}) = \left( \frac{1} {T_2 - T_1} \right)^2 
-\left( \frac{SD^2_{1}} {N_{1}} + \frac{SD^2_{2}} {N_{2}} \right),
+\sigma^2_{AAR} = \left( \frac{1} {T_2 - T_1} \right)^2 
+\left( \frac{SD^2_{1}} {N_{1}} + \frac{SD^2_{2}} {N_{2}} \right)
 $$
 
-where $SD_{1}$ and $SD_{2}$ and $N_1$ and $N_2$ are standard deviations and sampling sizes at temperature $T_1$ and $T_2$.
-Some may still find it difficult to see how we got this equation.
+where $SD_{1}$ and $SD_{2}$ and $N_{1}$ and $N_{2}$ are standard deviations and sampling sizes at temperature $T_{1}$ and $T_{2}$.
+Readers may still find it difficult to see how we got this equation.
 Let us explain further.
-The (sampling) standard error for $X_1$ is $SE_1 = SD_{1} / \sqrt{N_{1}}$ -- we think many of you know this as the formula to obtain *SE* from *SD*.
-Given this, the sampling variance for $X_1$ is $SD^2_{1} / N_{1}$, which you see as an element of the sampling variance of ARR along with the sampling variance for $X_2$, which is $X_1$ is $SD^2_{1} / N_{1}$.
-the term $(1/(T_2 - T_1))^2$ comes from recognizing $1/(T_2 - T_1)$ as a constant.
+The (sampling) standard error for $X_{1}$ is $SE_{1} = SD_{1} / \sqrt{N_{1}}$ -- many readers will probably know this as the formula for obtaining *SE* from *SD*.
+Given this, the sampling variance for $X_{1}$ is $SD^2_{1} / N_{1}$, which you see as an element of the sampling variance of ARR along with the sampling variance for $X_{2}$, which is $X_{1}$ is $SD^2_{1} / N_{1}$; the term $(1/(T_{2} - T_{1}))^2$ comes from recognizing $1/(T_{2} - T_{1})$ as a constant.
 
 Now, it is not uncommon that we use the same group of animals (or plants) at two temperature points.
-Then, we need to add the co-variance between $X_1$ and $X_2$ ($\text{Cov}(X_1,X_2)$); note that as above, the covariance equals the corresponding correlation multiplied by square-root of two (sampling) variances.
+If we do, however, then we need to add the co-variance between $X_{1}$ and $X_{2}$ ($\text{Cov}(X_{1},X_{2})$); note that as above, the co-variance equals the corresponding correlation multiplied by the square-root of two (sampling) variances.
 Therefore, the sampling variance can be now written as:
@@
 $$
-\text{Var}(\text{AAR}) = \left( \frac{1} {T_2 - T_1} \right)^2 
+\text{Var}(\text{AAR}) = \left( \frac{1} {T_{2} - T_{1}} \right)^2 
 \left( 
 \frac{SD^2_{1}} {N_1} + \frac{SD^2_{2}} {N_2} - 2r \sqrt{\frac{SD^2_{1}} {N_1}  \frac{SD^2_{2}} {N_2}} 
-\right).
-$$ By assuming the number of animals (*N*) were the same at the two temperature points, we can slightly simplify this formula:
+\right)
+$$ 
+By assuming the number of animals (*N*) are the same at the two temperature points, we can slightly simplify this formula:
 
 $$ 
-\text{Var}(\text{AAR}) = \left( 
+\sigma^2_{AAR} = \left( 
 \frac{1} {T_2 - T_1} 
-\right)
+\right)^2
 \left( 
 \frac{SD^2_{1} + SD^2_{2}  - 2rSD_{1}SD_{2}} {N} 
-\right).
+\right)
 $$
@@
 As you may notice, we need raw data to calculate *r*.
-So in reality, we often needs to assume a certain value of *r*.
-Noble et al (Mol Eco; REF) discuss why we can assume $r = 0.5$ and this may be the most reasonable thing to do when we do not have any estimate of *r*.
+So, in reality, we often need to assume a certain value of *r*.
+@Noble2017 discuss why we can assume $r = 0.5$ and this may be the most reasonable thing to do when we do not have any estimate of *r*.
 
@@
 
-### The delta method
+### The Delta Method
 
@@
 \ln{RR} = \ln \left ( \frac{X_{1}}{X_{2}}\right ) = \ln{X_1} -\ln{X_2}.
-$$ Here, $f(X_1) = \ln{X_1}$. By applying $f'(X_1) = 1/{X_1}$ to the delta method and using the variance's basic properties, we have:
+$$
+
+Here, $f(X_1) = \ln{X_1}$. By applying $f'(X_1) = 1/{X_1}$ (i.e. the first derivative of $lnX1$ is $1/{X_1}$) to the delta method and using the variance's basic properties, we have:
 
 $$
-\text{Var}(\ln{RR}) \approx  \left ( \frac{SD_{1}^2}{N_{1}X_{1}^2}\right ) + \left ( \frac{SD_{2}^2}{N_{2}X_{2}^2}\right ) 
+\sigma^2_{ln{RR}} \approx  \left ( \frac{SD_{1}^2}{N_{1}}\right ) * \left(\frac{1}{X_{1}} \right)^2 + \left ( \frac{SD_{2}^2}{N_{2}}\right ) * \left(\frac{1}{X_{2}} \right)^2 =   \left ( \frac{SD_{1}^2}{N_{1}X_{1}^2}\right ) + \left ( \frac{SD_{2}^2}{N_{2}X_{2}^2}\right )
+$$
+Note here again that the first term, $\frac{SD_{1}^2}{N_{1}}$ is the sampling variance for group 1, and we simply multiply this term by the square of the first derivative of $X_{1}$ as the Delta method tells us.
+Of course, readers will see that this is equivalent to the sampling variance for $ln_{RR}$ (Table 1).
+We can extend this sampling variance to include dependency between the groups as:
+
+$$
+\sigma^2_{ln{RR}} \approx  \left ( \frac{SD_{1}^2}{N_{1}X_{1}^2}\right ) + \left ( \frac{SD_{2}^2}{N_{2}X_{2}^2}\right ) 
 - 2r\sqrt{\frac{SD_{1}^2}{N_{1}X_{1}^2}}\sqrt{\frac{SD_{2}^2}{N_{2}X_{2}^2}},
 $$
-
 where $r$ is 0 when two sets of measurements are independent (therefore, the term including $r$ disappears), while $r$ is the correlation between $\ln{X_1}$ and $\ln{X_2}$.
@@
 Indeed, these were enough for us to derive sampling variance for 'new' effect sizes (e.g.
-$lnQ_{10}$; see the main text) and as in Nakagawa et al.
-(2015, MEE) and Senior et al.
-(2020, RSM).
+$lnQ_{10}$; see the main text) and as in @Nakagawa2015 and @Senior2020.

### 2021-07-12 MS/ms.Rmd
Modified MS a bit becasue of dependency in box. Fixed up a bunch of box stuff to be consistent with main MS a little more, mainly just add sigma to denote variances, just some added equation for readers to hopefully make it a littkle more clear the equivalency for Delta Methods.

@@
 We also describe more general approaches that can be usefully applied to a variety of different contexts to derive 'new' effects sizes and sampling variances.
-The effect sizes and their corresponding sampling variances we describe should help physiologists deal with common treatment differences across studies.
+The effect sizes and their corresponding sampling variances that we describe should help physiologists deal with common treatment differences across studies.
 By using effect sizes that account for components of effect heterogeneity, in combination with existing meta-analytic models, comparative physiologists can explore exciting new questions by making results from large-scale data sets collected from the literature more accessible and widely interpretable.
@@
 In some cases, however, the latter factors might actually not be 'nuisance' variables but the main interest of a synthesis.
-However, in many cases they can result in a more complicated interpretation of an effect measure then what is desired.
+Regardless, in many cases they can result in a more complicated interpretation of an effect measure then what is desired.
 
@@
 2) based on the methods provided, was the effect size likely susceptible to continuous variation in how treatments were applied (e.g., for contrast-based effects) or the conditions under which traits were measured (i.e., for correlations) across studies (i.e., 'nuisance heterogeneity')?
-3) If so, was the variation accounted for in the effect size or during analysis?, and finally, 4) how were effect sizes analysed in the quantitative synthesis, were these weighted analyses, and what program was used for analysis?
-We collected additional
+3) If so, was the variation accounted for in the effect size or during analysis?
+and finally, 4) how many analyses used 'weighted' meta-analytic models?
 
@@
 We highlight two examples in the box focusing mainly on generality.
-Below, we show using a common, well understood effect measure of interest to comparative physiology, $Q_{10}$ how we can formalise a traditional effect sizes', such as $lnRR$, to capture this 'nuisance variation'.
+Below, we show using a common, well understood effect measure of interest to comparative physiologists, $Q_{10}$, how we can formalise a traditional effect size, such as $lnRR$, to capture this 'nuisance variation'.
 
@@
 
-Assume that we are interested in understanding the overall effect of, say, stress (i.e., corticosterone - CORT) on reproduction [e.g., see @Podmola2018] we might extract data from studies manipulating corticosterone in bird eggs.
+Assume that we are interested in understanding the overall effect of, say, stress (i.e., corticosterone - CORT) on reproduction [e.g., see @Podmola2018].
+We might extract data from studies manipulating corticosterone in bird eggs.
 Of course, these studies are diverse, apply different dosages of corticosterone and are working across many species.
@@
 $$
-\begin{equation} 
-Y_{i} = \beta_{0} + a_{k[i]} + sp_{k[i]} + s_{j[i]} + e_{i} + m_{i}\
-(\#eq:MLMM)
-\end{equation} 
-$$ $$
-\begin{equation} 
-a_{k[i]}\sim N(0, \sigma^{2}_{phylogeny}\textbf{A}),\
-sp_{k[i]}\sim N(0, \sigma^{2}_{species}\textbf{I}),\
-s_{j[i]}\sim N(0, \sigma^{2}_{study}\textbf{I}),\
-e_{i}\sim N(0, \sigma^{2}_{residual}\textbf{I}),\
-m_{i} \sim N(0, v_{i})\
-(\#eq:dist)
-\end{equation} 
+Y_{i} = \beta_{0} + a_{k[i]} + sp_{k[i]} + s_{j[i]} + e_{i} + m_{i}\ \\
+a_{k[i]}\sim N(0, \sigma^{2}_{phylogeny}\textbf{A}), \\
+sp_{k[i]}\sim N(0, \sigma^{2}_{species}\textbf{I}), \\
+s_{j[i]}\sim N(0, \sigma^{2}_{study}\textbf{I}), \\
+e_{i}\sim N(0, \sigma^{2}_{residual}\textbf{I}), \\
+m_{i} \sim N(0, v_{i}\textbf{I}) \\
 $$
@@
 where $Y_{i}$ is the *i*th effect size (*i* = 1 ...
-$N_{ES}$, the number of effect sizes), $\beta_{0}$ is the overall meta-analytic mean, $a_{k[i]}$ is the phylogenetic effect (a random effect) for species *k* applied to effect size *i*.
-Phylogenetic effects are assumed to be normally distributed deviates sampled from a distribution with a mean of 0 and variance $\sigma^{2}_{phylogeny}$ [i.e., *N*$(0, \sigma^{2}_{phylogeny}\textbf{A})$], where $\textbf{A}$ is a phylogenetic correlation matrix derived from a phylogenetic tree, $sp_{k[i]}$ is the species-specific effect for the *k*th species applied to effect size *i*, $s_{j[i]}$ is the study-specific effect for the *j*th study applied to effect size *i*, $e_{i}$ is the effect size-specific effect (or within study effect, or residuals) for the *i*th effect size, and $m_{i}$ is the sampling variance effect around the *i*th effect as a result of variation in precision among each effect sizes, $v_{i}$, which is known as the sampling variance for effect.
+$N_{ES}$, the number of effect sizes), $\beta_{0}$ is the overall meta-analytic mean, $a_{k[i]}$ is the phylogenetic effect (a random effect) for species *k* applied to effect size *i* [i.e., species effects because of shared evolutionary history, @Cinar2021].
+Phylogenetic effects are assumed to be normally distributed deviates sampled from a distribution with a mean of 0 and variance $\sigma^{2}_{phylogeny}$ [i.e., *N*$(0, \sigma^{2}_{phylogeny}\textbf{A})$], where $\textbf{A}$ is a phylogenetic correlation matrix derived from a phylogenetic tree.
+$sp_{k[i]}$ is an additional species-specific effect for the *k*th species applied to effect size *i* [i.e., these are species-specific effects because of shared ecology and other factors, @Cinar2021], $s_{j[i]}$ is the study-specific effect for the *j*th study applied to effect size *i*, $e_{i}$ is the effect size-specific effect (or within study effect, or residuals) for the *i*th effect size, and $m_{i}$ is the sampling variance effect around the *i*th effect as a result of variation in precision among each effect sizes, $v_{i}$, which is known as the sampling variance for effect.
 This model is a 'weighted' multilevel meta-analysis model because the estimation of the overall meta-analytic mean, $\beta_{0}$, is weighted by the inverse sampling variance of each effect size.
-The fact that we can obtain an overall estimate of sampling variance (i.e., $\sigma^2_{m}$) is very important because it provides a way for us to understand just how much variation in effects are the result of sampling differences across studies versus other, potentially important sources of variation such as differences in the methods applied, species differences or even real biological effects that impact the effect size a study is likely to observe [@Nakagawa2017; @NakagawaSantos2012].
+Importantly, if we have effect sizes that are derived from the *same* sample of animals (or plants) (e.g., may be because many traits are measured on the same sets of animals) then we need to remove this dependency from the calculation of each $v_{i}$; we can then model the known sampling covariance between effect sizes by modifying \textbf{I} to include off-diagonals that account for this covariance [See Box 1 and @Noble2017].
+The fact that we can obtain an overall estimate of sampling variance (i.e., $\sigma^2_{m}$, see below for how it is defined) is very important because it provides a way for us to understand just how much variation in effects are the result of sampling differences across studies versus other, potentially important sources of variation such as differences in the methods applied, species differences or even real biological effects that impact the effect size a study is likely to observe [@Nakagawa2017; @NakagawaSantos2012].
 This is formalised in what we call 'heterogeneity analysis' which we describe below.
 Importantly, this model provides us with the answer to our overall question: Across all the species and studies manipulating egg corticosterone, how much of an overall effect does corticosterone have on reproduction relative to control conditions?
-<!--- don't we need to mention in the case of VCV for mi--->
 
-Of course, the overall effect does not provide us a way to interpret its magnitude in the context of how much CORT has been applied in the treatment.
+Of course, the overall effect does not provide us a way to interpret its magnitude in the context of how much CORT has been applied in the treatments used in the sample of studies.
 The most we can say about it, is that the effect is small, moderate or large out of the sample of effect sizes extracted from this set of studies.
@@
 When the model is refit with $c_{j}$ the estimated $\beta_{0}$ can now be more intuitively interpreted as the overall mean effect of CORT on reproduction at an average dosage difference between treatment and control groups.
-Importantly, by centering, we retain the original units (uL / g) of the variable, which can be very useful to allow for a more general interpretation of the effect magnitude (e.g., when the dosage different in 10 uL /g).
-This approach can even be extended to include other 'nuisance' variables that might creep into the dataset; the same centering can be done and the overall mean adjusted to include the new variable, in additional to dosage.
+Importantly, by centering, we retain the original units (uL / g) of the variable, which can be very useful to allow for a more general interpretation of the effect magnitude (e.g., when the dosage difference is 10 uL /g).
+Given it is very common to estimate and compare overall meta-analytic means (i.e., $B_{0}$) in meta-analyses this centering can be particularly useful in making these means more interpretable.Mean centering can even be extended to include other 'nuisance' variables that might creep into the dataset; the same centering can be done with a second variable, and the overall mean adjusted can be interpreted in the context of this new variable in additional to dosage.
 Of course, if one is not interested in the magnitude of effect, we could also change our question and simply model mean reproductive output as a function of dosage (often what are referred to as 'arm-based' meta-analytic models).
@@
 
-where *k* is the number of studies and the weights, $w_{i} = \frac{1}{v_{i}}$, can be calculated as the inverse of the sampling variance ($v_{i}$) for each effect size, *i*.
+where *k* is the number of studies and the weights, $w_{i} = \frac{1}{v_{i}}$, can be calculated using the inverse of the sampling variance ($v_{i}$) for each effect size, *i*.
 
@@
 Many readers will notice the similarities between $I^2$ and $R^2$ [@Nakgawa2013; @Nakagawa2010].
-If we want to formally assess how much effect size variation is the result of 'methodological factors 'nuisance' variation, such as temperature and dosage differences applied across studies, then we could fit our multilevel meta-regression model, including dosage or temperature (linear, quadratic or even more complex fits), and estimate how much variation is explained by these fixed effects following @Nakgawa2013.
+If we want to formally assess how much effect size variation is the result of 'nuisance' variation, such as temperature and dosage differences applied across studies, then we could fit our multilevel meta-regression model, including dosage or temperature (linear, quadratic or even more complex fits), and estimate how much variation is explained by these fixed effects following @Nakgawa2013.
 
@@
 In addition, if we were to repeat a study we would expect a new effect to fall within the range of 0.05 and 0.85, 95\% of the time [@Borenstein2019; @Nakagawa2021c].
-This is a very intuitive interpretation of how variable effects are, yet PIs are often not reported in meta-analyses [@Nakagawa2021c].
-As such, we encourage more meta-analysts to report these.
+This is a very intuitive interpretation of how variable effects are, yet PIs are often not reported in meta-analyses [@Nakagawa2021c], and we encourage more meta-analysts to report these.
 

### 2021-07-12 MS/box.Rmd
Tiny fix

@@
 The (sampling) standard error for $X_{1}$ is $SE_{1} = SD_{1} / \sqrt{N_{1}}$ -- many readers will probably know this as the formula for obtaining *SE* from *SD*.
-Given this, the sampling variance for $X_{1}$ is $SD^2_{1} / N_{1}$, which you see as an element of the sampling variance of ARR along with the sampling variance for $X_{2}$, which is $X_{1}$ is $SD^2_{1} / N_{1}$; the term $(1/(T_{2} - T_{1}))^2$ comes from recognizing $1/(T_{2} - T_{1})$ as a constant.
+Given this, the sampling variance for $X_{1}$ is $SD^2_{1} / N_{1}$, which you see as an element of the sampling variance of ARR along with the sampling variance for $X_{2}$, which is $X_{2}$ is $SD^2_{2} / N_{2}$; the term $(1/(T_{2} - T_{1}))^2$ comes from recognizing $1/(T_{2} - T_{1})$ as a constant.
 
@@
 $$
-\text{Var}(\text{AAR}) = \left( \frac{1} {T_{2} - T_{1}} \right)^2 
+\sigma^2_{AAR} = \left( \frac{1} {T_{2} - T_{1}} \right)^2 
 \left( 

### 2021-07-12 MS/ms.Rmd
Fixed word rendering of equation, finally.

@@
 $$
-Y_{i} = \beta_{0} + a_{k[i]} + sp_{k[i]} + s_{j[i]} + e_{i} + m_{i}\ \\
+\begin{split}
+Y_{i} = \beta_{0} + a_{k[i]} + sp_{k[i]} + s_{j[i]} + e_{i} + m_{i} \\
 a_{k[i]}\sim N(0, \sigma^{2}_{phylogeny}\textbf{A}), \\
@@
 m_{i} \sim N(0, v_{i}\textbf{I}) \\
+\end{split}
 $$

### 2021-07-12 MS/supp.Rmd
Updating download file from OSF because API is a pain in the butt. Fixed now, so just need to link to file and should download

@@
 # Citation
-This supplement is asscoaited with a special issue review paper and can be cited as follows:
+This supplement is associated with a special issue review paper and can be cited as follows:
 
@@
 ```{r loadpackages, echo = TRUE, class.source='klippy'}
-pacman::p_load(png, jpeg, pander, cowplot, flextable, tidyverse, metafor, orchaRd, here)
+pacman::p_load(png, jpeg, pander, cowplot, flextable, tidyverse, metafor, orchaRd, here, osfr)
 
@@
 # Example on how to download and load for reader. Should work anyway. Needs some testing
-download.file(url="https://ndownloader.figshare.com/files/7714777", destfile = "CaseStudy1.csv")
+osfr::osf_retrieve_file("https://osf.io/mnw5d/") %>% osfr::osf_download()
 
-data_CS1 <- read.csv(here("CaseStudy1.csv"))
+data_CS1 <- read.csv(here::here("CaseStudy1.csv"))
 
@@
 ```{r class.source='klippy'}
-download.file(url="REPLACE URL FROM OSF HERE", destfile = "CaseStudy2.csv")
 
-data_CS1 <- read.csv(here("CaseStudy2.csv"))
+osfr::osf_retrieve_file("https://osf.io/mnw5d/") %>% osfr::osf_download()
+
+data_CS1 <- read.csv(here::here("BPA_example.csv"))
+
+```
+
+```{r}
 

### 2021-07-12 R/survey_data_results.Rmd
Additional questions + finer categorisation in plots + minor fixes

@@
 title: "Survey Results from: Meta-analytic approaches and new effect sizes to account for heterogeneous effects in comparative physiology"
-author: Daniel W.A. Noble, Patrice Potter, Sammy Burke, Szymek Drobniak, Malgorzata Lagisz, Rose O’Dea, Shinichi Nakagawa
+author: Daniel W.A. Noble, Patrice Pottier, Sammy Burke, Szymek Drobniak, Malgorzata Lagisz, Rose O’Dea, Shinichi Nakagawa
 date: "`r Sys.Date()`"
@@
   ggplot() + tm +
-  geom_col(aes(x = meta_analysis_self_described, y = n), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
+  geom_col(aes(x = meta_analysis_self_described, y = n),
+           width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
   scale_y_continuous(expand=c(0,0)) +
@@
        y = "number of papers") 
+```
+
+How do the two categorisations (meta-analysis and comparative focus) combine?
+
+```{r}
+dat %>% 
+  ggplot() + tm +
+  geom_bar(aes(x = comparative_physiology_main_focus,
+               fill = meta_analysis_self_described,
+               y = ..count../sum(..count..)), width = 0.5,
+           colour = text.colour, size = 0.5) +
+  scale_y_continuous(expand=c(0,0)) +
+  scale_fill_viridis_d() +
+  labs(x = "main focus on comparative physiology",
+       y = "number of papers",
+       fill = "meta-analysis") 
 ```
@@
 
+Were effect sizes used in the analysis weighted by sampling variance?
+
 ```{r}
@@
 ### Effect size impacted by 'nuisance heterogeneity'? {.tabset .tabset-fade .tabset-pills}
+
+Could effect size be impacted by an additional continous predictor (e.g., temperature in thermal limit studies, dosage in hormone manipulation studies)?
 
@@
 
-Of the studis that said 'yes' how many actually modelled it or accounted for it?
+Of the studies that said 'yes' how many actually modelled it or accounted for it?
+
 ```{r}
@@
 ### Reported Heterogeneity? {.tabset .tabset-fade .tabset-pills}
-Of the studis that are weighted how many actually resported measures of heterogenity?
+
+Of the studies that are weighted how many actually reported measures of heterogeinity?
+
 ```{r}
@@
 
+### Handling sources of non-independence {.tabset .tabset-fade .tabset-pills}
+
+Did the analysis account for - or mention - additional non-independence arising from, e.g., phylogenetic relatedness or shared control treatments?
+The actual way of dealing with non-independence (n-i) will vary from study to study.
+
+```{r}
+dat %>%  janitor::tabyl(nonindependence_mentioned) %>% 
+  ggplot() + tm +
+  geom_col(aes(x = nonindependence_mentioned, y = percent), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
+  scale_y_continuous(expand=c(0,0), limits = c(0,1)) +
+  scale_x_discrete(labels = c('n-i dealt with w/o modelling', 'n-i modelled', 'unclear/other/not mentioned')) +
+  labs(x = "Non-independence handling",
+       y = "Frequency") 
+```
+
+### Publication bias {.tabset .tabset-fade .tabset-pills}
+
+What type of publication bias analysis was used in the analysis? Multiple metrics can be used per paper, hence frequencies won't sum to 100%.
+
+```{r}
+dat %>% dplyr::group_by(pub_bias_type) %>% janitor::tabyl(pub_bias_type) %>%
+  dplyr::summarise(GraphicalTest = dplyr::if_else(grepl("graphical tests", pub_bias_type), n, 0),
+                  RegressionTest = dplyr::if_else(grepl("regression test", pub_bias_type), n, 0),
+                    TrimAndFill = dplyr::if_else(grepl("trim-and-fill", pub_bias_type), n, 0),
+                 TimeLag = dplyr::if_else(grepl("time-lag", pub_bias_type), n, 0),
+                 OtherUnclear = dplyr::if_else(grepl("unclear", pub_bias_type), n, 0),
+                 None = dplyr::if_else(grepl("no", pub_bias_type), n, 0)) %>% 
+  colSums(.) %>% data.frame(effect = names(.), n = .) %>% mutate(prop = (n / sum(n)*100)) %>% arrange(effect) %>% 
+  ggplot() + tm + theme(axis.title.y = element_blank(),
+                        axis.text.y = element_text(size=8)) +
+  geom_col(aes(x = effect, y = n), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
+  scale_y_continuous(expand=c(0,0),breaks=seq(1,30,2)) +
+  scale_x_discrete(limits = c("None", "GraphicalTest", "RegressionTest", "TrimAndFill",
+                              "TimeLag", "OtherUnclear")) +
+  labs(x = "Effect Size",
+       y = "Number of Papers") +
+  coord_flip()
+```
+
 ## R Session Information   

### 2021-07-13 MS/supp.Rmd
small fix
Adding in meta-regression case study example for Szymek's dosage dataset. It needs to be corrected by S., but the skeleton is there now for how I am thinking about this

@@
 knitr::opts_chunk$set(echo = TRUE, cache = TRUE, tidy = TRUE)
+options(digits=2)
 ```
@@
 
-```{r loadpackages, echo = TRUE, class.source='klippy'}
-pacman::p_load(png, jpeg, pander, cowplot, flextable, tidyverse, metafor, orchaRd, here, osfr)
-
+```{r loadpackages, echo = TRUE, results = "hide", class.source='klippy'}
+#install.packages("pacman")
+pacman::p_load(devtools, png, jpeg, pander, cowplot, flextable, tidyverse, metafor, orchaRd, here, osfr, magrittr)
+devtools::install_github("itchyshin/orchard_plot", subdir = "orchaRd", force = TRUE, build_vignettes = TRUE)
 ```
@@
 # Example on how to download and load for reader. Should work anyway. Needs some testing
-osfr::osf_retrieve_file("https://osf.io/mnw5d/") %>% osfr::osf_download()
+#osfr::osf_retrieve_file("https://osf.io/mnw5d/") %>% osfr::osf_download()
 
-data_CS1 <- read.csv(here::here("CaseStudy1.csv"))
+#data_CS1 <- read.csv(here::here("CaseStudy1.csv"))
 
@@
 
-# Case Study 2:
-```{r class.source='klippy'}
+# Case Study 2: Multilevel Meta-regression Approaches to Control for Dosages
 
-osfr::osf_retrieve_file("https://osf.io/mnw5d/") %>% osfr::osf_download()
+In the next case study we'll demonstrate how to use multilevel meta-regression models to correct overall meta-analytic means for dosage differences applied across studies.
+The data in question was collected by @Podmola2018.
 
-data_CS1 <- read.csv(here::here("BPA_example.csv"))
+### Retrieve and Load the Data
+
+We'll first download the data from OSF, and load this into R. You can do this by copying and pasting the code below.
+
+```{r, class.source='klippy', results = 'hide'}
+
+# Download the data file from OSF
+osfr::osf_retrieve_file("https://osf.io/j85h3/") %>% osfr::osf_download(conflicts = "overwrite")
+
+# Load the data file.
+data_CS2 <- read.csv(here::here("ms", "Dosage_EggHormones_CS2.csv"), sep = ";")
 
@@
 
+### Interpreting Meta-analytic Menas Controlling for Dosages
+The data contains two columns of dosages....EXPLAIN all this.
+
+```{r}
+# Centre the dosage data on the mean. Note that, for comparability, we'll exclude 'NA' in dose so that models are fit with the exact same data.
+          data_CS2 %<>% mutate(z_total_dose_T = scale(total_dose_T, center = TRUE, scale = FALSE)) %>% filter(!is.na(z_total_dose_T))
+
+# Model that ignores "nuisance heterogeneity" for dosage applied
+     model_CS2_MLMA <- metafor::rma.mv(d ~ 1, V = var_d, random = list(~1|ID, ~1|paper), test = "t", dfs = "contain", data = data_CS2)
+     print(model_CS2_MLMA)
+
+# Calculate Prediction Intervals
+           pis_MLMA <- predict(model_CS2_MLMA)
+           print(pis_MLMA)
+
+# Calculate I2 as well
+                 I2 <- orchaRd::i2_ml(model_CS2_MLMA)
+                 print(I2)
+```
+
+We can see from above that the model 'ignoring' the nuisance heterogenity (model_CS2_MLMA) (i.e., the variability in effects resulting from dosage differences across studies) estimates an overall meta-analytic mean as `r coef(model_CS2_MLMA)` with a 95\% CI from `r model_CS2_MLMA$ci.lb` to `r model_CS2_MLMA$ci.ub`.
+Our prediction intervals suggest that heterogenity is high, reflected also in our $I_{total}^2$ estimate of `r I2[1]*100`\% -- 95\% of the time we expect the mean in repeated samples to fall between `r pis_MLMA$pi.lb` to `r pis_MLMA$pi.ub`.
+Approximately, `r I2[3]*100`\% of the total heterogenity is the result of differences between studies.
+Given that we have not controlled for dosage differences across studies all we can say is that the average SMD is rather small is the sample of studies that have applied these sets of dosages.
+In otherwords, on average, the means from the treatment and control groups differ by `r coef(model_CS2_MLMA)` standard deviation units.
+
+We can now model these dosage effects to control for 'nuisance heterogenity' and make the overall mean more interpretable.
+We'll first start by fitting and interpreting the coefficient just for the raw total dosage applied in a given study.
+To do this, we can now fit a multilevel meta-regression model as follows:
+
 ```{r}
 
+# Model that re-calibrates the overall meta-analytic mean (Intercept) to control for dosage administration
+    model_CS2_nuisance1 <- metafor::rma.mv(d ~ total_dose_T, V = var_d, random = list(~1|ID, ~1|paper), test = "t", dfs = "contain", data = data_CS2)
+    print(model_CS2_nuisance1)
 ```
+
+We can see from our model that controls for nuisance heterogenity (model_CS2_nuisance1) that we now estimate an overall meta-analytic mean as `r coef(model_CS2_nuisance1)[1]` with a 95\% CI from `r model_CS2_nuisance1$ci.lb[1]` to `r model_CS2_nuisance1$ci.ub[1]`.
+Importantly, this is the mean effect size when the total dosage applied is 0, which doesn't make much sense.
+As such, we can center total dosage applied to make the mean more 'meaningful' (mind the pun).
+
+```{r}
+
+# Model that re-calibrates the overall meta-analytic mean (Intercept) to control for dosage administration but uses centered dosage
+     model_CS2_nuisance2 <- metafor::rma.mv(d ~ z_total_dose_T, V = var_d, random = list(~1|ID, ~1|paper), test = "t", dfs = "contain", data = data_CS2)
+     print(model_CS2_nuisance2)
+
+# Calculate Prediction Intervals
+           pis_nuisance2 <- predict(model_CS2_nuisance2, newmods = 0)
+           print(pis_nuisance2)
+# Calculate I2 as well
+            I2_nuisance2 <- orchaRd::i2_ml(model_CS2_nuisance2)
+            print(I2_nuisance2)
+```
+
+Now that we have centered the total dosage around its mean (which is `r mean(data_CS2$total_dose_T, na.rm = TRUE)` uL difference(Szymek, not sure on units, sorry)) our overall meta-analytic mean (now estimated to be `r coef(model_CS2_nuisance2)[1]`,  with a 95\% CI from `r model_CS2_nuisance2$ci.lb[1]` to `r model_CS2_MLMA$ci.ub[1]`) is interpreted differently.
+Overall, the meta-analytic mean difference between treatments that differ by an average of `r mean(data_CS2$total_dose_T, na.rm = TRUE)` uL is `r coef(model_CS2_nuisance2)[1]` standard deviation units different.
+Its still a small overall effect size, but it has a clearer interpretation now.
+We can again calculate PI's and I^2 using the model.
+Overall, our prediction intervals suggest that heterogenity is still high even after accounting for dosage reflected also in our $I_{total}^2$ estimate of `r I2_nuisance2[1]*100`\% -- indeed, 95\% of the time we expect the mean in repeated samples to fall between `r pis_nuisance2$pi.lb[1]` to `r pis_nuisance2$pi.ub[1]`.
 
@@
 ```
+
+# References

### 2021-07-13 MS/supp.Rmd
Jusr fixing some spelling, plus also fxiing interprettaion to be more clear

@@
 
-```{r loadpackages, echo = TRUE, results = "hide", class.source='klippy'}
+```{r loadpackages, echo = TRUE, results = "hide", messages = FALSE, class.source='klippy'}
 #install.packages("pacman")
@@
 
-### Interpreting Meta-analytic Menas Controlling for Dosages
+### Interpreting Meta-analytic Means Controlling for Dosages
 The data contains two columns of dosages....EXPLAIN all this.
@@
 Its still a small overall effect size, but it has a clearer interpretation now.
-We can again calculate PI's and I^2 using the model.
-Overall, our prediction intervals suggest that heterogenity is still high even after accounting for dosage reflected also in our $I_{total}^2$ estimate of `r I2_nuisance2[1]*100`\% -- indeed, 95\% of the time we expect the mean in repeated samples to fall between `r pis_nuisance2$pi.lb[1]` to `r pis_nuisance2$pi.ub[1]`.
+We can again calculate PI's and $I^2$ using the model.
+Overall, our prediction intervals suggest that heterogenity is still high even after accounting for dosage reflected also in our $I_{total}^2$ estimate of `r I2_nuisance2[1]*100`\% -- indeed, 95\% of the time we expect the mean in repeated samples to fall between `r pis_nuisance2$pi.lb[1]` to `r pis_nuisance2$pi.ub[1]` when the average dosage differenc applied is `r mean(data_CS2$total_dose_T, na.rm = TRUE)` uL.
 

### 2021-07-13 MS/supp.Rmd
Spelling error fixed.

@@
 We can again calculate PI's and $I^2$ using the model.
-Overall, our prediction intervals suggest that heterogenity is still high even after accounting for dosage reflected also in our $I_{total}^2$ estimate of `r I2_nuisance2[1]*100`\% -- indeed, 95\% of the time we expect the mean in repeated samples to fall between `r pis_nuisance2$pi.lb[1]` to `r pis_nuisance2$pi.ub[1]` when the average dosage differenc applied is `r mean(data_CS2$total_dose_T, na.rm = TRUE)` uL.
+Overall, our prediction intervals suggest that heterogenity is still high even after accounting for dosage reflected also in our $I_{total}^2$ estimate of `r I2_nuisance2[1]*100`\% --  95\% of the time we expect the mean in repeated samples to fall between `r pis_nuisance2$pi.lb[1]` to `r pis_nuisance2$pi.ub[1]` when the average dosage difference applied is `r mean(data_CS2$total_dose_T, na.rm = TRUE)` uL.
 

### 2021-07-13 MS/supp.Rmd
Try to save time in rendering

@@
 pacman::p_load(devtools, png, jpeg, pander, cowplot, flextable, tidyverse, metafor, orchaRd, here, osfr, magrittr)
-devtools::install_github("itchyshin/orchard_plot", subdir = "orchaRd", force = TRUE, build_vignettes = TRUE)
+devtools::install_github("itchyshin/orchard_plot", subdir = "orchaRd", force = TRUE)
 ```

### 2021-07-13 MS/box.Rmd
Added a first crack at cerating a temperature standardised SMD

@@
 
+### Controlling for unitary differences and temperature across studies
+
+ARR assumes that the units for the mean difference across studies is consistent.
+This will often not be the case for many meta-analyses that hope to synthesise a wide diversity of trait types that vary in their units (e.g., ul/g, grams, seconds, minutes).
+Fortunately, $lnRR$ and SMD (Table 1) already control for unitary differences.
+As such, we can apply some of the same logic we discuss above to SMD, to correct for both temperature differences.
+Table 1 provides the formula for SMD, it's pooled standard deviation, and sampling variance.
+We won't re-iterate these formulas again.
+Just like with ARR we can apply our temperature correction to the SMD formula as follows:
+
+$$
+SMD_{T} = \frac{\left(\bar{X}_{2} - \bar{X}_{1}\right)}{SD_{p}\left( T_{2} - T_{1}\right)}J
+$$
+Here, we can see that the difference between $X_1$ and $X_2$ is standardised by the pooled SD, essentially correcting for unitary differences.
+Dividing SMD by the temperature difference on top of that results in correcting the effect size further by temperature.
+To derive the sampling variance for $SMD_T$ we can apply the same principles as we did above to derive an approximate sampling variance as:
+
+$$
+s_{SMD_{T}}^2 = \left(\frac{1}{{T_{2} - T_{1}}}\right)^2 +  \frac{N_{1} + N_{2}}{N_{1}N_{2}}  + \frac{SMD_{T}^2}{2\left( N_{1} + N_{2}\right)}
+$$
 ### Sampling variance for the difference between two slopes

### 2021-07-13 MS/box.Rmd
Just reorganised section of box to make flow better. First gcrack at temperature corrected SMD.

@@
 
-## *BOX 1: Example of how to derive sampling variance*
+## *BOX 1: Examples of how to derive sampling variances*
 
@@
 temperature, salinity, acidity).
-We also go on to derive sampling variance for the difference between two slopes so that we can use powerful meta-analytic models using this effect size.
+We also go on to derive sampling variance for the difference between two slopes, and finally end on showing how SMD can be corrected to account for both unitary and temperature differences across effect sizes.
+The sampling variances associated with these 'new' effect sizes will allow one to take advantage of powerful meta-analytic models.
 
@@
 
-### Controlling for unitary differences and temperature across studies
-
-ARR assumes that the units for the mean difference across studies is consistent.
-This will often not be the case for many meta-analyses that hope to synthesise a wide diversity of trait types that vary in their units (e.g., ul/g, grams, seconds, minutes).
-Fortunately, $lnRR$ and SMD (Table 1) already control for unitary differences.
-As such, we can apply some of the same logic we discuss above to SMD, to correct for both temperature differences.
-Table 1 provides the formula for SMD, it's pooled standard deviation, and sampling variance.
-We won't re-iterate these formulas again.
-Just like with ARR we can apply our temperature correction to the SMD formula as follows:
-
-$$
-SMD_{T} = \frac{\left(\bar{X}_{2} - \bar{X}_{1}\right)}{SD_{p}\left( T_{2} - T_{1}\right)}J
-$$
-Here, we can see that the difference between $X_1$ and $X_2$ is standardised by the pooled SD, essentially correcting for unitary differences.
-Dividing SMD by the temperature difference on top of that results in correcting the effect size further by temperature.
-To derive the sampling variance for $SMD_T$ we can apply the same principles as we did above to derive an approximate sampling variance as:
-
-$$
-s_{SMD_{T}}^2 = \left(\frac{1}{{T_{2} - T_{1}}}\right)^2 +  \frac{N_{1} + N_{2}}{N_{1}N_{2}}  + \frac{SMD_{T}^2}{2\left( N_{1} + N_{2}\right)}
-$$
 ### Sampling variance for the difference between two slopes
@@
 
+### Controlling for unitary differences and temperature across studies
+
+ARR assumes that the units for the mean difference across studies is consistent.
+This will often not be the case for many meta-analyses that hope to synthesise a wide diversity of trait types that vary in their units (e.g., ul/g, grams, seconds, minutes).
+Fortunately, $lnRR$ and SMD (Table 1) already control for unitary differences.
+As such, we can apply some of the same logic we discuss above to SMD to correct for both temperature and unitary differences.
+Table 1 provides the formula for SMD, it's pooled standard deviation, and sampling variance.
+We won't re-iterate these formulas again.
+Just like with ARR we can apply our temperature correction to the SMD formula as follows:
+
+$$
+SMD_{T} = \frac{\left(\bar{X}_{1} - \bar{X}_{2}\right)}{SD_{p}\left( T_{2} - T_{1}\right)}J
+$$
+
+Here, we can see that the difference between $X_1$ and $X_2$ is standardised by the pooled SD, essentially correcting for unitary differences.
+Dividing SMD by the temperature difference on top of that results in correcting the effect size further by temperature.
+To derive the sampling variance for $SMD_T$ we can apply the same principles as we did above to derive an approximate sampling variance as:
+
+$$
+s_{SMD_{T}}^2 = \left(\frac{1}{{T_{2} - T_{1}}}\right)^2 +  \frac{N_{1} + N_{2}}{N_{1}N_{2}}  + \frac{SMD_{T}^2}{2\left( N_{1} + N_{2}\right)}
+$$
+
 ### The Delta Method

### 2021-07-14 MS/ms.Rmd
Adding some survey results. They don't need to be too big.

@@
 #### *Current Meta-analytic Practices in Comparative Physiology*
+
+```{r setup2, include=FALSE}
+rm(list=ls())
+
+pacman::p_load(dplyr,ggplot2,here, pander, janitor)
+
+# loading data
+raw <- read.csv(here("data","MA_CompPysio_Survey.csv"))
+metadata <- read.csv(here("data","MA_CompPysio_Survey_metadata.csv"))
+
+# tidying data
+dat <- raw
+names(dat) <- metadata$Procesed.Column.Name[match(names(dat), metadata$Raw.Column.Name)]
+
+# tidying categorical options
+dat$meta_analysis_self_described <- factor(gsub(" \\(.*", "", dat$meta_analysis_self_described), levels = c("yes","no","unclear/other"))
+dat$comparative_physiology_main_focus <- factor(gsub(" \\(.*", "", dat$comparative_physiology_main_focus), levels = c("yes","no","unclear/other"))
+
+# fixing format of journals
+
+#dat$DOI[dat$journal=="2017"] # Typo
+dat$journal[dat$journal=="2017"] <- "Biology Letters"
+
+#dat$DOI[grep("Proceedings", dat$journal)] # all the same journal
+dat$journal[grep("Proceedings", dat$journal)] <- "Proceedings of the Royal Society B: Biological Sciences"
+
+# standardising DOI format
+dat$DOI <- gsub(".*org/", "", dat$DOI)
+dat$DOI <-gsub(".* ", "", dat$DOI)
+
+# ggplot2 theme for plots
+background.colour <- "white"
+text.colour <- "black"
+# Font Choice
+#loadfonts()
+text.font <- "Arial"
+
+tm <- theme(panel.background = element_rect(fill = background.colour),
+            plot.background = element_rect(fill = background.colour),
+            panel.grid = element_blank(),
+            text =  element_text(family = text.font, colour = text.colour),
+            axis.text = element_text(colour = text.colour),
+            axis.title.x = element_text(margin = margin(10,0,0,0)),
+            axis.title.y = element_text(margin = margin(0,10,0,0)),
+            axis.line = element_line(colour = text.colour, size = 0.5),
+            axis.ticks = element_line(colour = text.colour, size = 0.5),
+            plot.title = element_text(hjust = 0.5),
+            legend.background = element_rect(fill = background.colour),
+            legend.key = element_rect(fill = background.colour),
+            plot.margin = margin(6,6,6,6))
+
+effects <- dat %>% dplyr::group_by(effect_size_type) %>% janitor::tabyl(effect_size_type) %>%
+  dplyr::summarise(SMD = dplyr::if_else(grepl("SMD", effect_size_type), n, 0),
+                  lnRR = dplyr::if_else(grepl("Response Ratio", effect_size_type), n, 0),
+                    Zr = dplyr::if_else(grepl("correlation", effect_size_type), n, 0),
+                 Other = dplyr::if_else(grepl("other|Q10", effect_size_type), n, 0),
+                 Means = dplyr::if_else(grepl("mean/proportion/raw", effect_size_type), n, 0),
+                 lnCVR = dplyr::if_else(grepl("lnCVR", effect_size_type), n, 0),
+                 Slope = dplyr::if_else(grepl("slope", effect_size_type), n, 0)) %>% 
+  colSums(.) %>% data.frame(effect = names(.), n = .) %>% mutate(prop = n / sum(n)) %>% arrange(prop)
+
+hetero <- dat %>%  janitor::tabyl(cont_moderator_variable)
+hetero_dealt <- dat %>%  filter(!cont_moderator_variable_modelled=="") %>% janitor::tabyl(cont_moderator_variable_modelled)
+weighted <- dat %>% janitor::tabyl(meta_analysis_weighted) 
+weighted_meta <- dat %>% filter(meta_analysis_self_described == "yes") %>% janitor::tabyl(meta_analysis_weighted) 
+```
+
+Quantitative syntheses in comparative physiology commonly analyse raw summary statistics (`r with(effects, effects[effect == "Means","prop"])*100`\% of studies), followed closely by Fishers transformed correlation coefficients (Zr) (`r with(effects, effects[effect == "Zr","prop"])*100`\% of studies), standardised mean differences (SMD) and log response ratios (lnRR) (`r with(effects, effects[effect == "SMD","prop"])*100`\% and `r with(effects, effects[effect == "lnRR","prop"])*100`\%, respectively - See *Supplementary Materials* for a full breakdown).
+In many cases, studies make use of multiple effect size measures.
+Approximately `r with(hetero, hetero[cont_moderator_variable == "yes","percent"])*100`\% of effect sizes used within the study were deemed to be impacted by 'nuisance hetreogenity' in some form or another, and of the studies where this was the case, only `r with(hetero_dealt, hetero_dealt[cont_moderator_variable_modelled == "yes","percent"])*100`\% of the studies clearly dealt with it; usually through meta-regression modelling.
+Overall, `r with(weighted, weighted[meta_analysis_weighted == "weighted model","percent"])*100`\% of studies used a weighted meta-analytic model, however, of the studies self described as 'meta-analyses', `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","percent"])*100`\% (N = `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","n"])` of `r with(weighted_meta, sum(weighted_meta[,"n"]))`) did not actually weight their meta-analytic mean.
+
+```{r, fig1, fig.cap="test"}
+p1 = 
+p2 = dat %>% mutate(cont_moderator_variable_modelled = if_else(cont_moderator_variable_modelled == "", "N/A", cont_moderator_variable_modelled)) %>% 
+  ggplot() + tm +
+  geom_bar(aes(x = cont_moderator_variable,
+               fill = cont_moderator_variable_modelled,
+               y = ..count../sum(..count..)), width = 0.5,
+           colour = text.colour, size = 0.5) +
+  scale_y_continuous(expand=c(0,0), limits = c(0,1)) +
+  scale_fill_viridis_d() +
+  labs(x = "Nuisance Heterogenity?",
+       y = "Proportion",
+       fill = "Modelled Nuisance\n Heterogenity?")
+
+```
 

### 2021-07-14 R/survey_data_results.Rmd
Adding some more finesclae resolution to quetsions

@@
 
+How do the two categorisations (meta-analysis and weighting) combine?
+
+```{r}
+dat %>% 
+  ggplot() + tm +
+  geom_bar(aes(x = meta_analysis_self_described,
+               fill = meta_analysis_weighted,
+               y = ..count../sum(..count..)), width = 0.5,
+           colour = text.colour, size = 0.5) +
+  scale_y_continuous(expand=c(0,0), limits = c(0,1)) +
+  scale_fill_viridis_d() +
+  labs(x = "Meta-analysis?",
+       y = "Proportion",
+       fill = "Weighted?") 
+```
+
 ### Effect size impacted by 'nuisance heterogeneity'? {.tabset .tabset-fade .tabset-pills}
@@
        y = "Frequency") 
+```
+
+```{r}
+dat %>% mutate(cont_moderator_variable_modelled = if_else(cont_moderator_variable_modelled == "", "N/A", cont_moderator_variable_modelled)) %>% 
+  ggplot() + tm +
+  geom_bar(aes(x = cont_moderator_variable,
+               fill = cont_moderator_variable_modelled,
+               y = ..count../sum(..count..)), width = 0.5,
+           colour = text.colour, size = 0.5) +
+  scale_y_continuous(expand=c(0,0), limits = c(0,1)) +
+  scale_fill_viridis_d() +
+  labs(x = "Nuisance Heterogenity?",
+       y = "Proportion",
+       fill = "Modelled Nuisance\n Heterogenity?") 
 ```

### 2021-07-14 MS/ms.Rmd
Added survey results relevant to questioons, plus a figure.

@@
 
-pacman::p_load(dplyr,ggplot2,here, pander, janitor)
+pacman::p_load(dplyr,ggplot2,here, pander, janitor, patchwork)
 
@@
 weighted_meta <- dat %>% filter(meta_analysis_self_described == "yes") %>% janitor::tabyl(meta_analysis_weighted)
+
+summary <-  dat %>% dplyr::group_by(stat_model_type) %>% janitor::tabyl(stat_model_type) %>%
+  dplyr::summarise(`Multilevel Meta-analysis Model` = dplyr::if_else(grepl("multilevel meta-analysis", stat_model_type), n, 0),
+                  `Multilevel Metaregression Model` = dplyr::if_else(grepl("meta-regression models", stat_model_type), n, 0),
+                    `Linear Regression` = dplyr::if_else(grepl("linear regression", stat_model_type), n, 0),
+                 Other = dplyr::if_else(grepl("unclear/other", stat_model_type), n, 0),
+                 `Vote Counting` = dplyr::if_else(grepl("vote counting", stat_model_type), n, 0),
+                 `Weighted Regression` = dplyr::if_else(grepl("weighted regression including mixed effects models", stat_model_type), n, 0),
+                 `Random Effects Model` = dplyr::if_else(grepl("random-effects meta-analysis", stat_model_type), n, 0)) %>% 
+  colSums(.) %>% data.frame(effect = names(.), n = .) %>% mutate(prop = (n / sum(n))) %>% arrange(effect)
+rownames(summary) <- NULL
+
+het_reported <- dat %>%  filter(!heterogeneity_reported=="N/A (e.g.
+they conducted unweighted meta-analysis)") %>% mutate(heterogeneity_reported = if_else(heterogeneity_reported == "unclear/other (add comment)", "other", heterogeneity_reported)) %>% janitor::tabyl(heterogeneity_reported)
 ```
 
-Quantitative syntheses in comparative physiology commonly analyse raw summary statistics (`r with(effects, effects[effect == "Means","prop"])*100`\% of studies), followed closely by Fishers transformed correlation coefficients (Zr) (`r with(effects, effects[effect == "Zr","prop"])*100`\% of studies), standardised mean differences (SMD) and log response ratios (lnRR) (`r with(effects, effects[effect == "SMD","prop"])*100`\% and `r with(effects, effects[effect == "lnRR","prop"])*100`\%, respectively - See *Supplementary Materials* for a full breakdown).
+Quantitative syntheses in comparative physiology commonly analyse raw summary statistics (`r with(effects, effects[effect == "Means","prop"])*100`\% of studies), followed closely by Fishers transformed correlation coefficients (Zr) (`r with(effects, effects[effect == "Zr","prop"])*100`\% of studies), standardised mean differences (SMD) and log response ratios (lnRR) (`r with(effects, effects[effect == "SMD","prop"])*100`\% and `r with(effects, effects[effect == "lnRR","prop"])*100`\%, respectively; Figure \@ref(fig:fig1)A).
 In many cases, studies make use of multiple effect size measures.
-Approximately `r with(hetero, hetero[cont_moderator_variable == "yes","percent"])*100`\% of effect sizes used within the study were deemed to be impacted by 'nuisance hetreogenity' in some form or another, and of the studies where this was the case, only `r with(hetero_dealt, hetero_dealt[cont_moderator_variable_modelled == "yes","percent"])*100`\% of the studies clearly dealt with it; usually through meta-regression modelling.
+Approximately `r with(hetero, hetero[cont_moderator_variable == "yes","percent"])*100`\% of effect sizes used within the study were deemed to be impacted by 'nuisance heterogeneity' in some form or another (Figure \@ref(fig:fig1)B), and of the studies where this was the case, only `r with(hetero_dealt, hetero_dealt[cont_moderator_variable_modelled == "yes","percent"])*100`\% of the studies clearly dealt with it (Figure \@ref(fig:fig1)B); usually through meta-regression modelling.
 Overall, `r with(weighted, weighted[meta_analysis_weighted == "weighted model","percent"])*100`\% of studies used a weighted meta-analytic model, however, of the studies self described as 'meta-analyses', `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","percent"])*100`\% (N = `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","n"])` of `r with(weighted_meta, sum(weighted_meta[,"n"]))`) did not actually weight their meta-analytic mean.
+Many studies used 'Linear Regression' (including linear and generalised linear mixed effects models) as the main type of model fit to the data (Figure \@ref(fig:fig1)C).
+Of the studies using weighted meta-analytic models `r with(het_reported, sum(het_reported[1:2,"percent"])*100)`\% (N = `r with(het_reported, sum(het_reported[1:2,"n"]))` meta-analyses) did not report any measure of heterogeneity.
 
-```{r, fig1, fig.cap="test"}
-p1 = 
+```{r, fig1, fig.cap="**Summary of meta-analytic practices in comparative physiology.** (A) Different types of effect measures commonly used in meta-analyses and their releative frequency of use.
+(B) how many meta-analyses where 'nuisance heterogenity' have the potential to impact effect sizes, and the proportion of studies explicitly dealing with nuisance heterogenity.
+(C) Frequency of analytical approaches used to analyse effect measures.
+Note that only 'Weighted Regression', 'Random Effects Models', 'Multilevel Metaregression Models' and 'Multilevel Meta-analysis Models' are weighted models."}
+p1 = dat %>% dplyr::group_by(effect_size_type) %>% janitor::tabyl(effect_size_type) %>%
+  dplyr::summarise(SMD = dplyr::if_else(grepl("SMD", effect_size_type), n, 0),
+                  lnRR = dplyr::if_else(grepl("Response Ratio", effect_size_type), n, 0),
+                    Zr = dplyr::if_else(grepl("correlation", effect_size_type), n, 0),
+                 Other = dplyr::if_else(grepl("other|Q10", effect_size_type), n, 0),
+                 Means = dplyr::if_else(grepl("mean/proportion/raw", effect_size_type), n, 0),
+                 lnCVR = dplyr::if_else(grepl("lnCVR", effect_size_type), n, 0),
+                 Slope = dplyr::if_else(grepl("slope", effect_size_type), n, 0)) %>% 
+  colSums(.) %>% data.frame(effect = names(.), n = .) %>% mutate(prop = n / sum(n)) %>% arrange(effect) %>% 
+  ggplot() + tm + 
+  geom_col(aes(x = effect, y = prop), width = 0.5, fill = "black", colour = text.colour, size = 0.5) +
+  scale_y_continuous(expand=c(0,0), limits = c(0,0.35)) +
+  labs(x = "Effect Size",
+       y = "Frequency") +
+  coord_flip()
+
 p2 = dat %>% mutate(cont_moderator_variable_modelled = if_else(cont_moderator_variable_modelled == "", "N/A", cont_moderator_variable_modelled)) %>% 
@@
   scale_fill_viridis_d() +
-  labs(x = "Nuisance Heterogenity?",
-       y = "Proportion",
-       fill = "Modelled Nuisance\n Heterogenity?")
+  theme(legend.position = c(0.50, 0.8)) + 
+  labs(x = "Nuisance Heterogeneity?",
+       y = "Frequency",
+       fill = "Modeled Nuisance\nHeterogeneity?") 
+p3 <- summary %>% 
+  ggplot() + tm +
+  geom_col(aes(x = effect, y = prop), width = 0.5, fill = "black", colour = text.colour, size = 0.5) +
+  scale_y_continuous(expand=c(0,0),limits = c(0,0.4)) +
+  labs(x = "Analytical Approach",
+       y = "Frequency") +
+  coord_flip()
+
+p1 + p2 + p3 + plot_annotation(tag_levels = c("A"), tag_prefix = "(", tag_suffix = ")")
 
@@
 ```{r tablea, echo = FALSE, tab.cap = "Common effect sizes used throughout meta-analyses in comparative physiology, their associated sampling variances and examples on when they might be used."}
+
+FitFlextableToPage <- function(ft, pgwidth = 6){
+
+  ft_out <- ft %>% autofit()
+
+  ft_out <- width(ft_out, width = dim(ft_out)$widths*pgwidth /(flextable_dim(ft_out)$widths))
+  return(ft_out)
+}
 
@@
 
-tablea
+FitFlextableToPage(tablea, pgwidth = 8)
 

### 2021-07-14 R/survey_data_results.Rmd
Updated ccache

@@
 
-pacman::p_load(dplyr,ggplot2,here, pander, janitor)
+pacman::p_load(dplyr,ggplot2,here, pander, janitor, magrittr)
 
@@
 ```{r}
-dat %>% dplyr::group_by(stat_model_type) %>% janitor::tabyl(stat_model_type) %>%
-  dplyr::summarise(MLMA = dplyr::if_else(grepl("multilevel meta-analysis", stat_model_type), n, 0),
-                  MLMR = dplyr::if_else(grepl("meta-regression models", stat_model_type), n, 0),
-                    LinearRegrs = dplyr::if_else(grepl("linear regression", stat_model_type), n, 0),
+summary <-  dat %>% dplyr::group_by(stat_model_type) %>% janitor::tabyl(stat_model_type) %>%
+  dplyr::summarise(`Multilevel Meta-analysis Model` = dplyr::if_else(grepl("multilevel meta-analysis", stat_model_type), n, 0),
+                  `Multilevel Metaregression Model` = dplyr::if_else(grepl("meta-regression models", stat_model_type), n, 0),
+                    `Linear Regression` = dplyr::if_else(grepl("linear regression", stat_model_type), n, 0),
                  Other = dplyr::if_else(grepl("unclear/other", stat_model_type), n, 0),
-                 Vote = dplyr::if_else(grepl("vote counting", stat_model_type), n, 0),
-                 WeightedReg = dplyr::if_else(grepl("weighted regression including mixed effects models", stat_model_type), n, 0),
-                 RE = dplyr::if_else(grepl("random-effects meta-analysis", stat_model_type), n, 0)) %>% 
-  colSums(.) %>% data.frame(effect = names(.), n = .) %>% mutate(prop = (n / sum(n)*100)) %>% arrange(effect) %>% 
-  ggplot() + tm + theme(axis.title.y = element_blank(),
-                        axis.text.y = element_text(size=8)) +
-  geom_col(aes(x = effect, y = n), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
-  scale_y_continuous(expand=c(0,0),breaks=seq(1,20,2)) +
-  labs(x = "Effect Size",
-       y = "Number of Papers") +
+                 `Vote Counting` = dplyr::if_else(grepl("vote counting", stat_model_type), n, 0),
+                 `Weighted Regression` = dplyr::if_else(grepl("weighted regression including mixed effects models", stat_model_type), n, 0),
+                 `Random Effects Model` = dplyr::if_else(grepl("random-effects meta-analysis", stat_model_type), n, 0)) %>% 
+  colSums(.) %>% data.frame(effect = names(.), n = .) %>% mutate(prop = (n / sum(n))) %>% arrange(effect)
+rownames(summary) <- NULL
+
+summary %>% 
+  ggplot() + tm +
+  geom_col(aes(x = effect, y = prop), width = 0.5, fill = "black", colour = text.colour, size = 0.5) +
+  scale_y_continuous(expand=c(0,0),limits = c(0,0.4)) +
+  labs(x = "Analytical Approach",
+       y = "Frequency") +
   coord_flip()

### 2021-07-14 MS/box.Rmd
Fixed equations so they are uniform with MS

@@
 csl: ../bib/the-journal-of-experimental-biology.csl
-output: html_document
+output: 
+  bookdown::html_document2:
+    code_folding: hide
+    number_sections: no
+    toc: no
+    toc_depth: 6
+    toc_float: yes
+    bibliography: refs.bib
+  bookdown::word_document2:
+    toc: no
+    toc_depth: 6
+    number_sections: false
+    reference_docx: template.docx
+editor_options: 
+  chunk_output_type: console
 ---
@@
 $$
-\text{ARR} = \frac{X_{1} - X_{2}}{T_2 - T_1},
+\text{ARR} = \frac{M_{1} - M_{2}}{T_2 - T_1},
 $$
 
-where *T* stands for temperature in degrees Celsius and $T_{2} > T_{1}$, and $X_{1}$ and $X_{2}$ are the average physiological responses (estimated means) at two temperature points $T_{1}$ and $T_{2}$.
+where *T* stands for temperature in degrees Celsius and $T_{2} > T_{1}$, and $M_{1}$ and $M_{2}$ are the average physiological responses (estimated means) at two temperature points $T_{1}$ and $T_{2}$.
 
 To obtain the sampling variance for this equation (slope), we need to know several basic properties of variance.
-Let's assume $X_{1}$ is a random variable, which means that this variable has a mean and standard deviation (variance).
-Multiplying a constant ($a$) will change the variance by the square of that constant ($a^2$) while adding or subtracting the constant ($b$) does not change the variance of $X_{1}$.
+Let's assume $M_{1}$ is a random variable, which means that this variable has a mean and standard deviation (variance).
+Multiplying a constant ($a$) will change the variance by the square of that constant ($a^2$) while adding or subtracting the constant ($b$) does not change the variance of $M_{1}$.
 This can be summarized as:
@@
 
-Also, when adding two random variables ($X_{1}$ and $X_{2}$), the combined variance is the sum of the variance of $X_{1}$  and the variance of $X_{2}$ plus 2 times the covariance between $X_{1}$ and $X_{2}$.
+Also, when adding two random variables ($M_{1}$ and $M_{2}$), the combined variance is the sum of the variance of $X_{1}$  and the variance of $X_{2}$ plus 2 times the covariance between $M_{1}$ and $M_{2}$.
 This relationship can be written as:
@@
 $$
-\sigma^2_{X_1 \pm X_2} = \sigma^2_{X_1} + \sigma^2_{X_2} \pm 2\text{Cov}(X_1,X_2) \\
-= \sigma^2_{X_1} + \sigma^2_{X_2} \pm 2\text{Cor}(X_1,X_2)\sqrt{ \sigma^2_{X_1} \sigma^2_{X_2} }
+\sigma^2_{M_1 \pm M_2} = \sigma^2_{M_1} + \sigma^2_{M_2} \pm 2\text{Cov}(M_1,M_2) 
+= \sigma^2_{M_1} + \sigma^2_{M_2} \pm 2\text{Cor}(M_1,M_2)\sqrt{ \sigma^2_{M_1} \sigma^2_{M_2} }
 $$ 
-where the co-variance $\text{Cov}(X_1,X_2)$ equals to the correlation multiplied by the square-root of the two variances $2\text{Cor}(X_1,X_2)\sqrt{ \sigma^2_{X_1} \sigma^2_{X_2} }$.
+where the co-variance $\text{Cov}(M_1,M_2)$ equals to the correlation multiplied by the square-root of the two variances $2\text{Cor}(M_1,M_2)\sqrt{ \sigma^2_{M_1} \sigma^2_{M_2} }$.
 
-Importantly, when $X_{1}$ and $X_{2}$ are independent of each other the covariance is 0.
+Importantly, when $M_{1}$ and $M_{2}$ are independent of each other the covariance is 0.
 More concretely, if measurements are done on two different groups of animals at two different temperature points ($T_1$ and $T_2$), then the co-variances between these two sets of measurements are 0.
 
-Therefore, when $X_{1}$ and $X_{2}$ are independent, we can obtain the sampling variance for ARR as:
+Therefore, when $M_{1}$ and $M_{2}$ are independent, we can obtain the sampling variance for ARR as:
 
@@
 Now, it is not uncommon that we use the same group of animals (or plants) at two temperature points.
-If we do, however, then we need to add the co-variance between $X_{1}$ and $X_{2}$ ($\text{Cov}(X_{1},X_{2})$); note that as above, the co-variance equals the corresponding correlation multiplied by the square-root of two (sampling) variances.
+If we do, however, then we need to add the co-variance between $M_{1}$ and $M_{2}$ ($\text{Cov}(M_{1},M_{2})$); note that as above, the co-variance equals the corresponding correlation multiplied by the square-root of two (sampling) variances.
 Therefore, the sampling variance can be now written as:
@@
 $$
+
 By assuming the number of animals (*N*) are the same at the two temperature points, we can slightly simplify this formula:
@@
 
-where *r* is the correlation between a set of measurement $X_1$ and $X_2$ form the same individuals at two point $T_1$ and $T_2$.
+where *r* is the correlation between a set of measurement $M_1$ and $M_2$ form the same individuals at two point $T_1$ and $T_2$.
 As you may notice, we need raw data to calculate *r*.
@@
 $$
-\text{Var}(\text{ARRD}) = \left( \frac{1} {T_2 - T_1} \right)^2 
+\sigma^2_{ARRD} = \left( \frac{1} {T_2 - T_1} \right)^2 
 \left( \frac{SD^2_{f1}} {N_{f1}} + \frac{SD^2_{f2}} {N_{f2}} +
@@
 \right),
-$$ where subscripts *f* and *m* stands for 'females' and 'males'.
+$$
+
+where subscripts *f* and *m* stands for 'females' and 'males'.
 
@@
 $$
-\text{Var}(\text{ARRD}) = \left( \frac{1} {T_2 - T_1} \right)^2 
+\sigma^2_{ARRD} = \left( \frac{1} {T_2 - T_1} \right)^2 
 \left( 
@@
 $$
-\text{Var}(\text{ARRD}) = \left( \frac{1} {T_4 - T_3} \right)^2 
+\sigma^2_{ARRD} = \left( \frac{1} {T_4 - T_3} \right)^2 
 \left( 
@@
 $$
-SMD_{T} = \frac{\left(\bar{X}_{1} - \bar{X}_{2}\right)}{SD_{p}\left( T_{2} - T_{1}\right)}J
+SMD_{T} = \frac{\left(M_{1} - M_{2}\right)}{SD_{p}\left( T_{2} - T_{1}\right)}J
 $$
 
-Here, we can see that the difference between $X_1$ and $X_2$ is standardised by the pooled SD, essentially correcting for unitary differences.
+Here, we can see that the difference between $M_1$ and $M_2$ is standardised by the pooled SD, essentially correcting for unitary differences.
 Dividing SMD by the temperature difference on top of that results in correcting the effect size further by temperature.
@@
 $$
-\text{Var}(f(X_1)) \approx \text{Var}(X_1)* \left( 
-f'(X_1)
+\text{Var}(f(M_1)) \approx \text{Var}(M_1)* \left( 
+f'(M_1)
 \right)^2,
-$$ where $f(X_1)$ represents the function of the random variable $X_1$, and importantly, $f'(X_1)$ is the first derivative of $f(X_1)$.
+$$
+
+where $f(M_1)$ represents the function of the random variable $X_1$, and importantly, $f'(M_1)$ is the first derivative of $f(M_1)$.
 Probably it is hard to understand what does this really means without a concrete example.
@@
 $$
-\ln{RR} = \ln \left ( \frac{X_{1}}{X_{2}}\right ) = \ln{X_1} -\ln{X_2}.
+\ln{RR} = \ln \left ( \frac{M_{1}}{M_{2}}\right ) = \ln{M_1} -\ln{M_2}.
 $$
 
-Here, $f(X_1) = \ln{X_1}$. By applying $f'(X_1) = 1/{X_1}$ (i.e. the first derivative of $lnX1$ is $1/{X_1}$) to the delta method and using the variance's basic properties, we have:
+Here, $f(M_1) = \ln{M_1}$. By applying $f'(M_1) = 1/{M_1}$ (i.e. the first derivative of $lnM_1$ is $1/{M_1}$) to the delta method and using the variance's basic properties, we have:
 
 $$
-\sigma^2_{ln{RR}} \approx  \left ( \frac{SD_{1}^2}{N_{1}}\right ) * \left(\frac{1}{X_{1}} \right)^2 + \left ( \frac{SD_{2}^2}{N_{2}}\right ) * \left(\frac{1}{X_{2}} \right)^2 =   \left ( \frac{SD_{1}^2}{N_{1}X_{1}^2}\right ) + \left ( \frac{SD_{2}^2}{N_{2}X_{2}^2}\right )
+\sigma^2_{ln{RR}} \approx  \left ( \frac{SD_{1}^2}{N_{1}}\right ) * \left(\frac{1}{M_{1}} \right)^2 + \left ( \frac{SD_{2}^2}{N_{2}}\right ) * \left(\frac{1}{M_{2}} \right)^2 =   \left ( \frac{SD_{1}^2}{N_{1}M_{1}^2}\right ) + \left ( \frac{SD_{2}^2}{N_{2}M_{2}^2}\right )
 $$
@@
 $$
-\sigma^2_{ln{RR}} \approx  \left ( \frac{SD_{1}^2}{N_{1}X_{1}^2}\right ) + \left ( \frac{SD_{2}^2}{N_{2}X_{2}^2}\right ) 
-- 2r\sqrt{\frac{SD_{1}^2}{N_{1}X_{1}^2}}\sqrt{\frac{SD_{2}^2}{N_{2}X_{2}^2}},
+\sigma^2_{ln{RR}} \approx  \left ( \frac{SD_{1}^2}{N_{1}M_{1}^2}\right ) + \left ( \frac{SD_{2}^2}{N_{2}M_{2}^2}\right ) 
+- 2r\sqrt{\frac{SD_{1}^2}{N_{1}M_{1}^2}}\sqrt{\frac{SD_{2}^2}{N_{2}M_{2}^2}},
 $$
-where $r$ is 0 when two sets of measurements are independent (therefore, the term including $r$ disappears), while $r$ is the correlation between $\ln{X_1}$ and $\ln{X_2}$.
+where $r$ is 0 when two sets of measurements are independent (therefore, the term including $r$ disappears), while $r$ is the correlation between $\ln{M_1}$ and $\ln{M_2}$.
 As discussed, we usually do not have an estimate for this correlation coefficient.

### 2021-07-14 MS/ms.Rmd
Unified equations

@@
              "\\ln \\left( \\frac{M_{1}}{M_{2}}\\right)",
-             "\\frac{\\left( X_{2} - X_{1}\\right)}{SD_{p}}J",
+             "\\frac{\\left( M_{2} - M_{1}\\right)}{SD_{p}}J",
              # we need to spell out SD_p somewhere
@@
   \begin{aligned}
-  \ln{RR} = \ln\left ( \frac{X_{1}}{X_{2}}\right )
+  \ln{RR} = \ln\left ( \frac{M_{1}}{M_{2}}\right )
   \end{aligned}
@@
 \begin{equation} 
-  s^2_{lnRR} = \left ( \frac{SD_{1}^2}{N_{1}X_{1}^2}\right ) + \left ( \frac{SD_{2}^2}{N_{2}X_{2}^2}\right )
+  s^2_{lnRR} = \left ( \frac{SD_{1}^2}{N_{1}M_{1}^2}\right ) + \left ( \frac{SD_{2}^2}{N_{2}M_{2}^2}\right )
   (\#eq:slnRR)
 \end{equation} 
-$$ In equation \@ref(eq:lnRR), $X_{1}$ is the mean of group 1, often a control group, where as $X_{2}$ is the mean of group 2 (e.g., a treatment group).
+$$
+
+In equation \@ref(eq:lnRR), $X_{1}$ is the mean of group 1, often a control group, where as $X_{2}$ is the mean of group 2 (e.g., a treatment group).
 The mean of $X_{i}$ for group *i* can be any measurement type (e.g.

### 2021-07-14 MS/box.Rmd
think I see the dumb error I made in ox 1 SMD equation, maybe fixed now
equation fixed
Fixed a rogue X to M

@@
 $$
-\sigma^2(aX_1 \pm b)=a^2 * \sigma^2_{X_{1}}
+\sigma^2(aM_1 \pm b)=a^2 * \sigma^2_{M_{1}}
 $$
@@
 $$
-s_{SMD_{T}}^2 = \left(\frac{1}{{T_{2} - T_{1}}}\right)^2 +  \frac{N_{1} + N_{2}}{N_{1}N_{2}}  + \frac{SMD_{T}^2}{2\left( N_{1} + N_{2}\right)}
+s_{SMD_{T}}^2 = \left (\frac{N_{1} + N_{2}}{N_{1}N_{2}}  + \frac{SMD_{T}^2}{2\left( N_{1} + N_{2}\right)} \right) \left(\frac{1}{{T_{2} - T_{1}}}\right)^2
 $$
@@
 $$
-Note here again that the first term, $\frac{SD_{1}^2}{N_{1}}$ is the sampling variance for group 1, and we simply multiply this term by the square of the first derivative of $X_{1}$ as the Delta method tells us.
+Note here again that the first term, $\frac{SD_{1}^2}{N_{1}}$ is the sampling variance for group 1, and we simply multiply this term by the square of the first derivative of $M_{1}$ as the Delta method tells us.
 Of course, readers will see that this is equivalent to the sampling variance for $ln_{RR}$ (Table 1).

### 2021-07-15 MS/supp.Rmd
Added code for ARR and ARRD in supplement

@@
 ```
+
 ```{r klippy, echo=FALSE, include=TRUE, message=FALSE, warning=FALSE}
@@
 #install.packages("pacman")
-pacman::p_load(devtools, png, jpeg, pander, cowplot, flextable, tidyverse, metafor, orchaRd, here, osfr, magrittr)
+pacman::p_load(devtools, png, jpeg, pander, cowplot, flextable, tidyverse, metafor, orchaRd, here, osfr, magrittr, Rcpp)
 devtools::install_github("itchyshin/orchard_plot", subdir = "orchaRd", force = TRUE)
@@
 
-# Case Study 1: 
+# Case Study 1: Multilevel meta-analysis approaches to control for differences in treatment magnitude
+
+Here, we will demonstrate how to use analyse variation in slopes and differences in slopes between two groups.
+In this example, we will account for effects of known drivers of 'nuisance heterogeneity' at the level of the effect size.
+We use a case study by Pottier et al.
+*in review* which investigated the association between acclimation temperature, thermal tolerance and sex.
+We first demonstrate how to use meta-analytic approaches to investigate the variation in the relationship between acclimation temperature and thermal tolerance (i.e.
+variation in slope), and then demonstrate how to meta-analyse differences in slopes between two groups (i.e.
+sexes).
+
+## Multilvel meta-analysis of slopes
+
+We first download the data from OSF, and load this into R. You can do this by copying and pasting the code below.
+
 ```{r class.source='klippy'}
 
-# Example on how to download and load for reader. Should work anyway. Needs some testing
-#osfr::osf_retrieve_file("https://osf.io/mnw5d/") %>% osfr::osf_download()
+# Download the data file from OSF
+osfr::osf_retrieve_file("https://osf.io/qn2af/") %>% osfr::osf_download(conflicts = "overwrite")
 
-#data_CS1 <- read.csv(here::here("CaseStudy1.csv"))
+# Load the data file
+data_CS1a <- read.csv(here::here("ms", "CTmax_ARR.csv"))
+```
 
+### Calculate effect size
+
+In this section, we demonstrate how to calculate slope effect sizes and their associated sampling variance.
+Note that calculating slopes require the response variable to be measured with the same unit and does not apply to all meta-analyses.
+While this example focuses on thermal tolerance, the meta-analysis of slope may also be applicable to investigate changes in thermal preference, or metabolic scaling for example.
+
+In this example, we use a simplified data set from Pottier et al.
+*in review* and we demonstrate how to investigate the mean effect of acclimation temperature on heat tolerance.
+Because heat tolerance was consistently measured in degrees Celsius (`CTmax`) in the studies compiled, we can calculate the slope between acclimation temperature and heat tolerance, which is termed as the acclimation response ratio (`ARR`) in the literature.
+This effect size is calculated as the difference between the heat tolerance at the higher (`mean_high`) and the lower (`mean_low`) acclimation temperatures, divided by the difference between acclimation temperatures (`acc_temp_high` - `acc_temp_low`).
+The sampling variance of the slope (`Var_ARR`) can then be defined using properties of variance as per 'formula XXX`
+
+In this example, the slopes were calculated with stepwise comparisons between acclimation treatments.
+This method created a source of non-independence, with some treatments being involved in multiple comparisons (`shared_trt_ID`).
+To account for this, we divided by half the sample size of the observations in these non-independent comparisons (`n_low_adj` and `n_high_adj`) to divide by half the weight of these estimates.
+
+```{r, class.source='klippy', results = 'hide'}
+data_CS1a<-data_CS1a %>% 
+              mutate(ARR=(mean_high-mean_low)/(acc_temp_high - acc_temp_low),
+                     Var_ARR=((1/(acc_temp_high-acc_temp_low))^2*(sd_low^2/n_low_adj+sd_high^2/n_high_adj))) # Need to double check this formula, Shinichi pointed out that there might be a mistake.
+```
+
+In some cases, CTmax was measured twice on the same cohort of animals (e.g.
+using a different endpoint), which generates a source of non-independence between effect sizes.
+We can account for this source of non-independence by correlating errors between dependent effect sizes.
+The `make_VCV_matrix` from `metaAidR` is a handy function to perform this correction, and assume a correlation of r = 0.5 by default.
+We termed the created variance-covariance matrix as `VCV_ARR`.
+
+```{r, class.source='klippy', results = 'hide'}
+# Variance covariance matrix to account for non-independence of measurements performed on the same cohorts of animals
+VCV_ARR<- metaAidR::make_VCV_matrix(data_CS1a, V = "Var_ARR", cluster = "shared_measurement_ID", obs = "es_ID")
+```
+
+### Meta-analysis
+
+Then, we can run the multi-level meta-analytic model using the `rma.mv` function in the `metafor` package. 
+In this model, we used two random effects: `species_ID` and `es_ID` to account for between species variation and the variation associated with the residuals.
+Note that it is possible to assess the variation due to phylogenetic relatedness but we will keep it simple for demonstration purposes.
+We also did not assessed variation due to between-study differences because the levels of this variable was almost entirely overlapping with `species_ID` (i.e.
+`species_ID` and `study_ID` were indistinguishable).
+While we only present  an intercept-only model, this structure can be used to fit meta-regressions by fitting moderator variables.
+
+```{r, class.source='klippy', results = 'hide'}
+# Multi-level meta-analytic model
+Model_CS1a_MLMA<-metafor::rma.mv(yi=ARR~-1, V=VCV_ARR, 
+                   method="REML",
+                   random=list(~1|species_ID,
+                               ~1|es_ID), 
+                   test="t",
+                   dfs = "contain",
+                   data=data_CS1a)
+summary(Model_CS1a_MLMA)
+
+# Calculate Prediction Intervals
+PIs_CS1a_MLMA <- predict(model_CS1a_MLMA)
+print(PIs_CS1a_MLMA)
+
+# Calculate I2
+I2_CS1a <- orchaRd::i2_ml(Model_CS1a_MLMA)
+print(I2_CS1a)
+```
+
+## Multi-level Meta-analysis of slope differences between two groups
+
+We can imagine cases where one might be interested in comparing the slopes of two groups or treatments. 
+In this example, we demonstrate how to derive and analyse effect sizes when investigating differences in slopes.
+As per the previous example, such analysis require responses variables to be measured with the same unit.
+We use the same data set as before, but formatted in a slightly different way (i.e.
+columns were re-organised in a "wide" format to calculate differences between sexes).
+In this example, rather than investigating overall variation in `ARR`, we will investigate the difference in `ARR` between males and females.
+
+```{r class.source='klippy'}
+# Download the data file from OSF
+osfr::osf_retrieve_file("https://osf.io/mnw5d/") %>% osfr::osf_download(conflicts = "overwrite")
+
+# Load the data file
+data_CS1b <- read.csv(here::here("ms", "CTmax_ARR_sex.csv"))
+```
+
+### Calculate effect size
+
+First, we need to calculate the `ARR` of females (`ARR_f`) and males (`ARR_m`) with the formula we presented earlier. 
+We can then use the mean difference between `ARR_f` and `ARR_m` as an effect size, which we term here as `ARRD`. 
+The sampling variance was then calculated as per `formula XXX`
+
+```{r, class.source='klippy', results = 'hide'}
+data_CS1b<-data_CS1b %>% # calculate effect sizes
+
+  mutate(ARR_f=((mean_high_f-mean_low_f)/(acc_temp_high-acc_temp_low))) %>% 
+  mutate(ARR_m=((mean_high_m-mean_low_m)/(acc_temp_high-acc_temp_low))) %>% 
+  mutate(ARRD=ARR_f - ARR_m) %>% 
+  mutate(Var_ARRD=((1/(acc_temp_high-acc_temp_low))^2*(sd_low_f^2/n_low_f_adj+sd_high_f^2/n_high_f_adj+sd_low_m^2/n_low_m_adj+sd_high_m^2/n_high_m_adj)))  
+```
+
+### Meta-analysis
+
+Again, we first started by accounting for the non-independence of CTmax estimates measured on the same cohorts using a variance-covariance matrix termed as `VCV_ARRD`. 
+We then fit a multi-level meta-analytic model using a similar structure as demonstrated before. 
+Note that this model can be extended to meta-regressions by fitting moderator variables. 
+```{r, class.source='klippy', results = 'hide'}
+
+# Variance covariance matrix to account for non-independence of measurements performed on the same cohorts of animals
+VCV_ARRD<- metaAidR::make_VCV_matrix(data_CS1b, V = "Var_ARR", cluster = "shared_measurement_ID", obs = "es_ID")
+
+# Multi-level meta-analytic model
+model_CS1b_MLMA<-metafor::rma.mv(yi=ARRD~-1, V=VCV_ARRD, 
+                   method="REML",
+                   random=list(~1|species_ID,
+                               ~1|es_ID), 
+                   test="t",
+                   dfs = "contain",
+                   data=data_CS1b)
+print(model_CS1b_MLMA)
+
+# Calculate Prediction Intervals
+PIs_CS1b_MLMA <- predict(model_CS1b_MLMA)
+print(PIs_CS1b_MLMA)
+
+# Calculate I2
+I2_CS1b <- orchaRd::i2_ml(model_CS1b_MLMA)
+print(I2_CS1b)
 ```
@@
 
-```{r}
+```{r, class.source='klippy', results = 'hide'}
 # Centre the dosage data on the mean. Note that, for comparability, we'll exclude 'NA' in dose so that models are fit with the exact same data.

### 2021-07-15 MS/supp.Rmd
updating ignore file, and fixing some stuff in supp

@@
 Before embarking on the case studies readers will need to load the necessary R packages.
+Note that the first two lines are commented out.
+If you don't have these packages, just install these by removing the `#`.
 
@@
 #install.packages("pacman")
-pacman::p_load(devtools, png, jpeg, pander, cowplot, flextable, tidyverse, metafor, orchaRd, here, osfr, magrittr, Rcpp)
-devtools::install_github("itchyshin/orchard_plot", subdir = "orchaRd", force = TRUE)
+#devtools::install_github("itchyshin/orchard_plot", subdir = "orchaRd", force = TRUE)
+pacman::p_load(devtools, png, jpeg, pander, cowplot, flextable, tidyverse, metafor, orchaRd, here, osfr, magrittr)
 ```
@@
 
-### Calculate effect size
+### Calculate Effect Size
 
@@
 We can account for this source of non-independence by correlating errors between dependent effect sizes.
-The `make_VCV_matrix` from `metaAidR` is a handy function to perform this correction, and assume a correlation of r = 0.5 by default.
-We termed the created variance-covariance matrix as `VCV_ARR`.
+The `make_VCV_matrix` from [`metaAidR`](https://github.com/daniel1noble/metaAidR) is a handy function to perform this correction, and assume a correlation of r = 0.5 by default.
+We termed the created variance-covariance matrix `VCV_ARR`.
 
@@
 # Download the data file from OSF
-osfr::osf_retrieve_file("https://osf.io/mnw5d/") %>% osfr::osf_download(conflicts = "overwrite")
+osfr::osf_retrieve_file("https://osf.io/zubky/") %>% osfr::osf_download(conflicts = "overwrite")
 

### 2021-07-15 MS/supp.Rmd
Fixing Patrice's code a bit, and code chunks. Just to get it working. Problems with VCV matrix (might even be too complex)

@@
 #devtools::install_github("itchyshin/orchard_plot", subdir = "orchaRd", force = TRUE)
-pacman::p_load(devtools, png, jpeg, pander, cowplot, flextable, tidyverse, metafor, orchaRd, here, osfr, magrittr)
+#devtools::install_github("daniel1noble/metaAidR")
+pacman::p_load(devtools, png, jpeg, pander, cowplot, flextable, tidyverse, metafor, orchaRd, here, osfr, magrittr, metaAidR)
 ```
@@
 
-```{r class.source='klippy'}
+```{r class.source='klippy', results = 'hide'}
 
@@
 # Load the data file
-data_CS1a <- read.csv(here::here("ms", "CTmax_ARR.csv"))
+data_CS1a <- read.csv(here::here("CTmax_ARR.csv"))
 ```
@@
 
-```{r, class.source='klippy', results = 'hide'}
+```{r, class.source='klippy', results = 'hide', message=FALSE}
 # Variance covariance matrix to account for non-independence of measurements performed on the same cohorts of animals
 VCV_ARR<- metaAidR::make_VCV_matrix(data_CS1a, V = "Var_ARR", cluster = "shared_measurement_ID", obs = "es_ID")
+
+# This method should be similar from clubSandwich
+VCV_ARR2 <- clubSandwich::impute_covariance_matrix(data_CS1a$Var_ARR, cluster = "shared_measurement_ID", r =0.5)
 ```
@@
 
-```{r, class.source='klippy', results = 'hide'}
+```{r, class.source='klippy'}
 # Multi-level meta-analytic model
-Model_CS1a_MLMA<-metafor::rma.mv(yi=ARR~-1, V=VCV_ARR, 
+Model_CS1a_MLMA <- metafor::rma.mv(ARR ~ 1, V = VCV_ARR2, 
                    method="REML",
@@
 # Calculate Prediction Intervals
-PIs_CS1a_MLMA <- predict(model_CS1a_MLMA)
+PIs_CS1a_MLMA <- predict(Model_CS1a_MLMA)
 print(PIs_CS1a_MLMA)
@@
 
-## Multi-level Meta-analysis of slope differences between two groups
+## Multi-level Meta-analysis of Slope Differences between Two Groups
 
@@
 
-```{r class.source='klippy'}
+```{r class.source='klippy', results = 'hide'}
 # Download the data file from OSF
@@
 # Load the data file
-data_CS1b <- read.csv(here::here("ms", "CTmax_ARR_sex.csv"))
+data_CS1b <- read.csv(here::here("CTmax_ARR_sex.csv"))
 ```
 
-### Calculate effect size
+### Calculate Effect Size
 
@@
 Again, we first started by accounting for the non-independence of CTmax estimates measured on the same cohorts using a variance-covariance matrix termed as `VCV_ARRD`.
+
+```{r, class.source='klippy',  results = 'hide', message=FALSE}
+# Variance covariance matrix to account for non-independence of measurements performed on the same cohorts of animals
+#VCV_ARRD<- metaAidR::make_VCV_matrix(data_CS1b, V = "Var_ARR", cluster = "shared_measurement_ID", obs = "es_ID")
+VCV_ARRD <- clubSandwich::impute_covariance_matrix(data_CS1b$Var_ARRD, cluster = "shared_measurement_ID", r =0.5)
+```
+
 We then fit a multi-level meta-analytic model using a similar structure as demonstrated before. 
 Note that this model can be extended to meta-regressions by fitting moderator variables.
-```{r, class.source='klippy', results = 'hide'}
 
-# Variance covariance matrix to account for non-independence of measurements performed on the same cohorts of animals
-VCV_ARRD<- metaAidR::make_VCV_matrix(data_CS1b, V = "Var_ARR", cluster = "shared_measurement_ID", obs = "es_ID")
-
+```{r, class.source='klippy'}
 # Multi-level meta-analytic model
-model_CS1b_MLMA<-metafor::rma.mv(yi=ARRD~-1, V=VCV_ARRD, 
+model_CS1b_MLMA<-metafor::rma.mv(yi= ARRD~ 1, V = VCV_ARRD, 
                    method="REML",
@@
 
-```{r}
+```{r, echo = FALSE}
 pander(sessionInfo(), locale = FALSE)

### 2021-07-16 MS/supp.Rmd
Fixed ARR/ARRD code, removed VCV matrix because not working

@@
 title: "Supplemental Materials for: Meta-analytic approaches and new effect sizes to account for heterogeneous effects in comparative physiology"
-author: Daniel W.A. Noble, Patrice Potter, Sammy Burke, Szymek Drobniak, Malgorzata Lagisz, Rose O’Dea, Shinichi Nakagawa
+author: Daniel W.A. Noble, Patrice Pottier, Samantha Burke, Szymon M. Drobniak, Malgorzata Lagisz, Rose E. O’Dea, Shinichi Nakagawa
 date: "`r Sys.Date()`"
@@
 Daniel W.A.
-Noble, Patrice Potter, Sammy Burke, Szymek Drobniak, Malgorzata Lagisz, Rose O’Dea, Shinichi Nakagawa (2022) *Meta-analytic approaches and "new" effect sizes to account for heterogeneous effects in comparative physiology*.
+Noble, Patrice Pottier, Sammantha Burke, Szymon M.
+Drobniak, Malgorzata Lagisz, Rose E.
+O’Dea, Shinichi Nakagawa (2022) *Meta-analytic approaches and "new" effect sizes to account for heterogeneous effects in comparative physiology*.
 **Journal of Experimental Biology**
@@
 
+In this example, we will only use data measured on independent groups of animals, thus excluding data measured twice on the same cohort of animals (i.e.
+animals sharing the same `shared_measurement_ID` in the data).
+Note that it is possible to model this dependency and examples are provided in Noble et al.
+(2017) and Pottier et al.
+*in review*
+
 ```{r, class.source='klippy', results = 'hide'}
+
+# Calculate the effect sizes
 data_CS1a<-data_CS1a %>% 
               mutate(ARR=(mean_high-mean_low)/(acc_temp_high - acc_temp_low),
-                     Var_ARR=((1/(acc_temp_high-acc_temp_low))^2*(sd_low^2/n_low_adj+sd_high^2/n_high_adj))) # Need to double check this formula, Shinichi pointed out that there might be a mistake.
-```
+                     Var_ARR=((1/(acc_temp_high-acc_temp_low))^2*(sd_low^2/n_low_adj+sd_high^2/n_high_adj)))
 
-In some cases, CTmax was measured twice on the same cohort of animals (e.g.
-using a different endpoint), which generates a source of non-independence between effect sizes.
-We can account for this source of non-independence by correlating errors between dependent effect sizes.
-The `make_VCV_matrix` from [`metaAidR`](https://github.com/daniel1noble/metaAidR) is a handy function to perform this correction, and assume a correlation of r = 0.5 by default.
-We termed the created variance-covariance matrix `VCV_ARR`.
-
-```{r, class.source='klippy', results = 'hide', message=FALSE}
-# Variance covariance matrix to account for non-independence of measurements performed on the same cohorts of animals
-VCV_ARR<- metaAidR::make_VCV_matrix(data_CS1a, V = "Var_ARR", cluster = "shared_measurement_ID", obs = "es_ID")
-
-# This method should be similar from clubSandwich
-VCV_ARR2 <- clubSandwich::impute_covariance_matrix(data_CS1a$Var_ARR, cluster = "shared_measurement_ID", r =0.5)
+# Remove dependent effect sizes
+data_CS1a<-filter(data_CS1a,
+                    es_ID!="es85"&
+                    es_ID!="es86"&
+                    es_ID!="es87"&
+                    es_ID!="es98"&
+                    es_ID!="es282"&
+                    es_ID!="es283"&
+                    es_ID!="es284"&
+                    es_ID!="es286") 
 ```
@@
 ```{r, class.source='klippy'}
+
 # Multi-level meta-analytic model
-Model_CS1a_MLMA <- metafor::rma.mv(ARR ~ 1, V = VCV_ARR2, 
+model_CS1a_MLMA <- metafor::rma.mv(ARR ~ 1, V = Var_ARR, 
                    method="REML",
@@
                    test="t",
-                   dfs = "contain",
                    data=data_CS1a)
-summary(Model_CS1a_MLMA)
+print(model_CS1a_MLMA)
 
 # Calculate Prediction Intervals
-PIs_CS1a_MLMA <- predict(Model_CS1a_MLMA)
-print(PIs_CS1a_MLMA)
+PI_CS1a_MLMA <- predict(model_CS1a_MLMA)
+print(PI_CS1a_MLMA)
 
 # Calculate I2
-I2_CS1a <- orchaRd::i2_ml(Model_CS1a_MLMA)
+I2_CS1a <- orchaRd::i2_ml(model_CS1a_MLMA)
 print(I2_CS1a)
+
+# Plot the results
+orchard_plot(model_CS1a_MLMA, mod="Int", xlab="ARR")
 ```
+
+We can see from above that the model estimates an overall meta-analytic mean as `r coef(model_CS1a_MLMA)` with a 95\% CI from `r model_CS1a_MLMA$ci.lb` to `r model_CS1a_MLMA$ci.ub`.
+In other words, for each degree variation in acclimation temperature, the heat tolerance of the animals included in this data set vary by `r coef(model_CS1a_MLMA)` degrees on average.
+95\% of the time we expect the mean in repeated samples to fall between `r PI_CS1a_MLMA$cr.lb` to `r PI_CS1a_MLMA$cr.ub`.
+Our prediction intervals suggest that heterogeneity is high, reflected also in our $I_{total}^2$ estimate of `r I2_CS1a[1]*100`\%.
+Approximately, `r I2_CS1a[2]*100`\% of the total heterogeneity is the result of differences between species and `r I2_CS1a[3]*100`\% of the total heterogeneity is associated with the residuals.
+With this effect size (slope), the 'nuisance heterogeneity' is accounted for, to some extent, at the level of the effect size.
 
@@
 
+As before, we will only use data measured on independent groups of animals, thus excluding data measured twice on the same cohort of animals (i.e.
+animals sharing the same `shared_measurement_ID` in the data).
+
 ```{r, class.source='klippy', results = 'hide'}
@@
   mutate(Var_ARRD=((1/(acc_temp_high-acc_temp_low))^2*(sd_low_f^2/n_low_f_adj+sd_high_f^2/n_high_f_adj+sd_low_m^2/n_low_m_adj+sd_high_m^2/n_high_m_adj)))
+
+# Remove dependent effect sizes
+data_CS1b<-filter(data_CS1b,
+                    es_ID!="es85"&
+                    es_ID!="es86"&
+                    es_ID!="es87"&
+                    es_ID!="es98")
 ```
@@
 ### Meta-analysis
-
-Again, we first started by accounting for the non-independence of CTmax estimates measured on the same cohorts using a variance-covariance matrix termed as `VCV_ARRD`.
-
-```{r, class.source='klippy',  results = 'hide', message=FALSE}
-# Variance covariance matrix to account for non-independence of measurements performed on the same cohorts of animals
-#VCV_ARRD<- metaAidR::make_VCV_matrix(data_CS1b, V = "Var_ARR", cluster = "shared_measurement_ID", obs = "es_ID")
-VCV_ARRD <- clubSandwich::impute_covariance_matrix(data_CS1b$Var_ARRD, cluster = "shared_measurement_ID", r =0.5)
-```
 
@@
 ```{r, class.source='klippy'}
+
 # Multi-level meta-analytic model
-model_CS1b_MLMA<-metafor::rma.mv(yi= ARRD~ 1, V = VCV_ARRD, 
+model_CS1b_MLMA<-metafor::rma.mv(yi= ARRD~ 1, V = Var_ARRD, 
                    method="REML",
@@
                    test="t",
-                   dfs = "contain",
                    data=data_CS1b)
@@
 # Calculate Prediction Intervals
-PIs_CS1b_MLMA <- predict(model_CS1b_MLMA)
-print(PIs_CS1b_MLMA)
+PI_CS1b_MLMA <- predict(model_CS1b_MLMA)
+print(PI_CS1b_MLMA)
 
@@
 print(I2_CS1b)
+
+# Plot the results
+orchard_plot(model_CS1b_MLMA, mod="Int", xlab="ARR")
 ```
+
+We can see from above that the model estimates an overall meta-analytic mean as 0.002 with a 95\% CI from `r model_CS1b_MLMA$ci.lb` to `r model_CS1b_MLMA$ci.ub`.
+In other words, for each degree variation in acclimation temperature, the heat tolerance of females vary by an average of 0.002 degrees more than males.
+Note that the confidence intervals overlap with zero, which indicates that the difference between females and males is small, and not statistically significant.
+95\% of the time we expect the mean in repeated samples to fall between `r PI_CS1b_MLMA$cr.lb` to `r PI_CS1b_MLMA$cr.ub`.
+Our prediction intervals suggest that heterogeneity is small to moderate, reflected also in our $I_{total}^2$ estimate of `r I2_CS1b[1]*100`\%.
+Approximately, `r I2_CS1b[2]*100`\% of the total heterogeneity is the result of differences between species and `r I2_CS1b[3]*100`\% of the total heterogeneity is associated with the residuals.
 

### 2021-07-16 MS/ms.Rmd
Fixed some comments / suggestions from Megan. Still a few to deal with, but will see what others think. Added a new figure 1 to see if we can visualise things better

@@
 
-  pacman::p_load(flextable, tidyverse, equatags)  
+  pacman::p_load(flextable, tidyverse, equatags, png, magick)  
 ```
@@
 A critically important feature of a meta-analysis is its ability to account for sampling error [@Koricheva2013].
-The inverse of sampling error variance is used to weight studies, accordingly, in the analysis and make overall estimates more precise.
+The inverse of sampling error variance is used to weight studies in the analysis and make overall estimates more precise.
 While many meta-analyses might employ unweighted analyses, these studies will not gain greater precision on estimates because sampling variance cannot be formally accounted for in the analysis, even if the overall mean itself is unbiased [@Morrissey2016a].
@@
 To the uninitiated, this concern might not be unfounded given that heterogeneity in effects is often high in ecological and evolutionary meta-analyses [@Senior2016], telling us that the effect size varies a great deal from one population to another.
-However, to many, the very fact that highly heterogeneous effects exist is a core strength of meta-analysis [@Cooperetal2019; @Borenstein2019; @Gurevitch2018; @Glass2015].
-Indeed, exploring the reasons for why effects are likely to vary across studies "...is the spice of life" [p.g., 519; @Cooperetal2019].
+However, to many, having highly heterogeneous effects "...is the spice of life" [p.g., 519; @Cooperetal2019] because it provides opportunities to explore the reasons for why effects vary within and across studies [@Cooperetal2019; @Borenstein2019; @Gurevitch2018; @Glass2015].
 
@@
 We then formalise alternative effect sizes and their associated sampling variance to provide comparative physiologists opportunities to explicitly incorporate treatment differences into the effect size estimates to ease their interpretation.
-We then describe how more complex treatment differences, such as dosage differences (which may have non-linear effects) can be accommodated using multilevel meta-regression models.
+Finally, we describe how more complex treatment differences, such as dosage differences (which may have non-linear effects) can be accommodated using multilevel meta-regression models.
 We hope to show how expanding the meta-analytic toolkit for comparative physiologists will provide new opportunities to address global scale problems that attempt to understand how organisms will cope with rapidly changing environments in the future.
@@
 Meta-analysis is always concerned with effect heterogeneity; in other words, the factors that drive differences in the direction and magnitude an of effect within and across studies [@Nakagawa2017; @Gurevitch2018; @Cooperetal2019; @Borenstein2019].
-The concept of heterogeneity is vitally important because it tells us how general a specific conclusion is likely to be, how much of the variance we see is the result of real biology (and not just sampling variance), and provides a way to understand what the key biological factors are leading to an effect [@Nakagawa2017; @Borenstein2019].
+The concept of heterogeneity is vitally important because it tells us how general a specific conclusion is likely to be, how much of the variance we see is the result of real biology (not just sampling variance), and provides a way to understand what the key biological factors are leading to an effect [@Nakagawa2017; @Borenstein2019].
 There are a plethora of phenomena driving effect heterogeneity, some of which are interesting and others that are less so.
@@
 As a consequence, we need to rely on a sub-sample to estimate a population parameter (e.g., correlation between two traits).
-How many independent samples we collect impacts our precision in estimating this 'true' effect [@Borenstein2019].
+How many independent samples we collect impacts our precision in estimating the 'true' effect [@Borenstein2019].
 In meta-analysis we formally include sampling variance to remove this source of heterogeneity directly because it is known -- hence why having sampling variances for an effect is so important [@Gurevitch2018; @Koricheva2013].
@@
 For example, the methods for measuring an outcome variable can result in different effects, and it is important we know and understand this as it can determine how experiments are designed in the future.
-In other cases, methodological factors might be considered 'nuisance heterogeneity' [following from @Cooperetal2019] -- factors we know vary, but are rather unsurprising to us.
+In other cases, methodological factors might be considered 'nuisance heterogeneity' [following from @Cooperetal2019] -- factors we know vary, but are rather unsurprising to us (Figure \@ref(fig:fig1)).
 These might include differences in temperature, pH, dosages, water potential etc.
@@
 In some cases, however, the latter factors might actually not be 'nuisance' variables but the main interest of a synthesis.
-Regardless, in many cases they can result in a more complicated interpretation of an effect measure then what is desired.
+Regardless, in many cases they can result in a more complicated interpretation of an effect measure than what is desired.
 
-All the various sources of heterogeneity (except sampling variance) all contribute (to varying extents) to the 'apples and oranges' problem often touted as being an issues with some meta-analyses (or quantitative syntheses more generally).
+```{r, fig1, fig.cap="*Sources of effect size heterogeneity in meta-analyses*.
+Heterogeneity can come in various forms from effect measures varying as a result of shared evolutionary history (i.e., phylogeny), different trait types measured, and even sources of 'nuisance heterogeneity'.
+Nuisance heterogeneity can be factors, such as temperature differences impacting effect size measures, or dosages.
+We can control for these types of heterogeniety by reformalising effect sizes and/or using multilevel metaregression as we describe in our review"}
+image <- image_read(here::here("figs", "Fig1.png"))
+image
+```
+
+All the various sources of heterogeneity (except sampling variance) contribute (to varying extents) to the 'apples and oranges' problem often touted as being an issues with meta-analyses (or quantitative syntheses more generally).
 Indeed, some of this criticism revolves around combining studies that vary in their quality (e.g., observational vs experimental).
-Combining standardised effects, while ignoring these sources of heterogeneity can result in the meaning of a meta-analysis not being particularly useful to many.
+Combining standardised effects, while ignoring these sources of heterogeneity can result in the meaning of a meta-analysis not being particularly useful.
 However, many argue that this is just what we are interested in synthesizing [@Cooperetal2019; @Borenstein2019; @Gurevitch2018; @Glass2015].
@@
 For full details on the search strings used, dates searched, the number of papers found, and our PRISMA flowchart (along with reasons for exclusion at the full text stage) we refer readers to the *Supplementary Materials*.
-To address our questions, we categorised effect sizes as falling into the following categories: Response Ratio (lnRR), Standardised Mean Differences (SMD; e.g., Hedges d, g or Cohen's d), Correlation or Fisher's Z -transformed Correlation, Regression Slopes (Slopes), Risk Ratios, or whether the paper analysed the raw data or summary statistics directly (i.e., means/proportions) (which we label as raw/mean/proportion).
+To address our questions, we categorised effect sizes as falling into the following categories: Response Ratio (lnRR), Standardised Mean Differences (SMD; e.g., Hedges d, g or Cohen's d), Correlation or Fisher's Z -transformed Correlation, Regression Slopes (Slopes), Risk Ratios, or whether the paper analysed the raw data or summary statistics directly (i.e., means/proportions) (which we label as 'raw').
 For all other effects we labelled as 'other'.
 To determine whether effect sizes were likely to vary based on some underlying continuous variable or were dependent on the context in which traits were measured, we assessed whether authors: 1) acknowledged this explicitly in the paper or 2) accounted for it in their models.
-If it was not clear, two of us (DWAN & PP) discussed the paper, and made a decision.
+If it was not clear, two of us (DWAN & PP) discussed the paper, and made a decision about whether the effect measure was likely to be impacted.
 For example, trait means, such as ectothermic metabolic rate (i.e., raw/mean/proportion-based effect size), will vary depending on the temperature being measured, the magnitude of differences between two treatments (e.g, contrast-based effect sizes - SMD or lnRR) might depend on the temperature or dosage used in treatments, and the strength of relationship between two variables (e.g., correlation between behaviour and metabolism) might depend on the temperature context under which metabolic rate or behaviour were measured.
-Given the high heterogeneity in effects used in comparative physiology, we expected this to be common to most effect sizes, however, it has not been formally quantified.
+Given the high heterogeneity in effects used in comparative physiology, we expected 'nuisance heterogeneity' to be common to most effect sizes, however, it has not been formally quantified.
 We categorised the types of statistical models fit in each study as: 1) fixed-effect meta-analysis; 2) random effects meta-analysis (i.e., intercept only model, but has random study effects); 3) multi-level meta-analysis (i.e., intercept only model, but has multiple random effect levels such as study, species, observation-level random effects); 4) meta-regression models (i.e., a multilevel or random effect model with fixed effects - including random effects); 5) weighted regression models, including mixed effect models; and 6) linear regression models (including linear and generalised linear mixed effect models, and phylogenetic least squares models).
-Notably, only model types 1-5 are weighted models.
+Notably, only model types 1-5 are weighted models because they weight effect sizes based on the inverse of their sampling variance or sample size.
 
@@
 
-Quantitative syntheses in comparative physiology commonly analyse raw summary statistics (`r with(effects, effects[effect == "Means","prop"])*100`\% of studies), followed closely by Fishers transformed correlation coefficients (Zr) (`r with(effects, effects[effect == "Zr","prop"])*100`\% of studies), standardised mean differences (SMD) and log response ratios (lnRR) (`r with(effects, effects[effect == "SMD","prop"])*100`\% and `r with(effects, effects[effect == "lnRR","prop"])*100`\%, respectively; Figure \@ref(fig:fig1)A).
+Quantitative syntheses in comparative physiology commonly analyse raw summary statistics (`r with(effects, effects[effect == "Means","prop"])*100`\% of studies), followed closely by Fishers transformed correlation coefficients (Zr) (`r with(effects, effects[effect == "Zr","prop"])*100`\% of studies), standardised mean differences (SMD) and log response ratios (lnRR) (`r with(effects, effects[effect == "SMD","prop"])*100`\% and `r with(effects, effects[effect == "lnRR","prop"])*100`\%, respectively; Figure \@ref(fig:figsurv)A).
 In many cases, studies make use of multiple effect size measures.
-Approximately `r with(hetero, hetero[cont_moderator_variable == "yes","percent"])*100`\% of effect sizes used within the study were deemed to be impacted by 'nuisance heterogeneity' in some form or another (Figure \@ref(fig:fig1)B), and of the studies where this was the case, only `r with(hetero_dealt, hetero_dealt[cont_moderator_variable_modelled == "yes","percent"])*100`\% of the studies clearly dealt with it (Figure \@ref(fig:fig1)B); usually through meta-regression modelling.
+Approximately `r with(hetero, hetero[cont_moderator_variable == "yes","percent"])*100`\% of effect sizes used within the study we deemed to be impacted by 'nuisance heterogeneity' in some form or another (Figure \@ref(fig:figsurv)B), but of the studies where this was the case, only `r with(hetero_dealt, hetero_dealt[cont_moderator_variable_modelled == "yes","percent"])*100`\% of the studies clearly dealt with it (Figure \@ref(fig:figsurv)B); usually through meta-regression modelling.
 Overall, `r with(weighted, weighted[meta_analysis_weighted == "weighted model","percent"])*100`\% of studies used a weighted meta-analytic model, however, of the studies self described as 'meta-analyses', `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","percent"])*100`\% (N = `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","n"])` of `r with(weighted_meta, sum(weighted_meta[,"n"]))`) did not actually weight their meta-analytic mean.
-Many studies used 'Linear Regression' (including linear and generalised linear mixed effects models) as the main type of model fit to the data (Figure \@ref(fig:fig1)C).
-Of the studies using weighted meta-analytic models `r with(het_reported, sum(het_reported[1:2,"percent"])*100)`\% (N = `r with(het_reported, sum(het_reported[1:2,"n"]))` meta-analyses) did not report any measure of heterogeneity.
+Many studies used 'Linear Regression' (including linear and generalised linear mixed effects models) as the main type of model fit to the data (Figure \@ref(fig:figsurv)C).
+Of the studies using weighted meta-analytic models `r with(het_reported, sum(het_reported[1:2,"percent"])*100)`\% (N = `r with(het_reported, sum(het_reported[1:2,"n"]))` meta-analyses) did not report any measure of heterogeneity, which is unfortaunte given how important these measures are to interpreting effects.
 
-```{r, fig1, fig.cap="**Summary of meta-analytic practices in comparative physiology.** (A) Different types of effect measures commonly used in meta-analyses and their releative frequency of use.
+```{r, figsurv, fig.cap="**Summary of meta-analytic practices in comparative physiology.** (A) Different types of effect measures commonly used in meta-analyses and their relative frequency of use.
 (B) how many meta-analyses where 'nuisance heterogenity' have the potential to impact effect sizes, and the proportion of studies explicitly dealing with nuisance heterogenity.
@@
 The key features of all effect sizes used in meta-analyses are that they are: 1) statistical parameters that have been placed on a common scale so that they can be compared across studies and 2) that they have some associated measure of precision (i.e., sampling variance)[@Koricheva2013; @Borenstein2009; @Schmid2021].
-Effect sizes in comparative physiology are quite variable; they can be the mean difference between two groups (e.g., difference in mean between a control and treatment group - see @WuSeebacher2020), the slope of a regression (e.g., between body size and metabolic rate), a correlation between two variables, or even the raw mean (or variance) itself (e.g., comparing CTmax or CTmin across species - see @Sunday2014).
-In many cases, multiple types of effect sizes might be used depending on the question.
+Effect sizes in comparative physiology are quite variable; they can be the mean difference between two groups [e.g., difference in mean between a control and treatment group - see @WuSeebacher2020], the slope of a regression (e.g., between body size and metabolic rate), a correlation between two variables, or even the raw mean (or variance) itself [e.g., comparing CTmax or CTmin across species - see @Sunday2014].
+In many cases, different effect sizes might be used depending on the question.
 For example, studies interested in the effect of temperature on some physiological trait that have measured the trait across studies experimentally manipulating temperature could analyse the mean 'effect' by creating contrast-based effect sizes or by analysing the mean in each temperature treatment.
@@
 
-As is clear from Table \@ref(tab:tablea) none of the effect measures control for 'nuisance heterogeneity'.
+As can be seen in Table \@ref(tab:tablea) none of the effect measures control for 'nuisance heterogeneity'.
 For example, the magnitude of response between two treatment groups for lnRR or SMD might depend on just how different the temperatures, dosages, pH or water potential applied in each treatment.
@@
 As such, one needs to standardise the temperature measurement to compare across studies [@White2006; @Uyeda2017] (if, of course, temperature is not of interest in of itself).
-While we could of course model this explicitly, this may not always be desirable.
+While we could model this explicitly, this may not always be desirable.
 It can often be useful to standardise the effect to both ease its interpretation and simplify modelling.
@@
 #### *Comparing Changes in Mean Physiological Rates, $Q_{10}$*
-A very common occurrence in comparative physiology is to manipulate the temperature organisms experience and measure some physiological rate (e.g., metabolic rate).
-Using normal effect size measures (see Table \@ref(tab:tablea)) would result in the effect sizes varying in the types of temperatures applied within and across across studies contributing to 'comparability' issues.
-As such, it is often of interest to standardize effects by temperature.
+A common experiment in comparative physiology is to manipulate the temperature organisms experience and measure some physiological rate (e.g., metabolic rate).
+Using the effect size measures in Table \@ref(tab:tablea) would result in the effect sizes varying with the temperatures applied within and across across studies contributing to 'comparability' issues.
+For example, an effect size for a temperature manipulation of 10°C would be larger than an effect size for a temperature manipulation of 5°C (see Figure \@ref(fig:fig1)).
+As such, it is common to standardize effects by temperature.
 One common effect size measure already used in comparative physiology to compare physiological rates is $Q_{10}$ [e.g., @Rodgers2021; @Seebacher2015; @Havird2020], which describes the multiplicative change in physiological rates across a 10°C temperature change.
@@
 
-Prior to showing how the relevant $Q_{10}$ effect size can be calculated it can be helpful to understand its similarities to *lnRR*.
+Prior to showing how the relevant $Q_{10}$ effect size can be calculated it is useful to understand its similarities to *lnRR*.
 The *lnRR* described by @Hedges1999 and extended by @Lajeunesse2015 and can be calculated as follows [but see also @Senior2020]:
@@
 
-In equation \@ref(eq:lnRR), $X_{1}$ is the mean of group 1, often a control group, where as $X_{2}$ is the mean of group 2 (e.g., a treatment group).
+In equation \@ref(eq:lnRR), $M_{1}$ is the mean of group 1, often a control group, where as $M_{2}$ is the mean of group 2 (e.g., a treatment group).
 The mean of $X_{i}$ for group *i* can be any measurement type (e.g.
@@
 Here, we will refer to this as the log $Q_{10}$ response ratio, $lnRR_{Q_{10}}$.
-Notably, by taking the natural logarithm, there are two statistical advantages: 1) 0 becomes biological meaningful as 0 means two rates are the exactly the same and 'significantly different from 0' means that two rates are significantly different to each other and 2) $lnRR_{Q_{10}}$ is more likely to satisfy the assumption of residual normality than $Q_{10}$ (see @Hedges1999).
+Notably, by taking the natural logarithm, there are two statistical advantages: 1) 0 becomes biologically meaningful as 0 means two rates are the exactly the same and 'significantly different from 0' means that two rates are significantly different to each other and 2) $lnRR_{Q_{10}}$ is more likely to satisfy the assumption of residual normality than $Q_{10}$ (see @Hedges1999).
 The recognition of this equivalence means that we can easily calculate the sampling variance for equation \@ref(eq:lnq10) as follows:
@@
 For the purpose of our discussion, we will assume the meta-analyst needs to use more advanced multilevel models.
-Having said that, it maybe sufficient for a meta-analysis to make use of traditional random effects models.
+Having said that, it may be sufficient for a meta-analysis to make use of traditional random effects models.
 We refer readers to excellent reviews and books that overview the distinctions between common (fixed) effect, random effect and multilevel models and when one might want (or not want) to apply these models [@Nakagawa2017; @NakagawaSantos2012; @Koricheva2013; @Borenstein2009; @Schmid2021].
@@
 Of course, these studies are diverse, apply different dosages of corticosterone and are working across many species.
-If the studies are experimental in nature than a standardised effect size, such as $ln_{RR}$ or Hedges' *d*, might be applicable.
+If the studies are experimental in nature then a standardised effect size, such as $ln_{RR}$ or Hedges' *d*, might be applicable.
 We then might fit an overall multilevel meta-analytic model as follows:
@@
 Importantly, by centering, we retain the original units (uL / g) of the variable, which can be very useful to allow for a more general interpretation of the effect magnitude (e.g., when the dosage difference is 10 uL /g).
-Given it is very common to estimate and compare overall meta-analytic means (i.e., $B_{0}$) in meta-analyses this centering can be particularly useful in making these means more interpretable.Mean centering can even be extended to include other 'nuisance' variables that might creep into the dataset; the same centering can be done with a second variable, and the overall mean adjusted can be interpreted in the context of this new variable in additional to dosage.
-Of course, if one is not interested in the magnitude of effect, we could also change our question and simply model mean reproductive output as a function of dosage (often what are referred to as 'arm-based' meta-analytic models).
-Here, one can model the mean for each group (i.e., control and treatment group), and account for the known sampling variance associated with each group mean.
+Given it is very common to estimate and compare overall meta-analytic means (i.e., $B_{0}$) in meta-analyses this centering can be particularly useful in making these means more interpretable.
+Mean centering can even be extended to include other 'nuisance' variables that might creep into the dataset; the same centering can be done with a second variable, and the overall mean adjusted can be interpreted in the context of this new variable in addition to dosage.
+Of course, if one is not interested in the magnitude of the effect, we could also change our question and simply model mean reproductive output as a function of dosage (often what are referred to as 'arm-based' meta-analytic models).
+Here, one can model the mean for each group (i.e., control and treatment), and account for the known sampling variance associated with each group mean.
 Dosage, or other continuous variables like temperature, can then be modeled (accounting for sampling variance) to understand how mean reproductive output changes.
@@
 However, obvious drivers of effect size heterogeneity, such as temperature and dosage differences across studies, may not really be of interest.
-Indeed, comparative physiologists are likely to want an effect size or analytic approach that allows them to remove these 'nuisances'.
-Here, we provide a set of tools to deal with 'nuisance heterogeneity' by creatively 'reinventing' standard effect sizes or using meta-regression models.
+Comparative physiologists are likely to want an effect size or analytic approach that allows them to remove these 'nuisances'.
+Here, we provide a set of tools to deal with 'nuisance heterogeneity' by 'reinventing' standard effect sizes or using meta-regression models.
 Of course, 'nuisance heterogeneity' might in of itself be the main interest, in which case standard meta-regression approaches will work sufficiently.
 However, in many cases, comparative physiologists might simply want to focus on bigger, more interesting biological drivers of effect size direction and magnitude.
-However, estimating complex meta-regression models with a multitude of fixed effects might result in more challenging model interpretation.
-As such, a combined approach, where some of the known heterogeneity is dealt with by deriving a variant effect size and associated sampling variance, and other biologically interesting moderators are fit in a meta-regression model, might be desired.
+Estimating complex meta-regression models with a multitude of fixed effects might result, however, in more challenging model to interpret As such, a combined approach, where some of the known heterogeneity is dealt with by deriving a variant effect size and associated sampling variance, and other biologically interesting moderators are fit in a meta-regression model, might be desired.
 Indeed, this may even be a necessity to simplify the model.
@@
 
+## **Awknowledgements**
+We would like to thank the Editorial board (Craig Franklin, Michaela Handel and Charlotte Rutledge) for inviting us to contribute to this special issue along with feedback on previous drafts.
+We would also like to than Megan Head for comments on a previous draft.
+DWAN and SN were supported by ARC Discovery Projets (DP210101152 to DWAN and DPXX to SN).
+
 ## **References**

### 2021-07-16 MS/box.Rmd
Minor fixes from Megan

@@
 
-Here we show how to obtain sampling variance for a slope (or a 'rate of change') when you are given measurements of a physiological trait at two points in an environmental gradient (e.g.
+Here we show how to obtain sampling variance for a slope (or a 'rate of change') when you have measurements of a physiological trait at two points along an environmental gradient (e.g.
 temperature, salinity, acidity).
@@
 
-It may be the best to start with a real example that comparative physiologists can easily associate, namely the temperature acclimation slope or as we call it the (temperature) acclimation response ratio (ARR).
+Let's start with a real example that comparative physiologists can easily associate with, namely the temperature acclimation slope or as we call it the (temperature) acclimation response ratio (ARR).
 ARR can be defined as a slope for acclimated physiological responses at two different temperature points, defined as:
@@
 
-where *T* stands for temperature in degrees Celsius and $T_{2} > T_{1}$, and $M_{1}$ and $M_{2}$ are the average physiological responses (estimated means) at two temperature points $T_{1}$ and $T_{2}$.
+where *T* stands for temperature in degrees Celsius and $T_{2} > T_{1}$, and $M_{1}$ and $M_{2}$ are the average physiological responses (estimated means) at temperature points $T_{1}$ and $T_{2}$.
 
@@
 Importantly, when $M_{1}$ and $M_{2}$ are independent of each other the covariance is 0.
-More concretely, if measurements are done on two different groups of animals at two different temperature points ($T_1$ and $T_2$), then the co-variances between these two sets of measurements are 0.
+More concretely, if measurements are taken on two different groups of animals at two different temperatures ($T_1$ and $T_2$), then the co-variances between these two sets of measurements are 0.
 
@@
 
-Now, it is not uncommon that we use the same group of animals (or plants) at two temperature points.
+Now, it is not uncommon that we measure the same group of animals (or plants) at two temperatures.
 If we do, however, then we need to add the co-variance between $M_{1}$ and $M_{2}$ ($\text{Cov}(M_{1},M_{2})$); note that as above, the co-variance equals the corresponding correlation multiplied by the square-root of two (sampling) variances.
@@
 
-By assuming the number of animals (*N*) are the same at the two temperature points, we can slightly simplify this formula:
+By assuming the number of animals (*N*) are the same at the two temperatures, we can slightly simplify this formula:
 
@@
 So, in reality, we often need to assume a certain value of *r*.
-@Noble2017 discuss why we can assume $r = 0.5$ and this may be the most reasonable thing to do when we do not have any estimate of *r*.
+When we do not have an estimate of *r* we can reasonably assume it to be 0.5 [@Noble2017].
 
@@
 
-Now let us assume that we now want to know the difference between two different ARR values: female ARR, $\text{ARR}_{f}$ and Male ARR, $\text{ARR}_{m}$. Such a difference (ARRD) can be written as:
+Now let us assume that we want to know the difference between two different ARR values: female ARR, $\text{ARR}_{f}$ and Male ARR, $\text{ARR}_{m}$. Such a difference (ARRD) can be written as:
 
@@
 
-Now we have derive sampling variances for 'temperature' ARR and ARRD for both independent and dependent cases.
-But these formulas can be applied to changes in salinity, PH, oxygen and other abotic factors.
-Also, the constant components of these formulas can be flexibly adjusted.
+Here we have derived sampling variances for 'temperature' ARR and ARRD for both independent and dependent cases.
+But these formulas can also be applied to changes in other factors (e.g., salinity, pH, oxygen).
+Furthermore, the constant components of these formulas can be flexibly adjusted.
 For example, it may be possible that males and females were measured in slightly different temperatures; say females at $T_3$ and $T_4$ ($T_4 > T_3$) and male at $T_5$ and $T_6$ ($T_6 > T_5$) like below:
@@
 
-Also, note that the difference between slopes does not need to be that of males and females. It can be between experimental and control groups or comparing any two groups or situations.
+Also, note that the difference between slopes does not need to be that of males and females. This formula can be used to compare any two groups or situations.
 
@@
 ARR assumes that the units for the mean difference across studies is consistent.
-This will often not be the case for many meta-analyses that hope to synthesise a wide diversity of trait types that vary in their units (e.g., ul/g, grams, seconds, minutes).
+This will often not be the case for many meta-analyses that hope to synthesise a wide array of trait types that vary in their units (e.g., ul/g, grams, seconds, minutes).
 Fortunately, $lnRR$ and SMD (Table 1) already control for unitary differences.
@@
 Here, we can see that the difference between $M_1$ and $M_2$ is standardised by the pooled SD, essentially correcting for unitary differences.
-Dividing SMD by the temperature difference on top of that results in correcting the effect size further by temperature.
+Additionally, dividing SMD by the temperature difference results in further correcting the effect size by temperature.
 To derive the sampling variance for $SMD_T$ we can apply the same principles as we did above to derive an approximate sampling variance as:
@@
 where $f(M_1)$ represents the function of the random variable $X_1$, and importantly, $f'(M_1)$ is the first derivative of $f(M_1)$.
-Probably it is hard to understand what does this really means without a concrete example.
-So let's derive the sampling variance for $\ln{RR}$, which is:
+Let's demonstrate with a concrete example by re-deriving the sampling variance for $\ln{RR}$, which is:
 
@@
 Note here again that the first term, $\frac{SD_{1}^2}{N_{1}}$ is the sampling variance for group 1, and we simply multiply this term by the square of the first derivative of $M_{1}$ as the Delta method tells us.
-Of course, readers will see that this is equivalent to the sampling variance for $ln_{RR}$ (Table 1).
+Readers may notice that this is equivalent to the sampling variance for $ln_{RR}$ (Table 1).
 We can extend this sampling variance to include dependency between the groups as:
@@
 $lnQ_{10}$; see the main text) and as in @Nakagawa2015 and @Senior2020.
+
+# References

### 2021-07-17 MS/box.Rmd
boxed mended with a few new refs

@@
 temperature, salinity, acidity).
-We also go on to derive sampling variance for the difference between two slopes, and finally end on showing how SMD can be corrected to account for both unitary and temperature differences across effect sizes.
-The sampling variances associated with these 'new' effect sizes will allow one to take advantage of powerful meta-analytic models.
+We then go on to derive sampling variance for the difference between two slopes, and also how SMD (standardized mean difference) can be corrected to account for differences in both units (e.g.
+cm or mg) and points on an environmental gradient (e.g.
+temperature of 24 and 30 Celsius).
+Finally, we introduce a useful approximation technique known as 'the delta method'.
+The sampling variances associated with these 'new' effect sizes below will allow one to take advantage of powerful meta-analytic models.
 
@@
 To obtain the sampling variance for this equation (slope), we need to know several basic properties of variance.
-Let's assume $M_{1}$ is a random variable, which means that this variable has a mean and standard deviation (variance).
+Let's assume $M_{1}$ is a random variable, which means that this variable has a mean and standard deviation (variance; this standard decision is not 'sample' but 'sampling' standard deviation, which is often referred to as standard error).
 Multiplying a constant ($a$) will change the variance by the square of that constant ($a^2$) while adding or subtracting the constant ($b$) does not change the variance of $M_{1}$.
@@
 $$
-\sigma^2_{M_1 \pm M_2} = \sigma^2_{M_1} + \sigma^2_{M_2} \pm 2\text{Cov}(M_1,M_2) 
+\sigma^2(M_1 \pm M_2) = \sigma^2_{M_1} + \sigma^2_{M_2} \pm 2\text{Cov}(M_1,M_2) 
 = \sigma^2_{M_1} + \sigma^2_{M_2} \pm 2\text{Cor}(M_1,M_2)\sqrt{ \sigma^2_{M_1} \sigma^2_{M_2} }
 $$
+
 where the co-variance $\text{Cov}(M_1,M_2)$ equals to the correlation multiplied by the square-root of the two variances $2\text{Cor}(M_1,M_2)\sqrt{ \sigma^2_{M_1} \sigma^2_{M_2} }$.
@@
 Let us explain further.
-The (sampling) standard error for $X_{1}$ is $SE_{1} = SD_{1} / \sqrt{N_{1}}$ -- many readers will probably know this as the formula for obtaining *SE* from *SD*.
+The (sampling) standard error for $X_{1}$ is $SE_{1} = SD_{1} / \sqrt{N_{1}}$ -- many readers will probably know this as the formula for obtaining *SE* ('sampling' standard deviation) from *SD* ('sample' standard deviation; see Figure 1 in @Nakagawa2021b).
 Given this, the sampling variance for $X_{1}$ is $SD^2_{1} / N_{1}$, which you see as an element of the sampling variance of ARR along with the sampling variance for $X_{2}$, which is $X_{2}$ is $SD^2_{2} / N_{2}$; the term $(1/(T_{2} - T_{1}))^2$ comes from recognizing $1/(T_{2} - T_{1})$ as a constant.
@@
 Additionally, dividing SMD by the temperature difference results in further correcting the effect size by temperature.
-To derive the sampling variance for $SMD_T$ we can apply the same principles as we did above to derive an approximate sampling variance as:
+To derive the sampling variance for $SMD_T$ we can apply the same principle as we did above to derive an sampling variance as:
 
@@
 Therefore, we introduce a practical and widely applicable method to obtain approximate variance when the basic properties of variance cannot be applied.
-The method is widely known as the delta method, which can be written as:
-
-Here, we use the delta method to derive the sampling variance for the log repose ratio, which is:
+This is where the delta method comes in.
+The general form of this method can be written as:
 
@@
 \sigma^2_{ln{RR}} \approx  \left ( \frac{SD_{1}^2}{N_{1}}\right ) * \left(\frac{1}{M_{1}} \right)^2 + \left ( \frac{SD_{2}^2}{N_{2}}\right ) * \left(\frac{1}{M_{2}} \right)^2 =   \left ( \frac{SD_{1}^2}{N_{1}M_{1}^2}\right ) + \left ( \frac{SD_{2}^2}{N_{2}M_{2}^2}\right )
-$$
-Note here again that the first term, $\frac{SD_{1}^2}{N_{1}}$ is the sampling variance for group 1, and we simply multiply this term by the square of the first derivative of $M_{1}$ as the Delta method tells us.
+$$ Note here again that the first term, $\frac{SD_{1}^2}{N_{1}}$ is the sampling variance for group 1, and we simply multiply this term by the square of the first derivative of $M_{1}$ as the Delta method tells us.
 Readers may notice that this is equivalent to the sampling variance for $ln_{RR}$ (Table 1).
@@
 - 2r\sqrt{\frac{SD_{1}^2}{N_{1}M_{1}^2}}\sqrt{\frac{SD_{2}^2}{N_{2}M_{2}^2}},
-$$
-where $r$ is 0 when two sets of measurements are independent (therefore, the term including $r$ disappears), while $r$ is the correlation between $\ln{M_1}$ and $\ln{M_2}$.
+$$ where $r$ is 0 when two sets of measurements are independent (therefore, the term including $r$ disappears), while $r$ is the correlation between $\ln{M_1}$ and $\ln{M_2}$.
 As discussed, we usually do not have an estimate for this correlation coefficient.
@@
 $lnQ_{10}$; see the main text) and as in @Nakagawa2015 and @Senior2020.
+Also, see @Nakagawa2017 for more on the delta method (they explain the 'first and second-order' delta method)
 

### 2021-07-17 MS/ms.Rmd
this looks great - just a few comments

@@
 
-Meta-analysis is a tool that provides comparative physiologists with powerful, unbiased and quantitatively informed answers to topical research questions by synthesising effect sizes across disparate studies.
-Meta-analysis' core objective and strength is to distill published research results into standardised effect sizes that can be weighted (i.e., by their inverse sampling variance), and which can be compared across broad sets of research designs, study systems and species.
+Meta-analysis is a tool that provides comparative physiologists with powerful and quantitatively informed answers to topical research questions by synthesising effect sizes across disparate studies.
+<!--- I took "unbiased" out as this is not quite true - it can be till biased ----> Meta-analysis' core objective and strength is to distill published research results into standardised effect sizes that can be weighted (i.e., by their inverse sampling variance), and which can be compared across broad sets of research designs, study systems and species.
 Estimating overall effect sizes, and understanding what drives effect variability, provides opportunities to model how organisms will respond to pressing global challenges.
@@
 A critically important feature of a meta-analysis is its ability to account for sampling error [@Koricheva2013].
-The inverse of sampling error variance is used to weight studies in the analysis and make overall estimates more precise.
-While many meta-analyses might employ unweighted analyses, these studies will not gain greater precision on estimates because sampling variance cannot be formally accounted for in the analysis, even if the overall mean itself is unbiased [@Morrissey2016a].
+The inverse of sampling error variance is used to weight studies in the analysis and make overall estimates more precise (note that this statement is only completely true for the fixed-effect meta-analysis and that actual weighting is more complex in the model introduced below although this is a good intuition for all of us to have).
+<!--- just being careful ----> While many meta-analyses might employ unweighted analyses, these studies will not gain greater precision on estimates because sampling variance cannot be formally accounted for in the analysis, even if the overall mean itself may be unbiased [@Morrissey2016a].<!--- as said, unweighted will be more suseptible to publication bias ---->
 
-Despite its widespread adoption and well established methodological procedures, meta-analysis is often criticised for mixing 'apples and oranges' -- in other words, mixing effects from studies that lack comparability [@Gurevitch2018; @Arnqvist1995; @Gallo1979; @Carpenter2020; @Stewart2010; @Glass2015].
+Despite its widespread adoption and well-established methodological procedures, meta-analysis is often criticised for mixing 'apples and oranges' -- in other words, mixing effects from studies that lack comparability [@Gurevitch2018; @Arnqvist1995; @Gallo1979; @Carpenter2020; @Stewart2010; @Glass2015].
 Lack of comparability could result from studies differing in experimental design, species, measurement variables and sampling units, which can impact the generalisability of meta-analytic results [@Arnqvist1995; @Stewart2010].
@@
 Indeed, a combination of these approaches might often be ideal.
-We first conduct a survey of published meta-analyses in the field of comparative physiology to gauge methodological and meta-analytic practices -- determining what types of effect sizes are commonly used, how often effect size estimates are impacted by 'nuisance heterogeneity' and whether meta-analytic models (i.e., models that account for sampling variance) are commonly applied.
-We then formalise alternative effect sizes and their associated sampling variance to provide comparative physiologists opportunities to explicitly incorporate treatment differences into the effect size estimates to ease their interpretation.
+<!--- I guss if we map the road like this - it may be fine as readers have been warned ---> Then, we present results from a survey of published meta-analyses in the field of comparative physiology to gauge methodological and meta-analytic practices -- determining what types of effect sizes are commonly used, how often effect size estimates are impacted by 'nuisance heterogeneity' and whether meta-analytic models (i.e., models that account for sampling variance) are commonly applied.
+We also formalise alternative effect sizes and their associated sampling variance to provide comparative physiologists opportunities to explicitly incorporate treatment differences into the effect size estimates to ease their interpretation.
 Finally, we describe how more complex treatment differences, such as dosage differences (which may have non-linear effects) can be accommodated using multilevel meta-regression models.
@@
 
+<!--- Dan - this is really good below --->
 Generally, contributors to effect size heterogeneity fall within a number of broad categories.
@@
 
-Before embarking on "meta-analytic enlightenment" it is worth first understanding how comparative physiologists are currently conducting meta-analyses / comparative analysis.
+Before embarking on "meta-analytic enlightenment", it is worth first understanding how comparative physiologists are currently conducting meta-analyses / comparative analysis.
 As discussed above, different types of questions and experimental approaches will mix 'apples and oranges' to varying extents, and indeed, this heterogeneity (or basket of fruit) is often the main interest to comparative biologists.
@@
 #### *Current Meta-analytic Practices in Comparative Physiology*
-
+<!--- the fig 2 the label "Others" - should they come at the bottom??? Also, for the method - you may want to add all these data, survey etc can be found at the github repo??? --->
 ```{r setup2, include=FALSE}
@@
 
-Quantitative syntheses in comparative physiology commonly analyse raw summary statistics (`r with(effects, effects[effect == "Means","prop"])*100`\% of studies), followed closely by Fishers transformed correlation coefficients (Zr) (`r with(effects, effects[effect == "Zr","prop"])*100`\% of studies), standardised mean differences (SMD) and log response ratios (lnRR) (`r with(effects, effects[effect == "SMD","prop"])*100`\% and `r with(effects, effects[effect == "lnRR","prop"])*100`\%, respectively; Figure \@ref(fig:figsurv)A).
+Quantitative syntheses in comparative physiology commonly analyse raw summary statistics (`r with(effects, effects[effect == "Means","prop"])*100`% of studies), followed closely by Fishers transformed correlation coefficients (Zr) (`r with(effects, effects[effect == "Zr","prop"])*100`% of studies), standardised mean differences (SMD) and log response ratios (lnRR) (`r with(effects, effects[effect == "SMD","prop"])*100`% and `r with(effects, effects[effect == "lnRR","prop"])*100`%, respectively; Figure \@ref(fig:figsurv)A).
 In many cases, studies make use of multiple effect size measures.
-Approximately `r with(hetero, hetero[cont_moderator_variable == "yes","percent"])*100`\% of effect sizes used within the study we deemed to be impacted by 'nuisance heterogeneity' in some form or another (Figure \@ref(fig:figsurv)B), but of the studies where this was the case, only `r with(hetero_dealt, hetero_dealt[cont_moderator_variable_modelled == "yes","percent"])*100`\% of the studies clearly dealt with it (Figure \@ref(fig:figsurv)B); usually through meta-regression modelling.
-Overall, `r with(weighted, weighted[meta_analysis_weighted == "weighted model","percent"])*100`\% of studies used a weighted meta-analytic model, however, of the studies self described as 'meta-analyses', `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","percent"])*100`\% (N = `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","n"])` of `r with(weighted_meta, sum(weighted_meta[,"n"]))`) did not actually weight their meta-analytic mean.
+Approximately `r with(hetero, hetero[cont_moderator_variable == "yes","percent"])*100`% of effect sizes used within the study we deemed to be impacted by 'nuisance heterogeneity' in some form or another (Figure \@ref(fig:figsurv)B), but of the studies where this was the case, only `r with(hetero_dealt, hetero_dealt[cont_moderator_variable_modelled == "yes","percent"])*100`% of the studies clearly dealt with it (Figure \@ref(fig:figsurv)B); usually through meta-regression modelling.
+Overall, `r with(weighted, weighted[meta_analysis_weighted == "weighted model","percent"])*100`% of studies used a weighted meta-analytic model, however, of the studies self described as 'meta-analyses', `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","percent"])*100`% (N = `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","n"])` of `r with(weighted_meta, sum(weighted_meta[,"n"]))`) did not actually weight their meta-analytic mean.
 Many studies used 'Linear Regression' (including linear and generalised linear mixed effects models) as the main type of model fit to the data (Figure \@ref(fig:figsurv)C).
-Of the studies using weighted meta-analytic models `r with(het_reported, sum(het_reported[1:2,"percent"])*100)`\% (N = `r with(het_reported, sum(het_reported[1:2,"n"]))` meta-analyses) did not report any measure of heterogeneity, which is unfortaunte given how important these measures are to interpreting effects.
+Of the studies using weighted meta-analytic models `r with(het_reported, sum(het_reported[1:2,"percent"])*100)`% (N = `r with(het_reported, sum(het_reported[1:2,"n"]))` meta-analyses) did not report any measure of heterogeneity, which is unfortaunte given how important these measures are to interpreting effects.
 
@@
              # we need to spell out SD_p somewhere
-             "\\frac{1}{2}log\\left(\\frac{1+r}{1-r}\\right)")
+             "\\frac{1}{2}log\\left( \\frac{1+r}{1-r}\\ right)")
              #"log\\left(\\frac{y_{i2}+0.5}{n_{i2}-y_{i2}+0.5}\\right) ",
@@
 
-As can be seen in Table \@ref(tab:tablea) none of the effect measures control for 'nuisance heterogeneity'.
+As can be seen in Table \@ref(tab:tablea), none of the effect measures control for 'nuisance heterogeneity'.
 For example, the magnitude of response between two treatment groups for lnRR or SMD might depend on just how different the temperatures, dosages, pH or water potential applied in each treatment.
@@
 
-#### *Comparing Changes in Mean Physiological Rates, $Q_{10}$*
+#### *Comparing Changes in Mean Physiological Rates,* $Q_{10}$
+
 A common experiment in comparative physiology is to manipulate the temperature organisms experience and measure some physiological rate (e.g., metabolic rate).
@@
 Higher $Q_{10}$ values indicate larger changes in physiological rates.
-Currently, however, we do not have associated sampling variances derived for $Q_{10}$ making it challenging to make use of the full power of weighted meta-analytic models.
-Interestingly, $Q_{10}$ can be seen as a variant of *lnRR*, meaning that we can derive a $Q_{10}$ based effect size and sampling error using the well known mathematical properties of *lnRR*.
+Currently, however, we do not seem to have associated sampling variances derived for $Q_{10}$ in the literature, making it challenging to make use of the full power of weighted meta-analytic models.
+<!--- I am bing a bit more careful here ---> Interestingly, $Q_{10}$ can be seen as a variant of *lnRR*, meaning that we can derive a $Q_{10}$ based effect size and sampling error using the well known mathematical properties of *lnRR*.
 This opens up the meta-analytic toolbox and improves upon our ability to account for well known sources of non-independence that are typical in meta-analysis [@Lajeunesse2011; @Noble2017].
@@
 
-Our example using $Q_{10}$, a well known effect measure in comparative physiology, shows how common effect size's can be re-formalised to account for 'nuisance heterogeneity', in this case temperature.
+Our example using $Q_{10}$, a well-known effect measure in comparative physiology, shows how common effect size's can be re-formalised to account for 'nuisance heterogeneity', in this case temperature.
 Of course, in doing this we are making assumptions about the nature of temperature effects on an effect size.
@@
 If the studies are experimental in nature then a standardised effect size, such as $ln_{RR}$ or Hedges' *d*, might be applicable.
-We then might fit an overall multilevel meta-analytic model as follows:
-$$
+We then might fit an overall multilevel meta-analytic model as follows: $$
 \begin{split}
@@
 This model is a 'weighted' multilevel meta-analysis model because the estimation of the overall meta-analytic mean, $\beta_{0}$, is weighted by the inverse sampling variance of each effect size.
-Importantly, if we have effect sizes that are derived from the *same* sample of animals (or plants) (e.g., may be because many traits are measured on the same sets of animals) then we need to remove this dependency from the calculation of each $v_{i}$; we can then model the known sampling covariance between effect sizes by modifying \textbf{I} to include off-diagonals that account for this covariance [See Box 1 and @Noble2017].
+Importantly, if we have effect sizes that are derived from the *same* sample of animals (or plants) (e.g., may be because many traits are measured on the same sets of animals) then we need to remove this dependency from the calculation of each $v_{i}$; we can then model the known sampling covariance between effect sizes by modifying $\textbf{I}$ to include off-diagonals that account for this covariance [See Box 1 and @Noble2017].
 The fact that we can obtain an overall estimate of sampling variance (i.e., $\sigma^2_{m}$, see below for how it is defined) is very important because it provides a way for us to understand just how much variation in effects are the result of sampling differences across studies versus other, potentially important sources of variation such as differences in the methods applied, species differences or even real biological effects that impact the effect size a study is likely to observe [@Nakagawa2017; @NakagawaSantos2012].
@@
 
-Many readers will notice the similarities between $I^2$ and $R^2$ [@Nakgawa2013; @Nakagawa2010].
+Many readers will notice the similarities between $I^2$ and $R^2$ [@Nakgawa2013; @Nakagawa2010; @Nakagawa2017].
 If we want to formally assess how much effect size variation is the result of 'nuisance' variation, such as temperature and dosage differences applied across studies, then we could fit our multilevel meta-regression model, including dosage or temperature (linear, quadratic or even more complex fits), and estimate how much variation is explained by these fixed effects following @Nakgawa2013.
@@
 If the heterogeneity is high as a result of, say, dosages differences, then it is clear that the choice of dosage will have a critical impact on the effect of interest.
-Comparative physiologists interested in implementing these calculations can do so using our packages `orchaRd` [@Nakagawa2021c] or `metaAidR` (https://github.com/daniel1noble/metaAidR).
+Comparative physiologists interested in implementing these calculations can do so using our packages `orchaRd` [@Nakagawa2021c] or `metaAidR` (<https://github.com/daniel1noble/metaAidR>).
 
@@
 For example, assume that we were interested in the overall impact of salinity stress in freshwater fish.
-To tackle this question, we collected experimental studies measuring fish swim performance under high salinity treatments (~15-20ppm Na Cl) compared to freshwater (~0ppm Na Cl) controls; using SMD to quantify the magnitude of effect salinity had on swim performance.
+To tackle this question, we collected experimental studies measuring fish swim performance under high salinity treatments (\~15-20ppm Na Cl) compared to freshwater (\~0ppm Na Cl) controls; using SMD to quantify the magnitude of effect salinity had on swim performance.
 We conduct a meta-analysis and estimate an overall SMD of 0.50 with a prediction interval of 0.05 to 0.85.
 The PI indicates that effects can vary widely from as low as an SMD of 0.05 to as high as an SMD 0.95, depending on the population.
-In addition, if we were to repeat a study we would expect a new effect to fall within the range of 0.05 and 0.85, 95\% of the time [@Borenstein2019; @Nakagawa2021c].
+In addition, if we were to repeat a study we would expect a new effect to fall within the range of 0.05 and 0.85, 95% of the time [@Borenstein2019; @Nakagawa2021c].
 This is a very intuitive interpretation of how variable effects are, yet PIs are often not reported in meta-analyses [@Nakagawa2021c], and we encourage more meta-analysts to report these.
@@
 ## **Conclusions**
+
 Comparative physiologists are interested in meta-analysing effects across a diversity of species, experimental approaches / designs and environments.
@@
 
-## **Awknowledgements**
+## **Acknowledgements**
+
 We would like to thank the Editorial board (Craig Franklin, Michaela Handel and Charlotte Rutledge) for inviting us to contribute to this special issue along with feedback on previous drafts.
 We would also like to than Megan Head for comments on a previous draft.
-DWAN and SN were supported by ARC Discovery Projets (DP210101152 to DWAN and DPXX to SN).
+DWAN, SN, ML and REO were supported by ARC Discovery Projects (DP210101152 to DWAN and DP200100367 to SN, ML and DWAN).
+
+## **Author Contributions**
+<!--- we should probably do credit type contrbution stuff here just to make sure that you did most of the job and led the project--->
 

### 2021-07-18 MS/ms.Rmd
Correcting comments from Shin. Added a few things, updated figures

@@
 Meta-analysis is a tool that provides comparative physiologists with powerful and quantitatively informed answers to topical research questions by synthesising effect sizes across disparate studies.
-<!--- I took "unbiased" out as this is not quite true - it can be till biased ----> Meta-analysis' core objective and strength is to distill published research results into standardised effect sizes that can be weighted (i.e., by their inverse sampling variance), and which can be compared across broad sets of research designs, study systems and species.
+Meta-analysis' core objective and strength is to distill published research results into standardised effect sizes that can be weighted (i.e., by their inverse sampling variance), and which can be compared across broad sets of research designs, study systems and species.
 Estimating overall effect sizes, and understanding what drives effect variability, provides opportunities to model how organisms will respond to pressing global challenges.
@@
 A critically important feature of a meta-analysis is its ability to account for sampling error [@Koricheva2013].
-The inverse of sampling error variance is used to weight studies in the analysis and make overall estimates more precise (note that this statement is only completely true for the fixed-effect meta-analysis and that actual weighting is more complex in the model introduced below although this is a good intuition for all of us to have).
-<!--- just being careful ----> While many meta-analyses might employ unweighted analyses, these studies will not gain greater precision on estimates because sampling variance cannot be formally accounted for in the analysis, even if the overall mean itself may be unbiased [@Morrissey2016a].<!--- as said, unweighted will be more suseptible to publication bias ---->
+The inverse of sampling error variance is used to weight studies in the analysis and make overall estimates more precise (this is true for fixed effect models but note that weighting is more complex in multilevel meta-analytic models).
+While many meta-analyses might employ unweighted analyses, these studies will not gain greater precision on estimates because sampling variance cannot be formally accounted for in the analysis, even if the overall mean itself may be unbiased [@Morrissey2016a].
+In addition, unweighted meta-analyses are more susceptible to publication bias.
 
@@
 Indeed, a combination of these approaches might often be ideal.
-<!--- I guss if we map the road like this - it may be fine as readers have been warned ---> Then, we present results from a survey of published meta-analyses in the field of comparative physiology to gauge methodological and meta-analytic practices -- determining what types of effect sizes are commonly used, how often effect size estimates are impacted by 'nuisance heterogeneity' and whether meta-analytic models (i.e., models that account for sampling variance) are commonly applied.
+Then, we present results from a survey of published meta-analyses in the field of comparative physiology to gauge methodological and meta-analytic practices -- determining what types of effect sizes are commonly used, how often effect size estimates are impacted by 'nuisance heterogeneity' and whether meta-analytic models (i.e., models that account for sampling variance) are commonly applied.
 We also formalise alternative effect sizes and their associated sampling variance to provide comparative physiologists opportunities to explicitly incorporate treatment differences into the effect size estimates to ease their interpretation.
@@
 
-<!--- Dan - this is really good below --->
 Generally, contributors to effect size heterogeneity fall within a number of broad categories.
@@
 #### *Current Meta-analytic Practices in Comparative Physiology*
-<!--- the fig 2 the label "Others" - should they come at the bottom??? Also, for the method - you may want to add all these data, survey etc can be found at the github repo??? --->
+
 ```{r setup2, include=FALSE}
@@
 
-pacman::p_load(dplyr,ggplot2,here, pander, janitor, patchwork)
+pacman::p_load(dplyr,ggplot2,here, pander, janitor, patchwork, forcats)
 
@@
 Many studies used 'Linear Regression' (including linear and generalised linear mixed effects models) as the main type of model fit to the data (Figure \@ref(fig:figsurv)C).
-Of the studies using weighted meta-analytic models `r with(het_reported, sum(het_reported[1:2,"percent"])*100)`% (N = `r with(het_reported, sum(het_reported[1:2,"n"]))` meta-analyses) did not report any measure of heterogeneity, which is unfortaunte given how important these measures are to interpreting effects.
+Of the studies using weighted meta-analytic models `r with(het_reported, sum(het_reported[1:2,"percent"])*100)`% (N = `r with(het_reported, sum(het_reported[1:2,"n"]))` meta-analyses) did not report any measure of heterogeneity, which is unfortunate given how important these measures are to interpreting effects.
 
@@
   colSums(.) %>% data.frame(effect = names(.), n = .) %>% mutate(prop = n / sum(n)) %>% arrange(effect) %>% 
+  mutate(effect = fct_relevel(effect, c("Other", "Zr", "lnRR", "SMD", "lnCVR", "Slope", "Means"))) %>% 
   ggplot() + tm + 
@@
        fill = "Modeled Nuisance\nHeterogeneity?")
+
 p3 <- summary %>% 
+  mutate(effect = fct_relevel(effect, c("Other","Vote Counting", "Linear Regression", "Weighted Regression", "Random Effects Model", "Multilevel Meta-analysis Model", "Multilevel Metaregression Model"))) %>%
   ggplot() + tm +
@@
 Currently, however, we do not seem to have associated sampling variances derived for $Q_{10}$ in the literature, making it challenging to make use of the full power of weighted meta-analytic models.
-<!--- I am bing a bit more careful here ---> Interestingly, $Q_{10}$ can be seen as a variant of *lnRR*, meaning that we can derive a $Q_{10}$ based effect size and sampling error using the well known mathematical properties of *lnRR*.
+Interestingly, $Q_{10}$ can be seen as a variant of *lnRR*, meaning that we can derive a $Q_{10}$ based effect size and sampling error using the well known mathematical properties of *lnRR*.
 This opens up the meta-analytic toolbox and improves upon our ability to account for well known sources of non-independence that are typical in meta-analysis [@Lajeunesse2011; @Noble2017].
@@
 If the studies are experimental in nature then a standardised effect size, such as $ln_{RR}$ or Hedges' *d*, might be applicable.
-We then might fit an overall multilevel meta-analytic model as follows: $$
+We then might fit an overall multilevel meta-analytic model as follows:
+$$
 \begin{split}
@@
 Comparative physiologists are interested in meta-analysing effects across a diversity of species, experimental approaches / designs and environments.
+Importantly, sampling variances for many 'effect measures' commonly used by comparative physiologists (e.g., CTmax, Slopes etc) can be formalised and meta-analytic models applied; even though it is still common to see studies masquerading as meta-analyses despite not fitting meta-analytic models.
 While an overall meta-analytic mean may be of interest, more often than not, understanding the drivers of effect size heterogeneity will be the primary interest.
@@
 ## **Author Contributions**
-<!--- we should probably do credit type contrbution stuff here just to make sure that you did most of the job and led the project--->
+DWAN, SN: Project administration, Conceptualization, Writing - original draft, Visualization, Funding acquisition, Resources, Formal analysis, Methodology, Software; ML, PP, REO, SD, SB: Writing – review & editing, Visualization, Validation, Software, Data curation, Formal analysis.
 

### 2021-07-18 MS/box.Rmd
Fixed up small errors in box

@@
 To obtain the sampling variance for this equation (slope), we need to know several basic properties of variance.
-Let's assume $M_{1}$ is a random variable, which means that this variable has a mean and standard deviation (variance; this standard decision is not 'sample' but 'sampling' standard deviation, which is often referred to as standard error).
+Let's assume $M_{1}$ is a random variable, which means that this variable has a mean and standard deviation (variance; this standard deviation is not the 'sample' but the 'sampling' standard deviation, which is often referred to as standard error).
 Multiplying a constant ($a$) will change the variance by the square of that constant ($a^2$) while adding or subtracting the constant ($b$) does not change the variance of $M_{1}$.
@@
 Additionally, dividing SMD by the temperature difference results in further correcting the effect size by temperature.
-To derive the sampling variance for $SMD_T$ we can apply the same principle as we did above to derive an sampling variance as:
+To derive the sampling variance for $SMD_T$ we can apply the same principle as we did above to derive a sampling variance as:
 
@@
 $lnQ_{10}$; see the main text) and as in @Nakagawa2015 and @Senior2020.
-Also, see @Nakagawa2017 for more on the delta method (they explain the 'first and second-order' delta method)
+Also, see @Nakagawa2017ab for more on the delta method (they explain the 'first and second-order' delta method)
 

### 2021-07-21 MS/ms.Rmd
Fixing up Patrices great comments

@@
 ---
-title: "Meta-analytic approaches and 'new' effect sizes to account for heterogeneous effects in comparative physiology"
+title: "Meta-analytic approaches and effect sizes to account for 'nuisance heterogenity' in comparative physiology"
 bibliography: ../bib/refs.bib
@@
 
-Daniel W.A. Noble$^{1,*}$, Patrice Potter$^{2}$, Malgorzata Lagisz$^{2}$, Sammy Burke$^{2}$, Szymek Drobniak$^{2}$, Rose O'Dea$^{2}$, Shinichi Nakagawa$^{2}$
+Daniel W.A. Noble$^{1,*}$, Patrice Pottier$^{2}$, Malgorzata Lagisz$^{2}$, Samantha Burke$^{2}$, Szymon M. Drobniak$^{2}$, Rose E.  O'Dea$^{2}$, Shinichi Nakagawa$^{2}$
 
@@
 
-$^{2}$ School of Biological, Earth and Environmental Sciences, University of New South Wales, Sydney, NSW
+$^{2}$ Ecology & Evolution Research Centre, School of Biological, Earth and Environmental Sciences, University of New South Wales, Sydney, NSW
 
@@
 
-Meta-analysis is a tool that provides comparative physiologists with powerful and quantitatively informed answers to topical research questions by synthesising effect sizes across disparate studies.
-Meta-analysis' core objective and strength is to distill published research results into standardised effect sizes that can be weighted (i.e., by their inverse sampling variance), and which can be compared across broad sets of research designs, study systems and species.
-Estimating overall effect sizes, and understanding what drives effect variability, provides opportunities to model how organisms will respond to pressing global challenges.
-Despite this ambition, research designs in comparative physiology can appear, at the outset, as being vastly different to each other (e.g., using different temperatures or treatment dosages).
-Differences in treatments across studies has led many to believe that meta-analysis is an exercise in comparing "apples with oranges".
-Here, we dispel this myth by showing how standardised effects sizes can be used in conjunction with powerful multi-level meta-regression models to both account for factors driving differences across studies and make them more comparable.
-In addition, we formalise effect size measures that provide comparative physiologists with a means to directly make effect measures comparable, removing 'nuisance heterogeneity' without the need to resort to more complex statistical models that may be harder to interpret.
-We also describe more general approaches that can be usefully applied to a variety of different contexts to derive 'new' effects sizes and sampling variances.
-The effect sizes and their corresponding sampling variances that we describe should help physiologists deal with common treatment differences across studies.
-By using effect sizes that account for components of effect heterogeneity, in combination with existing meta-analytic models, comparative physiologists can explore exciting new questions by making results from large-scale data sets collected from the literature more accessible and widely interpretable.
+Meta-analysis is a powerful tool to generate quantitatively informed answers to pressing global challenges.
+By distilling data from broad sets of research designs and study systems into standardized effect sizes, meta-analyses provide physiologists with opportunities to estimate overall effect sizes and understand the drivers of effect variability.
+Despite this ambition, research designs in the field of comparative physiology can appear, at the outset, as being vastly different to each other because of 'nuisance heterogeneity' (e.g., different temperatures or treatment dosages used across studies).
+Such differences in treatments across studies has led many to believe that meta-analysis is an exercise in comparing "apples with oranges".
+Here, we dispel this myth by showing how standardised effects sizes can be used in conjunction with multilevel meta-regression models to both account for the factors driving differences across studies and make them more comparable.
+We formalise effect size measures (e.g., $Q_{10}$) that provide comparative physiologists with a means to remove 'nuisance heterogeneity' without the need to resort to more complex statistical models that may be harder to interpret.
+We also describe more general approaches that can be applied to a variety of different contexts to derive 'new' effects sizes and sampling variances opening up new possibilities.
+By using effect sizes that account for components of effect heterogeneity, in combination with existing meta-analytic models, comparative physiologists can explore exciting new questions and make results from large-scale data sets more accessible, comparable and widely interpretable.
 
@@
 
-A meta-analysis provides quantitatively informed answers to research questions by synthesising research results across studies and identifying sources of variation [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Arnqvist1995; @Koricheva2013; @Borenstein2019].
-Meta-analysing independent studies provides greater statistical power and precision than what any individual study on its own would be able to provide on a question - particularly given that most empirical studies are already under-powered in many areas of biology [@Forstmeier2017; @Jennions2003; @Button2013].
-By expressing study effects on a common scale (i.e., standardised effect size) a meta-analyst can gain broader insight into the direction and efficacy of a particular treatment effect or the strength of a relationship between two variables of interest [@Gurevitch2018; @Koricheva2013].
-Quantitative syntheses, including meta-analyses, have provided comparative physiologists with powerful insights on pressing global challenges - from testing whether physiological plasticity can buffer organisms against climate change [e.g, @Seebacher2015] to the degree to which endocrine disrupting chemicals, such as bis-phenol A (BPA), impact aquatic organisms [e.g., @WuSeebacher2020].
-
-Meta-analysis is a well-developed research field with a long history in statistics, medicine, psychology and ecology [@Gurevitch2018; @Nakagawa2017; @Glass2015].
-It has emerged as the 'gold-standard' across various disciplines for quantitative synthesis and is becoming increasingly more prominent in the field of comparative physiology.
-Formal meta-analyses are part of a systematic review and involve a systematic literature-based search, extraction of data from studies meeting specific inclusion criteria, and the subsequent calculation of effects sizes from summary statistics provided by papers.
-A meta-analysis should follow and report upon this entire process carefully to ensure the review process and data collation, are as transparent and reproducible as possible [i.e., see the Preferred Reporting Items for Systematic Reviews and Meta-Analyses in Ecology and Evolution (PRISMA-EcoEvo) protocol, @ODea2021].
+Meta-analysis has emerged as the 'gold-standard' across various disciplines for quantitative synthesis and is becoming increasingly more prominent in the field of comparative physiology  [@Gurevitch2018; @Nakagawa2017; @Glass2015].
+A meta-analysis provides quantitatively informed answers to research questions by synthesising research results across studies and identifying sources of variation across studies [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Arnqvist1995; @Koricheva2013; @Borenstein2019].
+Ideally, meta-analyses are part of a systematic review and carefully report upon this entire process to ensure the review and data collation are transparent and reproducible [i.e., see the Preferred Reporting Items for Systematic Reviews and Meta-Analyses in Ecology and Evolution (PRISMA-EcoEvo) protocol, @ODea2021].
 Aside from providing an up-to-date overview of a research field there are three major goals of meta-analysis: 1) to provide an overall mean estimate of a treatment effect or relationship, 2) to quantify effect size variance and understand key drivers explaining differences in effects across studies and 3) attempt to identify gaps and publication biases [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Koricheva2013; @Borenstein2019].
-A critically important feature of a meta-analysis is its ability to account for sampling error [@Koricheva2013].
-The inverse of sampling error variance is used to weight studies in the analysis and make overall estimates more precise (this is true for fixed effect models but note that weighting is more complex in multilevel meta-analytic models).
-While many meta-analyses might employ unweighted analyses, these studies will not gain greater precision on estimates because sampling variance cannot be formally accounted for in the analysis, even if the overall mean itself may be unbiased [@Morrissey2016a].
-In addition, unweighted meta-analyses are more susceptible to publication bias.
+Meta-analysing independent studies provides greater statistical power and precision than what any individual study on its own would be able to provide - particularly given that most empirical studies are already under-powered in many areas of biology [@Forstmeier2017; @Jennions2003; @Button2013].
+By expressing study effects on a common scale (i.e., standardised effect size) we can gain broader insight into the direction and efficacy of a particular treatment effect or the strength of a relationship between two variables of interest [@Gurevitch2018; @Koricheva2013].
+Meta-analyses have already provided comparative physiologists with powerful insights on pressing global challenges - from testing whether physiological plasticity can buffer organisms against climate change [e.g, @Seebacher2015] to the degree to which endocrine disrupting chemicals, such as bis-phenol A (BPA), impact aquatic organisms [e.g., @WuSeebacher2020].
 
@@
 Lack of comparability could result from studies differing in experimental design, species, measurement variables and sampling units, which can impact the generalisability of meta-analytic results [@Arnqvist1995; @Stewart2010].
-Indeed, study specific differences in comparative physiology are widespread.
-For example, experimental designs can vary in the temperatures that they apply or in the dosages of chemical modifiers used in experimental treatments [e.g., @WuSeebacher2020].
-To the uninitiated, this concern might not be unfounded given that heterogeneity in effects is often high in ecological and evolutionary meta-analyses [@Senior2016], telling us that the effect size varies a great deal from one population to another.
+For example, experimental designs in the field of comparative physiology can vary greatly in the temperatures or dosages of chemicals that they use in experimental treatments [e.g., @WuSeebacher2020].
+To the uninitiated, this concern might not be unfounded given that heterogeneity in effects is often high in ecological and evolutionary meta-analyses [@Senior2016], telling us that the effect size varies a great deal across studies.
 However, to many, having highly heterogeneous effects "...is the spice of life" [p.g., 519; @Cooperetal2019] because it provides opportunities to explore the reasons for why effects vary within and across studies [@Cooperetal2019; @Borenstein2019; @Gurevitch2018; @Glass2015].
 
-The goal of our review is to briefly overview the process of meta-analysis, making a case for why heterogeneity in a meta-analysis is a good thing for answering fundamental research problems and guiding research directions.
+The goal of our review is to briefly overview the process of meta-analysis, making a case for why heterogeneity is a good thing for answering fundamental research problems and guiding research directions.
 We introduce the idea of 'nuisance heterogeneity', showing comparative physiologists that it can be comfortably dealt with by re-formalising many existing effect sizes measures and/or by using multilevel meta-regression models.
-Indeed, a combination of these approaches might often be ideal.
 Then, we present results from a survey of published meta-analyses in the field of comparative physiology to gauge methodological and meta-analytic practices -- determining what types of effect sizes are commonly used, how often effect size estimates are impacted by 'nuisance heterogeneity' and whether meta-analytic models (i.e., models that account for sampling variance) are commonly applied.
-We also formalise alternative effect sizes and their associated sampling variance to provide comparative physiologists opportunities to explicitly incorporate treatment differences into the effect size estimates to ease their interpretation.
-Finally, we describe how more complex treatment differences, such as dosage differences (which may have non-linear effects) can be accommodated using multilevel meta-regression models.
-We hope to show how expanding the meta-analytic toolkit for comparative physiologists will provide new opportunities to address global scale problems that attempt to understand how organisms will cope with rapidly changing environments in the future.
+We also formalise alternative effect sizes and their associated sampling variance to provide comparative physiologists opportunities to explicitly incorporate 'nuisance heterogeneity' at the effect size level to ease their interpretation.
+Finally, we describe how more complex treatment differences, such as non-linear dosage differences, can be accommodated using multilevel meta-regression models.
+We hope that, by expanding the meta-analytic toolkit, it will provide new opportunities for comparative physiologists to address how organisms will cope with rapidly changing environments and anthropogenic stressors in the future.
 
@@
 
-Meta-analysis is always concerned with effect heterogeneity; in other words, the factors that drive differences in the direction and magnitude an of effect within and across studies [@Nakagawa2017; @Gurevitch2018; @Cooperetal2019; @Borenstein2019].
-The concept of heterogeneity is vitally important because it tells us how general a specific conclusion is likely to be, how much of the variance we see is the result of real biology (not just sampling variance), and provides a way to understand what the key biological factors are leading to an effect [@Nakagawa2017; @Borenstein2019].
+Meta-analysis is always concerned with effect heterogeneity; in other words, the factors that drive differences in the direction and magnitude of effects within and across studies [@Nakagawa2017; @Gurevitch2018; @Cooperetal2019; @Borenstein2019].
+The concept of heterogeneity is vitally important because it tells us how general findings are likely to be and how much of the variance we see is the result of real biology or methodological differences (not just sampling variance) [@Nakagawa2017; @Borenstein2019].
 There are a plethora of phenomena driving effect heterogeneity, some of which are interesting and others that are less so.
@@
 How many independent samples we collect impacts our precision in estimating the 'true' effect [@Borenstein2019].
-In meta-analysis we formally include sampling variance to remove this source of heterogeneity directly because it is known -- hence why having sampling variances for an effect is so important [@Gurevitch2018; @Koricheva2013].
+In a meta-analysis we formally include sampling variance to remove this source of heterogeneity directly because it is known [@Gurevitch2018; @Koricheva2013].
+While unweighted analyses are common, weighting studies makes overall estimates more precise, reliable and less susceptible to publication bias, even if the overall mean itself is unbiased [@Morrissey2016a].
+As such, weighting effect size estimates by their inverse sampling variance can be crucial in meta-analysis.
 Second, there are sociological factors impacting heterogeneity.
-These include attitudes towards publishing non-significant results.
+These include the ease with which novel and significant results are published relative to non-significant results.
 Low powered studies that do not find an 'effect' or that find an effect in the opposite direction often lead to what is called publication bias [@Jennions2013; @Nakagawa2021b; @Rothstein2005].
-Third, there is real biology driving differences in effects.
-This is particularly true in comparative physiology where different species with varying habitats, life-histories, mating systems and reproductive modes are synthesised.
+Third, real biological processes can drive effect heterogeneity.
+This is particularly true in comparative physiology where we synthesise data from different species with varying life-histories, habitats, mating systems and reproductive modes.
 As comparative physiologists, this is the stuff that gets us up every morning!
-Much variation could result from shared evolutionary history (i.e., phylogeny) or because of the different thermal environments species (or populations) occupy.
+Some variation could result from shared evolutionary history (i.e., phylogeny) or because of the different thermal environments species (or populations) occupy.
 We can model these biological factors to test predictions from hypotheses that we believe are key players impacting mean effect size and direction.
@@
 In some cases, these methodological factors are of direct interest.
-For example, the methods for measuring an outcome variable can result in different effects, and it is important we know and understand this as it can determine how experiments are designed in the future.
+For example, the methods for measuring an outcome variable can result in different effects, and it is important we know and understand this to determine how experiments can be designed in the future.
 In other cases, methodological factors might be considered 'nuisance heterogeneity' [following from @Cooperetal2019] -- factors we know vary, but are rather unsurprising to us (Figure \@ref(fig:fig1)).
 These might include differences in temperature, pH, dosages, water potential etc.
-It might already be clear that these factors will have an impact on the magnitude of an effect, but they might distract from the core interest of a meta-analysis.
+While these factors are likely to have an impact on the magnitude of an effect, they might distract from the core interest of a meta-analysis.
 In some cases, however, the latter factors might actually not be 'nuisance' variables but the main interest of a synthesis.
@@
 ```{r, fig1, fig.cap="*Sources of effect size heterogeneity in meta-analyses*.
-Heterogeneity can come in various forms from effect measures varying as a result of shared evolutionary history (i.e., phylogeny), different trait types measured, and even sources of 'nuisance heterogeneity'.
-Nuisance heterogeneity can be factors, such as temperature differences impacting effect size measures, or dosages.
+Heterogeneity can come in various forms, from effect measures varying as a result of shared evolutionary history (i.e., phylogeny), different trait types measured, and sources of 'nuisance heterogeneity'.
+In this example, nuisance heterogeneity is generated by differences in the experimental temperatures at which the animals were tested.
+However, nuisance heterogeneity can come in various other forms such as differences in dosage, or biochemical variables between used in the experiments.
 We can control for these types of heterogeniety by reformalising effect sizes and/or using multilevel metaregression as we describe in our review"}
@@
 
-All the various sources of heterogeneity (except sampling variance) contribute (to varying extents) to the 'apples and oranges' problem often touted as being an issues with meta-analyses (or quantitative syntheses more generally).
+Besides sampling variance, all the various sources of heterogeneity contribute (to varying extents) to the 'apples and oranges' problem often touted as compromising the reliability of meta-analyses.
 Indeed, some of this criticism revolves around combining studies that vary in their quality (e.g., observational vs experimental).
-Combining standardised effects, while ignoring these sources of heterogeneity can result in the meaning of a meta-analysis not being particularly useful.
-However, many argue that this is just what we are interested in synthesizing [@Cooperetal2019; @Borenstein2019; @Gurevitch2018; @Glass2015].
-In the words of Gene Glass, the father of meta-analysis: "Of course it [meta-analysis] mixes apples and oranges; in the study of fruit nothing else is sensible; comparing apples and oranges is the only endeavor worthy of true scientists; comparing apples to apples is trivial" [p.g., 224, @Glass2015].
-@Glass2015's intention was to simply highlight that whether comparing apples and oranges is a good idea simply boils down to the specific question of interest, the population one wishes to make conclusions about and how heterogeneous effects actually are.
+Combining standardised effects, while ignoring these sources of heterogeneity can indeed weaken the reliability of a meta-analysis.
+However, many argue that heterogeneity is just what we are interested in synthesizing [@Cooperetal2019; @Borenstein2019; @Gurevitch2018; @Glass2015].
+In the words of Gene Glass, the founder of meta-analysis: "Of course it [meta-analysis] mixes apples and oranges; in the study of fruit nothing else is sensible; comparing apples and oranges is the only endeavor worthy of true scientists; comparing apples to apples is trivial" [p.g., 224, @Glass2015].
+Whether comparing apples and oranges is a good idea simply boils down to the specific question of interest, the population one wishes to make conclusions about and how heterogeneous effects actually are.
 If we are interested in gaining insight into 'fruit' then synthesising apples and oranges is the only thing that makes sense.
-Instead, if we are interested in generalising only to apples then mixing fruit will not be ideal.
-In addition, if we want to understand why different 'fruit' vary in their effects, then we can only ask this question by including all fruit [@Borenstein2019].
+Instead, if we are interested in generalising only to apples, then mixing fruit will not be ideal.
+However, if we want to understand why different 'fruit' vary in their effects, then we can only ask this question by including all fruit [@Borenstein2019].
 
 We tend to agree with @Glass2015, and his sentiment is of particular relevance to comparative physiology.
-For example, if we want to understand the impact of a pollutant on reproduction in aquatic organisms then including aquatic mammals and fish would provide answers to this general question, even if their reproductive biology and physiology are known to differ.
-By synthesizing diverse study outcomes, it allows us to not just report on overall effects (if the question is relevant to ask), but to understand critical features of the literature, study systems (e.g., different effects of pollutants on fish and mammal reproduction) and approaches that can explain the diversity of effect outcomes observed.
-In doing so, it provides a richer set of conclusions that can draw attention to important sources of variability that might have otherwise been overlooked.
-Having said that, it is still very important to understand the limitations and diversity of studies included within a meta-analysis, and how this can affect interpretations made -- an important reason why transparency and reproducibility are such a prominent feature of meta-analysis (or ideally should be) [@ODea2021].
+For example, if we want to understand the impact of a pollutant on reproduction in aquatic organisms, including aquatic mammals and fish would provide answers to this general question, even if their reproductive biology and physiology are different.
+By synthesizing diverse study outcomes, not only does it allow to report on overall effects (if the question is relevant to ask), but it allows us to also understand critical features of the literature, study systems (e.g., different effects of pollutants on fish and mammal reproduction) and approaches that can explain the diversity of effect outcomes observed.
+Doing so provides a richer set of conclusions that can draw attention to important sources of variability that might have otherwise been overlooked.
+Having said that, it is still very important to understand the limitations and diversity of studies included in a meta-analysis, and how this can affect interpretations made -- an important reason why transparency and reproducibility are such a prominent feature of meta-analysis (or ideally should be) [@ODea2021].
 The validity of general conclusions to certain questions (e.g., what is the overall effect of a pollutant on reproduction?) will inevitably depend on the homogeneity of effects being synthesized.
@@
 If, however, an overall effect is accompanied by large heterogeneity estimates, then we would shift focus and explore drivers of that heterogeneity.
-For example, given the very different physiology of aquatic mammals and fish, understanding an overall combined effect on reproduction may not be particularly relevant, and indeed may be misleading.
-Therefore, understanding overall effects in each of these groups separately (and whether they differ) will be more useful.
-It is important to consider these questions when conducting meta-analyses.
+For example, given the very different physiology of aquatic mammals and fish, understanding an overall combined effect on reproduction may not be particularly relevant, and indeed may even be misleading.
+Therefore, understanding overall effects in each of these groups separately, and assess the extent to which they differ, may be more useful.
 
-Of course, there are certain types of heterogeneity that transcend different questions or that are simply a 'nuisance' to interpreting effects.
-In other words, if we compare different types of 'apples' is it still fair to synthesize these studies to understand overall effects?
-This situation might be analogous to a meta-analysis in comparative physiology that attempts to understand the effects of diet on fish growth across different populations of a widely distributed (cosmopolitan) species.
+There are, however, certain types of heterogeneity that transcend different questions or that are simply a 'nuisance' to interpreting effects.
+In other words, if we compare different varieties of 'apples', is it still fair to synthesize these studies to understand overall effects?
+In comparative physiology, this situation might be analogous to a meta-analysis that attempts to assess the effects of diet on fish growth across different populations of a widely distributed (cosmopolitan) species.
 Studies might rear populations of fish under different temperatures, but in the end, they are still all the same fish species, governed by the same thermodynamic effects on growth.
-In this situation, we might still be interested in understanding overall effects, but we may question whether such a conclusion is sensible given the diversity of temperatures applied.
-It is not always clear how we should tackle these sources of heterogeneity.
-If temperature differences are of direct interest, then we should definitely model them.
-If, however, it is less interesting, than say the diet administered, then it may introduce an unnecessary complication to the interpretation of the effect(s) of interest.
-Here, we focus on meta-analytic tools to circumvent these issues and demonstrate that the 'apples and oranges' problem is not really a problem at all.
+In this situation, we are still interested in understanding overall effects, but we may question whether such a conclusion is sensible given the diversity of temperatures applied.
+If temperature differences are of direct interest, then this variable can be formally incorporated in statistical models.
+If, however, it is not of primary interest, then it may introduce an unnecessary complication to the interpretation of the effect of diet on fish growth.
+Here, we focus on meta-analytic tools to circumvent these issues and demonstrate that the ‘apples and oranges’ problem is not really a problem at all.
 
@@
 
-Before embarking on "meta-analytic enlightenment", it is worth first understanding how comparative physiologists are currently conducting meta-analyses / comparative analysis.
-As discussed above, different types of questions and experimental approaches will mix 'apples and oranges' to varying extents, and indeed, this heterogeneity (or basket of fruit) is often the main interest to comparative biologists.
-To better understand the different types of effect sizes being used, their susceptibility to known sources of methodological / environmental variability across studies, and how these sources are controlled we conducted a literature survey.
+Before embarking overviewing strategies to deal with 'nuisance heterogeneity', it is worth first understanding how comparative physiologists are currently conducting meta-analyses and other quantitative syntheses.
+As discussed above, different types of questions and experimental approaches will mix 'apples and oranges' to varying extents, but this heterogeneity (or basket of fruit) is often the main interest to comparative biologists.
+We conducted a literature survey to better understand the different types of effect sizes being used, their susceptibility to known sources of methodological / environmental variability across studies, and how these sources are controlled we conducted a literature survey.
 To accomplish this goal, we searched for meta-analyses and comparative analyses that tackled questions using physiological data compiled from animal studies across multiple species.
@@
 We expected this to provide a contemporary overview of quantitative syntheses in comparative physiology while making the survey and screening feasible.
-We acknowledge that this may have missed some important, and influential, quantitative synthesis in the field of comparative physiology, but likely provided a random sample to inform on the questions we sought to address (see below).
+We acknowledge that this may have missed some important, and influential, quantitative syntheses in the field of comparative physiology, but likely provided a random sample to inform on the questions we sought to address (see below).
 
-We included quantitative syntheses, including meta-analyses (*sensu stricto*), that were focused on comparative physiological questions only.
+We included comparative / meta-analyses that were focused on comparative physiological questions.
 Narrative reviews and comments were not considered because they did not collate quantitative data from the literature.
-Studies needed to have collected physiological trait data from the literature including traits, such as hormones, thermal physiology (CTmax, CTmin, thermal preferences, thermal breadth, LT50, lethal thresholds), metabolic rates (routine, maximum, and minimum metabolic rate, aerobic scope), enzyme reaction rates and concentrations, oxidative stress and consequences (e.g., DNA damage, teleomere attrition), performance measurements (e.g., heart rates, sprint speed, swim speed, growth rates), body composition (e.g., fatty acid profiles) and immune traits (e.g., cell function, antibodies, ect.).
-Studies were also included if they measured the relationship between physiological traits and body size (e.g., metabolic scaling), reproductive allocation, or survival / mortality across taxa.
+Studies needed to have collected physiological trait data from the literature such as hormones, thermal physiology (CTmax, CTmin, thermal preferences, thermal breadth, LT50, lethal thresholds), metabolic rates (routine, maximum, and minimum metabolic rate, aerobic scope), enzyme reaction rates and concentrations, oxidative stress and consequences (e.g., DNA damage, teleomere attrition), performance measurements (e.g., heart rates, sprint speed, swim speed, growth rates), body composition (e.g., fatty acid profiles) and immune traits (e.g., cell function, antibodies).
+Studies were also included if they measured the relationship between physiological traits and body size (e.g., metabolic scaling), reproductive allocation, or survival across taxa.
 Studies on behavior were only included if the synthesis was explicitly interested in the proximate physiological drivers of behavioral variation.
-We also included meta-analyses that quantified plasticity in physiological traits across taxa for the purpose of understanding adaptive plasticity in response to environmental variation.
-While many studies in comparative physiology collect data as part of a comparative analysis, we focus here only on studies collating data from existing literature because this is the major data source for quantitative synthesis.
+We also included meta-analyses that quantified plasticity in physiological traits in response to environmental variation.
+While many studies in comparative physiology collect data as part of a comparative analysis, we focus here only on studies collating data from existing literature because this is the major data source in quantitative syntheses.
 Quantitative syntheses interested in phenology, bio-mechanics, sexual size dimorphism (i.e., SSD, except if the study was interested in sexual differences in physiological traits), those focused on validating physiological methodology, or characterising population genetic structure, gene transcription and quantitative genetics were excluded.
@@
 As such, these studies were also excluded.
-We restricted our focus to animal studies because plant synthesis papers were often only focused on ecological (e.g., quantified changes in abundance and distribution of species) or agricultural questions (e.g., studies on soil microbial function, nitrogen and phosphorus capture, methane output and greenhouse gas emissions).
+We restricted our focus to animal studies because most plant synthesis papers were focused on ecological (e.g., quantified changes in abundance and distribution of species) or agricultural questions (e.g., studies on soil microbial function, nitrogen and phosphorus capture, methane output and greenhouse gas emissions).
 
@@
 Any conflicts or disagreements were resolved by discussion and a consensus on a paper was reached.
-Out of the 417 papers, 79 full texts were screened and we included a total of 62 for final data extraction.
-For full details on the search strings used, dates searched, the number of papers found, and our PRISMA flowchart (along with reasons for exclusion at the full text stage) we refer readers to the *Supplementary Materials*.
+Out of the 417 papers originally identified, 79 full texts were screened for eligibility, and we included a total of 62 for final data extraction.
+For full details on the search strings used, dates searched, the number of papers found, and our PRISMA flowchart (along with reasons for exclusion at the full text stage) we refer readers to the *Supplementary Information*.
 To address our questions, we categorised effect sizes as falling into the following categories: Response Ratio (lnRR), Standardised Mean Differences (SMD; e.g., Hedges d, g or Cohen's d), Correlation or Fisher's Z -transformed Correlation, Regression Slopes (Slopes), Risk Ratios, or whether the paper analysed the raw data or summary statistics directly (i.e., means/proportions) (which we label as 'raw').
@@
 If it was not clear, two of us (DWAN & PP) discussed the paper, and made a decision about whether the effect measure was likely to be impacted.
-For example, trait means, such as ectothermic metabolic rate (i.e., raw/mean/proportion-based effect size), will vary depending on the temperature being measured, the magnitude of differences between two treatments (e.g, contrast-based effect sizes - SMD or lnRR) might depend on the temperature or dosage used in treatments, and the strength of relationship between two variables (e.g., correlation between behaviour and metabolism) might depend on the temperature context under which metabolic rate or behaviour were measured.
-Given the high heterogeneity in effects used in comparative physiology, we expected 'nuisance heterogeneity' to be common to most effect sizes, however, it has not been formally quantified.
-We categorised the types of statistical models fit in each study as: 1) fixed-effect meta-analysis; 2) random effects meta-analysis (i.e., intercept only model, but has random study effects); 3) multi-level meta-analysis (i.e., intercept only model, but has multiple random effect levels such as study, species, observation-level random effects); 4) meta-regression models (i.e., a multilevel or random effect model with fixed effects - including random effects); 5) weighted regression models, including mixed effect models; and 6) linear regression models (including linear and generalised linear mixed effect models, and phylogenetic least squares models).
+For example, trait means, such as ectothermic metabolic rate (i.e., raw/mean/proportion-based effect size), will vary depending on the temperature being measured.
+The magnitude of differences between two treatments (e.g, contrast-based effect sizes - SMD or lnRR) might depend on the pH or dosage used in treatments, and the strength of relationship between two variables (e.g., correlation between behaviour and metabolism) might depend on the temperature context under which metabolic rate or behaviour were measured.
+Given the high heterogeneity in effects used in comparative physiology, we expected 'nuisance heterogeneity' to be common to most effect sizes.
+We categorised the types of statistical models fit in each study as: 1) fixed-effect meta-analysis; 2) random effects meta-analysis (i.e., intercept only model, but has random study effects); 3) multilevel meta-analysis (i.e., intercept only model, but has multiple random effect levels such as study, species and observation-level random effects); 4) meta-regression models (i.e., a multilevel or random effect model with fixed effects - including random effects); 5) weighted regression models (including mixed effect models); and 6) linear regression models (including linear and generalised linear mixed effect models, and phylogenetic least squares models) [see @NakagawaSantos2012 for discussion of models].
 Notably, only model types 1-5 are weighted models because they weight effect sizes based on the inverse of their sampling variance or sample size.
@@
 In many cases, studies make use of multiple effect size measures.
-Approximately `r with(hetero, hetero[cont_moderator_variable == "yes","percent"])*100`% of effect sizes used within the study we deemed to be impacted by 'nuisance heterogeneity' in some form or another (Figure \@ref(fig:figsurv)B), but of the studies where this was the case, only `r with(hetero_dealt, hetero_dealt[cont_moderator_variable_modelled == "yes","percent"])*100`% of the studies clearly dealt with it (Figure \@ref(fig:figsurv)B); usually through meta-regression modelling.
-Overall, `r with(weighted, weighted[meta_analysis_weighted == "weighted model","percent"])*100`% of studies used a weighted meta-analytic model, however, of the studies self described as 'meta-analyses', `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","percent"])*100`% (N = `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","n"])` of `r with(weighted_meta, sum(weighted_meta[,"n"]))`) did not actually weight their meta-analytic mean.
+Approximately `r with(hetero, hetero[cont_moderator_variable == "yes","percent"])*100`% of effect sizes used within the study we deemed to be impacted by 'nuisance heterogeneity' in some form or another (Figure \@ref(fig:figsurv)B), but of the studies where this was the case, only `r with(hetero_dealt, hetero_dealt[cont_moderator_variable_modelled == "yes","percent"])*100`% of the studies clearly dealt with it (Figure \@ref(fig:figsurv)B); often through meta-regression modelling.
+Overall, `r with(weighted, weighted[meta_analysis_weighted == "weighted model","percent"])*100`% of studies used a weighted meta-analytic model, however, of the studies self described as 'meta-analyses', `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","percent"])*100`% (N = `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","n"])` of `r with(weighted_meta, sum(weighted_meta[,"n"]))`) did not account for sampling variance.
 Many studies used 'Linear Regression' (including linear and generalised linear mixed effects models) as the main type of model fit to the data (Figure \@ref(fig:figsurv)C).
@@
 ```{r, figsurv, fig.cap="**Summary of meta-analytic practices in comparative physiology.** (A) Different types of effect measures commonly used in meta-analyses and their relative frequency of use.
-(B) how many meta-analyses where 'nuisance heterogenity' have the potential to impact effect sizes, and the proportion of studies explicitly dealing with nuisance heterogenity.
+(B) How many meta-analyses where ‘nuisance heterogenity’ have the potential to impact effect sizes, and the proportion of studies explicitly dealing with nuisance heterogenity.
 (C) Frequency of analytical approaches used to analyse effect measures.
-Note that only 'Weighted Regression', 'Random Effects Models', 'Multilevel Metaregression Models' and 'Multilevel Meta-analysis Models' are weighted models."}
+Note that only ‘Weighted Regression’, ‘Random Effects Models’, ‘Multilevel Metaregression Models’ and ‘Multilevel Meta-analysis Models’ are weighted models.
+The results of this survey were drawn from 62 studies in comparative physiology."}
 p1 = dat %>% dplyr::group_by(effect_size_type) %>% janitor::tabyl(effect_size_type)  %>% 
@@
 Meta-analysis requires comparative physiologists to make use of effect sizes that are suitable for answering their specific question.
-The key features of all effect sizes used in meta-analyses are that they are: 1) statistical parameters that have been placed on a common scale so that they can be compared across studies and 2) that they have some associated measure of precision (i.e., sampling variance)[@Koricheva2013; @Borenstein2009; @Schmid2021].
-Effect sizes in comparative physiology are quite variable; they can be the mean difference between two groups [e.g., difference in mean between a control and treatment group - see @WuSeebacher2020], the slope of a regression (e.g., between body size and metabolic rate), a correlation between two variables, or even the raw mean (or variance) itself [e.g., comparing CTmax or CTmin across species - see @Sunday2014].
+The key features of all effect sizes used in meta-analyses are that: 1) they are statistical parameters that have been placed on a common scale so that they can be compared across studies and 2) they have some associated measure of precision (i.e., sampling variance) [@Koricheva2013; @Borenstein2009; @Schmid2021].
+Effect sizes in comparative physiology are quite variable; they can be the mean difference between two groups [e.g., difference in mean between a control and treatment group; e.g., @WuSeebacher2020], the slope of a regression (e.g., between body size and metabolic rate), a correlation between two variables (e.g., between hormone levels and behaviour), or even the raw mean (or variance) itself [e.g., comparing CTmax or CTmin across species - e.g., @Sunday2014].
 In many cases, different effect sizes might be used depending on the question.
-For example, studies interested in the effect of temperature on some physiological trait that have measured the trait across studies experimentally manipulating temperature could analyse the mean 'effect' by creating contrast-based effect sizes or by analysing the mean in each temperature treatment.
-The choice as to which one to use will boil down to the types of data available from primary studies, the specific question of interest and whether studies are observational or experimental in nature.
+For example, to investigate the effect of temperature on a physiological trait, one can compile studies experimentally manipulating temperature and analyse the mean 'effect' by creating contrast-based effect sizes, or alternatively, just model the trait in each temperature treatment.
+The choice as to which one to use boils down to the types of data available from primary studies, the specific question of interest, and whether studies are observational or experimental in nature.
 Considering our temperature example above, if we are interested in the magnitude of change between temperature treatments, we may want to use a contrast-based effect size, such as the log response ratio $\ln{RR}$.
-If we are instead interested in how the mean of some physiological trait changes with temperature we may instead model the mean itself.
-In the latter scenario, so long as all the means are measured in the same units (e.g., ; or can be converted to the same units) then the mean may provide the desired answer to a given question.
+Instead, if we are interested in how the mean of some physiological trait changes with temperature, we may model the mean itself.
+In the latter scenario, as long as all the means are measured in the same units (e.g., Celsius; or can be converted to the same units) then the mean may provide the desired answer to the original question.
 We provide details on different effect measures and associated sample sizes in Table \@ref(tab:tablea).
 
-```{r tablea, echo = FALSE, tab.cap = "Common effect sizes used throughout meta-analyses in comparative physiology, their associated sampling variances and examples on when they might be used."}
+```{r tablea, echo = FALSE, tab.cap = "Common effect sizes used throughout meta-analyses in comparative physiology, their associated sampling variances and examples on when they might be used.
+M: mean; SD: standard deviation; N: sample size; CTmin: critical thermal minimum; CTmax: critical thermal maximum; BPA: bisphenol A."}
 
@@
            "Standardised Mean Difference, SMD",
-           "Zr (Fisher Trasnformaiton of \n correlation Coefficient, r)")
+           "Zr (Fisher Transformation of \n correlation Coefficient, r)")
            #"Log Odds Ratio",
@@
 As can be seen in Table \@ref(tab:tablea), none of the effect measures control for 'nuisance heterogeneity'.
-For example, the magnitude of response between two treatment groups for lnRR or SMD might depend on just how different the temperatures, dosages, pH or water potential applied in each treatment.
-Even modelling just the mean often needs to control for various sources of 'nuisance heterogeneity'.
+For example, the magnitude of lnRR or SMD might depend on just how different the temperatures, dosages, pH or water potential applied in each treatment.
+The same applies for modelling the means.
 For example, standard metabolic rate (SMR) is temperature dependent.
@@
 We highlight two examples in the box focusing mainly on generality.
-Below, we show using a common, well understood effect measure of interest to comparative physiologists, $Q_{10}$, how we can formalise a traditional effect size, such as $lnRR$, to capture this 'nuisance variation'.
+Below, we show how to formalize a traditional effect size, $lnRR$, into a common measure of interest to comparative physiologists, $Q_{10}$, and show how this new effect size can capture “nuisance heterogeneity”.
 
@@
 As such, it is common to standardize effects by temperature.
-One common effect size measure already used in comparative physiology to compare physiological rates is $Q_{10}$ [e.g., @Rodgers2021; @Seebacher2015; @Havird2020], which describes the multiplicative change in physiological rates across a 10°C temperature change.
+One common effect size measure already used in comparative physiology to compare physiological rates is the temperature coefficient $Q_{10}$ [e.g., @Rodgers2021; @Seebacher2015; @Havird2020].
+This effect size describes the multiplicative change in physiological rates across a 10°C temperature change.
 Higher $Q_{10}$ values indicate larger changes in physiological rates.
-Currently, however, we do not seem to have associated sampling variances derived for $Q_{10}$ in the literature, making it challenging to make use of the full power of weighted meta-analytic models.
-Interestingly, $Q_{10}$ can be seen as a variant of *lnRR*, meaning that we can derive a $Q_{10}$ based effect size and sampling error using the well known mathematical properties of *lnRR*.
+However, currently there is no formal sampling variance associated with $Q_{10}$ in the literature, making it challenging to make use of the full power of weighted meta-analytic models.
+Interestingly, $Q_{10}$ can be seen as a variant of *lnRR*, meaning that we can derive a $Q_{10}$- based effect size and sampling error using the well-known mathematical properties of *lnRR*.
 This opens up the meta-analytic toolbox and improves upon our ability to account for well known sources of non-independence that are typical in meta-analysis [@Lajeunesse2011; @Noble2017].
@@
 
-In equation \@ref(eq:lnRR), $M_{1}$ is the mean of group 1, often a control group, where as $M_{2}$ is the mean of group 2 (e.g., a treatment group).
-The mean of $X_{i}$ for group *i* can be any measurement type (e.g.
+In equation \@ref(eq:lnRR), $M_{1}$ is the mean of group 1 (e.g., a control group), where as $M_{2}$ is the mean of group 2 (e.g., a treatment group).
+The mean, $M_{i}$, for group *i* can be any measurement type (e.g.
 a physiological rate, mass etc) so long as the measurement variable is ratio scale.
-Log transformation of this ratio makes the effect size normally distributed (most commonly assumed by meta-analytic models).
+Natural log transformation of this ratio makes the effect size normally distributed which is commonly assumed by meta-analytic models.
 Equation \@ref(eq:slnRR) is the analytical solution for *lnRR*'s sampling variance where, $SD_{1}^2$ and $SD_{2}^2$ is the sample variance in group 1 and 2, respectively and $N_{1}$ and $N_{2}$ is the sample size in group 1 and 2.
 
-The equations for *lnRR* and its sampling variance allow us to easily extend this to $Q_{10}$ based effect sizes. Recall that $Q_{10}$ is described as follows:
+The equations for *lnRR* and its sampling variance allow us to extend this to $Q_{10}$ based effect sizes. Recall that $Q_{10}$ is described as follows:
 
@@
 \end{equation} 
-$$ Here, $R_{1}$ and $R_{2}$ are mean physiological rates and $T_{1}$ and $T_{2}$ are the temperatures that these rates are measured.
-Log transformation of equation \@ref(eq:q10) leads to the following log transformed $Q_{10}$:
+$$
+
+Here, $R_{1}$ and $R_{2}$ are mean physiological rates and $T_{1}$ and $T_{2}$ are the temperatures that these rates are measured.
+Natural log transformation of equation \@ref(eq:q10) leads to the following log transformed $Q_{10}$:
 
@@
 \end{equation} 
-$$ Equation \@ref(eq:lnq10) is essentially a temperature corrected equivalent of lnRR when the numerator and denominator are measured at different temperatures.
+$$
+
+Equation \@ref(eq:lnq10) is essentially a temperature corrected equivalent of lnRR when the numerator and denominator are measured at different temperatures.
 This allows one to compare the mean of two temperature treatments directly regardless of the temperatures that these groups have been measured.
 Here, we will refer to this as the log $Q_{10}$ response ratio, $lnRR_{Q_{10}}$.
-Notably, by taking the natural logarithm, there are two statistical advantages: 1) 0 becomes biologically meaningful as 0 means two rates are the exactly the same and 'significantly different from 0' means that two rates are significantly different to each other and 2) $lnRR_{Q_{10}}$ is more likely to satisfy the assumption of residual normality than $Q_{10}$ (see @Hedges1999).
-The recognition of this equivalence means that we can easily calculate the sampling variance for equation \@ref(eq:lnq10) as follows:
+Notably, using this effect rather than the traditional $Q_{10}$ has two statistical advantages: 1) zero becomes biologically meaningful as 0 means two rates are the exactly the same and 'significantly different from zero' means that two rates are significantly different to each other and 2) $lnRR_{Q_{10}}$ is more likely to satisfy the assumption of residual normality than $Q_{10}$ (see @Hedges1999).
+The recognition of this equivalence means that we can calculate the sampling variance for equation \@ref(eq:lnq10) as follows:
 
@@
 
-Equations \@ref(eq:lnq10VR) and \@ref(eq:slnq10VR) describe the change in physiological rate variance (eqn \@ref(eq:lnq10VR)) across a 10°C temperature change along with its sampling variance (eqn \@ref(eq:slnq10VR)).
-While this is a useful metric, as discussed by @Nakagawa2015 there is often a strong mean-variance relationship that needs to be accounted for in analysing changes in variance.
+Equations \@ref(eq:lnq10VR) and \@ref(eq:slnq10VR) describe the change in physiological rate variance (eqn \@ref(eq:lnq10VR)) relative to a 10°C temperature change, along with its sampling variance (eqn \@ref(eq:slnq10VR)).
+While this is a useful metric, as discussed by @Nakagawa2015, there is often a strong mean-variance relationship that needs to be accounted for in analysing changes in variance.
 As such, we can calculate the coefficient of variation, which standardises changes in variance for changes in means as follows:
@@
 Our example using $Q_{10}$, a well-known effect measure in comparative physiology, shows how common effect size's can be re-formalised to account for 'nuisance heterogeneity', in this case temperature.
-Of course, in doing this we are making assumptions about the nature of temperature effects on an effect size.
+In doing so, we are making assumptions about the nature of temperature effects on an effect size.
 Nonetheless, we can apply similar approaches to other commonly used effect size metrics.
-We describe more generally how this can be done in Box 1, applying similar principles to standardise temperature differences for slopes and for standardised mean differences.
+We describe more generally how this can be done in Box 1, applying similar principles to standardise temperature differences for slopes and standardised mean differences.
 
@@
 
-It will not be possible to derive an effect size that completely controls for 'nuisance' heterogeneity at the effect size level all the time.
-This limitation is partly because treatment effects may not be simple linear or exponential functions of the mean response making the effect sizes we discuss above unsuitable [e.g., thermal performance curves; @Noble2018].
-For example, dosages applied to treatments can follow quite complex non-linear relationships (e.g., quadratic relationships) in relation to some mean response.
-When this occurs we recommend comparative physiologists apply meta-regression approaches, controlling for 'nuisance heterogeneity' as a moderator.
-In many cases, this will be the easiest, or even preferred approach because exploring drivers of heterogeneity will be the main interest in most meta-analyses anyway.
-Nonetheless, there are some simple statistical approaches a meta-analyst can use to then make the overall effects more easily interpretable, allowing one to control for 'nuisance heterogeneity', while also testing other biological moderators of interest [@Schielzeth2010].
+It will not be possible to always derive an effect size that completely controls for 'nuisance heterogeneity' at the effect size level all the time.
+This limitation is partly because treatment effects may not be simple linear or exponential functions of the mean response, making the effect sizes we discuss above unsuitable [e.g., thermal performance curves; @Noble2018].
+For example, dosages applied to treatments can follow quite complex non-linear (e.g., quadratic) relationships in relation to some mean response.
+When this occurs, we recommend comparative physiologists to apply meta-regression approaches, controlling for 'nuisance heterogeneity' as a moderator.
+In many cases, this will be the easiest, or even preferred approach because exploring drivers of heterogeneity is of prime interest in most meta-analyses anyway.
+Nonetheless, there are some simple statistical approaches a comparative physiologist can use to make the overall effects more easily interpretable, allowing one to control for 'nuisance heterogeneity', while also testing other biological moderators of interest [@Schielzeth2010].
 Before diving into meta-regression models, we will first overview the meta-analytic models commonly used.

### 2021-07-21 MS/ms.Rmd
Patrices comments for MS included

@@
 
-```{r, figsurv, fig.cap="**Summary of meta-analytic practices in comparative physiology.** (A) Different types of effect measures commonly used in meta-analyses and their relative frequency of use.
+```{r, figsurv, fig.wid = 16.833333, fig.height=6.611111,fig.cap="**Summary of meta-analytic practices in comparative physiology.** (A) Different types of effect measures commonly used in meta-analyses and their relative frequency of use.
 (B) How many meta-analyses where ‘nuisance heterogenity’ have the potential to impact effect sizes, and the proportion of studies explicitly dealing with nuisance heterogenity.
@@
   scale_fill_viridis_d() +
-  theme(legend.position = c(0.50, 0.8)) + 
+  theme(legend.position = c(0.45, 0.8)) + 
   labs(x = "Nuisance Heterogeneity?",
@@
 A common goal of meta-analysis is to obtain an overall meta-analytic mean effect size estimate and some form of uncertainty around that mean, like a 95% confidence interval (CI).
-Including a prediction interval (PI) can also be quite useful (see below for why) [@Nakagawa2021c].
+Including a prediction interval (PI) can also be useful (discussed below) [@Nakagawa2021c].
 Estimating an overall mean and 95% CI is generally done with a simple random effects or multilevel meta-analytic model that accounts for effect size sampling error [@Nakagawa2017; @NakagawaSantos2012].
 More often than not, meta-analyses in comparative physiology will have complex hierarchical structure.
-For example, multiple effect sizes may be taken from a single study on different traits measured on the same individuals, or come from many different species that share an evolutionary history [@Cinar2021; @Noble2017].
-As such, it is far more likely that comparative physiologists will need to apply a multi-level meta-analytic model to control for the various sources of non-independence, and whenever possible they should [@Cinar2021; @NakagawaSantos2012; @Song2021; @Nakagawa2021; @Noble2017].
+For example, multiple effect sizes may be taken from a single study on traits measured on the same individuals, or come from many different species that share an evolutionary history [@Cinar2021; @Noble2017].
+As such, it is far more likely that comparative physiologists will need to apply a multilevel meta-analytic model to control for the various sources of non-independence, and whenever possible, they should [@Cinar2021; @NakagawaSantos2012; @Song2021; @Nakagawa2021; @Noble2017].
 Multilevel models are also extremely useful in describing the various sources contributing to effect size variance (a feature we describe below).
-For the purpose of our discussion, we will assume the meta-analyst needs to use more advanced multilevel models.
-Having said that, it may be sufficient for a meta-analysis to make use of traditional random effects models.
+For the purpose of our discussion, we will assume one needs to use more advanced multilevel models.
+Having said that, in some instances, it may be sufficient for a meta-analysis to make use of traditional random effects models.
 We refer readers to excellent reviews and books that overview the distinctions between common (fixed) effect, random effect and multilevel models and when one might want (or not want) to apply these models [@Nakagawa2017; @NakagawaSantos2012; @Koricheva2013; @Borenstein2009; @Schmid2021].
@@
 We might extract data from studies manipulating corticosterone in bird eggs.
-Of course, these studies are diverse, apply different dosages of corticosterone and are working across many species.
-If the studies are experimental in nature then a standardised effect size, such as $ln_{RR}$ or Hedges' *d*, might be applicable.
+Of course, these studies are diverse, spanning many species and applying different dosages of corticosterone and are working across many species.
+If the studies are experimental in nature, then a standardised effect size, such as $ln_{RR}$ or SMD, might be applicable.
 We then might fit an overall multilevel meta-analytic model as follows:
@@
 Phylogenetic effects are assumed to be normally distributed deviates sampled from a distribution with a mean of 0 and variance $\sigma^{2}_{phylogeny}$ [i.e., *N*$(0, \sigma^{2}_{phylogeny}\textbf{A})$], where $\textbf{A}$ is a phylogenetic correlation matrix derived from a phylogenetic tree.
-$sp_{k[i]}$ is an additional species-specific effect for the *k*th species applied to effect size *i* [i.e., these are species-specific effects because of shared ecology and other factors, @Cinar2021], $s_{j[i]}$ is the study-specific effect for the *j*th study applied to effect size *i*, $e_{i}$ is the effect size-specific effect (or within study effect, or residuals) for the *i*th effect size, and $m_{i}$ is the sampling variance effect around the *i*th effect as a result of variation in precision among each effect sizes, $v_{i}$, which is known as the sampling variance for effect.
-This model is a 'weighted' multilevel meta-analysis model because the estimation of the overall meta-analytic mean, $\beta_{0}$, is weighted by the inverse sampling variance of each effect size.
-Importantly, if we have effect sizes that are derived from the *same* sample of animals (or plants) (e.g., may be because many traits are measured on the same sets of animals) then we need to remove this dependency from the calculation of each $v_{i}$; we can then model the known sampling covariance between effect sizes by modifying $\textbf{I}$ to include off-diagonals that account for this covariance [See Box 1 and @Noble2017].
+$sp_{k[i]}$ is an additional species-specific effect for the *k*th species applied to effect size *i* [i.e., these are species-specific effects because of shared ecology and other factors, @Cinar2021], $s_{j[i]}$ is the study-specific effect for the *j*th study applied to effect size *i*, $e_{i}$ is the effect size-specific effect (or within study effect, or residuals) for the *i*th effect size, and $m_{i}$ is the sampling variance effect around the *i*th effect as a result of variation in precision among each effect sizes, $v_{i}$, which is known as the sampling variance for the effect.
+This model is a 'weighted' multilevel meta-analysis model because the estimation of the overall meta-analytic mean, $\beta_{0}$, is partially weighted by the inverse sampling variance of each effect size.
+Importantly, if we have effect sizes that are derived from the *same* sample of organisms (e.g., because traits are measured on the same sets of individuals) then we need to remove this dependency from the calculation of each $v_{i}$; we can then model the known sampling covariance between effect sizes by modifying $\textbf{I}$ to include off-diagonals that account for this covariance [See Box 1 and @Noble2017].
 The fact that we can obtain an overall estimate of sampling variance (i.e., $\sigma^2_{m}$, see below for how it is defined) is very important because it provides a way for us to understand just how much variation in effects are the result of sampling differences across studies versus other, potentially important sources of variation such as differences in the methods applied, species differences or even real biological effects that impact the effect size a study is likely to observe [@Nakagawa2017; @NakagawaSantos2012].
@@
 
-Of course, the overall effect does not provide us a way to interpret its magnitude in the context of how much CORT has been applied in the treatments used in the sample of studies.
+Of course, the overall effect does not provide us with a way to interpret its magnitude in the context of how much CORT has been applied in the treatments used in the sample of studies.
 The most we can say about it, is that the effect is small, moderate or large out of the sample of effect sizes extracted from this set of studies.
@@
 By including these moderators in a meta-regression model, the interpretation of the overall meta-analytic mean, $\beta_{0}$, changes.
-For example, assume we collected the change in CORT dosage relative to a control group (i.e., in uL / g) for our meta-analysis on egg CORT effects on bird reproduction.
-If the untransformed dosage, $x_{j}$, is included in the model then the overall meta-analytic mean estimate, $\beta_{0}$, would be the mean effect of CORT relative to a control treatment, on reproduction when the dosage difference between the treatment and control group is 0 uL /g.
+For example, assume we collected the change in CORT dosage relative to a control group (i.e., in µL / g) for our meta-analysis on egg CORT effects on bird reproduction.
+If the untransformed dosage, $x_{j}$, is included in the model then the overall meta-analytic mean estimate, $\beta_{0}$, would be the mean effect of CORT on reproduction when the dosage difference between the treatment and control group is 0 µL /g.
 Of course, this interpretation does not make much sense.
 
-We can, however, apply some simple transformations to make the overall mean estimate more intuitive to understand with the added benefit that it can help improve the interpretation of non-linear parameters estimated by the model [@Schielzeth2010; @GelmanHill2007].
+We can, however, apply some simple transformations to make the overall mean estimate more intuitive while also improving the interpretation of non-linear parameters and interactions estimated from the model [@Schielzeth2010; @GelmanHill2007].
 One simple transformation would be to centre the variable $x_{j}$, by subtracting each value from the mean to create a new input variable (i.e., $c_{i}=x_{i}-\bar{x}$, where the subscript *i* denotes each individual effect size dosage).
 The new variable, $c_{j}$, is now centered on the mean and can replace $x_{j}$ in the meta-regression model.
-When the model is refit with $c_{j}$ the estimated $\beta_{0}$ can now be more intuitively interpreted as the overall mean effect of CORT on reproduction at an average dosage difference between treatment and control groups.
-Importantly, by centering, we retain the original units (uL / g) of the variable, which can be very useful to allow for a more general interpretation of the effect magnitude (e.g., when the dosage difference is 10 uL /g).
+When the model is refit with $c_{j}$, the estimated $\beta_{0}$ can now be more intuitively interpreted as the overall mean effect of CORT on reproduction at an average dosage difference between treatment and control groups.
+Importantly, by centering, we retain the original units (µL / g) of the variable, which can be very useful to ease the interpretation of the effect magnitude (e.g., when the dosage difference is 10 µL /g).
 Given it is very common to estimate and compare overall meta-analytic means (i.e., $B_{0}$) in meta-analyses this centering can be particularly useful in making these means more interpretable.
-Mean centering can even be extended to include other 'nuisance' variables that might creep into the dataset; the same centering can be done with a second variable, and the overall mean adjusted can be interpreted in the context of this new variable in addition to dosage.
-Of course, if one is not interested in the magnitude of the effect, we could also change our question and simply model mean reproductive output as a function of dosage (often what are referred to as 'arm-based' meta-analytic models).
+Mean centering can even be extended to include other 'nuisance' variables that might creep into the dataset; the same centering can be done with a second variable, and the overall mean adjusted and interpreted in the context of this new variable along with dosage.
+Of course, if one is not interested in the magnitude of the effect, we can simply model mean reproductive output as a function of dosage (often what are referred to as 'arm-based' meta-analytic models).
 Here, one can model the mean for each group (i.e., control and treatment), and account for the known sampling variance associated with each group mean.
-Dosage, or other continuous variables like temperature, can then be modeled (accounting for sampling variance) to understand how mean reproductive output changes.
+Dosage, or other continuous variables like temperature, can then be modeled (accounting for sampling variance) to understand how mean reproductive output varies.
 It is important to recognise that all means need to be comparable and that these models are more complex to fit.
@@
 In other words, linear / main effects can still be interpreted normally in the presence of non-linear / interactions fit in the model [@Schielzeth2010; @GelmanHill2007].
-We provide examples in the online supplementary material (with R code) to show readers how the models we describe above can be fit, and how, meta-analytic means can be adjusted for treatment heterogeneity.
+We provide examples in the online supplementary material (with R code) to show readers how the models we describe above can be fit, and how meta-analytic means can be adjusted for treatment heterogeneity.
 
@@
 
-As we have already emphasised, quantifying effect size heterogeneity (i.e., effect size variance) provides the impetus for exploring hypotheses that are thought to explain why effects might vary within and across studies, while also providing context for interpreting the generality of effects.
+As we have already emphasised, quantifying effect size heterogeneity provides the impetus for exploring why effects might vary within and across studies, while also providing context for interpreting the generality of effects.
 There are a number of measures commonly used to quantify effect size heterogeneity [@Borenstein2019], however, in ecological and evolutionary meta-analysis, heterogeneity is often calculated and reported as $I_{total}^2$ as follows (if using a multilevel meta-analytic model as we describe above):
@@
 Quantifying heterogeneity using $I_{total}^2$ provides a formal way to assess the relative amount of variation that is the result of 'true' biological or methodological differences as opposed to simply chance (i.e., sampling variance) [@NakagawaSantos2012; @Higgins2002].
-In other words, $I_{total}^2$ can be thought of as the percentage of variance between effect sizes after removing the effects of sampling error [@Higgins2002].
-We can only calculate this metric if we have an estimate of the sampling variance for a given effect measure because only then can we quantify the proportion of variation that is the result of sampling variability.
-@Senior2016 have shown that total heterogeneity is often extremely high in ecological and evolutionary meta-analysis (\~91%), suggesting that effect measures vary widely across and within studies.
-Some of the variation is clearly the result of working with different species or strains, different traits and different outcome measures, however, some of this variation also arises because of methodological differences across studies that might be related to the dosages or temperatures used for treatments.
+In other words, $I_{total}^2$ is the percentage of variance between effect sizes after removing the effects of sampling error [@Higgins2002].
+Note that we can only calculate this metric if we have an estimate of the sampling variance for a given effect measure because only then can we quantify the proportion of variation that is the result of sampling variability.
+@Senior2016 have shown that total heterogeneity is often extremely high in ecological and evolutionary meta-analysis (\~91%), suggesting that effect measures vary widely within and across studies.
+Some of the variation is clearly the result of working with different species and/or strains, or measuring different traits and outcome measures.
+However, some of this variation also arises because of methodological differences across studies that might be related to the dosages or temperatures used for treatments.
 
-Formally quantifying and presenting heterogeneity estimates from meta-analytic models can provide a way to understand the major drivers of effect size variation by allowing researchers to produce various $I^2$ estimates which can be compared within and across studies.
+Formally quantifying and presenting heterogeneity estimates from meta-analytic models can provide a way to understand the major drivers of effect size variation by producing various $I^2$ estimates that can be compared within and across studies.
 For example, we could fit the multilevel model described above to understand what proportion of variation is the result of, say, 'study' effects following @NakagawaSantos2012: $I^2_{study} = \frac{\sigma^2_{study}}{\sigma^2_{total}}$ where $\sigma^2_{study}$ is the study specific variance.
 
-Many readers will notice the similarities between $I^2$ and $R^2$ [@Nakgawa2013; @Nakagawa2010; @Nakagawa2017].
-If we want to formally assess how much effect size variation is the result of 'nuisance' variation, such as temperature and dosage differences applied across studies, then we could fit our multilevel meta-regression model, including dosage or temperature (linear, quadratic or even more complex fits), and estimate how much variation is explained by these fixed effects following @Nakgawa2013.
+Some readers may notice the similarities between $I^2$ and $R^2$ [@Nakgawa2013; @Nakagawa2010; @Nakagawa2017].
+If we want to formally assess how much effect size variation is the result of 'nuisance heterogeneity' (e.g.,  temperature and dosage differences applied across studies) then we could fit our multilevel meta-regression model, including dosage or temperature (linear, quadratic or even more complex fits), and estimate how much variation is explained by these fixed effects following @Nakgawa2013.
 
@@
 
-Note that this formula does not include $\sigma^2_{m}$ as sampling error variance is assumed to be known in meta-analysis as explained above.
+Note that this formula does not include $\sigma^2_{m}$ as sampling error variance is assumed to be known in meta-analysis, as explained above.
 When including continuous moderators, such as dosage, temperature, salinity, and even pH, $R^2_{marginal}$ provides a formal means to assess just how much variation in effects is the result of 'nuisance' heterogeneity at the effect size level.
-Other biological moderators of interest could also be included as fixed effects and $R^2_{marginal}$ calculated for each independently or all together.
-Importantly, moderators could be those that explain variation at the effect size level (i.e., dosage, temperature) or they could explain variation at the study or species level (e.g., reproductive mode, endothermy etc).
+Other biological moderators of interest could also be included as fixed effects and $R^2_{marginal}$ can be calculated for each independently, or all together.
+Importantly, moderators could be those that explain variation at the effect size level (i.e., dosage, temperature) or variation at the study or species level (e.g., reproductive mode, endothermy etc).
 $R^2_{marginal}$, or how we like to think of it in this context as $R^2_{'nuisance'}$, maybe a useful measure to help readers understand just how much effect variation can result from the specific treatment application.
@@
 Heterogeneity described using $I^2$ measures can be useful for understanding the relative contributions of different factors to effect size variation, however, prediction intervals might be more appropriate in many cases [@Nakagawa2021c; @Borenstein2019].
-Unlike $I^2$, prediction intervals (PI's) are probably more meaningful in the context of meta-analysis because they explicitly incorporate measures of dispersion around a mean effect size providing information about the likely effect size one can expect if we were to randomly sample a new population.
+Unlike $I^2$, prediction intervals (PI's) are probably more meaningful in the context of meta-analysis because they explicitly incorporate measures of dispersion around a mean effect size.
+They provide information about the likely effect size one can expect if we were to randomly sample a new population.
 For example, assume that we were interested in the overall impact of salinity stress in freshwater fish.
@@
 
-Comparative physiologists are interested in meta-analysing effects across a diversity of species, experimental approaches / designs and environments.
-Importantly, sampling variances for many 'effect measures' commonly used by comparative physiologists (e.g., CTmax, Slopes etc) can be formalised and meta-analytic models applied; even though it is still common to see studies masquerading as meta-analyses despite not fitting meta-analytic models.
+Comparative physiologists are interested in meta-analysing effects across a diversity of species, experimental designs and environments.
+Importantly, sampling variances for many effect sizes commonly used by comparative physiologists (e.g., CTmax, $Q_{10}$ etc) can be formalised and powerful meta-analytic models can be easily applied.
 While an overall meta-analytic mean may be of interest, more often than not, understanding the drivers of effect size heterogeneity will be the primary interest.
-However, obvious drivers of effect size heterogeneity, such as temperature and dosage differences across studies, may not really be of interest.
-Comparative physiologists are likely to want an effect size or analytic approach that allows them to remove these 'nuisances'.
-Here, we provide a set of tools to deal with 'nuisance heterogeneity' by 'reinventing' standard effect sizes or using meta-regression models.
-Of course, 'nuisance heterogeneity' might in of itself be the main interest, in which case standard meta-regression approaches will work sufficiently.
-However, in many cases, comparative physiologists might simply want to focus on bigger, more interesting biological drivers of effect size direction and magnitude.
-Estimating complex meta-regression models with a multitude of fixed effects might result, however, in more challenging model to interpret As such, a combined approach, where some of the known heterogeneity is dealt with by deriving a variant effect size and associated sampling variance, and other biologically interesting moderators are fit in a meta-regression model, might be desired.
+However, factors such as temperature and dosage differences across studies may generate obvious sources of heterogeneity that may not be of prime interest.
+Instead, comparative physiologists might simply want to focus on biological drivers of effect size variability and want an effect size or analytic approach that allows them to remove these ‘nuisances’.
+Here, we provide a set of tools to deal with ‘nuisance heterogeneity’ by ‘reinventing’ standard effect sizes and/or using mean centered nuisance variables in meta-regression models.
+Estimating complex meta-regression models with a multitude of fixed effects might result, however, in more challenging model interpretation.
+As such, a combined approach, where some of the known heterogeneity is dealt with by using an appropriate effect size and associated sampling variance while other biologically interesting moderators are fit in a meta-regression model might be desired.
 Indeed, this may even be a necessity to simplify the model.
-We hope the set of tools we describe provide clarification around different sources of heterogeneity; providing new ways to help comparative physiologists communicate effect measures more richly to guide our understanding and decisions around pressing global challenges.
+We wish the set of tools we describe provide clarification around importance and limitations of heterogeneity.
+We also hope to provide new ways to help comparative physiologists communicate effect measures more richly to guide our understanding and decisions around pressing global challenges.
 
@@
 DWAN, SN, ML and REO were supported by ARC Discovery Projects (DP210101152 to DWAN and DP200100367 to SN, ML and DWAN).
+PP and SB were supported by a UNSW Scientia PhD Scholarship.
 

### 2021-07-21 MS/ms.Rmd
Updated document

@@
 
-```{r, figsurv, fig.wid = 16.833333, fig.height=6.611111,fig.cap="**Summary of meta-analytic practices in comparative physiology.** (A) Different types of effect measures commonly used in meta-analyses and their relative frequency of use.
+```{r, figsurv, fig.wid = 16.833333, fig.height=5,fig.cap="**Summary of meta-analytic practices in comparative physiology.** (A) Different types of effect measures commonly used in meta-analyses and their relative frequency of use.
 (B) How many meta-analyses where ‘nuisance heterogenity’ have the potential to impact effect sizes, and the proportion of studies explicitly dealing with nuisance heterogenity.
@@
   scale_fill_viridis_d() +
-  theme(legend.position = c(0.45, 0.8)) + 
+  theme(legend.position = c(0.45, 0.8),
+        legend.background=element_blank()) + 
   labs(x = "Nuisance Heterogeneity?",

### 2021-07-21 MS/ms.Rmd
Sammy's comments integrated

@@
 
+    # If you have issues with flextable and equatags, make sure you have node.js and use mathjax_install(). See here:https://github.com/ardata-fr/equatags
   pacman::p_load(flextable, tidyverse, equatags, png, magick)  
@@
 Meta-analysis is always concerned with effect heterogeneity; in other words, the factors that drive differences in the direction and magnitude of effects within and across studies [@Nakagawa2017; @Gurevitch2018; @Cooperetal2019; @Borenstein2019].
-The concept of heterogeneity is vitally important because it tells us how general findings are likely to be and how much of the variance we see is the result of real biology or methodological differences (not just sampling variance) [@Nakagawa2017; @Borenstein2019].
-There are a plethora of phenomena driving effect heterogeneity, some of which are interesting and others that are less so.
+The concept of heterogeneity is vitally important because it tells us how general our findings are likely to be and how much of the variance we see is the result of real biology or methodological differences (not just sampling variance) [@Nakagawa2017; @Borenstein2019].
+There are many phenomena driving effect heterogeneity, some of which are interesting and others that are less so.
 
@@
 However, nuisance heterogeneity can come in various other forms such as differences in dosage, or biochemical variables between used in the experiments.
-We can control for these types of heterogeniety by reformalising effect sizes and/or using multilevel metaregression as we describe in our review"}
+We can control for these types of heterogeniety by reformalising effect sizes and/or using multilevel metaregression as we describe in our review."}
 image <- image_read(here::here("figs", "Fig1.png"))
@@
 For example, if we want to understand the impact of a pollutant on reproduction in aquatic organisms, including aquatic mammals and fish would provide answers to this general question, even if their reproductive biology and physiology are different.
-By synthesizing diverse study outcomes, not only does it allow to report on overall effects (if the question is relevant to ask), but it allows us to also understand critical features of the literature, study systems (e.g., different effects of pollutants on fish and mammal reproduction) and approaches that can explain the diversity of effect outcomes observed.
+By synthesizing diverse study outcomes, not only does it allow to report on overall effects (if the question is relevant to ask), but it allows us to also understand critical features of the literature, study systems (e.g., different effects of pollutants on fish and mammal reproduction), and approaches that can explain the diversity of effect outcomes observed.
 Doing so provides a richer set of conclusions that can draw attention to important sources of variability that might have otherwise been overlooked.
@@
 If, however, an overall effect is accompanied by large heterogeneity estimates, then we would shift focus and explore drivers of that heterogeneity.
-For example, given the very different physiology of aquatic mammals and fish, understanding an overall combined effect on reproduction may not be particularly relevant, and indeed may even be misleading.
+For example, given the very different physiology of aquatic mammals and fish, understanding an overall combined effect on reproduction may not be particularly relevant and may even be misleading.
 Therefore, understanding overall effects in each of these groups separately, and assess the extent to which they differ, may be more useful.
@@
 As discussed above, different types of questions and experimental approaches will mix 'apples and oranges' to varying extents, but this heterogeneity (or basket of fruit) is often the main interest to comparative biologists.
-We conducted a literature survey to better understand the different types of effect sizes being used, their susceptibility to known sources of methodological / environmental variability across studies, and how these sources are controlled we conducted a literature survey.
+We conducted a literature survey to better understand the different types of effect sizes being used, their susceptibility to known sources of methodological / environmental variability across studies, and how these sources are controlled, we conducted a literature survey.
 To accomplish this goal, we searched for meta-analyses and comparative analyses that tackled questions using physiological data compiled from animal studies across multiple species.
@@
 While many studies in comparative physiology collect data as part of a comparative analysis, we focus here only on studies collating data from existing literature because this is the major data source in quantitative syntheses.
-Quantitative syntheses interested in phenology, bio-mechanics, sexual size dimorphism (i.e., SSD, except if the study was interested in sexual differences in physiological traits), those focused on validating physiological methodology, or characterising population genetic structure, gene transcription and quantitative genetics were excluded.
+Quantitative syntheses interested in phenology, bio-mechanics, sexual size dimorphism (i.e., SSD, except if the study was interested in sexual differences in physiological traits), those focused on validating physiological methodology, or characterising population genetic structure, gene transcription, and quantitative genetics were excluded.
 There were also meta-analyses that focused on colour evolution and contrast which varied in their goals but were most often not focused on physiological questions.
 As such, these studies were also excluded.
-We restricted our focus to animal studies because most plant synthesis papers were focused on ecological (e.g., quantified changes in abundance and distribution of species) or agricultural questions (e.g., studies on soil microbial function, nitrogen and phosphorus capture, methane output and greenhouse gas emissions).
+We restricted our focus to animal studies because most plant synthesis papers were focused on ecological (e.g., quantified changes in abundance and distribution of species) or agricultural questions (e.g., studies on soil microbial function, nitrogen and phosphorus capture, methane output, and greenhouse gas emissions).
 
@@
 
-Quantitative syntheses in comparative physiology commonly analyse raw summary statistics (`r with(effects, effects[effect == "Means","prop"])*100`% of studies), followed closely by Fishers transformed correlation coefficients (Zr) (`r with(effects, effects[effect == "Zr","prop"])*100`% of studies), standardised mean differences (SMD) and log response ratios (lnRR) (`r with(effects, effects[effect == "SMD","prop"])*100`% and `r with(effects, effects[effect == "lnRR","prop"])*100`%, respectively; Figure \@ref(fig:figsurv)A).
+Quantitative syntheses in comparative physiology commonly analyse raw summary statistics (`r with(effects, effects[effect == "Means","prop"])*100`% of studies), followed closely by Fishers transformed correlation coefficients (Zr) (`r with(effects, effects[effect == "Zr","prop"])*100`% of studies), standardised mean differences (SMD) (`r with(effects, effects[effect == "SMD","prop"])*100`%  of studies), and log response ratios (lnRR) (`r with(effects, effects[effect == "lnRR","prop"])*100`%, of studies) (Figure \@ref(fig:figsurv)A).
 In many cases, studies make use of multiple effect size measures.
-Approximately `r with(hetero, hetero[cont_moderator_variable == "yes","percent"])*100`% of effect sizes used within the study we deemed to be impacted by 'nuisance heterogeneity' in some form or another (Figure \@ref(fig:figsurv)B), but of the studies where this was the case, only `r with(hetero_dealt, hetero_dealt[cont_moderator_variable_modelled == "yes","percent"])*100`% of the studies clearly dealt with it (Figure \@ref(fig:figsurv)B); often through meta-regression modelling.
-Overall, `r with(weighted, weighted[meta_analysis_weighted == "weighted model","percent"])*100`% of studies used a weighted meta-analytic model, however, of the studies self described as 'meta-analyses', `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","percent"])*100`% (N = `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","n"])` of `r with(weighted_meta, sum(weighted_meta[,"n"]))`) did not account for sampling variance.
+Approximately `r with(hetero, hetero[cont_moderator_variable == "yes","percent"])*100`% of effect sizes used within the study we deemed to be impacted by 'nuisance heterogeneity' in some form or another (Figure \@ref(fig:figsurv)B), but of the studies where this was the case, only `r with(hetero_dealt, hetero_dealt[cont_moderator_variable_modelled == "yes","percent"])*100`% of the studies clearly dealt with it (Figure \@ref(fig:figsurv)B), often through meta-regression modelling.
+Overall, `r with(weighted, weighted[meta_analysis_weighted == "weighted model","percent"])*100`% of studies used a weighted meta-analytic model; however, of the studies self described as 'meta-analyses', `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","percent"])*100`% (N = `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","n"])` of `r with(weighted_meta, sum(weighted_meta[,"n"]))`) did not account for sampling variance.
 Many studies used 'Linear Regression' (including linear and generalised linear mixed effects models) as the main type of model fit to the data (Figure \@ref(fig:figsurv)C).
@@
 Instead, if we are interested in how the mean of some physiological trait changes with temperature, we may model the mean itself.
-In the latter scenario, as long as all the means are measured in the same units (e.g., Celsius; or can be converted to the same units) then the mean may provide the desired answer to the original question.
+In the latter scenario, as long as all the means are measured in the same units (e.g., Celsius) or can be converted to the same units, then the mean may provide the desired answer to the original question.
 We provide details on different effect measures and associated sample sizes in Table \@ref(tab:tablea).
@@
            "Standardised Mean Difference, SMD",
-           "Zr (Fisher Transformation of \n correlation Coefficient, r)")
+           "Zr (Fisher Transformation of \n Correlation Coefficient, r)")
            #"Log Odds Ratio",
@@
 As can be seen in Table \@ref(tab:tablea), none of the effect measures control for 'nuisance heterogeneity'.
-For example, the magnitude of lnRR or SMD might depend on just how different the temperatures, dosages, pH or water potential applied in each treatment.
+For example, the magnitude of lnRR or SMD might depend on differences in the temperatures, dosages, pH, or water potential applied to each treatment.
 The same applies for modelling the means.
@@
 We highlight two examples in the box focusing mainly on generality.
-Below, we show how to formalize a traditional effect size, $lnRR$, into a common measure of interest to comparative physiologists, $Q_{10}$, and show how this new effect size can capture “nuisance heterogeneity”.
+Below, we show how we can formalise a traditional effect size, such as $lnRR$, to capture this ‘nuisance variation’ using a common, well understood effect measure of interest to comparative physiologists ($Q_{10}$).
 
@@
 A common experiment in comparative physiology is to manipulate the temperature organisms experience and measure some physiological rate (e.g., metabolic rate).
-Using the effect size measures in Table \@ref(tab:tablea) would result in the effect sizes varying with the temperatures applied within and across across studies contributing to 'comparability' issues.
+Using the effect size measures in Table \@ref(tab:tablea) would result in the effect sizes varying with the temperatures applied within and across studies contributing to 'comparability' issues.
 For example, an effect size for a temperature manipulation of 10°C would be larger than an effect size for a temperature manipulation of 5°C (see Figure \@ref(fig:fig1)).
@@
 Prior to showing how the relevant $Q_{10}$ effect size can be calculated it is useful to understand its similarities to *lnRR*.
-The *lnRR* described by @Hedges1999 and extended by @Lajeunesse2015 and can be calculated as follows [but see also @Senior2020]:
+The *lnRR* described by @Hedges1999 and extended by @Lajeunesse2015 can be calculated as follows [but see also @Senior2020]:
 
@@
 Natural log transformation of this ratio makes the effect size normally distributed which is commonly assumed by meta-analytic models.
-Equation \@ref(eq:slnRR) is the analytical solution for *lnRR*'s sampling variance where, $SD_{1}^2$ and $SD_{2}^2$ is the sample variance in group 1 and 2, respectively and $N_{1}$ and $N_{2}$ is the sample size in group 1 and 2.
+Equation \@ref(eq:slnRR) is the analytical solution for *lnRR*'s sampling variance where $SD_{1}^2$ and $SD_{2}^2$ is the sample variance in group 1 and 2, respectively and $N_{1}$ and $N_{2}$ is the sample size in group 1 and 2.
 
@@
 Equation \@ref(eq:lnq10) is essentially a temperature corrected equivalent of lnRR when the numerator and denominator are measured at different temperatures.
-This allows one to compare the mean of two temperature treatments directly regardless of the temperatures that these groups have been measured.
+This allows one to compare the mean of two temperature treatments directly regardless of the temperatures at which these groups have been measured.
 Here, we will refer to this as the log $Q_{10}$ response ratio, $lnRR_{Q_{10}}$.
@@
 
-Our example using $Q_{10}$, a well-known effect measure in comparative physiology, shows how common effect size's can be re-formalised to account for 'nuisance heterogeneity', in this case temperature.
+Our example using $Q_{10}$, a well-known effect measure in comparative physiology, shows how common effect size's can be re-formalised to account for 'nuisance heterogeneity' (in this case temperature).
 In doing so, we are making assumptions about the nature of temperature effects on an effect size.
@@
 More often than not, meta-analyses in comparative physiology will have complex hierarchical structure.
-For example, multiple effect sizes may be taken from a single study on traits measured on the same individuals, or come from many different species that share an evolutionary history [@Cinar2021; @Noble2017].
-As such, it is far more likely that comparative physiologists will need to apply a multilevel meta-analytic model to control for the various sources of non-independence, and whenever possible, they should [@Cinar2021; @NakagawaSantos2012; @Song2021; @Nakagawa2021; @Noble2017].
+For example, multiple effect sizes may be taken from a single study on traits measured on the same individuals or from many different species that share an evolutionary history [@Cinar2021; @Noble2017].
+As such, it is far more likely that comparative physiologists will need to apply a multilevel meta-analytic model to control for the various sources of non-independence, and, whenever possible, they should [@Cinar2021; @NakagawaSantos2012; @Song2021; @Nakagawa2021; @Noble2017].
 Multilevel models are also extremely useful in describing the various sources contributing to effect size variance (a feature we describe below).
@@
 Phylogenetic effects are assumed to be normally distributed deviates sampled from a distribution with a mean of 0 and variance $\sigma^{2}_{phylogeny}$ [i.e., *N*$(0, \sigma^{2}_{phylogeny}\textbf{A})$], where $\textbf{A}$ is a phylogenetic correlation matrix derived from a phylogenetic tree.
-$sp_{k[i]}$ is an additional species-specific effect for the *k*th species applied to effect size *i* [i.e., these are species-specific effects because of shared ecology and other factors, @Cinar2021], $s_{j[i]}$ is the study-specific effect for the *j*th study applied to effect size *i*, $e_{i}$ is the effect size-specific effect (or within study effect, or residuals) for the *i*th effect size, and $m_{i}$ is the sampling variance effect around the *i*th effect as a result of variation in precision among each effect sizes, $v_{i}$, which is known as the sampling variance for the effect.
+$sp_{k[i]}$ is an additional species-specific effect for the *k*th species applied to effect size *i* [i.e., these are species-specific effects because of shared ecology and other factors, @Cinar2021], $s_{j[i]}$ is the study-specific effect for the *j*th study applied to effect size *i*, $e_{i}$ is the effect size-specific effect (or within study effect, or residuals) for the *i*th effect size, and $m_{i}$ is the sampling variance effect around the *i*th effect as a result of variation in precision among each effect size, $v_{i}$ (which is known as the sampling variance for the effect).
 This model is a 'weighted' multilevel meta-analysis model because the estimation of the overall meta-analytic mean, $\beta_{0}$, is partially weighted by the inverse sampling variance of each effect size.
-Importantly, if we have effect sizes that are derived from the *same* sample of organisms (e.g., because traits are measured on the same sets of individuals) then we need to remove this dependency from the calculation of each $v_{i}$; we can then model the known sampling covariance between effect sizes by modifying $\textbf{I}$ to include off-diagonals that account for this covariance [See Box 1 and @Noble2017].
-The fact that we can obtain an overall estimate of sampling variance (i.e., $\sigma^2_{m}$, see below for how it is defined) is very important because it provides a way for us to understand just how much variation in effects are the result of sampling differences across studies versus other, potentially important sources of variation such as differences in the methods applied, species differences or even real biological effects that impact the effect size a study is likely to observe [@Nakagawa2017; @NakagawaSantos2012].
+Importantly, if we have effect sizes that are derived from the *same* sample of organisms (e.g., because traits are measured on the same sets of individuals), then we need to remove this dependency from the calculation of each $v_{i}$; we can then model the known sampling covariance between effect sizes by modifying $\textbf{I}$ to include off-diagonals that account for this covariance [See Box 1 and @Noble2017].
+The fact that we can obtain an overall estimate of sampling variance (i.e., $\sigma^2_{m}$, see below for how it is defined) is very important because it provides a way for us to understand just how much variation in effects are the result of sampling differences across studies versus other, potentially important sources of variation such as differences in the methods applied, species differences, or even real biological effects that impact the effect size a study is likely to observe [@Nakagawa2017; @NakagawaSantos2012].
 This is formalised in what we call 'heterogeneity analysis' which we describe below.
@@
 Of course, the overall effect does not provide us with a way to interpret its magnitude in the context of how much CORT has been applied in the treatments used in the sample of studies.
-The most we can say about it, is that the effect is small, moderate or large out of the sample of effect sizes extracted from this set of studies.
+The most we can say about it is that the effect is small, moderate or large out of the sample of effect sizes extracted from this set of studies.
 In the next section, we show how to 'correct' the overall effect size so that its interpretation is more meaningful.
@@
 Importantly, by centering, we retain the original units (µL / g) of the variable, which can be very useful to ease the interpretation of the effect magnitude (e.g., when the dosage difference is 10 µL /g).
-Given it is very common to estimate and compare overall meta-analytic means (i.e., $B_{0}$) in meta-analyses this centering can be particularly useful in making these means more interpretable.
+Given it is very common to estimate and compare overall meta-analytic means (i.e., $B_{0}$) in meta-analyses, this centering can be particularly useful in making these means more interpretable.
 Mean centering can even be extended to include other 'nuisance' variables that might creep into the dataset; the same centering can be done with a second variable, and the overall mean adjusted and interpreted in the context of this new variable along with dosage.
 Of course, if one is not interested in the magnitude of the effect, we can simply model mean reproductive output as a function of dosage (often what are referred to as 'arm-based' meta-analytic models).
-Here, one can model the mean for each group (i.e., control and treatment), and account for the known sampling variance associated with each group mean.
+Here, one can model the mean for each group (i.e., control and treatment) and account for the known sampling variance associated with each group mean.
 Dosage, or other continuous variables like temperature, can then be modeled (accounting for sampling variance) to understand how mean reproductive output varies.
@@
 As we have already emphasised, quantifying effect size heterogeneity provides the impetus for exploring why effects might vary within and across studies, while also providing context for interpreting the generality of effects.
-There are a number of measures commonly used to quantify effect size heterogeneity [@Borenstein2019], however, in ecological and evolutionary meta-analysis, heterogeneity is often calculated and reported as $I_{total}^2$ as follows (if using a multilevel meta-analytic model as we describe above):
+There are a number of measures commonly used to quantify effect size heterogeneity [@Borenstein2019]; however, in ecological and evolutionary meta-analysis, heterogeneity is often calculated and reported as $I_{total}^2$ as follows (if using a multilevel meta-analytic model as we describe above):
 
@@
 Other biological moderators of interest could also be included as fixed effects and $R^2_{marginal}$ can be calculated for each independently, or all together.
-Importantly, moderators could be those that explain variation at the effect size level (i.e., dosage, temperature) or variation at the study or species level (e.g., reproductive mode, endothermy etc).
+Importantly, moderators could be those that explain variation at the effect size level (i.e., dosage, temperature) or variation at the study or species level (e.g., reproductive mode, endothermy, etc.).
 $R^2_{marginal}$, or how we like to think of it in this context as $R^2_{'nuisance'}$, maybe a useful measure to help readers understand just how much effect variation can result from the specific treatment application.
-If the heterogeneity is high as a result of, say, dosages differences, then it is clear that the choice of dosage will have a critical impact on the effect of interest.
+If the heterogeneity is high as a result of, say, dosage differences, then it is clear that the choice of dosage will have a critical impact on the effect of interest.
 Comparative physiologists interested in implementing these calculations can do so using our packages `orchaRd` [@Nakagawa2021c] or `metaAidR` (<https://github.com/daniel1noble/metaAidR>).
 
-Heterogeneity described using $I^2$ measures can be useful for understanding the relative contributions of different factors to effect size variation, however, prediction intervals might be more appropriate in many cases [@Nakagawa2021c; @Borenstein2019].
+Heterogeneity described using $I^2$ measures can be useful for understanding the relative contributions of different factors to effect size variation; however, prediction intervals might be more appropriate in many cases [@Nakagawa2021c; @Borenstein2019].
 Unlike $I^2$, prediction intervals (PI's) are probably more meaningful in the context of meta-analysis because they explicitly incorporate measures of dispersion around a mean effect size.
@@
 For example, assume that we were interested in the overall impact of salinity stress in freshwater fish.
-To tackle this question, we collected experimental studies measuring fish swim performance under high salinity treatments (\~15-20ppm Na Cl) compared to freshwater (\~0ppm Na Cl) controls; using SMD to quantify the magnitude of effect salinity had on swim performance.
+To tackle this question, we collected experimental studies measuring fish swim performance under high salinity treatments (\~15-20ppm Na Cl) compared to freshwater (\~0ppm Na Cl) controls, using SMD to quantify the magnitude of effect salinity had on swim performance.
 We conduct a meta-analysis and estimate an overall SMD of 0.50 with a prediction interval of 0.05 to 0.85.
-The PI indicates that effects can vary widely from as low as an SMD of 0.05 to as high as an SMD 0.95, depending on the population.
-In addition, if we were to repeat a study we would expect a new effect to fall within the range of 0.05 and 0.85, 95% of the time [@Borenstein2019; @Nakagawa2021c].
+The PI indicates that effects can vary widely from as low as an SMD of 0.05 to as high as an SMD 0.85, depending on the population.
+In addition, if we were to repeat a similar study, we would expect a new effect to fall within the range of 0.05 and 0.85, 95% of the time [@Borenstein2019; @Nakagawa2021c].
 This is a very intuitive interpretation of how variable effects are, yet PIs are often not reported in meta-analyses [@Nakagawa2021c], and we encourage more meta-analysts to report these.
@@
 
-Comparative physiologists are interested in meta-analysing effects across a diversity of species, experimental designs and environments.
+Comparative physiologists are interested in meta-analysing effects across a diversity of species, experimental designs, and environments.
 Importantly, sampling variances for many effect sizes commonly used by comparative physiologists (e.g., CTmax, $Q_{10}$ etc) can be formalised and powerful meta-analytic models can be easily applied.
@@
 We would like to thank the Editorial board (Craig Franklin, Michaela Handel and Charlotte Rutledge) for inviting us to contribute to this special issue along with feedback on previous drafts.
-We would also like to than Megan Head for comments on a previous draft.
+We would also like to thank Megan Head for comments on a previous draft.
 DWAN, SN, ML and REO were supported by ARC Discovery Projects (DP210101152 to DWAN and DP200100367 to SN, ML and DWAN).

### 2021-07-21 MS/box.Rmd
Added Patrices comments

@@
 
-Here we show how to obtain sampling variance for a slope (or a 'rate of change') when you have measurements of a physiological trait at two points along an environmental gradient (e.g.
+Here, we show how to obtain sampling variance for a slope (or a 'rate of change') when you have measurements of a physiological trait at two points along an environmental gradient (e.g.
 temperature, salinity, acidity).
-We then go on to derive sampling variance for the difference between two slopes, and also how SMD (standardized mean difference) can be corrected to account for differences in both units (e.g.
+We then derive sampling variance for the difference between two slopes, and demonstrate how SMD (standardized mean difference) can be corrected to account for differences in both units (e.g.
 cm or mg) and points on an environmental gradient (e.g.
-temperature of 24 and 30 Celsius).
+temperature of 24 and 30 \&degC).
 Finally, we introduce a useful approximation technique known as 'the delta method'.
-The sampling variances associated with these 'new' effect sizes below will allow one to take advantage of powerful meta-analytic models.
+The sampling variances associated with these 'new' effect sizes below will allow comparative physiologists to take advantage of powerful meta-analytic models.
 
@@
 
-Let's start with a real example that comparative physiologists can easily associate with, namely the temperature acclimation slope or as we call it the (temperature) acclimation response ratio (ARR).
+Let's start with a real example that comparative physiologists can easily relate with, the slope of responses to temperature acclimation or,or as we call it, the acclimation response ratio (ARR).
 ARR can be defined as a slope for acclimated physiological responses at two different temperature points, defined as:
@@
 
-where *T* stands for temperature in degrees Celsius and $T_{2} > T_{1}$, and $M_{1}$ and $M_{2}$ are the average physiological responses (estimated means) at temperature points $T_{1}$ and $T_{2}$.
+where *T* stands for temperature in degrees Celsius and $T_{2} > T_{1}$, and $M_{1}$ and $M_{2}$ are the average physiological responses (e.g., mean CTmax) at temperature points $T_{1}$ and $T_{2}$.
 
-To obtain the sampling variance for this equation (slope), we need to know several basic properties of variance.
-Let's assume $M_{1}$ is a random variable, which means that this variable has a mean and standard deviation (variance; this standard deviation is not the 'sample' but the 'sampling' standard deviation, which is often referred to as standard error).
+To obtain the sampling variance for this equation (slope), we first need to describe some basic properties of variance.
+Let's assume $M_{1}$ is a random variable, which means that this variable has a mean and standard deviation [note that this standard deviation is not the 'sample' but the 'sampling' standard deviation, which is often referred to as standard error - see Figure 1 in @Nakagawa2021b].
 Multiplying a constant ($a$) will change the variance by the square of that constant ($a^2$) while adding or subtracting the constant ($b$) does not change the variance of $M_{1}$.
@@
 
-Importantly, when $M_{1}$ and $M_{2}$ are independent of each other the covariance is 0.
-More concretely, if measurements are taken on two different groups of animals at two different temperatures ($T_1$ and $T_2$), then the co-variances between these two sets of measurements are 0.
+Importantly, when $M_{1}$ and $M_{2}$ are independent to each other their covariance is 0.
+In other words, if measurements are taken on two different groups of animals at two different temperatures ($T_1$ and $T_2$), then the covariances between these two sets of measurements are 0.
 
@@
 where $SD_{1}$ and $SD_{2}$ and $N_{1}$ and $N_{2}$ are standard deviations and sampling sizes at temperature $T_{1}$ and $T_{2}$.
-Readers may still find it difficult to see how we got this equation.
+Readers may find it difficult to see how we obtained this equation.
 Let us explain further.
-The (sampling) standard error for $X_{1}$ is $SE_{1} = SD_{1} / \sqrt{N_{1}}$ -- many readers will probably know this as the formula for obtaining *SE* ('sampling' standard deviation) from *SD* ('sample' standard deviation; see Figure 1 in @Nakagawa2021b).
-Given this, the sampling variance for $X_{1}$ is $SD^2_{1} / N_{1}$, which you see as an element of the sampling variance of ARR along with the sampling variance for $X_{2}$, which is $X_{2}$ is $SD^2_{2} / N_{2}$; the term $(1/(T_{2} - T_{1}))^2$ comes from recognizing $1/(T_{2} - T_{1})$ as a constant.
+The (sampling) standard error for $X_{1}$ is $SE_{1} = SD_{1} / \sqrt{N_{1}}$.
+Given this, the sampling variance for $X_{1}$ is $SD^2_{1} / N_{1}$, and the sampling variance for $X_{2}$ is $SD^2_{2} / N_{2}$.
+You can see those elements of the sampling variance of ARR in the formula above.
+The term $(1/(T_{2} - T_{1}))^2$ comes from recognizing $1/(T_{2} - T_{1})$ as a constant.
 
-Now, it is not uncommon that we measure the same group of animals (or plants) at two temperatures.
-If we do, however, then we need to add the co-variance between $M_{1}$ and $M_{2}$ ($\text{Cov}(M_{1},M_{2})$); note that as above, the co-variance equals the corresponding correlation multiplied by the square-root of two (sampling) variances.
-Therefore, the sampling variance can be now written as:
+In ecological and evolutionary studies, it is not uncommon that we measure the same group of organisms at two temperatures.
+If we do, however, then we need to add the covariance between $M_{1}$ and $M_{2}$ ($\text{Cov}(M_{1},M_{2})$) in the equation.
+Note that, as above, the covariance equals the correlation multiplied by the square-root of two (sampling) variances.
+Therefore, the sampling variance of ARR can be now written as:
 
@@
 
-By assuming the number of animals (*N*) are the same at the two temperatures, we can slightly simplify this formula:
+By assuming the number of organisms (*N*) are the same at the two temperatures, we can slightly simplify this formula:
 
@@
 
-where *r* is the correlation between a set of measurement $M_1$ and $M_2$ form the same individuals at two point $T_1$ and $T_2$.
-As you may notice, we need raw data to calculate *r*.
-So, in reality, we often need to assume a certain value of *r*.
+where *r* is the correlation between a set of measurements $M_1$ and $M_2$ from the same individuals at two points $T_1$ and $T_2$.
+As you may notice, we need the raw data to calculate *r*.
+Therefore, in reality, we often need to assume a certain value of *r*.
 When we do not have an estimate of *r* we can reasonably assume it to be 0.5 [@Noble2017].
@@
 
-Using the basic properties of variance and the results from the above, the sample variance for ARRD can be derived, when measurements at two temperature points are independent, as:
+Using the properties of variance and the equations from above, the sampling variance for ARRD can be derived, when measurements at two temperature points are independent, as:
 
@@
 
-where subscripts *f* and *m* stands for 'females' and 'males'.
+where subscripts *f* and *m* stand for 'females' and 'males'.
 
@@
 Here we have derived sampling variances for 'temperature' ARR and ARRD for both independent and dependent cases.
-But these formulas can also be applied to changes in other factors (e.g., salinity, pH, oxygen).
-Furthermore, the constant components of these formulas can be flexibly adjusted.
+These formulas can also be applied to changes in other factors (e.g., salinity, pH, oxygen) by changing the temperature constant.
 For example, it may be possible that males and females were measured in slightly different temperatures; say females at $T_3$ and $T_4$ ($T_4 > T_3$) and male at $T_5$ and $T_6$ ($T_6 > T_5$) like below:
@@
 
-Also, note that the difference between slopes does not need to be that of males and females. This formula can be used to compare any two groups or situations.
+Also, note that the difference between slopes does not need to be that of males and females. This formula can be used to compare any two treatments or biological groups.
 
@@
 
-ARR assumes that the units for the mean difference across studies is consistent.
-This will often not be the case for many meta-analyses that hope to synthesise a wide array of trait types that vary in their units (e.g., ul/g, grams, seconds, minutes).
-Fortunately, $lnRR$ and SMD (Table 1) already control for unitary differences.
-As such, we can apply some of the same logic we discuss above to SMD to correct for both temperature and unitary differences.
+Calculating ARR assumes that the units for the mean difference across studies is consistent.
+Frequently, this will not be the case for meta-analyses that hope to synthesise a wide array of traits that vary in their units (e.g., ul/g, grams, seconds, minutes).
+Fortunately, $lnRR$ and SMD (Table 1) already controls for unitary differences.
+As such, we can apply similar logic that we discuss above so that SMD corrects for both temperature and unitary differences.
 Table 1 provides the formula for SMD, it's pooled standard deviation, and sampling variance.
-We won't re-iterate these formulas again.
-Just like with ARR we can apply our temperature correction to the SMD formula as follows:
+Just like with ARR, we can apply our temperature correction to the SMD formula as follows:
 
@@
 
-It is often limited when we can use the basic properties of variance to derive sampling variance.
+Deriving sampling variances using common properties of variance has its limits.
 Therefore, we introduce a practical and widely applicable method to obtain approximate variance when the basic properties of variance cannot be applied.
@@
 
-where $f(M_1)$ represents the function of the random variable $X_1$, and importantly, $f'(M_1)$ is the first derivative of $f(M_1)$.
-Let's demonstrate with a concrete example by re-deriving the sampling variance for $\ln{RR}$, which is:
+where $f(M_1)$ represents the function of the random variable $M_1$, and importantly, $f'(M_1)$ is the first derivative of $f(M_1)$.
+Let's demonstrate this with a concrete example by re-deriving the sampling variance for $\ln{RR}$ defined as:
 
@@
 \sigma^2_{ln{RR}} \approx  \left ( \frac{SD_{1}^2}{N_{1}}\right ) * \left(\frac{1}{M_{1}} \right)^2 + \left ( \frac{SD_{2}^2}{N_{2}}\right ) * \left(\frac{1}{M_{2}} \right)^2 =   \left ( \frac{SD_{1}^2}{N_{1}M_{1}^2}\right ) + \left ( \frac{SD_{2}^2}{N_{2}M_{2}^2}\right )
-$$ Note here again that the first term, $\frac{SD_{1}^2}{N_{1}}$ is the sampling variance for group 1, and we simply multiply this term by the square of the first derivative of $M_{1}$ as the Delta method tells us.
-Readers may notice that this is equivalent to the sampling variance for $ln_{RR}$ (Table 1).
+$$
+
+Note that the first term, $\frac{SD_{1}^2}{N_{1}}$ is once again the sampling variance for group 1, and we simply multiply this term by the square of the first derivative of $M_{1}$ as described by the Delta method.
+Readers may notice that this formula is now equivalent to the sampling variance for $ln_{RR}$ (Table 1).
 We can extend this sampling variance to include dependency between the groups as:
@@
 - 2r\sqrt{\frac{SD_{1}^2}{N_{1}M_{1}^2}}\sqrt{\frac{SD_{2}^2}{N_{2}M_{2}^2}},
-$$ where $r$ is 0 when two sets of measurements are independent (therefore, the term including $r$ disappears), while $r$ is the correlation between $\ln{M_1}$ and $\ln{M_2}$.
-As discussed, we usually do not have an estimate for this correlation coefficient.
+$$
 
-Finally, we note that by using the basic properties of variance and the delta method, one can derive sampling variance for most of cases.
-Indeed, these were enough for us to derive sampling variance for 'new' effect sizes (e.g.
-$lnQ_{10}$; see the main text) and as in @Nakagawa2015 and @Senior2020.
-Also, see @Nakagawa2017ab for more on the delta method (they explain the 'first and second-order' delta method)
+where r is the correlation between $\ln{M_1}$ and $\ln{M_2}$ when organisms are measured multiple times (with r often assumed to be 0.5), while r is 0 when two sets of measurements are independent.
+
+Finally, we note that, by using the basic properties of variance and the delta method, one can derive sampling variance for most effect size measures.
+For instances, these methods allowed us to derive sampling variance for 'new' effect sizes (e.g.
+$lnQ_{10}$; see the main text) and were used in @Nakagawa2015 and @Senior2020.
+We also refer the reader to @Nakagawa2017ab for additional details on the Delta method.
 

### 2021-07-21 MS/box.Rmd
Samm'ys comments in Box

@@
 
-Now let us assume that we want to know the difference between two different ARR values: female ARR, $\text{ARR}_{f}$ and Male ARR, $\text{ARR}_{m}$. Such a difference (ARRD) can be written as:
+Now let us assume that we want to know the difference between two different ARR values: female ARR, $\text{ARR}_{f}$ and male ARR, $\text{ARR}_{m}$. Such a difference (ARRD) can be written as:
 
@@
 As such, we can apply similar logic that we discuss above so that SMD corrects for both temperature and unitary differences.
-Table 1 provides the formula for SMD, it's pooled standard deviation, and sampling variance.
+Table 1 provides the formula for SMD, its pooled standard deviation, and sampling variance.
 Just like with ARR, we can apply our temperature correction to the SMD formula as follows:
@@
 
-Here, we can see that the difference between $M_1$ and $M_2$ is standardised by the pooled SD, essentially correcting for unitary differences.
+Here we can see that the difference between $M_1$ and $M_2$ is standardised by the pooled SD, essentially correcting for unitary differences.
 Additionally, dividing SMD by the temperature difference results in further correcting the effect size by temperature.
@@
 Therefore, we introduce a practical and widely applicable method to obtain approximate variance when the basic properties of variance cannot be applied.
-This is where the delta method comes in.
+This is where the Delta method comes in.
 The general form of this method can be written as:
@@
 
-Finally, we note that, by using the basic properties of variance and the delta method, one can derive sampling variance for most effect size measures.
-For instances, these methods allowed us to derive sampling variance for 'new' effect sizes (e.g.
+Finally, we note that, by using the basic properties of variance and the Delta method, one can derive sampling variance for most effect size measures.
+For instances, these methods allowed us to derive sampling variance for our 'new' effect sizes (e.g.
 $lnQ_{10}$; see the main text) and were used in @Nakagawa2015 and @Senior2020.

### 2021-07-21 R/survey_data_results.Rmd
Survey results and vis update

@@
 
-pacman::p_load(dplyr,ggplot2,here, pander, janitor, magrittr)
+pacman::p_load(dplyr,ggplot2,here, pander, janitor, magrittr,ggalluvial,ggpubr)
 
@@
 #loadfonts()
-text.font <- "Arial"
+text.font <- "Helvetica"
+line.width <- 0.6
 
@@
             axis.title.y = element_text(margin = margin(0,10,0,0)),
-            axis.line = element_line(colour = text.colour, size = 0.5),
-            axis.ticks = element_line(colour = text.colour, size = 0.5),
-            plot.title = element_text(hjust = 0.5),
+            axis.line = element_line(colour = text.colour, size = line.width),,
+            axis.ticks = element_line(colour = text.colour, size = line.width),
+            plot.title = element_text(hjust = line.width),
             legend.background = element_rect(fill = background.colour),
@@
             plot.margin = margin(6,6,6,6))
+
+tm2 <- theme(panel.background = element_rect(fill = background.colour),
+            plot.background = element_rect(fill = background.colour),
+            panel.grid = element_blank(),
+            text =  element_text(family = text.font, colour = text.colour, size = 15),
+            axis.text = element_text(colour = text.colour),
+            axis.text.y = element_text(angle = 90, vjust = 0.5, hjust = 0.5),
+            axis.title.x = element_text(margin = margin(10,0,0,0)),
+            axis.title.y = element_text(margin = margin(0,10,0,0)),
+            axis.line = element_line(colour = text.colour, size = line.width),,
+            axis.ticks = element_line(colour = text.colour, size = line.width),
+            plot.title = element_text(hjust = line.width),
+            legend.background = element_rect(fill = background.colour),
+            legend.key = element_rect(fill = background.colour),
+            plot.margin = margin(15,15,15,15))
 ```
@@
   ggplot() + tm +
-  geom_col(aes(x = effect, y = prop), width = 0.5, fill = "black", colour = text.colour, size = 0.5) +
+  geom_col(aes(x = effect, y = prop), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
   scale_y_continuous(expand=c(0,0),limits = c(0,0.4)) +
@@
 
+### Synthetic plot
+
+```{r}
+plot1 <- dat %>% 
+  ggplot() + tm2 + theme(legend.position = "top") +
+  geom_bar(aes(x = comparative_physiology_main_focus,
+               fill = cont_moderator_variable,
+               y = ..count../sum(..count..)), width = 0.5,
+           colour = NA, size = 0.5) +
+  scale_y_continuous(expand=c(0,0)) +
+  scale_fill_brewer(palette = "Set2") +
+  labs(x = "Main focus on comparative physiology",
+       y = "Number of papers",
+       fill = "Continuous predictor present")
+plot1
+
+plot2 <- dat %>% 
+  ggplot() + tm2 + theme(legend.position = "top") +
+  geom_bar(aes(x = pub_year,
+               fill = meta_analysis_self_described,
+               y = ..count../sum(..count..)), width = 0.5,
+           colour = NA, size = 0.5) +
+  scale_y_continuous(expand=c(0,0)) +
+  scale_fill_brewer(palette = "Set2") +
+  labs(x = "Year of publication",
+       y = "Number of papers",
+       fill = "Meta-analysis")
+plot2
+
+plot3 <- dat %>%
+  ggplot(mapping = aes(x = comparative_physiology_main_focus,
+               y = meta_analysis_self_described)) + tm2 +
+  theme(panel.border = element_rect(size = 0.5, fill = NA),
+        panel.grid.major = element_line(colour = "grey92"),
+        axis.text.y = element_text(angle = 90)) +
+  geom_count(mapping = aes(size = ..n.., colour = "A")) +
+  scale_size_continuous(range = c(20,40), guide = F) +
+  scale_colour_brewer(palette = "Set2", guide = F) +
+  # scale_y_continuous(expand=c(0,0)) +
+  # scale_fill_viridis_d() +
+  labs(x = "Main focus on comparative physiology",
+       y = "Number of papers")
+plot3
+
+plot4 <- dat %>%
+  ggplot(aes(axis1 = meta_analysis_self_described,
+             axis2 = comparative_physiology_main_focus,
+             axis3 = cont_moderator_variable)) +
+  ggalluvial::geom_alluvium(aes(fill = comparative_physiology_main_focus), width = 1/4, alpha = 0.8) +
+  tm2 + theme(axis.line = element_blank(), axis.ticks = element_blank()) +
+  theme(legend.position = "none", panel.grid = element_blank(), axis.text.y = element_blank()) +
+  scale_fill_brewer(palette = "Set2") +
+  ggalluvial::geom_stratum(fill = 'white', colour = 'black', width = 1/4) +
+  geom_text(stat = 'stratum',
+            aes(label = after_stat(stratum)),
+            # label = c('weighted', 'unweighted', 'unclear'),
+            colour = 'black') +
+  scale_x_discrete(expand = c(.1, .1), limits = c("Meta-analysis", "Comparative physiol.", "Cont. moderator"))
+plot4
+
+panels <- ggarrange(ggarrange(plot1, plot2, nrow = 1),
+                    ggarrange(plot3, plot4, nrow = 1, widths = c(1,2)),
+                    nrow = 2, ncol = 1)
+ggsave(panels, filename = "multipanel.pdf", device = "pdf")
+
+```
+
 ## R Session Information   

### 2021-07-22 R/survey_data_results.Rmd
tidying formatting of survey results

@@
 
+### Publication years {.tabset .tabset-fade .tabset-pills}
+
+```{r}
+dat %>% dplyr::group_by(pub_year) %>% dplyr::tally() %>% 
+  ggplot() + tm +
+  geom_col(aes(x = pub_year, y = n), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
+  scale_y_continuous(expand=c(0,0),breaks=seq(1,13,2)) +
+  scale_x_continuous(breaks = min(dat$pub_year):max(dat$pub_year)) +
+  labs(x = "publication year",
+       y = "number of papers")
+```
+
 ### Meta-analysis {.tabset .tabset-fade .tabset-pills}
@@
 
-Answer to the question ""Is the study's main focus on comparative physiology?"
+Answer to the question "Is the study's main focus on comparative physiology?"
 
@@
 - no =  does have physiological traits, but is interested in broader questions involving many different traits
-
-```{r}
-dat %>% dplyr::group_by(comparative_physiology_main_focus) %>% dplyr::tally() %>% 
-  ggplot() + tm +
-  geom_col(aes(x = comparative_physiology_main_focus, y = n), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
-  scale_y_continuous(expand=c(0,0)) +
-  labs(x = "main focus on comparative physiology",
-       y = "number of papers") 
-```
-
-How do the two categorisations (meta-analysis and comparative focus) combine?
 
@@
 
-### Effect Sizes Used {.tabset .tabset-fade .tabset-pills}
+## Meta-analytic models {.tabset}
+
+Note that single papers can report more than one approach (e.g., use different effect sizes and different models).
+
+### Effect sizes used {.tabset .tabset-fade .tabset-pills}
 
@@
                  Slope = dplyr::if_else(grepl("slope", effect_size_type), n, 0)) %>% 
-  colSums(.) %>% data.frame(effect = names(.), n = .) %>% mutate(prop = n / sum(n)) %>% arrange(effect) %>% 
+  colSums(.) %>% data.frame(effect = names(.), n = .) %>% mutate(prop = n / sum(n)) %>% arrange(prop) %>% mutate(effect=factor(effect,levels=unique(effect))) %>% 
   ggplot() + tm + theme(axis.title.y = element_blank(),
-                        axis.text.y = element_text(size=8)) +
+                        axis.text.y = element_text(size=10)) +
   geom_col(aes(x = effect, y = n), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
@@
 
-### Types of models used {.tabset .tabset-fade .tabset-pills}
-
-What models are used. Note that you need to take this approach because some papers use many different models.
+### Statistical models used {.tabset .tabset-fade .tabset-pills}
 
@@
                  `Random Effects Model` = dplyr::if_else(grepl("random-effects meta-analysis", stat_model_type), n, 0)) %>% 
-  colSums(.) %>% data.frame(effect = names(.), n = .) %>% mutate(prop = (n / sum(n))) %>% arrange(effect)
+  colSums(.) %>% data.frame(effect = names(.), n = .) %>% mutate(prop = (n / sum(n))) %>% arrange(prop) %>% mutate(effect=factor(effect,levels=unique(effect)))
 rownames(summary) <- NULL
@@
 summary %>% 
-  ggplot() + tm +
+  ggplot() + tm + theme(axis.title.y = element_blank(),
+                        axis.text.y = element_text(size=10)) +
   geom_col(aes(x = effect, y = prop), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
   scale_y_continuous(expand=c(0,0),limits = c(0,0.4)) +
-  labs(x = "Analytical Approach",
+  labs(title = "Analytical Approach",
        y = "Frequency") +
@@
 dat %>%  janitor::tabyl(meta_analysis_weighted) %>% 
-  ggplot() + tm +
+  ggplot() + tm +  theme(axis.title.y = element_blank(),
+                        axis.text.y = element_text(size=10)) +
   geom_col(aes(x = meta_analysis_weighted,  y = percent), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
   scale_y_continuous(expand=c(0,0), limits = c(0,1)) +
-  labs(x = "Weighted Model?",
-       y = "Frequency") 
+  labs(y = "Frequency") +
+  coord_flip()
 ```
@@
 
+## Heterogeneity {.tabset}
+
 ### Effect size impacted by 'nuisance heterogeneity'? {.tabset .tabset-fade .tabset-pills}
 
-Could effect size be impacted by an additional continous predictor (e.g., temperature in thermal limit studies, dosage in hormone manipulation studies)?
+Could effect size be impacted by an additional continuous predictor (e.g., temperature in thermal limit studies, dosage in hormone manipulation studies)?
 
-```{r}
-dat %>%  janitor::tabyl(cont_moderator_variable) %>% 
-  ggplot() + tm +
-  geom_col(aes(x = cont_moderator_variable, y = percent), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
-  scale_y_continuous(expand=c(0,0), limits = c(0,1)) +
-  labs(x = "Nuisance Heterogenity?",
-       y = "Frequency") 
-```
-
-### Dealt with nuisance in model? {.tabset .tabset-fade .tabset-pills}
-
-Of the studies that said 'yes' how many actually modelled it or accounted for it?
-
-```{r}
-dat %>%  filter(!cont_moderator_variable_modelled=="") %>% janitor::tabyl(cont_moderator_variable_modelled) %>% 
-  ggplot() + tm +
-  geom_col(aes(x = cont_moderator_variable_modelled, y = percent), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
-  scale_y_continuous(expand=c(0,0), limits = c(0,1)) +
-  labs(x = "Nuisance Heterogenity Modelled?",
-       y = "Frequency") 
-```
+If "yes", does the study investigate any continuous environmental or methodological factors as moderators?
 
@@
   ggplot() + tm +
-  geom_bar(aes(x = cont_moderator_variable,
+  geom_bar(aes(x = factor(cont_moderator_variable,levels=c("yes","no","unclear")),
                fill = cont_moderator_variable_modelled,
@@
 
-Of the studies that are weighted how many actually reported measures of heterogeinity?
+Of the studies that are weighted how many actually reported measures of heterogeneity?
 
@@
 dat %>%  filter(!heterogeneity_reported=="N/A (e.g.
-they conducted unweighted meta-analysis)") %>% mutate(heterogeneity_reported = if_else(heterogeneity_reported == "unclear/other (add comment)", "other", heterogeneity_reported)) %>% janitor::tabyl(heterogeneity_reported) %>%
+they conducted unweighted meta-analysis)") %>% mutate(heterogeneity_reported = if_else(heterogeneity_reported == "unclear/other (add comment)", "other", heterogeneity_reported)) %>% janitor::tabyl(heterogeneity_reported) %>% dplyr::arrange(-n) %>%
   ggplot() + tm +
-  geom_col(aes(x = heterogeneity_reported, y = percent), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
+  geom_col(aes(x = factor(heterogeneity_reported,levels=heterogeneity_reported), y = percent), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
   scale_y_continuous(expand=c(0,0), limits = c(0,1)) +
@@
 
-### Publication years {.tabset .tabset-fade .tabset-pills}
-
-```{r}
-dat %>% dplyr::group_by(pub_year) %>% dplyr::tally() %>% 
-  ggplot() + tm +
-  geom_col(aes(x = pub_year, y = n), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
-  scale_y_continuous(expand=c(0,0),breaks=seq(1,13,2)) +
-  scale_x_continuous(breaks = min(dat$pub_year):max(dat$pub_year)) +
-  labs(x = "publication year",
-       y = "number of papers")
-```
+## Non-independence and publication bias {.tabset}
 
@@
 ```{r}
-dat %>%  janitor::tabyl(nonindependence_mentioned) %>% 
-  ggplot() + tm +
-  geom_col(aes(x = nonindependence_mentioned, y = percent), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
+dat %>%  janitor::tabyl(nonindependence_mentioned) %>% dplyr::arrange(n) %>% 
+  ggplot() + tm + theme(axis.title.y=element_blank(),
+                        axis.text.y = element_text(size=10)) +
+  geom_col(aes(x = factor(nonindependence_mentioned,levels=nonindependence_mentioned), y = percent), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
   scale_y_continuous(expand=c(0,0), limits = c(0,1)) +
   scale_x_discrete(labels = c('n-i dealt with w/o modelling', 'n-i modelled', 'unclear/other/not mentioned')) +
-  labs(x = "Non-independence handling",
-       y = "Frequency") 
+  labs(title = "Non-independence handling",
+       y = "Frequency") +
+  coord_flip()
 ```
@@
                  None = dplyr::if_else(grepl("no", pub_bias_type), n, 0)) %>% 
-  colSums(.) %>% data.frame(effect = names(.), n = .) %>% mutate(prop = (n / sum(n)*100)) %>% arrange(effect) %>% 
+  colSums(.) %>% data.frame(effect = names(.), n = .) %>% mutate(prop = (n / sum(n)*100)) %>% arrange(n) %>% mutate(effect = factor(effect,levels=unique(effect))) %>% 
   ggplot() + tm + theme(axis.title.y = element_blank(),
-                        axis.text.y = element_text(size=8)) +
+                        axis.text.y = element_text(size=10)) +
   geom_col(aes(x = effect, y = n), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
   scale_y_continuous(expand=c(0,0),breaks=seq(1,30,2)) +
-  scale_x_discrete(limits = c("None", "GraphicalTest", "RegressionTest", "TrimAndFill",
-                              "TimeLag", "OtherUnclear")) +
   labs(x = "Effect Size",
@@
 
-### Synthetic plot
+## Other plots {.tabset}
 

### 2021-07-22 MS/ms.Rmd
Fixed Losia's comments

@@
 
-$^{1}$ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2600
+$^{1}$ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2600, Australia
 
-$^{2}$ Ecology & Evolution Research Centre, School of Biological, Earth and Environmental Sciences, University of New South Wales, Sydney, NSW
+$^{2}$ Ecology & Evolution Research Centre, School of Biological, Earth and Environmental Sciences, University of New South Wales, Sydney, NSW 2052, Australia
 
@@
 Despite this ambition, research designs in the field of comparative physiology can appear, at the outset, as being vastly different to each other because of 'nuisance heterogeneity' (e.g., different temperatures or treatment dosages used across studies).
-Such differences in treatments across studies has led many to believe that meta-analysis is an exercise in comparing "apples with oranges".
+Methodological differences across studies has led many to believe that meta-analysis is an exercise in comparing "apples with oranges".
 Here, we dispel this myth by showing how standardised effects sizes can be used in conjunction with multilevel meta-regression models to both account for the factors driving differences across studies and make them more comparable.
-We formalise effect size measures (e.g., $Q_{10}$) that provide comparative physiologists with a means to remove 'nuisance heterogeneity' without the need to resort to more complex statistical models that may be harder to interpret.
-We also describe more general approaches that can be applied to a variety of different contexts to derive 'new' effects sizes and sampling variances opening up new possibilities.
+We formalise effect size measures (e.g., $Q_{10}$) that provide comparative physiologists with a means to remove nuisance heterogeneity without the need to resort to more complex statistical models that may be harder to interpret.
+We also describe more general approaches that can be applied to a variety of different contexts to derive new effects sizes and sampling variances opening up new possibilities.
 By using effect sizes that account for components of effect heterogeneity, in combination with existing meta-analytic models, comparative physiologists can explore exciting new questions and make results from large-scale data sets more accessible, comparable and widely interpretable.
@@
 
-Meta-analysis has emerged as the 'gold-standard' across various disciplines for quantitative synthesis and is becoming increasingly more prominent in the field of comparative physiology  [@Gurevitch2018; @Nakagawa2017; @Glass2015].
-A meta-analysis provides quantitatively informed answers to research questions by synthesising research results across studies and identifying sources of variation across studies [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Arnqvist1995; @Koricheva2013; @Borenstein2019].
-Ideally, meta-analyses are part of a systematic review and carefully report upon this entire process to ensure the review and data collation are transparent and reproducible [i.e., see the Preferred Reporting Items for Systematic Reviews and Meta-Analyses in Ecology and Evolution (PRISMA-EcoEvo) protocol, @ODea2021].
-Aside from providing an up-to-date overview of a research field there are three major goals of meta-analysis: 1) to provide an overall mean estimate of a treatment effect or relationship, 2) to quantify effect size variance and understand key drivers explaining differences in effects across studies and 3) attempt to identify gaps and publication biases [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Koricheva2013; @Borenstein2019].
+Meta-analysis has emerged as the 'gold-standard' across various disciplines for quantitative synthesis and is increasingly prominent in the field of comparative physiology  [@Gurevitch2018; @Nakagawa2017; @Glass2015].
+Meta-analyses answer research questions by synthesising research results and identifying sources of variation across studies [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Arnqvist1995; @Koricheva2013; @Borenstein2019].
+Ideally, meta-analyses are part of a systematic review and methods are carefully reported upon to ensure the review and data collation are transparent and reproducible [i.e., see the Preferred Reporting Items for Systematic Reviews and Meta-Analyses in Ecology and Evolutionary Biology (PRISMA-EcoEvo) checklist, @ODea2021].
+
+A meta-analysis can have three goals: 1) to provide an overall mean estimate of a treatment effect or relationship, 2) to quantify effect size variance and understand key drivers explaining differences in effects across studies and 3) attempt to identify research gaps and publication biases [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Koricheva2013; @Borenstein2019].
 Meta-analysing independent studies provides greater statistical power and precision than what any individual study on its own would be able to provide - particularly given that most empirical studies are already under-powered in many areas of biology [@Forstmeier2017; @Jennions2003; @Button2013].
@@
 
-Despite its widespread adoption and well-established methodological procedures, meta-analysis is often criticised for mixing 'apples and oranges' -- in other words, mixing effects from studies that lack comparability [@Gurevitch2018; @Arnqvist1995; @Gallo1979; @Carpenter2020; @Stewart2010; @Glass2015].
-Lack of comparability could result from studies differing in experimental design, species, measurement variables and sampling units, which can impact the generalisability of meta-analytic results [@Arnqvist1995; @Stewart2010].
+Despite its widespread adoption and well-established methodological procedures, meta-analysis is often criticised for mixing 'apples and oranges' -- in other words, mixing effects from studies that are not comparable [@Gurevitch2018; @Arnqvist1995; @Gallo1979; @Carpenter2020; @Stewart2010; @Glass2015].
+Lack of comparability could result from studies differing in experimental design, species, measurement variables and sampling units [@Arnqvist1995; @Stewart2010].
 For example, experimental designs in the field of comparative physiology can vary greatly in the temperatures or dosages of chemicals that they use in experimental treatments [e.g., @WuSeebacher2020].
@@
 
-The goal of our review is to briefly overview the process of meta-analysis, making a case for why heterogeneity is a good thing for answering fundamental research problems and guiding research directions.
-We introduce the idea of 'nuisance heterogeneity', showing comparative physiologists that it can be comfortably dealt with by re-formalising many existing effect sizes measures and/or by using multilevel meta-regression models.
-Then, we present results from a survey of published meta-analyses in the field of comparative physiology to gauge methodological and meta-analytic practices -- determining what types of effect sizes are commonly used, how often effect size estimates are impacted by 'nuisance heterogeneity' and whether meta-analytic models (i.e., models that account for sampling variance) are commonly applied.
-We also formalise alternative effect sizes and their associated sampling variance to provide comparative physiologists opportunities to explicitly incorporate 'nuisance heterogeneity' at the effect size level to ease their interpretation.
+The goal of our review is to briefly overview the meta-analytic process and argue for the value of heterogeneity in answering fundamental research problems and guiding research directions.
+We show how 'nuisance heterogeneity' in comparative physiology can be comfortably dealt with by re-formalising many existing effect size measures and / or by using multilevel meta-regression models.
+Then, we present results from a survey of published meta-analyses in the field of comparative physiology to gauge methodological and meta-analytic practices -- determining what types of effect sizes are commonly used, how often effect size estimates are impacted by nuisance heterogeneity and whether meta-analytic models (i.e., models that account for sampling variance) are commonly applied.
+We also formalise alternative effect sizes and their associated sampling variance to provide comparative physiologists with opportunities to explicitly incorporate 'nuisance heterogeneity' at the effect size level to ease their interpretation.
 Finally, we describe how more complex treatment differences, such as non-linear dosage differences, can be accommodated using multilevel meta-regression models.
@@
 The concept of heterogeneity is vitally important because it tells us how general our findings are likely to be and how much of the variance we see is the result of real biology or methodological differences (not just sampling variance) [@Nakagawa2017; @Borenstein2019].
-There are many phenomena driving effect heterogeneity, some of which are interesting and others that are less so.
 
-Generally, contributors to effect size heterogeneity fall within a number of broad categories.
-First, sampling variance contributes to heterogeneity; the variability driven by the inherent uncertainty in sampling a given population.
-We cannot sample the entire population and nor do we necessarily want to.
-As a consequence, we need to rely on a sub-sample to estimate a population parameter (e.g., correlation between two traits).
-How many independent samples we collect impacts our precision in estimating the 'true' effect [@Borenstein2019].
-In a meta-analysis we formally include sampling variance to remove this source of heterogeneity directly because it is known [@Gurevitch2018; @Koricheva2013].
-While unweighted analyses are common, weighting studies makes overall estimates more precise, reliable and less susceptible to publication bias, even if the overall mean itself is unbiased [@Morrissey2016a].
-As such, weighting effect size estimates by their inverse sampling variance can be crucial in meta-analysis.
+There are many phenomena driving effect heterogeneity.
+First, there is inherent uncertainty in estimating the ‘true’ population effect (e.g., a correlation coefficeiont) from smaller samples [@Borenstein2019].
+A formal meta-analysis weights sample estimates by their precision, and removes this source of heterogeneity [@Gurevitch2018; @Koricheva2013].
+Removing sampling variance is possible because we know, mathematically, how to calculate it for many effect measures.
+While unweighted analyses are common, weighting studies makes overall estimates more precise, and less susceptible to publication bias (see below), even if the overall mean itself is unbiased [@Morrissey2016a].
 Second, there are sociological factors impacting heterogeneity.
-These include the ease with which novel and significant results are published relative to non-significant results.
-Low powered studies that do not find an 'effect' or that find an effect in the opposite direction often lead to what is called publication bias [@Jennions2013; @Nakagawa2021b; @Rothstein2005].
+These include the ease with which novel and significant results are published relative to non-significant results, manifesting as publication bias [@Jennions2013; @Nakagawa2021b; @Rothstein2005].
 Third, real biological processes can drive effect heterogeneity.
@@
 This improves our understanding of the biological world around us and helps inform on future research directions.
+
 Finally, methodological factors are also big contributors to effect variability.
@@
 
-```{r, fig1, fig.cap="*Sources of effect size heterogeneity in meta-analyses*.
-Heterogeneity can come in various forms, from effect measures varying as a result of shared evolutionary history (i.e., phylogeny), different trait types measured, and sources of 'nuisance heterogeneity'.
+```{r, fig1, fig.cap="**Sources of effect size heterogeneity in meta-analyses**.
+Heterogeneity can come in various forms, from effect measures varying as a result of shared evolutionary history (i.e., phylogeny), the different trait types measured, and sources of 'nuisance heterogeneity'.
 In this example, nuisance heterogeneity is generated by differences in the experimental temperatures at which the animals were tested.
-However, nuisance heterogeneity can come in various other forms such as differences in dosage, or biochemical variables between used in the experiments.
-We can control for these types of heterogeniety by reformalising effect sizes and/or using multilevel metaregression as we describe in our review."}
+However, nuisance heterogeneity can come in various other forms such as differences in dosage.
+We can control for these types of heterogeniety by reformalising effect sizes and/or using multilevel metaregression."}
 image <- image_read(here::here("figs", "Fig1.png"))
@@
 
-Besides sampling variance, all the various sources of heterogeneity contribute (to varying extents) to the 'apples and oranges' problem often touted as compromising the reliability of meta-analyses.
-Indeed, some of this criticism revolves around combining studies that vary in their quality (e.g., observational vs experimental).
+Besides sampling variance, all the sources of heterogeneity discussed above contribute (to varying extents) to the 'apples and oranges' problem often touted as compromising the reliability of meta-analyses.
 Combining standardised effects, while ignoring these sources of heterogeneity can indeed weaken the reliability of a meta-analysis.
@@
 Whether comparing apples and oranges is a good idea simply boils down to the specific question of interest, the population one wishes to make conclusions about and how heterogeneous effects actually are.
-If we are interested in gaining insight into 'fruit' then synthesising apples and oranges is the only thing that makes sense.
-Instead, if we are interested in generalising only to apples, then mixing fruit will not be ideal.
-However, if we want to understand why different 'fruit' vary in their effects, then we can only ask this question by including all fruit [@Borenstein2019].
+If we are interested in generalising only to apples, then mixing fruit will not be ideal.
+However, if we want to understand why different 'fruit' vary in their effects, then we need to consider apples and oranges together [@Borenstein2019].
 
-We tend to agree with @Glass2015, and his sentiment is of particular relevance to comparative physiology.
+We tend to agree with @Glass2015, and his sentiment is particularly relevant to comparative physiology.
 For example, if we want to understand the impact of a pollutant on reproduction in aquatic organisms, including aquatic mammals and fish would provide answers to this general question, even if their reproductive biology and physiology are different.
-By synthesizing diverse study outcomes, not only does it allow to report on overall effects (if the question is relevant to ask), but it allows us to also understand critical features of the literature, study systems (e.g., different effects of pollutants on fish and mammal reproduction), and approaches that can explain the diversity of effect outcomes observed.
-Doing so provides a richer set of conclusions that can draw attention to important sources of variability that might have otherwise been overlooked.
+Synthesizing diverse study outcomes allows us to also understand critical features of the literature, study systems (e.g., different effects of pollutants on fish and mammal reproduction), and approaches (e.g., short-term vs long-term studies) that can explain the diversity of effect outcomes observed.
+Doing so provides a rich set of conclusions that can draw attention to important sources of variability that might have otherwise been overlooked.
 Having said that, it is still very important to understand the limitations and diversity of studies included in a meta-analysis, and how this can affect interpretations made -- an important reason why transparency and reproducibility are such a prominent feature of meta-analysis (or ideally should be) [@ODea2021].
 The validity of general conclusions to certain questions (e.g., what is the overall effect of a pollutant on reproduction?) will inevitably depend on the homogeneity of effects being synthesized.
-If the estimate of an overall effect coincides with low heterogeneity estimates then the effects are reasonably consistent [@Borenstein2019].
-If, however, an overall effect is accompanied by large heterogeneity estimates, then we would shift focus and explore drivers of that heterogeneity.
+If the estimate of an overall effect coincides with low heterogeneity then the effects are reasonably consistent [@Borenstein2019].
+If, however, an overall effect is accompanied by large heterogeneity, then we would shift focus and explore drivers of that heterogeneity.
 For example, given the very different physiology of aquatic mammals and fish, understanding an overall combined effect on reproduction may not be particularly relevant and may even be misleading.
-Therefore, understanding overall effects in each of these groups separately, and assess the extent to which they differ, may be more useful.
+It may, therefore be more useful tounderstand overall effects in each of these groups separately, and assess the extent to which they differ.
 
-There are, however, certain types of heterogeneity that transcend different questions or that are simply a 'nuisance' to interpreting effects.
+Certain types of heterogeneity, however, get in the way of understanding real biological patterns and are simply a 'nuisance' to interpreting effects.
 In other words, if we compare different varieties of 'apples', is it still fair to synthesize these studies to understand overall effects?
 In comparative physiology, this situation might be analogous to a meta-analysis that attempts to assess the effects of diet on fish growth across different populations of a widely distributed (cosmopolitan) species.
-Studies might rear populations of fish under different temperatures, but in the end, they are still all the same fish species, governed by the same thermodynamic effects on growth.
+Studies might rear populations of the same fish species under different temperatures, but in the end, they are still all governed by the same thermodynamic effects on growth.
 In this situation, we are still interested in understanding overall effects, but we may question whether such a conclusion is sensible given the diversity of temperatures applied.
@@
 
-Before embarking overviewing strategies to deal with 'nuisance heterogeneity', it is worth first understanding how comparative physiologists are currently conducting meta-analyses and other quantitative syntheses.
-As discussed above, different types of questions and experimental approaches will mix 'apples and oranges' to varying extents, but this heterogeneity (or basket of fruit) is often the main interest to comparative biologists.
-We conducted a literature survey to better understand the different types of effect sizes being used, their susceptibility to known sources of methodological / environmental variability across studies, and how these sources are controlled, we conducted a literature survey.
-To accomplish this goal, we searched for meta-analyses and comparative analyses that tackled questions using physiological data compiled from animal studies across multiple species.
-We were specifically interested in asking: 1) what type of effect size was used within the quantitative synthesis?
+Before overviewing strategies to deal with nuisance heterogeneity, it is worth first understanding how comparative physiologists are currently conducting meta-analyses and other quantitative syntheses.
+As such, we conducted a literature survey to better understand the different types of effect sizes being used in comparative physiology, their susceptibility to known sources of methodological / environmental variability across studies, and how these sources are controlled.
+After searching for meta-analyses and comparative analyses that tackled questions using physiological data compiled from animal studies across multiple species, we we asked: 1) what type of effect size was used within the quantitative synthesis?
 2) based on the methods provided, was the effect size likely susceptible to continuous variation in how treatments were applied (e.g., for contrast-based effects) or the conditions under which traits were measured (i.e., for correlations) across studies (i.e., 'nuisance heterogeneity')?
-3) If so, was the variation accounted for in the effect size or during analysis?
+3) If so, was such variation accounted for in the effect size or during analysis?
 and finally, 4) how many analyses used 'weighted' meta-analytic models?
@@
 
-All searches were conducted in Scopus between May 16 - 18, 2021.
+All searches were conducted in Scopus between May 16 and 18, 2021.
 Briefly, we first did a series of pilot searches (detailed in Supplementary Materials) to refine our search query [See @Foo2021 for an overview of this process].
-We searched for studies that included: 'meta-analysis', 'meta regression' , 'comparative analysis', 'comprehensive analysis' 'global analysis' or 'macro physiology' in their title and abstract, restricting our search to key comparative physiology journals (detailed in Table S1 and S2 - Supplementary Materials) within the last 6 years.
+We searched for studies that included: 'meta-analysis', 'meta regression' , 'comparative analysis', 'comprehensive analysis' 'global analysis' or 'macro physiology' in their title or abstract, restricting our search to key comparative physiology journals (detailed in Table S1 and S2 - Supplementary Materials) within the last 6 years.
 We expected this to provide a contemporary overview of quantitative syntheses in comparative physiology while making the survey and screening feasible.
-We acknowledge that this may have missed some important, and influential, quantitative syntheses in the field of comparative physiology, but likely provided a random sample to inform on the questions we sought to address (see below).
+We acknowledge that this may have missed some important, and influential, quantitative syntheses in the field of comparative physiology, but likely provided an informative random sample.
 
-We included comparative / meta-analyses that were focused on comparative physiological questions.
+We included comparative studies / meta-analyses that were focused on physiological questions.
 Narrative reviews and comments were not considered because they did not collate quantitative data from the literature.
-Studies needed to have collected physiological trait data from the literature such as hormones, thermal physiology (CTmax, CTmin, thermal preferences, thermal breadth, LT50, lethal thresholds), metabolic rates (routine, maximum, and minimum metabolic rate, aerobic scope), enzyme reaction rates and concentrations, oxidative stress and consequences (e.g., DNA damage, teleomere attrition), performance measurements (e.g., heart rates, sprint speed, swim speed, growth rates), body composition (e.g., fatty acid profiles) and immune traits (e.g., cell function, antibodies).
+Studies needed to have collected physiological trait data, such as hormones, thermal physiology (CTmax, CTmin, thermal preferences, thermal breadth, LT50, lethal thresholds), metabolic rates (routine, maximum, and minimum metabolic rate, aerobic scope), enzyme reaction rates and concentrations, oxidative stress and consequences (e.g., DNA damage, teleomere attrition), performance measurements (e.g., heart rates, sprint speed, swim speed, growth rates), body composition (e.g., fatty acid profiles) and immune traits (e.g., cell function, antibodies).
 Studies were also included if they measured the relationship between physiological traits and body size (e.g., metabolic scaling), reproductive allocation, or survival across taxa.
@@
 While many studies in comparative physiology collect data as part of a comparative analysis, we focus here only on studies collating data from existing literature because this is the major data source in quantitative syntheses.
-Quantitative syntheses interested in phenology, bio-mechanics, sexual size dimorphism (i.e., SSD, except if the study was interested in sexual differences in physiological traits), those focused on validating physiological methodology, or characterising population genetic structure, gene transcription, and quantitative genetics were excluded.
-There were also meta-analyses that focused on colour evolution and contrast which varied in their goals but were most often not focused on physiological questions.
+We excluded quantitative syntheses interested in phenology, bio-mechanics, sexual size dimorphism (i.e., except if the study was interested in sexual differences in physiological traits), those focused on validating physiological methodology, or characterising population genetic structure, gene transcription, and quantitative genetics.
+There were also meta-analyses that focused on colour evolution which varied in their goals but were most often not focused on physiological questions.
 As such, these studies were also excluded.
@@
 All title, abstract and full text screening was done by two people (DWAN and ML).
-Any conflicts or disagreements were resolved by discussion and a consensus on a paper was reached.
+Any disagreements were resolved by discussion to reach a consensus.
 Out of the 417 papers originally identified, 79 full texts were screened for eligibility, and we included a total of 62 for final data extraction.
-For full details on the search strings used, dates searched, the number of papers found, and our PRISMA flowchart (along with reasons for exclusion at the full text stage) we refer readers to the *Supplementary Information*.
-To address our questions, we categorised effect sizes as falling into the following categories: Response Ratio (lnRR), Standardised Mean Differences (SMD; e.g., Hedges d, g or Cohen's d), Correlation or Fisher's Z -transformed Correlation, Regression Slopes (Slopes), Risk Ratios, or whether the paper analysed the raw data or summary statistics directly (i.e., means/proportions) (which we label as 'raw').
-For all other effects we labelled as 'other'.
+For full details on the search strings used, search dates, the number of papers found, and our PRISMA flowchart (along with reasons for exclusion at the full text stage) we refer readers to the Supplementary Information.
+
+To address our questions, we categorised effect sizes as falling into the following categories: Response Ratio (*lnRR*), Standardised Mean Differences (*SMD*; e.g., Hedges *d*, *g* or Cohen's *d*), Correlation or Fisher's Z -transformed correlation (*Zr*), Regression Slopes (Slopes), Risk Ratios, or whether the paper analysed the raw data or summary statistics directly (i.e., means/proportions) (which we labelled as 'raw').
+All other effects were labelled as 'other'.
 To determine whether effect sizes were likely to vary based on some underlying continuous variable or were dependent on the context in which traits were measured, we assessed whether authors: 1) acknowledged this explicitly in the paper or 2) accounted for it in their models.
@@
 For example, trait means, such as ectothermic metabolic rate (i.e., raw/mean/proportion-based effect size), will vary depending on the temperature being measured.
-The magnitude of differences between two treatments (e.g, contrast-based effect sizes - SMD or lnRR) might depend on the pH or dosage used in treatments, and the strength of relationship between two variables (e.g., correlation between behaviour and metabolism) might depend on the temperature context under which metabolic rate or behaviour were measured.
+The magnitude of differences between two treatments (e.g, contrast-based effect sizes -- *SMD* or *lnRR*) might depend on the pH or dosage used in treatments, and the strength of relationship between two variables (e.g., correlation between behaviour and metabolism) might depend on the temperature context under which metabolic rate or behaviour were measured.
 Given the high heterogeneity in effects used in comparative physiology, we expected 'nuisance heterogeneity' to be common to most effect sizes.
-We categorised the types of statistical models fit in each study as: 1) fixed-effect meta-analysis; 2) random effects meta-analysis (i.e., intercept only model, but has random study effects); 3) multilevel meta-analysis (i.e., intercept only model, but has multiple random effect levels such as study, species and observation-level random effects); 4) meta-regression models (i.e., a multilevel or random effect model with fixed effects - including random effects); 5) weighted regression models (including mixed effect models); and 6) linear regression models (including linear and generalised linear mixed effect models, and phylogenetic least squares models) [see @NakagawaSantos2012 for discussion of models].
-Notably, only model types 1-5 are weighted models because they weight effect sizes based on the inverse of their sampling variance or sample size.
+We categorised the types of statistical models fit in each study as: 1) fixed-effect meta-analysis; 2) random-effects meta-analysis (i.e., intercept-only model, but has random study effects); 3) multilevel meta-analysis (i.e., intercept-only model, but has multiple random effect levels such as study, species and observation-level random effects); 4) meta-regression models (i.e., a multilevel or random-effects model with fixed effects - including random effects); 5) weighted regression models (including mixed- effects models); and 6) linear regression models (including linear and generalised linear mixed-effect models, and phylogenetic least squares models) [see @NakagawaSantos2012 for discussion of models].
+Notably, only model types 1--5 are weighted models because they weight effect sizes based on the inverse of their sampling variance or sample size.
 
@@
 
-Quantitative syntheses in comparative physiology commonly analyse raw summary statistics (`r with(effects, effects[effect == "Means","prop"])*100`% of studies), followed closely by Fishers transformed correlation coefficients (Zr) (`r with(effects, effects[effect == "Zr","prop"])*100`% of studies), standardised mean differences (SMD) (`r with(effects, effects[effect == "SMD","prop"])*100`%  of studies), and log response ratios (lnRR) (`r with(effects, effects[effect == "lnRR","prop"])*100`%, of studies) (Figure \@ref(fig:figsurv)A).
+The results of our literature survey show that quantitative syntheses in comparative physiology commonly analyse raw summary statistics (`r with(effects, effects[effect == "Means","prop"])*100`% of studies), followed closely by Fishers transformed correlation coefficients (*Zr*) (`r with(effects, effects[effect == "Zr","prop"])*100`% of studies), standardised mean differences (*SMD*) (`r with(effects, effects[effect == "SMD","prop"])*100`%  of studies), and log response ratios (*lnRR*) (`r with(effects, effects[effect == "lnRR","prop"])*100`%, of studies) (Figure \@ref(fig:figsurv)A).
 In many cases, studies make use of multiple effect size measures.
@@
 ```{r, figsurv, fig.wid = 16.833333, fig.height=5,fig.cap="**Summary of meta-analytic practices in comparative physiology.** (A) Different types of effect measures commonly used in meta-analyses and their relative frequency of use.
-(B) How many meta-analyses where ‘nuisance heterogenity’ have the potential to impact effect sizes, and the proportion of studies explicitly dealing with nuisance heterogenity.
-(C) Frequency of analytical approaches used to analyse effect measures.
+(B) (B) Frequencies of studies where ‘nuisance heterogenity’ had the potential to impact effect sizes (x-axis), and the frequencies of studies explicitly dealing with nuisance heterogeneity (bar colour).
+(C) Frequencies of analytical approaches used to analyse effect measures.
 Note that only ‘Weighted Regression’, ‘Random Effects Models’, ‘Multilevel Metaregression Models’ and ‘Multilevel Meta-analysis Models’ are weighted models.
@@
                  Other = dplyr::if_else(grepl("other|Q10", effect_size_type), n, 0),
-                 Means = dplyr::if_else(grepl("mean/proportion/raw", effect_size_type), n, 0),
+                 Mean = dplyr::if_else(grepl("mean/proportion/raw", effect_size_type), n, 0),
                  lnCVR = dplyr::if_else(grepl("lnCVR", effect_size_type), n, 0),
@@
 p3 <- summary %>% 
-  mutate(effect = fct_relevel(effect, c("Other","Vote Counting", "Linear Regression", "Weighted Regression", "Random Effects Model", "Multilevel Meta-analysis Model", "Multilevel Metaregression Model"))) %>%
+  mutate(effect = fct_relevel(effect, c("Other","Vote Counting", "Linear Regression", "Weighted Regression", "Random-Effects Model", "Multilevel Meta-analysis Model", "Multilevel Metaregression Model"))) %>%
   ggplot() + tm +
@@
 
-Meta-analysis requires comparative physiologists to make use of effect sizes that are suitable for answering their specific question.
 The key features of all effect sizes used in meta-analyses are that: 1) they are statistical parameters that have been placed on a common scale so that they can be compared across studies and 2) they have some associated measure of precision (i.e., sampling variance) [@Koricheva2013; @Borenstein2009; @Schmid2021].
-Effect sizes in comparative physiology are quite variable; they can be the mean difference between two groups [e.g., difference in mean between a control and treatment group; e.g., @WuSeebacher2020], the slope of a regression (e.g., between body size and metabolic rate), a correlation between two variables (e.g., between hormone levels and behaviour), or even the raw mean (or variance) itself [e.g., comparing CTmax or CTmin across species - e.g., @Sunday2014].
+Effect sizes in comparative physiology are quite diverse; they can be the mean difference between two groups [e.g., difference in mean between a control and treatment group; e.g., @WuSeebacher2020], the slope of a regression (e.g., between body size and metabolic rate), a correlation between two variables (e.g., between hormone levels and behaviour), or even the raw mean (or variance) itself [e.g., comparing CTmax or CTmin across species - e.g., @Sunday2014].
 In many cases, different effect sizes might be used depending on the question.
@@
 The choice as to which one to use boils down to the types of data available from primary studies, the specific question of interest, and whether studies are observational or experimental in nature.
-Considering our temperature example above, if we are interested in the magnitude of change between temperature treatments, we may want to use a contrast-based effect size, such as the log response ratio $\ln{RR}$.
+Considering our temperature example above, if we are interested in the magnitude of change between temperature treatments, we may want to use a contrast-based effect size, such as the log response ratio, *$\ln{RR}$*.
 Instead, if we are interested in how the mean of some physiological trait changes with temperature, we may model the mean itself.
-In the latter scenario, as long as all the means are measured in the same units (e.g., Celsius) or can be converted to the same units, then the mean may provide the desired answer to the original question.
+In the latter scenario, as long as all the means are measured in the same units (e.g., degrees Celsius) or can be converted to the same units, then the mean may provide the desired answer to the original question.
 We provide details on different effect measures and associated sample sizes in Table \@ref(tab:tablea).
@@
 names <- c("Mean",
-           "Log Standard deviation, lnSD",
-           "Log Response Ratio, lnRR",
+           "Log Standard deviation, \\textit{lnSD}",
+           "Log Response Ratio, \\textit{lnRR}",
            # leave this for now??? - we introduce this later
-           "Standardised Mean Difference, SMD",
-           "Zr (Fisher Transformation of \n Correlation Coefficient, r)")
+           "Standardised Mean Difference, \\textit{SMD}",
+           "\\textit{Zr} (Fisher Transformation of \n Correlation Coefficient, r)")
            #"Log Odds Ratio",
@@
              # we need to spell out SD_p somewhere
-             "\\frac{1}{2}log\\left( \\frac{1+r}{1-r}\\ right)")
+             "\\frac{1}{2}log \\left( \\frac{1+r}{1-r}\\right)")
              #"log\\left(\\frac{y_{i2}+0.5}{n_{i2}-y_{i2}+0.5}\\right) ",
@@
 eg <- c("CTmin, CTmax, Metabolic Rate (MR)",
-        "Variability in CTmin, CTmax, MR",
+        "Variability in CTmin, CTmax, Metabolic Rate (MR)",
         "Ratio between BPA treatment (BPA-exposed group) and control (no BPA)",
@@
 As can be seen in Table \@ref(tab:tablea), none of the effect measures control for 'nuisance heterogeneity'.
-For example, the magnitude of lnRR or SMD might depend on differences in the temperatures, dosages, pH, or water potential applied to each treatment.
+For example, the magnitude of *lnRR* or *SMD* might depend on differences in the temperatures, dosages, pH, or water potential applied to each treatment.
 The same applies for modelling the means.
-For example, standard metabolic rate (SMR) is temperature dependent.
-As such, one needs to standardise the temperature measurement to compare across studies [@White2006; @Uyeda2017] (if, of course, temperature is not of interest in of itself).
+For example, standard metabolic rate (SMR) is temperature-dependent.
+As such, one needs to standardise the temperature measurement to compare across studies [@White2006; @Uyeda2017] (if, of course, temperature is not of interest itself).
 While we could model this explicitly, this may not always be desirable.
@@
 A common experiment in comparative physiology is to manipulate the temperature organisms experience and measure some physiological rate (e.g., metabolic rate).
-Using the effect size measures in Table \@ref(tab:tablea) would result in the effect sizes varying with the temperatures applied within and across studies contributing to 'comparability' issues.
+Using the effect size measures from Table \@ref(tab:tablea) would result in the effect sizes varying with the temperatures applied within and across studies contributing to 'comparability' issues.
 For example, an effect size for a temperature manipulation of 10°C would be larger than an effect size for a temperature manipulation of 5°C (see Figure \@ref(fig:fig1)).
@@
 Higher $Q_{10}$ values indicate larger changes in physiological rates.
-However, currently there is no formal sampling variance associated with $Q_{10}$ in the literature, making it challenging to make use of the full power of weighted meta-analytic models.
-Interestingly, $Q_{10}$ can be seen as a variant of *lnRR*, meaning that we can derive a $Q_{10}$- based effect size and sampling error using the well-known mathematical properties of *lnRR*.
-This opens up the meta-analytic toolbox and improves upon our ability to account for well known sources of non-independence that are typical in meta-analysis [@Lajeunesse2011; @Noble2017].
+However, currently there is no formal sampling variance associated with $Q_{10}$, making it challenging to make use of the full power of weighted meta-analytic models.
+Interestingly, $Q_{10}$ can be seen as a variant of *lnRR*, meaning that we can derive a $Q_{10}$-based effect size and sampling error using the well-known mathematical properties of *lnRR*.
+This opens up the meta-analytic toolbox and improves our ability to account for well known sources of non-independence [@Lajeunesse2011; @Noble2017].
 
@@
 The mean, $M_{i}$, for group *i* can be any measurement type (e.g.
-a physiological rate, mass etc) so long as the measurement variable is ratio scale.
-Natural log transformation of this ratio makes the effect size normally distributed which is commonly assumed by meta-analytic models.
-Equation \@ref(eq:slnRR) is the analytical solution for *lnRR*'s sampling variance where $SD_{1}^2$ and $SD_{2}^2$ is the sample variance in group 1 and 2, respectively and $N_{1}$ and $N_{2}$ is the sample size in group 1 and 2.
+a physiological rate, mass etc) so long as the variable is measured on the ratio scale.
+Natural log transformation of this ratio makes the effect size normally distributed (a commonly assumed by meta-analytic models).
+Equation \@ref(eq:slnRR) is the analytical solution for *lnRR*'s sampling variance where $SD_{1}^2$ and $SD_{2}^2$ are the sample variance in group 1 and 2, respectively, and $N_{1}$ and $N_{2}$ are the sample size in group 1 and 2.
 
@@
 
-Equation \@ref(eq:lnq10) is essentially a temperature corrected equivalent of lnRR when the numerator and denominator are measured at different temperatures.
+Equation \@ref(eq:lnq10) is essentially a temperature-corrected equivalent of *lnRR* when the numerator and denominator are measured at different temperatures.
 This allows one to compare the mean of two temperature treatments directly regardless of the temperatures at which these groups have been measured.
 Here, we will refer to this as the log $Q_{10}$ response ratio, $lnRR_{Q_{10}}$.
-Notably, using this effect rather than the traditional $Q_{10}$ has two statistical advantages: 1) zero becomes biologically meaningful as 0 means two rates are the exactly the same and 'significantly different from zero' means that two rates are significantly different to each other and 2) $lnRR_{Q_{10}}$ is more likely to satisfy the assumption of residual normality than $Q_{10}$ (see @Hedges1999).
+Notably, using this effect rather than the traditional $Q_{10}$ has two statistical advantages: 1) zero becomes biologically meaningful as zero means two rates are exactly the same and 'significantly different from zero' means that two rates are significantly different to each other and 2) $lnRR_{Q_{10}}$ is more likely to satisfy the assumption of residual normality than $Q_{10}$ [see @Hedges1999].
 The recognition of this equivalence means that we can calculate the sampling variance for equation \@ref(eq:lnq10) as follows:
@@
 
-Equations \@ref(eq:lnq10VR) and \@ref(eq:slnq10VR) describe the change in physiological rate variance (eqn \@ref(eq:lnq10VR)) relative to a 10°C temperature change, along with its sampling variance (eqn \@ref(eq:slnq10VR)).
+Equations \@ref(eq:lnq10VR) and \@ref(eq:slnq10VR) describe the change in physiological rate variance [equation \@ref(eq:lnq10VR)] relative to a 10°C temperature change, along with its sampling variance [equation \@ref(eq:slnq10VR)].
 While this is a useful metric, as discussed by @Nakagawa2015, there is often a strong mean-variance relationship that needs to be accounted for in analysing changes in variance.
@@
 
-where $CV$ is the coefficient of variation defined as $SD / R$. Whether one choose to use SD or CV-based effect size depends on questions at hand [See @Nakagawa2015; @Senior2020].
+where $CV$ is the coefficient of variation defined as $SD / R$. Whether one choose to use SD or CV-based effect size depends on questions at hand [see @Nakagawa2015; @Senior2020].
 
-Our example using $Q_{10}$, a well-known effect measure in comparative physiology, shows how common effect size's can be re-formalised to account for 'nuisance heterogeneity' (in this case temperature).
+Our example using $Q_{10}$, a well-known effect measure in comparative physiology, shows that common effect size's can be re-formalised to account for nuisance heterogeneity (in this case temperature).
 In doing so, we are making assumptions about the nature of temperature effects on an effect size.
@@
 
-It will not be possible to always derive an effect size that completely controls for 'nuisance heterogeneity' at the effect size level all the time.
+It will not be possible to always derive an effect size that completely controls for nuisance heterogeneity at the effect size level all the time.
 This limitation is partly because treatment effects may not be simple linear or exponential functions of the mean response, making the effect sizes we discuss above unsuitable [e.g., thermal performance curves; @Noble2018].
-For example, dosages applied to treatments can follow quite complex non-linear (e.g., quadratic) relationships in relation to some mean response.
-When this occurs, we recommend comparative physiologists to apply meta-regression approaches, controlling for 'nuisance heterogeneity' as a moderator.
-In many cases, this will be the easiest, or even preferred approach because exploring drivers of heterogeneity is of prime interest in most meta-analyses anyway.
-Nonetheless, there are some simple statistical approaches a comparative physiologist can use to make the overall effects more easily interpretable, allowing one to control for 'nuisance heterogeneity', while also testing other biological moderators of interest [@Schielzeth2010].
+For example, dosages applied to treatments can follow quite complex non-linear relationships in relation to some mean response (e.g., quadratic relationships).
+When this occurs, we recommend comparative physiologists to apply meta-regression approaches, controlling for nuisance heterogeneity as a moderator.
+In many cases, this will be the easiest, or even preferred, approach because exploring drivers of heterogeneity is of prime interest in most meta-analyses anyway.
+Nonetheless, there are some simple statistical approaches a comparative physiologist can use to make the overall effects more easily interpretable, allowing one to control for nuisance heterogeneity, while also testing other biological moderators of interest [@Schielzeth2010].
 Before diving into meta-regression models, we will first overview the meta-analytic models commonly used.
 
-#### *Multi-level Meta-Analysis when the Overall Effect is of Interest*
+#### *Multilevel Meta-Analysis when the Overall Effect is of Interest*
 
@@
 Including a prediction interval (PI) can also be useful (discussed below) [@Nakagawa2021c].
-Estimating an overall mean and 95% CI is generally done with a simple random effects or multilevel meta-analytic model that accounts for effect size sampling error [@Nakagawa2017; @NakagawaSantos2012].
+Estimating an overall mean and 95% CI is generally done with a simple random-effects or multilevel meta-analytic model that accounts for effect size sampling error [@Nakagawa2017; @NakagawaSantos2012].
 More often than not, meta-analyses in comparative physiology will have complex hierarchical structure.
 For example, multiple effect sizes may be taken from a single study on traits measured on the same individuals or from many different species that share an evolutionary history [@Cinar2021; @Noble2017].
-As such, it is far more likely that comparative physiologists will need to apply a multilevel meta-analytic model to control for the various sources of non-independence, and, whenever possible, they should [@Cinar2021; @NakagawaSantos2012; @Song2021; @Nakagawa2021; @Noble2017].
+As such, it is far more likely that comparative physiologists will need to apply a multilevel meta-analytic model to control for the various sources of non-independence [@Cinar2021; @NakagawaSantos2012; @Song2021; @Nakagawa2021; @Noble2017].
 Multilevel models are also extremely useful in describing the various sources contributing to effect size variance (a feature we describe below).
@@
 Having said that, in some instances, it may be sufficient for a meta-analysis to make use of traditional random effects models.
-We refer readers to excellent reviews and books that overview the distinctions between common (fixed) effect, random effect and multilevel models and when one might want (or not want) to apply these models [@Nakagawa2017; @NakagawaSantos2012; @Koricheva2013; @Borenstein2009; @Schmid2021].
+We refer readers to excellent reviews and books that overview the distinctions between common (fixed) effect, random-effect and multilevel models and when one might want (or not want) to apply these models [@Nakagawa2017; @NakagawaSantos2012; @Koricheva2013; @Borenstein2009; @Schmid2021].
 
-Assume that we are interested in understanding the overall effect of, say, stress (i.e., corticosterone - CORT) on reproduction [e.g., see @Podmola2018].
+Assume that we are interested in understanding the overall effect of, say, corticosterone (CORT) on reproduction [e.g., see @Podmola2018].
 We might extract data from studies manipulating corticosterone in bird eggs.
-Of course, these studies are diverse, spanning many species and applying different dosages of corticosterone and are working across many species.
-If the studies are experimental in nature, then a standardised effect size, such as $ln_{RR}$ or SMD, might be applicable.
+Of course, these studies are diverse, spanning many species and applying different dosages of corticosterone.
+If the studies are experimental in nature, then a standardised effect size, such as $lnRR$ or *SMD*, might be applicable.
 We then might fit an overall multilevel meta-analytic model as follows:
@@
 Importantly, if we have effect sizes that are derived from the *same* sample of organisms (e.g., because traits are measured on the same sets of individuals), then we need to remove this dependency from the calculation of each $v_{i}$; we can then model the known sampling covariance between effect sizes by modifying $\textbf{I}$ to include off-diagonals that account for this covariance [See Box 1 and @Noble2017].
-The fact that we can obtain an overall estimate of sampling variance (i.e., $\sigma^2_{m}$, see below for how it is defined) is very important because it provides a way for us to understand just how much variation in effects are the result of sampling differences across studies versus other, potentially important sources of variation such as differences in the methods applied, species differences, or even real biological effects that impact the effect size a study is likely to observe [@Nakagawa2017; @NakagawaSantos2012].
+The fact that we can obtain an overall estimate of sampling variance (i.e., $\sigma^2_{m}$, see below for how it is defined) is very important because it provides a way for us to understand just how much variation in effects are the result of sampling differences across studies versus other, potentially important sources of variation, such as differences in the methods applied, species differences, or even real biological effects that impact the effect size a study is likely to observe [@Nakagawa2017; @NakagawaSantos2012].
 This is formalised in what we call 'heterogeneity analysis' which we describe below.
-Importantly, this model provides us with the answer to our overall question: Across all the species and studies manipulating egg corticosterone, how much of an overall effect does corticosterone have on reproduction relative to control conditions?
+Importantly, this model provides us with the answer to our question: across all the species and studies manipulating egg corticosterone, how much of an overall effect does corticosterone have on reproduction relative to control conditions?
 
 Of course, the overall effect does not provide us with a way to interpret its magnitude in the context of how much CORT has been applied in the treatments used in the sample of studies.
-The most we can say about it is that the effect is small, moderate or large out of the sample of effect sizes extracted from this set of studies.
+The most we can say about it is that the effect is small, moderate or large given the sample of effect sizes extracted from this set of studies.
 In the next section, we show how to 'correct' the overall effect size so that its interpretation is more meaningful.
@@
 We can, however, apply some simple transformations to make the overall mean estimate more intuitive while also improving the interpretation of non-linear parameters and interactions estimated from the model [@Schielzeth2010; @GelmanHill2007].
-One simple transformation would be to centre the variable $x_{j}$, by subtracting each value from the mean to create a new input variable (i.e., $c_{i}=x_{i}-\bar{x}$, where the subscript *i* denotes each individual effect size dosage).
+One simple transformation would be to centre the variable $x_{j}$ by subtracting each value from the mean to create a new input variable (i.e., $c_{i}=x_{i}-\bar{x}$, where the subscript *i* denotes each individual effect size dosage).
 The new variable, $c_{j}$, is now centered on the mean and can replace $x_{j}$ in the meta-regression model.
@@
 Here, one can model the mean for each group (i.e., control and treatment) and account for the known sampling variance associated with each group mean.
-Dosage, or other continuous variables like temperature, can then be modeled (accounting for sampling variance) to understand how mean reproductive output varies.
+Dosage, or other continuous variables, like temperature, can then be modeled (accounting for sampling variance) to understand how mean reproductive output varies.
 It is important to recognise that all means need to be comparable and that these models are more complex to fit.
@@
 In other words, linear / main effects can still be interpreted normally in the presence of non-linear / interactions fit in the model [@Schielzeth2010; @GelmanHill2007].
-We provide examples in the online supplementary material (with R code) to show readers how the models we describe above can be fit, and how meta-analytic means can be adjusted for treatment heterogeneity.
+We provide examples in the online Supplementary Material (with R code) to show readers how the models we describe above can be fit, and how meta-analytic means can be adjusted for treatment heterogeneity.
 
@@
 
-Quantifying heterogeneity using $I_{total}^2$ provides a formal way to assess the relative amount of variation that is the result of 'true' biological or methodological differences as opposed to simply chance (i.e., sampling variance) [@NakagawaSantos2012; @Higgins2002].
+Quantifying heterogeneity using $I_{total}^2$ provides a formal way to assess the relative amount of variation that is the result of 'true' biological or methodological differences as opposed to chance (i.e., sampling variance) [@NakagawaSantos2012; @Higgins2002].
 In other words, $I_{total}^2$ is the percentage of variance between effect sizes after removing the effects of sampling error [@Higgins2002].
@@
 @Senior2016 have shown that total heterogeneity is often extremely high in ecological and evolutionary meta-analysis (\~91%), suggesting that effect measures vary widely within and across studies.
-Some of the variation is clearly the result of working with different species and/or strains, or measuring different traits and outcome measures.
-However, some of this variation also arises because of methodological differences across studies that might be related to the dosages or temperatures used for treatments.
+Some of the variation is clearly the result of working with different species, strains, or measuring different traits and outcome measures.
+However, some of this variation also arises because of methodological differences across studies (e.g., different temperature or dosage treatments).
 
 Formally quantifying and presenting heterogeneity estimates from meta-analytic models can provide a way to understand the major drivers of effect size variation by producing various $I^2$ estimates that can be compared within and across studies.
-For example, we could fit the multilevel model described above to understand what proportion of variation is the result of, say, 'study' effects following @NakagawaSantos2012: $I^2_{study} = \frac{\sigma^2_{study}}{\sigma^2_{total}}$ where $\sigma^2_{study}$ is the study specific variance.
+For example, we could fit the multilevel model described above to understand what proportion of variation is the result of, say, 'study' effects following @NakagawaSantos2012: $I^2_{study} = \frac{\sigma^2_{study}}{\sigma^2_{total}}$ where $\sigma^2_{study}$ is the study-specific variance.
 
 Some readers may notice the similarities between $I^2$ and $R^2$ [@Nakgawa2013; @Nakagawa2010; @Nakagawa2017].
-If we want to formally assess how much effect size variation is the result of 'nuisance heterogeneity' (e.g.,  temperature and dosage differences applied across studies) then we could fit our multilevel meta-regression model, including dosage or temperature (linear, quadratic or even more complex fits), and estimate how much variation is explained by these fixed effects following @Nakgawa2013.
+If we want to formally assess how much effect size variation is the result of nuisance heterogeneity (e.g.,  temperature and dosage differences applied across studies) then we could fit our multilevel meta-regression model including dosage or temperature (linear, quadratic or even more complex fits), and estimate how much variation is explained by these fixed effects following @Nakgawa2013.
 
@@
 Importantly, moderators could be those that explain variation at the effect size level (i.e., dosage, temperature) or variation at the study or species level (e.g., reproductive mode, endothermy, etc.).
-$R^2_{marginal}$, or how we like to think of it in this context as $R^2_{'nuisance'}$, maybe a useful measure to help readers understand just how much effect variation can result from the specific treatment application.
+$R^2_{marginal}$, or how we like to think of it in this context as $R^2_{nuisance}$, maybe a useful measure to help readers understand just how much effect variation can result from the specific treatment application.
 If the heterogeneity is high as a result of, say, dosage differences, then it is clear that the choice of dosage will have a critical impact on the effect of interest.
@@
 For example, assume that we were interested in the overall impact of salinity stress in freshwater fish.
-To tackle this question, we collected experimental studies measuring fish swim performance under high salinity treatments (\~15-20ppm Na Cl) compared to freshwater (\~0ppm Na Cl) controls, using SMD to quantify the magnitude of effect salinity had on swim performance.
-We conduct a meta-analysis and estimate an overall SMD of 0.50 with a prediction interval of 0.05 to 0.85.
-The PI indicates that effects can vary widely from as low as an SMD of 0.05 to as high as an SMD 0.85, depending on the population.
+To tackle this question, we collected experimental studies measuring fish swim performance under high salinity treatments (\~15--20ppm Na Cl) compared to freshwater (\~0ppm Na Cl) controls, using *SMD* to quantify the effect salinity had on swim performance.
+We conduct a meta-analysis and estimate an overall *SMD* of 0.50 with a 95% prediction interval of 0.05 to 0.85.
+The PI indicates that effects can vary widely from as low as an *SMD* of 0.05 to as high as an *SMD* 0.85, depending on the population.
 In addition, if we were to repeat a similar study, we would expect a new effect to fall within the range of 0.05 and 0.85, 95% of the time [@Borenstein2019; @Nakagawa2021c].
@@
 Comparative physiologists are interested in meta-analysing effects across a diversity of species, experimental designs, and environments.
-Importantly, sampling variances for many effect sizes commonly used by comparative physiologists (e.g., CTmax, $Q_{10}$ etc) can be formalised and powerful meta-analytic models can be easily applied.
+Importantly, sampling variances for many effect sizes commonly used by comparative physiologists (e.g., CTmax, $Q_{10}$ etc) can be formalised and powerful meta-analytic models can be easily applied to these effect measures.
 While an overall meta-analytic mean may be of interest, more often than not, understanding the drivers of effect size heterogeneity will be the primary interest.
@@
 Instead, comparative physiologists might simply want to focus on biological drivers of effect size variability and want an effect size or analytic approach that allows them to remove these ‘nuisances’.
-Here, we provide a set of tools to deal with ‘nuisance heterogeneity’ by ‘reinventing’ standard effect sizes and/or using mean centered nuisance variables in meta-regression models.
+Here, we provide a set of tools to deal with ‘nuisance heterogeneity’ by reinventing standard effect sizes and/or using mean centered nuisance variables in meta-regression models.
 Estimating complex meta-regression models with a multitude of fixed effects might result, however, in more challenging model interpretation.
@@
 Indeed, this may even be a necessity to simplify the model.
-We wish the set of tools we describe provide clarification around importance and limitations of heterogeneity.
+The set of tools we describe provide clarification around importance and limitations of heterogeneity.
 We also hope to provide new ways to help comparative physiologists communicate effect measures more richly to guide our understanding and decisions around pressing global challenges.
@@
 ## **Author Contributions**
-DWAN, SN: Project administration, Conceptualization, Writing - original draft, Visualization, Funding acquisition, Resources, Formal analysis, Methodology, Software; ML, PP, REO, SD, SB: Writing – review & editing, Visualization, Validation, Software, Data curation, Formal analysis.
+DWAN, SN: Project Administration, Conceptualization, Writing - original draft, Visualization, Funding acquisition, Resources, Formal Analysis, Methodology, Software; ML, PP, REO, SD, SB: Writing – review & editing, Visualization, Validation, Software, Data Curation, Formal analysis.
 

### 2021-07-22 MS/ms.Rmd
Final fixes from Losia added new figs

@@
 We can control for these types of heterogeniety by reformalising effect sizes and/or using multilevel metaregression."}
-image <- image_read(here::here("figs", "Fig1.png"))
+image <- image_read(here::here("figs", "Fig1_v2_ML.png"))
 image
@@
 While we could model this explicitly, this may not always be desirable.
-It can often be useful to standardise the effect to both ease its interpretation and simplify modelling.
+It can often be useful to standardise the effect to both ease its interpretation and simplify modelling (Figure \@ref(fig:fig0)).
 In Box 1 we provide readers with guidance on how comparative physiologists can apply corrections to the effect measure itself.
@@
 Below, we show how we can formalise a traditional effect size, such as $lnRR$, to capture this ‘nuisance variation’ using a common, well understood effect measure of interest to comparative physiologists ($Q_{10}$).
+
+```{r, fig0, fig.cap="**Effect sizes from old to new**. We still need a legend..insert here?"}
+image <- image_read(here::here("figs", "Fig0_v1_ML.png"))
+image
+```
 

### 2021-07-22 MS/box.Rmd
Box updated with Losia's comments

@@
 
-Here, we show how to obtain sampling variance for a slope (or a 'rate of change') when you have measurements of a physiological trait at two points along an environmental gradient (e.g.
-temperature, salinity, acidity).
-We then derive sampling variance for the difference between two slopes, and demonstrate how SMD (standardized mean difference) can be corrected to account for differences in both units (e.g.
+Here, we show how to obtain sampling variance for a slope (or a 'rate of change') when you have measurements of a physiological trait at two points along an environmental gradient (e.g., temperature, salinity, acidity).
+We then derive sampling variance for the difference between two slopes, and demonstrate how *SMD* can be corrected to account for differences in both units (e.g.
 cm or mg) and points on an environmental gradient (e.g.
@@
 
-Let's start with a real example that comparative physiologists can easily relate with, the slope of responses to temperature acclimation or,or as we call it, the acclimation response ratio (ARR).
-ARR can be defined as a slope for acclimated physiological responses at two different temperature points, defined as:
+Let's start with a real example that comparative physiologists can easily relate with, the slope of responses to temperature acclimation, or as we call it, the acclimation response ratio (*ARR*).
+*ARR* can be defined as a slope for acclimated physiological responses at two different temperature points, defined as:
 
@@
 
-Therefore, when $M_{1}$ and $M_{2}$ are independent, we can obtain the sampling variance for ARR as:
+Therefore, when $M_{1}$ and $M_{2}$ are independent, we can obtain the sampling variance for *ARR* as:
 
@@
 Given this, the sampling variance for $X_{1}$ is $SD^2_{1} / N_{1}$, and the sampling variance for $X_{2}$ is $SD^2_{2} / N_{2}$.
-You can see those elements of the sampling variance of ARR in the formula above.
+You can see those elements of the sampling variance of *ARR* in the formula above.
 The term $(1/(T_{2} - T_{1}))^2$ comes from recognizing $1/(T_{2} - T_{1})$ as a constant.
@@
 Note that, as above, the covariance equals the correlation multiplied by the square-root of two (sampling) variances.
-Therefore, the sampling variance of ARR can be now written as:
+Therefore, the sampling variance of *ARR* can be now written as:
 
@@
 
-Now let us assume that we want to know the difference between two different ARR values: female ARR, $\text{ARR}_{f}$ and male ARR, $\text{ARR}_{m}$. Such a difference (ARRD) can be written as:
+Now let us assume that we want to know the difference between two different *ARR* values: female *ARR*, $\text{ARR}_{f}$ and male *ARR*, $\text{ARR}_{m}$. Such a difference (*ARRD*) can be written as:
 
@@
 
-Using the properties of variance and the equations from above, the sampling variance for ARRD can be derived, when measurements at two temperature points are independent, as:
+Using the properties of variance and the equations from above, the sampling variance for *ARRD* can be derived, when measurements at two temperature points are independent, as:
 
@@
 
-Here we have derived sampling variances for 'temperature' ARR and ARRD for both independent and dependent cases.
+Here we have derived sampling variances for 'temperature' *ARR* and *ARRD* for both independent and dependent cases.
 These formulas can also be applied to changes in other factors (e.g., salinity, pH, oxygen) by changing the temperature constant.
@@
 
-Calculating ARR assumes that the units for the mean difference across studies is consistent.
+Calculating *ARR* assumes that the units for the mean difference across studies is consistent.
 Frequently, this will not be the case for meta-analyses that hope to synthesise a wide array of traits that vary in their units (e.g., ul/g, grams, seconds, minutes).
-Fortunately, $lnRR$ and SMD (Table 1) already controls for unitary differences.
-As such, we can apply similar logic that we discuss above so that SMD corrects for both temperature and unitary differences.
-Table 1 provides the formula for SMD, its pooled standard deviation, and sampling variance.
-Just like with ARR, we can apply our temperature correction to the SMD formula as follows:
+Fortunately, *$lnRR$* and *SMD* (Table 1) already controls for unitary differences.
+As such, we can apply similar logic that we discuss above so that *SMD* corrects for both temperature and unitary differences.
+Table 1 provides the formula for *SMD*, its pooled standard deviation, and sampling variance.
+Just like with *ARR*, we can apply our temperature correction to the *SMD* formula as follows:
 

### 2021-07-22 MS/box.Rmd
Box updated with Losia's comment

@@
 
-Here, $f(M_1) = \ln{M_1}$. By applying $f'(M_1) = 1/{M_1}$ (i.e. the first derivative of $lnM_1$ is $1/{M_1}$) to the delta method and using the variance's basic properties, we have:
+Here, $f(M_1) = \ln{M_1}$. By applying $f'(M_1) = 1/{M_1}$ (i.e. the first derivative of $lnM_1$ is $1/{M_1}$) to the Delta method and using the variance's basic properties, we have:
 
@@
 Note that the first term, $\frac{SD_{1}^2}{N_{1}}$ is once again the sampling variance for group 1, and we simply multiply this term by the square of the first derivative of $M_{1}$ as described by the Delta method.
-Readers may notice that this formula is now equivalent to the sampling variance for $ln_{RR}$ (Table 1).
+Readers may notice that this formula is now equivalent to the sampling variance for $lnRR$ (Table 1).
 We can extend this sampling variance to include dependency between the groups as:

### 2021-07-22 MS/ms.Rmd
updated to ms and cache. Mainly on Table 1

@@
 As comparative physiologists, this is the stuff that gets us up every morning!
-Some variation could result from shared evolutionary history (i.e., phylogeny) or because of the different thermal environments species (or populations) occupy.
 We can model these biological factors to test predictions from hypotheses that we believe are key players impacting mean effect size and direction.
@@
 For example, given the very different physiology of aquatic mammals and fish, understanding an overall combined effect on reproduction may not be particularly relevant and may even be misleading.
-It may, therefore be more useful tounderstand overall effects in each of these groups separately, and assess the extent to which they differ.
+It may, therefore be more useful to understand overall effects in each of these groups separately, and assess the extent to which they differ.
 
@@
 names <- c("Mean",
-           "Log Standard deviation, \\textit{lnSD}",
-           "Log Response Ratio, \\textit{lnRR}",
+           "Log Standard deviation, lnSD",
+           "Log Response Ratio, lnRR",
            # leave this for now??? - we introduce this later
-           "Standardised Mean Difference, \\textit{SMD}",
-           "\\textit{Zr} (Fisher Transformation of \n Correlation Coefficient, r)")
+           "Standardised Mean Difference, SMD",
+           "Zr (Fisher Transformation of \n Correlation Coefficient, r)")
            #"Log Odds Ratio",
@@
           flextable::compose(j = 1:4, part = "header", value = as_paragraph(as_b(c("Effect Measure", "Definition", "Sampling Variance", "Examples")))) %>% 
-          flextable::compose(j = 2:3, value = as_paragraph(as_equation(c(eqns_yi, eqns_vi))))             %>%
+          flextable::compose(j = 2:3, value = as_paragraph(as_equation(c( eqns_yi, eqns_vi))))             %>%
           flextable::compose(j = 4, value = as_paragraph(eg))             %>%

### 2021-07-22 MS/supp.Rmd
CS2 update, packages update, path correction in some sections

@@
 #devtools::install_github("daniel1noble/metaAidR")
-pacman::p_load(devtools, png, jpeg, pander, cowplot, flextable, tidyverse, metafor, orchaRd, here, osfr, magrittr, metaAidR)
+pacman::p_load(devtools, png, jpeg, pander, cowplot, flextable, formatR, magick,
+               tidyverse, metafor, orchaRd, here, osfr, magrittr, metaAidR)
 ```
@@
 data_CS1a<-data_CS1a %>% 
-              mutate(ARR=(mean_high-mean_low)/(acc_temp_high - acc_temp_low),
-                     Var_ARR=((1/(acc_temp_high-acc_temp_low))^2*(sd_low^2/n_low_adj+sd_high^2/n_high_adj)))
+              mutate(ARR=(mean_high_f-mean_low_f)/(acc_temp_high - acc_temp_low),
+                     Var_ARR=((1/(acc_temp_high-acc_temp_low))^2*(sd_low_f^2/n_low_f_adj+sd_high_f^2/n_high_f_adj)))
 
@@
 The data in question was collected by @Podmola2018.
+The meta-analysis reviewed published studies reporting the outcomes of experiments that manipulated levels of steroid hormones (testosterone and corticosterone) and recorded the impact of such manipulations on offspring traits.
+The aim was to establish the generality and homogeneity of such experimental effects, and their dependence on several moderator variables, most importantly the type of measured ofspring traits, the type of hormone used, and several methodological factors (administration route, hormone vehicle, offspring developmental stage, etc.
+- for details please consult the original study).
+The data used here as a subset of the original data, limited to effect sizes recorded in experiments manipulating the hormones *in ovo*.
 
@@
 # Load the data file.
-data_CS2 <- read.csv(here::here("ms", "Dosage_EggHormones_CS2.csv"), sep = ";")
+data_CS2_all <- read.csv(here::here("Dosage_EggHormones_CS2.csv"), sep = ";")
 
@@
 ### Interpreting Meta-analytic Means Controlling for Dosages
-The data contains two columns of dosages....EXPLAIN all this.
+
+The data contains two categorical moderator variables to be included in the model: `hormone1` - identifies the type of steroid hormone (*androgen* vs.
+*corticosterone*); `trait1` - the type of offpsring trait measured (physiology, behaviour, survival, reproduction).
+Random effects include study ID (`ID`), species ID (`species_lat`) and study ID (`paper`).
+
+The dosage variables are reported separately for each hormone in ng/yolk (`total_dose_T`, `total_dose_A4` & `total_dose_CORT`) and in fractions of natural per-yolk concentration (`total_dose_p_T`, etc.) The latter value is available only for studies that reported natural hormone concentrations (`T_yolk`, `A4_yolk`, `CORT_yolk`).
+
+Below we are considering a subset of data related to testosterone manipulation - this hormone is often mixed with androstendione, which further justifies analysing it separately.
 
 ```{r, class.source='klippy', results = 'hide'}
-# Centre the dosage data on the mean. Note that, for comparability, we'll exclude 'NA' in dose so that models are fit with the exact same data.
-          data_CS2 %<>% mutate(z_total_dose_T = scale(total_dose_T, center = TRUE, scale = FALSE)) %>% filter(!is.na(z_total_dose_T))
+# Centre the dosage data on the mean. Note that, for comparability, we'll exclude 'NA'
+# in dose so that models are fit with the exact same data.
+data_CS2 <- data_CS2_all %>% mutate(z_total_dose_T = scale(total_dose_T, center = TRUE, scale = FALSE),
+                     z_total_dose_p_T = scale(total_dose_p_T, center = TRUE, scale = FALSE)) %>% filter(!is.na(z_total_dose_T))
 
 # Model that ignores "nuisance heterogeneity" for dosage applied
-     model_CS2_MLMA <- metafor::rma.mv(d ~ 1, V = var_d, random = list(~1|ID, ~1|paper), test = "t", dfs = "contain", data = data_CS2)
-     print(model_CS2_MLMA)
+model_CS2_MLMA_1 <- metafor::rma.mv(d ~ 1, V = var_d,
+                                    method="REML",
+                                  random = list(~1|ID, ~1|paper, ~1|species_lat),
+                                  test = "t", dfs = "contain", data = data_CS2)
+print(model_CS2_MLMA_1)
 
 # Calculate Prediction Intervals
-           pis_MLMA <- predict(model_CS2_MLMA)
-           print(pis_MLMA)
+pis_MLMA_1 <- predict(model_CS2_MLMA_1)
+print(pis_MLMA_1)
 
 # Calculate I2 as well
-                 I2 <- orchaRd::i2_ml(model_CS2_MLMA)
-                 print(I2)
+I2_1 <- orchaRd::i2_ml(model_CS2_MLMA_1)
+print(I2_1)
+
+# Plot the results
+orchard_plot(model_CS2_MLMA_1, mod="Int", xlab="Cohen's d")
 ```
 
-We can see from above that the model 'ignoring' the nuisance heterogenity (model_CS2_MLMA) (i.e., the variability in effects resulting from dosage differences across studies) estimates an overall meta-analytic mean as `r coef(model_CS2_MLMA)` with a 95\% CI from `r model_CS2_MLMA$ci.lb` to `r model_CS2_MLMA$ci.ub`.
-Our prediction intervals suggest that heterogenity is high, reflected also in our $I_{total}^2$ estimate of `r I2[1]*100`\% -- 95\% of the time we expect the mean in repeated samples to fall between `r pis_MLMA$pi.lb` to `r pis_MLMA$pi.ub`.
-Approximately, `r I2[3]*100`\% of the total heterogenity is the result of differences between studies.
-Given that we have not controlled for dosage differences across studies all we can say is that the average SMD is rather small is the sample of studies that have applied these sets of dosages.
-In otherwords, on average, the means from the treatment and control groups differ by `r coef(model_CS2_MLMA)` standard deviation units.
+We can see from above that the model 'ignoring' the nuisance heterogenity (`model_CS2_MLMA_1`) (i.e., the variability in effects resulting from dosage differences across studies) estimates an overall meta-analytic mean as `r coef(model_CS2_MLMA_1)` with a 95\% CI from `r model_CS2_MLMA_1$ci.lb` to `r model_CS2_MLMA_1$ci.ub`.
+Our prediction intervals suggest that heterogenity is high, reflected also in our $I_{total}^2$ estimate of `r I2_1[1]*100`\% -- 95\% of the time we expect the mean in repeated samples to fall between `r pis_MLMA_1$pi.lb` to `r pis_MLMA_1$pi.ub`.
+Approximately, `r I2_1[3]*100`\% of the total heterogenity is the result of differences between studies.
+Given that we have not controlled for dosage differences across studies all we can say is that the average SMD is rather small in the sample of studies that have applied these sets of dosages.
+In other words, on average, the means from the treatment and control groups differ by `r coef(model_CS2_MLMA_1)` standard deviation units.
 
@@
 ```{r}
-
 # Model that re-calibrates the overall meta-analytic mean (Intercept) to control for dosage administration
-    model_CS2_nuisance1 <- metafor::rma.mv(d ~ total_dose_T, V = var_d, random = list(~1|ID, ~1|paper), test = "t", dfs = "contain", data = data_CS2)
+model_CS2_nuisance1 <- metafor::rma.mv(d ~ total_dose_T, V = var_d,
+                                       method="REML",
+                                       random = list(~1|ID, ~1|paper, ~1|species_lat),
+                                       test = "t", dfs = "contain", data = data_CS2)
 print(model_CS2_nuisance1)
@@
 
-# Model that re-calibrates the overall meta-analytic mean (Intercept) to control for dosage administration but uses centered dosage
-     model_CS2_nuisance2 <- metafor::rma.mv(d ~ z_total_dose_T, V = var_d, random = list(~1|ID, ~1|paper), test = "t", dfs = "contain", data = data_CS2)
+# Model that re-calibrates the overall meta-analytic mean (Intercept) to control for dosage
+# administration but uses centered dosage
+model_CS2_nuisance2 <- metafor::rma.mv(d ~ z_total_dose_T, V = var_d,
+                                       method="REML",
+                                       random = list(~1|ID, ~1|paper, ~1|species_lat),
+                                       test = "t", dfs = "contain", data = data_CS2)
 print(model_CS2_nuisance2)
@@
 
-Now that we have centered the total dosage around its mean (which is `r mean(data_CS2$total_dose_T, na.rm = TRUE)` uL difference(Szymek, not sure on units, sorry)) our overall meta-analytic mean (now estimated to be `r coef(model_CS2_nuisance2)[1]`,  with a 95\% CI from `r model_CS2_nuisance2$ci.lb[1]` to `r model_CS2_MLMA$ci.ub[1]`) is interpreted differently.
-Overall, the meta-analytic mean difference between treatments that differ by an average of `r mean(data_CS2$total_dose_T, na.rm = TRUE)` uL is `r coef(model_CS2_nuisance2)[1]` standard deviation units different.
+Now that we have centered the total dosage around its mean (which is `r mean(data_CS2$total_dose_T, na.rm = TRUE)` ng/yolk, our overall meta-analytic mean (now estimated to be `r coef(model_CS2_nuisance2)[1]`,  with a 95\% CI from `r model_CS2_nuisance2$ci.lb[1]` to `r model_CS2_nuisance2$ci.ub[1]`) is interpreted differently.
+Overall, the meta-analytic mean difference between treatments that differ by an average of `r mean(data_CS2$total_dose_T, na.rm = TRUE)` ng/yolk is `r coef(model_CS2_nuisance2)[1]` standard deviation units different.
 Its still a small overall effect size, but it has a clearer interpretation now.
 We can again calculate PI's and $I^2$ using the model.
-Overall, our prediction intervals suggest that heterogenity is still high even after accounting for dosage reflected also in our $I_{total}^2$ estimate of `r I2_nuisance2[1]*100`\% --  95\% of the time we expect the mean in repeated samples to fall between `r pis_nuisance2$pi.lb[1]` to `r pis_nuisance2$pi.ub[1]` when the average dosage difference applied is `r mean(data_CS2$total_dose_T, na.rm = TRUE)` uL.
+Overall, our prediction intervals suggest that heterogenity is still high even after accounting for dosage reflected also in our $I_{total}^2$ estimate of `r I2_nuisance2[1]*100`\% --  95\% of the time we expect the mean in repeated samples to fall between `r pis_nuisance2$pi.lb[1]` to `r pis_nuisance2$pi.ub[1]` when the average dosage difference applied is `r mean(data_CS2$total_dose_T, na.rm = TRUE)` ng/yolk.
+Notably, the prediction interval after modelling the nuisance heterogeneity shrink.
+
+An alternative formulation of the dosage effect could be used taking into account the fact that absolute dose may not reflect each dose's biological effect - the latter will likely depend on the original, natural concentration of the hormone, and how much it is modified by the experiment.
+The below model uses the alternative dosage formulation.
+
+```{r}
+# Model that re-calibrates the overall meta-analytic mean (Intercept) to control for dosage
+# administration but uses centered dosage (expressed as the fraction of natural hormone concentration)
+data_CS2 <- data_CS2 %>% filter(!is.na(z_total_dose_p_T))
+model_CS2_nuisance3 <- metafor::rma.mv(d ~ z_total_dose_p_T, V = var_d,
+                                       method="REML",
+                                       random = list(~1|ID, ~1|paper, ~1|species_lat),
+                                       test = "t", dfs = "contain", data = data_CS2)
+print(model_CS2_nuisance3)
+
+# Calculate Prediction Intervals
+pis_nuisance3 <- predict(model_CS2_nuisance3, newmods = 0)
+print(pis_nuisance3)
+# Calculate I2 as well
+I2_nuisance3 <- orchaRd::i2_ml(model_CS2_nuisance3)
+print(I2_nuisance3)
+```
+
+Follow-up steps could include expanding the model to comprise both hormone types (testosterone and corticosterone), modelling their impact using a categorical predictor (`hormone1`) and also possibly interacting the dosage effect with the type of hormone applied.
+
+```{r}
+data_CS2b <- data_CS2_all %>% mutate(z_total_dose = scale(total_dose, center = TRUE, scale = FALSE)) %>% filter(!is.na(z_total_dose))
+# Model that re-calibrates the overall meta-analytic mean (Intercept) to control for dosage
+# administration but uses centered dosage
+model_CS2_nuisance4 <- metafor::rma.mv(d ~ hormone1 * z_total_dose, V = var_d,
+                                       method="REML",
+                                       random = list(~1|ID, ~1|paper, ~1|species_lat),
+                                       test = "t", dfs = "contain", data = data_CS2b)
+print(model_CS2_nuisance4)
+
+```
 
@@
 
-img1 <- readPNG("../figs/PRISMA_diagram_v0.png")
+img1 <- readPNG(here::here("figs", "PRISMA_diagram_v0.png"))
 
@@
 
-table <- read.csv("../tables/Table_S1.csv")
+table <- read.csv(here::here("tables","Table_S1.csv"))
 
@@
 
-table <- read.csv("../tables/Table_S2.csv")
+table <- read.csv(here::here("tables","Table_S2.csv"))
 

### 2021-07-22 supp.Rmd
Corrected ARR code

--- 2021-07-22 MS/supp.Rmd
@@
 data_CS1a<-data_CS1a %>% 
-              mutate(ARR=(mean_high_f-mean_low_f)/(acc_temp_high - acc_temp_low),
-                     Var_ARR=((1/(acc_temp_high-acc_temp_low))^2*(sd_low_f^2/n_low_f_adj+sd_high_f^2/n_high_f_adj)))
+              mutate(ARR=(mean_high-mean_low)/(acc_temp_high - acc_temp_low),
+                     Var_ARR=((1/(acc_temp_high-acc_temp_low))^2*(sd_low^2/n_low_adj+sd_high^2/n_high_adj)))
 
@@
 ```{r, class.source='klippy', results = 'hide'}
-data_CS1b<-data_CS1b %>% # calculate effect sizes
 
-  mutate(ARR_f=((mean_high_f-mean_low_f)/(acc_temp_high-acc_temp_low))) %>% 
-  mutate(ARR_m=((mean_high_m-mean_low_m)/(acc_temp_high-acc_temp_low))) %>% 
-  mutate(ARRD=ARR_f - ARR_m) %>% 
-  mutate(Var_ARRD=((1/(acc_temp_high-acc_temp_low))^2*(sd_low_f^2/n_low_f_adj+sd_high_f^2/n_high_f_adj+sd_low_m^2/n_low_m_adj+sd_high_m^2/n_high_m_adj)))
+# calculate effect sizes
+data_CS1b<-data_CS1b %>% 
+  mutate(ARR_f=((mean_high_f-mean_low_f)/(acc_temp_high-acc_temp_low)),
+         ARR_m=((mean_high_m-mean_low_m)/(acc_temp_high-acc_temp_low)),
+         ARRD= ARR_f - ARR_m,
+         Var_ARRD=((1/(acc_temp_high-acc_temp_low))^2*(sd_low_f^2/n_low_f_adj+sd_high_f^2/n_high_f_adj+sd_low_m^2/n_low_m_adj+sd_high_m^2/n_high_m_adj)))
 
 # Remove dependent effect sizes
-data_CS1b<-filter(data_CS1b,
+data_CS1b <- filter(data_CS1b,
                     es_ID!="es85"&

### 2021-07-23 supp.Rmd
Added survey panels to supplement

@@
 ---
-title: "Supplemental Materials for: Meta-analytic approaches and new effect sizes to account for heterogeneous effects in comparative physiology"
+title: "Supplemental Materials for: Meta-analytic approaches and effect sizes to account for ‘nuisance heterogeneity’ in comparative physiology"
 author: Daniel W.A. Noble, Patrice Pottier, Samantha Burke, Szymon M. Drobniak, Malgorzata Lagisz, Rose E. O’Dea, Shinichi Nakagawa
 date: "`r Sys.Date()`"
-bibliography: ../bib/refs.bib
-csl: ../bib/the-journal-of-experimental-biology.csl
+bibliography: ./bib/refs.bib
+csl: ./bib/the-journal-of-experimental-biology.csl
 output: 
@@
 Daniel W.A.
-Noble, Patrice Pottier, Sammantha Burke, Szymon M.
-Drobniak, Malgorzata Lagisz, Rose E.
-O’Dea, Shinichi Nakagawa (2022) *Meta-analytic approaches and "new" effect sizes to account for heterogeneous effects in comparative physiology*.
+Noble, Patrice Pottier, Malgorzata Lagisz, Samantha Burke, Szymon M.
+Drobniak, Rose E.
+O’Dea, Shinichi Nakagawa (2022) *Meta-analytic approaches and effect sizes to account for ‘nuisance heterogeneity’ in comparative physiology*.
 **Journal of Experimental Biology**
@@
 
-In this supplement we will demonstrate some of the principles we describe in our review paper.
+In this supplement, we will demonstrate some of the principles we describe in our review paper.
 We'll show readers ways they can apply some of the 'new' effect sizes we describe to account for 'nuisance heterogeneity' in combination with multilevel meta-analytic models (MLMA) and/or multilevel meta-regression models.
@@
 
-Before embarking on the case studies readers will need to load the necessary R packages.
+Before embarking on the case studies, readers will need to load the necessary R packages.
 Note that the first two lines are commented out.
@@
 
-# Case Study 1: Multilevel meta-analysis approaches to control for differences in treatment magnitude
+# Case Study 1: Multilevel Meta-analysis Approaches to Control for Nuisance Heterogeneity at the Effect Size Level
 
-Here, we will demonstrate how to use analyse variation in slopes and differences in slopes between two groups.
+Here, we will demonstrate how to analyse variation and differences in slopes between two groups.
 In this example, we will account for effects of known drivers of 'nuisance heterogeneity' at the level of the effect size.
@@
 
-## Multilvel meta-analysis of slopes
+## Multilevel Meta-analysis of Slopes
 
-We first download the data from OSF, and load this into R. You can do this by copying and pasting the code below.
+We first download the data from OSF and load this into R. You can do this by copying and pasting the code below.
 
@@
 In this section, we demonstrate how to calculate slope effect sizes and their associated sampling variance.
-Note that calculating slopes require the response variable to be measured with the same unit and does not apply to all meta-analyses.
-While this example focuses on thermal tolerance, the meta-analysis of slope may also be applicable to investigate changes in thermal preference, or metabolic scaling for example.
+Note that calculating slopes requires the response variable to be measured with the same unit and does not apply to all meta-analyses.
+While this example focuses on thermal tolerance, the meta-analysis of slope may also be applicable to investigate changes in thermal preference or metabolic scaling, for example.
 
 In this example, we use a simplified data set from Pottier et al.
-*in review* and we demonstrate how to investigate the mean effect of acclimation temperature on heat tolerance.
+*in review*, and we demonstrate how to investigate the mean effect of acclimation temperature on heat tolerance.
 Because heat tolerance was consistently measured in degrees Celsius (`CTmax`) in the studies compiled, we can calculate the slope between acclimation temperature and heat tolerance, which is termed as the acclimation response ratio (`ARR`) in the literature.
 This effect size is calculated as the difference between the heat tolerance at the higher (`mean_high`) and the lower (`mean_low`) acclimation temperatures, divided by the difference between acclimation temperatures (`acc_temp_high` - `acc_temp_low`).
-The sampling variance of the slope (`Var_ARR`) can then be defined using properties of variance as per 'formula XXX`
+The sampling variance of the slope (`Var_ARR`) can then be defined using properties of variance as per Box 1 in the main manuscript.
 
@@
 Note that it is possible to assess the variation due to phylogenetic relatedness but we will keep it simple for demonstration purposes.
-We also did not assessed variation due to between-study differences because the levels of this variable was almost entirely overlapping with `species_ID` (i.e.
+We also did not assess variation due to between-study differences because the levels of this variable were almost entirely overlapping with `species_ID` (i.e.
 `species_ID` and `study_ID` were indistinguishable).
+
 While we only present  an intercept-only model, this structure can be used to fit meta-regressions by fitting moderator variables.
@@
 In other words, for each degree variation in acclimation temperature, the heat tolerance of the animals included in this data set vary by `r coef(model_CS1a_MLMA)` degrees on average.
-95\% of the time we expect the mean in repeated samples to fall between `r PI_CS1a_MLMA$cr.lb` to `r PI_CS1a_MLMA$cr.ub`.
-Our prediction intervals suggest that heterogeneity is high, reflected also in our $I_{total}^2$ estimate of `r I2_CS1a[1]*100`\%.
-Approximately, `r I2_CS1a[2]*100`\% of the total heterogeneity is the result of differences between species and `r I2_CS1a[3]*100`\% of the total heterogeneity is associated with the residuals.
+95\% of the time we expect the mean in repeated samples to fall between `r PI_CS1a_MLMA$cr.lb` and `r PI_CS1a_MLMA$cr.ub`.
+Our prediction intervals suggest that heterogeneity is high, reflected in our $I_{total}^2$ estimate of `r I2_CS1a[1]*100`\%.
+Approximately, `r I2_CS1a[2]*100`\% of the total heterogeneity is the result of differences between species, and `r I2_CS1a[3]*100`\% of the total heterogeneity is associated with the residuals.
 With this effect size (slope), the 'nuisance heterogeneity' is accounted for, to some extent, at the level of the effect size.
@@
 In this example, we demonstrate how to derive and analyse effect sizes when investigating differences in slopes.
-As per the previous example, such analysis require responses variables to be measured with the same unit.
+As per the previous example, such analysis requires response variables to be measured with the same unit.
 We use the same data set as before, but formatted in a slightly different way (i.e.
@@
 We can then use the mean difference between `ARR_f` and `ARR_m` as an effect size, which we term here as `ARRD`. 
-The sampling variance was then calculated as per `formula XXX`
+The sampling variance was then calculated as per Box 1 in the main manuscript.
 
@@
 Note that the confidence intervals overlap with zero, which indicates that the difference between females and males is small, and not statistically significant.
-95\% of the time we expect the mean in repeated samples to fall between `r PI_CS1b_MLMA$cr.lb` to `r PI_CS1b_MLMA$cr.ub`.
-Our prediction intervals suggest that heterogeneity is small to moderate, reflected also in our $I_{total}^2$ estimate of `r I2_CS1b[1]*100`\%.
-Approximately, `r I2_CS1b[2]*100`\% of the total heterogeneity is the result of differences between species and `r I2_CS1b[3]*100`\% of the total heterogeneity is associated with the residuals.
+95\% of the time, we expect the mean in repeated samples to fall between `r PI_CS1b_MLMA$cr.lb` and `r PI_CS1b_MLMA$cr.ub`.
+Our prediction intervals suggest that heterogeneity is small to moderate, reflected in our $I_{total}^2$ estimate of `r I2_CS1b[1]*100`\%.
+Approximately, `r I2_CS1b[2]*100`\% of the total heterogeneity is the result of differences between species, and `r I2_CS1b[3]*100`\% of the total heterogeneity is associated with the residuals.
 
@@
 
-In the next case study we'll demonstrate how to use multilevel meta-regression models to correct overall meta-analytic means for dosage differences applied across studies.
+In the next case study we'll demonstrate how to use multilevel meta-regression models to correct the overall meta-analytic mean for dosage differences applied across studies.
 The data in question was collected by @Podmola2018.
 The meta-analysis reviewed published studies reporting the outcomes of experiments that manipulated levels of steroid hormones (testosterone and corticosterone) and recorded the impact of such manipulations on offspring traits.
-The aim was to establish the generality and homogeneity of such experimental effects, and their dependence on several moderator variables, most importantly the type of measured ofspring traits, the type of hormone used, and several methodological factors (administration route, hormone vehicle, offspring developmental stage, etc.
+The aim was to establish the generality and homogeneity of such experimental effects, and their dependence on several moderator variables, most importantly the type of measured offspring traits, the type of hormone used, and several methodological factors (administration route, hormone vehicle, offspring developmental stage, etc.
 - for details please consult the original study).
@@
 
-We'll first download the data from OSF, and load this into R. You can do this by copying and pasting the code below.
+We'll first download the data from OSF and load this into R. You can do this by copying and pasting the code below.
 
@@
 The data contains two categorical moderator variables to be included in the model: `hormone1` - identifies the type of steroid hormone (*androgen* vs.
-*corticosterone*); `trait1` - the type of offpsring trait measured (physiology, behaviour, survival, reproduction).
-Random effects include study ID (`ID`), species ID (`species_lat`) and study ID (`paper`).
+*corticosterone*); `trait1` - the type of offspring trait measured (physiology, behaviour, survival, reproduction).
+Random effects include study / observation ID (`ID`), species ID (`species_lat`) and study ID (`paper`).
 
-The dosage variables are reported separately for each hormone in ng/yolk (`total_dose_T`, `total_dose_A4` & `total_dose_CORT`) and in fractions of natural per-yolk concentration (`total_dose_p_T`, etc.) The latter value is available only for studies that reported natural hormone concentrations (`T_yolk`, `A4_yolk`, `CORT_yolk`).
+The dosage variables are reported separately for each hormone in ng/g yolk (`total_dose_T`, `total_dose_A4` & `total_dose_CORT`) and in fractions of natural per-yolk concentration (`total_dose_p_T`, etc.) The latter value is available only for studies that reported natural hormone concentrations (`T_yolk`, `A4_yolk`, `CORT_yolk`).
 
@@
 # in dose so that models are fit with the exact same data.
-data_CS2 <- data_CS2_all %>% mutate(z_total_dose_T = scale(total_dose_T, center = TRUE, scale = FALSE),
-                     z_total_dose_p_T = scale(total_dose_p_T, center = TRUE, scale = FALSE)) %>% filter(!is.na(z_total_dose_T))
+data_CS2 <- data_CS2_all %>% 
+            mutate(z_total_dose_T = scale(total_dose_T, center = TRUE, scale = FALSE),
+                   z_total_dose_p_T = scale(total_dose_p_T, center = TRUE, scale = FALSE)) %>% 
+            filter(!is.na(z_total_dose_T))
 
@@
 
-We can see from above that the model 'ignoring' the nuisance heterogenity (`model_CS2_MLMA_1`) (i.e., the variability in effects resulting from dosage differences across studies) estimates an overall meta-analytic mean as `r coef(model_CS2_MLMA_1)` with a 95\% CI from `r model_CS2_MLMA_1$ci.lb` to `r model_CS2_MLMA_1$ci.ub`.
-Our prediction intervals suggest that heterogenity is high, reflected also in our $I_{total}^2$ estimate of `r I2_1[1]*100`\% -- 95\% of the time we expect the mean in repeated samples to fall between `r pis_MLMA_1$pi.lb` to `r pis_MLMA_1$pi.ub`.
-Approximately, `r I2_1[3]*100`\% of the total heterogenity is the result of differences between studies.
-Given that we have not controlled for dosage differences across studies all we can say is that the average SMD is rather small in the sample of studies that have applied these sets of dosages.
+We can see from above that the model 'ignoring' the nuisance heterogeneity (`model_CS2_MLMA_1`) (i.e., the variability in effects resulting from dosage differences across studies) estimates an overall meta-analytic mean as `r as.numeric(coef(model_CS2_MLMA_1))` with a 95\% CI from `r model_CS2_MLMA_1$ci.lb` to `r model_CS2_MLMA_1$ci.ub`.
+Our prediction intervals suggest that heterogeneity is high, reflected in our $I_{total}^2$ estimate of `r I2_1[1]*100`\% -- 95\% of the time we expect the mean in repeated samples to fall between `r pis_MLMA_1$pi.lb` and `r pis_MLMA_1$pi.ub`.
+Approximately `r I2_1[3]*100`\% of the total heterogeneity is the result of differences between studies.
+Given that we have not controlled for dosage differences across studies, all we can say is that the average SMD is rather small in the sample of studies that have applied these sets of dosages.
 In other words, on average, the means from the treatment and control groups differ by `r coef(model_CS2_MLMA_1)` standard deviation units.
 
-We can now model these dosage effects to control for 'nuisance heterogenity' and make the overall mean more interpretable.
+We can now model these dosage effects to control for 'nuisance heterogeneity' and make the overall mean more interpretable.
 We'll first start by fitting and interpreting the coefficient just for the raw total dosage applied in a given study.
@@
 
-We can see from our model that controls for nuisance heterogenity (model_CS2_nuisance1) that we now estimate an overall meta-analytic mean as `r coef(model_CS2_nuisance1)[1]` with a 95\% CI from `r model_CS2_nuisance1$ci.lb[1]` to `r model_CS2_nuisance1$ci.ub[1]`.
+We can see from our model that controls for nuisance heterogeneity (model_CS2_nuisance1) that we now estimate an overall meta-analytic mean as `r as.numeric(coef(model_CS2_nuisance1))[1]` with a 95\% CI from `r model_CS2_nuisance1$ci.lb[1]` to `r model_CS2_nuisance1$ci.ub[1]`.
 Importantly, this is the mean effect size when the total dosage applied is 0, which doesn't make much sense.
-As such, we can center total dosage applied to make the mean more 'meaningful' (mind the pun).
+We can center the total dosage applied to make the mean more 'meaningful' (mind the pun).
 
 ```{r}
-
 # Model that re-calibrates the overall meta-analytic mean (Intercept) to control for dosage
@@
 print(pis_nuisance2)
+
 # Calculate I2 as well
@@
 
-Now that we have centered the total dosage around its mean (which is `r mean(data_CS2$total_dose_T, na.rm = TRUE)` ng/yolk, our overall meta-analytic mean (now estimated to be `r coef(model_CS2_nuisance2)[1]`,  with a 95\% CI from `r model_CS2_nuisance2$ci.lb[1]` to `r model_CS2_nuisance2$ci.ub[1]`) is interpreted differently.
-Overall, the meta-analytic mean difference between treatments that differ by an average of `r mean(data_CS2$total_dose_T, na.rm = TRUE)` ng/yolk is `r coef(model_CS2_nuisance2)[1]` standard deviation units different.
+Now that we have centered the total dosage around its mean (which is `r mean(data_CS2$total_dose_T, na.rm = TRUE)` ng/ g yolk, our overall meta-analytic mean (now estimated to be `r coef(model_CS2_nuisance2)[1]`,  with a 95\% CI from `r model_CS2_nuisance2$ci.lb[1]` to `r model_CS2_nuisance2$ci.ub[1]`) is interpreted differently.
+Overall, the meta-analytic mean difference between treatments that differ by an average of `r mean(data_CS2$total_dose_T, na.rm = TRUE)` ng/ g yolk is `r coef(model_CS2_nuisance2)[1]` standard deviation units different.
 Its still a small overall effect size, but it has a clearer interpretation now.
 We can again calculate PI's and $I^2$ using the model.
-Overall, our prediction intervals suggest that heterogenity is still high even after accounting for dosage reflected also in our $I_{total}^2$ estimate of `r I2_nuisance2[1]*100`\% --  95\% of the time we expect the mean in repeated samples to fall between `r pis_nuisance2$pi.lb[1]` to `r pis_nuisance2$pi.ub[1]` when the average dosage difference applied is `r mean(data_CS2$total_dose_T, na.rm = TRUE)` ng/yolk.
+Overall, our prediction intervals suggest that heterogeneity is still high even after accounting for dosage reflected also in our $I_{total}^2$ estimate of `r I2_nuisance2[1]*100`\% --  95\% of the time we expect the mean in repeated samples to fall between `r pis_nuisance2$pi.lb[1]` to `r pis_nuisance2$pi.ub[1]` when the average dosage difference applied is `r mean(data_CS2$total_dose_T, na.rm = TRUE)` ng/ g yolk.
 Notably, the prediction interval after modelling the nuisance heterogeneity shrink.
 
-An alternative formulation of the dosage effect could be used taking into account the fact that absolute dose may not reflect each dose's biological effect - the latter will likely depend on the original, natural concentration of the hormone, and how much it is modified by the experiment.
-The below model uses the alternative dosage formulation.
+An alternative formulation of the dosage effect could take into account the fact that absolute dose may not reflect each dose's biological effect.
+In other words,the effect will likely depend on the original, natural concentration of the hormone, and how much it is modified by the experiment.
+The model below model uses this alternative dosage formulation.
 
@@
 
-# Supplementary Materials for Survey Study Selection
+# Supplementary Materials for Survey
 
+### Details on Study Selection
 Here we provide greater detail on the search strategy, keyword selection and the numbers of final studies included at each step pf the screening process for our survey.
@@
 
+## Additional Survey Results
+
+We collected data on additional questions about studies that maybe of use. Below, we present these results.
+
+```{r setup2, include=FALSE}
+rm(list=ls())
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+
+pacman::p_load(dplyr,ggplot2,here, pander, janitor, magrittr,ggalluvial,ggpubr)
+
+# loading data
+raw <- read.csv(here("data","MA_CompPysio_Survey.csv"))
+metadata <- read.csv(here("data","MA_CompPysio_Survey_metadata.csv"))
+
+# tidying data
+dat <- raw
+names(dat) <- metadata$Procesed.Column.Name[match(names(dat), metadata$Raw.Column.Name)]
+
+# tidying categorical options
+dat$meta_analysis_self_described <- factor(gsub(" \\(.*", "", dat$meta_analysis_self_described), levels = c("yes","no","unclear/other"))
+dat$comparative_physiology_main_focus <- factor(gsub(" \\(.*", "", dat$comparative_physiology_main_focus), levels = c("yes","no","unclear/other"))
+
+# fixing format of journals
+
+#dat$DOI[dat$journal=="2017"] # Typo
+dat$journal[dat$journal=="2017"] <- "Biology Letters"
+
+#dat$DOI[grep("Proceedings", dat$journal)] # all the same journal
+dat$journal[grep("Proceedings", dat$journal)] <- "Proceedings of the Royal Society B: Biological Sciences"
+
+# standardising DOI format
+dat$DOI <- gsub(".*org/", "", dat$DOI)
+dat$DOI <-gsub(".* ", "", dat$DOI)
+
+# ggplot2 theme for plots
+background.colour <- "white"
+text.colour <- "black"
+# Font Choice
+#loadfonts()
+text.font <- "Helvetica"
+line.width <- 0.6
+
+tm <- theme(panel.background = element_rect(fill = background.colour),
+            plot.background = element_rect(fill = background.colour),
+            panel.grid = element_blank(),
+            text =  element_text(family = text.font, colour = text.colour),
+            axis.text = element_text(colour = text.colour),
+            axis.title.x = element_text(margin = margin(10,0,0,0)),
+            axis.title.y = element_text(margin = margin(0,10,0,0)),
+            axis.line = element_line(colour = text.colour, size = line.width),,
+            axis.ticks = element_line(colour = text.colour, size = line.width),
+            plot.title = element_text(hjust = line.width),
+            legend.background = element_rect(fill = background.colour),
+            legend.key = element_rect(fill = background.colour),
+            plot.margin = margin(6,6,6,6))
+
+tm2 <- theme(panel.background = element_rect(fill = background.colour),
+            plot.background = element_rect(fill = background.colour),
+            panel.grid = element_blank(),
+            text =  element_text(family = text.font, colour = text.colour, size = 15),
+            axis.text = element_text(colour = text.colour),
+            axis.text.y = element_text(angle = 90, vjust = 0.5, hjust = 0.5),
+            axis.title.x = element_text(margin = margin(10,0,0,0)),
+            axis.title.y = element_text(margin = margin(0,10,0,0)),
+            axis.line = element_line(colour = text.colour, size = line.width),,
+            axis.ticks = element_line(colour = text.colour, size = line.width),
+            plot.title = element_text(hjust = line.width),
+            legend.background = element_rect(fill = background.colour),
+            legend.key = element_rect(fill = background.colour),
+            plot.margin = margin(15,15,15,15))
+```
+
+## Sample of `r nrow(dat)` papers {.tabset} 
+### Meta-analysis {.tabset .tabset-fade .tabset-pills}
+
+#### Self describing as a meta-analysis?
+Answer to the question "Is paper self-describing as containing a meta-analysis (or meta-regression) or actually using meta-analysis/regression approach?".
+
+```{r}
+dat %>% dplyr::group_by(meta_analysis_self_described) %>% dplyr::tally() %>% 
+  ggplot() + tm +
+  geom_col(aes(x = meta_analysis_self_described, y = n),
+           width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
+  scale_y_continuous(expand=c(0,0)) +
+  labs(x = "meta-analysis or meta-regression",
+       y = "number of papers") 
+```
+
+#### Comparative physiology {.tabset .tabset-fade .tabset-pills}
+
+Answer to the question "Is the study's main focus on comparative physiology?"
+
+- yes = focused only on physiological traits very clearly)  
+- no =  does have physiological traits, but is interested in broader questions involving many different traits
+
+```{r}
+dat %>% 
+  ggplot() + tm +
+  geom_bar(aes(x = comparative_physiology_main_focus,
+               fill = meta_analysis_self_described,
+               y = ..count../sum(..count..)), width = 0.5,
+           colour = text.colour, size = 0.5) +
+  scale_y_continuous(expand=c(0,0)) +
+  scale_fill_viridis_d() +
+  labs(x = "main focus on comparative physiology",
+       y = "number of papers",
+       fill = "meta-analysis") 
+```
+
+### Meta-analytic models {.tabset .tabset-fade .tabset-pills}
+
+Note that single papers can report more than one approach (e.g., use different effect sizes and different models).
+
+#### Effect sizes used
+
+```{r}
+dat %>% dplyr::group_by(effect_size_type) %>% janitor::tabyl(effect_size_type) %>%
+  dplyr::summarise(SMD = dplyr::if_else(grepl("SMD", effect_size_type), n, 0),
+                  lnRR = dplyr::if_else(grepl("Response Ratio", effect_size_type), n, 0),
+                    Zr = dplyr::if_else(grepl("correlation", effect_size_type), n, 0),
+                 Other = dplyr::if_else(grepl("other|Q10", effect_size_type), n, 0),
+                 Means = dplyr::if_else(grepl("mean/proportion/raw", effect_size_type), n, 0),
+                 lnCVR = dplyr::if_else(grepl("lnCVR", effect_size_type), n, 0),
+                 Slope = dplyr::if_else(grepl("slope", effect_size_type), n, 0)) %>% 
+  colSums(.) %>% data.frame(effect = names(.), n = .) %>% mutate(prop = n / sum(n)) %>% arrange(prop) %>% mutate(effect=factor(effect,levels=unique(effect))) %>% 
+  ggplot() + tm + theme(axis.title.y = element_blank(),
+                        axis.text.y = element_text(size=10)) +
+  geom_col(aes(x = effect, y = n), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
+  scale_y_continuous(expand=c(0,0),breaks=seq(1,20,2)) +
+  labs(x = "Effect Size",
+       y = "Number of Papers") +
+  coord_flip()
+```
+
+#### Statistical models used
+
+What statistical models were used?
+
+```{r}
+summary <-  dat %>% dplyr::group_by(stat_model_type) %>% janitor::tabyl(stat_model_type) %>%
+  dplyr::summarise(`Multilevel Meta-analysis Model` = dplyr::if_else(grepl("multilevel meta-analysis", stat_model_type), n, 0),
+                  `Multilevel Metaregression Model` = dplyr::if_else(grepl("meta-regression models", stat_model_type), n, 0),
+                    `Linear Regression` = dplyr::if_else(grepl("linear regression", stat_model_type), n, 0),
+                 Other = dplyr::if_else(grepl("unclear/other", stat_model_type), n, 0),
+                 `Vote Counting` = dplyr::if_else(grepl("vote counting", stat_model_type), n, 0),
+                 `Weighted Regression` = dplyr::if_else(grepl("weighted regression including mixed effects models", stat_model_type), n, 0),
+                 `Random Effects Model` = dplyr::if_else(grepl("random-effects meta-analysis", stat_model_type), n, 0)) %>% 
+  colSums(.) %>% data.frame(effect = names(.), n = .) %>% mutate(prop = (n / sum(n))) %>% arrange(prop) %>% mutate(effect=factor(effect,levels=unique(effect)))
+rownames(summary) <- NULL
+
+summary %>% 
+  ggplot() + tm + theme(axis.title.y = element_blank(),
+                        axis.text.y = element_text(size=10)) +
+  geom_col(aes(x = effect, y = prop), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
+  scale_y_continuous(expand=c(0,0),limits = c(0,0.4)) +
+  labs(title = "Analytical Approach",
+       y = "Frequency") +
+  coord_flip()
+```
+
+#### Weighted models?
+
+Were effect sizes used in the analysis weighted by sampling variance?
+
+```{r}
+dat %>%  janitor::tabyl(meta_analysis_weighted) %>% 
+  ggplot() + tm +  theme(axis.title.y = element_blank(),
+                        axis.text.y = element_text(size=10)) +
+  geom_col(aes(x = meta_analysis_weighted,  y = percent), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
+  scale_y_continuous(expand=c(0,0), limits = c(0,1)) +
+  labs(y = "Frequency") +
+  coord_flip()
+```
+
+How do the two categorisations (meta-analysis and weighting) combine?
+
+```{r}
+dat %>% 
+  ggplot() + tm +
+  geom_bar(aes(x = meta_analysis_self_described,
+               fill = meta_analysis_weighted,
+               y = ..count../sum(..count..)), width = 0.5,
+           colour = text.colour, size = 0.5) +
+  scale_y_continuous(expand=c(0,0), limits = c(0,1)) +
+  scale_fill_viridis_d() +
+  labs(x = "Meta-analysis?",
+       y = "Proportion",
+       fill = "Weighted?") 
+```
+
+### Heterogeneity {.tabset .tabset-fade .tabset-pills}
+
+#### Effect size impacted by 'nuisance heterogeneity'?
+
+Could effect size be impacted by an additional continuous predictor (e.g., temperature in thermal limit studies, dosage in hormone manipulation studies)?
+
+If "yes", does the study investigate any continuous environmental or methodological factors as moderators?
+
+```{r}
+dat %>% mutate(cont_moderator_variable_modelled = if_else(cont_moderator_variable_modelled == "", "N/A", cont_moderator_variable_modelled)) %>% 
+  ggplot() + tm +
+  geom_bar(aes(x = factor(cont_moderator_variable,levels=c("yes","no","unclear")),
+               fill = cont_moderator_variable_modelled,
+               y = ..count../sum(..count..)), width = 0.5,
+           colour = text.colour, size = 0.5) +
+  scale_y_continuous(expand=c(0,0), limits = c(0,1)) +
+  scale_fill_viridis_d() +
+  labs(x = "Nuisance Heterogeneity?",
+       y = "Proportion",
+       fill = "Modeled Nuisance\n Heterogeneity?") 
+```
+
+#### Reported Heterogeneity?
+
+Of the studies that are weighted how many actually reported measures of heterogeneity?
+
+```{r}
+dat %>%  filter(!heterogeneity_reported=="N/A (e.g.
+they conducted unweighted meta-analysis)") %>% mutate(heterogeneity_reported = if_else(heterogeneity_reported == "unclear/other (add comment)", "other", heterogeneity_reported)) %>% janitor::tabyl(heterogeneity_reported) %>% dplyr::arrange(-n) %>%
+  ggplot() + tm +
+  geom_col(aes(x = factor(heterogeneity_reported,levels=heterogeneity_reported), y = percent), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
+  scale_y_continuous(expand=c(0,0), limits = c(0,1)) +
+  labs(x = "Heterogeneity reported?",
+       y = "Frequency") 
+```
+
+### Non-independence and publication bias {.tabset .tabset-fade .tabset-pills}
+
+#### Handling sources of non-independence
+
+Did the analysis account for - or mention - additional non-independence arising from, e.g., phylogenetic relatedness or shared control treatments?
+The actual way of dealing with non-independence (n-i) will vary from study to study.
+
+```{r}
+dat %>%  janitor::tabyl(nonindependence_mentioned) %>% dplyr::arrange(n) %>% 
+  ggplot() + tm + theme(axis.title.y=element_blank(),
+                        axis.text.y = element_text(size=10)) +
+  geom_col(aes(x = factor(nonindependence_mentioned,levels=nonindependence_mentioned), y = percent), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
+  scale_y_continuous(expand=c(0,0), limits = c(0,1)) +
+  scale_x_discrete(labels = c('n-i dealt with w/o modelling', 'n-i modeled', 'unclear/other/not mentioned')) +
+  labs(title = "Non-independence handling",
+       y = "Frequency") +
+  coord_flip()
+```
+
+#### Publication bias
+
+What type of publication bias analysis was used in the analysis? Multiple metrics can be used per paper, hence frequencies won't sum to 100%.
+
+```{r}
+dat %>% dplyr::group_by(pub_bias_type) %>% janitor::tabyl(pub_bias_type) %>%
+  dplyr::summarise(GraphicalTest = dplyr::if_else(grepl("graphical tests", pub_bias_type), n, 0),
+                  RegressionTest = dplyr::if_else(grepl("regression test", pub_bias_type), n, 0),
+                    TrimAndFill = dplyr::if_else(grepl("trim-and-fill", pub_bias_type), n, 0),
+                 TimeLag = dplyr::if_else(grepl("time-lag", pub_bias_type), n, 0),
+                 OtherUnclear = dplyr::if_else(grepl("unclear", pub_bias_type), n, 0),
+                 None = dplyr::if_else(grepl("no", pub_bias_type), n, 0)) %>% 
+  colSums(.) %>% data.frame(effect = names(.), n = .) %>% mutate(prop = (n / sum(n)*100)) %>% arrange(n) %>% mutate(effect = factor(effect,levels=unique(effect))) %>% 
+  ggplot() + tm + theme(axis.title.y = element_blank(),
+                        axis.text.y = element_text(size=10)) +
+  geom_col(aes(x = effect, y = n), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
+  scale_y_continuous(expand=c(0,0),breaks=seq(1,30,2)) +
+  labs(x = "Effect Size",
+       y = "Number of Papers") +
+  coord_flip()
+```
+
+### Other plots {.tabset .tabset-fade .tabset-pills}
+
+```{r, message=FALSE, warning=FALSE}
+plot1 <- dat %>% 
+  ggplot() + tm2 + theme(legend.position = "top") +
+  geom_bar(aes(x = comparative_physiology_main_focus,
+               fill = cont_moderator_variable,
+               y = ..count../sum(..count..)), width = 0.5,
+           colour = NA, size = 0.5) +
+  scale_y_continuous(expand=c(0,0)) +
+  scale_fill_brewer(palette = "Set2") +
+  labs(x = "Main focus on comparative physiology",
+       y = "Frequency",
+       fill = "Continuous predictor present")
+plot1
+
+plot2 <- dat %>% 
+  ggplot() + tm2 + theme(legend.position = "top") +
+  geom_bar(aes(x = pub_year,
+               fill = meta_analysis_self_described,
+               y = ..count../sum(..count..)), width = 0.5,
+           colour = NA, size = 0.5) +
+  scale_y_continuous(expand=c(0,0)) +
+  scale_fill_brewer(palette = "Set2") +
+  labs(x = "Year of publication",
+       y = "Frequency",
+       fill = "Meta-analysis")
+plot2
+
+plot3 <- dat %>%
+  ggplot(mapping = aes(x = comparative_physiology_main_focus,
+               y = meta_analysis_self_described)) + tm2 +
+  theme(panel.border = element_rect(size = 0.5, fill = NA),
+        panel.grid.major = element_line(colour = "grey92"),
+        axis.text.y = element_text(angle = 90)) +
+  geom_count(mapping = aes(size = ..n.., colour = "A")) +
+  scale_size_continuous(range = c(20,40), guide = F) +
+  scale_colour_brewer(palette = "Set2", guide = F) +
+  # scale_y_continuous(expand=c(0,0)) +
+  # scale_fill_viridis_d() +
+  labs(x = "Main focus on comparative physiology?",
+       y = "Self described as a meta-analysis?")
+plot3
+
+plot4 <- dat %>%
+  ggplot(aes(axis1 = meta_analysis_self_described,
+             axis2 = comparative_physiology_main_focus,
+             axis3 = cont_moderator_variable)) +
+  ggalluvial::geom_alluvium(aes(fill = comparative_physiology_main_focus), width = 1/4, alpha = 0.8) +
+  tm2 + theme(axis.line = element_blank(), axis.ticks = element_blank()) +
+  theme(legend.position = "none", panel.grid = element_blank(), axis.text.y = element_blank()) +
+  scale_fill_brewer(palette = "Set2") +
+  ggalluvial::geom_stratum(fill = 'white', colour = 'black', width = 1/4) +
+  geom_text(stat = 'stratum',
+            aes(label = after_stat(stratum)),
+            # label = c('weighted', 'unweighted', 'unclear'),
+            colour = 'black') +
+  scale_x_discrete(expand = c(.1, .1), limits = c("Meta-analysis", "Comparative physiol.", "Cont. moderator"))
+plot4
+
+panels <- ggarrange(ggarrange(plot1, plot2, nrow = 1),
+                    ggarrange(plot3, plot4, nrow = 1, widths = c(1,2)),
+                    nrow = 2, ncol = 1)
+ggsave(panels, filename = "multipanel.pdf", device = "pdf")
+
+```
+
 # Session Information

### 2021-07-23 MS/ms.Rmd
Fixed up MS with sd comments

@@
 ---
-title: "Meta-analytic approaches and effect sizes to account for 'nuisance heterogenity' in comparative physiology"
+title: "Meta-analytic approaches and effect sizes to account for 'nuisance heterogeneity' in comparative physiology"
 bibliography: ../bib/refs.bib
@@
 Meta-analysis is always concerned with effect heterogeneity; in other words, the factors that drive differences in the direction and magnitude of effects within and across studies [@Nakagawa2017; @Gurevitch2018; @Cooperetal2019; @Borenstein2019].
-The concept of heterogeneity is vitally important because it tells us how general our findings are likely to be and how much of the variance we see is the result of real biology or methodological differences (not just sampling variance) [@Nakagawa2017; @Borenstein2019].
+The concept of heterogeneity is vitally important because it tells us how general our findings are likely to be and how much of the variance we see is the result of real biology or methodological differences (after meta-analytically accounting for sampling variance) [@Nakagawa2017; @Borenstein2019].
 
 There are many phenomena driving effect heterogeneity.
-First, there is inherent uncertainty in estimating the ‘true’ population effect (e.g., a correlation coefficeiont) from smaller samples [@Borenstein2019].
+First, there is inherent uncertainty in estimating the ‘true’ population effect (e.g., a correlation coefficient) from smaller samples [@Borenstein2019].
 A formal meta-analysis weights sample estimates by their precision, and removes this source of heterogeneity [@Gurevitch2018; @Koricheva2013].
@@
 As comparative physiologists, this is the stuff that gets us up every morning!
-We can model these biological factors to test predictions from hypotheses that we believe are key players impacting mean effect size and direction.
+We can model these biological factors by including relevant predictors (moderator variables) and/or random effects (to account for non-independence of effects).
+By doing so, we can test predictions from hypotheses that we believe are key players impacting mean effect size and direction.
 This improves our understanding of the biological world around us and helps inform on future research directions.
@@
 These might include differences in temperature, pH, dosages, water potential etc.
-While these factors are likely to have an impact on the magnitude of an effect, they might distract from the core interest of a meta-analysis.
-In some cases, however, the latter factors might actually not be 'nuisance' variables but the main interest of a synthesis.
-Regardless, in many cases they can result in a more complicated interpretation of an effect measure than what is desired.
+Regardless of the relative importance of such variables compared to core questions in a meta-analysis, nuisance variables may complicate the interpretation of effect sizes used if not accounted for properly.
 
@@
 If we are interested in generalising only to apples, then mixing fruit will not be ideal.
-However, if we want to understand why different 'fruit' vary in their effects, then we need to consider apples and oranges together [@Borenstein2019].
+However, if we want to understand why different 'fruit' vary in their properties, then we need to consider apples and oranges together [@Borenstein2019].
 
@@
 Doing so provides a rich set of conclusions that can draw attention to important sources of variability that might have otherwise been overlooked.
-Having said that, it is still very important to understand the limitations and diversity of studies included in a meta-analysis, and how this can affect interpretations made -- an important reason why transparency and reproducibility are such a prominent feature of meta-analysis (or ideally should be) [@ODea2021].
+Having said that, it is still very important to understand the limitations and diversity of studies included in a meta-analysis, and how this can affect interpretations made -- an important reason why transparency and reproducibility (or ideally should be) are such a prominent feature of meta-analysis [@ODea2021].
 The validity of general conclusions to certain questions (e.g., what is the overall effect of a pollutant on reproduction?) will inevitably depend on the homogeneity of effects being synthesized.
@@
 As such, we conducted a literature survey to better understand the different types of effect sizes being used in comparative physiology, their susceptibility to known sources of methodological / environmental variability across studies, and how these sources are controlled.
-After searching for meta-analyses and comparative analyses that tackled questions using physiological data compiled from animal studies across multiple species, we we asked: 1) what type of effect size was used within the quantitative synthesis?
-2) based on the methods provided, was the effect size likely susceptible to continuous variation in how treatments were applied (e.g., for contrast-based effects) or the conditions under which traits were measured (i.e., for correlations) across studies (i.e., 'nuisance heterogeneity')?
+After searching for meta-analyses and comparative analyses that tackled questions using physiological data compiled from animal studies across multiple species, we asked: 1) what type of effect size was used within the quantitative synthesis?
+2) based on the methods provided, was the effect size likely susceptible to nuisance heterogeneity?
 3) If so, was such variation accounted for in the effect size or during analysis?
@@
 Narrative reviews and comments were not considered because they did not collate quantitative data from the literature.
-Studies needed to have collected physiological trait data, such as hormones, thermal physiology (CTmax, CTmin, thermal preferences, thermal breadth, LT50, lethal thresholds), metabolic rates (routine, maximum, and minimum metabolic rate, aerobic scope), enzyme reaction rates and concentrations, oxidative stress and consequences (e.g., DNA damage, teleomere attrition), performance measurements (e.g., heart rates, sprint speed, swim speed, growth rates), body composition (e.g., fatty acid profiles) and immune traits (e.g., cell function, antibodies).
+Studies needed to have collected physiological trait data, such as hormone levels, thermal physiological parameters (CTmax, CTmin, thermal preferences, thermal breadth, LT50, lethal thresholds), metabolic rates (routine, maximum, and minimum metabolic rate, aerobic scope), enzyme reaction rates and concentrations, oxidative stress measures and consequences (e.g., DNA damage, teleomere attrition), performance measurements (e.g., heart rates, sprint speed, swim speed, growth rates), body composition (e.g., fatty acid profiles) and immune traits (e.g., cell function, antibodies).
 Studies were also included if they measured the relationship between physiological traits and body size (e.g., metabolic scaling), reproductive allocation, or survival across taxa.
@@
 For example, the magnitude of *lnRR* or *SMD* might depend on differences in the temperatures, dosages, pH, or water potential applied to each treatment.
-The same applies for modelling the means.
+The same applies to modelling the means.
 For example, standard metabolic rate (SMR) is temperature-dependent.
@@
 In Box 1 we provide readers with guidance on how comparative physiologists can apply corrections to the effect measure itself.
-We highlight two examples in the box focusing mainly on generality.
+We highlight two examples in Box 1 that can be easily generalized to alternative effect size measures and cases.
 Below, we show how we can formalise a traditional effect size, such as $lnRR$, to capture this ‘nuisance variation’ using a common, well understood effect measure of interest to comparative physiologists ($Q_{10}$).
 
-```{r, fig0, fig.cap="**Effect sizes from old to new**. We still need a legend..insert here?"}
+```{r, fig0, fig.cap="**Effect sizes from old to new**.
+Traditional effect sizes (top left) are somehow detached from more biologically relevant measures commonly used in comparative physiology (top right).
+By combining traditional effects with physiological parameters, and correcting the resulting quantities for nuisance parameters, we can derive a new generation of biologically relevant, easily interpretable effect measures for use in meta-analyses."}
 image <- image_read(here::here("figs", "Fig0_v1_ML.png"))
@@
 
-Assume that we are interested in understanding the overall effect of, say, corticosterone (CORT) on reproduction [e.g., see @Podmola2018].
-We might extract data from studies manipulating corticosterone in bird eggs.
-Of course, these studies are diverse, spanning many species and applying different dosages of corticosterone.
+Assume that we are interested in understanding the overall effect of, say, testosterone (T) on offspring traits [e.g., see @Podmola2018].
+We might extract data from studies manipulating T in bird eggs.
+Of course, these studies are diverse, spanning many species and applying different dosages of T.
 If the studies are experimental in nature, then a standardised effect size, such as $lnRR$ or *SMD*, might be applicable.
@@
 This is formalised in what we call 'heterogeneity analysis' which we describe below.
-Importantly, this model provides us with the answer to our question: across all the species and studies manipulating egg corticosterone, how much of an overall effect does corticosterone have on reproduction relative to control conditions?
+Importantly, this model provides us with the answer to our question: across all the species and studies manipulating egg T, how much of an overall effect does T have on offspring traits relative to control conditions?
 
-Of course, the overall effect does not provide us with a way to interpret its magnitude in the context of how much CORT has been applied in the treatments used in the sample of studies.
+Of course, the overall effect does not provide us with a way to interpret its magnitude in the context of how much T has been applied in the treatments used in the sample of studies.
 The most we can say about it is that the effect is small, moderate or large given the sample of effect sizes extracted from this set of studies.
@@
 By including these moderators in a meta-regression model, the interpretation of the overall meta-analytic mean, $\beta_{0}$, changes.
-For example, assume we collected the change in CORT dosage relative to a control group (i.e., in µL / g) for our meta-analysis on egg CORT effects on bird reproduction.
-If the untransformed dosage, $x_{j}$, is included in the model then the overall meta-analytic mean estimate, $\beta_{0}$, would be the mean effect of CORT on reproduction when the dosage difference between the treatment and control group is 0 µL /g.
+For example, assume we collected the change in *in ovo* testosterone dosage relative to a control group (i.e., in ng T / g yolk) for our meta-analysis on egg T effects on bird offspring traits in birds.
+If the untransformed dosage, $x_{j}$, is included in the model then the overall meta-analytic mean estimate, $\beta_{0}$, would be the mean effect of T on reproduction when the dosage difference between the treatment and control group is 0 ng T / g yolk (i.e., it would be reflective of unmanipulated eggs).
 Of course, this interpretation does not make much sense.
@@
 We can, however, apply some simple transformations to make the overall mean estimate more intuitive while also improving the interpretation of non-linear parameters and interactions estimated from the model [@Schielzeth2010; @GelmanHill2007].
-One simple transformation would be to centre the variable $x_{j}$ by subtracting each value from the mean to create a new input variable (i.e., $c_{i}=x_{i}-\bar{x}$, where the subscript *i* denotes each individual effect size dosage).
+One simple transformation would be to centre the variable $x_{j}$ by subtracting each value from the mean to create a new input variable (i.e., $c_{j}=x_{j}-\bar{x}$, where the subscript *j* denotes each individual effect size dosage).
 The new variable, $c_{j}$, is now centered on the mean and can replace $x_{j}$ in the meta-regression model.
 When the model is refit with $c_{j}$, the estimated $\beta_{0}$ can now be more intuitively interpreted as the overall mean effect of CORT on reproduction at an average dosage difference between treatment and control groups.
-Importantly, by centering, we retain the original units (µL / g) of the variable, which can be very useful to ease the interpretation of the effect magnitude (e.g., when the dosage difference is 10 µL /g).
+Importantly, by centering, we retain the original units (ng T / g yolk) of the variable, which can be very useful to ease the interpretation of the effect magnitude (e.g., when the dosage difference is 10 ng T / g yolk).
 Given it is very common to estimate and compare overall meta-analytic means (i.e., $B_{0}$) in meta-analyses, this centering can be particularly useful in making these means more interpretable.
@@
 
-Centering moderator variables, like temperature and dosage, not only provides a way to make the overall mean effect more interpretable in the face of treatment heterogeneity, but it also allows more complex relationships to be fit without compromising interpretations, such as when one includes non-linear parameters (e.g., polynomials) and interactions with other variables.
+Centering moderator variables, like temperature and dosage, not only provides a way to make the overall mean effect more interpretable in the face of treatment heterogeneity, but it also allows more complex relationships to be fit without compromising interpretations, such as when one includes non-linear parameters (e.g., higher-order polynomials) and interactions with other variables.
 In other words, linear / main effects can still be interpreted normally in the presence of non-linear / interactions fit in the model [@Schielzeth2010; @GelmanHill2007].
@@
 
-#### *Heterogeneity Analysis: How Much Effect Size Variation Actually Exists?*
+#### *Heterogeneity Analysis: How Much Nuisance Heterogeneity Actually Exists?*
 
@@
 We would also like to thank Megan Head for comments on a previous draft.
-DWAN, SN, ML and REO were supported by ARC Discovery Projects (DP210101152 to DWAN and DP200100367 to SN, ML and DWAN).
+DWAN, SMD, SN, ML and REO were supported by ARC Discovery Projects (DP210101152 to DWAN, DE180100202 to SMD, and DP200100367 to SN, ML and DWAN).
 PP and SB were supported by a UNSW Scientia PhD Scholarship.

### 2021-07-23 supp.Rmd
Fixed naming of axes in places so consistent

@@
 In this supplement, we will demonstrate some of the principles we describe in our review paper.
-We'll show readers ways they can apply some of the 'new' effect sizes we describe to account for 'nuisance heterogeneity' in combination with multilevel meta-analytic models (MLMA) and/or multilevel meta-regression models.
-We realise that 'nuisance heterogeneity' may be a misnomer in some senses because such forms of heterogeneity may actually be the main interest of a given meta-analysis; in which case, multilevel meta-regressions are the way to go!
+We'll show readers ways they can apply some of the 'new' effect sizes we describe to account for nuisance heterogeneity in combination with multilevel meta-analytic models (MLMA) and/or multilevel meta-regression models.
+We realise that nuisance heterogeneity may be a misnomer in some senses because such forms of heterogeneity may actually be the main interest of a given meta-analysis; in which case, multilevel meta-regressions are the way to go!
 
@@
 We then show readers how to interpret this mean and associated heterogeneity.
-In the second case study, we use a common effect size metric and instead model the 'nuisance' heterogeneity using a multi-level meta-regression approach.
+In the second case study, we use a common effect size metric and instead model the nuisance heterogeneity using a multi-level meta-regression approach.
 We also focus on showing readers how to interpret effects from this model along with heterogeneity.
@@
 Here, we will demonstrate how to analyse variation and differences in slopes between two groups.
-In this example, we will account for effects of known drivers of 'nuisance heterogeneity' at the level of the effect size.
+In this example, we will account for effects of known drivers of nuisance heterogeneity at the level of the effect size.
 We use a case study by Pottier et al.
@@
 Approximately, `r I2_CS1a[2]*100`\% of the total heterogeneity is the result of differences between species, and `r I2_CS1a[3]*100`\% of the total heterogeneity is associated with the residuals.
-With this effect size (slope), the 'nuisance heterogeneity' is accounted for, to some extent, at the level of the effect size.
+With this effect size (slope), the nuisance heterogeneity is accounted for, to some extent, at the level of the effect size.
 
@@
 
-We can now model these dosage effects to control for 'nuisance heterogeneity' and make the overall mean more interpretable.
+We can now model these dosage effects to control for nuisance heterogeneity and make the overall mean more interpretable.
 We'll first start by fitting and interpreting the coefficient just for the raw total dosage applied in a given study.
@@
   scale_fill_viridis_d() +
-  labs(x = "main focus on comparative physiology",
-       y = "number of papers",
-       fill = "meta-analysis") 
+  labs(x = "Main focus on comparative physiology?",
+       y = "Frequency",
+       fill = "Meta-analysis") 
 ```
@@
   labs(x = "Nuisance Heterogeneity?",
-       y = "Proportion",
+       y = "Frequency",
        fill = "Modeled Nuisance\n Heterogeneity?") 

### 2021-07-23 MS/box.Rmd
szd fixes to box

@@
 temperature of 24 and 30 \&degC).
-Finally, we introduce a useful approximation technique known as 'the delta method'.
+Finally, we introduce a useful approximation technique known as 'the Delta method'.
 The sampling variances associated with these 'new' effect sizes below will allow comparative physiologists to take advantage of powerful meta-analytic models.
@@
 To obtain the sampling variance for this equation (slope), we first need to describe some basic properties of variance.
-Let's assume $M_{1}$ is a random variable, which means that this variable has a mean and standard deviation [note that this standard deviation is not the 'sample' but the 'sampling' standard deviation, which is often referred to as standard error - see Figure 1 in @Nakagawa2021b].
-Multiplying a constant ($a$) will change the variance by the square of that constant ($a^2$) while adding or subtracting the constant ($b$) does not change the variance of $M_{1}$.
+Let's assume $M_{1}$ is a random variable drawn from a distribution that can be characterised by a mean and standard deviation [note that this standard deviation is not the 'sample' but the 'sampling' standard deviation, which is often referred to as standard error - see Figure 1 in @Nakagawa2021b].
+Multiplying it by a constant ($a$) will change the variance by the square of that constant ($a^2$) while adding or subtracting the constant ($b$) does not change the variance of $M_{1}$.
 This can be summarized as:
@@
 
-Also, when adding two random variables ($M_{1}$ and $M_{2}$), the combined variance is the sum of the variance of $X_{1}$ and the variance of $X_{2}$ plus 2 times the covariance between $M_{1}$ and $M_{2}$.
+Also, when adding two random variables ($M_{1}$ and $M_{2}$), the combined variance is the sum of the variance of $M_{1}$ and the variance of $M_{2}$ plus 2 times the covariance between $M_{1}$ and $M_{2}$.
 This relationship can be written as:
@@
 
-where the co-variance $\text{Cov}(M_1,M_2)$ equals to the correlation multiplied by the square-root of the two variances $2\text{Cor}(M_1,M_2)\sqrt{ \sigma^2_{M_1} \sigma^2_{M_2} }$.
+where the co-variance $\text{Cov}(M_1,M_2)$ equals to the correlation multiplied by the square-root of the product of two variances $2\text{Cor}(M_1,M_2)\sqrt{ \sigma^2_{M_1} \sigma^2_{M_2} }$.
 
@@
 Let us explain further.
-The (sampling) standard error for $X_{1}$ is $SE_{1} = SD_{1} / \sqrt{N_{1}}$.
-Given this, the sampling variance for $X_{1}$ is $SD^2_{1} / N_{1}$, and the sampling variance for $X_{2}$ is $SD^2_{2} / N_{2}$.
+The (sampling) standard error for $M_{1}$ is $SE_{1} = SD_{1} / \sqrt{N_{1}}$.
+Given this, the sampling variance for $M_{1}$ is $SD^2_{1} / N_{1}$, and the sampling variance for $M_{2}$ is $SD^2_{2} / N_{2}$.
 You can see those elements of the sampling variance of *ARR* in the formula above.
@@
 
-By assuming the number of organisms (*N*) are the same at the two temperatures, we can slightly simplify this formula:
+By assuming the numbers of organisms (*N*) are the same at the two temperatures, we can slightly simplify this formula:
 
@@
 
-Now let us assume that we want to know the difference between two different *ARR* values: female *ARR*, $\text{ARR}_{f}$ and male *ARR*, $\text{ARR}_{m}$. Such a difference (*ARRD*) can be written as:
+Now let us assume that we want to know the difference between two different *ARR* values: e.g., female *ARR*, $\text{ARR}_{f}$ and male *ARR*, $\text{ARR}_{m}$.
+Such a difference (*ARRD*) can be written as:
 
@@
 These formulas can also be applied to changes in other factors (e.g., salinity, pH, oxygen) by changing the temperature constant.
+Also, our calculation can easily account for methodological inconsistencies.
 For example, it may be possible that males and females were measured in slightly different temperatures; say females at $T_3$ and $T_4$ ($T_4 > T_3$) and male at $T_5$ and $T_6$ ($T_6 > T_5$) like below:
@@
 
-### Controlling for unitary differences and temperature across studies
+### Controlling for unit differences and temperature across studies
 
@@
 
-Here we can see that the difference between $M_1$ and $M_2$ is standardised by the pooled SD, essentially correcting for unitary differences.
-Additionally, dividing SMD by the temperature difference results in further correcting the effect size by temperature.
+Here we can see that the difference between $M_1$ and $M_2$ is standardised by the pooled SD, essentially correcting for differences in measurement units.
+Additionally, dividing *SMD* by the temperature difference results in further correcting the effect size by the applied temperature difference.
 To derive the sampling variance for $SMD_T$ we can apply the same principle as we did above to derive a sampling variance as:
@@
 $$
-\text{Var}(f(M_1)) \approx \text{Var}(M_1)* \left( 
-f'(M_1)
+\text{Var}(f(X)) \approx \text{Var}(X)* \left( 
+f'(X)
 \right)^2,
@@
 
-where $f(M_1)$ represents the function of the random variable $M_1$, and importantly, $f'(M_1)$ is the first derivative of $f(M_1)$.
+where $f(X)$ represents the function of the random variable $X$, and importantly, $f'(X)$ is the first derivative of $f(X)$.
 Let's demonstrate this with a concrete example by re-deriving the sampling variance for $\ln{RR}$ defined as:

### 2021-07-25 MS/ms.Rmd
Fixed up comments from Shin

@@
 Despite this ambition, research designs in the field of comparative physiology can appear, at the outset, as being vastly different to each other because of 'nuisance heterogeneity' (e.g., different temperatures or treatment dosages used across studies).
-Methodological differences across studies has led many to believe that meta-analysis is an exercise in comparing "apples with oranges".
+Methodological differences across studies have led many to believe that meta-analysis is an exercise in comparing "apples with oranges".
 Here, we dispel this myth by showing how standardised effects sizes can be used in conjunction with multilevel meta-regression models to both account for the factors driving differences across studies and make them more comparable.
@@
 ```{r tablea, echo = FALSE, tab.cap = "Common effect sizes used throughout meta-analyses in comparative physiology, their associated sampling variances and examples on when they might be used.
-M: mean; SD: standard deviation; N: sample size; CTmin: critical thermal minimum; CTmax: critical thermal maximum; BPA: bisphenol A."}
+M: mean; SD: standard deviation; N: sample size; CTmin: critical thermal minimum; CTmax: critical thermal maximum; LC_50: median lethal concentration; LT_50: median lethal temperature; BPA: bisphenol A."}
 
@@
 # Maybe add some examples for each effect size in a new column. SHould help
-eg <- c("CTmin, CTmax, Metabolic Rate (MR)",
+eg <- c("CTmin, CTmax, LC50, LT50, Metabolic Rate (MR)",
         "Variability in CTmin, CTmax, Metabolic Rate (MR)",
@@
 While we could model this explicitly, this may not always be desirable.
-It can often be useful to standardise the effect to both ease its interpretation and simplify modelling (Figure \@ref(fig:fig0)).
-In Box 1 we provide readers with guidance on how comparative physiologists can apply corrections to the effect measure itself.
+It can often be useful to standardise the effect to both ease its interpretation and simplify modelling.
+In Box 1, we provide readers with guidance on how comparative physiologists can apply corrections to the effect measure itself.
 We highlight two examples in Box 1 that can be easily generalized to alternative effect size measures and cases.
 Below, we show how we can formalise a traditional effect size, such as $lnRR$, to capture this ‘nuisance variation’ using a common, well understood effect measure of interest to comparative physiologists ($Q_{10}$).
+Figure \@ref(fig:fig0) summarises different effect sizes that we mention in Table 1, Box 1 and the section below.
 
 ```{r, fig0, fig.cap="**Effect sizes from old to new**.
-Traditional effect sizes (top left) are somehow detached from more biologically relevant measures commonly used in comparative physiology (top right).
-By combining traditional effects with physiological parameters, and correcting the resulting quantities for nuisance parameters, we can derive a new generation of biologically relevant, easily interpretable effect measures for use in meta-analyses."}
+‘Traditional’ effect sizes (top left) are somehow detached from more biologically relevant measures commonly used in ‘Ccomparative physiology’ (top right) although statistical connections have always existed (‘Universal’; top middle).
+By combining traditional effects with physiological parameters, and correcting the resulting quantities for nuisance parameters, we can derive a new generation of biologically relevant, easily interpretable effect measures for use in meta-analyses (‘Expanded’; bottom).
+For abbreviations, see Table 1."}
 image <- image_read(here::here("figs", "Fig0_v1_ML.png"))
@@
 $$
+\begin{equation} 
 \begin{split}
@@
 \end{split}
+(\#eq:MLM)
+\end{equation} 
 $$
@@
 
-$$ Y_{i} = \beta_{0} + \sum \beta_{j}x_{j} + a_{k[i]} + sp_{k[i]} + s_{j[i]} + e_{i} + m_{i} $$
+$$ 
+\begin{equation} 
+Y_{i} = \beta_{0} + \sum \beta_{j}x_{j} + a_{k[i]} + sp_{k[i]} + s_{j[i]} + e_{i} + m_{i} \
+(\#eq:MLMR)
+\end{equation} 
+$$
 
@@
 Importantly, by centering, we retain the original units (ng T / g yolk) of the variable, which can be very useful to ease the interpretation of the effect magnitude (e.g., when the dosage difference is 10 ng T / g yolk).
-Given it is very common to estimate and compare overall meta-analytic means (i.e., $B_{0}$) in meta-analyses, this centering can be particularly useful in making these means more interpretable.
+Given it is very common to estimate and compare overall meta-analytic means (i.e., $\beta_{0}$) in meta-analyses, this centering can be particularly useful in making these means more interpretable.
 Mean centering can even be extended to include other 'nuisance' variables that might creep into the dataset; the same centering can be done with a second variable, and the overall mean adjusted and interpreted in the context of this new variable along with dosage.
@@
 $$ 
-I^2_{total} = \frac{\sigma^2_{study} + \sigma^2_{phylogeny} + \sigma^2_{species} + \sigma^2_{residual}}{\sigma^2_{study} + \sigma^2_{phylogeny} + \sigma^2_{species} + \sigma^2_{residual} +\sigma^2_{m}}
+\begin{equation}
+I^2_{total} = \frac{\sigma^2_{study} + \sigma^2_{phylogeny} + \sigma^2_{species} + \sigma^2_{residual}}{\sigma^2_{study} + \sigma^2_{phylogeny} + \sigma^2_{species} + \sigma^2_{residual} +\sigma^2_{m}} \
+(\#eq:itot)
+\end{equation}
 $$
 
-where $\sigma^2_{total} = \sigma^2_{study} + \sigma^2_{phylogeny} + \sigma^2_{species} + \sigma^2_{residual} +\sigma^2_{m}$ is the total effect size variance and $\sigma^2_{m}$ is the total sampling error variance calculated as:
+where $\sigma^2_{total} = \sigma^2_{study} + \sigma^2_{phylogeny} + \sigma^2_{species} + \sigma^2_{residual} +\sigma^2_{m}$ is the total effect size variance and $\sigma^2_{m}$ is the 'typical' sampling error variance calculated as:
 
 $$
-\sigma_{m}^2 = \sum w_{i}\left( k-1\right) / \left[ \left( \sum w_{i}\right)^2  + \sum w_{i}^2\right]
+\begin{equation}
+\sigma_{m}^2 = \sum w_{i}\left( k-1\right) / \left[ \left( \sum w_{i}\right)^2  + \sum w_{i}^2\right] \
+(\#eq:w)
+\end{equation}
 $$
@@
 
-$$ R^2_{marginal} = \frac{\sigma^2_{fixed}}{\sigma^2_{fixed} + \sigma^2_{study} + \sigma^2_{phylogeny} + \sigma^2_{species} + \sigma^2_{residual}}$$
+$$
+\begin{equation}
+R^2_{marginal} = \frac{\sigma^2_{fixed}}{\sigma^2_{fixed} + \sigma^2_{study} + \sigma^2_{phylogeny} + \sigma^2_{species} + \sigma^2_{residual}} \
+(\#eq:r2)
+\end{equation}
+$$
 
@@
 In addition, if we were to repeat a similar study, we would expect a new effect to fall within the range of 0.05 and 0.85, 95% of the time [@Borenstein2019; @Nakagawa2021c].
-This is a very intuitive interpretation of how variable effects are, yet PIs are often not reported in meta-analyses [@Nakagawa2021c], and we encourage more meta-analysts to report these.
+This is a very intuitive interpretation of how variable effects are, yet PIs are often not reported in meta-analyses [@Nakagawa2021c], and we encourage more meta-analysts to report these (for examples of PIs, see Supplementary Materials).
 
@@
 Comparative physiologists are interested in meta-analysing effects across a diversity of species, experimental designs, and environments.
-Importantly, sampling variances for many effect sizes commonly used by comparative physiologists (e.g., CTmax, $Q_{10}$ etc) can be formalised and powerful meta-analytic models can be easily applied to these effect measures.
+Importantly, sampling variances for many effect sizes commonly used by comparative physiologists (e.g., CTmax, $Q_{10}$ etc) can be formalized and powerful meta-analytic models can be easily applied to these effect measures (Figure \@ref(fig:fig0)).
 While an overall meta-analytic mean may be of interest, more often than not, understanding the drivers of effect size heterogeneity will be the primary interest.
@@
 Instead, comparative physiologists might simply want to focus on biological drivers of effect size variability and want an effect size or analytic approach that allows them to remove these ‘nuisances’.
-Here, we provide a set of tools to deal with ‘nuisance heterogeneity’ by reinventing standard effect sizes and/or using mean centered nuisance variables in meta-regression models.
+Here, we provide a set of tools to deal with ‘nuisance heterogeneity’ (Figure \@ref(fig:fig1))by reinventing standard effect sizes and/or using mean centered nuisance variables in meta-regression models.
 Estimating complex meta-regression models with a multitude of fixed effects might result, however, in more challenging model interpretation.

### 2021-07-25 MS/ms.Rmd
Read and fixed a few small things in MS

@@
 We formalise effect size measures (e.g., $Q_{10}$) that provide comparative physiologists with a means to remove nuisance heterogeneity without the need to resort to more complex statistical models that may be harder to interpret.
-We also describe more general approaches that can be applied to a variety of different contexts to derive new effects sizes and sampling variances opening up new possibilities.
+We also describe more general approaches that can be applied to a variety of different contexts to derive new effects sizes and sampling variances opening new possibilities.
 By using effect sizes that account for components of effect heterogeneity, in combination with existing meta-analytic models, comparative physiologists can explore exciting new questions and make results from large-scale data sets more accessible, comparable and widely interpretable.
@@
 
-Meta-analysis has emerged as the 'gold-standard' across various disciplines for quantitative synthesis and is increasingly prominent in the field of comparative physiology  [@Gurevitch2018; @Nakagawa2017; @Glass2015].
+Meta-analysis has emerged as the 'gold-standard' across various disciplines for quantitative synthesis and is becoming increasingly prominent in the field of comparative physiology  [@Gurevitch2018; @Nakagawa2017; @Glass2015].
 Meta-analyses answer research questions by synthesising research results and identifying sources of variation across studies [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Arnqvist1995; @Koricheva2013; @Borenstein2019].
@@
 A meta-analysis can have three goals: 1) to provide an overall mean estimate of a treatment effect or relationship, 2) to quantify effect size variance and understand key drivers explaining differences in effects across studies and 3) attempt to identify research gaps and publication biases [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Koricheva2013; @Borenstein2019].
-Meta-analysing independent studies provides greater statistical power and precision than what any individual study on its own would be able to provide - particularly given that most empirical studies are already under-powered in many areas of biology [@Forstmeier2017; @Jennions2003; @Button2013].
+Meta-analysing independent studies provides greater statistical power and precision than what any individual study on its own would be able to provide -- particularly given that most empirical studies are already under-powered in many areas of biology [@Forstmeier2017; @Jennions2003; @Button2013].
 By expressing study effects on a common scale (i.e., standardised effect size) we can gain broader insight into the direction and efficacy of a particular treatment effect or the strength of a relationship between two variables of interest [@Gurevitch2018; @Koricheva2013].
-Meta-analyses have already provided comparative physiologists with powerful insights on pressing global challenges - from testing whether physiological plasticity can buffer organisms against climate change [e.g, @Seebacher2015] to the degree to which endocrine disrupting chemicals, such as bis-phenol A (BPA), impact aquatic organisms [e.g., @WuSeebacher2020].
+Meta-analyses have already provided comparative physiologists with powerful insights on pressing global challenges -- from testing whether physiological plasticity can buffer organisms against climate change [e.g, @Seebacher2015] to the degree to which endocrine disrupting chemicals, such as bis-phenol A (BPA), impact aquatic organisms [e.g., @WuSeebacher2020].
 
@@
 The goal of our review is to briefly overview the meta-analytic process and argue for the value of heterogeneity in answering fundamental research problems and guiding research directions.
-We show how 'nuisance heterogeneity' in comparative physiology can be comfortably dealt with by re-formalising many existing effect size measures and / or by using multilevel meta-regression models.
-Then, we present results from a survey of published meta-analyses in the field of comparative physiology to gauge methodological and meta-analytic practices -- determining what types of effect sizes are commonly used, how often effect size estimates are impacted by nuisance heterogeneity and whether meta-analytic models (i.e., models that account for sampling variance) are commonly applied.
-We also formalise alternative effect sizes and their associated sampling variance to provide comparative physiologists with opportunities to explicitly incorporate 'nuisance heterogeneity' at the effect size level to ease their interpretation.
+We present results from a survey of published meta-analyses in the field of comparative physiology to gauge methodological and meta-analytic practices -- determining what types of effect sizes are commonly used, how often effect size estimates are impacted by nuisance heterogeneity and whether meta-analytic models (i.e., models that account for sampling variance) are commonly applied.
+Then, we show how 'nuisance heterogeneity' in comparative physiology can be comfortably dealt with by re-formalising many existing effect size measures and / or by using multilevel meta-regression models.
+We formalise alternative effect sizes and their associated sampling variance to provide comparative physiologists with opportunities to explicitly incorporate 'nuisance heterogeneity' at the effect size level to ease their interpretation.
 Finally, we describe how more complex treatment differences, such as non-linear dosage differences, can be accommodated using multilevel meta-regression models.
@@
 Doing so provides a rich set of conclusions that can draw attention to important sources of variability that might have otherwise been overlooked.
-Having said that, it is still very important to understand the limitations and diversity of studies included in a meta-analysis, and how this can affect interpretations made -- an important reason why transparency and reproducibility (or ideally should be) are such a prominent feature of meta-analysis [@ODea2021].
+Having said that, it is still very important to understand the limitations and diversity of studies included in a meta-analysis, and how this can affect interpretations made -- an important reason why transparency and reproducibility are such a prominent feature of meta-analysis (or ideally should be) [@ODea2021].
 The validity of general conclusions to certain questions (e.g., what is the overall effect of a pollutant on reproduction?) will inevitably depend on the homogeneity of effects being synthesized.
@@
 In many cases, studies make use of multiple effect size measures.
-Approximately `r with(hetero, hetero[cont_moderator_variable == "yes","percent"])*100`% of effect sizes used within the study we deemed to be impacted by 'nuisance heterogeneity' in some form or another (Figure \@ref(fig:figsurv)B), but of the studies where this was the case, only `r with(hetero_dealt, hetero_dealt[cont_moderator_variable_modelled == "yes","percent"])*100`% of the studies clearly dealt with it (Figure \@ref(fig:figsurv)B), often through meta-regression modelling.
+Approximately `r with(hetero, hetero[cont_moderator_variable == "yes","percent"])*100`% of effect sizes used within the study were deemed to be impacted by nuisance heterogeneity in some form or another (Figure \@ref(fig:figsurv)B), but of the studies where this was the case, only `r with(hetero_dealt, hetero_dealt[cont_moderator_variable_modelled == "yes","percent"])*100`% of the studies clearly dealt with it (Figure \@ref(fig:figsurv)B), often through meta-regression modelling.
 Overall, `r with(weighted, weighted[meta_analysis_weighted == "weighted model","percent"])*100`% of studies used a weighted meta-analytic model; however, of the studies self described as 'meta-analyses', `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","percent"])*100`% (N = `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","n"])` of `r with(weighted_meta, sum(weighted_meta[,"n"]))`) did not account for sampling variance.
@@
 
-```{r tablea, echo = FALSE, tab.cap = "Common effect sizes used throughout meta-analyses in comparative physiology, their associated sampling variances and examples on when they might be used.
+```{r tablea, echo = FALSE, tab.cap = "**Common effect sizes used throughout meta-analyses in comparative physiology, their associated sampling variances and examples on when they might be used**.
 M: mean; SD: standard deviation; N: sample size; CTmin: critical thermal minimum; CTmax: critical thermal maximum; LC_50: median lethal concentration; LT_50: median lethal temperature; BPA: bisphenol A."}
@@
                ref_symbols = c("a"),
-               part = "body", inline = TRUE)
+               part = "body", inline = TRUE) %>% 
+          flextable::font(part = "all", fontname = "Times New Roman")
 
@@
 
-As can be seen in Table \@ref(tab:tablea), none of the effect measures control for 'nuisance heterogeneity'.
+As can be seen in Table \@ref(tab:tablea), none of the effect measures control for nuisance heterogeneity.
 For example, the magnitude of *lnRR* or *SMD* might depend on differences in the temperatures, dosages, pH, or water potential applied to each treatment.
@@
 We highlight two examples in Box 1 that can be easily generalized to alternative effect size measures and cases.
-Below, we show how we can formalise a traditional effect size, such as $lnRR$, to capture this ‘nuisance variation’ using a common, well understood effect measure of interest to comparative physiologists ($Q_{10}$).
-Figure \@ref(fig:fig0) summarises different effect sizes that we mention in Table 1, Box 1 and the section below.
+Below, we show how we can formalise a traditional effect size, such as $lnRR$, to capture this nuisance variation using a common, well understood effect measure of interest to comparative physiologists ($Q_{10}$).
+Figure \@ref(fig:fig0) summarises the different effect sizes that we mention in Table 1, Box 1 and the section below.
 
 ```{r, fig0, fig.cap="**Effect sizes from old to new**.
-‘Traditional’ effect sizes (top left) are somehow detached from more biologically relevant measures commonly used in ‘Ccomparative physiology’ (top right) although statistical connections have always existed (‘Universal’; top middle).
-By combining traditional effects with physiological parameters, and correcting the resulting quantities for nuisance parameters, we can derive a new generation of biologically relevant, easily interpretable effect measures for use in meta-analyses (‘Expanded’; bottom).
+‘Traditional’ effect sizes (top left) are somehow detached from more biologically relevant measures commonly used in ‘Comparative physiology’ (top right) although statistical connections have always existed (‘Universal’; top middle).
+By combining traditional effects with physiological parameters, and correcting the resulting quantities for nuisance variation, we can derive a new generation of biologically relevant, easily interpretable effect measures for use in meta-analyses (‘Expanded’; bottom).
 For abbreviations, see Table 1."}
@@
 
-In equation \@ref(eq:lnRR), $M_{1}$ is the mean of group 1 (e.g., a control group), where as $M_{2}$ is the mean of group 2 (e.g., a treatment group).
+In equation \@ref(eq:lnRR), $M_{1}$ is the mean of group 1 (e.g., a control group), whereas $M_{2}$ is the mean of group 2 (e.g., a treatment group).
 The mean, $M_{i}$, for group *i* can be any measurement type (e.g.
 a physiological rate, mass etc) so long as the variable is measured on the ratio scale.
-Natural log transformation of this ratio makes the effect size normally distributed (a commonly assumed by meta-analytic models).
+Natural log transformation of this ratio makes the effect size normally distributed (as commonly assumed by meta-analytic models).
 Equation \@ref(eq:slnRR) is the analytical solution for *lnRR*'s sampling variance where $SD_{1}^2$ and $SD_{2}^2$ are the sample variance in group 1 and 2, respectively, and $N_{1}$ and $N_{2}$ are the sample size in group 1 and 2.
@@
 
-It will not be possible to always derive an effect size that completely controls for nuisance heterogeneity at the effect size level all the time.
+It will not always be possible to derive an effect size that completely controls for nuisance heterogeneity at the effect size level.
 This limitation is partly because treatment effects may not be simple linear or exponential functions of the mean response, making the effect sizes we discuss above unsuitable [e.g., thermal performance curves; @Noble2018].
@@
 By including these moderators in a meta-regression model, the interpretation of the overall meta-analytic mean, $\beta_{0}$, changes.
-For example, assume we collected the change in *in ovo* testosterone dosage relative to a control group (i.e., in ng T / g yolk) for our meta-analysis on egg T effects on bird offspring traits in birds.
-If the untransformed dosage, $x_{j}$, is included in the model then the overall meta-analytic mean estimate, $\beta_{0}$, would be the mean effect of T on reproduction when the dosage difference between the treatment and control group is 0 ng T / g yolk (i.e., it would be reflective of unmanipulated eggs).
+For example, assume we collected the change in *in ovo* testosterone dosage relative to a control group (i.e., in ng T / g yolk) for our meta-analysis on egg T effects on bird offspring traits.
+If the untransformed dosage, $x_{j}$, is included in the model then the overall meta-analytic mean estimate, $\beta_{0}$, would be the mean effect of T on traits when the dosage difference between the treatment and control group is 0 ng T / g yolk (i.e., it would be reflective of unmanipulated eggs).
 Of course, this interpretation does not make much sense.
@@
 We can, however, apply some simple transformations to make the overall mean estimate more intuitive while also improving the interpretation of non-linear parameters and interactions estimated from the model [@Schielzeth2010; @GelmanHill2007].
-One simple transformation would be to centre the variable $x_{j}$ by subtracting each value from the mean to create a new input variable (i.e., $c_{j}=x_{j}-\bar{x}$, where the subscript *j* denotes each individual effect size dosage).
+One simple transformation would be to centre the variable $x_{j}$ by subtracting each value from the mean to create a new input variable (i.e., $c_{j}=x_{j}-\bar{x}$, where the subscript *j* denotes each individual effect size dosage difference).
 The new variable, $c_{j}$, is now centered on the mean and can replace $x_{j}$ in the meta-regression model.
-When the model is refit with $c_{j}$, the estimated $\beta_{0}$ can now be more intuitively interpreted as the overall mean effect of CORT on reproduction at an average dosage difference between treatment and control groups.
+When the model is refit with $c_{j}$, the estimated $\beta_{0}$ can now be more intuitively interpreted as the overall mean effect of T on offspring traits at an average dosage difference between treatment and control groups.
 Importantly, by centering, we retain the original units (ng T / g yolk) of the variable, which can be very useful to ease the interpretation of the effect magnitude (e.g., when the dosage difference is 10 ng T / g yolk).
+
 Given it is very common to estimate and compare overall meta-analytic means (i.e., $\beta_{0}$) in meta-analyses, this centering can be particularly useful in making these means more interpretable.
@@
 
-As we have already emphasised, quantifying effect size heterogeneity provides the impetus for exploring why effects might vary within and across studies, while also providing context for interpreting the generality of effects.
+As we have already emphasised, quantifying effect size heterogeneity provides the impetus for exploring why effects might vary within and across studies, while also providing context for interpreting the generality of overall effects.
 There are a number of measures commonly used to quantify effect size heterogeneity [@Borenstein2019]; however, in ecological and evolutionary meta-analysis, heterogeneity is often calculated and reported as $I_{total}^2$ as follows (if using a multilevel meta-analytic model as we describe above):
@@
 Instead, comparative physiologists might simply want to focus on biological drivers of effect size variability and want an effect size or analytic approach that allows them to remove these ‘nuisances’.
-Here, we provide a set of tools to deal with ‘nuisance heterogeneity’ (Figure \@ref(fig:fig1))by reinventing standard effect sizes and/or using mean centered nuisance variables in meta-regression models.
+Here, we provide a set of tools to deal with ‘nuisance heterogeneity’ (Figure \@ref(fig:fig1)) by reinventing standard effect sizes and/or using mean centered nuisance variables in meta-regression models.
 Estimating complex meta-regression models with a multitude of fixed effects might result, however, in more challenging model interpretation.

### 2021-07-25 supp.Rmd
Fixing bug in rendering coefficients

@@
 print(model_CS1a_MLMA)
-
+B <- coef(model_CS1a_MLMA)
 # Calculate Prediction Intervals
@@
 
-We can see from above that the model estimates an overall meta-analytic mean as `r coef(model_CS1a_MLMA)` with a 95\% CI from `r model_CS1a_MLMA$ci.lb` to `r model_CS1a_MLMA$ci.ub`.
-In other words, for each degree variation in acclimation temperature, the heat tolerance of the animals included in this data set vary by `r coef(model_CS1a_MLMA)` degrees on average.
+We can see from above that the model estimates an overall meta-analytic mean as `r model_CS1a_MLMA$b` with a 95\% CI from `r model_CS1a_MLMA$ci.lb` to `r model_CS1a_MLMA$ci.ub`.
+In other words, for each degree variation in acclimation temperature, the heat tolerance of the animals included in this data set vary by `r model_CS1a_MLMA$b` degrees on average.
 95\% of the time we expect the mean in repeated samples to fall between `r PI_CS1a_MLMA$cr.lb` and `r PI_CS1a_MLMA$cr.ub`.
@@
 
-We can see from above that the model 'ignoring' the nuisance heterogeneity (`model_CS2_MLMA_1`) (i.e., the variability in effects resulting from dosage differences across studies) estimates an overall meta-analytic mean as `r as.numeric(coef(model_CS2_MLMA_1))` with a 95\% CI from `r model_CS2_MLMA_1$ci.lb` to `r model_CS2_MLMA_1$ci.ub`.
+We can see from above that the model 'ignoring' the nuisance heterogeneity (`model_CS2_MLMA_1`) (i.e., the variability in effects resulting from dosage differences across studies) estimates an overall meta-analytic mean as `r model_CS2_MLMA_1$b` with a 95\% CI from `r model_CS2_MLMA_1$ci.lb` to `r model_CS2_MLMA_1$ci.ub`.
 Our prediction intervals suggest that heterogeneity is high, reflected in our $I_{total}^2$ estimate of `r I2_1[1]*100`\% -- 95\% of the time we expect the mean in repeated samples to fall between `r pis_MLMA_1$pi.lb` and `r pis_MLMA_1$pi.ub`.
@@
 Given that we have not controlled for dosage differences across studies, all we can say is that the average SMD is rather small in the sample of studies that have applied these sets of dosages.
-In other words, on average, the means from the treatment and control groups differ by `r coef(model_CS2_MLMA_1)` standard deviation units.
+In other words, on average, the means from the treatment and control groups differ by `r model_CS2_MLMA_1$b` standard deviation units.
 
@@
 
-We can see from our model that controls for nuisance heterogeneity (model_CS2_nuisance1) that we now estimate an overall meta-analytic mean as `r as.numeric(coef(model_CS2_nuisance1))[1]` with a 95\% CI from `r model_CS2_nuisance1$ci.lb[1]` to `r model_CS2_nuisance1$ci.ub[1]`.
+We can see from our model that controls for nuisance heterogeneity (model_CS2_nuisance1) that we now estimate an overall meta-analytic mean as `r model_CS2_nuisance1$b[1]` with a 95\% CI from `r model_CS2_nuisance1$ci.lb[1]` to `r model_CS2_nuisance1$ci.ub[1]`.
 Importantly, this is the mean effect size when the total dosage applied is 0, which doesn't make much sense.
@@
 
-Now that we have centered the total dosage around its mean (which is `r mean(data_CS2$total_dose_T, na.rm = TRUE)` ng/ g yolk, our overall meta-analytic mean (now estimated to be `r coef(model_CS2_nuisance2)[1]`,  with a 95\% CI from `r model_CS2_nuisance2$ci.lb[1]` to `r model_CS2_nuisance2$ci.ub[1]`) is interpreted differently.
-Overall, the meta-analytic mean difference between treatments that differ by an average of `r mean(data_CS2$total_dose_T, na.rm = TRUE)` ng/ g yolk is `r coef(model_CS2_nuisance2)[1]` standard deviation units different.
-Its still a small overall effect size, but it has a clearer interpretation now.
+Now that we have centered the total dosage around its mean (which is `r mean(data_CS2$total_dose_T, na.rm = TRUE)` ng/ g yolk, our overall meta-analytic mean (now estimated to be `r model_CS2_nuisance2$b[1]`,  with a 95\% CI from `r model_CS2_nuisance2$ci.lb[1]` to `r model_CS2_nuisance2$ci.ub[1]`) is interpreted differently.
+Overall, the meta-analytic mean difference between treatments that differ by an average of `r mean(data_CS2$total_dose_T, na.rm = TRUE)` ng/ g yolk is `r model_CS2_nuisance2$b[1]` standard deviation units different.
+It's still a small overall effect size, but it has a clearer interpretation now.
 We can again calculate PI's and $I^2$ using the model.
@@
 
-## Additional Survey Results
+# Supplementary Survey Results
 

### 2021-09-17 MS/ms.Rmd
Fixed MS
Fixed Figure 1 and 3 legends

@@
 Heterogeneity can come in various forms, from effect measures varying as a result of shared evolutionary history (i.e., phylogeny), the different trait types measured, and sources of 'nuisance heterogeneity'.
-In this example, nuisance heterogeneity is generated by differences in the experimental temperatures at which the animals were tested.
+In this example, nuisance heterogeneity is generated by differences in the experimental temperatures at which the animals were tested ('gray' shaded area on top).
 However, nuisance heterogeneity can come in various other forms such as differences in dosage.
-We can control for these types of heterogeniety by reformalising effect sizes and/or using multilevel metaregression."}
+We can control for these types of heterogeniety by reformalising effect sizes and/or using multilevel metaregression ('white' area on the bottom)."}
 image <- image_read(here::here("figs", "Fig1_v2_ML.png"))
@@
 
-## **Opening Up New Opportunities in Comparative Physiology: Expanding the Breadth of Effect Sizes to Deal with "Nuisance Heterogeneity"**
+## **Opening New Opportunities in Comparative Physiology: Expanding the Breadth of Effect Sizes to Deal with "Nuisance Heterogeneity"**
 
@@
 By combining traditional effects with physiological parameters, and correcting the resulting quantities for nuisance variation, we can derive a new generation of biologically relevant, easily interpretable effect measures for use in meta-analyses (‘Expanded’; bottom).
-For abbreviations, see Table 1."}
+For abbreviations of common effect sizes see Table 1.
+lnRRQ10 = Q10 response ratio; lnCVRQ10 = log Q10 coefficient of variation ratio; SMDT = Temperature corrected standardised mean difference; ARR = acclimation response ratio."}
 image <- image_read(here::here("figs", "Fig0_v1_ML.png"))

### 2021-09-17 MS/ms.Rmd
Fixed BPA to generalise a bit to pollutants

@@
         "Variability in CTmin, CTmax, Metabolic Rate (MR)",
-        "Ratio between BPA treatment (BPA-exposed group) and control (no BPA)",
+        "Ratio between pollutant exposed treatment (e.g., BPA-exposed group) and control (no pollutant)",
         "Difference in immune response between males and females or performance difference in the presence of stressor compared to absence of stressor",

### 2021-09-17 MS/ms.Rmd
Fixed a few more thigs

@@
 Meta-analyses answer research questions by synthesising research results and identifying sources of variation across studies [@Nakagawa2017; @Gurevitch1999; @Gurevitch2018; @Cooper2009; @Arnqvist1995; @Koricheva2013; @Borenstein2019].
-Ideally, meta-analyses are part of a systematic review and methods are carefully reported upon to ensure the review and data collation are transparent and reproducible [i.e., see the Preferred Reporting Items for Systematic Reviews and Meta-Analyses in Ecology and Evolutionary Biology (PRISMA-EcoEvo) checklist, @ODea2021].
+Ideally, meta-analyses are part of a systematic review.
+As such, methods are carefully reported upon to ensure the review and data collation are transparent and reproducible [i.e., see the Preferred Reporting Items for Systematic Reviews and Meta-Analyses in Ecology and Evolutionary Biology (PRISMA-EcoEvo) checklist, @ODea2021].
 
@@
 By expressing study effects on a common scale (i.e., standardised effect size) we can gain broader insight into the direction and efficacy of a particular treatment effect or the strength of a relationship between two variables of interest [@Gurevitch2018; @Koricheva2013].
-Meta-analyses have already provided comparative physiologists with powerful insights on pressing global challenges -- from testing whether physiological plasticity can buffer organisms against climate change [e.g, @Seebacher2015] to the degree to which endocrine disrupting chemicals, such as bis-phenol A (BPA), impact aquatic organisms [e.g., @WuSeebacher2020].
+Meta-analyses have already provided comparative physiologists with powerful insights on pressing global challenges -- from testing whether physiological plasticity can buffer organisms against climate change [e.g, @Seebacher2015] to the degree to which endocrine disrupting chemicals, such as bisphenol A (BPA), impact aquatic organisms [e.g., @WuSeebacher2020].
 
@@
 Narrative reviews and comments were not considered because they did not collate quantitative data from the literature.
-Studies needed to have collected physiological trait data, such as hormone levels, thermal physiological parameters (CTmax, CTmin, thermal preferences, thermal breadth, LT50, lethal thresholds), metabolic rates (routine, maximum, and minimum metabolic rate, aerobic scope), enzyme reaction rates and concentrations, oxidative stress measures and consequences (e.g., DNA damage, teleomere attrition), performance measurements (e.g., heart rates, sprint speed, swim speed, growth rates), body composition (e.g., fatty acid profiles) and immune traits (e.g., cell function, antibodies).
+Studies needed to have collected physiological trait data, such as hormone levels, thermal physiological parameters (Critical thermal maximum (CTmax), critical thermal minimum (CTmin), thermal preferences, thermal breadth, lethal thermal tolerance limit (LT50), lethal thresholds), metabolic rates (routine, maximum, and minimum metabolic rate, aerobic scope), enzyme reaction rates and concentrations, oxidative stress measures and consequences (e.g., DNA damage, teleomere attrition), performance measurements (e.g., heart rates, sprint speed, swim speed, growth rates), body composition (e.g., fatty acid profiles) and immune traits (e.g., cell function, antibodies).
 Studies were also included if they measured the relationship between physiological traits and body size (e.g., metabolic scaling), reproductive allocation, or survival across taxa.

### 2021-09-17 MS/ms.Rmd
Fixed up legend, and some description of the lit search.

@@
 Narrative reviews and comments were not considered because they did not collate quantitative data from the literature.
-Studies needed to have collected physiological trait data, such as hormone levels, thermal physiological parameters (Critical thermal maximum (CTmax), critical thermal minimum (CTmin), thermal preferences, thermal breadth, lethal thermal tolerance limit (LT50), lethal thresholds), metabolic rates (routine, maximum, and minimum metabolic rate, aerobic scope), enzyme reaction rates and concentrations, oxidative stress measures and consequences (e.g., DNA damage, teleomere attrition), performance measurements (e.g., heart rates, sprint speed, swim speed, growth rates), body composition (e.g., fatty acid profiles) and immune traits (e.g., cell function, antibodies).
+Studies needed to have collected physiological trait data, such as hormone levels, thermal physiological parameters (Critical thermal maximum (CTmax), critical thermal minimum (CTmin), thermal preferences, thermal breadth, lethal thermal tolerance limit (LT50), lethal thresholds), metabolic rates (routine, maximum, and minimum metabolic rate, aerobic scope), enzyme reaction rates and concentrations, oxidative stress measures and consequences (e.g., DNA damage, teleomere attrition), performance (e.g., maximum heart rates, sprint speed, swim speed) and growth rates, body composition (e.g., fatty acid profiles) and immune traits (e.g., cell function, antibodies).
 Studies were also included if they measured the relationship between physiological traits and body size (e.g., metabolic scaling), reproductive allocation, or survival across taxa.
 Studies on behavior were only included if the synthesis was explicitly interested in the proximate physiological drivers of behavioral variation.
-We also included meta-analyses that quantified plasticity in physiological traits in response to environmental variation.
+We also included meta-analyses that quantified the change in physiological traits in response to environmental variation (i.e., phenotypic plasticity).
 While many studies in comparative physiology collect data as part of a comparative analysis, we focus here only on studies collating data from existing literature because this is the major data source in quantitative syntheses.
-We excluded quantitative syntheses interested in phenology, bio-mechanics, sexual size dimorphism (i.e., except if the study was interested in sexual differences in physiological traits), those focused on validating physiological methodology, or characterising population genetic structure, gene transcription, and quantitative genetics.
+We excluded quantitative syntheses interested in phenology, biomechanics, sexual size dimorphism (i.e., except if the study was interested in sexual differences in physiological traits), those focused on validating physiological methodology, or characterising population genetic structure, gene transcription, and quantitative genetics.
 There were also meta-analyses that focused on colour evolution which varied in their goals but were most often not focused on physiological questions.
@@
 ```{r, figsurv, fig.wid = 16.833333, fig.height=5,fig.cap="**Summary of meta-analytic practices in comparative physiology.** (A) Different types of effect measures commonly used in meta-analyses and their relative frequency of use.
-(B) (B) Frequencies of studies where ‘nuisance heterogenity’ had the potential to impact effect sizes (x-axis), and the frequencies of studies explicitly dealing with nuisance heterogeneity (bar colour).
+(B) Frequency of studies where ‘nuisance heterogenity’ had the potential to impact effect sizes (x-axis), and the frequencies of studies explicitly dealing with nuisance heterogeneity (bar colour).
 (C) Frequencies of analytical approaches used to analyse effect measures.

### 2021-09-17 MS/ms.Rmd
Fixing figure. Some small changes in levels in data.

@@
   colSums(.) %>% data.frame(effect = names(.), n = .) %>% mutate(prop = n / sum(n)) %>% arrange(effect) %>% 
-  mutate(effect = fct_relevel(effect, c("Other", "Zr", "lnRR", "SMD", "lnCVR", "Slope", "Means"))) %>% 
+  mutate(effect = fct_relevel(effect, c("Other", "Zr", "lnRR", "SMD", "lnCVR", "Slope", "Mean"))) %>% 
   ggplot() + tm + 
@@
 p3 <- summary %>% 
-  mutate(effect = fct_relevel(effect, c("Other","Vote Counting", "Linear Regression", "Weighted Regression", "Random-Effects Model", "Multilevel Meta-analysis Model", "Multilevel Metaregression Model"))) %>%
+  mutate(effect = fct_relevel(effect, c("Other","Vote Counting", "Linear Regression", "Weighted Regression", "Random Effects Model", "Multilevel Meta-analysis Model", "Multilevel Metaregression Model"))) %>%
   ggplot() + tm +
@@
 For example, assume that we were interested in the overall impact of salinity stress in freshwater fish.
-To tackle this question, we collected experimental studies measuring fish swim performance under high salinity treatments (\~15--20ppm Na Cl) compared to freshwater (\~0ppm Na Cl) controls, using *SMD* to quantify the effect salinity had on swim performance.
+To tackle this question, we collected experimental studies measuring fish swimming performance under high salinity treatments (\~15--20ppm Na Cl) compared to freshwater (\~0ppm Na Cl) controls, using *SMD* to quantify the effect salinity had on swim performance.
 We conduct a meta-analysis and estimate an overall *SMD* of 0.50 with a 95% prediction interval of 0.05 to 0.85.

### 2021-09-17 MS/ms.Rmd
Fixed figure so that weighted models are now coloured

@@
     # If you have issues with flextable and equatags, make sure you have node.js and use mathjax_install(). See here:https://github.com/ardata-fr/equatags
-  pacman::p_load(flextable, tidyverse, equatags, png, magick)  
+  pacman::p_load(flextable, tidyverse, equatags, png, magick, RColorBrewer)  
 ```
@@
 (C) Frequencies of analytical approaches used to analyse effect measures.
-Note that only ‘Weighted Regression’, ‘Random Effects Models’, ‘Multilevel Metaregression Models’ and ‘Multilevel Meta-analysis Models’ are weighted models.
+'Orange' bars indicate weighted models.
 The results of this survey were drawn from 62 studies in comparative physiology."}
@@
 p3 <- summary %>% 
-  mutate(effect = fct_relevel(effect, c("Other","Vote Counting", "Linear Regression", "Weighted Regression", "Random Effects Model", "Multilevel Meta-analysis Model", "Multilevel Metaregression Model"))) %>%
+  mutate(effect = fct_relevel(effect, c("Other","Vote Counting", "Linear Regression", "Weighted Regression", "Random Effects Model", "Multilevel Meta-analysis Model", "Multilevel Metaregression Model")),
+              col = c("#66C2A5", "#8DA0CB", "#8DA0CB", "#66C2A5", "#8DA0CB", "#66C2A5", "#8DA0CB")) %>% 
   ggplot() + tm +
-  geom_col(aes(x = effect, y = prop), width = 0.5, fill = "black", colour = text.colour, size = 0.5) +
+  geom_col(aes(x = effect, y = prop, fill = col), width = 0.5,colour = text.colour, size = 0.5) +
   scale_y_continuous(expand=c(0,0),limits = c(0,0.4)) +
+  scale_fill_brewer(palette = "Set2") + 
   labs(x = "Analytical Approach",
        y = "Frequency") +
+  theme(legend.position = "none") +
   coord_flip()

### 2021-09-18 MS/ms.Rmd
Fixed more minor revisions. Need to add a couple more refs

@@
 Here, we dispel this myth by showing how standardised effects sizes can be used in conjunction with multilevel meta-regression models to both account for the factors driving differences across studies and make them more comparable.
-We formalise effect size measures (e.g., $Q_{10}$) that provide comparative physiologists with a means to remove nuisance heterogeneity without the need to resort to more complex statistical models that may be harder to interpret.
+We formalise effect size measures (e.g., the temperature coefficient, $Q_{10}$) that provide comparative physiologists with a means to remove nuisance heterogeneity without the need to resort to more complex statistical models that may be harder to interpret.
 We also describe more general approaches that can be applied to a variety of different contexts to derive new effects sizes and sampling variances opening new possibilities.
@@
 As can be seen in Table \@ref(tab:tablea), none of the effect measures control for nuisance heterogeneity.
-For example, the magnitude of *lnRR* or *SMD* might depend on differences in the temperatures, dosages, pH, or water potential applied to each treatment.
+For example, the magnitude of *lnRR* or *SMD* might depend on differences in the temperatures, dosages, or pH applied to each treatment.
 The same applies to modelling the means.
@@
 We highlight two examples in Box 1 that can be easily generalized to alternative effect size measures and cases.
-Below, we show how we can formalise a traditional effect size, such as $lnRR$, to capture this nuisance variation using a common, well understood effect measure of interest to comparative physiologists ($Q_{10}$).
+Below, we show how we can formalise a traditional effect size, such as $lnRR$, to capture this nuisance variation.
+We use a common, well understood, effect measure of interest to comparative physiologists -- the temperature coefficient ($Q_{10}$).
 Figure \@ref(fig:fig0) summarises the different effect sizes that we mention in Table 1, Box 1 and the section below.

### 2021-09-18 MS/ms.Rmd
Added refs to the examples of effect size metrics

@@
 The key features of all effect sizes used in meta-analyses are that: 1) they are statistical parameters that have been placed on a common scale so that they can be compared across studies and 2) they have some associated measure of precision (i.e., sampling variance) [@Koricheva2013; @Borenstein2009; @Schmid2021].
-Effect sizes in comparative physiology are quite diverse; they can be the mean difference between two groups [e.g., difference in mean between a control and treatment group; e.g., @WuSeebacher2020], the slope of a regression (e.g., between body size and metabolic rate), a correlation between two variables (e.g., between hormone levels and behaviour), or even the raw mean (or variance) itself [e.g., comparing CTmax or CTmin across species - e.g., @Sunday2014].
+Effect sizes in comparative physiology are quite diverse; they can be the mean difference between two groups [e.g., difference in mean between a control and treatment group; e.g., @WuSeebacher2020], the slope of a regression [e.g., between body size and metabolic rate, @Uyeda2017], a correlation between two variables [(]e.g., between hormone levels and behaviour, @Holtman2016], or even the raw mean (or variance) itself [e.g., comparing CTmax or CTmin across species - e.g., @Sunday2014].
 In many cases, different effect sizes might be used depending on the question.

### 2021-09-18 MS/box.Rmd
Fixed box formatting error
Fixed wording in box

@@
 
-Here, we show how to obtain sampling variance for a slope (or a 'rate of change') when you have measurements of a physiological trait at two points along an environmental gradient (e.g., temperature, salinity, acidity).
+Here, we show how to obtain sampling variance for a slope (or a 'rate of change') when you have measurements of a physiological trait at two points along an environmental gradient (e.g., temperature, salinity, pH).
 We then derive sampling variance for the difference between two slopes, and demonstrate how *SMD* can be corrected to account for differences in both units (e.g.
 cm or mg) and points on an environmental gradient (e.g.
-temperature of 24 and 30 \&degC).
+temperature of 24 and 30 °C).
 Finally, we introduce a useful approximation technique known as 'the Delta method'.

### 2021-09-18 MS/ms.Rmd
Added differences between CI and PI.

@@
 Briefly, we first did a series of pilot searches (detailed in Supplementary Materials) to refine our search query [See @Foo2021 for an overview of this process].
-We searched for studies that included: 'meta-analysis', 'meta regression' , 'comparative analysis', 'comprehensive analysis' 'global analysis' or 'macro physiology' in their title or abstract, restricting our search to key comparative physiology journals (detailed in Table S1 and S2 - Supplementary Materials) within the last 6 years.
+We searched for studies that included: 'meta-analysis', 'meta regression' , 'comparative analysis', 'comprehensive analysis' 'global analysis' or 'macro physiology' in their title or abstract.
+We restricted our search to key comparative physiology journals known to the authors that would likely contain literature-based quantitative syntheses within the last 6 years (detailed in Table S1 and S2 - Supplementary Materials).
 We expected this to provide a contemporary overview of quantitative syntheses in comparative physiology while making the survey and screening feasible.
@@
 Heterogeneity described using $I^2$ measures can be useful for understanding the relative contributions of different factors to effect size variation; however, prediction intervals might be more appropriate in many cases [@Nakagawa2021c; @Borenstein2019].
+Prediction intervals describe the range of plausible effect size values expected from a future study [@Nakagawa2021c].
+This is different from a confidence interval that expresses the range of uncertainty around a statistical parameter estimate.
 Unlike $I^2$, prediction intervals (PI's) are probably more meaningful in the context of meta-analysis because they explicitly incorporate measures of dispersion around a mean effect size.

### 2021-09-21 MS/ms.Rmd
Justed updated akwnow
Added in Laguenesse 2010

@@
 
-Meta-analysis is always concerned with effect heterogeneity; in other words, the factors that drive differences in the direction and magnitude of effects within and across studies [@Nakagawa2017; @Gurevitch2018; @Cooperetal2019; @Borenstein2019].
-The concept of heterogeneity is vitally important because it tells us how general our findings are likely to be and how much of the variance we see is the result of real biology or methodological differences (after meta-analytically accounting for sampling variance) [@Nakagawa2017; @Borenstein2019].
+Meta-analysis is always concerned with effect heterogeneity; in other words, the factors that drive differences in the direction and magnitude of effects within and across studies [@Nakagawa2017; @Gurevitch2018; @Cooperetal2019; @Borenstein2019; @Lag2010].
+The concept of heterogeneity is vitally important because it tells us how general our findings are likely to be and how much of the variance we see is the result of real biology or methodological differences (after meta-analytically accounting for sampling variance) [@Nakagawa2017; @Borenstein2019; @Lag2010].
 
@@
 Combining standardised effects, while ignoring these sources of heterogeneity can indeed weaken the reliability of a meta-analysis.
-However, many argue that heterogeneity is just what we are interested in synthesizing [@Cooperetal2019; @Borenstein2019; @Gurevitch2018; @Glass2015].
+However, many argue that heterogeneity is just what we are interested in synthesizing [@Cooperetal2019; @Borenstein2019; @Gurevitch2018; @Glass2015; @Lag2010].
 In the words of Gene Glass, the founder of meta-analysis: "Of course it [meta-analysis] mixes apples and oranges; in the study of fruit nothing else is sensible; comparing apples and oranges is the only endeavor worthy of true scientists; comparing apples to apples is trivial" [p.g., 224, @Glass2015].
@@
 We would like to thank the Editorial board (Craig Franklin, Michaela Handel and Charlotte Rutledge) for inviting us to contribute to this special issue along with feedback on previous drafts.
-We would also like to thank Megan Head for comments on a previous draft.
+We would also like to thank Megan Head and two anonymous reviewers for helpful comments on previous drafts.
 DWAN, SMD, SN, ML and REO were supported by ARC Discovery Projects (DP210101152 to DWAN, DE180100202 to SMD, and DP200100367 to SN, ML and DWAN).

### 2021-09-21 MS/ms.Rmd
Added survey statement to abstract and conclusion

@@
 Here, we dispel this myth by showing how standardised effects sizes can be used in conjunction with multilevel meta-regression models to both account for the factors driving differences across studies and make them more comparable.
-We formalise effect size measures (e.g., the temperature coefficient, $Q_{10}$) that provide comparative physiologists with a means to remove nuisance heterogeneity without the need to resort to more complex statistical models that may be harder to interpret.
+We assess the prevelance of nuisance hetrogeneity in the comparative physiology literature -- showing it is common and often not accounted for in analyses.
+We then formalise effect size measures (e.g., the temperature coefficient, $Q_{10}$) that provide comparative physiologists with a means to remove nuisance heterogeneity without the need to resort to more complex statistical models that may be harder to interpret.
 We also describe more general approaches that can be applied to a variety of different contexts to derive new effects sizes and sampling variances opening new possibilities.
@@
 Instead, comparative physiologists might simply want to focus on biological drivers of effect size variability and want an effect size or analytic approach that allows them to remove these ‘nuisances’.
+Surveying the comparative physiology literature shows that nuisance heterogenity is common, and is often not completely dealt with in a meta-analysis.
 Here, we provide a set of tools to deal with ‘nuisance heterogeneity’ (Figure \@ref(fig:fig1)) by reinventing standard effect sizes and/or using mean centered nuisance variables in meta-regression models.

### 2021-10-04 MS/ms.Rmd
Added reference to robust variance estimators
Changed wording a bit

@@
 We then formalise effect size measures (e.g., the temperature coefficient, $Q_{10}$) that provide comparative physiologists with a means to remove nuisance heterogeneity without the need to resort to more complex statistical models that may be harder to interpret.
-We also describe more general approaches that can be applied to a variety of different contexts to derive new effects sizes and sampling variances opening new possibilities.
+We also describe more general approaches that can be applied to a variety of different contexts to derive new effects sizes and sampling variances, opening up new possibilities for quantitative synthesis.
 By using effect sizes that account for components of effect heterogeneity, in combination with existing meta-analytic models, comparative physiologists can explore exciting new questions and make results from large-scale data sets more accessible, comparable and widely interpretable.
@@
 We can model these biological factors by including relevant predictors (moderator variables) and/or random effects (to account for non-independence of effects).
-By doing so, we can test predictions from hypotheses that we believe are key players impacting mean effect size and direction.
+By doing so, we can test predictions from hypotheses about the key players impacting mean effect size and direction.
 This improves our understanding of the biological world around us and helps inform on future research directions.
@@
 Importantly, if we have effect sizes that are derived from the *same* sample of organisms (e.g., because traits are measured on the same sets of individuals), then we need to remove this dependency from the calculation of each $v_{i}$; we can then model the known sampling covariance between effect sizes by modifying $\textbf{I}$ to include off-diagonals that account for this covariance [See Box 1 and @Noble2017].
+Alternatively, robust variance estimators can also be used to deal with effect size non-independence [@Song2021; @Nakagawa2021].
 The fact that we can obtain an overall estimate of sampling variance (i.e., $\sigma^2_{m}$, see below for how it is defined) is very important because it provides a way for us to understand just how much variation in effects are the result of sampling differences across studies versus other, potentially important sources of variation, such as differences in the methods applied, species differences, or even real biological effects that impact the effect size a study is likely to observe [@Nakagawa2017; @NakagawaSantos2012].

### 2021-10-04 supp.Rmd
Added the details of searches to supplement. Moved from main MS

@@
 ### Details on Study Selection
-Here we provide greater detail on the search strategy, keyword selection and the numbers of final studies included at each step pf the screening process for our survey.
+Here we provide greater detail on the search strategy, keyword selection and the numbers of final studies included at each step of the screening process for our survey.
+We searched for studies that included: ‘meta-analysis,’ ‘meta regression’ , ‘comparative analysis,’ ‘comprehensive analysis’ ‘global analysis’ or ‘macro physiology’ in their title or abstract, restricting our search to key comparative physiology journals (detailed in Table S1 and S2 - Supplementary Materials) within the last 6 years.
+The journals used and their ISSN numbers are provided in Table \@ref(tab:tabS2).
+The full search strings used to refine our search query can be found in Table \@ref(tab:tabS1).
+Initial searches were conducted in Scopus between May 16 and 18, 2021.
+We updated our survey with an additional search on September 1, 2021 with the addition of new journals (See Table \@ref(tab:tabS1) and \@ref(tab:tabS2)).
+We expected this to provide a contemporary overview of quantitative syntheses in comparative physiology while making the survey and screening feasible.
+Note that results from our final searches are the ones we used.
+
+All title, abstract and full text screening was done by two people (DWAN and ML).
+Any disagreements were resolved by discussion to reach a consensus.
+Out of the 417 papers originally identified, 79 full texts were screened for eligibility, and we included a total of 62 for final data extraction.
+We excluded N = 17 meta-/comparative analyses because they: 1) did not include physiological traits (N = 4); 2) were empirical studies that collected their own data and did not collate data from the literature (N = 10); 3) Were not actual quantitative syntheses, but rather systematic reviews (N = 1) and 4) were studies with a focus on biomechanics (N = 2).
 Figure \@ref(fig:figS1) outlines our PRSIMA flowchart detailing the number of papers hit, their sources and how many records were excluded and included at each screening phase.
-The full search strings used to refine our search query can be found in Table \@ref(tab:tabS1).
-Note that results from our final searches (25 & 28) are the ones we used.
-Our query was restricted to a pre-specified set of comparative physiology journals within the last 6 years of publication.
-The journals used and their ISSN numbers are provided in Table \@ref(tab:tabS2).
-In total, out of the 79 papers screened at the full-text stage we ended up including 62 full texts.
-We excluded N = 17 meta-/comparative analyses because they: 1) did not include physiological traits (N = 4); 2) were empirical studies that collected their own data and did not collate data from the literature (N = 10); 3) Were not actual quantitative syntheses, but rather systematic reviews (N = 1) and 4) were studies with a focus on biomechanics (N = 2).
+
+We included comparative studies / meta-analyses that were focused on physiological questions.
+Narrative reviews and comments were not considered because they did not collate quantitative data from the literature.
+Studies needed to have collected physiological trait data, such as hormone levels, thermal physiological parameters (Critical thermal maximum (CTmax), critical thermal minimum (CTmin), thermal preferences, thermal breadth, lethal thermal tolerance limit (LT50), lethal thresholds), metabolic rates (routine, maximum, and minimum metabolic rate, aerobic scope), enzyme reaction rates and concentrations, oxidative stress measures and consequences (e.g., DNA damage, teleomere attrition), performance (e.g., maximum heart rates, sprint speed, swim speed) and growth rates, body composition (e.g., fatty acid profiles) and immune traits (e.g., cell function, antibodies).
+Studies were also included if they measured the relationship between physiological traits and body size (e.g., metabolic scaling), reproductive allocation, or survival across taxa.
+Studies on behavior were only included if the synthesis was explicitly interested in the proximate physiological drivers of behavioral variation.
+We also included meta-analyses that quantified the change in physiological traits in response to environmental variation (i.e., phenotypic plasticity).
+While many studies in comparative physiology collect data as part of a comparative analysis, we focus here only on studies collating data from existing literature because this is the major data source in quantitative syntheses.
+We excluded quantitative syntheses interested in phenology, biomechanics, sexual size dimorphism (i.e., except if the study was interested in sexual differences in physiological traits), those focused on validating physiological methodology, or characterising population genetic structure, gene transcription, and quantitative genetics.
+There were also meta-analyses that focused on colour evolution which varied in their goals but were most often not focused on physiological questions.
+As such, these studies were also excluded.
+We restricted our focus to animal studies because most plant synthesis papers were focused on ecological (e.g., quantified changes in abundance and distribution of species) or agricultural questions (e.g., studies on soil microbial function, nitrogen and phosphorus capture, methane output, and greenhouse gas emissions).
 

### 2021-10-04 MS/ms.Rmd
Major overhaul of survey section. Integrates its purpose better with the heterogenity idea, splits results up into the sections where results make sense to convey to reader ...survye data on effects now in effect size section and survey on models in the mdoel section.

@@
 
+## **Nuisance Heterogeneity in Comparative Physiology**
+
 Certain types of heterogeneity, however, get in the way of understanding real biological patterns and are simply a 'nuisance' to interpreting effects.
@@
 If, however, it is not of primary interest, then it may introduce an unnecessary complication to the interpretation of the effect of diet on fish growth.
-Here, we focus on meta-analytic tools to circumvent these issues and demonstrate that the ‘apples and oranges’ problem is not really a problem at all.
 
-## **Survey of Meta-Analytic Practices in Comparative Physiology**
-
-Before overviewing strategies to deal with nuisance heterogeneity, it is worth first understanding how comparative physiologists are currently conducting meta-analyses and other quantitative syntheses.
-As such, we conducted a literature survey to better understand the different types of effect sizes being used in comparative physiology, their susceptibility to known sources of methodological / environmental variability across studies, and how these sources are controlled.
-After searching for meta-analyses and comparative analyses that tackled questions using physiological data compiled from animal studies across multiple species, we asked: 1) what type of effect size was used within the quantitative synthesis?
+Here, we focus on meta-analytic solutions to circumvent nuisance heterogeneity showing how it can easily be overcome using a number of meta-analytic tools.
+Prior to overviewing the solutions, we conducted a literature survey to better understand the different types of effect sizes being used in comparative physiology, the susceptibility of studies to nuisance heterogeneity, and how these sources are currently (if at all) being controlled for in a meta-analysis.
+More specifically we asked: 1) what type of effect size was used within the quantitative synthesis?
 2) based on the methods provided, was the effect size likely susceptible to nuisance heterogeneity?
 3) If so, was such variation accounted for in the effect size or during analysis?
-and finally, 4) how many analyses used 'weighted' meta-analytic models?
+and finally, 4) how many analyses used ‘weighted’ meta-analytic models?
 
-#### *Literature Search and Survey Data Collection*
-
-All searches were conducted in Scopus between May 16 and 18, 2021.
+All searches were conducted in Scopus between May 16 and 18, 2021, with a follow up serach on September 1, 2021 (see the Supplementary Information).
 Briefly, we first did a series of pilot searches (detailed in Supplementary Materials) to refine our search query [See @Foo2021 for an overview of this process].
@@
 We acknowledge that this may have missed some important, and influential, quantitative syntheses in the field of comparative physiology, but likely provided an informative random sample.
-
-We included comparative studies / meta-analyses that were focused on physiological questions.
-Narrative reviews and comments were not considered because they did not collate quantitative data from the literature.
-Studies needed to have collected physiological trait data, such as hormone levels, thermal physiological parameters (Critical thermal maximum (CTmax), critical thermal minimum (CTmin), thermal preferences, thermal breadth, lethal thermal tolerance limit (LT50), lethal thresholds), metabolic rates (routine, maximum, and minimum metabolic rate, aerobic scope), enzyme reaction rates and concentrations, oxidative stress measures and consequences (e.g., DNA damage, teleomere attrition), performance (e.g., maximum heart rates, sprint speed, swim speed) and growth rates, body composition (e.g., fatty acid profiles) and immune traits (e.g., cell function, antibodies).
-Studies were also included if they measured the relationship between physiological traits and body size (e.g., metabolic scaling), reproductive allocation, or survival across taxa.
-Studies on behavior were only included if the synthesis was explicitly interested in the proximate physiological drivers of behavioral variation.
-We also included meta-analyses that quantified the change in physiological traits in response to environmental variation (i.e., phenotypic plasticity).
-While many studies in comparative physiology collect data as part of a comparative analysis, we focus here only on studies collating data from existing literature because this is the major data source in quantitative syntheses.
-We excluded quantitative syntheses interested in phenology, biomechanics, sexual size dimorphism (i.e., except if the study was interested in sexual differences in physiological traits), those focused on validating physiological methodology, or characterising population genetic structure, gene transcription, and quantitative genetics.
-There were also meta-analyses that focused on colour evolution which varied in their goals but were most often not focused on physiological questions.
-As such, these studies were also excluded.
-We restricted our focus to animal studies because most plant synthesis papers were focused on ecological (e.g., quantified changes in abundance and distribution of species) or agricultural questions (e.g., studies on soil microbial function, nitrogen and phosphorus capture, methane output, and greenhouse gas emissions).
 
@@
 Notably, only model types 1--5 are weighted models because they weight effect sizes based on the inverse of their sampling variance or sample size.
-
-#### *Current Meta-analytic Practices in Comparative Physiology*
 
@@
 
+## **Opening New Opportunities in Comparative Physiology: Expanding the Breadth of Effect Sizes to Deal with Nuisance Heterogeneity**
+
+#### *Common Effect Sizes and Sampling Errors that are Useful in Comparative Physiology*
+
+The key features of all effect sizes used in meta-analyses are that: 1) they are statistical parameters that have been placed on a common scale so that they can be compared across studies and 2) they have some associated measure of precision (i.e., sampling variance) [@Koricheva2013; @Borenstein2009; @Schmid2021].
+Effect sizes in comparative physiology are quite diverse; they can be the mean difference between two groups [e.g., difference in mean between a control and treatment group; e.g., @WuSeebacher2020], the slope of a regression [e.g., between body size and metabolic rate, @Uyeda2017], a correlation between two variables [(]e.g., between hormone levels and behaviour, @Holtman2016], or even the raw mean (or variance) itself [e.g., comparing CTmax or CTmin across species - e.g., @Sunday2014].
+In many cases, different effect sizes might be used depending on the question.
+For example, to investigate the effect of temperature on a physiological trait, one can compile studies experimentally manipulating temperature and analyse the mean 'effect' by creating contrast-based effect sizes, or alternatively, just model the trait in each temperature treatment.
+The choice as to which one to use boils down to the types of data available from primary studies, the specific question of interest, and whether studies are observational or experimental in nature.
+Considering our temperature example above, if we are interested in the magnitude of change between temperature treatments, we may want to use a contrast-based effect size, such as the log response ratio, *$\ln{RR}$*.
+Instead, if we are interested in how the mean of some physiological trait changes with temperature, we may model the mean itself.
+In the latter scenario, as long as all the means are measured in the same units (e.g., degrees Celsius) or can be converted to the same units, then the mean may provide the desired answer to the original question.
+
 The results of our literature survey show that quantitative syntheses in comparative physiology commonly analyse raw summary statistics (`r with(effects, effects[effect == "Means","prop"])*100`% of studies), followed closely by Fishers transformed correlation coefficients (*Zr*) (`r with(effects, effects[effect == "Zr","prop"])*100`% of studies), standardised mean differences (*SMD*) (`r with(effects, effects[effect == "SMD","prop"])*100`%  of studies), and log response ratios (*lnRR*) (`r with(effects, effects[effect == "lnRR","prop"])*100`%, of studies) (Figure \@ref(fig:figsurv)A).
+We provide details on different effect measures and associated sample sizes in Table \@ref(tab:tablea).
 In many cases, studies make use of multiple effect size measures.
 Approximately `r with(hetero, hetero[cont_moderator_variable == "yes","percent"])*100`% of effect sizes used within the study were deemed to be impacted by nuisance heterogeneity in some form or another (Figure \@ref(fig:figsurv)B), but of the studies where this was the case, only `r with(hetero_dealt, hetero_dealt[cont_moderator_variable_modelled == "yes","percent"])*100`% of the studies clearly dealt with it (Figure \@ref(fig:figsurv)B), often through meta-regression modelling.
-Overall, `r with(weighted, weighted[meta_analysis_weighted == "weighted model","percent"])*100`% of studies used a weighted meta-analytic model; however, of the studies self described as 'meta-analyses', `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","percent"])*100`% (N = `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","n"])` of `r with(weighted_meta, sum(weighted_meta[,"n"]))`) did not account for sampling variance.
-Many studies used 'Linear Regression' (including linear and generalised linear mixed effects models) as the main type of model fit to the data (Figure \@ref(fig:figsurv)C).
-Of the studies using weighted meta-analytic models `r with(het_reported, sum(het_reported[1:2,"percent"])*100)`% (N = `r with(het_reported, sum(het_reported[1:2,"n"]))` meta-analyses) did not report any measure of heterogeneity, which is unfortunate given how important these measures are to interpreting effects.
 
@@
 ```
-
-## **Opening New Opportunities in Comparative Physiology: Expanding the Breadth of Effect Sizes to Deal with "Nuisance Heterogeneity"**
-
-#### *Common Effect Sizes and Sampling Errors that are Useful in Comparative Physiology*
-
-The key features of all effect sizes used in meta-analyses are that: 1) they are statistical parameters that have been placed on a common scale so that they can be compared across studies and 2) they have some associated measure of precision (i.e., sampling variance) [@Koricheva2013; @Borenstein2009; @Schmid2021].
-Effect sizes in comparative physiology are quite diverse; they can be the mean difference between two groups [e.g., difference in mean between a control and treatment group; e.g., @WuSeebacher2020], the slope of a regression [e.g., between body size and metabolic rate, @Uyeda2017], a correlation between two variables [(]e.g., between hormone levels and behaviour, @Holtman2016], or even the raw mean (or variance) itself [e.g., comparing CTmax or CTmin across species - e.g., @Sunday2014].
-In many cases, different effect sizes might be used depending on the question.
-For example, to investigate the effect of temperature on a physiological trait, one can compile studies experimentally manipulating temperature and analyse the mean 'effect' by creating contrast-based effect sizes, or alternatively, just model the trait in each temperature treatment.
-The choice as to which one to use boils down to the types of data available from primary studies, the specific question of interest, and whether studies are observational or experimental in nature.
-Considering our temperature example above, if we are interested in the magnitude of change between temperature treatments, we may want to use a contrast-based effect size, such as the log response ratio, *$\ln{RR}$*.
-Instead, if we are interested in how the mean of some physiological trait changes with temperature, we may model the mean itself.
-In the latter scenario, as long as all the means are measured in the same units (e.g., degrees Celsius) or can be converted to the same units, then the mean may provide the desired answer to the original question.
-We provide details on different effect measures and associated sample sizes in Table \@ref(tab:tablea).
 
@@
 
-#### *Formalising Effect Size Metrics that Compare Changes in Variability Across Treatments in the Presence of "Nuisance Heterogeneity"*
+#### *Formalising Effect Size Metrics that Compare Changes in Variability Across Treatments in the Presence of Nuisance Heterogeneity*
 
@@
 $sp_{k[i]}$ is an additional species-specific effect for the *k*th species applied to effect size *i* [i.e., these are species-specific effects because of shared ecology and other factors, @Cinar2021], $s_{j[i]}$ is the study-specific effect for the *j*th study applied to effect size *i*, $e_{i}$ is the effect size-specific effect (or within study effect, or residuals) for the *i*th effect size, and $m_{i}$ is the sampling variance effect around the *i*th effect as a result of variation in precision among each effect size, $v_{i}$ (which is known as the sampling variance for the effect).
+
 This model is a 'weighted' multilevel meta-analysis model because the estimation of the overall meta-analytic mean, $\beta_{0}$, is partially weighted by the inverse sampling variance of each effect size.
+Weighted meta-analytic models are important to use because they 1) improve precision on meta-analytic mean estimates by accounting for sampling variance; 2) allow for a formal analysis of heterogeneity; 3) and give precedence to higher quality studies (see below).
+From our survey, `r with(weighted, weighted[meta_analysis_weighted == "weighted model","percent"])*100`% of studies used a weighted meta-analytic model; however, of the studies self described as 'meta-analyses', `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","percent"])*100`% (N = `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","n"])` of `r with(weighted_meta, sum(weighted_meta[,"n"]))`) did not account for sampling variance.
+Many studies used 'Linear Regression' (including linear and generalised linear mixed effects models) as the main type of model fit to the data (Figure \@ref(fig:figsurv)C).
+Of the studies using weighted meta-analytic models `r with(het_reported, sum(het_reported[1:2,"percent"])*100)`% (N = `r with(het_reported, sum(het_reported[1:2,"n"]))` meta-analyses) did not report any measure of heterogeneity, which is unfortunate given how important these measures are to interpreting effects.
+
 Importantly, if we have effect sizes that are derived from the *same* sample of organisms (e.g., because traits are measured on the same sets of individuals), then we need to remove this dependency from the calculation of each $v_{i}$; we can then model the known sampling covariance between effect sizes by modifying $\textbf{I}$ to include off-diagonals that account for this covariance [See Box 1 and @Noble2017].
@@
 This is formalised in what we call 'heterogeneity analysis' which we describe below.
+
 Importantly, this model provides us with the answer to our question: across all the species and studies manipulating egg T, how much of an overall effect does T have on offspring traits relative to control conditions?
-
 Of course, the overall effect does not provide us with a way to interpret its magnitude in the context of how much T has been applied in the treatments used in the sample of studies.
@@
 We would like to thank the Editorial board (Craig Franklin, Michaela Handel and Charlotte Rutledge) for inviting us to contribute to this special issue along with feedback on previous drafts.
-We would also like to thank Megan Head and two anonymous reviewers for helpful comments on previous drafts.
+We would also like to thank Megan Head and two anonymous reviewers for very helpful comments on previous drafts.
 DWAN, SMD, SN, ML and REO were supported by ARC Discovery Projects (DP210101152 to DWAN, DE180100202 to SMD, and DP200100367 to SN, ML and DWAN).

### 2021-10-04 MS/box.Rmd
Added ref to ARR main effects and interaction derivation in supplement

@@
 where *T* stands for temperature in degrees Celsius and $T_{2} > T_{1}$, and $M_{1}$ and $M_{2}$ are the average physiological responses (e.g., mean CTmax) at temperature points $T_{1}$ and $T_{2}$.
+Many studies might manipulate multiple variables using a fully factorial design (e.g., temperature and pH), however, for simplicity we assume the study only manipulates temperature.
+In the supplement, we also show how to derive *ARR* from fully factorial studies (i.e., main effects and interactions).
 
@@
 $$
-\sigma^2_{AAR} = \left( \frac{1} {T_2 - T_1} \right)^2 
+\sigma^2_{ARR} = \left( \frac{1} {T_2 - T_1} \right)^2 
 \left( \frac{SD^2_{1}} {N_{1}} + \frac{SD^2_{2}} {N_{2}} \right)

### 2021-10-04 supp.Rmd
Added ARR main effects and interaction derivation to supplement

@@
 
+# Supplementary Material for Box 1
+
+In Box 1 we briefly mention how *ARR* can be derived for studies manipulating a single variable, temperature.
+In reality studies often employ a fully factorial design, manipulating two variables at once (e.g., temperture and pH).
+We can easily derive *ARR* to accomodate the estimation of the main effects of, and even the interaction between, the two variables.
+Recall that *ARR* is defined as follows:
+
+$$
+\text{ARR} = \frac{M_{1} - M_{2}}{T_2 - T_1},
+$$
+
+If we have a fully factorial study manipulating temperature and pH we can estimate the main effect of temperature across the pH treatments and its sampling error (assuming groups are independent and equal sample sizes) as:
+
+$$
+\text{ARR}_{m} = \frac{ \left( M_{pH1,T1} + M_{pH2,T1} \right) - \left( M_{pH1,T2} + M_{pH2,T2} \right)}{2\left( T_2 - T_1 \right)}
+$$
+$$
+\sigma^2_{ARR_{m}} = \left( \frac{1} {2\left( T_2 - T_1 \right)} \right)^2 
+\left( \left(\frac{SD^2_{pH1,T1}} {N_{pH1,T1}} + \frac{SD^2_{pH2,T1}} {N_{pH2,T1}}\right)+ \left(\frac{SD^2_{pH1,T2}} {N_{pH1,T2}} + \frac{SD^2_{pH2,T2}} {N_{pH2,T2}}\right) \right)
+$$
+
+The interaction (i), to be clear, can be calculated as:
+
+$$
+\text{ARR}_{m} = \frac{ \left( M_{pH1,T1} - M_{pH2,T1} \right) - \left( M_{pH1,T2} - M_{pH2,T2} \right)}{T_2 - T_1 }
+$$
+$$
+\sigma^2_{ARR_{m}} = \left( \frac{1} {T_2 - T_1} \right)^2 
+\left( \frac{SD^2_{pH1,T1}} {N_{pH1,T1}} + \frac{SD^2_{pH1,T2}} {N_{pH1,T2}}+ \frac{SD^2_{pH2,T1}} {N_{pH2,T1}} + \frac{SD^2_{pH2,T2}} {N_{pH2,T2}} \right)
+$$
 # Supplementary Materials for Survey 
-
 ### Details on Study Selection

### 2021-10-04 MS/ms.Rmd
Removed sentence in figure legend. Fixed first paragraph of new section.

@@
 
-Certain types of heterogeneity, however, get in the way of understanding real biological patterns and are simply a 'nuisance' to interpreting effects.
-In other words, if we compare different varieties of 'apples', is it still fair to synthesize these studies to understand overall effects?
-In comparative physiology, this situation might be analogous to a meta-analysis that attempts to assess the effects of diet on fish growth across different populations of a widely distributed (cosmopolitan) species.
+Certain types of heterogeneity get in the way of understanding real biological patterns and are simply a ‘nuisance’ to interpreting effects.
+Take for example a meta-analysis that attempts to assess the effects of diet on fish growth across different populations of a widely distributed (cosmopolitan) species.
 Studies might rear populations of the same fish species under different temperatures, but in the end, they are still all governed by the same thermodynamic effects on growth.
-In this situation, we are still interested in understanding overall effects, but we may question whether such a conclusion is sensible given the diversity of temperatures applied.
+In this situation, we are still interested in understanding overall diet effects, but we may question whether such a conclusion is sensible given the diversity of temperatures applied.
 If temperature differences are of direct interest, then this variable can be formally incorporated in statistical models.
 If, however, it is not of primary interest, then it may introduce an unnecessary complication to the interpretation of the effect of diet on fish growth.
+Such heterogeneity is an important  contributing factor to the ‘apples and oranges’ problems described above.
 
@@
 The key features of all effect sizes used in meta-analyses are that: 1) they are statistical parameters that have been placed on a common scale so that they can be compared across studies and 2) they have some associated measure of precision (i.e., sampling variance) [@Koricheva2013; @Borenstein2009; @Schmid2021].
-Effect sizes in comparative physiology are quite diverse; they can be the mean difference between two groups [e.g., difference in mean between a control and treatment group; e.g., @WuSeebacher2020], the slope of a regression [e.g., between body size and metabolic rate, @Uyeda2017], a correlation between two variables [(]e.g., between hormone levels and behaviour, @Holtman2016], or even the raw mean (or variance) itself [e.g., comparing CTmax or CTmin across species - e.g., @Sunday2014].
+Effect sizes in comparative physiology are quite diverse; they can be the mean difference between two groups [e.g., difference in mean between a control and treatment group; e.g., @WuSeebacher2020], the slope of a regression [e.g., between body size and metabolic rate, @Uyeda2017], a correlation between two variables [e.g., between hormone levels and behaviour, @Holtman2016], or even the raw mean (or variance) itself [e.g., comparing CTmax or CTmin across species - e.g., @Sunday2014].
 In many cases, different effect sizes might be used depending on the question.
@@
 (C) Frequencies of analytical approaches used to analyse effect measures.
-'Orange' bars indicate weighted models.
-The results of this survey were drawn from 62 studies in comparative physiology."}
+'Orange' bars indicate weighted models."}
 p1 = dat %>% dplyr::group_by(effect_size_type) %>% janitor::tabyl(effect_size_type)  %>% 

### 2021-10-07 MS/ms.Rmd
small changes
Just some editing. Reword new section

@@
 We also describe more general approaches that can be applied to a variety of different contexts to derive new effects sizes and sampling variances, opening up new possibilities for quantitative synthesis.
-By using effect sizes that account for components of effect heterogeneity, in combination with existing meta-analytic models, comparative physiologists can explore exciting new questions and make results from large-scale data sets more accessible, comparable and widely interpretable.
+By using effect sizes that account for components of effect heterogeneity, in combination with existing meta-analytic models, comparative physiologists can explore exciting new questions while making results from large-scale data sets more accessible, comparable and widely interpretable.
 
@@
 Then, we show how 'nuisance heterogeneity' in comparative physiology can be comfortably dealt with by re-formalising many existing effect size measures and / or by using multilevel meta-regression models.
-We formalise alternative effect sizes and their associated sampling variance to provide comparative physiologists with opportunities to explicitly incorporate 'nuisance heterogeneity' at the effect size level to ease their interpretation.
+We formalise alternative effect sizes and their associated sampling variance to provide comparative physiologists with opportunities to explicitly incorporate nuisance heterogeneity at the effect size level to ease their interpretation.
 Finally, we describe how more complex treatment differences, such as non-linear dosage differences, can be accommodated using multilevel meta-regression models.
@@
 Meta-analysis is always concerned with effect heterogeneity; in other words, the factors that drive differences in the direction and magnitude of effects within and across studies [@Nakagawa2017; @Gurevitch2018; @Cooperetal2019; @Borenstein2019; @Lag2010].
-The concept of heterogeneity is vitally important because it tells us how general our findings are likely to be and how much of the variance we see is the result of real biology or methodological differences (after meta-analytically accounting for sampling variance) [@Nakagawa2017; @Borenstein2019; @Lag2010].
+The concept of heterogeneity is vitally important because it tells us how general our findings are likely to be and how much of the variance we see is the result of real biology or methodological differences (after accounting for sampling variance) [@Nakagawa2017; @Borenstein2019; @Lag2010].
 
@@
 
-## **Nuisance Heterogeneity in Comparative Physiology**
+## **Nuisance Heterogeneity Complicates Meta-analytic Interpretations**
 
-Certain types of heterogeneity get in the way of understanding real biological patterns and are simply a ‘nuisance’ to interpreting effects.
+Nuisance heterogeneity can get in the way of understanding real biological patterns that interest comparative physiologists.
 Take for example a meta-analysis that attempts to assess the effects of diet on fish growth across different populations of a widely distributed (cosmopolitan) species.

### 2021-10-07 MS/ms.Rmd
Did some small wording changes to make it flow a little better in teh new section

@@
 In this situation, we are still interested in understanding overall diet effects, but we may question whether such a conclusion is sensible given the diversity of temperatures applied.
-If temperature differences are of direct interest, then this variable can be formally incorporated in statistical models.
-If, however, it is not of primary interest, then it may introduce an unnecessary complication to the interpretation of the effect of diet on fish growth.
+If temperature differences are of direct interest then this variable can be formally incorporated in statistical models.
+If, however, it is not the primary interest, then it may introduce an unnecessary complication to the interpretation of the effect of diet on fish growth.
 Such heterogeneity is an important  contributing factor to the ‘apples and oranges’ problems described above.
+Nonetheless, there is limited discussion about the ways in which it can be dealt with in the literature.
 
@@
 
-All searches were conducted in Scopus between May 16 and 18, 2021, with a follow up serach on September 1, 2021 (see the Supplementary Information).
-Briefly, we first did a series of pilot searches (detailed in Supplementary Materials) to refine our search query [See @Foo2021 for an overview of this process].
-We searched for studies that included: 'meta-analysis', 'meta regression' , 'comparative analysis', 'comprehensive analysis' 'global analysis' or 'macro physiology' in their title or abstract.
+We searched the Scopus database between May 16 and 18, 2021, with a follow up search on September 1, 2021 (see the Supplementary Information).
+After a series of pilot searches (detailed in Supplementary Materials) to refine our search string [See @Foo2021 for an overview of this process], we searched for studies that included: 'meta-analysis', 'meta regression' , 'comparative analysis', 'comprehensive analysis' 'global analysis' or 'macro physiology' in their title or abstract.
 We restricted our search to key comparative physiology journals known to the authors that would likely contain literature-based quantitative syntheses within the last 6 years (detailed in Table S1 and S2 - Supplementary Materials).
@@
 For example, trait means, such as ectothermic metabolic rate (i.e., raw/mean/proportion-based effect size), will vary depending on the temperature being measured.
-The magnitude of differences between two treatments (e.g, contrast-based effect sizes -- *SMD* or *lnRR*) might depend on the pH or dosage used in treatments, and the strength of relationship between two variables (e.g., correlation between behaviour and metabolism) might depend on the temperature context under which metabolic rate or behaviour were measured.
-Given the high heterogeneity in effects used in comparative physiology, we expected 'nuisance heterogeneity' to be common to most effect sizes.
-We categorised the types of statistical models fit in each study as: 1) fixed-effect meta-analysis; 2) random-effects meta-analysis (i.e., intercept-only model, but has random study effects); 3) multilevel meta-analysis (i.e., intercept-only model, but has multiple random effect levels such as study, species and observation-level random effects); 4) meta-regression models (i.e., a multilevel or random-effects model with fixed effects - including random effects); 5) weighted regression models (including mixed- effects models); and 6) linear regression models (including linear and generalised linear mixed-effect models, and phylogenetic least squares models) [see @NakagawaSantos2012 for discussion of models].
+The magnitude of differences between two treatments (e.g, contrast-based effect sizes -- *SMD* or *lnRR*) will depend on the pH or dosage used in treatments, and the strength of relationship between two variables (e.g., correlation between behaviour and metabolism) might depend on the temperature context under which metabolic rate or behaviour were measured.
+Given the high heterogeneity in effects used in comparative physiology, we expected nuisance heterogeneity to be common to most effect sizes.
+
+We also categorised the types of statistical models fit in each study as: 1) fixed-effect meta-analysis; 2) random-effects meta-analysis (i.e., intercept-only model, but has random study effects); 3) multilevel meta-analysis (i.e., intercept-only model, but has multiple random effect levels such as study, species and observation-level random effects); 4) meta-regression models (i.e., a multilevel or random-effects model with fixed effects - including random effects); 5) weighted regression models (including mixed- effects models); and 6) linear regression models (including linear and generalised linear mixed-effect models, and phylogenetic least squares models) [see @NakagawaSantos2012 for discussion of models].
 Notably, only model types 1--5 are weighted models because they weight effect sizes based on the inverse of their sampling variance or sample size.
+
+We summarise the results of our literature survey below while discussing solutions for dealing with nuisance heterogeneity.
 

### 2021-10-08 MS/ms.Rmd
Fixing sentences that need to be reworded

@@
 Effect sizes in comparative physiology are quite diverse; they can be the mean difference between two groups [e.g., difference in mean between a control and treatment group; e.g., @WuSeebacher2020], the slope of a regression [e.g., between body size and metabolic rate, @Uyeda2017], a correlation between two variables [e.g., between hormone levels and behaviour, @Holtman2016], or even the raw mean (or variance) itself [e.g., comparing CTmax or CTmin across species - e.g., @Sunday2014].
+
 In many cases, different effect sizes might be used depending on the question.
@@
 ```{r, figsurv, fig.wid = 16.833333, fig.height=5,fig.cap="**Summary of meta-analytic practices in comparative physiology.** (A) Different types of effect measures commonly used in meta-analyses and their relative frequency of use.
-(B) Frequency of studies where ‘nuisance heterogenity’ had the potential to impact effect sizes (x-axis), and the frequencies of studies explicitly dealing with nuisance heterogeneity (bar colour).
+(B) Frequency of studies where nuisance heterogenity had the potential to impact effect sizes (x-axis), and the frequencies of studies explicitly dealing with nuisance heterogeneity (bar colour).
 (C) Frequencies of analytical approaches used to analyse effect measures.
@@
 
-As can be seen in Table \@ref(tab:tablea), none of the effect measures control for nuisance heterogeneity.
-For example, the magnitude of *lnRR* or *SMD* might depend on differences in the temperatures, dosages, or pH applied to each treatment.
+As can be seen in Table \@ref(tab:tablea), none of the effect measures control for nuisance heterogeneity -- a point reinforced by our survey.
+For example, the magnitude of *lnRR* or *SMD* can depend on differences in the temperatures, dosages, or pH applied to each treatment.
 The same applies to modelling the means.
@@
 As such, one needs to standardise the temperature measurement to compare across studies [@White2006; @Uyeda2017] (if, of course, temperature is not of interest itself).
-While we could model this explicitly, this may not always be desirable.
+While we could model nuisance heterogeneity explicitly, this may not always be desirable.
 It can often be useful to standardise the effect to both ease its interpretation and simplify modelling.
 In Box 1, we provide readers with guidance on how comparative physiologists can apply corrections to the effect measure itself.
-We highlight two examples in Box 1 that can be easily generalized to alternative effect size measures and cases.
-Below, we show how we can formalise a traditional effect size, such as $lnRR$, to capture this nuisance variation.
+We highlight two examples in Box 1 that can be easily generalized to alternative effect size measures and show how they are distinct from traditional effect measures (Figure \@ref(fig:fig0)).
+Below we focus in on one familiar example to elaborate on how a traditional effect size, such as $lnRR$, can be reformalised to capture nuisance variation.
 We use a common, well understood, effect measure of interest to comparative physiologists -- the temperature coefficient ($Q_{10}$).
-Figure \@ref(fig:fig0) summarises the different effect sizes that we mention in Table 1, Box 1 and the section below.
 

### 2021-10-08 MS/ms.Rmd
Full edit

@@
 Natural log transformation of this ratio makes the effect size normally distributed (as commonly assumed by meta-analytic models).
-Equation \@ref(eq:slnRR) is the analytical solution for *lnRR*'s sampling variance where $SD_{1}^2$ and $SD_{2}^2$ are the sample variance in group 1 and 2, respectively, and $N_{1}$ and $N_{2}$ are the sample size in group 1 and 2.
+Equation \@ref(eq:slnRR) is the analytical solution for *lnRR*'s sampling variance where $SD_{1}^2$ and $SD_{2}^2$ is the sample standard deviation and $N_{1}$ and $N_{2}$ is the sample size for group 1 and 2, respectively.
 
@@
 
-## **Meta-Analytic Models to Control for and Investigate Heterogeneous Effects Within and Across Studies**
+## **Meta-Analytic Models to Control for Nuisance Heterogeneity and Investigate Heterogeneous Effects Within and Across Studies**
 
@@
 For example, dosages applied to treatments can follow quite complex non-linear relationships in relation to some mean response (e.g., quadratic relationships).
-When this occurs, we recommend comparative physiologists to apply meta-regression approaches, controlling for nuisance heterogeneity as a moderator.
+When this occurs, we recommend comparative physiologists apply meta-regression approaches, controlling for nuisance heterogeneity as a moderator.
 In many cases, this will be the easiest, or even preferred, approach because exploring drivers of heterogeneity is of prime interest in most meta-analyses anyway.
@@
 As such, it is far more likely that comparative physiologists will need to apply a multilevel meta-analytic model to control for the various sources of non-independence [@Cinar2021; @NakagawaSantos2012; @Song2021; @Nakagawa2021; @Noble2017].
-Multilevel models are also extremely useful in describing the various sources contributing to effect size variance (a feature we describe below).
+Multilevel models are also extremely useful in describing the various drivers of effect size variance (a feature we describe below).
 For the purpose of our discussion, we will assume one needs to use more advanced multilevel models.
@@
 This model is a 'weighted' multilevel meta-analysis model because the estimation of the overall meta-analytic mean, $\beta_{0}$, is partially weighted by the inverse sampling variance of each effect size.
-Weighted meta-analytic models are important to use because they 1) improve precision on meta-analytic mean estimates by accounting for sampling variance; 2) allow for a formal analysis of heterogeneity; 3) and give precedence to higher quality studies (see below).
+Weighted meta-analytic models are important to use because they: 1) improve the precision on meta-analytic mean estimates by accounting for sampling variance; 2) allow for a formal analysis of heterogeneity; 3) and give precedence to higher quality studies (see below).
 From our survey, `r with(weighted, weighted[meta_analysis_weighted == "weighted model","percent"])*100`% of studies used a weighted meta-analytic model; however, of the studies self described as 'meta-analyses', `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","percent"])*100`% (N = `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","n"])` of `r with(weighted_meta, sum(weighted_meta[,"n"]))`) did not account for sampling variance.
@@
 
-#### *Multilevel Meta-regression to Understand Variation and Improve Interpretation*
+#### *Multilevel Meta-regression to Understand Variation, Account for Nuisance Heterogeneity and Improve Effect Interpretation*
 
-Heterogeneity among effects that result from 'nuisance heterogeneity' can be dealt with using multilevel meta-regression models.
+Heterogeneity among effects that result from nuisance heterogeneity can be dealt with using multilevel meta-regression models.
 Multilevel meta-regression models include all the same random effects that we have already discussed, but they also include fixed effects (i.e., predictors or moderators) that attempt to explain changes in the mean effect size.
@@
 Note that this formula does not include $\sigma^2_{m}$ as sampling error variance is assumed to be known in meta-analysis, as explained above.
-When including continuous moderators, such as dosage, temperature, salinity, and even pH, $R^2_{marginal}$ provides a formal means to assess just how much variation in effects is the result of 'nuisance' heterogeneity at the effect size level.
+When including continuous moderators, such as dosage, temperature, salinity, and even pH, $R^2_{marginal}$ provides a formal means to assess just how much variation in effects is the result of nuisance heterogeneity.
 Other biological moderators of interest could also be included as fixed effects and $R^2_{marginal}$ can be calculated for each independently, or all together.
 Importantly, moderators could be those that explain variation at the effect size level (i.e., dosage, temperature) or variation at the study or species level (e.g., reproductive mode, endothermy, etc.).
-$R^2_{marginal}$, or how we like to think of it in this context as $R^2_{nuisance}$, maybe a useful measure to help readers understand just how much effect variation can result from the specific treatment application.
+$R^2_{marginal}$, or how we like to think of it in this context as $R^2_{nuisance}$, may be a useful measure to help readers understand just how much effect variation can result from the specific treatment application.
 If the heterogeneity is high as a result of, say, dosage differences, then it is clear that the choice of dosage will have a critical impact on the effect of interest.
@@
 Surveying the comparative physiology literature shows that nuisance heterogenity is common, and is often not completely dealt with in a meta-analysis.
-Here, we provide a set of tools to deal with ‘nuisance heterogeneity’ (Figure \@ref(fig:fig1)) by reinventing standard effect sizes and/or using mean centered nuisance variables in meta-regression models.
+Here, we provide a set of tools to deal with nuisance heterogeneity (Figure \@ref(fig:fig1)) by reinventing standard effect sizes and/or using mean centered nuisance variables in meta-regression models.
 Estimating complex meta-regression models with a multitude of fixed effects might result, however, in more challenging model interpretation.
-As such, a combined approach, where some of the known heterogeneity is dealt with by using an appropriate effect size and associated sampling variance while other biologically interesting moderators are fit in a meta-regression model might be desired.
+As such, a combined approach might be more desirable.
+Nuisance heterogeneity can be dealt with by using an appropriate effect size and associated sampling variance in combination with meta-regression models that contain moderators that test biological hypotheses of interest.
 Indeed, this may even be a necessity to simplify the model.
-The set of tools we describe provide clarification around importance and limitations of heterogeneity.
+The set of tools we describe provide clarification around the importance and limitations of heterogeneity.
 We also hope to provide new ways to help comparative physiologists communicate effect measures more richly to guide our understanding and decisions around pressing global challenges.

### 2021-10-08 supp.Rmd
Fixing supplement formatting error

@@
 $$
+
+We can apply similar logic to other effect size measures  of interest.
+
 # Supplementary Materials for Survey 

### 2021-10-08 supp.Rmd
Added new PRISMA
Updated PRISMA text

@@
 Any disagreements were resolved by discussion to reach a consensus.
-Out of the 417 papers originally identified, 79 full texts were screened for eligibility, and we included a total of 62 for final data extraction.
+Out of the 426 papers originally identified, 80 full texts were screened for eligibility, and we included a total of 63 for final data extraction.
 We excluded N = 17 meta-/comparative analyses because they: 1) did not include physiological traits (N = 4); 2) were empirical studies that collected their own data and did not collate data from the literature (N = 10); 3) Were not actual quantitative syntheses, but rather systematic reviews (N = 1) and 4) were studies with a focus on biomechanics (N = 2).
@@
 
-img1 <- readPNG(here::here("figs", "PRISMA_diagram_v0.png"))
+img1 <- readPNG(here::here("figs", "PRISMA_diagram_v1.png"))
 
@@
             flextable::compose(j = 5, part = "header", value = as_paragraph(as_b("Comments")))          %>% 
-            flextable::compose(j = 6, part = "header", value = as_paragraph(as_b("Notes"))) 
+            flextable::compose(j = 6, part = "header", value = as_paragraph(as_b("Notes"))) %>% 
+  width(j = 3, 8)
  table_s1

### 2021-10-08 supp.Rmd
Added ref to Patrice's study

@@
 In this example, we will account for effects of known drivers of nuisance heterogeneity at the level of the effect size.
-We use a case study by Pottier et al.
-*in review* which investigated the association between acclimation temperature, thermal tolerance and sex.
+We use a case study by @Pottier2021 which investigated the association between acclimation temperature, thermal tolerance and sex.
 We first demonstrate how to use meta-analytic approaches to investigate the variation in the relationship between acclimation temperature and thermal tolerance (i.e.
@@
 
-In this example, we use a simplified data set from Pottier et al.
-*in review*, and we demonstrate how to investigate the mean effect of acclimation temperature on heat tolerance.
+In this example, we use a simplified data set from @Pottier2021, and we demonstrate how to investigate the mean effect of acclimation temperature on heat tolerance.
 Because heat tolerance was consistently measured in degrees Celsius (`CTmax`) in the studies compiled, we can calculate the slope between acclimation temperature and heat tolerance, which is termed as the acclimation response ratio (`ARR`) in the literature.
@@
 Then, we can run the multi-level meta-analytic model using the `rma.mv` function in the `metafor` package.
+
 In this model, we used two random effects: `species_ID` and `es_ID` to account for between species variation and the variation associated with the residuals.
@@
 95\% of the time we expect the mean in repeated samples to fall between `r PI_CS1a_MLMA$cr.lb` and `r PI_CS1a_MLMA$cr.ub`.
+
 Our prediction intervals suggest that heterogeneity is high, reflected in our $I_{total}^2$ estimate of `r I2_CS1a[1]*100`\%.

### 2021-10-08 MS/box.Rmd
Final fixes to send out. Added Patrice's paper

@@
 
-Let's start with a real example that comparative physiologists can easily relate with, the slope of responses to temperature acclimation, or as we call it, the acclimation response ratio (*ARR*).
+Let's start with a real example that comparative physiologists can easily relate with, the slope of responses to temperature acclimation, or as we call it, the acclimation response ratio (*ARR*) [@Pottier2021].
 *ARR* can be defined as a slope for acclimated physiological responses at two different temperature points, defined as:

### 2021-10-12 MS/ms.Rmd
Updated PRISMA text
Fixed up Patrice's comments

@@
 Finally, we describe how more complex treatment differences, such as non-linear dosage differences, can be accommodated using multilevel meta-regression models.
-We hope that, by expanding the meta-analytic toolkit, it will provide new opportunities for comparative physiologists to address how organisms will cope with rapidly changing environments and anthropogenic stressors in the future.
+We hope that expanding the meta-analytic toolkit will provide new opportunities for comparative physiologists to address how organisms will cope with rapidly changing environments and anthropogenic stressors in the future.
 
@@
 For example, given the very different physiology of aquatic mammals and fish, understanding an overall combined effect on reproduction may not be particularly relevant and may even be misleading.
-It may, therefore be more useful to understand overall effects in each of these groups separately, and assess the extent to which they differ.
+It may, therefore, be more useful to understand overall effects in each of these groups separately, and assess the extent to which they differ.
 
@@
 In this situation, we are still interested in understanding overall diet effects, but we may question whether such a conclusion is sensible given the diversity of temperatures applied.
-If temperature differences are of direct interest then this variable can be formally incorporated in statistical models.
+If temperature differences are of direct interest, then this variable can be formally incorporated in statistical models.
 If, however, it is not the primary interest, then it may introduce an unnecessary complication to the interpretation of the effect of diet on fish growth.
@@
 We searched the Scopus database between May 16 and 18, 2021, with a follow up search on September 1, 2021 (see the Supplementary Information).
-After a series of pilot searches (detailed in Supplementary Materials) to refine our search string [See @Foo2021 for an overview of this process], we searched for studies that included: 'meta-analysis', 'meta regression' , 'comparative analysis', 'comprehensive analysis' 'global analysis' or 'macro physiology' in their title or abstract.
+After a series of pilot searches (detailed in Supplementary Materials) to refine our search string [See @Foo2021 for an overview of this process], we searched for studies that included: 'meta-analysis', 'meta regression', 'comparative analysis', 'comprehensive analysis' 'global analysis' or 'macro physiology' in their title or abstract.
 We restricted our search to key comparative physiology journals known to the authors that would likely contain literature-based quantitative syntheses within the last 6 years (detailed in Table S1 and S2 - Supplementary Materials).
@@
 Any disagreements were resolved by discussion to reach a consensus.
-Out of the 417 papers originally identified, 79 full texts were screened for eligibility, and we included a total of 62 for final data extraction.
+Out of the 426 papers originally identified, 80 full texts were screened for eligibility, and we included a total of 63 for final data extraction.
 For full details on the search strings used, search dates, the number of papers found, and our PRISMA flowchart (along with reasons for exclusion at the full text stage) we refer readers to the Supplementary Information.
@@
         "Ratio between pollutant exposed treatment (e.g., BPA-exposed group) and control (no pollutant)",
-        "Difference in immune response between males and females or performance difference in the presence of stressor compared to absence of stressor",
+        "Difference in immune response between males and females, performance difference in the presence of stressor compared to absence of stressor",
         "Relationship between sex hormones and immune responses or metabolic rate and behaviour")
@@
 Importantly, this model provides us with the answer to our question: across all the species and studies manipulating egg T, how much of an overall effect does T have on offspring traits relative to control conditions?
-Of course, the overall effect does not provide us with a way to interpret its magnitude in the context of how much T has been applied in the treatments used in the sample of studies.
+Of course, the overall effect does not provide us with a way to interpret its magnitude in the context of how much testosterone (T) has been applied in the treatments used in the sample of studies.
 The most we can say about it is that the effect is small, moderate or large given the sample of effect sizes extracted from this set of studies.

### 2021-11-15 MS/ms.Rmd
Small revisions to text

@@
 
-Importantly, if we have effect sizes that are derived from the *same* sample of organisms (e.g., because traits are measured on the same sets of individuals), then we need to remove this dependency from the calculation of each $v_{i}$; we can then model the known sampling covariance between effect sizes by modifying $\textbf{I}$ to include off-diagonals that account for this covariance [See Box 1 and @Noble2017].
+Importantly, if we have effect sizes that are derived from the *same* sample of organisms (e.g., because traits are measured on the same sets of individuals), then we need to remove this dependency from the calculation of each $v_{i}$; we can then account for the assumed sampling covariance between effect sizes by modifying $\textbf{I}$ to include off-diagonals that describe this covariance [See Box 1 and @Noble2017].
 Alternatively, robust variance estimators can also be used to deal with effect size non-independence [@Song2021; @Nakagawa2021].

### 2021-11-17 MS/ms.Rmd
Update to MS to include link to supplement

@@
 
-We searched the Scopus database between May 16 and 18, 2021, with a follow up search on September 1, 2021 (see the Supplementary Information).
+We searched the Scopus database between May 16 and 18, 2021, with a follow up search on September 1, 2021 (see the Supplementary Information at https://daniel1noble.github.io/nuisance_hetreogeneity/).
 After a series of pilot searches (detailed in Supplementary Materials) to refine our search string [See @Foo2021 for an overview of this process], we searched for studies that included: 'meta-analysis', 'meta regression', 'comparative analysis', 'comprehensive analysis' 'global analysis' or 'macro physiology' in their title or abstract.
-We restricted our search to key comparative physiology journals known to the authors that would likely contain literature-based quantitative syntheses within the last 6 years (detailed in Table S1 and S2 - Supplementary Materials).
+We restricted our search to key comparative physiology journals known to the authors that would likely contain literature-based quantitative syntheses within the last 6 years (detailed in Supplemental Tables).
 We expected this to provide a contemporary overview of quantitative syntheses in comparative physiology while making the survey and screening feasible.
@@
 Instead, if we are interested in how the mean of some physiological trait changes with temperature, we may model the mean itself.
-In the latter scenario, as long as all the means are measured in the same units (e.g., degrees Celsius) or can be converted to the same units, then the mean may provide the desired answer to the original question.
+In the latter scenario, if all the means are measured in the same units (e.g., degrees Celsius) or can be converted to the same units, then the mean may provide the desired answer to the original question.
 
@@
 Estimating an overall mean and 95% CI is generally done with a simple random-effects or multilevel meta-analytic model that accounts for effect size sampling error [@Nakagawa2017; @NakagawaSantos2012].
-More often than not, meta-analyses in comparative physiology will have complex hierarchical structure.
+Often, meta-analyses in comparative physiology will have complex hierarchical structure.
 For example, multiple effect sizes may be taken from a single study on traits measured on the same individuals or from many different species that share an evolutionary history [@Cinar2021; @Noble2017].
@@
 Weighted meta-analytic models are important to use because they: 1) improve the precision on meta-analytic mean estimates by accounting for sampling variance; 2) allow for a formal analysis of heterogeneity; 3) and give precedence to higher quality studies (see below).
-From our survey, `r with(weighted, weighted[meta_analysis_weighted == "weighted model","percent"])*100`% of studies used a weighted meta-analytic model; however, of the studies self described as 'meta-analyses', `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","percent"])*100`% (N = `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","n"])` of `r with(weighted_meta, sum(weighted_meta[,"n"]))`) did not account for sampling variance.
+From our survey, `r with(weighted, weighted[meta_analysis_weighted == "weighted model","percent"])*100`% of studies used a weighted meta-analytic model; however, of the studies self-described as 'meta-analyses', `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","percent"])*100`% (N = `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","n"])` of `r with(weighted_meta, sum(weighted_meta[,"n"]))`) did not account for sampling variance.
 Many studies used 'Linear Regression' (including linear and generalised linear mixed effects models) as the main type of model fit to the data (Figure \@ref(fig:figsurv)C).
@@
 As we have already emphasised, quantifying effect size heterogeneity provides the impetus for exploring why effects might vary within and across studies, while also providing context for interpreting the generality of overall effects.
-There are a number of measures commonly used to quantify effect size heterogeneity [@Borenstein2019]; however, in ecological and evolutionary meta-analysis, heterogeneity is often calculated and reported as $I_{total}^2$ as follows (if using a multilevel meta-analytic model as we describe above):
+There are several measures commonly used to quantify effect size heterogeneity [@Borenstein2019]; however, in ecological and evolutionary meta-analysis, heterogeneity is often calculated and reported as $I_{total}^2$ as follows (if using a multilevel meta-analytic model as we describe above):
 
@@
 In addition, if we were to repeat a similar study, we would expect a new effect to fall within the range of 0.05 and 0.85, 95% of the time [@Borenstein2019; @Nakagawa2021c].
-This is a very intuitive interpretation of how variable effects are, yet PIs are often not reported in meta-analyses [@Nakagawa2021c], and we encourage more meta-analysts to report these (for examples of PIs, see Supplementary Materials).
+This is a very intuitive interpretation of how variable effects are, yet PIs are often not reported in meta-analyses [@Nakagawa2021c], and we encourage more meta-analysts to report these (for examples of PIs, see Supplementary Material at https://daniel1noble.github.io/nuisance_hetreogeneity/).
 
@@
 
+##Data Availability Statement
+Supplementary information, data, code and results associated with this paper can all be found at: https://daniel1noble.github.io/nuisance_hetreogeneity/.
+
 ## **References**
